### 2023-06-19 chapter_2/src/_chapter_2.qmd
I hate submodules

# How do colors convey political information and effect individual attitudes? {#sec-2}
<!--
    - Description: QMD script for chapter 1
    - Updated: 2022-12-28
    - Updated by: dcr
    - Notes:
        * Code:
            ** pre-test:
                *** 00_pre-test.py
                *** table called pre-test
            ** Scraping:
                *** CAPD
                    **** Execute 01_capd_text_scraping.ipynb interactively
                        ***** table called ch_1_capd_yard_signs
                    **** Execute 02_capd_img_scraping.ipynb interactively
                        ***** table called ch_1_capd_yard_signs
                    **** Execute 03_capd_downloading_images.py
                        ***** does so at end of 02_capd_img_scraping.ipynb
                    **** Execute 04_mit_election_lab_merge.py
                        ***** does so in the some-script-execution block below
        * Writing:
            ** First should write an annotated bibliography for this chapter
            ** Once annotated bibliography is complete, should have enough to start working on a pre-registered report for this chapter

-->

# Introduction

::: {#fig-pre-2000-logos layout-nrow="2"}
![Republicans pre-2000](../../assets/rnc_logo_pre-2000.png){#fig-republican}

![Democrats pre-2000](../../assets/dnc_logo_1960.png){#fig-democrat}

![Republicans 2023](../../assets/rnc_logo_2023.png){#fig-republican-post}

![Democrats 2023](../../assets/dnc_logo_2023.png){#fig-democrat-post}

Party logos
:::

Are colors important to politics? I argue that they convey information that matters to campaigns and voters. People rely on more than purely political information to understand politics [@pietraszewski_et-al_2015_c]. To reduce cognitive load, the affiliation detection system allows for efficient social behavior prediction by associating various cues with a group. In politics, associating Black voters with the Democratic party and White voters with the Republican party is one example [@pietraszewski_et-al_2015_c]. As Americans consistently link the colors red and blue with the Republican and Democratic parties [@elving_2014_npr;@williams_et-al_2022_jomp], as well as their connection to ideology [see @maestre_medero_2022_pr for example], we should explore whether color acts as an affiliative cue for individuals in American politics.

Existing theories of political information processing have yet to examine visual information more broadly. As a simple yet ubiquitous piece of visual information, color may have more influence over shaping political views than we give it credit. As visual information is processed automatically and faster than other forms of information [see @ames_et-al_2012_ohsn], I argue that it triggers associated neurological pathways that shape the subsequent information processing of the more traditionally considered types of political information. Such a process implies that the presence of politically-relevant colors has the potential to, directly and indirectly shape political attitudes.

I propose two studies to test these claims. Yard signs are a simple yet effective source of campaign branding for political candidates. They shape the attitudes of those who view them [@makse_et-al_2019_oup], and they can even aggregatively shape electoral outcomes [@green_et-al_2016_es]. As yard signs are a simple and static form of campaign advertising, they cannot rely heavily on more complicated forms of information. However, one form of information they rely on and vary in is their color. With these characteristics, yard signs are an ideal candidate both from a statistical standpoint and also substantive. From a statistical standpoint, as they are static forms of party branding they have fewer moving parts, reducing the statistical confounds that may increase Type I errors. From a substantive standpoint, while we understand that yard signs matter to campaigns, we have yet to systematically explore more simple design choices such as color.

In [Study 1](#sec-study-1), I propose an experiment that examines whether the public notice and whether their attitudes are shaped by "Republican Red" and "Democratic Blue" on the yard signs of a fictional candidate. In [Study 2](#sec-study-2), I examine whether campaigns react to the partisan composition of an electorate in recognition of color's importance to voter decision-making and attitude formation. First, I have informal interviews with campaign staff to determine what shapes the decisions about what colors to include on a campaign's yard sign.Second, I do this by examining how electoral context shapes variation in using these partisan colors.

I then present a pre-test that experimentally tests whether yard signs using "Republican Red," "Democrat Blue," and White lead to different perceptions of the candidate's political views. I find that a fictional candidate with a background of "Republican Red" is perceived to be more Republican, and a fictional candidate with a background of "Democrat Blue" are perceived to be more Democratic. I also find that Republican voters are more likely to report a willingness to vote for the candidate with "Republican Red" on the yard sign, and Democratic voters are more likely to vote for the candidate with "Democrat Blue" on the yard sign.

# The role of visual information in politics

A central theme of an edited issue of *The International Journal of Press/Politics* is that visual politics is important and understudied [@lilleker_2019_pm]. Those who are engaged in these questions attribute these challenges to methodological sophistication and the difficult task of interdisciplinary theorizing [@gerodimos_2019_pm; @bucy_joo_2021_ijpp].

The rise of television consumption changed the focus of the medium in the research for political communication scholars [@hall-jamieson_2014_ohpc]. In a similar way, so does the rise of image-based social media and has set new agendas. For several methodological and disciplinary reasons, the visual aspects of television were of little focus in the literature [@bucy_joo_2021_ijpp]. However, the news organizations and politicians are responding to the ubiquitous use of the public to use image-dominant social media platforms like TikTok and Instagram, by joining such platforms. They are relatively active on these platforms as well. Scholars need to make this transition to integrate the role of simple visual information into our theories of political information processing (abbreviated as *pip*) and attitude formation.

How does politically-relevant visual information matter to politics? From an evolutionary-biological perspective, visual information has been a common source of information for millions of years that a variety of single-and-multi-cell organisms rely upon to evaluate their environment [see @grabe_bucy_2009_oup, Chapter 1 for a useful discussion]. Visual information processing, as an ancient biological invention, the human brain is organized around the processing of it. Reflecting on this, many neuroscience scholars argue that visual information is the fastest form of information processing for humans. For example, even complex visual information, such as the warmth expressed in someone's facial features, is automatically and subconsciously processed in only about 33 milliseconds (abbreviated as ms) [@ames_et-al_2012_ohsn].

Approached from a different perspective, as humans are cognitive misers \index{cognitive misers}, visual information in the realm of politics provides efficient information to voters about politically-relevant actors and events [@lilleker_2019_pm]. Evidence suggests that voters rely on simple visual information in the background of an image to infer ideological positions [@dan_arendt_2021_ijpp] and that coverage reflects electability perceptions [@stewart_et-al_2021_ijpp] -- these influence reported desire to vote for the candidate. Images posted on social media by politicians provide more personalized information about them, and they take on their own styles [@lindholm_et-al_2021_ijpp; @peng_2021_ijpp], reflecting that it is an alternative source of information curated to attract support. Evidence suggests that even simple party branding on yard signs has an emotional appeal and encourages a shift in attitudes toward the person who owns the yard sign [@makse_et-al_2019_oup]. That is, even branding as simple as yard signs appears to influence the attitudes of those who view them. However, like all types of party branding, there remain questions about the individual visual components' contribution.

While visual politics is enjoying more attention from social scientists, there still needs to be more focus on the simplest visual information: color. In the context of the United States, the "Republican red" and "Democratic blue" is a relatively recent invention that likely has significant import in an era of significant effort by the parties to distinguish themselves from each other [@clifford_2020_pb] and where voters toe the party line [@utych_2020_es]. Since the 2000 presidential election, the media have consistently used red on their electoral maps in "horserace" journalism to represent Republicans and blue to represent Democrats [@elving_2014_npr]. The supposed consequence is that Democrats now report a preference for the color blue over the color red, and Republicans report a preference for the color red over the color blue [@schloss_palmer_2014_pbr]. Others have demonstrated the strategic choices that candidates make on branding choices -- including color -- based on the types of information they want to convey to voters to distinguish them from their rivals [see @williams_et-al_2022_jomp]. Beyond this, however, we have yet to develop and test theories about color's broader impacts on political information processing and attitude formation.

As the broader field of study of visual politics is under-theorized, theorizing about the use of color as a form of information is also quite limited -- perhaps even more so. The literature that does exist argues that colors are a source of visual information to classify more abstract concepts for voters. For example, in western Europe, voters are better at connecting the ideological positioning of a party with the color they use in their branding [@casiraghi_et-al_2022_pp]. The ability to do so is strengthened when the party is longer-surviving and is more prominent [@casiraghi_et-al_2022_pp]. The use of politically-relevant colors activates biases toward pre-existing ideological and partisan preferences among voters in a Spanish sample [@maestre_medero_2022_pr]. And male and female candidates in the United States use different colors -- among other things such as fonts -- in their campaign branding to convey distinguishing information about themselves [@williams_et-al_2022_jomp]. Despite the existing evidence, the particular psychological mechanisms driving this remain unclear. For example, it is unclear how colors may be organized into a cognitive schema that enables voters to quickly access and connect these colors to more complex political attitudes. Furthermore, it is unclear from existing evidence how colors may not just be associated with complex attitudes, but how they may enable political attitude formation and may strengthen existing connections between different political objects. As a jumping-off point, we can use the literature of political information processing (abbreviated as *pip*)\index{political information processing} to establish a common understanding of how political information is processed and how attitudes are formed by the processing of political information.

The first prominent model of *pip* derives from rational choice perspectives. The memory-based model of *pip* views attitudes as a weighted collection of prior information [see @zaller_1992_cup]. As individuals receive new information, they organize it into a schema that is relative to prior objects they already have encoded. By encoding this new information, the model predicts that individuals incorporate this new object with similar objects to form an attitude. This schema then may be more accessible in similar contexts and may then sample from its elements when prompted to express a political attitude. While the Receive-Accept-Sample (RAS) model accepts the view that expressed attitudes are a weighting of information most accessible at the time of attitude expression [@zaller_feldman_1992_ajps], it still presupposes that the weighting is an average of prior information.

The second prominent model challenges this latter point. The online model of *pip* contends that individuals do not evenly weigh information, but that whether they even store it in their long-term memory to access later is biased in the direction of supporting pre-existing attitudes [@lodge_taber_2013_cup]; this phenomenon is referred to as motivated reasoning by the psychology literature [@kunda_1990_pb]. This model suggests that people ignore new information that goes against their prior beliefs and that information confirmatory of their preferences is quicker to access -- referred to as hot cognition [@lodge_taber_2013_cup].

The online model conceptualizes this underlying information encoding and attitude retrieval mechanism as automatic [@lodge_taber_2013_cup]. This occurs due to the information's strong associations with valanced appraisals of the information guiding the attitude [@lodge_taber_2013_cup]. This brings political scientists closer to the dominant conceptualizations among neuroscientists and psychologists concerned with memory retrieval, encoding, and attitude formation [see @fazio_2007_sc]. Namely, that memories are encoded and retrieved quickly based on associations due to their association with valanced appraisals [@kensinger_fields_2022_ohhum]. What remains unexplored is how visual information such as color may prime individuals to engage in motivated reasoning pre-consciously. If they keep their attention on the object, what paths are activated by such information?

# Integrating color into a model of political information processing

Existing models of *pip* primarily focus on complex forms of political information such as text. As individuals process visual information before other sorts of information, we might expect that they may form a snap judgment or the initial appraisal of an object. This has several important implications, from suggesting that we broaden our theories of *pip* to reconsider what constitutes politically-relevant information to what it means for our substantive understanding of how people process political information and the calculus involved in political attitude formation.

Though the online information processing model goes a long way to inform us about how our physiology engages attitude formation and retrieval, the types of information it considers necessarily limits the theory's applicability to other forms of political information. Color and other simple visual information are processed much quicker and occur more frequently than text-based information [@mehta_zhu_2009_s]. As the color and other visual information are processed differently, we should also consider its use as political information. As visual information is affectively encoded [@cimbalo_et-al_1978_jgp], it can affect the affective state and processing of more complex information, such as text. The visual information provides a snap judgment or an impression of the object through faster processing and activates particular neurological processes that influence subsequent information appraisals [@ames_et-al_2012_ohsn]. This implies that the conclusions drawn from such *pip* models may be systematically biased without considering the upstream effects of non-text information; such as simple visual information like color.

Before expanding upon the role of colors in shaping political attitudes, let me first define an attitude as a concept. An attitude represents an accessible, valanced evaluation of associated prior information and experiences. This conceptualization fits with that of the Object-Evaluation Associations Model [@fazio_2007_sc]. As opposed to viewing attitudes as a latent collection of memories, as is done in the memory-based model of *pip* [@zaller_feldman_1992_ajps], it views attitudes as measurable evaluations of memories. As memories are at the core of an attitude, the association of memories with its evaluative component [see @kensinger_fields_2022_ohhum] contributes to the perspective that attitudes are affective. This implies that we should be able to measure attitudes but that such an operationalization requires careful consideration of the context's role in any given measure of an attitude as they result from memories [@fazio_2007_sc].

In line with the existing models of *pip*, I conceptualize attitudes as associative. This means that attitudes may be unstable - not stochastically, in any case. As attitudes are associative, they manifest slightly differently depending on the associative paths activated [@fazio_2007_sc]. The retrieval of relevant memories to the attitude depends on many factors, such as the recency of the event, the similarity of the context, and the importance or salience of the memory [@kahana_et-al_2022_ohhum]. This means that the memories retrieved to contribute to an attitude are quite variable. However, to understand where that variability comes from, we must understand the deeper processes influencing how information is encoded and later retrieved. This illustrates my need to build upon the reigning models of *pip*. Colors may act as a contextual feature that may lead to this variability in how a given set of political information may shape attitudes.

Colors are associative and are affectively encoded [@cimbalo_et-al_1978_jgp]. When individuals access a memory, they do not just recall an object, but they may recall visual information such as the color of an object [@mehta_zhu_2009_s]. Due to these features, colors can be processed unconsciously and very quickly [@mehta_zhu_2009_s]. As they are affectively encoded, their associations with particular memory contribute to the evaluative component of the memory. For example, individuals associate colors like red with anger and arousal [@valdez_mehrabian_1994], whereas individuals associate blue with things like happiness and pleasure [@dandrade_egan_1974_ae]. This means that colors are compelling as contextual information shaping the subsequent processing and integration of "traditional" forms of political information to construct an attitude. As the preference for a particular color correlates with political attitudes [@schloss_palmer_2014_pbr], they may have some causal influence upon political attitudes; rather than just a correlation with them.

According to the literature in affective neuroscience, visual information is processed in parts of the brain, such as the visual cortex [@goldstein_brockmole_2017_cl]. This will activate other areas of the brain and will make associated paths "hot." One such area is the amygdala. Neuroscientists believe that as visual information is quickly and subconsciously processed, the amygdala takes and appraises it based on the paths it activated; this generates a simple affective response to such information [@winkielman_et-al_2011_ohsn]. More complex, categorical emotion occurs later in conscious processing [@winkielman_et-al_2011_ohsn]. Once politically-relevant visual information is detected, the retina passes it to the brain. Once there, the brain attempts to classify the visual information by activating networks of neurons associated with the current information. With these activated pathways, the brain also attempts to appraise such information based on quick classification. For attitude formation, this implies that, as memories are affectively encoded [@kensinger_fields_2022_ohhum], these memories help areas such as the amygdala to appraise the current information.

These fast affective classifications are valanced rather than the more laborious categorization of specific emotions (e.g., anger, anxiety, fear, happy). What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_2000_arps], I conceptualize affect as a more extensive system that considers emotion only as a conscious classification process that occurs later than initial valanced appraisals of an object [@sander_2013_chhan; @ralph_anderson_2018_pup]. That is, emotion -- the complex classification of appraisals -- is a conscious component of affect. The pre-conscious process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_et-al_2011_ohsn; @dror_2017_er].

The pre-conscious appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_et-al_2011_jop; @ralph_anderson_2018_pup]. This has evolutionary roots for survival [@ralph_anderson_2018_pup; @parker_2003_p]. While affective appraisals can lead to complex motivations, such as anxiety leading to motivations for information seeking [@marcus_2000_arps], affective appraisals are valanced and are more automatic [@winkielman_et-al_2011_ohsn]. These affective appraisals lead to a desire to either retract or engage more with the object [@valentino_et-al_2011_jop]. The snap judgment resulting from the automatic processing of politically relevant visual information should likely lead to an affective response that motivates either a desire to engage more with the object or disengage.

While the visual information may encourage a particular immediate reaction to engage or disengage from the information, subsequent information processing and more conscious processing adjusts this initial appraisal generated by the snap judgment [@kensinger_fields_2022_ohhum]. While subsequent information may amend one's snap-judgment, the snap-judgment nevertheless influences the processing of subsequent information by activating particular paths, which is later encoded as associated with the object as it converts to a memory [@lodge_taber_2013_cup; @kensinger_fields_2022_ohhum].

@fig-snap-judgement-model presents an illustration of the snap-judgment model.

```{mermaid}
%%| label: fig-snap-judgement-model
%%| fig-cap: Snap judgement model
%%| fig-width: 6
%%{init: {'theme':'base', 'themeVariables':{'primaryColor':'#ffffff', 'primaryBorderColor': '#000000'}}}%%
graph TD;
    A[Detection of politically-relevant visual information] --> B(Activation of retrieval mechanism);
    B --> C[Memory and contiguous paths hot];
    C --> D[Appraisal of hot autonomous nervous system];
    D --> E1[Negative Valence];
    D --> E2[Positive Valence];
    E1 --> F1[Disengagement motivation];
    E2 --> F2[Attention activated];
    F1 --> |Neg. new information| G1[Encoded as negative];
    F1 --> |Pos. new information| G2[Encoded as positive];
    F2 --> |Neg. new information| G3[Encoded as negative];
    F2 --> |Pos. new information| G4[Encoded as positive];
    G1 --> H1[Strengthens negative path];
    G2 --> H2[Weakens negative path];
    G3 --> H3[Weakens positive path];
    G4 --> H4[Strengthens positive path];
    G2 --> |forgotten| H1;
    H2 --> |reinforced| G2;
    H3 --> |reinforced| G3;
    G3 --> |forgotten| H4;
```

All of this means for *pip* is that when we view political events or consume political information with a visual component, we are going to encode visual information along with it. Taking expectations formed from theories of motivated reasoning [see @kunda_1990_pb], I expect that the visual information that we encode with it is likely congruent with the evaluation of the object; we are likely to be unwilling to encode the visual information that is not congruent with the visual information as we do with text-based political information [see @lodge_taber_2013_cup]. That is because unconsciously, we will experience a motivation to disengage from such information as soon as we appraise the visual aspects of an object as incongruent with existing attitudes and, therefore, be uncomfortable. It should also influence how we retrieve memories when we encounter new information, which will affect the attitudes we express. Additionally, this predicts that we will spend less time processing, accessing, and encoding congruent information [@lodge_taber_2013_cup].

Let me illustrate the snap-judgment model with a common experience for residents of the United States. Say you are driving down a highway. At 65 miles an hour, you are traveling at about 95 feet per second at this speed. You split your attention. You focus your eyes on the conditions of the road in front of you, the cars in front of you, and the rear-view mirror where your kids are either dropping food in the crevice between the seats or trying to grab your attention. Out of the corner of your eye, you see a sign. It is not a road sign because it is not on the familiar white or yellow background with black lettering. It is election season. You correctly infer that it is a political yard sign. In this split second, you notice the sign's color and may see a name: Mitch McConnell. You now are racking your brain to think about who that is. If you are politically engaged, you might come to that recognition of the name quickly or it may take you significantly longer if you are less politically engaged [see @kahana_et-al_2022_ohhum]. You figure out that they are a Republican politician. You may have come to this with the help of the fact that every year you have seen yard signs on this stretch of highway. You know that when you see those electoral maps pop up on your news app on your phone that the electoral forecasts always represent Republican support with red and blue for Democrats. Once you have figured out who this person is, with the help of this other information, you react: "ugh, that guy is too loyal to Trump" or "yeah! He's loyal to Trump". You've expressed a political attitude.

What the snap-judgment model predicts is happening in your head is that as soon as the light that bounces off the sign to produce a particular wavelength hits your eyes, your brain is already trying to make sense of this information. This is a valuable tool for survival that biology has optimized for millions of years [@parker_2003_p]. Rather than slowly processing the visual information and finding yourself in the jaws of a predator or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and subconsciously [@newell_1990_hup]. To make sense of such information, it accesses familiar information similar to what it is currently attempting to process for efficiency [@kahana_et-al_2022_ohhum]. This is accessing memories and contains valanced information [@kensinger_fields_2022_ohhum]: should I avoid this, or is it pleasant? Once the brain has finished such processing, it can pass its prediction to your conscious memory. Once you form a reflex of avoid or approach, this opens up space for your brain to process the more complex information: to take the patterns of the light as shapes that construct symbols and letters. This comes later because this information not only requires access to information about what it *is* but also what it *means*; once you understand what it means, you have the information necessary to evaluate it.

The snap-judgment model predicts that you first process the colors of the yard sign. You access associative memory to figure out what those particular wavelengths represent: red, white, blue? As these colors are associated with different emotional states [see @cimbalo_et-al_1978_jgp] and the resulting behavioral consequences, your brain starts sending signals to the rest of your body to prepare it to react [see @sander_2013_chhan; @dror_2017_er]. You now need to figure out what the rest of that information was. What were the patterns of that light? It appears that there were some white letters on the sign. There was an "E," a "L," an "E," a "C," and a "T." That creates the word "ELECT." Meaning to vote for. There were some more letters on the sign: an "M," an "I," a "T," a "C," and an "H." A name. The full name is "Mitch McConnell". Since it is about politics, it must be a politician named Mitch McConnell. Now imagine the information was the same, except the color was blue. You may take more time to figure out how that Mitch McConnell person is and come to your reaction to seeing their yard sign. This is because, without the color red, you first are thinking about Democrats who are named Mitch McConnell. Only when you come up empty on your mental Rolodex do you figure out that it is the Republican Mitch McConnell.

How do you react to the color and then to the name? Social groupings are not simply abstract concepts invented by social psychologists; our neurobiology reflects them. For example, researchers find activation of parts of the brain, such as the anterior insula, when we see someone in our social group outperformed by someone from the out-group [see @zink_barter_2012_ohsn]. The anterior insula activity is associated with physical and emotional pain, not just for ourselves but also for others [@adolphs_janowski_2011_ohsn]. Others have also observed that when seeing someone part of a high-status social group, there is an increase in activity in the sensorimotor cortex and supplementary motor area, indicating more activity in the areas of the brain that encourage movement [@zink_et-al_2008_n]. Visual information about someone in your social group speeds up processing, is more salient, and demands more attention than visual information about an object outside your social group [@zink_barter_2012_ohsn].

There is significant evidence supporting the theory that our partisan identification reflects more than just our attitudes about politics but a social identity [see @campbell_et-al_1960_jws; @mason_2018_cup] that guides our attitudes [see @achen_bartels_2016_pup; @white_et-al_2014_apsr; also @bullock_2011_apsr]. As our political attitudes reflect shared views among co-partisans [@pickup_et-al_2020_pb], the congruence between political information and our partisan identification influences our reactions to such political information. This means that the visual information we glean from politics will likely motivate those neurological features of social groups and explain the resulting behavioral manifestations reacting to such information. That information is also likely to be processed at different rates as well. That is, while visual information carries general affective associations, we should also expect associations between politically-relevant colors with partisan identification.

+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
| Hypotheses   | Expectation                                                                                                                                         |
+==============+:===================================================================================================================================================:+
| $H_1$        | People notice color                                                                                                                                 |
+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_2$        | Colors shape perceptions of candidate based on partisan associations                                                                                |
+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_3$        | Candidates using Red are more supported by Republicans; candidates using Blue are more supported by Democrats                                       |
+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_4$        | Republicans spend less time evaluating candidates using Red; Democrats spend less time evaluating candidates using Blue                             |
+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_5$        | Campaigns recognize the importance of color to voters' evaluations of candidates and respond strategically                                          |
+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+

: Summary of hypotheses {#tbl-hypotheses}

From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that these colors that they notice shape perceptions about the person and ideological symbol represented in the branding -- meaning that they express different levels of preference for receiving more information that is similar to what they saw and their levels of preference for supporting such a campaign ($H_{2}$); that the consistency of information explains more positive perceptions -- simple visual information with more complex "traditional" information ($H_{3}$); this positive and consistent information is processed quicker than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) in line with their primary objective of reelection [@fenno_1973_lb; @mayhew_1974_yup]. A summary of these hypotheses are included in @tbl-hypotheses.

# Pre-test {#sec-pre-test}

```{r}
#| label: setup-pre-test-block

    #* Set seed
set.seed(12062022)
# Source cleaning script
source("01_pre-test_cleaning.R")
    #* Load functions
box::use(
    data.table[...],
    modelsummary[modelsummary, datasummary_skim],
    cmdstanr[...],
    brms[bf, prior, brm, rename_pars, make_stancode, make_standata, pp_check, cumulative, bernoulli],
    rstan[read_stan_csv],
    marginaleffects[avg_slopes, posterior_draws, plot_slopes],
    ggplot2[ggplot, aes, labs, theme_minimal, scale_y_discrete, geom_boxplot],
    bayesplot[color_scheme_set, bayesplot_theme_set, mcmc_combo, mcmc_areas, pp_check],
    ggdist[stat_halfeye]
)
#cmdstanr::set_cmdstan_path("C:\\cmdstan")
    #* default theme
#red_custom <- c("#DCBCBC", "#C79999", "#B97C7C", "#FFFFFF", "#8F2727", "#7C0000")
color_scheme_set(scheme = "gray")
bayesplot_theme_set(new = theme_minimal())
    #* default tails
options("marginaleffects_posterior_interval" = "hdi")

```

I conducted a pre-test in November 2019 with a sample of over 400 undergraduate students at a large university in the northwestern region of the United States. I recruited students enrolled in a political science course and were offered extra credit for their participation in the study. The study asked participants to participate in 5 survey experiments administered by those affiliated with the university's college-level unit. These other survey experiments focus on capturing local policy issues around urban design and criminal justice and probing participants about political participation in local and national-level elections. Subjects participated in my survey experiment after one that examined their levels of political participation in local, state, and national elections.

```{r}
#| label: tbl-pre-test-descriptive-stats
#| tbl-cap: Descriptive statistics of pre-test measures

data[["clean"]][ # select the following columns
    , .(Female, White, age, PartyId, BlueTreatment, RedTreatment, Vote)
] |>
datasummary_skim( # make a table of descriptive statistics
    notes = c( # add some notes to the table
        "Data source: Pre-test experiment.",
        '"Unique" column includes missing values.'
    )
)
```

Using the `modelsummary` [@modelsummary] package implemented in the `R` language [@r_software], I create @tbl-pre-test-descriptive-stats which presents the descriptive characteristics of the sample. The sample is primarily White with over 80% self-reporting that they are White(coded as: 0 = non-White, 1 = White). The sample also skews slightly female on sex, with about 60% reporting that they are female (coded as 0 = Male, 1 = Female). The sample also, unsurprisingly, skews young, with the average respondent reporting an age of about 22 years old. The average respondent also appears to be an independent but leans Republican (coded as -3 = strong Democrat, -2 = Democrat, -1 = leans Democrat, 0 = Independent, 1 = leans Republican, 2 = Republican, 3 = strong Republican).

I randomly assign participants to three conditions. The conditions prompt subjects to "Imagine that \[they\] are driving along a road and see this yard sign" with the same message "Vote for Riley." The conditions vary on the color of the background for the image.[^color_influence_pre-reg_anon-1] In the control condition, the background was white. Then I had a red yard sign and a blue yard sign condition. I asked participants questions operationalized as outcomes of interest on a separate screen.

[^color_influence_pre-reg_anon-1]: The Appendix contains the images used for the treatments and the particular wording for the dependent variables.

To provide a preliminary test of $H_1$ and $H_2$, I ask participants to report whether the candidate was a "Republican, Democrat, or Independent." I test whether participants presumed that the candidate was of a particular partisan persuasion based only on the color choice of the yard sign alone. I created two indicator variables of the treatment the subjects received: whether or not they had the blue or red yard sign treatment. The placebo condition (the white yard sign treatment) is treated as the baseline condition when including both treatment indicator variables in the model.

To examine whether subjects presumed a partisan affiliation of the fictional candidate, I use the `brms` [@brms] implementation of `STAN` to fit an ordinal logistic regression model using the cumulative PDF with a inverse logit link function. My model specification is reflected in @eq-party-specification. I use posterior prediction checks after fitting the model to examine whether the predicted values from the posterior draws resemble my observed values. I calculate the average marginal effects across my posterior draws with High Density Intervals (as opposed to Equal Tail Intervals) and plot the distributions of these. In @fig-party-pre-test-ames, the bars reflect the 90% and 95% credible intervals whereas the dot reflects the median posterior draw.

$$
\begin{split}
  \alpha \sim Student-T(3,0,2.5) \\
  \beta_i \sim Normal(0, 1) \\
  \hat{Party_i} = Cumulative(logit^{-1}(\alpha_1 + \alpha_2 + \beta_1 \times Red Treatment + \beta_2 \times Blue Treatment))
\end{split}
$$ {#eq-party-specification}

```{r}
#| label: party-pre-test-model
#| include: false

source("04_pre-test_party_model.R")
```

```{r}
#| label: fig-party-pre-test-ames
#| fig-cap: Effect of treatments on party perceptions

PartyAMES <- avg_slopes(
  PartyModel,
  type = "link"
) |>
posterior_draws()

ggplot(
  data = PartyAMES,
  aes(
    x = draw,
    y = term
  )
) +
stat_halfeye(
  slab_alpha = 0.45
) +
theme_minimal() +
labs(
  x = "Average Marginal Effect",
  y = "",
  caption = "Data source: Pre-test.\n Distribution of AME's for model posterior draws using HDI's.\n Dot reflects median posterior draw where bars reflect 90% and 95% credible intervals."
) +
scale_y_discrete(
  labels = c(
    "Blue Treatment",
    "Red Treatment"
  )
)
```

The results suggest that for those in the red yard sign treatment condition perceive the candidate to be a Republican. Whereas, those assigned to the blue yard sign treatment condition perceived the owner of the yard sign to be a Democrat. This is without *any* information about the political candidate. Both of these treatments have a quite large effect on conveying the partisanship of the candidate. This finding fits with the expectation that individuals have internalized the use of color in party branding and are independently capable and willing to make that connection. This preliminary evidence suggests that color likely conveys important information to the public.

Individuals associate Republicans with the color Red and Democrats with the color Blue. Do these associations influence their attitudes? In addition to asking participants about whether they perceived the candidate was Republican or Democratic, prior to that question, I asked participants whether they would be willing to vote for the candidate and whether they would want to avoid engaging with the candidate's campaign materials in the future. I used these two questions to construct a measure of willingness to engage with the fictional candidate. Those who reported that they do not want to vote for the candidate *and* want to avoid the candidate in the future I coded with a value of 1. Those who reported a mix of responses were coded as 2. Finally, those that reported that they were willing to vote for the candidate *and* wanted to receive more information about the candidate were coded as 3. Again, the *only* information they have about the candidate is conveyed on the yard sign. I fit an ordinal logistic regression model again using the `brms` [@brms] implementation of `STAN`. My model specification is conveyed in @eq-vote-specification.

$$
\begin{split}
  \alpha \sim Student-T(3,0,2.5) \\
  \beta_i \sim Normal(0, 1) \\
  \hat{Party_i} = Cumulative(logit^{-1}(\alpha_1 + \alpha_2 + \beta_1 \times Red Treatment + \beta_2 \times Blue Treatment \\
    + \beta_3 \times Party Identification (3-item) \\
    + \beta_4 \times Red Treatment \times Party Identification (3-item) \\
    + \beta_5 \times Blue Treatment \times Party Identification (3-item)))
\end{split}
$$ {#eq-vote-specification}

I expect that the effect of the treatment on willingness to engage more with the candidate, either in terms of learning more [@lodge_taber_2013_cup] and voting [@broockman_kalla_2022_ajps] is dependent on whether that candidate is a co-partisan. I also examined this model with a variety of priors and settled on priors I believe to reflect maximum entropy principles [@mcelreath_2020_crc] and those that produced posterior predictive checks with predicted values from the model resembling those observed in my data. I use the `marginaleffects` package [@marginaleffects] to calculate and plot the conditional marginal effects.

```{r}
#| label: pre-test-vote-model
#| include: false

source("05_pre-test_vote_model.R")
```

```{r}
#| label: fig-pre-test-vote-cmes
#| layout-nrow: 2
#| fig-cap: "Effect of yard sign color on candidate evaluation"
#| fig-subcap:
#|  - "Republicans would vote for candidate with Red yard sign"
#|  - "No difference among partisans in support for candidate with Blue yard sign"
#| fig-width: 6
red_cme <- plot_slopes(
    VotePreTestModel,
    variables = "RedTreatment",
    condition = "PartyId",
    type = "link"
) +
theme_minimal() +
labs(
    x = "Party Identification",
    y = "CME of Red Treatment",
    caption = "Data source: Pre-test.\n Conditional Marginal Effects of Red Treatment upon support for candidate.\n Uncertainty reflected by predicted posterior draws at the 95% level with HDI's."
)

blue_cme <- plot_slopes(
    VotePreTestModel,
    variables = "BlueTreatment",
    condition = "PartyId",
    type = "link"
) +
theme_minimal() +
labs(
    x = "Party Identification",
    y = "CME of Blue Treatment",
    caption = "Data source: Pre-test.\n Conditional Marginal Effects of Blue Treatment upon support for candidate.\n Uncertainty reflected by predicted posterior draws at the 95% level with HDI's."
)

red_cme
blue_cme
```

@fig-pre-test-vote-cmes presents results suggesting that among Republicans receiving the red treatment, they are more likely to indicate a positive valence toward the candidate than Democrats, who are more likely to report a negative evaluation of the candidate. While Democrats receiving the blue treatment are more likely to report a positive valence toward the candidate relative to Republicans, the effect is plausibly zero. This may be an artifact of asymmetric political polarization. Some scholars suggest that Republicans are much more group-oriented than Democrats [see @lupton_et-al_2020_bjps]; these results may fit with such a narrative. Republicans are reactive to those they may presume to be co-partisan in a way that Democrats do not appear to be as reactive in a similar magnitude.

The evidence from this pre-test is limited. The experimental design is not testing pre-conscious evaluations. The treatments are explicitly political and rely upon a convenience sample of those enrolled in political science classes. The ability of individuals to associate partisanship with the treatments is likely overstated. The sample is also quite unrepresentative, so the inference is indeed threatened. As I discussed with the third model, I also have omitted variable bias as the result of my outcome is a better measure of approach behaviors for those who are extroverted.

Though there are problems with the design here, it does serve some purpose for this project. It demonstrates that despite its problems, color can betray information at some level when thinking of politics. It also provides a functional first test of a possible research design to examine what this particular design can and cannot tell me about my proposed mechanism.

# Study 1 {#sec-study-1}

The purpose of [Study 1](#sec-study-1) is to examine the average treatment effect [^color_influence_pre-reg_anon-2] of color in a common form of campaign branding -- yard signs -- on the attitudes of the observer. Evidence suggests that yard signs *do* matter in shaping political attitudes [@makse_et-al_2019_oup], vote intentions [@makse_et-al_2019_oup], and even electoral outcomes [@green_et-al_2016_es]. As they are simple, cheap, intrusive, and common forms of campaign branding, they provide a conservative test of the effects of color in campaign branding. Using yard signs in this study, I test the first four hypotheses I derive from the snap-judgment model. First, [Study 1](#sec-study-1) tests the claim that individuals do indeed notice the color of electoral yard signs. Next, it tests the claim that these colors that individuals detect influence the viewer's evaluations of the yard sign and the candidate represented on it. [Study 1](#sec-study-1) then tests the claim that the effects on perception are moderated by how consistent the color is with the more complex information displayed on the yard sign. Furthermore, finally, [Study 1](#sec-study-1) examines whether positive information that contains consistency is processed quicker than negative or inconsistent information. That is, do partisans quickly detect and encode information from a clearly co-partisan political candidate?

[^color_influence_pre-reg_anon-2]: $\frac{1}{n}\sum{}{i}(Y_i(d=1) - Y_i(d=0))$ [see @lundberg_et-al_2021_asr]

## Design

I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia[^color_influence_pre-reg_anon-4] and are provided with a demographics and political attitudes questionnaire. As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_et-al_2018_ajps], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment. This questionnaire includes common questions about the participant's ascriptive and descriptive characteristics and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.

[^color_influence_pre-reg_anon-3]: I pay subjects a rate of \$12.00 per hour. On top of the price per participant, Prolific charges a 30% servicing fee and an additional fee to guarantee a nationally representative sample.

[^color_influence_pre-reg_anon-4]: Pavolovia allows for researchers to host and run open source experiments for about \$0.20 per participant (to cover their server costs). I use it primarily to integrate the JavaScript components from the jsPsych package [@jspsych] for my experimental design.

I include those questions in the questionnaire due to expectations that they may act as confounds in my hypotheses. As political knowledge intertwines with the strength to which an individual identifies with a political party [@delli-carpini_keeter_1996_yup], I expect that political knowledge is an important confounder in my tests of $H_2$, $H_3$, and $H_4$. Therefore, I include a standard battery (the American National Election Study's battery) for assessing political knowledge.[^color_influence_pre-reg_anon-5] As political knowledge is shaped by levels of interest in politics as well [@delli-carpini_keeter_1996_yup], I include the American National Election Study's question to assess levels of self-reported interest in politics. I include a battery to measure patriotism. For this measure, participants can respond to values between 1 (not proud at all) and 4 (very proud) to the following questions: "When I hear the American national anthem, it makes me feel" and "when I say the American pledge of allegiance, it makes me feel" [@huddy_khatib_2007_ajps; @perez_et-al_2019_jop]. I additionally include some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these are correlates with partisan identification [see @campbell_et-al_1960_jws; @mason_2018_cup].

[^color_influence_pre-reg_anon-5]: A table including the wording of this, and all, measures are included in the Supplementary Information.

Additionally, I include a question about the respondent's sex assigned at birth and about whether they have received a diagnosis of any color blindness. As some individuals may possess undiagnosed colorblindness, asking about their sex assists in covariate balance. I additionally include four open-ended questions asking participants to describe (1) their "first memory of a political event," (2) "what occurred in the most recent political event" they encountered, (3) how they "keep up-to-date with current political events," and (4) "what occurred in the most recent non-political event" they encountered. The use of multiple open-ended questions helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [see @kennedy_et-al_2021_poq]. Given estimates using these exclusion criteria, I would expect that upwards of 40% of my original sample will fail these attention checks [@kennedy_et-al_2021_poq]; thus, the large sample size.

I then present participants with an instruction screen informing them of the task for the experiment. In the first trial of the experiment, participants I randomly presented participants with two of three possible yard signs, one at a time. These yard signs are simple with the text "Vote for Riley" and a solid background color of either "Republican Red," "Democratic Blue," or White.[^color_influence_pre-reg_anon-6] There is an added component to this, however.

[^color_influence_pre-reg_anon-6]: See the supplementary information to view all of the stimuli used in [Study 1](#sec-study-1).

Rather than use eye-tracking devices and software, I instead use Mouseview.js [see @anwyl-irvine_et-al_2022_brm], which either blocks out or blurs a large portion of the participant's screen and encourages them to move their mouse to view different parts of the screen in isolation. As the participants move their cursor around the screen, it tracks the coordinates of the cursor along with the "dwell" time of the cursor in that particular coordinate. One primary benefit of Mouseview.js is that it allows researchers to field their experiments outside of a lab-based setting -- while providing results that robustly correlate with the results from a design employing eye-tracking hardware [@anwyl-irvine_et-al_2022_brm]. This allows researchers to rely less on convenience samples, which are common with eye-tracking studies. For my design, I am particularly concerned about reliance on a convenience sample due to variations in participants' ability to detect and process color in the U.S. population relative to a student sample. This means that Mouseview.js is a handy tool for my study. A published pilot version of the experiment used in [Study 1](#sec-study-1) on [Pavlovia](https://run.pavlovia.org/damoncroberts/diss_ch_1_pre-reg/?__pilotToken=c74d97b01eae257e44aa9d5bade97baf&__oauthToken=9a645f267f9b83c8ebb48e60093bae5a746da56a6c824b8343389a9329fa2365).

When viewing each yard sign in the first trial, there is a blur over a substantial portion of the screen. At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_pieters_2008_rmr].[^color_influence_pre-reg_anon-7] Participants move their cursor to explore the yard sign. I allot 5000 ms to perform the exploration until the image goes away to encourage a consistent and short duration to explore the image.[^color_influence_pre-reg_anon-8] After exploring each image, I asked participants what colors were on the yard sign and whether they felt that the candidate represented on the yard sign was a Democrat, a Republican, or Neither. After viewing both images, I ask subjects to indicate their preference among the two images. To ensure that participants have a standardized initial placement of their cursor, I display a blank page before viewing the yard sign that requires participants to click a "Next" button. Immediately after clicking "Next," participants are shown the yard sign. The goal is to ensure that variation in where participants explore the image is not dependent on a non-standard starting point for their cursor. I additionally utilize a gaussian blur for the overlay of the image rather than a solid overlay obstructing the participant's view. This gaussian blur allows participants to see a blurred visual field beyond the cursor. This allows participants to see enough to take purposeful action to explore blurred parts of the image that attract them [@anwyl-irvine_et-al_2022_brm]. The use of the gaussian blur requires that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_et-al_2022_brm]. This will require participants to either switch browsers or to not participate in the study if they are using Safari at the time they are recruited by Prolific to participate in the study. As this requirement is enforced *before* joining the study, this should not have an effect on the number of excluded participants from my original sample nor on a nationally representative original sample.

[^color_influence_pre-reg_anon-7]: I include a screenshot providing an example of what the participants are able to see with the blur included in the supplementary materials.

[^color_influence_pre-reg_anon-8]: In marketing research, some studies give participants about 6000 milliseconds in eye-tracking studies to examine a brand and to formulate an intention to purchase a product or not [@wedel_pieters_2008_rmr]. With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure-evoking images uses 10000 milliseconds; but is intended to be an extended amount of time [@anwyl-irvine_et-al_2022_brm].

There are three more trials that are much like the first trial. What is different between the two other trials is that I vary the amount of color that is on the yard signs (trials 2 and 3). I provide more textual information that deviates from the association of Republicans with red and Democrats with blue (trial 4). Examples of all of these yard signs are included in the supplementary materials.

## Do individuals notice color in political branding?

To address this first question, I use two measures of a participant's attention toward the colors on the yard sign. I collected the first measure through a question posed to the participant after viewing each yard sign, "what color was the yard sign?". The second measure is more implicit than the first: it accounts for the time someone's mouse hovered over the non-text elements of the yard sign relative to how long their mouse hovered over the text. The self-reported measure allows us to examine the conscious detection of color, while the more implicit measure allows us to examine where individuals' attention goes: toward the color or the text.

This is primarily a descriptive exercise, and I intend to compare the differences in measures between the "non-partisan" (white) yard signs and the partisan (red and blue) yard signs. I will examine the differences in measures between the partisan yard signs among self-identified partisan respondents. I additionally include additional models that interact partisanship with age and political knowledge. As the consistent usage by the parties to use the colors red and blue did not occur until the 2000 presidential election, those that were in their early adult years during that time experienced partisan politics where colors were not a strong cue. I additionally expect that those who are more politically knowledgeable should rely on these partisan cues more as they tend to be stronger partisans [@delli-carpini_keeter_1996_yup].

## Do colors shape perceptions of political objects?

To address the following question of whether the colors affect perceptions of the candidate and the yard sign, I ask participants to report whether they perceived the candidate to be a partisan -- either Republican, Democrat, or as non-partisan immediately after viewing each image. Everything on the yard signs remains constant except for the color. As representations of ideology are associated with more than just political views but things like space [@mills_et-al_2016_bbr] and color [@maestre_medero_2022_pr], differences between respondents on the perceived political affiliations of the candidate should be more than stochastic differences. However, differences occur based on the associations between red and blue with partisanship and the lack of political information that the color white conveys.

I examine differences in respondents' reported perceptions of the candidate's partisan affiliation. As respondents are making the choice between two yard signs, my estimand of interest is of a pairwise comparison of the two yard signs they see in each trial. While these are most common in ranking athletic teams, there is recent academic interest in these estimands as they allow researchers to examine the "popularity" of a particular treatment when experimental participants are asked to choose between two options [see @hopkins_noel_2022_ajps]. As color is the only information that changes between yard signs in a given trial, pairwise comparisons are a more appropriate estimand than those from conjoint analyses which often produce treatments that simultaneously vary a number of dimensions of a profile [@bansak_et-al_2021_cup]. There are a handful of options about how to calculate a pairwise comparison, but I elect to estimate a Bradley-Terry score. Bradley-Terry scores are designed for determining "winners" that account for a variety of predictors [@schnakenberg_penn_2013_pa]. Unlike Elo Scores, a popular alternative, Bradley-Terry scores do not require every pairwise matchup to determine a winner.

## Do these perceptions require consistency between information types?

Another hypothesis derived from the snap-judgment model suggests that inconsistency in the yard sign's visual information will lead to more mixed perceptions of the candidate's political stances. The design of the latter trials in the study presents yard signs with mixtures of non-partisan and out-partisan colors. For example, primarily red and presumably Republican yard signs, but has some blue or white in them.

I take the same analytical strategy to address this question as I did before. I estimate the Bradley-Terry scores among respondents. I should expect that the trials that use less "consistent" visual information demonstrate more ambivalence among respondents in their reported perceptions of the politician's positions. Specifically, I expect that participants will perceive the yard signs that have both red and blue on them as more moderate and that the higher proportion of the color red or blue among the two colors will lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic.

## Do partisans process co-partisan branding faster?

The other analytical tasks do not examine expectations derived from the motivated reasoning portion of the model. That is, do people process in-group information faster than out-group information? There is evidence of these tendencies in political circumstances [@lodge_taber_2013_cup].

To examine whether motivated reasoning is also active with the processing of politically-relevant color, I examine the difference between the amount of time between the start of viewing a stimulus and clicking "Next" to stop viewing the stimulus among those who were viewing a presumed co-partisan yard sign relative to those viewing a presumed out-partisan yard sign. As motivated reasoning tends to be more prevalent among strong partisans and those highly knowledgeable and interested in politics [@lodge_taber_2013_cup], I control for responses to the pre-treatment knowledge, interest, and partisan strength batteries.

## Checking the robustness of my analytical strategy with simulations

The @sec-pre-test provides a lot of useful information that I might use to construct my expectations for what I'll discover in @sec-study-1. Rather than evaluating my design choices based on expected long-run tendencies, I explicitly use the results from @sec-pre-test and adjust that information with assumptions about differences between @sec-pre-test and @sec-study-1's design to construct expectations that directly feed into my analytical choices. That is, rather than evaluating my design in the Frequentist framework, I rely on results from the @sec-pre-test to help with constructing my priors that I will use in a Bayesian model specification. Bayesian models often face criticism for the seemingly subjectivity introduced into a model specification by including one's priors into the calculation of one's estimates. While there has been a lot of ink spilt debating the validity of this claim, a Bayesian model specification seems particularly useful in the context of pre-registering a study. @sec-pre-test provides results which give me a benchmark by which I might refine my expectations about the effect of color on people's perceptions about politics; it gives me a concrete $\beta$ coefficient. I can then use this information to construct my priors for my model. As I admit to a number of problems with my @sec-pre-test, my priors will reflect my uncertainty about whether those particular estimates should hold in @sec-study-1 and allows me to define an interval of effect sizes as opposed to a point estimate. These priors are updated by my likelihood distribution that is constructed by the data I collect in @sec-study-1. What this implies is that the more data I have, even if my priors are incorrect, I will converge upon the effect in the population [@johnson_et-al_2021_crc]. However, since my priors require uncertainty, the weight of my priors on my eventual estimate are weaker the more uncertainty I specify. The lessons this provides for a pre-registered report suggests that I can use the results from my @sec-pre-test to inform choices for @sec-study-1, but that, though I use that information to inform my choices for the pre-registered report, I explicitly define how I expect that the results for @sec-study-1 are different than those in @sec-pre-test and that the data for @sec-study-1 directly update my expectations set by @sec-pre-test.

As my estimation strategy does not assume long-run convergence to the population, many assume that my Bayesian models are agnostic to the sample size and often eschew power analyses. However, as estimates from a Bayesian model are weighted by the observed data and my priors, I want to examine the robustness of my model specification using simulated data that vary on sample size. While I do expect that my priors will shift slightly depending on my pre-registered analyses here and upon exploratory data analysis once I collect my data, using simulated data to examine my analytical pipeline offers the opportunity to demonstrate my model specification's ability to converge upon parameters defined by a hypothetical data generating process.

Using the `fabricatr` [@fabricatr] package, I simulate a population with an N of 1,00,000. The specified data generating processes for each of the variables are included in @lst-sim-dgp and @lst-sim-dgp-2. I then generate 500 random samples for each sample size of 200, 400, 600, and 800 participants. This sample size is not the size of the total sample I intend to recruit but is the total sample that I have data on after excluding those who fail attention checks and those who provide duplicate responses. Some estimate that insincere responses account for about 40% of a researcher's original sample [@kennedy_et-al_2021_poq]. Therefore the total sample that I recruit from prolific should be about 40% larger than the total sample size used in these simulations.

``` {#lst-sim-dgp .r lst-cap="Code to generate simulated population data"}

dgp <- fabricate(
    N = 100000, # N in the population
    E = rnorm(N), # epsilon term
    age = round( # define age variable
        runif(N, 18, 85)
    ),
    gender = draw_binary( # define binary gender identity variable
        N,
        prob = 0.5
    ),
    white = draw_binary( # define white indicator variable
        N,
        prob = 0.6
    ),
    PartyId = draw_ordered( # define party identity variable as 3-item ordinal
        x = rnorm(
            N,
            mean = 0.4 * age - 0.6 * gender + 0.7 * white + E
        ),
        breaks = c(
            -Inf, 20.14, 23.01, Inf
        )
    ),
    Attention = draw_ordered( # define Attention variable as 5-item ordinal
        x = rnorm(
            N,
            mean = 0.5 * age - 0.3 * gender + 0.1 * white + E
        ),
        breaks = c(
            -Inf, 16.5, 28.26, 36.54, 43.82, Inf
        )
    ),
    Knowledge = rnorm( # define Knowledge variable
        N,
        mean = 0.6 * age - 0.5 * gender + 0.2 * white + 0.8 * Attention + E
    )/100,
    ...
```

``` {#lst-sim-dgp-2 .r lst-cap="Code to generate simulated population data (continued)"}
  ...
    RedTreatment = draw_binary( # Simulate treatment assignment with prob 1/3
        N,
        prob = 1/3
    ),
    BlueTreatment = draw_binary( # Simulate treatment assignment with prob 1/3
        N,
        prob = 1/3
    ),
    PartyGuess = draw_ordered( # Define PartyGuess outcome variable as 3-item ordinal
        x = rnorm(
            N,
            mean = (
              2 * RedTreatment + -2 * BlueTreatment - 0.01 * age 
              - 0.1 * RedTreatment * age + 0.1 * BlueTreatment * age 
              + 0.1 * Attention + 0.1 * Knowledge + E
            )
        ),
        breaks = c(
            -Inf, -0.5, 0, Inf
        )
    ),
    PartyGuessTrialTwo = draw_ordered( # Define PartyGuess outcome variable as 3-item categorical
        x = rnorm(
            N,
            mean = (
              2 * RedTreatment + -2 * BlueTreatment - 0.01 * age 
              - 0.1 * RedTreatment * age + 0.1 * BlueTreatment * age 
              + 0.1 * Attention + 0.1 * Knowledge + E
            )
        ),
        breaks = c(
            -Inf, -0.5, 0, Inf
        )
    ),
    Vote = draw_ordered( # Define Vote outcome variable as indicator variable
        x = rnorm(
            N,
            mean = (
              1 * RedTreatment + - 1 * BlueTreatment - 0.01 * age 
              + 0.1 * Attention + 0.1 * Knowledge + E
            )
        ),
        breaks = c(
            -Inf, 0, Inf
        )
    )
)
```

To examine my analytic strategy's ability to converge upon the population's data generating process for respondents' perceptions of the fictional candidate's partisanship, I specify a ordinal logistic regression where I set relatively constrained priors upon the beta coefficients, as depicted in @eq-party-guess-priors.

$$
\begin{split}
  \alpha \sim Student-T(3,0,2.5) \\
  \beta_i \sim Normal(0, 1) \\
  \hat{Party_i} = Cumulative(logit^{-1}(\alpha_1 + \alpha_2 \\ 
   + \beta_1 \times Red Treatment + \beta_2 \times Blue Treatment \\
   + \beta_3 \times age + \beta_4 \times Red treatment \times age + \beta_5 \times Blue treatment \times age \\
   + \beta_7 \times Attention + \beta_7 \times Knowledge))
\end{split}
$$ {#eq-party-guess-priors}

These priors suggest that I believe 68% of my beta coefficients, given the data, should be between -1 and 1; with the median of the estimates at 0.

After fitting each model, I construct 95% high density interval credible intervals from the model's posterior draws. I then record a value of 1 if the credible interval does not contain zero (true positive) and a value of 0 if the credible interval does (false negative) for each parameter. Once I have run each of my models for the specified sample size, I calculate the average of true positive and false negatives. This gives me a percentage of the time that I would come to the correct conclusion that there is a non-zero effect on that parameter. @tbl-true-positive-rates documents these calculations for each sample size.

```{r}
#| label: load-simulation-results

Sample200Results <- readRDS(file ="../../data/prr/sample200SimResults.RDS")
Sample400Results <- readRDS(file ="../../data/prr/sample400SimResults.RDS")
Sample600Results <- readRDS(file ="../../data/prr/sample600SimResults.RDS")
Sample800Results <- readRDS(file ="../../data/prr/sample800SimResults.RDS")
```

+-------------+-----------------------------------------------------------------------------+
| Sample size | True positive rate                                                          |
+=============+=============================================================================+
| n = 200     | -   Red treatment: `r sprintf('%.3f', Sample200Results[,1])`                
|             |                                                                             
|             | -   Blue treatment: `r sprintf('%.3f', Sample200Results[,2])`               
|             |                                                                             
|             | -   Age: `r sprintf('%.3f', Sample200Results[,3])`                          
|             |                                                                             
|             | -   Red treatment $\times$ Age: `r sprintf('%.3f', Sample200Results[,4])`   
|             |                                                                             
|             | -   Blue treatment $\times$ Age: `r sprintf('%.3f', Sample200Results[,5])`  
|             |                                                                             
|             | -   Attention: `r sprintf('%.3f', Sample200Results[,6])`                    
|             |                                                                             
|             | -   Knowledge: `r sprintf('%.3f', Sample200Results[,7])`                    
+-------------+-----------------------------------------------------------------------------+
| n = 400     | -   Red treatment: `r sprintf('%.3f', Sample400Results[,1])`                
|             |                                                                             
|             | -   Blue treatment: `r sprintf('%.3f', Sample400Results[,2])`               
|             |                                                                             
|             | -   Age: `r sprintf('%.3f', Sample400Results[,3])`                          
|             |                                                                             
|             | -   Red treatment $\times$ Age: `r sprintf('%.3f', Sample400Results[,4])`   
|             |                                                                             
|             | -   Blue treatment $\times$ Age: `r sprintf('%.3f', Sample400Results[,5])`  
|             |                                                                             
|             | -   Attention: `r sprintf('%.3f', Sample400Results[,6])`                    
|             |                                                                             
|             | -   Knowledge: `r sprintf('%.3f', Sample400Results[,7])`                    
+-------------+-----------------------------------------------------------------------------+
| n = 600     | -   Red treatment: `r sprintf('%.3f', Sample600Results[,1])`                
|             |                                                                             
|             | -   Blue treatment: `r sprintf('%.3f', Sample600Results[,2])`               
|             |                                                                             
|             | -   Age: `r sprintf('%.3f', Sample600Results[,3])`                          
|             |                                                                             
|             | -   Red treatment $\times$ Age: `r sprintf('%.3f', Sample600Results[,4])`   
|             |                                                                             
|             | -   Blue treatment $\times$ Age: `r sprintf('%.3f', Sample600Results[,5])`  
|             |                                                                             
|             | -   Attention: `r sprintf('%.3f', Sample600Results[,6])`                    
|             |                                                                             
|             | -   Knowledge: `r sprintf('%.3f', Sample600Results[,7])`                    
+-------------+-----------------------------------------------------------------------------+
| n = 800     | -   Red treatment: `r sprintf('%.3f', Sample800Results[,1])`                
|             |                                                                             
|             | -   Blue treatment: `r sprintf('%.3f', Sample800Results[,2])`               
|             |                                                                             
|             | -   Age: `r sprintf('%.3f', Sample800Results[,3])`                          
|             |                                                                             
|             | -   Red treatment $\times$ Age: `r sprintf('%.3f', Sample800Results[,4])`   
|             |                                                                             
|             | -   Blue treatment $\times$ Age: `r sprintf('%.3f', Sample800Results[,5])`  
|             |                                                                             
|             | -   Attention: `r sprintf('%.3f', Sample800Results[,6])`                    
|             |                                                                             
|             | -   Knowledge: `r sprintf('%.3f', Sample800Results[,7])`                    
+-------------+-----------------------------------------------------------------------------+

: True positive rate {#tbl-true-positive-rates}

The results of my simulation suggest that I should aim for a sample of 600 respondents once I have excluded those that do not meet the inclusion criteria (i.e., fail attention checks, duplicated IP addresses and provide insincere responses to the open-ended prompts). Given estimates of poor responses for about 40% of some samples [@kennedy_et-al_2021_poq], I should aim to recruit a total of 1500 participants for Study 1.

# Study 2 {#sec-study-2}

[Study 1](#sec-study-1) presents evidence in support of the snap-judgment model in a relatively artificial way. The yard signs presented as stimuli are elementary in information content and design. Furthermore, viewing yard signs in real-world scenarios does not occur through a computer screen with an overlay allowing individuals to observe only a fraction of the screen simultaneously.

One way to examine the real-world effects of color on decisions about campaign branding is to go directly to the experts. If the effects of [Study 1](#sec-study-1) hold up in natural conditions, we should expect that campaigns make strategic decisions to nurture this behavior. Descriptive evidence suggests that female candidates in the United States make different branding decisions based on the constituency and whether their opponent is a man or a woman [@williams_et-al_2022_jomp]. If the color of a yard sign does indeed matter and its electoral effects depend on the perceptions of potential voters, we should expect that campaigns are less likely to place yard signs with a large amount of Red or Blue in more moderate districts. However, in districts where there is a strong partisan base, we should expect that the candidate of the popular party will use the party's color more, while the disadvantaged candidate will use their party's color less as a way to either play up or down their loyalty to their party.

## Are colors on yard signs a strategic choice by campaigns?

In this first part of [Study 2](#sec-study-2), I do a number of informal interviews with managers of national, state, and local campaigns. In these interviews, I simply ask the campaign managers: "what goes into your decision for the colors to put on your yard sign?" The goal of this open-ended question is to hear from the practitioners whether they perceive the yard sign color as a strategic decision for the campaign. I then follow-up to ask "do you think that the color choices you make for the yard signs matter to voters?" The goal of this question is to examine whether practitioners intuitively perceive their strategic choices to have efficacy in the election. I then ask them "if colors matter and you choose to use them strategically, do you use certain colors to attract certain groups of voters that may not be reliably in your base of support?" The goal of this question is to get at the argument that the colors that campaigns use are meant as a way to communicate the partisan and ideological alignment of the candidate with the voters. Finally, I get directly to the point "what information about the candidate are you trying to convey to potential voters when you choose the colors on your yard signs?"

While it is useful to hear from practitioners whether they strategically use colors for their yard signs and whether they believe that their strategic choices matter, there are many open questions. Firstly, the selection of whom to interview is dependent on convenience and the accessability of the campaign manager. In other words, some campaign managers may be quite hard to contact due to sparse information about them or they may be hard to contact as a result of their schedules. Second, it is doubtful that campaign managers will openly admit that the choices they make are not strategic or that they think their strategic choices have little effects on the campaign's outcome.

To address these remaining questions, I employ a second part of [Study 2](#sec-study-2) which relies upon observational data and leverages congressional redistricting following the 2020 National Census to examine whether the partisan context of a district is associated with changes to color choices for campaigns in that same district. As this is likely a very endogenous process -- where voters are influenced by the colors used and the voters influence the colors that are used -- the primary goal of this second part of the study is to demonstrate that the parties are *responding* to their intuition that suggests that colors matter to the campaign; it is not to make any directional claim that partisan composition of a district *determines* the colors on a yard sign.

## Do branding choices reflect electoral context?

```{python}
#| label: some-script-execution
#| eval: false
import os
os.system('../study_2/code/03_capd_downloading_images.py')
os.system('../study_2/code/04_mit_election_lab_merge.py')
os.system('../study_2/code/05_color_detection.py')
```

To examine whether the use of colors on yard signs varies systematically depending on the electoral context, using the `selenium` [@selenium] and `time` [@time] `python` [@python] packages, I collect images from 2018, 2020, and 2022 Congressional elections for the House of Representatives across the United States. These yard signs are pulled together on one website by the Center for American Politics and Design[^color_influence_pre-reg_anon-9]. With these data, I detect the percentage of the "Republican Red" and "Democratic Blue" on the yard signs. I then use redistricting data from the [MIT election lab and Redistricting Data Hub](https://redistrictingdatahub.org/data/about-our-data/) to determine districts that did and did not have changes in the 5-year rolling average partisan vote share but that are also nationally representative. As there are a number of external factors that may effect choice in yard sign color besides perceptions of how it may attract voters, this threatens my ability to make claims about any estimation of an Average Treatment Effect [^color_influence_pre-reg_anon-10]. Instead these data are used to perform a synthetic control design to give me causal leverage over the role that electoral context has on the proportion of partisan colors (i.e., red and blue) on yard signs relative to non-partisan colors by estimating a Local Average Treatment Effect [^color_influence_pre-reg_anon-11] on districts that were redistricted but vary in whether the redistricting leads to a partisan gerrymandered district or not. This analysis aims to bear evidence on the hypothesis that campaigns respond to the preferences of partisan voters and adjust their branding as a result. In this case, the branding is the color of the yard sign. First, I'll explain how I collected data on the proportion of partisan and non-partisan colors on these yard signs from the [Center for American Politics and Design](https://www.politicsanddesign.com).

[^color_influence_pre-reg_anon-9]: See: https://www.politicsanddesign.com/

[^color_influence_pre-reg_anon-10]: $\frac{1}{n}\sum{}{i}(Y_i(d=1) - Y_i(d=0))$ [see @lundberg_et-al_2021_asr]

[^color_influence_pre-reg_anon-11]: $E[(Y^1_i - Y^0_i) | d^1_i - d^0_i = 1]$ \[see @cunningham_2021_yup\]

I collected the GOP logo used on their official Twitter account during the 2022 midterm election cycle to provide an example of how color detection works. With the `opencv` package [@opencv_library], I load this image and convert it to a three-dimensional `numpy` [@numpy] array that contains information about the GBR (reversed RBG) values for the pixels in that image. I resized the images to be a standardized 224 $x$ 224 pixels. I train the computer to detect a range of GBR values that encompass the official "Republican Red" [^color_influence_pre-reg_anon-12]. For the broader exercise, I do it for the color white[^color_influence_pre-reg_anon-13] and "Democratic blue" [^color_influence_pre-reg_anon-14]. Once this range of values is specified, the computer detects the pixels that do not contain values within this pre-specified range and converts those values to represent the color black. @fig-color-detection-example presents this process using the `opencv` [@opencv_library] and `matplotlib` [@matplotlib] packages.

[^color_influence_pre-reg_anon-12]: lower values: (93, 9, 12), higher values: (236, 69, 75)

[^color_influence_pre-reg_anon-13]: upper and lower values: (255, 255, 255)

[^color_influence_pre-reg_anon-14]: lower values: (0, 18, 26), higher values: (102, 212, 255)

```{python}
#| label: example detection
#| echo: false

from sys import path # for path management
from cv2 import imread, imwrite # for color detection
    #* user-defined
#path.append("../")
from helper import colorDetector

# Define colors to detect
    #* White
        #** Not defined. Default for colorDetector()
    #* Red
republican_red = [232, 27, 35] # target color
red_lower = [93, 9, 12] # lower end of spectrum for red
red_higher = [237, 69, 75] # higher end of spectrum for red

# Load gop image to read
img = imread("../../data/study_2/gop_2022.png")

# Detect colors
percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)

transformed= imwrite("../../data/study_2/gop_2022_transformed.png", img_transformed) # save transformed image

masked= imwrite("../../data/study_2/gop_2022_detected.png", result) # save masked image
```

::: {#fig-color-detection-example layout-ncol="2"}
![Resized original image](../../data/study_2/gop_2022_transformed.png){#fig-resized}

![Masked](../../data/study_2/gop_2022_detected.png){#fig-masked}

Detecting colors in the GOP logo
:::

I then extract the values in the array that are non-black and calculate the percentage of non-black pixels (as depicted in @eq-img-color-percentage).

$$
\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}
$$ {#eq-img-color-percentage}

```{python}
#| output: asis
# Print calculated percentage of example
print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
```

With these data, I estimate a mixed effects model with intercept random effects at the district level and intercept fixed effects at the election year level to examine the district and within election year differences between choices to employ more "partisan" colors on a yard sign based on historical data on the electoral performance of partisan and non-partisan candidates. That is, I examine whether there are differences between how campaigns respond to redistricting that make the electorate for that constituency more partisan or less partisan while controlling for a number of election-year and campaign specific factors. Support for $H_5$ would suggest that campaigns in districts that are more partisan will shift to use more traditionally-partisan colors while campaigns in districts that do not shift to have a more historically partisan constituency will use fewer of those traditionally-partisan colors.

# Discussion

Not only do yard signs matter for electoral strategy, outcomes, and voter attitudes and perceptions, but I suspect that the yard signs' color partially explains these phenomena.

While yard signs are a simple form of party branding, richer theorizing about how diverse types of potentially politically-relevant information allows us to fill some of these gaps. In the case of yard signs, while some may be skeptical of whether yard signs and campaigns, more generally, matter for electoral outcomes, an application of the snap-judgment model on yard signs suggests that they indeed have potential and provide an explanation as to how it occurs.

Outside of color on yard signs, I suspect that color provides valuable information that is processed efficiently by the public. Due to this, voters can connect colors like Red and Blue to make assumptions about a political candidate's partisan affiliation. With this information, voters can then evaluate the candidate. This is a much simpler task than hearing the candidate's positions on immigration, for example, and then making a connection to their partisan affiliation.

{{< pagebreak >}}

### 2023-06-19 chapter_2/src/appendix.qmd
I hate submodules

# Chapter 2 Appendix {#sec-2-a}

```{r}
#| label: setup

# Load helpful functions
box::use(
  modelsummary[
    modelsummary
  ]
)

# Load fitted models and ppc checks
load(
  file = "../data/temp/models/study_1_fitted.RData"
)
```

## Measures

{{< pagebreak >}}

## Hypothesis 1

### Models

{{< pagebreak >}}

### Posterior Predictive Checks

{{< pagebreak >}}

## Hypothesis 2

### Models

```{r}
#| label: tbl-hypothesis-2-main
#| tbl-cap: Full results for reported models in $H_2$
# Redefine names
list_fitted_split_1 <- list(
  "Red treatment" = list_fitted[["h_2"]][["red"]]
  , "Blue treatment" = list_fitted[["h_2"]][["blue"]]
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

```{r}
#| label: tbl-interacted-models-h-2
#| tbl-cap: $H_2$ models moderated by age
# Redefine names
list_fitted_split_2 <- list(
  "Red treatment - Age moderating" = list_fitted[["h_2"]][["red_interact"]]
  , "Blue treatment - Age moderating" = list_fitted[["h_2"]][["blue_interact"]]
)

# Make table
modelsummary(
  list_fitted_split_2
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_age" = "Age"
    , "b_trial_1_red_stimuli:age" = "Red yard sign $\\times$ Age"
    , "b_trial_1_blue_stimuli:age" = "Blue yard sign $\\times$ Age"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```
```{r}
#| label: tbl-robustness-alt-specification-h-2
#| tbl-cap: $H_2$ models with alternative specification
# Redefine names
list_fitted_split_3 <- list(
  "Single model" = list_fitted[["h_2"]][["single_model"]]
)

# Make table
modelsummary(
  list_fitted_split_3
  , coef_map = c(
    "b_trial_1_red_stimuli_alt" = "Red yard sign"
    , "b_trial_1_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brakcets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

```{r}
#| label: tbl-colorblindness
#| tbl-cap: $H_2$ moderated by colorblindness

# Redefine names
list_fitted_split_4 <- list(
  "Red - Color blindness moderating" = list_fitted[["h_2"]][["red_colorblind"]]
  , "Blue - Color blindness moderating" = list_fitted[["h_2"]][["blue_colorblind"]]
)
# Make table
modelsummary(
  list_fitted_split_4
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_trial_1_red_stimuli:color_blind_dummy" = "Red yard sign $\\times$ Color blind"
    , "b_trial_1_blue_stimuli:color_blind_dummy" = "Blue yard sign $\\times$ Color blind"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

### Posterior Predictive Checks
```{r}
#| label: fig-h-2-ppc
#| layout-ncol: 2
#| fig-cap: Posterior predictive checks of models in $H_2$
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment
#|   - Red treatment (Moderated by age)
#|   - Blue treatment (Moderated by age)
#|   - Single model
#|   - Red treatment (Moderated by colorblindness)
#|   - Blue treatment (Moderated by colorblindness)

list_ppc[["h_2"]][["red"]]
list_ppc[["h_2"]][["blue"]]
list_ppc[["h_2"]][["red_interact"]]
list_ppc[["h_2"]][["blue_interact"]]
list_ppc[["h_2"]][["single_model"]]
list_ppc[["h_2"]][["red_colorblind"]]
list_ppc[["h_2"]][["blue_colorblind"]]
```

{{< pagebreak >}}
\blandscape

```{r}
#| label: tbl-hypothesis-2a
#| tbl-cap: Full results for models testing bounds of $H_2$
# Redefine names
model_names <- list(
  "Trial 2 - Red treatment" = list_fitted[["h_2a"]][["trial_2_red"]]
  , "Trial 2 - Blue treatment" = list_fitted[["h_2a"]][["trial_2_blue"]]
  , "Trial 2 - Single model" = list_fitted[["h_2a"]][["trial_2_single_model"]]
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_2_red_stimuli" = "Red yard sign"
    , "b_trial_2_blue_stimuli" = "Blue yard sign"
    , "b_trial_2_red_stimuli_alt" = "Red yard sign"
    , "b_trial_2_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

```{r}
#| label: tbl-hypothesis-2a-cont
#| tbl-cap: Full results for models testing bounds of $H_2$ (cont.)
# Redefine names
model_names <- list(
  "Trial 3 - Red treatment" = list_fitted[["h_2a"]][["trial_3_red"]]
  , "Trial 3 - Blue treatment" = list_fitted[["h_2a"]][["trial_3_blue"]]
  , "Trial 3 - Single model" = list_fitted[["h_2a"]][["trial_3_single_model"]]
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_3_red_stimuli" = "Red yard sign"
    , "b_trial_3_blue_stimuli" = "Blue yard sign"
    , "b_trial_3_red_stimuli_alt" = "Red yard sign"
    , "b_trial_3_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

\elandscape
{{< pagebreak >}}

### Posterior Predictive Checks
```{r}
#| label: fig-h-2a-ppc
#| layout-ncol: 2
#| fig-cap: Posterior predictive checks of models in $H_2$
#| fig-subcap:
#|   - Red treatment (Trial 2)
#|   - Blue treatment (Trial 2)
#|   - Combined model (Trial 2)
#|   - Red treatment (Trial 3)
#|   - Blue treatment (Trial 3)
#|   - Combined model (Trial 3)

list_ppc[["h_2a"]][["trial_2_red"]]
list_ppc[["h_2a"]][["trial_2_blue"]]
list_ppc[["h_2a"]][["trial_2_single_model"]]
list_ppc[["h_2a"]][["trial_3_red"]]
list_ppc[["h_2a"]][["trial_3_blue"]]
list_ppc[["h_2a"]][["trial_3_single_model"]]
```

{{< pagebreak >}}

## Hypothesis 3

### Models

```{r}
#| label: tbl-h-3-main
#| tbl-cap: Support of candidate based on partisanship

# Redefine names
model_names <- list(
  "Red stimuli" = list_fitted[["h_3"]][["red"]]
  , "Blue stimuli" = list_fitted[["h_3"]][["blue"]]
)

# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_pid_7" = "Party ID"
    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
    , "b_age" = "Age"
    , "b_gender_idMale" = "Gender - Male"
    , "b_gender_idNonMbinary" = "Gender - Non-binary"
    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
    , "b_race_idBlacknonMhispanic" = "Black"
    , "b_race_idHispanice" = "Hispanic"
    , "b_race_idMultipleraces" = "Multiple races"
    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
    , "b_race_idWhitenonMhispanic" = "White"
  )  
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

{{< pagebreak >}}

### Posterior predictive Checks

{{< pagebreak >}}

## Hypothesis 4

### Models

{{< pagebreak >}}

### Posterior Predictive Checks

### 2023-06-19 chapter_2/src/manuscript.qmd
I hate submodules

# Does color convey political information?
<!--
    - Description: QMD script for empirical chapter 1
    - Updated: 2023-07-16
    - Notes:
        * Code:
        * Writing:
-->

## Introduction

::: {#fig-party-brand layout-ncol=2}

![Republicans pre-2000](assets/img/rnc_logo_pre-2000.png){#fig-republican}

![Democrats pre-2000](assets/img/dnc_logo_1960.png){#fig-democrat}

![Republicans 2023](assets/img/rnc_logo_2023.png){#fig-republican-post}

![Democrats 2023](assets/img/dnc_logo_2023.png){#fig-democrat-post}

Party logos
:::

Do the colors red and blue mean much to citizens in the context of politics? Before the 2000 Presidential Election, television networks used a variety of different colors when presenting electoral maps to visually communicate which candidate had won the electoral votes for each state. However, beginning in the 2000 election, networks consistently used the color red to indicate that George W. Bush (the Republican party's nominee) had won a state's electoral votes and the color blue to indicate that Al Gore (the Democratic party's nominee) had won a state's electoral votes [@elving_2014_npr].

The parties have seemingly adopted these brands[@williams_et-al_2022_jomp] and @fig-party-brand conveniently demonstrates this. While one may wonder, "Are news networks to credit/blame for giving the parties these colors?" or "Did news networks do this because choices in party branding was going this way anyhow?", this chapter wants to examine this from an alternative perspective that centers voters. Specifically, this chapter seeks to address the question of whether voters recognize these tendencies and whether this influences their levels of support for candidates in a variety of contexts.

One way in which voters may encourage the parties to adopt a consistent, but yet distinct, brand -- in terms of color -- is through the party's desire to capture as many voters as possible [@downs_1957_jpe]. For most voters, following politics and forming opinions on every policy position and candidate is cognitively demanding and time consuming. As a result, voters often satisfice and tend to repeatedly support the same party across elections [@campbell_et-al_1960_jws]. Building on these perspectives, decades of work suggests that voters see the parties as more than just a cluster of political elites who have formed a coalition around similar perspectives on policy, but that voters actually see these parties as a "team" or a social group by which one includes in their definition of self [@campbell_et-al_1960_jws;@mason_2018_cup]. As a result of this, partisans have a tendency to stick with candidates that clearly align themselves with one group and to distinguish themselves from the other group [@utych_2020_es].

Taking this perspective, this chapter argues that color works as a useful heuristic (mental shortcut) for the average citizen to figure out whether a political candidate is a Republican, a Democrat, or neither. Much like a sports team, we might expect that the athletes for our favorite team will be wearing the colors for the team they play for, even if we may not be familiar with a player who may have joined the team after the most recent draft or trade deadline [see @kurzban_et-al_2001_pnas;@pietraszewski_et-al_2015_c]. As a result of these connections between the party and a particular color, individuals will either report lower levels of support for a candidate that uses a color associated with the other political party and will report higher levels of support for the candidate using the colors that are associated with the individual's preferred party. I expect that these effects hold up particularly in the circumstance where voters have no substantive information about the candidate. Before bringing empirical evidence to examine these claims, the chapter elaborates on the argument and outlines a set of expectations about how color conveys group membership and what we may expect citizens' reactions are to such information.

## How do voters evaluate political candidates?

Political pscyhologists have amassed a great deal of evidence suggesting that voters are not objective consumers of political information. First, voters are cognitive misers and seek to find shortcuts to come to decisions about politics such as who to vote for [@lau_redlawsk_2001_ajps]. Second, one such shortcut that voters may use is by relying on the party of the candidate as opposed to relying on consistent ideological principles [@converse_1964_cr;@barber_pope_2019_apsr]. Third, the reason that partisanship is such a useful heuristic is that it now reflects a social identity that people use when defining who they are as opposed to thinking of their alignment with the parties as just a reflection of their current policy positions [@campbell_et-al_1960_jws;@mason_2018_cup;@groenendyk_2012_pb]. That is, someone's partisanship is expressive as opposed to a reflection of their evaluation of the performance of the policies advocated for by the party [@huddy_et-al_2015_apsr]. Evidence suggests that even those who claim they are independent are not necessarily less susceptible to this tendency to align their expressed support with a preferred party, but really are those who tend to dislike participating and reporting that they participate in "partisan politics" [@klar_krupnikov_2016_cup;@robison_2022_prq].

This literature in political psychology heavily borrows from social psychology which first argues that social groups are a highly effective and efficient way by which humans make decisions in a variety of contexts in and beyond politics [@tajfel_turner_1979_ejsp]; and that these social groups and our preferences for one group versus another are even reflected in neurobiological functions [@zink_barter_2012_ohsn]. Further, this literature borrows from the idea that we are motivated to defend our prior beliefs and stances. That is, we are not always motivated to collect and respond to accurate information, but we often have this strong bias to find ways to borrow and rely upon information that makes us feel good about pour prior positions [@kunda_1990_pb].

What this evidence suggests is that voters are highly motivated to defend prior positions and are often thinking about politics in terms of alignment with their preferred party [@groenendyk_2012_pb;@mason_2018_cup]. This evidence is often cited as the primary explanation for the emotionally charged negative reactions to the other parties [@iyengar_westwood_2015_ajps;@westwood_peterson_2022_pb]. This evidence also suggests that the two parties are central in how people evaluate politics -- regardless of whether or not an individual expresses high or low levels of partisan animosity. People often see politics in the United States as either a "Do I support the Democrats or do I support the Republicans?" and the two parties have put in significant efforts to make this a feature [@lee_2009;@clifford_2020_pb]. This distinction between the parties at the elite levels are reflected in real ideological polarization among elites [@enders_2021_jop] that even manifest as an unwillingness to talk to members of the other party on the House floor [@dietrich_2021_pa].

In summary, the parties use the colors red and blue at varying rates in contemporary politics [@williams_et-al_2022_jomp], they are polarized [@enders_2021_jop], and seek to find ways to distinguish themselves from the other party [@lee_2009]. For voters, they are receptive to such efforts among elites [@zaller_1992_cup;@leonard_et-al_2021_pnas] and often have motivations to stick with the party that they have supported regardless of ideological shifts [@barber_pope_2019_apsr]. Much of this information included in the literature discussed here thinks of it in terms of communicated policy positions. Over the next few pages, I build on these perspectives to argue that color is one type of symbology that the party and its candidates may use to quickly and efficiently communicate party aliance to potential voters.

## Building an intuition for color's effect on politics

+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
| Hypotheses   | Expectation                                                                                                                                         |
+==============+:===================================================================================================================================================:+
| $H_1$        | People notice color                                                                                                                                 |
+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_2$        | Red is associated with Republicans and Blue is associated with Democrats                                                                            |
+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_3$        | Candidates using Red are more supported by Republicans; candidates using Blue are more supported by Democrats                                       |
+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_4$        | Republicans spend less time evaluating candidates using Red; Democrats spend less time evaluating candidates using Blue                             |
+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_5$        | Campaigns recognize the importance of color to voters' evaluations of candidates and respond strategically                                          |
+--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+

: Summary of hypotheses {#tbl-hypotheses}

## Study 1

```{r}
#| label: study-1-setup

# Load some handy functons
box::use(
    data.table[...]
    , modelsummary[
        datasummary_skim
        , datasummary_balance
    ]
    , ./R/predicted_prob_bar[...]
)

# Execute the cleaning script
source("./eda/study_1/cleaning.R")
# Load fitted models
load("../data/temp/models/study_1_fitted.RData")
```

The purpose of [Study 1](#sec-study-1) is to examine whether the color choices on an almost ubiquitus form of campaign branding -- yard signs -- influence people's perceptions of political candidates. Evidence suggests that yard signs *do* matter in shaping political attitudes [@makse_et-al_2019_oup], vote intentions [@makse_et-al_2019_oup], and even electoral outcomes [@green_et-al_2016_es]. As they are simple, cheap, intrusive, and common forms of campaign branding, they provide a conservative test of the effects of color in campaign branding. Using yard signs in this study, I test the first four hypotheses I derive from the snap-judgment model. First, [Study 1](#sec-study-1) tests the claim that individuals do indeed notice the color of electoral yard signs. Next, it tests the claim that these colors that individuals detect influence the viewer's evaluations of the yard sign and the candidate represented on it. [Study 1](#sec-study-1) then tests the claim that the effects on perception are moderated by how consistent the color is with the more complex information displayed on the yard sign. Finally, [Study 1](#sec-study-1) examines whether positive information that contains consistency is processed quicker than negative or inconsistent information. That is, do partisans quickly detect and encode information from a clearly co-partisan political candidate?

### Research design

I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia[^color_influence_pre-reg_anon-4] and are provided with a demographics and political attitudes questionnaire. As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_et-al_2018_ajps], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment. This questionnaire includes common questions about the participant's ascriptive and descriptive characteristics and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.

[^color_influence_pre-reg_anon-3]: I pay subjects a rate of \$12.00 per hour. On top of the price per participant, Prolific charges a 30% servicing fee.

[^color_influence_pre-reg_anon-4]: Pavolovia allows for researchers to host and run open source experiments for about \$0.20 per participant (to cover their server costs). I use it primarily to integrate the JavaScript components from the jsPsych package [@jspsych] for my experimental design.

I include those questions in the questionnaire due to expectations that they may act as confounds in my hypotheses. As political knowledge intertwines with the strength to which an individual identifies with a political party [@delli-carpini_keeter_1996_yup], I expect that political knowledge is an important confounder in my tests of $H_2$, $H_3$, and $H_4$. Therefore, I include a standard battery (the American National Election Study's battery) for assessing political knowledge.[^color_influence_pre-reg_anon-5] As political knowledge is shaped by levels of interest in politics as well [@delli-carpini_keeter_1996_yup], I include the American National Election Study's question to assess levels of self-reported interest in politics. I additionally include some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these are correlates with partisan identification [see @campbell_et-al_1960_jws; @mason_2018_cup].

[^color_influence_pre-reg_anon-5]: A table including the wording of this, and all, measures are included in the Supplementary Information.

Additionally, I include a question about the respondent's sex assigned at birth and about whether they have received a diagnosis of any color blindness. As some individuals may possess undiagnosed colorblindness, asking about their sex assists in covariate balance. I additionally include an open-ended question asking participants to describe their "first memory of a political event." The use of an open-ended question helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [see @kennedy_et-al_2021_poq]. Given estimates using these exclusion criteria, I would expect that upwards of 40% of my original sample will fail these attention checks [@kennedy_et-al_2021_poq]; thus, the large sample size.

I then present participants with an instruction screen informing them of the task for the experiment. In the first trial of the experiment, participants I randomly presented participants with two of three possible yard signs, one at a time. These yard signs are simple with the text "Riley Ready to Lead" and a solid background color of either "Republican Red," "Democratic Blue," or White.[^color_influence_pre-reg_anon-6] There is an added component to this, however.

[^color_influence_pre-reg_anon-6]: See the supplementary information to view all of the stimuli used in [Study 1](#sec-study-1).

Rather than use eye-tracking devices and software, I instead use Mouseview.js [see @anwyl-irvine_et-al_2022_brm], which either blocks out or blurs a large portion of the participant's screen and encourages them to move their mouse to view different parts of the screen in isolation. As the participants move their cursor around the screen, it tracks the coordinates of the cursor along with the "dwell" time of the cursor in that particular coordinate. One primary benefit of Mouseview.js is that it allows researchers to field their experiments outside of a lab-based setting -- while providing results that robustly correlate with the results from a design employing eye-tracking hardware [@anwyl-irvine_et-al_2022_brm]. This allows researchers to rely less on convenience samples, which are common with eye-tracking studies. For my design, I am particularly concerned about reliance on a convenience sample due to variations in participants' ability to detect and process color in the U.S. population relative to a student sample. This means that Mouseview.js is a handy tool for my study. A published pilot version of the experiment used in [Study 1](#sec-study-1) on [Pavlovia](https://run.pavlovia.org/damoncroberts/diss_ch_1_pre-reg/?__pilotToken=c74d97b01eae257e44aa9d5bade97baf&__oauthToken=9a645f267f9b83c8ebb48e60093bae5a746da56a6c824b8343389a9329fa2365).

When viewing each yard sign in the first trial, there is a blur over a substantial portion of the screen. At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_pieters_2008_rmr].[^color_influence_pre-reg_anon-7] Participants move their cursor to explore the yard sign. I allot 5000 ms to perform the exploration until the image goes away to encourage a consistent and short duration to explore the image.[^color_influence_pre-reg_anon-8] After exploring each image, I asked participants what colors were on the yard sign and whether they felt that the candidate represented on the yard sign was a Democrat, a Republican, or Neither. After viewing both images, I ask subjects to indicate their preference among the two images. To ensure that participants have a standardized initial placement of their cursor, I display a blank page before viewing the yard sign that requires participants to click a "Next" button. Immediately after clicking "Next," participants are shown the yard sign. The goal is to ensure that variation in where participants explore the image is not dependent on a non-standard starting point for their cursor. I additionally utilize a gaussian blur for the overlay of the image rather than a solid overlay obstructing the participant's view. This gaussian blur allows participants to see a blurred visual field beyond the cursor. This allows participants to see enough to take purposeful action to explore blurred parts of the image that attract them [@anwyl-irvine_et-al_2022_brm]. The use of the gaussian blur requires that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_et-al_2022_brm]. This will require participants to either switch browsers or to not participate in the study if they are using Safari at the time they are recruited by Prolific to participate in the study. As this requirement is enforced *before* joining the study, this should not have an effect on the number of excluded participants from my original sample.

[^color_influence_pre-reg_anon-7]: I include a screenshot providing an example of what the participants are able to see with the blur included in the supplementary materials.

[^color_influence_pre-reg_anon-8]: In marketing research, some studies give participants about 6000 milliseconds in eye-tracking studies to examine a brand and to formulate an intention to purchase a product or not [@wedel_pieters_2008_rmr]. With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure-evoking images uses 10000 milliseconds; but is intended to be an extended amount of time [@anwyl-irvine_et-al_2022_brm].

There are three more trials that are much like the first trial. What is different between the two other trials is that I vary the amount of color that is on the yard signs (trials 2 and 3). I provide more textual information that deviates from the association of Republicans with red and Democrats with blue (trial 4). Examples of all of these yard signs are included in the supplementary materials.

@tbl-study-1-descriptives presents some characteristics of the sample on the whole.

```{r}
#| label: tbl-study-1-descriptives
#| tbl-cap: Descriptive statistics of Prolific sample

df_demographics_subset <- list_df[["cleaned"]][
    , .(
        Age = age
        , `Color blind` = color_blind_dummy
        , Female = female_sex
        , White = white
        , Hispanic = hispanic
        , Black = black
        , `Party ID` = pid_7
    )
] |> 
as.data.frame()

datasummary_skim(
    df_demographics_subset
    , histogram = FALSE
    , notes = c(
      "Data source: Pavlovia."
      , "Sample characteristics."
    )
)
```

### Do individuals notice color in political branding?

To address this first question, I use two measures of a participant's attention toward the colors on the yard sign. I collected the first measure through a question posed to the participant after viewing each yard sign, "what color was the yard sign?". The second measure is more implicit than the first: it accounts for the time someone's mouse hovered over the non-text elements of the yard sign relative to how long their mouse hovered over the text. The self-reported measure allows us to examine the conscious detection of color, while the more implicit measure allows us to examine where individuals' attention goes: toward the color or the text.

This is primarily a descriptive exercise, and I intend to compare the differences in measures between the "non-partisan" (white) yard signs and the partisan (red and blue) yard signs. I will examine the differences in measures between the partisan yard signs among self-identified partisan respondents. I additionally include additional models that interact partisanship with age and political knowledge. As the consistent usage by the parties to use the colors red and blue did not occur until the 2000 presidential election, those that were in their early adult years during that time experienced partisan politics where colors were not a strong cue. I additionally expect that those who are more politically knowledgeable should rely on these partisan cues more as they tend to be stronger partisans [@delli-carpini_keeter_1996_yup].

```{r}
#| label: tbl-h1-trial-1
#| tbl-cap: Average time between cursor movements (Trial 1)
df_movement_trial_1 <- list_df[["cleaned"]][
  , .(
    trial_1_difference_Time
    , trial_1_stimulus
    , trial_1_difference_X
    , trial_1_difference_Y
  )
]
setnames(
  df_movement_trial_1
  , old = c(
    "trial_1_difference_Time"
    , "trial_1_difference_X"
    , "trial_1_difference_Y"
  )
  , new = c(
    "$\\Delta_{t}$ (milliseconds)"
    , "$\\Delta_{x}$ (pixels)"
    , "$\\Delta_{y}$ (pixels)"
  )
)

datasummary_balance(
  ~trial_1_stimulus
  , data = df_movement_trial_1
  , notes = "Data source: Prolific sample."
  , escape = FALSE
)
```

```{r}
#| label: tbl-h1-trial-2
#| tbl-cap: Average time between cursor movements (Trial 2)
df_movement_trial_2 <- list_df[["cleaned"]][
  , .(
    trial_2_difference_Time
    , trial_2_stimulus
    , trial_2_difference_X
    , trial_2_difference_Y
  )
]
setnames(
  df_movement_trial_2
  , old = c(
    "trial_2_difference_Time"
    , "trial_2_difference_X"
    , "trial_2_difference_Y"
  )
  , new = c(
    "$\\Delta_{t}$ (milliseconds)"
    , "$\\Delta_{x}$ (pixels)"
    , "$\\Delta_{y}$ (pixels)"
  )
)
modelsummary::datasummary_balance(
  ~trial_2_stimulus
  , data = df_movement_trial_2
  , notes = "Data source: Prolific sample."
  , escape = FALSE
)
```

```{r}
#| label: tbl-h1-trial-3
#| tbl-cap: Average time between cursor movements (Trial 3)
df_movement_trial_3 <- list_df[["cleaned"]][
  , .(
    trial_3_difference_Time
    , trial_3_stimulus
    , trial_3_difference_X
    , trial_3_difference_Y
  )
]
setnames(
  df_movement_trial_3
  , old = c(
    "trial_3_difference_Time"
    , "trial_3_difference_X"
    , "trial_3_difference_Y"
  )
  , new = c(
    "$\\Delta_{t}$(milliseconds)"
    , "$\\Delta_{x}$ (pixels)"
    , "$\\Delta_{y}$ (pixels)"
  )
)

modelsummary::datasummary_balance(
  ~trial_3_stimulus
  , data = df_movement_trial_3
  , notes = "Data source: Prolific sample."
  , escape = FALSE
)
```

### Do colors shape perceptions of political objects?

To address the following question of whether the colors affect perceptions of the candidate and the yard sign, I ask participants to report whether they perceived the candidate to be a partisan -- either Republican, Democrat, or as non-partisan immediately after viewing each image. Everything on the yard signs remains constant except for the color. As representations of ideology are associated with more than just political views but things like space [@mills_et-al_2016_bbr] and color [@maestre_medero_2022_pr], differences between respondents on the perceived political affiliations of the candidate should be more than "by chance" differences. However, differences occur based on the associations between red and blue with partisanship and the lack of political information that the color white conveys.

I examine differences in respondents' reported perceptions of the candidate's partisan affiliation. As participants are asked this question for each treatment they view, the estimand of interest reflects the difference in perceptions of the candidate's partisan affiliation between the yard sign that they saw averaged across respondents. I estimate two ordered logistic regression where the main independent variables of interest are two indicator variables for whether respondents received the "red yard sign" or the "blue yard sign" in each round of Trial 1. The baseline category for both of those indicator variables is if they instead saw the "white yard sign".

My defined priors for both of these models' coefficients are Normally distributed with a mean of zero and a standard deviation of one. This reflects me starting from the position that my data need to provide evidence in support of my hypotheses rather than disproving them. The priors do allow for me to express uncertainty with this as I do have a belief that there is a chance my hypotheses are correct. Both models return $\hat{R}$ values of 1 indicating convergence and I confirm model performance by reporting the distributions of predicted values implied by my posterior distribution. These posterior predictive checks are included in @fig-h-2-ppc.

@fig-h-2-predictions present the predicted probabilities of an average subject reporting the candidate was either a Democrat, Independent, or Republican when viewing the different yard signs. The error bars reflect the high density credible interval for 95% of my posterior draws. Each bar reflects the predicted probability of an outcome -- listing the candidate is either a Democrat, Independent, or Republican. When interpreting the error bars, you will want to look at the difference in the error bars *between* yard sign treatments rather than *within* treatment. We see that the models indicate statistically meaningful differences between the yard sign treatments for each outcome. That is, the red and blue yard signs did shift people's perceptions of the partisanship of the candidate relative to the white yard sign. The credible intervals of these models are reported in the appendix in @tbl-hypothesis-2-main which contains the rest of the results from these models.

Digging in a little bit more about what these perceptions were, the predicted probability that subjects perceive the candidate with a Red yard sign to be Republican is almost 70%, whereas it is only about 30% when viewing a white yard sign. When given a red yard sign, the predicted probability the candidate is marked to be an independent is less than 30% and less than 5% to be a Democrat. However, when viewing a blue yard sign, the predicted probability of a subject perceiving the candidate to be a Democrat is at about 50% whereas it is less than 20% with a white yard sign. When viewing a blue yard sign, the predicted probability of subjects perceiving the candidate to be a Republican is less than 10% and about 45% to be an Independent. The full results are reported in @tbl-hypothesis-2-main in the appendix.

```{r}
#| label: fig-h-2-predictions
#| layout-nrow: 1
#| fig-cap: The partisanship of candidates change depending on the color of the yard sign
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["red"]]
  , x_axis = "trial_1_red_stimuli"
)
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["blue"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
)
red
blue
```

As the consistency by which the parties have used either the color red or blue has increased since the 2000's, I suspect that the age of my subjects may moderate this relationship. That is, the tendency for subjects to label red yard signs as a Republican candidate versus a different color may be stronger for those who are younger as the consistency in branding is the political environment they have been around more. I expect this particular relationship may be weaker for older subjects as they may place current branding strategies in a larger political context where this was not always the case.

I fit two ordered logistic regressions where the independent variables are indicator variables reporting whether the participant received the red (the first model) or they recieved the blue treatment (the second model). Those included in the baseline category for both models are those who received the white yard sign treatment. Since I believe that age may moderate this effect, I include an interaction term for both of these models that multiplies these treatment indicator variables with age.

Though my pre-registered expectations were that age would moderate this effect, these models suggest that there are not substantive or statistically meaningful differences in how older and younger participants responded to these treatments. The results of these models are included in the appendix in @tbl-hypothesis-2-main.

### Do these perceptions require consistency between information types?

Another hypothesis derived from the snap-judgment model suggests that inconsistency in the yard sign's visual information will lead to more mixed perceptions of the candidate's political stances. The design of the latter trials in the study presents yard signs with mixtures of non-partisan and out-partisan colors. For example, primarily red and presumably Republican yard signs, but has some blue or white in them.

I should expect that the trials that use less "consistent" visual information demonstrate more ambivalence among respondents in their reported perceptions of the politician's positions. Specifically, I expect that participants will perceive the yard signs that have both red and blue on them as more moderate and that the higher proportion of the color red or blue among the two colors will lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic. This is not to say that I expect the results to change significantly, but rather that the certainty by which I can predict individuals' guesses of the candidate's partisan affiliation to be weaker.

I fit four ordered logistic regression models. Two for each trial. Where each model for each trial models whether an average subject in the study reported that the yard sign they saw in the trial was a Democrat, Indepdent, or a Republican. @tbl-hypothesis-2a located in the appendix reports the full results of these models while @fig-h-2a-ppc located in the appendix reports the posterior predictive checks of these models.

```{r}
#| label: fig-h-2a-predictions
#| layout-nrow: 2
#| fig-cap: Mixing red and blue in a yard sign increases uncertainty about partisanship
#| fig-subcap:
#|   - Trial 2 Red treatment
#|   - Trial 2 Blue treatment
#|   - Trial 3 Red treatment
#|   - Trial 3 Blue treatment
plot_trial_2_red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_2_red"]]
  , x_axis = "trial_2_red_stimuli"
)
plot_trial_2_blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_2_blue"]]
  , x_axis = "trial_2_blue_stimuli"
  , treatment = "Blue"
)
plot_trial_3_red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_3_red"]]
  , x_axis = "trial_3_red_stimuli"
)
plot_trial_3_blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_3_blue"]]
  , x_axis = "trial_3_blue_stimuli"
  , treatment = "Blue"
)
plot_trial_2_red
plot_trial_2_blue
plot_trial_3_red
plot_trial_3_blue
```

The results from these models offer partial support for my expectations. First, I see that yard signs using less blue are not as distinguishably Democratic as the white yard sign. In other words, voters are not meaningfully more likely to report that the yard sign with less blue on it belongs to a Democratic candidate as a white and black yard sign. So, the strength of using a blue yard sign to communicate alignment with the Democratic party weakens if you use less blue relative to white or include red on it. With red yard signs, however, we see that voters still see them to be belonging to Republican candidates even when we reduce the amount of red on the yard sign and even include blue.

One potential reason for this may be the association of the American flag when using all three colors. Particularly given the Republican party's tendency to condemn those who do not adhere to social norms about showing respect to the American flag. This, however, is untestable based on the data I did not collect for this study. So, this explanation is speculation. However, what we do see is that there are bounds by which at least the color blue on a yard sign indicates to voters that the candidate is a Democrat. What remains unclear is whether these perceptions of ownership by a partisan candidate influences people's willingness to support that candidate or to express favoritism towards it ($H_3$).

### Does the color of a yard sign explain support for a candidate?

```{r}
#| label: fig-h-3-predictions
#| layout-nrow: 1
#| fig-cap: Probability of voting for candidate with yard sign
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_3"]][["red"]]
  , x_axis = "trial_1_red_stimuli"
  , treatment = "Red"
  , hypothesis = "H3"
  , x_label = "Party ID"
  , y_label = "Pr(Vote for candidate)"
  , legend_title = "Treatment"
)
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_3"]][["blue"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
  , hypothesis = "H3"
  , x_label = "Party ID"
  , y_label = "Pr(Vote for candidate)"
  , legend_title = "Treatment"
)
red
blue
```

### Do partisans process co-partisan branding faster?

The other analytical tasks do not examine expectations derived from the motivated reasoning portion of the model. That is, do people process in-group information faster than out-group information? There is evidence of these tendencies in political circumstances [@lodge_taber_2013_cup].

To examine whether motivated reasoning is also active with the processing of politically-relevant color, I examine the difference between the amount of time between the start of viewing a stimulus and clicking "Next" to stop viewing the stimulus among those who were viewing a presumed co-partisan yard sign relative to those viewing a presumed out-partisan yard sign. As motivated reasoning tends to be more prevalent among strong partisans and those highly knowledgeable and interested in politics [@lodge_taber_2013_cup], I control for responses to the pre-treatment knowledge, interest, and partisan strength batteries.

## Study 2

### 2023-06-19 chapter_2/src/prr/color_influence_pre-reg_anon.qmd
I hate submodules

--- 2023-06-19 chapter_2/src/_chapter_2.qmd
@@
-# How do colors convey political information and effect individual attitudes? {#sec-2}
-<!--
-    - Description: QMD script for chapter 1
-    - Updated: 2022-12-28
-    - Updated by: dcr
-    - Notes:
-        * Code:
-            ** pre-test:
-                *** 00_pre-test.py
-                *** table called pre-test
-            ** Scraping:
-                *** CAPD
-                    **** Execute 01_capd_text_scraping.ipynb interactively
-                        ***** table called ch_1_capd_yard_signs
-                    **** Execute 02_capd_img_scraping.ipynb interactively
-                        ***** table called ch_1_capd_yard_signs
-                    **** Execute 03_capd_downloading_images.py
-                        ***** does so at end of 02_capd_img_scraping.ipynb
-                    **** Execute 04_mit_election_lab_merge.py
-                        ***** does so in the some-script-execution block below
-        * Writing:
-            ** First should write an annotated bibliography for this chapter
-            ** Once annotated bibliography is complete, should have enough to start working on a pre-registered report for this chapter
+---
+title: |
+  Pre-analysis plan
+subtitle: |
+  How do colors convey political information and affect individual attitudes?
+#code-repo: |
+#  For replication, go to: <https://github.com/DamonCharlesRoberts/color_as_political_information>.
+author:
+  - name: Anonymized for peer review
+  #- name: Damon C. Roberts
+  #  email: damon.roberts-1@colorado.edu
+  #  orcid: 0000-0002-4360-3675
+  #  title: PhD Candidate
+  #  affiliations:
+  #    - id: CU
+  #      name: University of Colorado Boulder
+  #      department: Political Science
+  #      address: 333 UCB
+  #      city: Boulder
+  #      region: CO 
+  #      postal-code: 80309-0333
+abstract: |
+  Colors are important to politics as a form of political information.
+Building upon existing theories of political information processing, attitude formation, and affect in neuroscience, I present a snap-judgement model of political information processing.
+In this model, colors provide automatic information about a politically-relevant object that may shape subsequent processing of more complex information.
+The model has important implications for how we consider the role that visual information has on political information processing and attitude formation.
+The model additionally provides clarity on motivations behind party branding and the ways in which information may activate partisan biases pre-consciously.
+I test this model using a survey experiment tracking participants' mouse movements to view different parts of yard signs that vary the use of partisan and non-partisan colors.
+I additionally leverage congressional redistricting to examine changes in color use for political yard signs as a strategic choice for attracting voters by communicating partisanship.
+bibliography: "../../../assets/references.bib"
+format:
+  hikmah-pdf:
+    # Spit out in drafts directory
+    latex-output-dir: "../../out/prr"
+    # Use biblatex-chicago
+    biblatex-chicago: true
+    biblio-style: authordate
+    biblatexoptions: 
+      - backend=biber
+      - autolang=hyphen
+      - isbn=false
+      - uniquename=false
+code-overflow: wrap
+nocite: |
+  @quarto
+execute:
+  echo: false
+  warning: false
+  message: false
+  cache: false
+params:
+  replicate: false
+---
 
--->
-
-# Introduction
-
-::: {#fig-pre-2000-logos layout-nrow="2"}
-![Republicans pre-2000](../../assets/rnc_logo_pre-2000.png){#fig-republican}
-
-![Democrats pre-2000](../../assets/dnc_logo_1960.png){#fig-democrat}
-
-![Republicans 2023](../../assets/rnc_logo_2023.png){#fig-republican-post}
-
-![Democrats 2023](../../assets/dnc_logo_2023.png){#fig-democrat-post}
-
-Party logos
-:::
-
-Are colors important to politics?
-I argue that they convey information that matters to campaigns and voters.
-People rely on more than purely political information to understand politics [@pietraszewski_et-al_2015_c].
-To reduce cognitive load, the affiliation detection system allows for efficient social behavior prediction by associating various cues with a group.
-In politics, associating Black voters with the Democratic party and White voters with the Republican party is one example [@pietraszewski_et-al_2015_c].
-As Americans consistently link the colors red and blue with the Republican and Democratic parties [@elving_2014_npr;@williams_et-al_2022_jomp], as well as their connection to ideology [see @maestre_medero_2022_pr for example], we should explore whether color acts as an affiliative cue for individuals in American politics.
-
-Existing theories of political information processing have yet to examine visual information more broadly.
-As a simple yet ubiquitous piece of visual information, color may have more influence over shaping political views than we give it credit.
-As visual information is processed automatically and faster than other forms of information [see @ames_et-al_2012_ohsn], I argue that it triggers associated neurological pathways that shape the subsequent information processing of the more traditionally considered types of political information.
-Such a process implies that the presence of politically-relevant colors has the potential to, directly and indirectly shape political attitudes.
-
-I propose two studies to test these claims.
-Yard signs are a simple yet effective source of campaign branding for political candidates.
-They shape the attitudes of those who view them [@makse_et-al_2019_oup], and they can even aggregatively shape electoral outcomes [@green_et-al_2016_es].
-As yard signs are a simple and static form of campaign advertising, they cannot rely heavily on more complicated forms of information.
-However, one form of information they rely on and vary in is their color.
-With these characteristics, yard signs are an ideal candidate both from a statistical standpoint and also substantive.
-From a statistical standpoint, as they are static forms of party branding they have fewer moving parts, reducing the statistical confounds that may increase Type I errors.
-From a substantive standpoint, while we understand that yard signs matter to campaigns, we have yet to systematically explore more simple design choices such as color.
-
-In [Study 1](#sec-study-1), I propose an experiment that examines whether the public notice and whether their attitudes are shaped by "Republican Red" and "Democratic Blue" on the yard signs of a fictional candidate.
-In [Study 2](#sec-study-2), I examine whether campaigns react to the partisan composition of an electorate in recognition of color's importance to voter decision-making and attitude formation.
-First, I have informal interviews with campaign staff to determine what shapes the decisions about what colors to include on a campaign's yard sign.Second, I do this by examining how electoral context shapes variation in using these partisan colors.
-
-I then present a pre-test that experimentally tests whether yard signs using "Republican Red," "Democrat Blue," and White lead to different perceptions of the candidate's political views.
-I find that a fictional candidate with a background of "Republican Red" is perceived to be more Republican, and a fictional candidate with a background of "Democrat Blue" are perceived to be more Democratic.
-I also find that Republican voters are more likely to report a willingness to vote for the candidate with "Republican Red" on the yard sign, and Democratic voters are more likely to vote for the candidate with "Democrat Blue" on the yard sign.
-
-# The role of visual information in politics
-
-A central theme of an edited issue of *The International Journal of Press/Politics* is that visual politics is important and understudied [@lilleker_2019_pm].
-Those who are engaged in these questions attribute these challenges to methodological sophistication and the difficult task of interdisciplinary theorizing [@gerodimos_2019_pm; @bucy_joo_2021_ijpp].
-
-The rise of television consumption changed the focus of the medium in the research for political communication scholars [@hall-jamieson_2014_ohpc].
-In a similar way, so does the rise of image-based social media and has set new agendas.
-For several methodological and disciplinary reasons, the visual aspects of television were of little focus in the literature [@bucy_joo_2021_ijpp].
-However, the news organizations and politicians are responding to the ubiquitous use of the public to use image-dominant social media platforms like TikTok and Instagram, by joining such platforms.
-They are relatively active on these platforms as well.
-Scholars need to make this transition to integrate the role of simple visual information into our theories of political information processing (abbreviated as *pip*) and attitude formation.
-
-How does politically-relevant visual information matter to politics?
-From an evolutionary-biological perspective, visual information has been a common source of information for millions of years that a variety of single-and-multi-cell organisms rely upon to evaluate their environment [see @grabe_bucy_2009_oup, Chapter 1 for a useful discussion].
-Visual information processing, as an ancient biological invention, the human brain is organized around the processing of it.
-Reflecting on this, many neuroscience scholars argue that visual information is the fastest form of information processing for humans.
-For example, even complex visual information, such as the warmth expressed in someone's facial features, is automatically and subconsciously processed in only about 33 milliseconds (abbreviated as ms) [@ames_et-al_2012_ohsn].
-
-Approached from a different perspective, as humans are cognitive misers \index{cognitive misers}, visual information in the realm of politics provides efficient information to voters about politically-relevant actors and events [@lilleker_2019_pm].
-Evidence suggests that voters rely on simple visual information in the background of an image to infer ideological positions [@dan_arendt_2021_ijpp] and that coverage reflects electability perceptions [@stewart_et-al_2021_ijpp] -- these influence reported desire to vote for the candidate.
-Images posted on social media by politicians provide more personalized information about them, and they take on their own styles [@lindholm_et-al_2021_ijpp; @peng_2021_ijpp], reflecting that it is an alternative source of information curated to attract support.
-Evidence suggests that even simple party branding on yard signs has an emotional appeal and encourages a shift in attitudes toward the person who owns the yard sign [@makse_et-al_2019_oup].
-That is, even branding as simple as yard signs appears to influence the attitudes of those who view them.
-However, like all types of party branding, there remain questions about the individual visual components' contribution.
-
-While visual politics is enjoying more attention from social scientists, there still needs to be more focus on the simplest visual information: color.
-In the context of the United States, the "Republican red" and "Democratic blue" is a relatively recent invention that likely has significant import in an era of significant effort by the parties to distinguish themselves from each other [@clifford_2020_pb] and where voters toe the party line [@utych_2020_es].
-Since the 2000 presidential election, the media have consistently used red on their electoral maps in "horserace" journalism to represent Republicans and blue to represent Democrats [@elving_2014_npr].
-The supposed consequence is that Democrats now report a preference for the color blue over the color red, and Republicans report a preference for the color red over the color blue [@schloss_palmer_2014_pbr].
-Others have demonstrated the strategic choices that candidates make on branding choices -- including color -- based on the types of information they want to convey to voters to distinguish them from their rivals [see @williams_et-al_2022_jomp].
-Beyond this, however, we have yet to develop and test theories about color's broader impacts on political information processing and attitude formation.
-
-As the broader field of study of visual politics is under-theorized, theorizing about the use of color as a form of information is also quite limited -- perhaps even more so.
-The literature that does exist argues that colors are a source of visual information to classify more abstract concepts for voters.
-For example, in western Europe, voters are better at connecting the ideological positioning of a party with the color they use in their branding [@casiraghi_et-al_2022_pp].
-The ability to do so is strengthened when the party is longer-surviving and is more prominent [@casiraghi_et-al_2022_pp].
-The use of politically-relevant colors activates biases toward pre-existing ideological and partisan preferences among voters in a Spanish sample [@maestre_medero_2022_pr].
-And male and female candidates in the United States use different colors -- among other things such as fonts -- in their campaign branding to convey distinguishing information about themselves [@williams_et-al_2022_jomp].
-Despite the existing evidence, the particular psychological mechanisms driving this remain unclear.
-For example, it is unclear how colors may be organized into a cognitive schema that enables voters to quickly access and connect these colors to more complex political attitudes.
-Furthermore, it is unclear from existing evidence how colors may not just be associated with complex attitudes, but how they may enable political attitude formation and may strengthen existing connections between different political objects.
-As a jumping-off point, we can use the literature of political information processing (abbreviated as *pip*)\index{political information processing} to establish a common understanding of how political information is processed and how attitudes are formed by the processing of political information.
-
-The first prominent model of *pip* derives from rational choice perspectives.
-The memory-based model of *pip* views attitudes as a weighted collection of prior information [see @zaller_1992_cup].
-As individuals receive new information, they organize it into a schema that is relative to prior objects they already have encoded.
-By encoding this new information, the model predicts that individuals incorporate this new object with similar objects to form an attitude.
-This schema then may be more accessible in similar contexts and may then sample from its elements when prompted to express a political attitude.
-While the Receive-Accept-Sample (RAS) model accepts the view that expressed attitudes are a weighting of information most accessible at the time of attitude expression [@zaller_feldman_1992_ajps], it still presupposes that the weighting is an average of prior information.
-
-The second prominent model challenges this latter point.
-The online model of *pip* contends that individuals do not evenly weigh information, but that whether they even store it in their long-term memory to access later is biased in the direction of supporting pre-existing attitudes [@lodge_taber_2013_cup]; this phenomenon is referred to as motivated reasoning by the psychology literature [@kunda_1990_pb].
-This model suggests that people ignore new information that goes against their prior beliefs and that information confirmatory of their preferences is quicker to access -- referred to as hot cognition [@lodge_taber_2013_cup].
-
-The online model conceptualizes this underlying information encoding and attitude retrieval mechanism as automatic [@lodge_taber_2013_cup].
-This occurs due to the information's strong associations with valanced appraisals of the information guiding the attitude [@lodge_taber_2013_cup].
-This brings political scientists closer to the dominant conceptualizations among neuroscientists and psychologists concerned with memory retrieval, encoding, and attitude formation [see @fazio_2007_sc].
-Namely, that memories are encoded and retrieved quickly based on associations due to their association with valanced appraisals [@kensinger_fields_2022_ohhum].
-What remains unexplored is how visual information such as color may prime individuals to engage in motivated reasoning pre-consciously.
-If they keep their attention on the object, what paths are activated by such information?
-
-# Integrating color into a model of political information processing
-
-Existing models of *pip* primarily focus on complex forms of political information such as text.
-As individuals process visual information before other sorts of information, we might expect that they may form a snap judgment or the initial appraisal of an object.
-This has several important implications, from suggesting that we broaden our theories of *pip* to reconsider what constitutes politically-relevant information to what it means for our substantive understanding of how people process political information and the calculus involved in political attitude formation.
-
-Though the online information processing model goes a long way to inform us about how our physiology engages attitude formation and retrieval, the types of information it considers necessarily limits the theory's applicability to other forms of political information.
-Color and other simple visual information are processed much quicker and occur more frequently than text-based information [@mehta_zhu_2009_s].
-As the color and other visual information are processed differently, we should also consider its use as political information.
-As visual information is affectively encoded [@cimbalo_et-al_1978_jgp], it can affect the affective state and processing of more complex information, such as text.
-The visual information provides a snap judgment or an impression of the object through faster processing and activates particular neurological processes that influence subsequent information appraisals [@ames_et-al_2012_ohsn].
-This implies that the conclusions drawn from such *pip* models may be systematically biased without considering the upstream effects of non-text information; such as simple visual information like color.
-
-Before expanding upon the role of colors in shaping political attitudes, let me first define an attitude as a concept.
-An attitude represents an accessible, valanced evaluation of associated prior information and experiences.
-This conceptualization fits with that of the Object-Evaluation Associations Model [@fazio_2007_sc].
-As opposed to viewing attitudes as a latent collection of memories, as is done in the memory-based model of *pip* [@zaller_feldman_1992_ajps], it views attitudes as measurable evaluations of memories.
-As memories are at the core of an attitude, the association of memories with its evaluative component [see @kensinger_fields_2022_ohhum] contributes to the perspective that attitudes are affective.
-This implies that we should be able to measure attitudes but that such an operationalization requires careful consideration of the context's role in any given measure of an attitude as they result from memories [@fazio_2007_sc].
-
-In line with the existing models of *pip*, I conceptualize attitudes as associative.
-This means that attitudes may be unstable - not stochastically, in any case.
-As attitudes are associative, they manifest slightly differently depending on the associative paths activated [@fazio_2007_sc].
-The retrieval of relevant memories to the attitude depends on many factors, such as the recency of the event, the similarity of the context, and the importance or salience of the memory [@kahana_et-al_2022_ohhum].
-This means that the memories retrieved to contribute to an attitude are quite variable.
-However, to understand where that variability comes from, we must understand the deeper processes influencing how information is encoded and later retrieved.
-This illustrates my need to build upon the reigning models of *pip*.
-Colors may act as a contextual feature that may lead to this variability in how a given set of political information may shape attitudes.
-
-Colors are associative and are affectively encoded [@cimbalo_et-al_1978_jgp].
-When individuals access a memory, they do not just recall an object, but they may recall visual information such as the color of an object [@mehta_zhu_2009_s].
-Due to these features, colors can be processed unconsciously and very quickly [@mehta_zhu_2009_s].
-As they are affectively encoded, their associations with particular memory contribute to the evaluative component of the memory.
-For example, individuals associate colors like red with anger and arousal [@valdez_mehrabian_1994], whereas individuals associate blue with things like happiness and pleasure [@dandrade_egan_1974_ae].
-This means that colors are compelling as contextual information shaping the subsequent processing and integration of "traditional" forms of political information to construct an attitude.
-As the preference for a particular color correlates with political attitudes [@schloss_palmer_2014_pbr], they may have some causal influence upon political attitudes; rather than just a correlation with them.
-
-According to the literature in affective neuroscience, visual information is processed in parts of the brain, such as the visual cortex [@goldstein_brockmole_2017_cl].
-This will activate other areas of the brain and will make associated paths "hot." One such area is the amygdala.
-Neuroscientists believe that as visual information is quickly and subconsciously processed, the amygdala takes and appraises it based on the paths it activated; this generates a simple affective response to such information [@winkielman_et-al_2011_ohsn].
-More complex, categorical emotion occurs later in conscious processing [@winkielman_et-al_2011_ohsn].
-Once politically-relevant visual information is detected, the retina passes it to the brain.
-Once there, the brain attempts to classify the visual information by activating networks of neurons associated with the current information.
-With these activated pathways, the brain also attempts to appraise such information based on quick classification.
-For attitude formation, this implies that, as memories are affectively encoded [@kensinger_fields_2022_ohhum], these memories help areas such as the amygdala to appraise the current information.
-
-These fast affective classifications are valanced rather than the more laborious categorization of specific emotions (e.g., anger, anxiety, fear, happy).
-What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_2000_arps], I conceptualize affect as a more extensive system that considers emotion only as a conscious classification process that occurs later than initial valanced appraisals of an object [@sander_2013_chhan; @ralph_anderson_2018_pup].
-That is, emotion -- the complex classification of appraisals -- is a conscious component of affect.
-The pre-conscious process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_et-al_2011_ohsn; @dror_2017_er].
-
-The pre-conscious appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_et-al_2011_jop; @ralph_anderson_2018_pup].
-This has evolutionary roots for survival [@ralph_anderson_2018_pup; @parker_2003_p].
-While affective appraisals can lead to complex motivations, such as anxiety leading to motivations for information seeking [@marcus_2000_arps], affective appraisals are valanced and are more automatic [@winkielman_et-al_2011_ohsn].
-These affective appraisals lead to a desire to either retract or engage more with the object [@valentino_et-al_2011_jop].
-The snap judgment resulting from the automatic processing of politically relevant visual information should likely lead to an affective response that motivates either a desire to engage more with the object or disengage.
-
-While the visual information may encourage a particular immediate reaction to engage or disengage from the information, subsequent information processing and more conscious processing adjusts this initial appraisal generated by the snap judgment [@kensinger_fields_2022_ohhum].
-While subsequent information may amend one's snap-judgment, the snap-judgment nevertheless influences the processing of subsequent information by activating particular paths, which is later encoded as associated with the object as it converts to a memory [@lodge_taber_2013_cup; @kensinger_fields_2022_ohhum].
-
-@fig-snap-judgement-model presents an illustration of the snap-judgment model.
-
-```{mermaid}
-%%| label: fig-snap-judgement-model
-%%| fig-cap: Snap judgement model
-%%| fig-width: 6
-%%{init: {'theme':'base', 'themeVariables':{'primaryColor':'#ffffff', 'primaryBorderColor': '#000000'}}}%%
-graph TD;
-    A[Detection of politically-relevant visual information] --> B(Activation of retrieval mechanism);
-    B --> C[Memory and contiguous paths hot];
-    C --> D[Appraisal of hot autonomous nervous system];
-    D --> E1[Negative Valence];
-    D --> E2[Positive Valence];
-    E1 --> F1[Disengagement motivation];
-    E2 --> F2[Attention activated];
-    F1 --> |Neg. new information| G1[Encoded as negative];
-    F1 --> |Pos. new information| G2[Encoded as positive];
-    F2 --> |Neg. new information| G3[Encoded as negative];
-    F2 --> |Pos. new information| G4[Encoded as positive];
-    G1 --> H1[Strengthens negative path];
-    G2 --> H2[Weakens negative path];
-    G3 --> H3[Weakens positive path];
-    G4 --> H4[Strengthens positive path];
-    G2 --> |forgotten| H1;
-    H2 --> |reinforced| G2;
-    H3 --> |reinforced| G3;
-    G3 --> |forgotten| H4;
-```
-
-All of this means for *pip* is that when we view political events or consume political information with a visual component, we are going to encode visual information along with it.
-Taking expectations formed from theories of motivated reasoning [see @kunda_1990_pb], I expect that the visual information that we encode with it is likely congruent with the evaluation of the object; we are likely to be unwilling to encode the visual information that is not congruent with the visual information as we do with text-based political information [see @lodge_taber_2013_cup].
-That is because unconsciously, we will experience a motivation to disengage from such information as soon as we appraise the visual aspects of an object as incongruent with existing attitudes and, therefore, be uncomfortable.
-It should also influence how we retrieve memories when we encounter new information, which will affect the attitudes we express.
-Additionally, this predicts that we will spend less time processing, accessing, and encoding congruent information [@lodge_taber_2013_cup].
-
-Let me illustrate the snap-judgment model with a common experience for residents of the United States.
-Say you are driving down a highway.
-At 65 miles an hour, you are traveling at about 95 feet per second at this speed.
-You split your attention.
-You focus your eyes on the conditions of the road in front of you, the cars in front of you, and the rear-view mirror where your kids are either dropping food in the crevice between the seats or trying to grab your attention.
-Out of the corner of your eye, you see a sign.
-It is not a road sign because it is not on the familiar white or yellow background with black lettering.
-It is election season.
-You correctly infer that it is a political yard sign.
-In this split second, you notice the sign's color and may see a name: Mitch McConnell.
-You now are racking your brain to think about who that is.
-If you are politically engaged, you might come to that recognition of the name quickly or it may take you significantly longer if you are less politically engaged [see @kahana_et-al_2022_ohhum].
-You figure out that they are a Republican politician.
-You may have come to this with the help of the fact that every year you have seen yard signs on this stretch of highway.
-You know that when you see those electoral maps pop up on your news app on your phone that the electoral forecasts always represent Republican support with red and blue for Democrats.
-Once you have figured out who this person is, with the help of this other information, you react: "ugh, that guy is too loyal to Trump" or "yeah!
-He's loyal to Trump".
-You've expressed a political attitude.
-
-What the snap-judgment model predicts is happening in your head is that as soon as the light that bounces off the sign to produce a particular wavelength hits your eyes, your brain is already trying to make sense of this information.
-This is a valuable tool for survival that biology has optimized for millions of years [@parker_2003_p].
-Rather than slowly processing the visual information and finding yourself in the jaws of a predator or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and subconsciously [@newell_1990_hup].
-To make sense of such information, it accesses familiar information similar to what it is currently attempting to process for efficiency [@kahana_et-al_2022_ohhum].
-This is accessing memories and contains valanced information [@kensinger_fields_2022_ohhum]: should I avoid this, or is it pleasant?
-Once the brain has finished such processing, it can pass its prediction to your conscious memory.
-Once you form a reflex of avoid or approach, this opens up space for your brain to process the more complex information: to take the patterns of the light as shapes that construct symbols and letters.
-This comes later because this information not only requires access to information about what it *is* but also what it *means*; once you understand what it means, you have the information necessary to evaluate it.
-
-The snap-judgment model predicts that you first process the colors of the yard sign.
-You access associative memory to figure out what those particular wavelengths represent: red, white, blue?
-As these colors are associated with different emotional states [see @cimbalo_et-al_1978_jgp] and the resulting behavioral consequences, your brain starts sending signals to the rest of your body to prepare it to react [see @sander_2013_chhan; @dror_2017_er].
-You now need to figure out what the rest of that information was.
-What were the patterns of that light?
-It appears that there were some white letters on the sign.
-There was an "E," a "L," an "E," a "C," and a "T." That creates the word "ELECT." Meaning to vote for.
-There were some more letters on the sign: an "M," an "I," a "T," a "C," and an "H." A name.
-The full name is "Mitch McConnell".
-Since it is about politics, it must be a politician named Mitch McConnell.
-Now imagine the information was the same, except the color was blue.
-You may take more time to figure out how that Mitch McConnell person is and come to your reaction to seeing their yard sign.
-This is because, without the color red, you first are thinking about Democrats who are named Mitch McConnell.
-Only when you come up empty on your mental Rolodex do you figure out that it is the Republican Mitch McConnell.
-
-How do you react to the color and then to the name?
-Social groupings are not simply abstract concepts invented by social psychologists; our neurobiology reflects them.
-For example, researchers find activation of parts of the brain, such as the anterior insula, when we see someone in our social group outperformed by someone from the out-group [see @zink_barter_2012_ohsn].
-The anterior insula activity is associated with physical and emotional pain, not just for ourselves but also for others [@adolphs_janowski_2011_ohsn].
-Others have also observed that when seeing someone part of a high-status social group, there is an increase in activity in the sensorimotor cortex and supplementary motor area, indicating more activity in the areas of the brain that encourage movement [@zink_et-al_2008_n].
-Visual information about someone in your social group speeds up processing, is more salient, and demands more attention than visual information about an object outside your social group [@zink_barter_2012_ohsn].
-
-There is significant evidence supporting the theory that our partisan identification reflects more than just our attitudes about politics but a social identity [see @campbell_et-al_1960_jws; @mason_2018_cup] that guides our attitudes [see @achen_bartels_2016_pup; @white_et-al_2014_apsr; also @bullock_2011_apsr].
-As our political attitudes reflect shared views among co-partisans [@pickup_et-al_2020_pb], the congruence between political information and our partisan identification influences our reactions to such political information.
-This means that the visual information we glean from politics will likely motivate those neurological features of social groups and explain the resulting behavioral manifestations reacting to such information.
-That information is also likely to be processed at different rates as well.
-That is, while visual information carries general affective associations, we should also expect associations between politically-relevant colors with partisan identification.
+{{< pagebreak >}}
 
@@
 +--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
-| $H_2$        | Colors shape perceptions of candidate based on partisan associations                                                                                |
+| $H_2$        | Red is associated with Republicans and Blue is associated with Democrats                                                                            |
 +--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
@@
 
-From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that these colors that they notice shape perceptions about the person and ideological symbol represented in the branding -- meaning that they express different levels of preference for receiving more information that is similar to what they saw and their levels of preference for supporting such a campaign ($H_{2}$); that the consistency of information explains more positive perceptions -- simple visual information with more complex "traditional" information ($H_{3}$); this positive and consistent information is processed quicker than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) in line with their primary objective of reelection [@fenno_1973_lb; @mayhew_1974_yup].
+From my review of the literature in political science, neuroscience, and communication, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that these colors that they notice shape perceptions about the person and ideological symbol represented in the branding -- meaning that they express different levels of preference for receiving more information that is similar to what they saw and their levels of preference for supporting such a campaign ($H_{2}$); that the consistency of information explains more positive perceptions -- simple visual information with more complex "traditional" information ($H_{3}$); this positive and consistent information is processed quicker than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) in line with their primary objective of reelection [@fenno_1973_lb; @mayhew_1974_yup].
 A summary of these hypotheses are included in @tbl-hypotheses.
@@
 #| label: setup-pre-test-block
-
-    #* Set seed
-set.seed(12062022)
+# set working directory
+#setwd("./chapter_2/src/prr")
+# Set seed
+set.seed(12102022)
+#setwd("./chapter_2/src/prr")
 # Source cleaning script
-source("01_pre-test_cleaning.R")
-    #* Load functions
+source("eda/pre-test/01_pre-test_cleaning.R")
+# Load relevant functions
+if (params$replicate == TRUE){
   box::use(
-    data.table[...],
-    modelsummary[modelsummary, datasummary_skim],
-    cmdstanr[...],
-    brms[bf, prior, brm, rename_pars, make_stancode, make_standata, pp_check, cumulative, bernoulli],
-    rstan[read_stan_csv],
-    marginaleffects[avg_slopes, posterior_draws, plot_slopes],
-    ggplot2[ggplot, aes, labs, theme_minimal, scale_y_discrete, geom_boxplot],
-    bayesplot[color_scheme_set, bayesplot_theme_set, mcmc_combo, mcmc_areas, pp_check],
-    ggdist[stat_halfeye]
+    modelsummary[
+      datasummary_skim
+    ]
+    ,marginaleffects[
+      avg_slopes
+      ,posterior_draws
+      ,plot_slopes
+    ]
+    ,ggplot2[
+      ggplot
+      ,aes
+      ,theme_minimal
+      ,labs
+      ,scale_y_discrete
+    ]
+    ,ggdist[
+      stat_halfeye
+    ]
+    ,brms[
+      brmsformula
+      ,cumulative
+      ,prior
+    ]
+    ,rstan[stan_model]
+    ,./R/sim_all[sim_all]
+    ,./R/discrepancy_df[discrepancy_df]
+    ,./R/true_positive_hist[true_positive_hist]
   )
-#cmdstanr::set_cmdstan_path("C:\\cmdstan")
-    #* default theme
-#red_custom <- c("#DCBCBC", "#C79999", "#B97C7C", "#FFFFFF", "#8F2727", "#7C0000")
-color_scheme_set(scheme = "gray")
-bayesplot_theme_set(new = theme_minimal())
+} else {
+  box::use(
+    modelsummary[
+      datasummary_skim
+    ]
+    ,marginaleffects[
+      avg_slopes
+      ,posterior_draws
+      ,plot_slopes
+    ]
+    ,ggplot2[
+      ggplot
+      ,aes
+      ,theme_minimal
+      ,labs
+      ,scale_y_discrete
+    ]
+    ,ggdist[
+      stat_halfeye
+    ]
+    ,./R/discrepancy_df[discrepancy_df]
+    ,./R/true_positive_hist[true_positive_hist]
+  )
+}
   #* default tails
@@
 
-data[["clean"]][ # select the following columns
-    , .(Female, White, age, PartyId, BlueTreatment, RedTreatment, Vote)
-] |>
+df_select <- data[["clean"]][ # select the following columns
+  , c("Female", "White", "age", "PartyId", "BlueTreatment", "RedTreatment", "Vote"), with = FALSE
+] |> as.data.frame()
+
 datasummary_skim( # make a table of descriptive statistics
-    notes = c( # add some notes to the table
+  df_select
+  , notes = c( # add some notes to the table
       "Data source: Pre-test experiment.",
@@
   )
+  , histogram = FALSE
+  , output = "latex"
 )
@@
 
-source("04_pre-test_party_model.R")
+if (params$replicate == TRUE) {
+  PartyFormula <- bf(
+    Party ~ RedTreatment + BlueTreatment
+    ,family = cumulative(link = "logit")
+  )
+  PartyModel <- brm(
+    formula = PartyFormula,
+    ,data = data[["clean"]]
+    ,chains = 1
+    ,silent = 0
+  )
+  # Store model object
+  save(
+    PartyModel
+    ,file="../../data/models/prr/pre-test/pre-test_party_model.RDS"
+  )
+} else (
+  # load the stored model object
+  load(
+    file="../../data/models/prr/pre-test/pre-test_party_model.RDS"
+  )
+)
+
 ```
@@
 
-PartyAMES <- avg_slopes(
+partyAMES <- avg_slopes(
   PartyModel,
@@
 ggplot(
-  data = PartyAMES,
+  data = partyAMES,
   aes(
@@
   y = "",
-  caption = "Data source: Pre-test.\n Distribution of AME's for model posterior draws using HDI's.\n Dot reflects median posterior draw where bars reflect 90% and 95% credible intervals."
+  caption = "Data source: Pre-test.\n Distribution of AME's for model posterior draws using HDI's.\n Interpreted as the logged odds of labelling the candidate as a partisan\n given whether they viewed a red yard sign or blue yard sign\n while holding all other variables at their mean value.\n Dot reflects median posterior draw where bars reflect 90% and 95% credible intervals."
 ) +
@@
 #| include: false
-
-source("05_pre-test_vote_model.R")
+if (params$replicate == TRUE) {
+  # fit the model
+  VotePreTestFormula <- bf(
+    Vote ~ RedTreatment + BlueTreatment + PartyId + RedTreatment * PartyId + BlueTreatment * PartyId
+    ,family = cumulative(link = "logit")
+  )
+  VotePreTestModel <- brm(
+    formula = VotePreTestFormula
+    ,data = data[["clean"]]
+    ,chains = 1
+    ,silent = 0
+  )
+  # Store model object
+  save(
+    VotePreTestModel
+    ,file="../../data/models/prr/pre-test/pre-test_vote_model.RDS"
+  )
+} else {
+  # load the stored model object
+  load(
+    file="../../data/models/prr/pre-test/pre-test_vote_model.RDS"
+  )
+}
 ```
@@
     y = "CME of Red Treatment",
-    caption = "Data source: Pre-test.\n Conditional Marginal Effects of Red Treatment upon support for candidate.\n Uncertainty reflected by predicted posterior draws at the 95% level with HDI's."
+    caption = "Data source: Pre-test.\n Conditional Marginal Effects of Red Treatment upon support for candidate.\n Interpreted as the logged-odds of voting for fictional candidate\n conditional on varying levels of Party Identification.\n Uncertainty reflected by predicted posterior draws at the 95% level with HDI's."
 )
@@
     y = "CME of Blue Treatment",
-    caption = "Data source: Pre-test.\n Conditional Marginal Effects of Blue Treatment upon support for candidate.\n Uncertainty reflected by predicted posterior draws at the 95% level with HDI's."
+    caption = "Data source: Pre-test.\n Conditional Marginal Effects of Blue Treatment upon support for candidate.\n Interpreted as the logged-odds of voting for fictional candidate\n conditional on varying levels of Party Identification.\n Uncertainty reflected by predicted posterior draws at the 95% level with HDI's."
 )
@@
 The ability of individuals to associate partisanship with the treatments is likely overstated.
-The sample is also quite unrepresentative, so the inference is indeed threatened.
 As I discussed with the third model, I also have omitted variable bias as the result of my outcome is a better measure of approach behaviors for those who are extroverted.
@@
 
-[^color_influence_pre-reg_anon-3]: I pay subjects a rate of \$12.00 per hour.
-On top of the price per participant, Prolific charges a 30% servicing fee and an additional fee to guarantee a nationally representative sample.
+[^color_influence_pre-reg_anon-3]: I pay subjects a rate of \$12.00 per hour. On top of the price per participant, Prolific charges a 30% servicing fee.
 
@@
 As some individuals may possess undiagnosed colorblindness, asking about their sex assists in covariate balance.
-I additionally include four open-ended questions asking participants to describe (1) their "first memory of a political event," (2) "what occurred in the most recent political event" they encountered, (3) how they "keep up-to-date with current political events," and (4) "what occurred in the most recent non-political event" they encountered.
-The use of multiple open-ended questions helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [see @kennedy_et-al_2021_poq].
+I additionally include an open-ended question asking participants to describe their "first memory of a political event." The use of an open-ended question helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [see @kennedy_et-al_2021_poq].
 Given estimates using these exclusion criteria, I would expect that upwards of 40% of my original sample will fail these attention checks [@kennedy_et-al_2021_poq]; thus, the large sample size.
@@
 In the first trial of the experiment, participants I randomly presented participants with two of three possible yard signs, one at a time.
-These yard signs are simple with the text "Vote for Riley" and a solid background color of either "Republican Red," "Democratic Blue," or White.[^color_influence_pre-reg_anon-6] There is an added component to this, however.
+These yard signs are simple with the text "Riley Ready to Lead" and a solid background color of either "Republican Red," "Democratic Blue," or White.[^color_influence_pre-reg_anon-6] There is an added component to this, however.
 
@@
 This will require participants to either switch browsers or to not participate in the study if they are using Safari at the time they are recruited by Prolific to participate in the study.
-As this requirement is enforced *before* joining the study, this should not have an effect on the number of excluded participants from my original sample nor on a nationally representative original sample.
+As this requirement is enforced *before* joining the study, this should not have an effect on the number of excluded participants from my original sample.
 
@@
 I examine differences in respondents' reported perceptions of the candidate's partisan affiliation.
-As respondents are making the choice between two yard signs, my estimand of interest is of a pairwise comparison of the two yard signs they see in each trial.
+As participants are asked this question for each treatment they view, the estimand of interest reflects the difference in perceptions of the candidate's partisan affiliation between the yard sign that they saw averaged across respondents.
+I estimate two ordered logistic regression where the main independent variables of interest are two indicator variables for whether respondents received the "red yard sign" or the "blue yard sign" in each round of Trial 1.
+The baseline category for both of those indicator variables is if they instead saw the "white yard sign".
+
+As the consistency by which the parties have used either the color red or blue has increased since the 2000's, I suspect that the age of my subjects may moderate this relationship.
+That is, the tendency for subjects to label red yard signs as a Republican candidate versus a different color may be stronger for those who are younger as the consistency in branding is the political environment they have been around more.
+I expect this particular relationship may be weaker for older subjects as they may place current branding strategies in a larger political context where this was not always the case.
+
+<!-- As respondents are making the choice between two yard signs, my estimand of interest is of a pairwise comparison of the two yard signs they see in each trial.
 While these are most common in ranking athletic teams, there is recent academic interest in these estimands as they allow researchers to examine the "popularity" of a particular treatment when experimental participants are asked to choose between two options [see @hopkins_noel_2022_ajps].
@@
 Unlike Elo Scores, a popular alternative, Bradley-Terry scores do not require every pairwise matchup to determine a winner.
-
+-->
 ## Do these perceptions require consistency between information types?
@@
 
-I take the same analytical strategy to address this question as I did before.
-I estimate the Bradley-Terry scores among respondents.
 I should expect that the trials that use less "consistent" visual information demonstrate more ambivalence among respondents in their reported perceptions of the politician's positions.
 Specifically, I expect that participants will perceive the yard signs that have both red and blue on them as more moderate and that the higher proportion of the color red or blue among the two colors will lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic.
+This is not to say that I expect the results to change significantly, but rather that the certainty by which I can predict individuals' guesses of the candidate's partisan affiliation to be weaker.
 
@@
 
-The @sec-pre-test provides a lot of useful information that I might use to construct my expectations for what I'll discover in @sec-study-1.
-Rather than evaluating my design choices based on expected long-run tendencies, I explicitly use the results from @sec-pre-test and adjust that information with assumptions about differences between @sec-pre-test and @sec-study-1's design to construct expectations that directly feed into my analytical choices.
-That is, rather than evaluating my design in the Frequentist framework, I rely on results from the @sec-pre-test to help with constructing my priors that I will use in a Bayesian model specification.
+The [Pre-test](#pre-test-sec-pre-test) provides a lot of useful information that I might use to construct my expectations for what I'll discover in [Study 1](#study-1-sec-study-1).
+Rather than evaluating my design choices based on expected long-run tendencies, I explicitly use the results from the [Pre-test](#pre-test-sec-pre-test) and adjust that information with assumptions about differences between the [Pre-test](#pre-test-sec-pre-test) and [Study 1's](#study-1-sec-study-1) design to construct expectations that directly feed into my analytical choices.
+That is, rather than evaluating my design in the Frequentist framework, I rely on results from the [Pre-test](#pre-test-sec-pre-test) to help with constructing my priors that I will use in a Bayesian model specification.
 Bayesian models often face criticism for the seemingly subjectivity introduced into a model specification by including one's priors into the calculation of one's estimates.
 While there has been a lot of ink spilt debating the validity of this claim, a Bayesian model specification seems particularly useful in the context of pre-registering a study.
-@sec-pre-test provides results which give me a benchmark by which I might refine my expectations about the effect of color on people's perceptions about politics; it gives me a concrete $\beta$ coefficient.
+The [Pre-test](#pre-test-sec-pre-test) provides results which give me a benchmark by which I might refine my expectations about the effect of color on people's perceptions about politics; it gives me a concrete $\beta$ coefficient.
 I can then use this information to construct my priors for my model.
-As I admit to a number of problems with my @sec-pre-test, my priors will reflect my uncertainty about whether those particular estimates should hold in @sec-study-1 and allows me to define an interval of effect sizes as opposed to a point estimate.
-These priors are updated by my likelihood distribution that is constructed by the data I collect in @sec-study-1.
+As I admit to a number of problems with my [Pre-test](#pre-test-sec-pre-test), my priors will reflect my uncertainty about whether those particular estimates should hold in [Study 1](#study-1-sec-study-1) and allows me to define an interval of effect sizes as opposed to a point estimate.
+These priors are updated by my likelihood function that is constructed by the data I collect in [Study 1](#study-1-sec-study-1).
 What this implies is that the more data I have, even if my priors are incorrect, I will converge upon the effect in the population [@johnson_et-al_2021_crc].
 However, since my priors require uncertainty, the weight of my priors on my eventual estimate are weaker the more uncertainty I specify.
-The lessons this provides for a pre-registered report suggests that I can use the results from my @sec-pre-test to inform choices for @sec-study-1, but that, though I use that information to inform my choices for the pre-registered report, I explicitly define how I expect that the results for @sec-study-1 are different than those in @sec-pre-test and that the data for @sec-study-1 directly update my expectations set by @sec-pre-test.
+The lessons this provides for a pre-registered report suggests that I can use the results from my [Pre-test](#pre-test-sec-pre-test) to inform choices for [Study 1](#study-1-sec-study-1), but that, though I use that information to inform my choices for the pre-registered report, I explicitly define how I expect that the results for [Study 1](#study-1-sec-study-1) are different than those in [Pre-test](#pre-test-sec-pre-test) and that the data for [Study 1](#study-1-sec-study-1) directly update my expectations set by [Pre-test](#pre-test-sec-pre-test).
 
@@
 
-Using the `fabricatr` [@fabricatr] package, I simulate a population with an N of 1,00,000.
+Using the `fabricatr` [@fabricatr] package, I simulate a population with an N of 1,000,000.
 The specified data generating processes for each of the variables are included in @lst-sim-dgp and @lst-sim-dgp-2.
@@
 Some estimate that insincere responses account for about 40% of a researcher's original sample [@kennedy_et-al_2021_poq].
-Therefore the total sample that I recruit from prolific should be about 40% larger than the total sample size used in these simulations.
+However, it is important to note that this is a quite conservative estimate of the proportion of insincere responses as this estimate comes from platforms that are notorious for poor convenience samples such as MTURK.
 
@@
 
-These priors suggest that I believe 68% of my beta coefficients, given the data, should be between -1 and 1; with the median of the estimates at 0.
+These priors suggest that I believe 68% of my beta coefficients on a logged-odds scale, given the data, should be between -1 and 1; with the median of the estimates at 0.
+This is quite a conservative estimate given the results from my pre-test.
+This is also a quite conservative estimate given that the primary %\beta$ coefficients of interest are both at 0.1 on the logged-odds scale.
 
@@
 This gives me a percentage of the time that I would come to the correct conclusion that there is a non-zero effect on that parameter.
-@tbl-true-positive-rates documents these calculations for each sample size.
+@fig-true-positive-rate documents these calculations for each sample size.
 
@@
 
-Sample200Results <- readRDS(file ="../../data/prr/sample200SimResults.RDS")
-Sample400Results <- readRDS(file ="../../data/prr/sample400SimResults.RDS")
-Sample600Results <- readRDS(file ="../../data/prr/sample600SimResults.RDS")
-Sample800Results <- readRDS(file ="../../data/prr/sample800SimResults.RDS")
+if (params$replicate == TRUE) {
+  # Define model arguments
+  formula <- brmsformula(
+    PartyGuess ~ RedTreatment + BlueTreatment + age +
+    RedTreatment:age + BlueTreatment:age +
+    Attention + Knowledge
+  )
+  compiled <- stan_model(
+    "./STAN/vote_guess_simulated_model.stan"
+    ,model_name="partyGuess"
+  )
+  family <- cumulative(link="logit")
+  priors <- prior(
+    stats::Normal(0,1)
+    ,class=b
+  )
+    # Run model
+  modelDiscrepancies <- sim_all(
+    n=c(200,400,600,800)
+    ,num_samples=500
+    ,formula=formula
+    ,compiled=compiled
+    ,family=family
+    ,priors=priors
+    ,model="partyGuess"
+  )
+    # store model
+  save(
+      modelDiscrepancies
+      ,file="../../data/models/prr/sim/sim.RDS"
+  )
+} else {
+  load(
+    file="../../data/models/prr/sim/sim.RDS"
+  )
+}
 ```
 
-+-------------+-----------------------------------------------------------------------------+
-| Sample size | True positive rate                                                          |
-+=============+=============================================================================+
-| n = 200     | -   Red treatment: `r sprintf('%.3f', Sample200Results[,1])`                
-|             |                                                                             
-|             | -   Blue treatment: `r sprintf('%.3f', Sample200Results[,2])`               
-|             |                                                                             
-|             | -   Age: `r sprintf('%.3f', Sample200Results[,3])`                          
-|             |                                                                             
-|             | -   Red treatment $\times$ Age: `r sprintf('%.3f', Sample200Results[,4])`   
-|             |                                                                             
-|             | -   Blue treatment $\times$ Age: `r sprintf('%.3f', Sample200Results[,5])`  
-|             |                                                                             
-|             | -   Attention: `r sprintf('%.3f', Sample200Results[,6])`                    
-|             |                                                                             
-|             | -   Knowledge: `r sprintf('%.3f', Sample200Results[,7])`                    
-+-------------+-----------------------------------------------------------------------------+
-| n = 400     | -   Red treatment: `r sprintf('%.3f', Sample400Results[,1])`                
-|             |                                                                             
-|             | -   Blue treatment: `r sprintf('%.3f', Sample400Results[,2])`               
-|             |                                                                             
-|             | -   Age: `r sprintf('%.3f', Sample400Results[,3])`                          
-|             |                                                                             
-|             | -   Red treatment $\times$ Age: `r sprintf('%.3f', Sample400Results[,4])`   
-|             |                                                                             
-|             | -   Blue treatment $\times$ Age: `r sprintf('%.3f', Sample400Results[,5])`  
-|             |                                                                             
-|             | -   Attention: `r sprintf('%.3f', Sample400Results[,6])`                    
-|             |                                                                             
-|             | -   Knowledge: `r sprintf('%.3f', Sample400Results[,7])`                    
-+-------------+-----------------------------------------------------------------------------+
-| n = 600     | -   Red treatment: `r sprintf('%.3f', Sample600Results[,1])`                
-|             |                                                                             
-|             | -   Blue treatment: `r sprintf('%.3f', Sample600Results[,2])`               
-|             |                                                                             
-|             | -   Age: `r sprintf('%.3f', Sample600Results[,3])`                          
-|             |                                                                             
-|             | -   Red treatment $\times$ Age: `r sprintf('%.3f', Sample600Results[,4])`   
-|             |                                                                             
-|             | -   Blue treatment $\times$ Age: `r sprintf('%.3f', Sample600Results[,5])`  
-|             |                                                                             
-|             | -   Attention: `r sprintf('%.3f', Sample600Results[,6])`                    
-|             |                                                                             
-|             | -   Knowledge: `r sprintf('%.3f', Sample600Results[,7])`                    
-+-------------+-----------------------------------------------------------------------------+
-| n = 800     | -   Red treatment: `r sprintf('%.3f', Sample800Results[,1])`                
-|             |                                                                             
-|             | -   Blue treatment: `r sprintf('%.3f', Sample800Results[,2])`               
-|             |                                                                             
-|             | -   Age: `r sprintf('%.3f', Sample800Results[,3])`                          
-|             |                                                                             
-|             | -   Red treatment $\times$ Age: `r sprintf('%.3f', Sample800Results[,4])`   
-|             |                                                                             
-|             | -   Blue treatment $\times$ Age: `r sprintf('%.3f', Sample800Results[,5])`  
-|             |                                                                             
-|             | -   Attention: `r sprintf('%.3f', Sample800Results[,6])`                    
-|             |                                                                             
-|             | -   Knowledge: `r sprintf('%.3f', Sample800Results[,7])`                    
-+-------------+-----------------------------------------------------------------------------+
+```{r}
+#| label: fig-true-positive-rate
+#| layout-nrow: 4
+#| fig-width: 6
+#| fig-cap: True positive rate
+#| fig-subcap: 
+#|  - "Red treatment"
+#|  - "Blue treatment"
+#|  - "Age"
+#|  - "Red treatment x Age"
+#|  - "Blue treatment x Age"
+#|  - "Attention"
+#|  - "Knowledge"
+cleanNames <- c(
+  "Sample size"
+  ,"Red treatment"
+  ,"Blue treatment"
+  ,"Age"
+  ,"Red treatment x Age"
+  ,"Blue treatment x Age"
+  ,"Attention"
+  ,"Knowledge"
+)
+truePositiveDF <- discrepancy_df(
+  list=modelDiscrepancies
+  ,new_names=cleanNames
+)
+plotList <- lapply(
+  cleanNames
+  ,true_positive_hist
+  ,df=truePositiveDF
+)
+plotList[[2]]
+plotList[[3]]
+plotList[[4]]
+plotList[[5]]
+plotList[[6]]
+plotList[[7]]
+plotList[[8]]
+```
 
-: True positive rate {#tbl-true-positive-rates}
-
-The results of my simulation suggest that I should aim for a sample of 600 respondents once I have excluded those that do not meet the inclusion criteria (i.e., fail attention checks, duplicated IP addresses and provide insincere responses to the open-ended prompts).
-Given estimates of poor responses for about 40% of some samples [@kennedy_et-al_2021_poq], I should aim to recruit a total of 1500 participants for Study 1.
+Given that my estimates of insincere responses, of effect size, and that these simulations use models examining my moderating hypothesis, the rates of true positives are likely quite conservative.
+The results of my simulation suggest that I should aim for a sample size greater than 400 once I've excluded insincere responses.
+Combining this with funding considerations, I will recruit total sample size of 1000 participants for Study 1.
 
@@
 #path.append("../")
-from helper import colorDetector
+from PY.helper import colorDetector
 
@@
 # Load gop image to read
-img = imread("../../data/study_2/gop_2022.png")
+img = imread("../../assets/img/gop_2022.png")
 
@@
 
-transformed= imwrite("../../data/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
+transformed= imwrite("../../assets/img/gop_2022_transformed.png", img_transformed) # save transformed image
 
-masked= imwrite("../../data/study_2/gop_2022_detected.png", result) # save masked image
+masked= imwrite("../../assets/img/gop_2022_detected.png", result) # save masked image
 ```
@@
 ::: {#fig-color-detection-example layout-ncol="2"}
-![Resized original image](../../data/study_2/gop_2022_transformed.png){#fig-resized}
+![Resized original image](../../assets/img/gop_2022_transformed.png){#fig-resized}
 
-![Masked](../../data/study_2/gop_2022_detected.png){#fig-masked}
+![Masked](../../assets/img/gop_2022_detected.png){#fig-masked}
 

### 2023-06-19 chapter_3/src/prr/dcr_color_and_deliberation_prr.qmd
I hate submodules

---
title: |
  How does visual information influence social interactions?
code-repo: |
  For replication, go to: <https://github.com/DamonCharlesRoberts/visual_information_and_political_participation>.
author:
  - name: Damon C. Roberts
    email: damon.roberts-1@colorado.edu
    orcid: 0000-0002-4360-3675
    title: PhD Candidate
    affiliations:
      - id: CU
        name: University of Colorado Boulder
        department: Political Science
        address: 333 UCB
        city: Boulder
        region: CO 
        postal-code: 80309-0333
abstract: |
  If colors have associations with partisan groups, do they shape our willingness to converse with others? This chapter argues that colors are not only relevant to politics and act as a reliable heuristic for people to determine the partisanship of another person, but it additionally makes the argument that this has downstream consequences for our attitudes and behaviors. The existing literature on political deliberation is currently grappling with the capacity of conversations to persuade others about politics. There is mixed evidence suggesting that it can get people to change their minds under the right conditions.  However, these "right" conditions are often challenging to develop organically. This chapter presents a theory that I refer to as the snap-judgment model of political visual information processing that explains one potential source of this limitation. Here, I present a pre-registered report that elaborates on this literature, how the theory helps with this puzzle, and presents two research designs test my claims. I conclude the pre-registered report with a simulation exploring the sensitivity of conclusions I can draw from such a research design and resulting modeling strategies.

bibliography: "../../../assets/references.bib"
format:
  hikmah-pdf:
    # Spit out in drafts directory
    latex-output-dir: "../../out/prr"
    # Use biblatex-chicago
    biblatex-chicago: true
    biblio-style: authordate
    biblatexoptions: 
      - backend=biber
      - autolang=hyphen
      - isbn=false
      - uniquename=false
    geometry:
      - top=1in
      - bottom=1in
      - left=1in
      - right=1in
      - heightrounded
    linestretch: 2
    fontsize: 12pt
nocite: |
  @quarto
execute:
  echo: false
  warning: false
  message: false
  cache: false
params:
  replicate: false
---
{{< pagebreak >}}

# Introduction

The project argues that colors are essential to politics. It argues that, as a pre-conscious form of information, they have downstream consequences on our attitude, expression, and behavior. This chapter addresses the question, "Well do they influence our attitude expression, and do they influence our behavior?" Demonstrating that people recognize color in politics is not sufficient to say that they matter in politics.

There is an expansive landscape that captures both formal and informal forms of political behaviors and a vast net to cast when trying to capture attitudes. To not turn this chapter into an impossibly long read, I will focus on what attitudes and behaviors I explore.

Conversations about politics are an essential part of participatory democracy [@huckfeldt_2007_ohpb]. They encourage many different forms of more formal political engagement [@verba_et-al_1995_hup;@klofstad_2007_prq;@eveland_hively_2009_joc;@matthes_et-al_2019_pc], and are a helpful resource that people can tap into for information about candidates and current events [@mcclurg_2003_prq;@eveland_hively_2009_joc], is argued to be capable of buffering animosity towards those in "the other party" [@levendusky_stecula_2021_cup], and even a source of persuasion [@beck_et-al_2002;@sokhey_stapleton_2020_ohep].

Though having conversations are important for the Aristotlean conception of a democratic citizen, some evidence suggests that we are relatively reluctant to have conversations where there is disagreement [@mutz_2006_cup;@carlson_settle_2022_cup]. Though we often experience emotions associated with discomfort when about to talk politics, there is significant support for the idea that these conversations are still helpful as a source of information [see @shapiro_et-al_2020_oh] and as a source of meaningful persuasion [@levendusky_stecula_2021_cup;see @sokhey_stapleton_2020_ohep].

As others have demonstrated that there are more considerations than just partisan congruency deterimining whether you engage in a conversation before it starts [@wolak_sokhey_2022_apr], color can be one example. Fitting with my larger argument, color activates particular pathways in one's cognitive schema, which activate positive or negative feelings (a valanced affective state), which can drive behavior and result in information processing for attitude expression and encoding. Specifically, I explore whether the color of someone's clothes can affect the propensity by which someone is willing to have a conversation with them and whether these evaluations can be changed.

This argument has several implications for the current ways we think about politics. First, we should consider how *all* forms of information influence attitude expression and the motivations guiding politically-relevant behaviors. Second, as I hope it will become apparent, my argument in this chapter provides an example of how conversations about politics can persuade people and how they are limited in doing so.

Before I elaborate on how this process occurs and on my expectations, I first want to elaborate on some fundamentals of the social neuroscience and social psychology literature that I am borrowing concepts from to build my model and, therefore, the expectations I derive from it.

# The cognitive architecture of attitudes

Neuroscientists and psychologists often conceptualize attitudes as an evaluation some external object [@fazio_2007_sc]. While this is a much more broad conceptualization than the one we often have when we think of political attitudes [see @zaller_1992_cup;@zaller_feldman_1992_ajps], at their core attitudes about politics are much the same -- they are some positive or negative reaction to taxes; to let a woman choose what is best for her physical health, to make it harder for someone to buy a gun. Conceptualizing attitudes as an object-evaluation simplifies, but, more important, it aids in helping us get a sense of how they work.

The first foundation I rely upon is that our brain operates through a vast and complex network of connected bits of information. Despite popular scientific interpretations of it, the brain is not a compartmentalized file system of memories [@ralph_anderson_2018_pup] -- what I will use as a short-hand to refer to pre-existing information that we have stored in our brain and access to evaluate new information. Instead, our brain is a series of interconnected information. Some connections are stronger than others. Several things determine the strength of these connections [@kahana_et-al_2022_ohhum]; however, we encode sensory information with strong ties to affective responses [see @winkielman_et-al_2011_ohsn].

The second foundation I rely upon is making a conceptual distinction between emotion and affect to explain the connection between them and attitudes. Emotion is an incredibly complex concept and has been a critical debate in the affective neuroscience literature since the $18^th$ century, with Hume, Smith, and later taken up by Darwin. Modern conceptualizations of emotion by affective neuroscientists see it as a set of distinct and conscious classifications meant to describe one's appraisal of their reaction to some object. On the other hand, experts in this field conceptualize affect as a more simplistic, but pre-conscious, valanced appraisal of an object. That is, experts in this field conceptualize affect as you feeling positive or negative toward something. This appraisal happens quickly and is often considered unconscious [@sander_2013_chhan;@ralph_anderson_2018_pup]. When exposed to new information, we often have a physiological reaction and a valanced appraisal of it [@dror_2017_er]. This is where attitudes and affective responses to information collide. To evaluate some new information to form an attitude about it, we often rely on valanced appraisals of it [@fazio_2007_sc]. As a result, this information is central to our encoding of this information when forming a memory [@cunningham_et-al_2012_ohsn].

The third foundation I rely upon is that we can rely on sensory receptors to collect information and to use it to form an attitude toward an object while also using that information when encoding it. Visual information, in particular, is a decisive biological advantage for survival. For example, pokeberries look a lot like grapes. However, they grow on a red stem instead of a green one. If we eat too many pokeberries, it can cause significant digestive problems for us. Being able to rely on vision and remember that visual information is quite valuable. Not only does vision aid in helping us remember what visual characteristics of some plant made us sick and which one did not, but we also store visual information from social interactions. Visual forms of information are among the fastest to be processed [see @ames_et-al_2012_ohsn].

The fourth foundation, which is related to the third: information about social hierarchies, is part of our cognitive schemas. As social psychologists have spent more than the past five decades laying out a case for the importance of social groups on how we see our world [see @tajfel_turner_1979_ejsp], social neuroscientists have also been opening up the drywall to explore how we keep that information straight in our heads. Another central characteristic of the strength characterizing a connection in our head is how it fits with relevant social groups [@zink_barter_2012_ohsn]. This explains how social groups lend themselves to such *strong* affective responses to threats [@zahn_et-al_2011_ohsn;@huddy_2001_pp].

To tie things together, the fifth foundation is to conceptualize these connections as multi-dimensional. An encoded memory depends on more than just the valanced, sensory, and social group information connected to it. These components can extend beyond a memory to connect memories of positive things, red objects, and Liverpool F.C. fans. The relevance by which a particular memory matters to evaluate an object depends on more than just these similarities but on factors like the recency by which we engage with the information [@kahana_et-al_2022_ohhum;@zaller_feldman_1992_ajps].

These five foundations are glossing over complex debates in various subfields of neuroscience and psychology. However, they are helpful starting points for political scientists to borrow from to engage in interdisciplinary conceptualizations of related and common theories we use in political psychology and behavior. These five foundations paint a brain that acts as an interconnected structure. This structure relies on different pieces, each with its purpose. Each piece of information, however, connects a memory to other memories. Relying upon these structures allows us to access existing information and evaluate new information quickly. We can take relevant features of our existing memories and use those to construct a valanced reaction to the information coming in. Though this complicates our ability to construct a genealogy of an attitude's associated memories [@kahana_et-al_2022_ohhum], it enables us to have a coherent imagining of how the brain functions and its tendencies.

# The cognitive architecture and color in politics

You are out and about running errands on a Sunday morning. While doing so, you see someone wearing a red hat. They are approaching us. Now, all you have seen so far is that they have a red hat and look like they want to start a conversation with you. There are a couple of things that are occurring inside of our heads based on our cognitive architecture. The first is that the hat is red. Nevertheless, you have seen *lots* of red things. You need to narrow this down.

You know that a political event is happening down the street later today, and you know that it involves the Republican party. Suddenly, you know pretty quickly that this person is a Republican. You have one of two feelings: "cool" or "shoot" (perhaps with more colorful language). How did you make this leap?

You captured some visual information, identified it, and went through your index of red things. However, knowing that it could very well be related to politics, you went through your index of red things in politics. You connected that the Republican party uses a lot of the color red, particularly more recently [see @elving_2014_npr]. You have strong affective reactions to the Republican party. Not because the Republican party is an organism that is a predator of humans, but because you know that you are either opposed to them as a group of people or you like them because you are also Republican. This is how many political scientists conceptualize our valanced responses to the political parties [@iyengar_westwood_2015_ajps;@mason_2018_cup].

Now say that instead of a political rally down the street, it was a basketball game, and the Miami Heat are playing. Instead of assuming they were a Republican, you may assume they are a Miami Heat fan. Instead of thinking, "They are a Republican; I want to talk to them because I like Republicans," you may now think, "They are a Miami Heat fan; I want to talk to them because I like the Miami Heat!"

This process communicates some important features of how color may be relevant in shaping one's tendency to engage in a conversation about politics. The first is that the saliency of that color in politics and whether politics is relevant in the first place is an important feature. Second, it argues that we can connect information as simple as color, connect it to a social group and then have our feelings toward that social group come to the forefront of our thought process. Beyond politics, evidence suggests that color can be a strong visual cue to identify social group membership [@pietraszewski_et-al_2015_c]. In politics, the colors red and blue have been used consistently since the 2000 election on electoral maps [@elving_2014_npr], and as previous work has demonstrated, including the previous chapter, the connection between Republicans with the color red and Democrats with the color blue. Specifically red with the republican party and blue with the Democratic party [see @williams_et-al_2022_jomp].

Once you have had this reaction, you are motivated to avoid or participate in this conversation. This is because we tend to avoid things we evaluate as unfavorable or to approach them [@valentino_et-al_2011_jop]. Many take evidence of intense affective polarization among the public on the grounds of partisanship as an intractable societal issue due to these features. When we fall into this track of negative or positive thinking and are now motivated to engage with new information in a particular way, depending on whether we are motivated to engage or disengage with the information, many reasonably assume that we cannot learn anything new. We either support our pre-existing beliefs, or shut down and limit exposure to countervailing information [@taber_lodge_2006_ajps]. Partisanship is a social group [@mason_2018_cup] that motivates this behavior for many people [@lodge_taber_2013_cup]. While some hope that other social groups may provide cross-cutting forces to reduce these impacts, some evidence suggests that partisan identification has become the central politically-relevant social group that guides the rest of them [@mason_2018_cup].

In the context of conversing about politics, many have taken these features as a condemnation of conversations about politics. As we seek to avoid disagreeable conversations, particularly with those we are close to [@mutz_2006_cup], evidence of increasing homogeneity in our networks, in terms of partisan identification [@butters_hare_2022_pb], may make it easy to assume that we are always going to avoid conversations with those we disagree with and that we do not change our minds on that.

There are some reasons why we may push back on such a pessimistic perspective, however. From the cognitive architecture standpoint, these tracks are not bowling alleys where you can only go down one way and cannot change course. Classic theories on motivated reasoning suggest that we are biased to seek information that fits with our prior beliefs but also seek out accuracy motivations [@kunda_1990_pb]. Evidence in political science suggests that exposure to a lot of new information that runs counter to our preferred pre-existing beliefs can persuade us [@redlawsk_et-al_2010_pp]. We can also persuade people under the right emotional conditions [@albertson_et-al_2020_ohep]. However, a handful of studies may mean something other than this is occurring. So, a recent Herculean effort to perform a meta-analysis on existing experiments on persuasion and attitude change in political science demonstrates that persuasion is possible and that these effects are not some coincidence; in fact, they seem to be about the same strength across several contexts [@coppock_2022_ucp]. One such context is motivating people to collect accurate information [@bayes_et-al_2020_pp]. Coincidentally, conversations about politics are often motivated by a desire to collect information [@beck_et-al_2002;@huckfeldt_2007_ohpb; see also @gastil_et-al_2002_jop;@shapiro_et-al_2020_oh].

Further evidence suggests that the deleterious effects on democratic behavior of political conversation often occur in the context where someone is in the political minority beyond just that conversation as well [@mcclurg_2006_pb]. While we are not particularly motivated to seek out conversations with those we disagree with, it does not necessarily mean that it leads to this motivated backlash where political conversations only act as echo-chambers. This seems especially true given that we can only sometimes pick when and where we have conversations about politics.

So where does this leave us? Coming to some conclusion about someone based on the color their clothing does not necessarily mean that we are not willing to have a conversation with them if new information comes about. It also does not mean that the content of the conversation cannot impact us. As many scholars who push back against the claims that persuasion can occur readily admit, there are limitations to new information's effects. I am no different in that regard. From the perspective of the fundamentals of cognitive architecture, new information can put us on branching paths in the network, but it does not necessarily reverse course. The memories we accessed initially are a select set of memories and have limited connections. We are not forgetting all that information and starting from a naive position. We are accessing memories that are associated with those memories we initially accessed. This means we can adjust our evaluation of the object but do not necessarily forget where we have been. From the perspective of existing in political science, which aligns with my more interdisciplinary perspective, we still have strong motivations to protect our pre-existing beliefs and do not necessarily "weigh" or equally consider this new information relative to each other [@zaller_1992_cup]. The benefits of this new information often have a timestamp on it. The persuasive benefits of this new information are not necessarily gone after a predetermined amount of time, but it has diminishing returns. A meta-analysis reveals that after about ten days, the positive effects of new information on persuasion are about one-third the size it was initially [@coppock_2022_ucp]. This fits with evidence suggesting that evaluations often rely upon relatively recently encoded attitudes [@kahana_et-al_2022_ohhum].^[See also @zaller_1992_cup for the political science perspective.] If the new information fits with pre-existing beliefs, we continue down the same path. It perhaps gets even more robust because we now have more information to tap into that fits with our prior beliefs. @fig-theory provides a visual representation of this process.

{{< include ../../../assets/_theory.qmd >}}

+--------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Hypotheses   | Expectation                                                                                                                                                                                                                                                               |
+==============+:=========================================================================================================================================================================================================================================================================:+
| $H_1$        | People notice the color of clothing a potential conversation partner is wearing.                                                                                                                                                                                          |
+--------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_2$        | When primed to think about politics, people are less likely to want to have a conversation with someone wearing a blue shirt if they are a Republican and a red shirt if they are a Democrat.                                                                             |
+--------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_3$        | When learning more information about someone that fits with our initial impression, our motivation of engagement or disengagement is stronger than if the information were incongruent with our initial impressions.                                                      |
+--------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| $H_4$        | When learning more information about someone that does not fit with our initial impression, the new information can shift our motivations to have the conversation or to disengage. However, this difference is smaller than if both forms of information were congruent. |
+--------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

: Summary of hypotheses {#tbl-hypotheses}

<!--
  NOTE: ADD SOMETHING ABOUT ASYMMETRIC POLARIZATION
-->

# Study 1 {#sec-study-1}

## Study design

[Study 1](#study-1) seeks to address $H_1$ and $H_2$. In [Study 1](#study-1), I recruit participants from ***[YouGov/Qualtrics/Whatever online panels are in vogue that week]***. First, I ask participants several questions about their demographic background (i.e., age, gender identity, education, and income). I additionally present them with a battery to measure conflict avoidance as potential confounds.

After getting some background information on my participants, I randomly split the sample into two conditions. The first condition is a "political prime" condition, and the second is a "no political prime" condition. For the participants in the political prime condition, I ask them several questions about their political attitudes. This includes questions about their partisan identification and their attention to politics. While I do not make a significant effort to prime politics, I design these questions to make politics salient for them. Those assigned to the second condition, no political prime, participants are asked these questions after the primary treatment, but not before. I designed this to test the scope conditions of the relevance of clothing color in conversation when politics is not salient. The additional benefit is that it counterbalances the party identification variable, so I am not systematically introducing priming and post-treatment bias.

In the primary treatment of the study, I randomly assign participants to one of two conditions. In both conditions, participants are instructed, "You will have a conversation with this person." In these instructions, I do not state this is will be a "political conversation" or a "conversation about politics." I see these instructions as substantively different from the latter phrasings prime politics. The goal is that the priming (or no priming) done before this treatment will be what is making politics salient or not.

Below those instructions, I show participants an image of a person with either a blue or a red shirt. The first hypothesis would suggest that there should be differences in how willing someone would be to have a conversation between the priming conditions. For those not primed with politics beforehand, we should expect that the color of the shirt should not matter and for there to not be any substantively different levels of willingness to have that conversation between the red shirt, blue shirt conditions; the color of the shirt is not particularly relevant information.

The second hypothesis would suggest that those given the political prime would be more willing to have a conversation with someone who is wearing the color affiliated with their partisanship (e.g., Democrats are more willing to have conversations with a discussion partner with a blue shirt than a red shirt) and less so with those who is not. Those in the non-political priming conditions, we should expect that there would be no real substantive difference between conditions as politics is not salient, and the color of the shirt should have no significant meaning to them.

## Modeling strategy

To address $H_1$, the outcome variable of interest is whether or not people notice the color of the shirt (0 or 1,) as explained by whether they received the political prime or not (0 or 1). I will fit a logistic regression to examine whether there are differences in the outcome depending on this prime.

To address $H_2$, the outcome variable of interest is a five-item Likert response to the statement, "I am willing to have a conversation with this person." Therefore, I elect to use an ordered logistic regression as my estimator. In terms of the particular model, there are some considerations I need to make.

In the context of my experiment, I hypothesize that the participants' responses are primarily explained by whether that person is wearing a red or blue shirt. This effect, however, is likely moderated by a couple of things. First, if $H_1$ holds, the polarity in outcome responses will be partly explained by whether politics is at the top of the mind. Second, I expect that the strength of the relationship of the shirt color and the priming will depend on the party identification of the study participant. More specifically, if they are Republican, I would expect that those with the political prime who see a red shirt will be much more favorable of conversing with the fictional discussion partner than those without the political prime and those who saw a fictional discussion partner with a blue shirt. I expect the opposite for self-identifying Democrats -- Democrats who receive the political prime will report being more willing to have a conversation with the discussion partner when the partner is wearing a blue shirt relative to Democrats who did not receive a prime *and* Democrats who saw a discussion partner with a red shirt.

The setup for the study is a 2x2x2 factorial design. Often the standard practice is to use a triple interaction. I believe that is reasonable enough. The triple interaction would allow me to test whether the partisan identification of the participant moderates the relationship between the shirt color and the prime. However, the interaction term would test whether Democrats and Republicans differ in how they respond to these conditions instead of testing what those differences are. What seems more appropriate to me is a test of whether Republicans primed with politics are more willing to talk to people wearing red shirts relative to those who do not recieve the political prime and those wearing blue shirts; as a second question to look at whether Democrats who receive the political prime are more willing to talk to people wearing Blue shirts more than those who do not receive the political prime and those wearing red shirts. I am not claiming whether strength of these relationships operates differently among Republicans and Democrats but rather that it is two separate questions. Therefore, I also consider a split sample approach whereby I split my sample into Democrats and Republicans and run a regression on each sub-sample. For each of these regressions, I include an interaction term to study the moderating effect of the prime on the effect that shirt color has on willingness to talk to them. Since party identification is not randomly assigned, I include potential confounders impact people's propensity to discuss politics and their party identification (i.e., age, gender, education, income, and conflict avoidance).

In the [Simulation section](#simulation) below, I provide further details discussing some practical considerations I must weigh in my decisions. In particular, both model choices to examine $H_2$ are rather complicated models. As my models will rely on the Bayesian implementation of regression, the inferences I can draw are dependent on the data from the sample, much more so as it does not rely on assumptions about long-run tendencies. Therefore, I want to examine my models' ability to converge on the correct answer given various sample sizes. In that section, I provide more details about the model, sample sizes, and prior distribution specifications.

# Study 2

## Study design

The setup for [Study 2](#study-2) is largely the same. Like in [Study 1](#study-1), I ask participants several questions about their demographic background and ask them about conflict avoidance. As well as [Study 1](#study-1), I initially split the sample randomly into two conditions: a political prime and a no political prime condition. The purpose of doing this is not necessarily to prime politics anymore. However, it is done more so for counterbalancing so that I am not systematically introducing post-treatment bias, nor am I strengthening the effects of the treatment through systematically priming politics. Like in [Study 1](#study-1), I instruct participants that they will be having a conversation with someone and will show them someone wearing either a red or a blue t-shirt.

[Study 2](#study-2) is different in that I now include that person's policy preferences below the image. Below the image is a "profile" for this person that describes their political positions by listing their party identification, whether they support universal basic income, abortion, and gun control. What varies in the four conditions is, first, whether the person is wearing a blue or a red shirt. The second dimension the conditions vary on is whether that profile of political attitudes matches the presumed partisanship affiliated with their shirt color. For example, a participant seeing a discussion partner with a red t-shirt that identifies as a Democrat, is supportive of universal basic income (UBI), is pro-choice and is supportive of gun control would be considered an incongruent condition as opposed to the same discussion partner with the red t-shirt that identifies as a Republican that is not supportive of UBI, is pro-life, and is not supportive of gun control.

I chose these particular policies for a number of reasons. The first reason being that these policies are hot-button issues. While some skeptics of my research design may be concerned with me activating strong valenced responses, I argue that these choices increase the external validity of my study in that it is realistic that most people have *some* opinion (support or do not support) on these issues. These are the things the Jane Q. Public may bring up in a conversation as opposed to something like local zoning laws. In addition to external validity, I argue that these are the sorts of policies my participants would have some opinion on. As these are polarized issues, these are the sorts of policy issues people are concerned about discussing with others. They are less concerned about talking politics when discussing something like a local zoning law that limits the number of unrelated people that can not live with each other (save for perhaps Boulder, Colorado).

After seeing this profile, I ask participants whether they are willing to have a conversation with this person. I still should expect $H_2$ to hold in that Democrats will be more willing to talk with those wearing blue shirts, and Republicans will be more willing to talk to those in red shirts. However, I should expect that the degree to which this occurs will be limited based on whether their stated partisan identification and policy preferences are congruent. I suspect those that have political attitudes that are incongruent with the respondents' will receive less support than those that have congruent policy attitudes. However, I suspect that those wearing shirts that are incongruent but with congruent policy preferences will be less popular as a potential discussion partner than one with both a congruent shirt and policy preferences. The snap-judgment model suggests that we are capable of overwriting our initial impressions. However, we are limited in our ability to do so.

## Modeling strategy

The design of this study is a 2x2 factorial design, as opposed to a 2x2x2 like [Study 1](#study-1). $H_3$ and $H_4$ are questions on different sides of the same coin. For [Study 2](#study-2), I seek to answer whether color does modifies people's perceptions of another person's politics by the color of their shirt. The study design makes the stated policy positions consistent and evident as to their stances. What varies in the design, and where I get my leverage to answer this question, is by varying both the shirt color and the congruency by which that shirt color, and assumed partisanship from it, fits with the stated policy positions of the fictional discussion partner.

As the outcome of interest is still the five-item Likert response to their willingness to engage in the conversation, I intend to fit two ordered logistic regressions. In terms of the model, I intend to include an interactive term. I seek to see whether the effect of shirt color on willingness to talk to someone is conditional on whether the color on that shirt is congruent with the familiar blue association with Democrats and red association with Republicans. Like my modeling strategy in [Study 1]{#study-1}, I am not necessarily interested in drawing inferences about the difference in the slopes between Democrats and Republicans on this conditional effect. Rather, I just want to identify what those slopes are for Republicans and Democrats. As I did with [Study 1](#study-1), I am still curious about what insights we may glean from a model that addresses that question, but it is not a primary motivation of this chapter. Therefore, I intend to relegate such a model to the chapter's appendix.

# Simulation {#sec-simulation}

The stated models above have theoretical motivations. Unfortunately for the social scientist, our theoretical motivations do not necessarily mean that our inferential ones also follow. The purpose of these simulations is not to convince myself or the reader that my stated modeling strategy is appropriate and "good" in some objective sense. Rather, its purpose is to give me a sense of the sensitivity of my ability to draw correct conclusions despite the reasonable amounts of uncertainty that quantitative work generates.

I intend to fit these models through the Bayesian regression framework. There are a number of benefits to Bayesian approaches to regression and hypothesis testing that scholars have debated for centuries. I am not going to hash out those debates here. However, from the perspective of pre-registering my expectations of a model, a Bayesian approach to regression seems particularly appropriate. The primary reason for this is that the Bayesian approach to regression requires that you report your prior beliefs about the explanatory effect of your predictor variables on an outcome. You incorporate these prior beliefs into your model as a distribution that indicates what you think is the most likely size of the effect and the probability of other less-likely effect sizes. This allows you to reflect uncertainty about the size of the effect but still makes explicit what you believe. You multiply your prior distribution with your likelihood distribution constructed with the data. This approach enables me to report my beliefs and my associated uncertainty about those effect sizes. They do not dictate the model, however. The more data you have, the less weight your prior beliefs have -- even ones that indicate you have little uncertainty about your beliefs. As the size of the data removes the "subjectivity" that many believe to be a problem introduced in Bayesian approaches to regression, one particularly important part of this pre-registered report is to demonstrate the sensitivity of my ability to draw inferences based on the size of my sample Additionally, some of my stated models are more complex than others. Therefore, the amount of information my model needs to be sure that my hypotheses are correct increases.

I first start by using the `fabricatr` package [@fabricatr] to simulate population data for both studies. I generate these simulated data from data generating processes that I define.^[I include the particulars of these data generating processes in the supplementary materials. I do not include them here because the primary goal of this exercise is to see whether or not I can draw correct inferences about reasonably similar data generating processes rather than on me defining these data generating processes as correct themselves.] I randomly draw from this population dataset at four different sample sizes: 200, 400, 600, and 800. For each of these sample sizes, I draw 100 samples. I do not perform these simulations for [Study 2](#study-2) as the design is largely the same, as well as the modeling strategies.

```{r}
#| label: setup
#setwd("./src/prr")
# modularly load packages
box::use(
  ./R/sample[
    study_simulator
  ]
  , ./R/model[
    fit_sims
  ]
  , ./R/plot[...]
  , data.table[...]
  , parallel[...]
  , brms[
    make_stancode
    , brmsformula
    , set_prior
    , bernoulli
    , cumulative
  ]
  , rstan[
    stan_model
  ]
)
# Set up cores
cores <- detectCores() - 1
# List sample size
list_sample_size <- c(200, 400, 600, 800)
# Number of samples
int_n_samples <- 1000
```

```{r}
#| label: simulate
if (params$replicate == TRUE) {
  # sample the data at different sample sizes
  list_simulated <- mclapply(
    list_sample_size
    , function(x) {
      df_sample <- study_simulator(
        study = 1
        , n = x
        , n_samples = int_n_samples
        , seed = 121022
      )
      # Return df_sample
      return(df_sample)
    }
    , mc.cores = cores
  )
  # store in a rdata file
  save(
    list_simulated
    , file = "../../data/temp/prr/simulated_samples.RData"
  )
} else {
  load(
    file = "../../data/temp/prr/simulated_samples.RData"
  )
}
```

On each of these samples, I fit the stated models using the `rstan` package [@rstan]. For all models, I define my prior distribution as a normal distribution with a mean of 0 and a standard deviation of 1. While this is not truly my prior beliefs of the effect sizes, I am using the prior distribution as an informed prior that states that I largely believe the effects to be zero, or at least to be very small. This acts as a quite conservative test of my models' ability to lead me to the correct inferences. Once fitted, I find the minimum and maximum value on the posterior distribution for each of my coefficients and identify whether that posterior distribution overlaps with zero. My hypotheses are directional in that I not only believe that the effect of my predictor terms should not be zero, but I also believe that these effects are either positive or negative.

I calculate a true positive rate by first ensuring that the minimum and maximum values of my posterior distribution for each $\hat{\beta_i}$ coefficient do not overlap with zero. If I would come to the wrong conclusion about my hypothesis by examining my posterior distribution, I record a value of 0; if it is correct, I code it as a 1. I then average over the 100 samples for each sample size. This gives me a true positive rate for each sample size for each $\hat{\beta_i}$ coefficient.

```{r}
#| label: make-stan-code
if (params$replicate == TRUE) {
  df_example <- list_simulated[[1]][
    sample == 1,
  ]
  df_example_split_rep <- df_example[
    party_id == "Strong Republican" | party_id == "Republican" | party_id == "Lean Republican"
  ]
  df_example_split_dem <- df_example[
    party_id == "Strong Democrat" | party_id == "Democrat" | party_id == "Lean Democrat"
  ]
  # Model 1: Predict whether they notice
  formula_study_1_model_1 <- brmsformula(
    notice ~ prime
  )
  prior_study_1_model_1 <- set_prior(
    "normal(0,1)"
    , class = "b"
  )
  stancode_study_1_model_1 <- make_stancode(
    formula = formula_study_1_model_1
    , data = df_example
    , family = bernoulli(link = "logit")
    , prior = prior_study_1_model_1
    , save_model = "./STAN/study_1_model_1.stan"
  )

  # Model 2: Predict willingness
    #* Full interaction
  formula_study_1_model_2 <- brmsformula(
    willing ~ blue_shirt + prime + party_id + blue_shirt * prime * party_id + gender + education + income + conflict + attention
  )
  prior_study_1_model_2 <- set_prior(
    "normal(0,1)"
    , class = "b"
  )
  stancode_study_1_model_2 <- make_stancode(
    formula = formula_study_1_model_2
    , data = df_example
    , family = cumulative(link = "logit")
    , prior = prior_study_1_model_2
    , save_model = "./STAN/study_1_model_2.stan"
  )
    #* Split sample
  formula_study_1_model_2_alt <- brmsformula(
    willing ~ blue_shirt + prime + blue_shirt * prime + gender + education + income + conflict + attention
  )
  prior_study_1_model_2_alt <- set_prior(
    "normal(0, 1)"
    , class = "b"
  )
  stancode_study_1_model_2_alt <- make_stancode(
    formula = formula_study_1_model_2_alt
    , data = df_example_split_rep
    , data2 = df_example_split_dem
    , family = cumulative(link = "logit")
    , prior = prior_study_1_model_2_alt
    , save_model = "./STAN/study_1_model_2_alt.stan"
  )
}
```

```{r}
#| label: fit-simulated-models
if (params$replicate == TRUE) {
  # Model 1
    #* Compile the stan model
  compiled_study_1_model_1 <- stan_model(
    file = "./STAN/study_1_model_1.stan"
    , model_name = "study_1_model_1"
  )
    #* Define model formula
  formula_study_1_model_1 <- brmsformula(
    notice ~ prime
  )
    #* Define the family
  family_study_1_model_1 <- bernoulli(link = "logit")
    #* Define priors
  prior_study_1_model_1 <- set_prior(
    "normal(0,1)"
    , class = "b"
  )
    #* Fit model at different sample sizes
  list_fitted_samples <- mclapply(
    list_simulated
    , function(x) {
      fit_sims(
        data_frame = x
        , compiled_stan_model = compiled_study_1_model_1
        , formula = formula_study_1_model_1
        , family = family_study_1_model_1
        , prior = prior_study_1_model_1
      )
    }
    , mc.cores = cores
  )
    #* collapse into a single data.table object
  names(list_fitted_samples) <- list_sample_size
  df_fitted_samples_model_1 <- rbindlist(
    list_fitted_samples
    , idcol = "sample_size"
  )[
    , sample_size := factor(sample_size)
  ]
  # Model 2
    #* Compile the stan model
  compiled_study_1_model_2 <- stan_model(
    file = "./STAN/study_1_model_2.stan"
    , model_name = "study_1_model_2"
  )
    #* Define model formula
  formula_study_1_model_2 <- brmsformula(
    willing ~ blue_shirt + prime + party_id + blue_shirt * prime * party_id + gender + education + income + conflict + attention
  )
    #* Define the family
  family_study_1_model_2 <- cumulative(link = "logit")
    #* Define priors
  prior_study_1_model_2 <- set_prior(
    "normal(0, 1)"
    , class = "b"
  )
    #* Fit model at different sample sizes
  list_fitted_samples_model_2 <- mclapply(
    list_simulated
    , function(x) {
      fit_sims(
        data_frame = x
        , compiled_stan_model = compiled_study_1_model_2,
        , parameters = c("b[1]", "b[2]", "b[3]", "b[4]")
        , formula = formula_study_1_model_2
        , priors = prior_study_1_model_2
        , family = family_study_1_model_2
      )
    }
    , mc.cores = cores
  )
    #* collapse into a single data.table object
  names(list_fitted_samples_model_2) <- list_sample_size
  df_fitted_samples_model_2 <- rbindlist(
    list_fitted_samples_model_2
    , idcol = "sample_size"
  )[
    , sample_size := factor(sample_size)
  ]
    #* alternative model
      #** compile model
  compiled_study_1_model_2_alt <- stan_model(
    file = "./STAN/study_1_model_2_alt.stan"
    , model_name = "study_1_model_2_alt"
  )
      #** formula
  formula_study_1_model_2_alt <- brmsformula(
    willing ~ blue_shirt + prime + blue_shirt * prime
  )
      #** clean data
  list_sim_rep_data <- lapply(
    list_simulated
    , function(x) {
      x[
        party_id == "Strong Republican" | party_id == "Republican" | party_id == "Lean Republican"
      ]
    }
  )
  list_sim_dem_data <- lapply(
    list_simulated
    , function(x) {
      x[
        party_id == "Strong Democrat" | party_id == "Democrat" | party_id == "Lean Democrat"
      ]
    }
  )
      #** fit model
  list_fitted_samples_model_2_alt <- mclapply(
    list_simulated
    , function(x) {
        fit_sims(
          data_frame = x
          , compiled_stan_model = compiled_study_1_model_2_alt
          , parameters = c("b[1]", "b[2]", "b[3]")
          , formula = formula_study_1_model_2_alt
          , priors = prior_study_1_model_2_alt
          , family = family_study_1_model_2
        )
    }
    , mc.cores = cores
  )
  names(list_fitted_samples_model_2_alt) <- list_sample_size
  df_fitted_samples_model_2_alt <- rbindlist(
    list_fitted_samples_model_2_alt
    , idcol= "sample_size"
  )

  # Save results
    #* study 1, model 1
  save(
    df_fitted_samples_model_1
    , file = "../../data/temp/prr/fitted_model_1.RData"
  )
    #* study 1, model 2
  save(
    df_fitted_samples_model_2
    , file = "../../data/temp/prr/fitted_model_2.RData"
  )
    #* study 1, model 2 alternate
  save(
    df_fitted_samples_model_2_alt
    , file = "../../data/temp/prr/fitted_model_2_alt.RData"
  )
} else {
  load(
    file = "../../data/temp/prr/fitted_model_1.RData"
  )
  load(
    file = "../../data/temp/prr/fitted_model_2.RData"
  )
  load(
    file = "../../data/temp/prr/fitted_model_2_alt.RData"
  )
}
```

The following histograms report the true positive rate for each $\hat{\beta_i}$ coefficient at different sample sizes for [Study 1](#study-1). Across models and across the two studies, I see that most models perform pretty well at any of the sample sizes. It is important to note that these sample sizes reflect the number of observations included in the models, not the total sample size. As many online convenience samples struggle with inattentive respondents, insincere responses, bots, etcetera [see @kennedy_et-al_2021_poq], I am going to be quite conservative and try to recruit at least 800 respondents for these two studies.

```{r}
#| label: fig-true-positive-study-1-model-1
#| fig-cap: True positive rate from simulations - Model 1
#| fig-width: 8
#| layout-nrow: 1
plot_study_1_model_1 <- true_positive_plot(data_frame = df_fitted_samples_model_1)
plot_study_1_model_1[[1]]

```

```{r}
#| label: fig-true-positive-study-1-model-2
#| fig-cap: True positive rate from simulations - Model 2
#| fig-width: 8
#| layout-nrow: 2
#| fig-subcap:
#|   - $\hat{\beta}_1$
#|   - $\hat{\beta}_2$
#|   - $\hat{\beta}_3$
#|   - $\hat{\beta}_4$
plot_study_1_model_2 <- true_positive_plot(data_frame = df_fitted_samples_model_2)
plot_study_1_model_2[[1]]
plot_study_1_model_2[[2]]
plot_study_1_model_2[[3]]
plot_study_1_model_2[[4]]
```

```{r}
#| label: fig-true-positive-study-1-model-2-alt
#| fig-cap: True positive rate from simulations - Model 2, Split sample
#| fig-width: 8
#| layout-nrow: 2
#| fig-subcap:
#|   - $\hat{\beta}_1$
#|   - $\hat{\beta}_2$
#|   - $\hat{\beta}_3$

plot_study_1_model_2_alt <- true_positive_plot(data_frame = df_fitted_samples_model_2_alt)
plot_study_1_model_2_alt[[1]]
plot_study_1_model_2_alt[[2]]
plot_study_1_model_2_alt[[3]]
```

# Discussion

Previous chapters provide (as of right now) preliminary evidence supporting my claim that color matters and convey group-based partisan information to average citizens. This chapter pushes the envelope in a few ways. First, this chapter seeks to move past the argument that "people notice color, and it is relevant in politics." Specifically, this chapter seeks to examine whether it has the capacity to shape attitudes and behavior by elaborating on the mechanisms by which it does so. Second, it examines the limitations or the scope conditions of this claim. It argues that this works so long as politics is salient. Third, this chapter argues that color does not simply act as an alternative form of political information influencing political attitudes and their resulting behaviors but that it shapes the way we consider more traditionally considered forms of political information, such as stated policy positions. Fourth, this chapter explores the way in which that color influences our tendencies to avoid conversations about politics with out-partisans and to be more amenable to conversations with those we already agree with.

This pre-registered report documents my expectations before collecting or seeing any data that I can leverage to explore these claims. It also provides documentation of my concrete hypotheses, modeling strategies, and expectations about the sensitivity by which my research design and modeling strategies allow me to draw correct inferences from the data.

{{< pagebreak >}}

### 2023-06-19 chapter_2/src/eda/study_1/cleaning.R

@@ -1,0 +1,204 @@
+# Title: cleaning script for pavlovia data
+
+# Notes
+  #* Description
+    #**This is a cleaning script for the pavlovia data.
+    #** It takes the csv files, extracts some data from them,
+    #** merges in the prolific demographic data, then removes
+    #** duplicated rows based on session_id, then converts
+    #** columns to correct data types.
+  #* Updated:
+    #** 2023-06-16
+    #** dcr
+
+# Setup
+  #* Load useful functions
+box::use(
+  data.table[...]
+  , ./R/clean_data[clean_data]
+)
+
+# Cleaning
+  #* Do basic cleaning to return a minimally usable data.frame
+list_df <- list() # create an empty list for my data_frames
+list_df[["original"]] <- clean_data(
+  folder = "../data/original/study_1/data"
+  , prolific_data = "../data/clean/prolific_demographic_data.csv"
+)
+  #* Create measures
+list_df[["cleaned"]] <- list_df[["original"]][
+    #** Generate 7-item pid measure
+    #** Coded as -3 = Strong Democrat, 3 = Strong republican
+  , pid_7 := fcase(
+    pid_3 == "Democrat" & pid_d_str == "Strong", -3
+    , pid_3 == "Democrat" & pid_d_str == "Not very strong", -2
+    , pid_3 == "Democrat" & is.na(pid_d_str), -1
+    , pid_3 == "Independent" & ind_lean == "Closer to Democratic", -1
+    , pid_3 == "Other" & ind_lean == "Closer to Democratic", -1
+    , pid_3 == "Independent" | pid_3 == "Other" & ind_lean == "Neither", 0
+    , pid_3 == "Other" & ind_lean == "Closer to Republican party", 1
+    , pid_3 == "Independent" & ind_lean == "Closer to Republican party", 1
+    , pid_3 == "Republican" & is.na(pid_r_str), 1
+    , pid_3 == "Republican" & pid_r_str == "Not very strong", 2
+    , pid_3 == "Republican" & pid_r_str == "Strong", 3
+  )
+]
+#* Recoding/adding factors
+list_df[["cleaned"]] <- list_df[["cleaned"]][
+  #** convert age to numeric
+  , age := as.numeric(age)
+][
+  #** convert attention to numeric
+  , attention := fcase(
+    attention == "Never", 0
[…]

### 2023-06-19 chapter_2/test/test_clean_data.R

@@ -1,0 +1,31 @@
+# Title: test clean_data function
+
+# Notes:
+    #* Description
+        #** testing of the clean_data funciton
+    #* Updated
+        #** 2023-06-12
+        #** dcr
+
+# Setup
+    #* set working directory
+#setwd("../src/")
+setwd("./src/")
+    #* load relevat packages
+box::use(
+    ./R/clean_data[...]
+    , data.table[...]
+)
+    #* examples
+        #** load single file
+df_temp <- read.csv(
+    file = "/Users/dcr/Library/CloudStorage/Dropbox/current_projects/dissertation/chapter_2/data/original/study_1/data/diss_ch_1_pre-reg_PARTICIPANT_SESSION_2023-06-12_10h09.02.63.csv"
+)
+
+df_test <- extract_file(df_temp)
+
+      #** Full test
+df_test <- clean_data(
+    folder = "../data/original/study_1/data"
+    , prolific_data = "../data/clean/prolific_demographic_data.csv"
+)

### 2023-06-20 chapter_2/src/appendix.qmd
add time elapsed model to ch2

@@
     modelsummary
+    , datasummary_skim
   ]
+  , data.table[...]
 )
@@
   file = "../data/temp/models/study_1_fitted.RData"
+)
+# Load data
+list_df <- list()
+list_df[["cleaned"]] <- read.csv(
+  file = "../data/clean/cleaned_pavlovia.csv"
 )
@@
     , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
+    , "b_attention" = "Attention"
     , "b_age" = "Age"
@@
 
+```{r}
+#| label: fig-h-3
+#| layout-ncol: 2
+#| fig-cap: Posterior Predictive checks for $H_3$ models
+#| fig-subcap:
+#|   - Red treatment
+#|   - Blue treatment
+list_ppc[["h_3"]][["red"]]
+list_ppc[["h_3"]][["blue"]]
+```
+
 {{< pagebreak >}}
@@
 
+```{r}
+#| label: tbl-h-4-dispersion
+#| tbl-cap: Checking for over-dispersion of data
+df_over_dispersed <- list_df[["cleaned"]][, c("trial_1_time_elapsed")]
+names(df_over_dispersed)[names(df_over_dispersed) == 'trial_1_time_elapsed'] <- 'Time Elapsed'
+datasummary_skim(
+  df_over_dispersed
+  , notes = "Data source: Prolific sample."
+  , histogram = FALSE
+)
+```
+
 ### Models
+
+```{r}
+#| label: tbl-h-4
+#| tbl-cap: The effect of partisan congruency on time spent looking at a yard sign
+# Redefine names
+model_names <- list(
+  "Red stimuli" = list_fitted[["h_4"]][["red"]]
+  , "Blue stimuli" = list_fitted[["h_4"]][["blue"]]
+)
+
+# Make table
+modelsummary(
+  model_names
+  , coef_map = c(
+    "b_trial_1_red_stimuli" = "Red yard sign"
+    , "b_trial_1_blue_stimuli" = "Blue yard sign"
+    , "b_pid_7" = "Party ID"
+    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
+    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
+    , "b_attention" = "Attention"
+    , "b_age" = "Age"
+    , "b_gender_idMale" = "Gender - Male"
+    , "b_gender_idNonMbinary" = "Gender - Non-binary"
+    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
+    , "b_race_idBlacknonMhispanic" = "Black"
+    , "b_race_idHispanice" = "Hispanic"
+    , "b_race_idMultipleraces" = "Multiple races"
+    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
+    , "b_race_idWhitenonMhispanic" = "White"
+  )  
+  , statistic = "conf.int"
+  , gof_map = gm 
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  , output = "latex"
+)
+```
 
@@
 ### Posterior Predictive Checks
+
+```{r}
+#| label: fig-h-4
+#| layout-ncol: 2
+#| fig-cap: Posterior predictive checks of $H_4$ models
+#| fig-subcap:
+#|   - Red
+#|   - Blue
+list_ppc[["h_4"]][["red"]]
+list_ppc[["h_4"]][["blue"]]
+```

### 2023-06-20 chapter_2/src/manuscript.qmd
add time elapsed model to ch2

@@
     , notes = c(
-      "Data source: Pavlovia."
+      "Data source: Prolific."
       , "Sample characteristics."
     )
+    , output = "latex"
 )
@@
   , escape = FALSE
+  , output = "latex"
 )
@@
 
+```{r}
+#| label: fig-h-4
+#| fig-cap: The effect of party congruency on time spent looking at yard sign
+#| layout-ncol: 2
+#| fig-subcap:
+#|   - Red treatment
+#|   - Blue treatment
+
+red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_4"]][["red"]]
+  , x_axis = "trial_1_red_stimuli"
+  , treatment = "Red"
+  , hypothesis = "H4"
+  , x_label = "Party ID"
+  , y_label = "Predicted amount of time elapsed"
+  , legend_title = "Treatment"
+)
+blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_4"]][["blue"]]
+  , x_axis = "trial_1_blue_stimuli"
+  , treatment = "Blue"
+  , hypothesis = "H4"
+  , x_label = "Party ID"
+  , y_label = "Predicted amount of time elapsed"
+  , legend_title = "Treatment"
+)
+red
+blue
+```
+
 ## Study 2

### 2023-06-20 chapter_2/src/models/study_1_fitting.R

@@ -10,7 +10,7 @@
 
 # Setup
     #* set working directory
-setwd("./src")
+setwd("./chapter_2/src")
     #* execute cleaning script
 source("./eda/study_1/cleaning.R")
     #* load helpful functions
@@ -177,14 +177,14 @@ list_ppc[["h_2a"]][["trial_3_single_model"]] <- pp_check(
 # Hypothesis 3
   #* Fit the models
 list_fitted[["h_3"]][["red"]] <- brm(
-  formula = trial_1_vote ~ trial_1_red_stimuli + pid_7 + trial_1_red_stimuli * pid_7 + age + gender_id + race_id
+  formula = trial_1_vote ~ trial_1_red_stimuli + pid_7 + trial_1_red_stimuli * pid_7 + attention + age + gender_id + race_id
   , data = list_df[["cleaned"]]
   , family = bernoulli(link = "logit")
   , prior = set_prior("normal(0, 1)", class = "b")
   , backend = "cmdstanr"
 )
 list_fitted[["h_3"]][["blue"]] <- brm(
-  formula = trial_1_vote ~ trial_1_blue_stimuli + pid_7 + trial_1_blue_stimuli * pid_7 + age + gender_id + race_id
+  formula = trial_1_vote ~ trial_1_blue_stimuli + pid_7 + trial_1_blue_stimuli * pid_7 + attention + age + gender_id + race_id
   , data = list_df[["cleaned"]]
   , family = bernoulli(link = "logit")
   , prior = set_prior("normal(0, 1)", class = "b")
@@ -198,7 +198,28 @@ list_ppc[["h_3"]][["blue"]] <- pp_check(
   list_fitted[["h_3"]][["blue"]]
 )
 # Hypothesis 4
-
+  #* Fit models
+list_fitted[["h_4"]][["red"]] <- brm(
+  formula = trial_1_time_elapsed ~ trial_1_red_stimuli + pid_7 + trial_1_red_stimuli * pid_7 + attention + age + gender_id + race_id
+  , data = list_df[["cleaned"]]
+  , family = negbinomial
+  , prior = set_prior("normal(0, 1)", class = "b")
+  , backend = "cmdstanr"
+)
+list_fitted[["h_4"]][["blue"]] <- brm(
+  formula = trial_1_time_elapsed ~ trial_1_blue_stimuli + pid_7 + trial_1_blue_stimuli * pid_7 + attention + age + gender_id + race_id
[…]

### 2023-06-20 chapter_2/src/manuscript.qmd
study 1 results done

@@
 I provide more textual information that deviates from the association of Republicans with red and Democrats with blue (trial 4).
-Examples of all of these yard signs are included in the supplementary materials.
+Examples of all of these yard signs are included in the appendix.
+For readers interested in the more technical details, the appendix acommpanying this chapter also includes a table of the data collected in the experiment -- @tbl-study-1-measures; reports full results, posterior predictive checks, and more detailed discussions for all of the models used in the remainder of this section.
 
 @tbl-study-1-descriptives presents some characteristics of the sample on the whole.
+The sample is relatively young with a mean age of 36.6 years old, few report being diagnosed with colorblindness, about 40% of the sample identifies as female, 70% of the sample identifies as White while only 10% report being Hispanic and Black.
+The average respondent in the sample reports leaning Democratic.
 
@@
 
-To address this first question, I use two measures of a participant's attention toward the colors on the yard sign.
-I collected the first measure through a question posed to the participant after viewing each yard sign, "what color was the yard sign?".
-The second measure is more implicit than the first: it accounts for the time someone's mouse hovered over the non-text elements of the yard sign relative to how long their mouse hovered over the text.
-The self-reported measure allows us to examine the conscious detection of color, while the more implicit measure allows us to examine where individuals' attention goes: toward the color or the text.
-
-This is primarily a descriptive exercise, and I intend to compare the differences in measures between the "non-partisan" (white) yard signs and the partisan (red and blue) yard signs.
-I will examine the differences in measures between the partisan yard signs among self-identified partisan respondents.
-I additionally include additional models that interact partisanship with age and political knowledge.
-As the consistent usage by the parties to use the colors red and blue did not occur until the 2000 presidential election, those that were in their early adult years during that time experienced partisan politics where colors were not a strong cue.
-I additionally expect that those who are more politically knowledgeable should rely on these partisan cues more as they tend to be stronger partisans [@delli-carpini_keeter_1996_yup].
+To address this first question, I use a couple of proxy measures for people's attention paid to the yard signs.
+I collect the first measure through recording the movement of the subjects' cursors along the x-and-y-axes.
+The second measure accounts for the amount of time participants' cursor lingers over a particular coordinate on their screen.
+Presumably, the more participants explore the yard sign, the more they are finding visual information that they can use to evaluate the candidate.
+While these two measures are simple proxies and are not sufficient measures of "noticing the yard sign," they allow us to get a sense of the patterns by which people explore the yard signs across treatment conditions.
+It also helps with my confidence in the degree to which variation between the treatments among different groups of participants are due to actual differences in how people processed these treatments and not due to random chance.
 
@@
 
+@tbl-h1-trial-1, @tbl-h1-trial-2, and @tbl-h1-trial-3 report the average difference in milliseconds and pixels along the x-and-y-axis of the subjects' screen when exploring the yard signs.
+These tables demonstrate a few things.
+First, the average participant in each treatment condition appear to be spending more time exploring the yard signs when there are more "conflicting" colors (trials 2 and 3).
+Second, we see that, for the most part, the average participant in the Red and Blue yard sign conditions spend more time exploring those yard signs than the participants viewing the White yard sign.
+
+Overall, it appears that people viewed the yard signs differently depending on which yard sign they were looking at.
+Now, I turn to exploring how features about the subjects themselves may shape the way they interact and respond to this visual information on the yard signs.
+
 ### Do colors shape perceptions of political objects?
 
-To address the following question of whether the colors affect perceptions of the candidate and the yard sign, I ask participants to report whether they perceived the candidate to be a partisan -- either Republican, Democrat, or as non-partisan immediately after viewing each image.
+To address the question of whether the colors affect perceptions of the candidate and the yard sign, I ask participants to report whether they perceived the candidate to be a partisan -- either Republican, Democrat, or as non-partisan immediately after viewing each image.
 Everything on the yard signs remains constant except for the color.
@@
 The baseline category for both of those indicator variables is if they instead saw the "white yard sign".
-
-My defined priors for both of these models' coefficients are Normally distributed with a mean of zero and a standard deviation of one.
-This reflects me starting from the position that my data need to provide evidence in support of my hypotheses rather than disproving them.
-The priors do allow for me to express uncertainty with this as I do have a belief that there is a chance my hypotheses are correct.
-Both models return $\hat{R}$ values of 1 indicating convergence and I confirm model performance by reporting the distributions of predicted values implied by my posterior distribution.
-These posterior predictive checks are included in @fig-h-2-ppc.
 
@@
 
+I also explore whether these effects may be weaker for those with colorblindness.
+The results of this model is reported @tbl-colorblindness, which is located in the appendix.
+The results do not suggest that they are.
+However, given that I had a very small number of respondents reporting colorblindness, the lack of substantive or statistical effects here are likely because I do not have enough participants with colorblindness in each group to compare.
+
+I also test whether my effects here are sensitive to my choice to run two separate regression models -- one for each treatment.
+I fit a single ordered logistic regression with two indicator variables for the treatment coded as: 0 did not receive red/blue treatment, 1 did receive treatment.
+The full results of this alternative model specification is included in @tbl-robustness-alt-specification-h-2 This means that the intercept term for the regression would be the predicted probability of the average respondent labeling the owner of the yard sign as either Democrat, Independent, or Republican.
+The conclusions I draw from this regression model do not change the ones I make here with @fig-h-2-predictions.
+
+In summary, I find that subjects perceive candidates with red yard signs as Republican, candidates with blue yard signs as Democratic, and candidates with white yard signs as being neither -- an Independent.
+These yard signs are *very* red and blue, however.
+In the next section, I examine how these effects may be weaker when we use less red or blue and include more blue or red.
+That is, see if using both colors on the yard signs has the capacity to increase uncertainty about the perception of partisan affiliation.
+
 ### Do these perceptions require consistency between information types?
 
-Another hypothesis derived from the snap-judgment model suggests that inconsistency in the yard sign's visual information will lead to more mixed perceptions of the candidate's political stances.
 The design of the latter trials in the study presents yard signs with mixtures of non-partisan and out-partisan colors.
 For example, primarily red and presumably Republican yard signs, but has some blue or white in them.
-
 I should expect that the trials that use less "consistent" visual information demonstrate more ambivalence among respondents in their reported perceptions of the politician's positions.
@@
 Two for each trial.
-Where each model for each trial models whether an average subject in the study reported that the yard sign they saw in the trial was a Democrat, Indepdent, or a Republican.
-@tbl-hypothesis-2a located in the appendix reports the full results of these models while @fig-h-2a-ppc located in the appendix reports the posterior predictive checks of these models.
+Where each model for each trial calculates whether an average subject in the study reported that the yard sign they saw in the trial was a Democrat, Indepdent, or a Republican.
+The predicted probabilities for each outcome occuring under different treatments and for different trials are presented in @fig-h-2a-predictions.
+@tbl-hypothesis-2a and @tbl-hypothesis-2a-cont located in the appendix reports the full results of these models while @fig-h-2a-ppc located in the appendix reports the posterior predictive checks of these models.
 
@@
 
+An important implication of the snap-judgment model suggests that if individuals perceive candidates using the color red as Republican while candidates using the color blue as Democratic, that partisans may be more attracted to yard signs displaying the color that fits with these associations.
+That is, if the color red conveys group membership to the Republican party, we should expect that Republican individuals should like the red yard signs more and be more willing to vote for candidates using those colors in their campaign materials.
+We should expect a similar thing with Democrats but with blue yard signs.
+Another expectation is that we should expect these relationships to be relatively strong despite little substantive information (e.g., policy positions and name recognition) about the candidate if color does indeed matter as a form of political information.
+
+After the three trials, I asked participants which of the three yard signs they would vote for.
+I create an indicator variable from this question that documents whether participants would vote for the candidate that owns the first yard sign (1) or not (0).
+I fit two logistic regression models with the vote variable as the outcome I am trying to explain.
+In the first of the two logistic regression models, I examine whether the effect that receiving a red versus a white stimuli is moderated by the participants' partisanship.
+As partisanship and its moderating effect on the treatment is of interest here while not being randomly assigned, I control for a number of confounding variables such as attention paid to politics, age, gender identification, and racial identification.
+The second logistic regression model is much like the first.
+The difference is that instead of examining the moderated effect of the red treatment, I examine the moderated effect of the blue treatment.
+As I am still interested in examining how partisan identification modifies the relationship between support for the candidate when comparing a blue versus a white yard sign, I include the same controls as I did with the first logistic regression model.
+I include the full table of results for both of these models in @tbl-h-3-main which is located in the appendix.
+
 ```{r}
@@
 
+@fig-h-3-predictions presents the average predicted probability that respondents who vary on treatment assignment and partisan identification would support the candidate.
+The results fit with my expectations.
+First, I see that the predicted probability that a strong Democrat would vote for a candidate with a red yard sign is less than 10% while for strong Republicans it is at about 70%.
+Likewise, we see that strong Democrats much prefer a candidate with a blue yard sign than a candidate with a white yard sign; 80% relative to 40%, respectively.
+Strong Republicans are unlikely to vote for a candidate with a blue yard sign and a white yard sign with their predicted probability of voting for either of those candidates below 30%.
+
 ### Do partisans process co-partisan branding faster?
@@
 To examine whether motivated reasoning is also active with the processing of politically-relevant color, I examine the difference between the amount of time between the start of viewing a stimulus and clicking "Next" to stop viewing the stimulus among those who were viewing a presumed co-partisan yard sign relative to those viewing a presumed out-partisan yard sign.
-As motivated reasoning tends to be more prevalent among strong partisans and those highly knowledgeable and interested in politics [@lodge_taber_2013_cup], I control for responses to the pre-treatment knowledge, interest, and partisan strength batteries.
+As the outcome is a count of the amount of time participants spent looking at a yard sign, I turn to a class of regression models that work well for explaining outcomes measured as count data.
+By the nature of my measure, I do not believe that participants can record a value of 0 as time elapsed is measured in milliseconds.
+Additionally, I expect that there will be what is referred to over-dispersion as I expect to have a large bulk of participants recording a very small time elapsed while there may be others who may record quite a large time elapsed.
+In the appendix, I include @tbl-h-4-dispersion which summarizes the time elapsed outcome variable; which indeed demonstrates over-dispersion in this variable with the outcome being the time elapsed.
+Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.
+I therefore fit two poisson-gamma models (sometimes referred to as negative binomial regression).
+I am interested in testing whether time elapsed can be explained by not only the color of the yard sign that the subject was viewing, but also that this effect is moderated by their partisanship.
+I therefore include an interaction term between stimuli and the partisan identification of the respondent.
+Like before, as partisan identification is not randomly assigned, I control for confounds such as attention paid to politics, age, gender identity, and racial identity.
+@tbl-h-4 located in the appendix is the full table of results for these two poisson-gamma regression models.
+@fig-h-4-ppc also indicates that the model does a quite good job at predicting the distribution of the time elapsed outcome variable.
 
@@
 
+@fig-h-4 presents the average predicted elapsed time for participants in different contexts.
+Overall, these results communicate that I do not find conclusive support for my expectations on $H_4$ in either regression model.
+Strong Democrats do appear to spend more time looking at red yard signs than white ones, once I account for the variation in the data, I cannot be sure that these differences are not due to random chance.
+I also see that there are not really any differences (substantive or statistical) between partisans looking at blue versus white yard signs.
+
 ## Study 2

### 2023-06-20 chapter_2/src/study_2/01_capd_text_scraping.py
setup poetry and download and clean study 2 data

@@ -2,19 +2,20 @@
 
 # Notes:
     #* Description: Jupyter Notebook to scrape CAPD site for yard signs in 2018-2022 national elections
-    #* Updated: 2022-11-28
+    #* Updated: 2023-06-20
     #* Updated by: dcr 
 
 # Load Modules
 import time # library to help with sleep and wait times
 from selenium import webdriver # to setup the driver
 from selenium.webdriver.chrome.options import Options # to specify options for my chrome webdriver
+from selenium.webdriver.chrome.service import Service as ChromeService
 from webdriver_manager.chrome import ChromeDriverManager # use the driver manager so that I don't have to download it and keep track of versions myself
 from selenium.webdriver.support.ui import WebDriverWait # use this so that I can wait on my driver to load the page completely before searching
 from selenium.webdriver.common.by import By # using the By function to help with the xpath searching
 from selenium.webdriver.support import expected_conditions as EC # load the expected_conditions function to make sure all elements matching the xpath happen before the driver stops waiting on the loading
 import polars as pl # need the pandas package for dataFrames
-import duckdb # need to store data into database
+#import duckdb # need to store data into database
 
 # Scraping of CAPD site
 
@@ -22,7 +23,7 @@ import duckdb # need to store data into database
 options = Options() # set webdriver options
 options.add_argument("start-maximized") # set an option for the webdriver to automatically open chrome browser that I can interact with the page
 
-driver = webdriver.Chrome(ChromeDriverManager().install(), options=options) # setup chrome webdriver
+driver = webdriver.Chrome() # setup chrome webdriver
 
 wait = WebDriverWait(driver, 100000) # specify wait time for the page before stopping it from collecting links in xpath
 
@@ -36,6 +37,7 @@ txt_url = driver.find_elements(By.XPATH, "//div[@class='candidate-card-text']/ul
 txt_url2 = [] # make empty list object to store urls in
 for i in txt_url:
     txt_url2.append(i.text) # grab the text for each of the sessions
+
 driver.close() # close the driver
 
 # Data wrangling
@@ -43,38 +45,40 @@ txt_url4 = [i for i in txt_url2 if i] # take the elements of txt_url2 and place 
 
 yard_signs = pl.DataFrame({
     #* Put the txt_url4 list into a column called Full
-    "Full": txt_url4}).with_columns([
+    "full": txt_url4}).with_columns([
[…]

### 2023-06-20 chapter_2/src/study_2/05_mit_election_lab_merge.py

@@ -10,16 +10,16 @@
 
 # Load modules
     #* from env
-import duckdb # for database access
+#import duckdb # for database access
 import polars as pl # for DataFrame management
 import numpy as np # for array management
     #* User-defined
-from PY.helper import names
+from chapter_2.src.PY.helper import names
 
 # Check out the election lab data
 election_lab = pl.read_csv(
     #* lazy load the csv file
-    "data/chapter_1/1976-2020-house.csv",
+    "./chapter_2/data/original/study_2/1976-2020-house.csv",
     null_values=""
     ).select([
     #* select the following columns
@@ -35,102 +35,96 @@ election_lab = pl.read_csv(
         pl.col("state").str.to_lowercase().alias("state"),
     #* create candidate_Name column
         #pl.col("candidate").str.to_lowercase().alias("Candidate_Name")
-    ]).with_column(
-        pl.concat_str(["state", "district"], sep = "-").alias("State_District")
-    ).with_column(
-        pl.when(pl.col("State_District") == "alaska-0")
+    ]).with_columns(
+        pl.concat_str(["state", "district"], separator = "-").alias("state_district")
+    ).with_columns(
+        pl.when(pl.col("state_district") == "alaska-0")
         .then("alaska-1")
-        .otherwise(pl.col("State_District")).alias("State_District")
-    ).with_column(
-        pl.when(pl.col("State_District") == "vermont-0")
+        .otherwise(pl.col("state_district")).alias("state_district")
+    ).with_columns(
+        pl.when(pl.col("state_district") == "vermont-0")
        .then("vermont-1")
-       .otherwise(pl.col("State_District")).alias("State_District") 
-    ).with_column(
-        pl.when(pl.col("State_District") == "montana-0")
+       .otherwise(pl.col("state_district")).alias("state_district") 
+    ).with_columns(
+        pl.when(pl.col("state_district") == "montana-0")
         .then("montana-1")
-        .otherwise(pl.col("State_District")).alias("State_District")
-    ).with_column(
-        pl.when(pl.col("State_District") == "wyoming-0")
+        .otherwise(pl.col("state_district")).alias("state_district")
+    ).with_columns(
+        pl.when(pl.col("state_district") == "wyoming-0")
         .then("wyoming-1")
[…]

### 2023-06-20 assets/_theory.qmd
adjust title of theory fig and then add some slides pre-FRAPSA

---
format: html
---
```{mermaid}
%%| label: fig-theory
%%| fig-cap: Snap-judgment model of politically-relevant visual information
%%| fig-width: 6.5
%%{init: {'theme':'base', 'themeVariables':{'primaryColor':'#ffffff', 'primaryBorderColor': '#000000'}}}%%
graph TD
    A[Detection of politically-relevant visual information] --> B(Activation of retrieval mechanism)
    B --> C[Memory and contiguous paths hot]
    C --> D[Appraisal of hot autonomous nervous system]
    D --> E1[Negative Valence]
    D --> E2[Positive Valence]
    E1 --> F1[Disengagement motivation]
    E2 --> F2[Attention activated]
    F1 --> |Neg. new information| G1[Encoded as negative]
    F1 --> |Pos. new information| G2[Encoded as positive]
    F2 --> |Neg. new information| G3[Encoded as negative]
    F2 --> |Pos. new information| G4[Encoded as positive]
    G1 --> H1[Strengthens negative path]
    G2 --> H2[Weakens negative path]
    G3 --> H3[Weakens positive path]
    G4 --> H4[Strengthens positive path]
    G2 --> |forgotten| H1
    H2 --> |reinforced| G2
    H3 --> |reinforced| G3
    G3 --> |forgotten| H4
```

### 2023-06-20 chapter_3/src/slides/slides.qmd
add slides for prr of chapter_3 pre-FRAPSA/ISPP

---
title: "How does color influence our political conversations?"
author:
  - name: Damon C. Roberts
    title: PhD Candidate
    affiliations:
      - id: CU
        name: University of Colorado Boulder
        department: Political Science
        address: 333 UCB
        city: Boulder
        region: CO 
        postal-code: 80309-0333
    attributes:
      corresponding: true
format:
  revealjs: 
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: true
    slide-number: true
    toc: true
    toc-depth: 1
    slide-level: 3
    bibliography: ../../../assets/references.bib
    footer: |
        <span class="faux-block">{{< fa brands creative-commons >}} 2021-2023 Damon Charles Roberts</span>
        <span class="faux-block"><br>All content licensed under {{< fa brands creative-commons >}} {{< fa brands creative-commons-by >}} {{< fa brands creative-commons-sa >}} [Creative Commons CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/)</span>
    self-contained: true
    output-file: color_and_conversation.html
execute:
  echo: false
---

```{r}
#| label: setup-block

# Load some nifty functions
box::use(
  ../../../chapter_2/src/R/predicted_prob_bar[...]
)
# Load fitted models
load(
  file = "../../../chapter_2/data/temp/models/study_1_fitted.RData"
)
```

# Background

---

- Chapter from a larger book project
- Book examines
  - does color convey political information?
    - particularly partisan affiliation

## Key findings from other chapters

---

```{r}
#| label: fig-associations
#| layout-ncol: 2
#| fig-cap: People associate red yard signs with Republicans and blue yard signs with Democrats
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["red"]]
  , x_axis = "trial_1_red_stimuli"
)
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["blue"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
)
red
blue
```

---

```{r}
#| label: fig-associations-weaker
#| layout-ncol: 2
#| fig-cap: Mixing red and blue in a yard sign increases uncertainty about partisanship
#| fig-subcap:
#|   - Trial 2 Red treatment
#|   - Trial 2 Blue treatment
#|   - Trial 3 Red treatment
#|   - Trial 3 Blue treatment
plot_trial_2_red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_2_red"]]
  , x_axis = "trial_2_red_stimuli"
)
plot_trial_2_blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_2_blue"]]
  , x_axis = "trial_2_blue_stimuli"
  , treatment = "Blue"
)
plot_trial_3_red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_3_red"]]
  , x_axis = "trial_3_red_stimuli"
)
plot_trial_3_blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_3_blue"]]
  , x_axis = "trial_3_blue_stimuli"
  , treatment = "Blue"
)
plot_trial_2_red
plot_trial_2_blue
plot_trial_3_red
plot_trial_3_blue
```

---

```{r}
#| label: fig-vote
#| layout-ncol: 2
#| fig-cap: Republicans report a higher probability of voting for candidates with red yard signs; Democrats report a higher probability of voting for candidates with blue yard signs
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_3"]][["red"]]
  , x_axis = "trial_1_red_stimuli"
  , treatment = "Red"
  , hypothesis = "H3"
  , x_label = "Party ID"
  , y_label = "Pr(Vote for candidate)"
  , legend_title = "Treatment"
)
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_3"]][["blue"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
  , hypothesis = "H3"
  , x_label = "Party ID"
  , y_label = "Pr(Vote for candidate)"
  , legend_title = "Treatment"
)
red
blue
```

# Question guiding this chapter

- Does color influence whether we talk about politics?

# Building a theory of snap-judgment based on politically-relevant visual information

## A common language

- Valance: a positive or negative response to an object.
- Affect (or affective state): feeling positive or negative in response to an object.
  - Pre-conscious response
- Emotion: Much more complex labels assigned to affective responses.
  - Often requires some amount of conscious processing to assign an appropriate label.
  - Slower
- Attitudes are an expression of valanced responses to some object.

## Learning from our psychology and neuroscience friends 😊

- There are a lot of useful things that we can borrow from social and affective neuroscientists and social psychologists

---

1. Memory reflects stored prior experiences with various objects
  - These memories are not just factual recollections of things
    - e.g., the balloon was red.
  - Memories often encode your affective responses to that object.
2. Relatedly, memories are multi-dimensional
3. How we form an attitude with new information (or a combination of it) is by accessing memories that share features in common with the object.
4. Memories are a complex web of prior experiences that have a whole lot of strands connecting them.
5. Social groups and social hiearchies are a dimension that we pay attention to and encode along with a memory.

## A snap-judgment model of politically-relevant visual information

---

{{< include ../../../assets/_theory.qmd >}}

# References

:::{#refs}
:::

### 2023-06-21 chapter_3/src/slides/slides.qmd
some more iterations of slides for ch3

@@
 author:
-  - name: Damon C. Roberts
-    title: PhD Candidate
-    affiliations:
-      - id: CU
-        name: University of Colorado Boulder
-        department: Political Science
-        address: 333 UCB
-        city: Boulder
-        region: CO 
-        postal-code: 80309-0333
-    attributes:
-      corresponding: true
+  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
 format:
@@
     transition: slide
-    scrollable: true
+    scrollable: false
     incremental: true
@@
 
+::: footer
+:::
 ---
 
-- Chapter from a larger book project
-- Book examines
+::: {.notes}
+- This is a chapter from a larger book project.
+- The book addresses the question: 
   - does color convey political information? 
-    - particularly partisan affiliation
+  - does it have pre-conscious effects on information that comes later?
+:::
+
+::: footer
+:::
 
@@
 
+::: {.notes}
+- Ran a study on prolific
+- Counterbalanced questions of attention, age, gender, race, colorblindness, partisan identity, etc.
+- Ran three trials that used mousetracking software
+- See one of three yard signs in each trial
+  - Red, blue, or white yard sign
+:::
+
+::: footer
+:::
 ---
@@
 
+::: {.notes}
+- Average predicted probabilities from two ordered logistic regressions
+- Outcome is the respondent's belief that the candidate was either a Republican, Independent, or a Democrat.
+- Read each figure by comparing the same colored bars. 
+- Candidates using red yard signs are more likely to be seen as Republican
+- Candidates using blue yard signs are more likely to be seen as Democrat
+:::
+
+::: footer
+:::
 ---
@@
 
+::: {.notes}
+- The other two trials used less of the primary color and brought in more red or blue
+- Do this as a test of the strength of these effects
+- See that the results (kind of) weaken.
+  - See that these effects weaken for the blue treatment. Much less change for the red treatment. Likely American flag.
+:::
+
+::: footer
+:::
 ---
@@
 
+::: {.notes}
+- After viewing the three trials, participants are asked which of the three yard signs they prefer.
+- Make a dichotomous variable of whether or not they like the first trial's yard sign.
+- run logistic regressions to see whether votes are explained by the stimuli moderated by partisan identification
+- See that there is a low predicted probability of strong Democrats voting for a candidate with a red yard sign.
+  - See that the predicted probability of strong Republicans voting for a candidate with a red yard sign is high.
+- See that there is a low predicted probability of strong republicans voting for a candidate with a blue yard sign.
+  - See that the predicted probability of a strong Democrat voting for a candidate with a blue yard sign is high.
+:::
+
+::: footer
+:::
+
 # Question guiding this chapter
@@
 
+::: {.notes}
+- Color seems to hold information about partisan affilations
+  - Red = Republican
+  - Blue = Democrat
+- Unclear what sorts of effects this will have on attitudes and behaviors, though.
+:::
+
+::: footer
+:::
+
 # Building a theory of snap-judgment based on politically-relevant visual information
+
+::: footer
+:::
 
@@
   - Slower
-- Attitudes are an expression of valanced responses to some object.
+- Attitudes are an expression of valanced responses to some object [@fazio_2007_sc].
 
-## Learning from our psychology and neuroscience friends 😊
+::: footer
+:::
 
-- There are a lot of useful things that we can borrow from social and affective neuroscientists and social psychologists
+## A cognitive architecture
+
+::: footer
+:::
 
@@
 
-1. Memory reflects stored prior experiences with various objects
-  - These memories are not just factual recollections of things
-    - e.g., the balloon was red.
-  - Memories often encode your affective responses to that object.
-2. Relatedly, memories are multi-dimensional
-3. How we form an attitude with new information (or a combination of it) is by accessing memories that share features in common with the object.
-4. Memories are a complex web of prior experiences that have a whole lot of strands connecting them.
-5. Social groups and social hiearchies are a dimension that we pay attention to and encode along with a memory.
+1. Memories are stored prior experiences [@cunningham_2021_yup].
+  - often encode affective responses
+2. Memories are multi-dimensional [@kahana_et-al_2022_ohhum].
+3. Sensory and affective information is often encoded in memories [@kensinger_fields_2022_ohhum].
+4. Memories are a complex network [@kahana_et-al_2022_ohhum].
+  - Interconnected by different bits of information
+5. Social groups and hierarchies are reflected in this network  [@santavirta_et-al_2023_n].
+
+::: footer
+:::
 
 ## A snap-judgment model of politically-relevant visual information
+
+::: footer
+:::
 
@@
 
+::: {.notes}
+Scenario.
+- At the airport and watching the news
+- Someone sits next to you before boarding
+- They are wearing a red hat
+- You might have one of two reactions
+- A small conversation starts up since they see you watching the news.
+- You see its a MAGA hat but they tell you they are having a hard time squaring some of their other beliefs with the stances of the party on immigration.
+- You may shift your initial impression a bit. Feel more positive or more negative. However, you haven't fully reversed course on that. You have learned something though.
+
+Implications.
+- Color has downstream effects on our attitudes towards an object related to politics.
+- The degree to which color matters in politics is whether or not it is primed.
+:::
+
+::: footer
+:::
+
+# Proposed research design
+
+## Study 1
+
++---------------------:+:-----------------:+
+| 🚫 Prime, Red shirt  | Prime, Red shirt  |
++----------------------+-------------------+
+| 🚫 Prime, Blue shirt | Prime, Blue shirt |
++----------------------+-------------------+
+
+: $2 \times 2$ factorial design {#tbl-study-1}
+
+::: footer
+:::
+
+## Study 2
+
++-------------------------:+:---------------------:+
+| Red shirt, 🚫 congruent  | Red shirt, congruent  |
++--------------------------+-----------------------+
+| Blue shirt, 🚫 congruent | Blue shirt, congruent |
++--------------------------+-----------------------+
+
+: $2 \times 2$ factorial design {#tbl-study-2}
+
+::: footer
+:::
+
 # References
 
-:::{#refs}
+::: {#refs}
 :::
+
+::: footer
+:::

### 2023-06-21 chapter_2/src/appendix.qmd

@@
 
-{{< pagebreak >}}
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Measure                     | Question                                                                                                                                                                                                                                                                                                  | Coded as                                                                                                                                                           |
++=============================+:=========================================================================================================================================================================================================================================================================================================:+:==================================================================================================================================================================:+
+| Age                         | Confirm your age                                                                                                                                                                                                                                                                                          | Text entry                                                                                                                                                         |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Gender                      | What is your gender identity?
+| Non-binary, Female, Male, Prefer not to choose, Other                                                                                                              |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Sex                         | What is your sex assigned at birth?
+| Female, Male, Other                                                                                                                                                |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Race                        | Which ethnic or racial category best describes you?
+| White, non-Hispanic; Black, non-Hispanic; Hispanic; Asian or Native Hawaiian/other Pacific Islander; Native American/Alaska Native or other race; Multiple races   |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Color blind                 | Have you been diagnosed with any of the following visual impairments that are not treated with corrective lenses?
+| Color blindness (any form); Blurred vision (not treatable by corrective lenses); Macular degeneration; Glaucoma; Cataract; Diabetic retinopathy; None of the above |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Attention                   | How often do you pay attention to what is going on in government and politics?
+| Always; Most of the time; About half the time; Some of the time; Never                                                                                             |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Party ID                    | Generally speaking, do you usually think of yourself as a Democrat, a Republican, an Independent, or what?; Would you say that you are a strong [Republican/Democrat] or not a very strong [Republican/Democrat]?; Do you think of yourself as closer to the Republican party or to the Democratic party?
+| Republican, Democrat, Independent, Other; Strong, Not very strong; Closer to the Republican party, Neither, Closer to Democratic                                   |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Attn.
+Check                 | In a few words describe what is your first memory of a political event.
+| Text entry                                                                                                                                                         |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Trial stimuli               | Yard sign assigned                                                                                                                                                                                                                                                                                        | 0 = White, 1 = Red/Blue                                                                                                                                            |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Trial stimuli alt           | Yard sign assigned                                                                                                                                                                                                                                                                                        | 0 = Not red/blue, 1 = Red/Blue                                                                                                                                     |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Time elapsed                | NA                                                                                                                                                                                                                                                                                                        | Difference between time at start of trial and stop                                                                                                                 |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| $\Delta_{t}$ (milliseconds) | NA                                                                                                                                                                                                                                                                                                        | Time elapsed between cursor movements                                                                                                                              |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| $\Delta_{x}$ (pixels)       | NA                                                                                                                                                                                                                                                                                                        | Number of pixels moved along x-axis                                                                                                                                |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| $\Delta_{y}$ (pixels)       | NA                                                                                                                                                                                                                                                                                                        | Number of pixels moved along y-axis                                                                                                                                |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Candidate party             | Is this candidate a Republican, a Democrat, or Neither?
+| Republican, Democrat, Neither                                                                                                                                      |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Candidate vote              | Of the three candidates who would you most likely vote for?
+| The first yard sign, The second yard sign, The third yard sign                                                                                                     |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Candidate vote indicator    | NA                                                                                                                                                                                                                                                                                                        | 0 = Would not vote for first yard sign, 1 = Would vote for first yard sign                                                                                         |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
 
-## Hypothesis 1
-
-### Models
-
-{{< pagebreak >}}
-
-### Posterior Predictive Checks
+: Study 1 Measures {#tbl-study-1-measures}
 
@@
 
+To test whether people associate the color red on a political yard sign with Republicans and the color blue on a political yard sign with Democrats.
+
 ### Models
+
+These first two models are ordered logistic regressions.
+The outcome of interest is a 3-item response of whether they perceived the owner of the yard sign to be a Republican, a Democrat, or neither.
+This variable was recoded to be 1 = Democrat, 2 = Independent, and 3 = Republican.
+In the first ordered logistic regression, I predict this outcome with a indicator variable of whether the participant saw a white yard sign (value of 0) or saw a red yard sign (value of 1).
+
+My defined priors for the beta coefficient are $Normal(0, 1)$.
+This means that I think that 68% of the non-transformed beta coefficients I think will be between -1 and 1, with the remaining 32% being larger than that.
+I fit the models on 4 chains with 2000 chains each (1000 warmup, and 1000 sampled).
+
+@tbl-hypothesis-2-main reports the logged-odds of a subject reporting that a subject was either a Democrat, Independent, or Republican.
+Positive logged-odds indicate that the logged-odds of a subject reporting a candidate is a Republican increase, whereas a negative value indicate that the logged-odds of reporting the candidate is a Democrat.
 
@@
 
+I also suspected that these effects could be moderated or sensitive to other things. First @tbl-interacted-models-h-2 reports how these effects in @tbl-hypothesis-2-main may be moderated by age.
+
 ```{r}
@@
 ```
+
+Additionally, I seek to test whether these effects reported in @tbl-hypothesis-2-main are sensitive to the way I chose to test these effects.
+Specifically, I code the predictor variables as 0 = not red/blue, 1 = red/blue.
+This gives me two variables that I include in a single ordered logistic regression.
+This means that the intercept term is the logged-odds of defining the participants as either Democrat, Independent, or Republican if the subject received a white yard sign.
+The two beta coefficients, in that model reflect the difference in the logged-odds of reporting that the candidate was either a Democrat, Independent, or Republican when they received the red or blue yard sign relative to the white yard sign.
+The results remain robust to this alternative specification.
+
 ```{r}
@@
 ```
+
+Finally, I check to see if the results reported in @tbl-hypothesis-2-main are moderated by subjects that are colorblind.
+Though, I have reasons to beleive they are, the sample does not really lend itself to a robust test of this.
+The sample does not have a large number of respondents who indicated that they were diagnosed with some type of colorblindness.
+Therefore, I likely do not have enough data points for colorblind respondents in these different groups.
 
@@
 ### Posterior Predictive Checks
+
+To check whether my model specification (the variables that I included and the priors I define) are robust, I plot the posterior predictive checks for the model.
+These posterior predictive checks take the predicted values given my posterior distribution for each of these models, and plots the distribution of these predicted values relative to the distribution of actual values tha I have in my dataset.
+A well-specified model would show that there are not large nor systematic differences between the distributions of the predicted and actual values.
+Here, it appears that all of the models do a pretty good job.
+
 ```{r}
@@
 ```
+
+## $H_{2a}$
+
+An aditional analysis I include is to examine the bounds by which these effects hold if we vary the amount of partisan colors are on a yard sign.
+The second and third trials introduce variations of the yard signs in the first trial that include more white and even more color for the opposing political party (if red or blue condition).
+The goal here is to see whether these results that are reported in @tbl-hypothesis-2-main are weaker for these other two trials.
+
+I specify the exact same models as I did for @tbl-hypothesis-2-main.
+The only difference is that these variables record responses and treatment assignment for trials two and three.
+The results that are reported in @tbl-hypothesis-2a and @tbl-hypothesis-2a-cont suggest that my initial suspicions have *some* validity to them.
+That is, we see that the effects reported in @tbl-hypothesis-2-main are much weaker for blue yard signs -- participants are not as decisive in reporting that the candidate with the blue yard signs are Democrats.
+The effects reported in @tbl-hypothesis-2-main seem to hold for the red yard signs, however.
+Like before, I examine whether these results are robust to an alternative model specification (a single model with two treatment indicator variables).
+Like with tests of $H_2$, it appears that they are.
+
+### Models
 
@@
 ### Posterior Predictive Checks
+
+To confirm that my models return predicted values from the posterior distribution that reflect my actual data, I plot the posterior predictive checks for each model.
+All six models appear to do a pretty good job.
+
 ```{r}
@@
 ### Models
+
+Here, I am testing whether candidates with red yard signs are supported more by Republican subjects and whether candidates with blue yard signs are supported more by Democratic subjects.
+In my original study, I ask participants after all three trials to report which of the three yard signs they would vote for.
+Here, I recode this response to be a binary outcome -- would they vote for the first yard sign they saw (value of 1) or not.
+Like I have done in previous tests, I run two models -- each where the predictor is a indicator of whether they received the red/blue treatment (value of 1) or the white treatment.
+Since the outcome is dichotomous, instead of an ordered logistic regression, I instead run a logistic regression.
+Since partisan identification is a primary part of the inferential task here and since it cannot be experimentally treated, I need to control for some confounds such as attention to politics, age, gender identification, and racial identity.
+
+@tbl-h-3-main reports the results of these models.
+The results suggest that Republicans are indeed more supportive of candidates using the color red, not supportive of candidates using the color blue, and are not supportive of candidates using the color white.
+The results also suggest that Democrats are more supportive of candidates of using the color blue, and are much less supportive of candidates using the colors red or white.
 
@@
 
+To confirm that these models return sensical predictions, I again plot the posterior predictions.
+@fig-h-3-ppc seems to suggest that both models do a pretty good job at returning a distribution fo predicted outcomes in terms of differences between those values and outcomes measured in my sample.
+
 ```{r}
-#| label: fig-h-3
+#| label: fig-h-3-ppc
 #| layout-ncol: 2
@@
 
+$H_4$ seeks to test whether partisan subjects spend more time looking at the yard sign of political opponents than those they share a partisan identity with.
+Specifically, it seeks to see whether the elapsed time for the trials are longer for participants assigned to a red or blue yard sign condition if the subject is a Democrat or Republican (respectively) relative to Republicans or Democrats (respectively).
+
+The outcome variable is a count of how many milliseconds a respondent was in a given trial.
+As this is count data, I have high suspicion of over-dispersion (meaning that the mean value and the median value are unequal).
+To make sure that I am correct in this, I generate a table reporting the summary statistics of the time elapsed in @tbl-h-4-dispersion.
+
 ```{r}
@@
 
+It appears that there is some over-dispersion here. Therefore, my choices for which type of count model to use leans away from the poisson regression and onto something like a poisson-gamma model.
+
 ### Models
+
+As mentioned above, the outcome here is the time elapsed for a trial (in milliseconds).
+Since this is a count outcome, I should be using a type of model that uses a link function in the poisson family as opposed to the exponential family.
+As @tbl-h-4-dispersion demonstrated, the data are over-dispersed.
+Therefore, I use a poisson-gamma model as my link function which is often referred to as a negative binomial regression.
+I still have priors suggesting that my beta coefficients are $Normal(0, 1)$.
+
+Like I have done before, I run two models.
+One for each partisan stimuli with the baseline category as the White yard sign condition.
+As the hypothesis goes beyond saying that I think subjects in the red/blue treatment will spend more time looking at the yard sign than in the white, but instead say that I think this will be moderated by partisanship, I include a interaction term in each of these models.
+Additionally, as partisan identification is a key explantory variable here and is not experimentally treated, I control for a numbe of potential confounds such as attention to politics, age, gender identity, and racial identity.
+The results of these models are recorded in @tbl-h-4.
 
@@
 
+As I made a modeling choice based on the overdispersion of the outcome variable, I want to confirm that these models did an adequate job at returning predicted values based on my posterior distribution relative to the actual data in the sample.
+The posterior predictive checks suggest that it did indeed do a pretty good job.
+It looks like I may be slightly underestimating some lower values for the elapsed time, but the distribution on the whole looks pretty good -- including on the tails.
+
 ```{r}
-#| label: fig-h-4
+#| label: fig-h-4-ppc
 #| layout-ncol: 2

### 2023-06-21 chapter_2/src/manuscript.qmd

@@
 
-Do the colors red and blue mean much to citizens in the context of politics?
-Before the 2000 Presidential Election, television networks used a variety of different colors when presenting electoral maps to visually communicate which candidate had won the electoral votes for each state.
-However, beginning in the 2000 election, networks consistently used the color red to indicate that George W.
-Bush (the Republican party's nominee) had won a state's electoral votes and the color blue to indicate that Al Gore (the Democratic party's nominee) had won a state's electoral votes [@elving_2014_npr].
+Are colors important to politics?
+I argue that they convey information that matters to campaigns and voters.
+People rely on more than information about policy positions to understand politics [see @pietraszewski_et-al_2015_c;@perez_tavits_2022_pup as examples].
+To reduce cognitive load, the affiliation detection system allows for efficient social behavior prediction by associating various cues with a group.
+In politics, associating Black voters with the Democratic party and White voters with the Republican party is one example [@pietraszewski_et-al_2015_c].
+As Americans consistently link the colors red and blue with the Republican and Democratic parties [@elving_2014_npr;@williams_et-al_2022_jomp], as well as their connection to ideology [see @maestre_medero_2022_pr for example], we should explore the degree to which color not only acts as an affiliative cue, but whether it is strong enough to drive individual behavior, and whether it is a strong enough shift to shape electoral strategy.
 
-The parties have seemingly adopted these brands[@williams_et-al_2022_jomp] and @fig-party-brand conveniently demonstrates this.
-While one may wonder, "Are news networks to credit/blame for giving the parties these colors?" or "Did news networks do this because choices in party branding was going this way anyhow?", this chapter wants to examine this from an alternative perspective that centers voters.
-Specifically, this chapter seeks to address the question of whether voters recognize these tendencies and whether this influences their levels of support for candidates in a variety of contexts.
+As a simple yet ubiquitous piece of visual information, color may have more influence over shaping political views than we have given it credit thus far.
+As visual information is processed automatically and faster than other forms of information [see @ames_et-al_2012_ohsn], in this chapter I argue that it triggers associated neurological pathways and leads us to form a snap-judgment (an attitude without subsequent, more complex, information) that we rely upon for attitudinal and behavioral outcomes.
+Later chapters will explore the degree to which the inclusion of subsequent substantive policy information overrides this snap-judgement.
 
-One way in which voters may encourage the parties to adopt a consistent, but yet distinct, brand -- in terms of color -- is through the party's desire to capture as many voters as possible [@downs_1957_jpe].
-For most voters, following politics and forming opinions on every policy position and candidate is cognitively demanding and time consuming.
-As a result, voters often satisfice and tend to repeatedly support the same party across elections [@campbell_et-al_1960_jws].
-Building on these perspectives, decades of work suggests that voters see the parties as more than just a cluster of political elites who have formed a coalition around similar perspectives on policy, but that voters actually see these parties as a "team" or a social group by which one includes in their definition of self [@campbell_et-al_1960_jws;@mason_2018_cup].
-As a result of this, partisans have a tendency to stick with candidates that clearly align themselves with one group and to distinguish themselves from the other group [@utych_2020_es].
+To give a preview for this chapter, I propose two studies to explore the claims I make in this chapter.
+Yard signs are a simple yet effective source of campaign branding for political candidates.
+They shape the attitudes of those who view them [@makse_et-al_2019_oup], and have enough of an individual-level effect that they shape aggregate attitudes in the form of electoral outcomes [@green_et-al_2016_es].
+As yard signs are a simple and static form of campaign advertising, they cannot rely heavily on more complicated forms of information.
+However, one form of information they rely on and vary in is their color.
+With these characteristics, yard signs are an ideal candidate both from a statistical standpoint and also substantive.
+From a statistical standpoint, as they are static forms of party branding they have fewer moving parts, which help isolate the effect that color has on shaping attitudes.
+From a substantive standpoint, while we understand that yard signs matter to campaigns, we have yet to systematically explore more simple design choices such as color.
 
-Taking this perspective, this chapter argues that color works as a useful heuristic (mental shortcut) for the average citizen to figure out whether a political candidate is a Republican, a Democrat, or neither.
-Much like a sports team, we might expect that the athletes for our favorite team will be wearing the colors for the team they play for, even if we may not be familiar with a player who may have joined the team after the most recent draft or trade deadline [see @kurzban_et-al_2001_pnas;@pietraszewski_et-al_2015_c].
-As a result of these connections between the party and a particular color, individuals will either report lower levels of support for a candidate that uses a color associated with the other political party and will report higher levels of support for the candidate using the colors that are associated with the individual's preferred party.
-I expect that these effects hold up particularly in the circumstance where voters have no substantive information about the candidate.
-Before bringing empirical evidence to examine these claims, the chapter elaborates on the argument and outlines a set of expectations about how color conveys group membership and what we may expect citizens' reactions are to such information.
+In [Study 1](#sec-study-1), I conduct an online experiment that examines whether the public notice color and whether their attitudes are shaped by "Republican Red" and "Democratic Blue" on the yard signs of a fictional candidate.
+Based on informal conversations with campaign marketing consultants, it appears that campaigns are aware that the colors red and blue betray the partisanship of a candidate to voter.
+So in [Study 2](#sec-study-2), I examine whether campaigns react to the partisan composition of an electorate as a response to these individual-level patterns.
+I do this by examining how electoral context shapes variation in using these partisan colors.
+While these two studies highlight endogenous processes, I am not necessarily arguing that either of these patterns only flow one way.
+In fact, I believe that there is a necessary feedback loop between the parties and their base of support.
+Voters support candidates who signal strong allegiance to the party to increase their chances for electoral success [@utych_2020_es] and the parties are motivated to distinguish themselves [@lee_2009;@clifford_2020_pb] as a result of their high levels of ideological and affective polarization [@dietrich_2021_pa;@enders_2021_jop].
 
-## How do voters evaluate political candidates?
+From the first study, I find that individuals do shift their perceptions of political candidates in response to the use of the colors red and blue, they consistently and strongly associate Republicans with the color red and Democrats with the color blue, and their willingness to vote for a candidate can be dramatically different depending on whether the color used aligns with the individual's partisan identification.
 
-Political pscyhologists have amassed a great deal of evidence suggesting that voters are not objective consumers of political information.
-First, voters are cognitive misers and seek to find shortcuts to come to decisions about politics such as who to vote for [@lau_redlawsk_2001_ajps].
-Second, one such shortcut that voters may use is by relying on the party of the candidate as opposed to relying on consistent ideological principles [@converse_1964_cr;@barber_pope_2019_apsr].
-Third, the reason that partisanship is such a useful heuristic is that it now reflects a social identity that people use when defining who they are as opposed to thinking of their alignment with the parties as just a reflection of their current policy positions [@campbell_et-al_1960_jws;@mason_2018_cup;@groenendyk_2012_pb].
-That is, someone's partisanship is expressive as opposed to a reflection of their evaluation of the performance of the policies advocated for by the party [@huddy_et-al_2015_apsr].
-Evidence suggests that even those who claim they are independent are not necessarily less susceptible to this tendency to align their expressed support with a preferred party, but really are those who tend to dislike participating and reporting that they participate in "partisan politics" [@klar_krupnikov_2016_cup;@robison_2022_prq].
+## The role of visual information in politics
 
-This literature in political psychology heavily borrows from social psychology which first argues that social groups are a highly effective and efficient way by which humans make decisions in a variety of contexts in and beyond politics [@tajfel_turner_1979_ejsp]; and that these social groups and our preferences for one group versus another are even reflected in neurobiological functions [@zink_barter_2012_ohsn].
-Further, this literature borrows from the idea that we are motivated to defend our prior beliefs and stances.
-That is, we are not always motivated to collect and respond to accurate information, but we often have this strong bias to find ways to borrow and rely upon information that makes us feel good about pour prior positions [@kunda_1990_pb].
+<!--
+A central theme of an edited issue of *The International Journal of Press/Politics* is that visual politics is important and understudied [@lilleker_2019_pm].
+Those who are engaged in these questions attribute these challenges to methodological sophistication and the difficult task of interdisciplinary theorizing [@gerodimos_2019_pm; @bucy_joo_2021_ijpp].
 
-What this evidence suggests is that voters are highly motivated to defend prior positions and are often thinking about politics in terms of alignment with their preferred party [@groenendyk_2012_pb;@mason_2018_cup].
-This evidence is often cited as the primary explanation for the emotionally charged negative reactions to the other parties [@iyengar_westwood_2015_ajps;@westwood_peterson_2022_pb].
-This evidence also suggests that the two parties are central in how people evaluate politics -- regardless of whether or not an individual expresses high or low levels of partisan animosity.
-People often see politics in the United States as either a "Do I support the Democrats or do I support the Republicans?" and the two parties have put in significant efforts to make this a feature [@lee_2009;@clifford_2020_pb].
-This distinction between the parties at the elite levels are reflected in real ideological polarization among elites [@enders_2021_jop] that even manifest as an unwillingness to talk to members of the other party on the House floor [@dietrich_2021_pa].
+The rise of television consumption changed the focus of the medium in the research for political communication scholars [@hall-jamieson_2014_ohpc].
+In a similar way, so does the rise of image-based social media and has set new agendas.
+For several methodological and disciplinary reasons, the visual aspects of television were of little focus in the literature [@bucy_joo_2021_ijpp].
+However, the news organizations and politicians are responding to the ubiquitous use of the public to use image-dominant social media platforms like TikTok and Instagram, by joining such platforms.
+They are relatively active on these platforms as well.
+Scholars need to make this transition to integrate the role of simple visual information into our theories of political information processing (abbreviated as *pip*) and attitude formation.
+-->
 
-In summary, the parties use the colors red and blue at varying rates in contemporary politics [@williams_et-al_2022_jomp], they are polarized [@enders_2021_jop], and seek to find ways to distinguish themselves from the other party [@lee_2009].
-For voters, they are receptive to such efforts among elites [@zaller_1992_cup;@leonard_et-al_2021_pnas] and often have motivations to stick with the party that they have supported regardless of ideological shifts [@barber_pope_2019_apsr].
-Much of this information included in the literature discussed here thinks of it in terms of communicated policy positions.
-Over the next few pages, I build on these perspectives to argue that color is one type of symbology that the party and its candidates may use to quickly and efficiently communicate party aliance to potential voters.
+How does politically-relevant visual information matter to politics?
+From an evolutionary-biological perspective, visual information has been a common source of information for millions of years that a variety of single-and-multi-cell organisms rely upon to evaluate their environment [see @grabe_bucy_2009_oup, Chapter 1 for a useful discussion].
+Visual information processing, as an ancient biological invention, the human brain is organized around the processing of it.
+Reflecting on this, many scholars of neuroscience argue that visual information is the fastest form of information processing for humans.
+For example, even complex visual information, such as the warmth expressed in someone's facial features, is automatically and pre-consciously processed in only about 33 milliseconds (abbreviated as ms) [@ames_et-al_2012_ohsn].
 
-## Building an intuition for color's effect on politics
+Approached from a different perspective, as humans are cognitive misers \index{cognitive misers}, visual information in the realm of politics provides efficient information to voters about politically-relevant actors and events [@lilleker_2019_pm].
+Evidence suggests that even simple party branding on yard signs has an emotional appeal and encourages a shift in attitudes toward the person who owns the yard sign [@makse_et-al_2019_oup].
+That is, even branding as simple as yard signs appears to influence the attitudes of those who view them.
+However, like all types of party branding, there remain questions about the individual visual components' contribution.
+
+More simple forms of visual information are likely even more efficient forms of information.
+In the context of the United States, the "Republican red" and "Democratic blue" is a relatively recent invention that likely has significant import in an era of significant effort by the parties to distinguish themselves from each other [@clifford_2020_pb] and where voters toe the party line [@utych_2020_es].
+Since the 2000 presidential election, the media have consistently used red on their electoral maps in "horserace" journalism to represent Republicans and blue to represent Democrats [@elving_2014_npr].
+The supposed consequence is that Democrats now report a preference for the color blue over the color red, and Republicans report a preference for the color red over the color blue [@schloss_palmer_2014_pbr].
+Others have demonstrated the strategic choices that candidates make on branding choices -- including color -- based on the types of information they want to convey to voters to distinguish them from their rivals [see @williams_et-al_2022_jomp].
+
+What remains unclear is whether these patterns are just simply patterns or whether there are identifiable causes to these patterns.
+While political psychologists are increasingly interdisciplinary and rely on psychology and neuroscience, it is relatively unclear how color can convey information as complex as politics.
+Further, it is unclear whether such a simple type of information has enough efficacy to shape political outcomes such as voting intention.
+This chapter is a first cut at addressing these open questions.
+
+<!--
+In western Europe, voters are better at connecting the ideological positioning of a party with the color they use in their branding [@casiraghi_et-al_2022_pp].
+The ability to do so is strengthened when the party is longer-surviving and is more prominent [@casiraghi_et-al_2022_pp].
+The use of politically-relevant colors activates biases toward pre-existing ideological and partisan preferences among voters in a Spanish sample [@maestre_medero_2022_pr].
+And male and female candidates in the United States use different colors -- among other things such as fonts -- in their campaign branding to convey distinguishing information about themselves [@williams_et-al_2022_jomp].
+Despite the existing evidence, the particular psychological mechanisms driving this remain unclear.
+For example, it is unclear how colors may be organized into a cognitive schema that enables voters to quickly access and connect these colors to more complex political attitudes.
+Furthermore, it is unclear from existing evidence how colors may not just be associated with complex attitudes, but how they may enable political attitude formation and may strengthen existing connections between different political objects.
+As a jumping-off point, we can use the literature of political information processing (abbreviated as *pip*)\index{political information processing} to establish a common understanding of how political information is processed and how attitudes are formed by the processing of political information.
+
+The first prominent model of *pip* derives from rational choice perspectives.
+The memory-based model of *pip* views attitudes as a weighted collection of prior information [see @zaller_1992_cup].
+As individuals receive new information, they organize it into a schema that is relative to prior objects they already have encoded.
+By encoding this new information, the model predicts that individuals incorporate this new object with similar objects to form an attitude.
+This schema then may be more accessible in similar contexts and may then sample from its elements when prompted to express a political attitude.
+While the Receive-Accept-Sample (RAS) model accepts the view that expressed attitudes are a weighting of information most accessible at the time of attitude expression [@zaller_feldman_1992_ajps], it still presupposes that the weighting is an average of prior information.
+
+The second prominent model challenges this latter point.
+The online model of *pip* contends that individuals do not evenly weigh information, but that whether they even store it in their long-term memory to access later is biased in the direction of supporting pre-existing attitudes [@lodge_taber_2013_cup]; this phenomenon is referred to as motivated reasoning by the psychology literature [@kunda_1990_pb].
+This model suggests that people ignore new information that goes against their prior beliefs and that information confirmatory of their preferences is quicker to access -- referred to as hot cognition [@lodge_taber_2013_cup].
+
+The online model conceptualizes this underlying information encoding and attitude retrieval mechanism as automatic [@lodge_taber_2013_cup].
+This occurs due to the information's strong associations with valanced appraisals of the information guiding the attitude [@lodge_taber_2013_cup].
+This brings political scientists closer to the dominant conceptualizations among neuroscientists and psychologists concerned with memory retrieval, encoding, and attitude formation [see @fazio_2007_sc].
+Namely, that memories are encoded and retrieved quickly based on associations due to their association with valanced appraisals [@kensinger_fields_2022_ohhum].
+What remains unexplored is how visual information such as color may prime individuals to engage in motivated reasoning pre-consciously.
+If they keep their attention on the object, what paths are activated by such information?
+
+-->
+## Integrating color into a model of political information processing
+
+Existing models of political information processing (abbreviated here as *pip*) primarily focus on complex forms of political information such as policy positions communicated verbally or through text.
+As individuals process visual information before other sorts of information, we might expect that they may form a snap judgment or the initial appraisal of an object.
+
+Color and other simple visual information are processed much quicker and occur more frequently than text-based information that may be communicated through a news article [@mehta_zhu_2009_s].
+As the color and other visual information are processed differently, we should also consider its use as political information.
+As visual information is affectively encoded [@cimbalo_et-al_1978_jgp], it can affect the affective state and processing of more complex information, such as text.
+The visual information provides a snap judgment or an impression of the object through faster processing and activates particular neurological processes that influence subsequent information appraisals [@ames_et-al_2012_ohsn].
+This implies that snap-judgments from visual forms of political information may have downstream effects that shape the way in which we engage with forms of political information that we traditionally consider.
+
+Before expanding upon the role of colors in shaping political attitudes, let me first define an attitude as a concept.
+An attitude represents an accessible, valanced evaluation of associated prior information and experiences.
+This conceptualization fits with that of the Object-Evaluation Associations Model [@fazio_2007_sc].
+As opposed to viewing attitudes as a latent collection of memories, it views attitudes as measurable evaluations of memories.
+As memories are at the core of an attitude, the association of memories with its evaluative component [see @kensinger_fields_2022_ohhum] contributes to the perspective that attitudes are affective.
+This implies that we should be able to measure attitudes but that such an operationalization requires careful consideration of the context's role in any given measure of an attitude as they result from memories [@fazio_2007_sc].
+In this chapter, I consider colors' effect on shaping attitudes about a political object -- a yard sign.
+As I hold this constant in the chapter, concerns about variation in what people are thinking about when seeing the color red and blue is less of a concern in this chapter.
+Later chapters grapple with this consideration.
+
+In line with existing theories of *pip*, I conceptualize attitudes as associative.
+This means that attitudes may be unstable - not randomly, in any case.
+As attitudes are associative, they manifest slightly differently depending on the associative paths activated [@fazio_2007_sc].
+The retrieval of relevant memories to the attitude depends on many factors, such as the recency of the event, the similarity of the context, and the importance or salience of the memory [@kahana_et-al_2022_ohhum].
+This means that the memories retrieved to contribute to an attitude are quite variable.
+However, to understand where that variability comes from, we must understand the deeper processes influencing how information is encoded and later retrieved.
+This illustrates my need to build upon the reigning models of *pip*.
+Colors may act as a contextual feature that may lead to this variability in how a given set of political information may shape attitudes.
+
+Colors are associative and are affectively encoded [@cimbalo_et-al_1978_jgp].
+When individuals access a memory, they do not just recall an object, but they may recall visual information such as the color of an object [@mehta_zhu_2009_s].
+Due to these features, colors can be processed pre-consciously and very quickly [@mehta_zhu_2009_s].
+As they are affectively encoded, their associations with particular memory contribute to the evaluative component of the memory.
+For example, individuals associate colors like red with anger and arousal [@valdez_mehrabian_1994], whereas individuals associate blue with things like happiness and pleasure [@dandrade_egan_1974_ae].
+This means that colors are compelling as contextual information shaping the subsequent processing and integration of "traditional" forms of political information to construct an attitude.
+As the preference for a particular color correlates with political attitudes [@schloss_palmer_2014_pbr], they may have some causal influence upon political attitudes; rather than just a correlation with them.
+
+According to the literature in affective neuroscience, visual information is processed in various parts of the brain, such as the visual cortex [@goldstein_brockmole_2017_cl].
+These types of processes do not occur in particular areas of the brain as some like to think.
+As attitudes are associative, components of our brain works as this complex highway connecting different types of information.
+As a result, the processing of visual information will activate other areas of the brain and will make associated paths "hot." One such area is the amygdala.
+Neuroscientists believe that as visual information is quickly and subconsciously processed, the amygdala takes and appraises it based on the paths it activated; this generates a simple affective response to such information [@winkielman_et-al_2011_ohsn].
+More complex, categorical emotion occurs later in conscious processing [@winkielman_et-al_2011_ohsn].
+
+To provide a less technical description of the processes occuring here, once politically-relevant visual information is detected, the retina passes it to the brain.
+Once there, the brain attempts to classify the visual information by activating networks of neurons associated with the current information.
+With these activated pathways, the brain also attempts to appraise such information based on quick classification.
+For attitude formation, this implies that, as memories are affectively encoded [@kensinger_fields_2022_ohhum], these memories help areas such as the amygdala to appraise the current information.
+
+These fast affective classifications are valanced rather than the more laborious categorization of specific emotions (e.g., anger, anxiety, fear, happy).
+What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_2000_arps], I conceptualize affect as a more extensive system that considers emotion only as a conscious classification process that occurs later than initial valanced appraisals of an object [@sander_2013_chhan; @ralph_anderson_2018_pup].
+That is, emotion -- the complex classification of appraisals -- is a conscious component of affect.
+The pre-conscious process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_et-al_2011_ohsn; @dror_2017_er].
+
+The pre-conscious appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_et-al_2011_jop; @ralph_anderson_2018_pup].
+This has evolutionary roots for survival [@ralph_anderson_2018_pup; @parker_2003_p].
+While affective appraisals can lead to complex motivations, such as anxiety leading to motivations for information seeking [@marcus_2000_arps], affective appraisals are valanced and are more automatic [@winkielman_et-al_2011_ohsn].
+These affective appraisals lead to a desire to either retract or engage more with the object [@valentino_et-al_2011_jop].
+The snap judgment resulting from the automatic processing of politically relevant visual information should likely lead to an affective response that motivates either a desire to engage more with the object or disengage.
+
+While the visual information may encourage a particular immediate reaction to engage or disengage from the information, subsequent information processing and more conscious processing adjusts this initial appraisal generated by the snap judgment [@kensinger_fields_2022_ohhum].
+While subsequent information may amend one's snap-judgment, the snap-judgment nevertheless influences the processing of subsequent information by activating particular paths, which is later encoded as associated with the object as it converts to a memory [@lodge_taber_2013_cup; @kensinger_fields_2022_ohhum].
+
+Beyond a motivated backlash effect, the popular application of motivated reasoning to political science finds evidence suggesting that individuals take more time processing information that runs against their pre-existing preferences [@taber_lodge_2006_ajps].
+The explanation for this is that people are finding ways to come up with counterarguments to such information.
+Therefore, it is possible that we may expect that those interacting with visual information of a political party for which they disagree with spend more time looking at those objects.
+
+@fig-snap-judgement-model presents an illustration of the snap-judgment model.
+
+```{mermaid}
+%%| label: fig-snap-judgement-model
+%%| fig-cap: Snap judgement model
+%%| fig-width: 6
+%%{init: {'theme':'base', 'themeVariables':{'primaryColor':'#ffffff', 'primaryBorderColor': '#000000'}}}%%
+graph TD;
+    A[Detection of politically-relevant visual information] --> B(Activation of retrieval mechanism);
+    B --> C[Memory and contiguous paths hot];
+    C --> D[Appraisal of hot autonomous nervous system];
+    D --> E1[Negative Valence];
+    D --> E2[Positive Valence];
+    E1 --> F1[Disengagement motivation];
+    E2 --> F2[Attention activated];
+    F1 --> |Neg. new information| G1[Encoded as negative];
+    F1 --> |Pos. new information| G2[Encoded as positive];
+    F2 --> |Neg. new information| G3[Encoded as negative];
+    F2 --> |Pos. new information| G4[Encoded as positive];
+    G1 --> H1[Strengthens negative path];
+    G2 --> H2[Weakens negative path];
+    G3 --> H3[Weakens positive path];
+    G4 --> H4[Strengthens positive path];
+    G2 --> |forgotten| H1;
+    H2 --> |reinforced| G2;
+    H3 --> |reinforced| G3;
+    G3 --> |forgotten| H4;
+```
+
+Let me illustrate the snap-judgment model with a common experience for residents of the United States.
+Say you are driving down a highway.
+At 65 miles an hour, you are traveling at about 95 feet per second at this speed.
+You split your attention.
+You focus your eyes on the conditions of the road in front of you, the cars in front of you, and the rear-view mirror where your kids are either dropping food in the crevice between the seats or trying to grab your attention.
+Out of the corner of your eye, you see a sign.
+It is not a road sign because it is not on the familiar white or yellow background with black lettering.
+It is election season.
+You correctly infer that it is a political yard sign.
+In this split second, you notice the sign's color and may see a name: Mitch McConnell.
+You now are racking your brain to think about who that is.
+If you are politically engaged, you might come to that recognition of the name quickly or it may take you significantly longer if you are less politically engaged [see @kahana_et-al_2022_ohhum].
+You figure out that they are a Republican politician.
+You may have come to this with the help of the fact that every year you have seen yard signs on this stretch of highway.
+You know that when you see those electoral maps pop up on your news app on your phone that the electoral forecasts always represent Republican support with red and blue for Democrats.
+Once you have figured out who this person is, with the help of this other information, you react: "ugh, that guy is too loyal to Trump" or "yeah!
+He's loyal to Trump".
+You've expressed a political attitude.
+
+What the snap-judgment model predicts is happening in your head is that as soon as the light that bounces off the sign to produce a particular wavelength hits your eyes, your brain is already trying to make sense of this information.
+This is a valuable tool for survival that biology has optimized for millions of years [@parker_2003_p].
+Rather than slowly processing the visual information and finding yourself in the jaws of a predator or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and subconsciously [@newell_1990_hup].
+To make sense of such information, it accesses familiar information similar to what it is currently attempting to process for efficiency [@kahana_et-al_2022_ohhum].
+This is accessing memories and contains valanced information [@kensinger_fields_2022_ohhum]: should I avoid this, or is it pleasant?
+Once the brain has finished such processing, it can pass its prediction to your conscious memory.
+Once you form a reflex of avoid or approach, this opens up space for your brain to process the more complex information: to take the patterns of the light as shapes that construct symbols and letters.
+This comes later because this information not only requires access to information about what it *is* but also what it *means*; once you understand what it means, you have the information necessary to evaluate it.
+
+The snap-judgment model predicts that you first process the colors of the yard sign.
+You access associative memory to figure out what those particular wavelengths represent: red, white, blue?
+As these colors are associated with different emotional states [see @cimbalo_et-al_1978_jgp] and the resulting behavioral consequences, your brain starts sending signals to the rest of your body to prepare it to react [see @sander_2013_chhan; @dror_2017_er].
+You now need to figure out what the rest of that information was.
+What were the patterns of that light?
+It appears that there were some white letters on the sign.
+There was an "E," a "L," an "E," a "C," and a "T." That creates the word "ELECT." Meaning to vote for.
+There were some more letters on the sign: an "M," an "I," a "T," a "C," and an "H." A name.
+The full name is "Mitch McConnell".
+Since it is about politics, it must be a politician named Mitch McConnell.
+Now imagine the information was the same, except the color was blue.
+You may take more time to figure out how that Mitch McConnell person is and come to your reaction to seeing their yard sign.
+This is because, without the color red, you first are thinking about Democrats who are named Mitch McConnell.
+Only when you come up empty on your mental Rolodex do you figure out that it is the Republican Mitch McConnell.
+
+How do you react to the color and then to the name?
+Social groupings are not simply abstract concepts invented by social psychologists; our neurobiology reflects them.
+For example, researchers find activation of parts of the brain, such as the anterior insula, when we see someone in our social group outperformed by someone from the out-group [see @zink_barter_2012_ohsn].
+The anterior insula activity is associated with physical and emotional pain, not just for ourselves but also for others [@adolphs_janowski_2011_ohsn].
+Others have also observed that when seeing someone part of a high-status social group, there is an increase in activity in the sensorimotor cortex and supplementary motor area, indicating more activity in the areas of the brain that encourage movement [@zink_et-al_2008_n].
+Visual information about someone in your social group speeds up processing, is more salient, and demands more attention than visual information about an object outside your social group [@zink_barter_2012_ohsn].
+
+There is significant evidence supporting the theory that our partisan identification reflects more than just our attitudes about politics but a social identity [see @campbell_et-al_1960_jws; @mason_2018_cup] that guides our attitudes [see @achen_bartels_2016_pup; @white_et-al_2014_apsr; also @bullock_2011_apsr].
+As our political attitudes reflect shared views among co-partisans [@pickup_et-al_2020_pb], the congruence between political information and our partisan identification influences our reactions to such political information.
+This means that the visual information we glean from politics will likely motivate those neurological features of social groups and explain the resulting behavioral manifestations reacting to such information.
+That information is also likely to be processed at different rates as well.
+That is, while visual information carries general affective associations, we should also expect associations between politically-relevant colors with partisan identification.
 
@@
 +--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
-| $H_2$        | Red is associated with Republicans and Blue is associated with Democrats                                                                            |
+| $H_2$        | Colors shape perceptions of candidate based on partisan associations                                                                                |
 +--------------+-----------------------------------------------------------------------------------------------------------------------------------------------------+
@@
 : Summary of hypotheses {#tbl-hypotheses}
+
+From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that these colors that they notice shape perceptions about the person and ideological symbol represented in the branding -- meaning that they express different levels of preference for receiving more information that is similar to what they saw and their levels of preference for supporting such a campaign ($H_{2}$); that the consistency of information explains more positive perceptions -- simple visual information with more complex "traditional" information ($H_{3}$); this positive and consistent information is processed quicker than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) in line with their primary objective of reelection [@fenno_1973_lb; @mayhew_1974_yup].
+A summary of these hypotheses are included in @tbl-hypotheses.
 

### 2023-06-21 chapter_3/src/slides/slides.qmd

@@
     transition: slide
-    scrollable: false
+    scrollable: true
     incremental: true
@@
 #| label: setup-block
-
 # Load some nifty functions
@@
   ../../../chapter_2/src/R/predicted_prob_bar[...]
+  , ../prr/R/plot[...]
 )
@@
 )
+# Load simulation results
+load(
+  file = "../../data/temp/prr/fitted_model_1.RData"
+)
+load(
+  file = "../../data/temp/prr/fitted_model_2.RData"
+)
+load(
+  file = "../../data/temp/prr/fitted_model_2_alt.RData"
+)
 ```
@@
 # Background
-
-::: footer
-:::
----
 
@@
   , x_axis = "trial_1_red_stimuli"
+  , treatment = "Red"
 )
@@
 :::
+
 ---
@@
 3. Sensory and affective information is often encoded in memories [@kensinger_fields_2022_ohhum].
+
+::: footer
+:::
+
+---
+
 4. Memories are a complex network [@kahana_et-al_2022_ohhum].
@@
 
+# Hypotheses
+
+1. People notice the color of clothing a potential conversation partner is wearing.
+2. When primed to think about politics, people are less likely to want to have a conversation with someone wearing a blue shirt if they are a Republican and a red shirt if they are a Democrat.
+
+::: footer
+:::
+
+---
+
+3.
+When learning more information about someone that fits with our initial impression, our motivation of engagement or disengagement is stronger than if the information were incongruent with our initial impressions.
+4.
+When learning more information about someone that does not fit with our initial impression, the new information can shift our motivations to have the conversation or to disengage.
+However, this difference is smaller than if both forms of information were congruent.
+
+::: footer
+:::
+
 # Proposed research design
+
+::: footer
+:::
 
@@
 : $2 \times 2$ factorial design {#tbl-study-1}
+
+::: {.notes}
+- Here I want to test a couple of things.
+  - does color factor into whether people are willing to have a conversation with someone?
+  - does this matter under different circumstances?
+  - and do Republicans want to talk to those wearing red more than Democrats; while Democrats want to talk to those wearing blue more than Republicans?
+:::
 
@@
 
+::: {.notes}
+- Want to check out a couple other things here:
+  - does the snap-judgment someone makes have downstream effects, even when given more traditionally considered forms of political information?
+  - does new information shift our views? Do we double down? under what circumstances?
+:::
+
+::: footer
+:::
+
+# Sensitivity of conclusions to sample size, research design, and modeling strategies
+
+::: {.notes}
+- the results of a bayesian model are kind of like an average of your prior beliefs and your data that you have on hand
+  - what this means is that I start off with a belief about how things are, then add data to see if that distribution changes
+- for hypothesis testing, I'll start off by saying that the most likely outcome is that my hypotheses are wrong and that the effect is likely 0.
+  - though, I'll allow for some uncertainty to be expressed by saying that there is some amount of probability that the effect could be positive or negative, but most effects are going to be pretty small substantively speaking.
+- This is reflected with a normally distributed prior and a standard deviation of 1
+- Now my task is to see whether, given a DGP that I know how it looks in the population, my particular research design and modeling strategies can produce a posterior destribution that help me  conclude that the effects are not zero when my DGP says that they aren't zero.
+That is, can my research design and modeling strategies bring me to the correct conclusions and provide evidence in support of my hypotheses as opposed to the null hypothesis?
+:::
+
+::: footer
+:::
+
+---
+
+$$
+\begin{align}
+\text{Age} = uniform(18, 85) \\
+\text{Gender} = bernoulli(0.5) \\
+\text{Education} = normal(-0.1 * Age + 0.1 * gender + 
+  \\ 14 + normal(0, 1), 0.5) \\
+\end{align}
+$$
+
+$$
+\begin{align}
+\text{Income} = normal(2 * age + 0.7 * gender + \\ 
+40000 + normal(0, 1), 200000) \\
+\text{Conflict Avoidant (latent)} = normal(0.3 * gender + \\ 
+2.4 + normal(0, 1)) \\
+\end{align}
+$$
+
+$$
+\begin{align}
+\text{Party identification (latent)} = normal(0.4 * age - \\ 
+0.6 * gender + 0.5 * income + normal(0, 1)) \\
+\text{attention (latent)} = normal(0.5 * age - \\ 
+0.3 * gender + 0.1 * income + normal(0, 1))
+\end{align}
+$$
+
+$$
+\begin{align}
+\text{treatment}_{prime} = bernoulli(0.5) \\
+\text{treatment}_{blue} = bernoulli(0.5) \\
+\end{align}
+$$
+$$
+\begin{align}
+\text{notice} = bernoulli(1 * prime) \\
+\text{willing (latent)} = normal(0.1 * treatment_{prime} + 
+\\ 0.1 * treatment_{blue} + 0.1 * \text{party identification} + 
+\\ 0.5 * treatment_{prime} * treatment_{blue} * \text{party identification} + 
+\\ normal(0, 1))
+\end{align}
+$$
+
+::: {.notes}
+- I start by defining a population that is one-hundred-thousand strong
+- I randomly sample from this population produced by the data generating process here
+  - I do it at different sample sizes: 200, 400, 600, 800
+  - For each of these sample sizes, I get 100 samples each
+:::
+
+::: footer
+:::
+
+## Fitting the models on the simulated data
+
+::: footer
+:::
+
+### Model 1
+
+$$
+\begin{align}
+Pr(notice_i = 1) \sim logistic(\phi_i + \alpha) \\
+\phi_i = \beta_1 * treatment_{prime_i} \\
+\beta_1 \sim Normal(0, 1) \\
+\alpha_i \sim student(0,3,2.5)
+\end{align}
+$$
+
+::: {.notes}
+- This model is fitted on each sample for each sample size.
+- So 400 times
+:::
+::: footer
+:::
+
+### Model 2
+
+$$
+\begin{align}
+Willing_i \sim CDF(logistic(\phi_i + \alpha)) \\
+\phi_i = \beta_1 * treatment_{blue_i} + \beta_2 * treatment_{prime_i} + \\ \beta_3 * treatment_{blue_i} * treatment_{prime_i} + \\
+\beta_4 * gender_i + \beta_5 * education_i + \\ \beta_6 * income_i + \beta_7 * conflict_i + \beta_8 * attention_i \\
+\beta_j \sim Normal(0, 1) \\
+\alpha_j \sim student(0, 3, 2.5)
+\end{align}
+$$
+
+::: {.notes}
+- Here, I do a split sample version of the model. 
+- One of these for Republicans and one of these for Democrats.
+- I fit these models for each sub sample for each sample size.
+- 800 times
+:::
+::: footer
+:::
+
+### Model 2 (alternate)
+
+$$
+\begin{align}
+Willing_i \sim CDF(logistic(\phi_i + \alpha)) \\
+\phi_i = \beta_1 * treatment_{blue_i} + \\ \beta_2 * treatment_{prime_i} + \beta_3 * \text{Party ID}_i + \\
+\beta_4 * treatment_{blue_i} * treatment_{prime_i} * \text{Party ID}_i + \\
+\beta_4 * gender_i + \beta_5 * education_i + \\ \beta_6 * income_i + \beta_7 * conflict_i + \beta_8 * attention_i \\
+\beta_j \sim Normal(0, 1) \\
+\alpha_j \sim student(0, 3, 2.5)
+\end{align}
+$$
+
+::: {.notes}
+- Here's an alternative specification. Instead of doing a split sample, I just do the triple interaction.
+- I fit one of these on each sample for each sample size.
+- 400 times
+:::
+::: footer
+:::
+
+## Performance
+
+::: {.notes}
+- Know that none of the parameters are zero.
+- Though they are super small, so this is a pretty conservative test.
+- Look at the 95% credible intervals
+  - If the credible overlaps with zero, record a value of 0. If not, record value of 1.
+:::
+::: footer
+:::
+
+### Model 1
+```{r}
+#| label: fig-true-positive-study-1-model-1
+#| fig-cap: True positive rate from simulations - Model 1
+#| layout-nrow: 1
+plot_study_1_model_1 <- true_positive_plot(data_frame = df_fitted_samples_model_1)
+plot_study_1_model_1[[1]]
+```
+
+::: footer
+:::
+
+### Model 2
+
+```{r}
+#| label: fig-true-positive-study-1-model-2-alt
+#| fig-cap: True positive rate from simulations - Model 2, Split sample
+#| layout-ncol: 2
+#| fig-subcap:
+#|   - $\hat{\beta}_1$
+#|   - $\hat{\beta}_2$
+#|   - $\hat{\beta}_3$
+
+plot_study_1_model_2_alt <- true_positive_plot(data_frame = df_fitted_samples_model_2_alt)
+plot_study_1_model_2_alt[[1]]
+plot_study_1_model_2_alt[[2]]
+plot_study_1_model_2_alt[[3]]
+```
+::: footer
+:::
+
+---
+
+```{r}
+#| label: fig-true-positive-study-1-model-2
+#| fig-cap: True positive rate from simulations - Model 2
+#| layout-ncol: 2
+#| fig-subcap:
+#|   - $\hat{\beta}_1$
+#|   - $\hat{\beta}_2$
+#|   - $\hat{\beta}_3$
+#|   - $\hat{\beta}_4$
+plot_study_1_model_2 <- true_positive_plot(data_frame = df_fitted_samples_model_2)
+plot_study_1_model_2[[1]]
+plot_study_1_model_2[[2]]
+plot_study_1_model_2[[3]]
+plot_study_1_model_2[[4]]
+```
+
 ::: footer

### 2023-06-23 chapter_2/src/appendix.qmd
study 2 models done for CH2git add -A! Just need to write

@@
 ```
+
+## Hypothesis 5
+
+For $H_5$, I am interested in examining whether or not districts that lean towards one party more than the other have candidates use more of the color in line with the party that has a historical advantage and less of the color for the party that tends to suffer electorally speaking.
+
+### Models
+
+As I mention in the main text of the book, I note that I regress the 5-year rolling average of the democratic vote share in a state upon the proportion of the color red and blue on the yard signs downloaded from the Center for American Political Design.
+The outcome is a continous and bounded variable between the value of 0 and 1.
+I note in the main text that I use a ordered beta regression, but here I provide more specifics.
+As the outcome is continuous but bounded between 0 and 1, treating the outcome variable as a continous variable with no finite bounding as I would with a OLS would be inappropriate.
+To ensure that I am using the most appropriate estimator to explain the outcome of interest, I elect to use an ordered beta regression.
+Beta regression models are a type of distributional model that essentially tries to model the distribution of the outcome variable.
+The standard beta regression model can fit models where the outcome is (0, 1).
+However, my outcome is [0, 1).
+I could elect to use a zero-inflated beta regression which would allow me to appropriately model this outcome.
+However, @kubinec_2022_pa demonstrates that the ordered beta regression is a much more efficient and accurate (in terms of a number of various metrics) approach to dealing with outcomes that can equal either 0 or 1.
+
+The default priors for $\beta_i$ is $N(0, 5)$ in the $ordbetareg$ [@kubinec_2022_pa] package that I use to fit the model.
+However, I receive warnings indicating that there are divergent transitions.
+For HMC, divergent transitions indicate that the sampler is having problems with the curvature of your posterior distribution.
+As I note in the main text of the book, I am using a multilevel model that includes a partially pooled parameter for the districts and use two non-pooled parameters for the state and the election year.
+This is a pretty complex problem.
+Especially givent the estimator that I am using here.
+More troubling still is that my $\hat{R}$ values are not equal to 1 for either model.
+These two things together suggest that there is a pretty serious problem and that my posterior distributions are quite unstable.
+
+To try to fix this issue, I adjust the prior for $\beta_1$ to $N(0, 2)$.
+While I still receive a warning about divergences in both models, the number of them drops down to about 30 out of 4000.
+Additionally the $\hat{R}$ values are at 1.
+Together, these tell me that these priors likely helped the models quite a bit and feel more confident in the stability of my model.
+@tbl-hypothesis-5 presents the results of this second specification of the model.
+
+```{r}
+#| label: tbl-hypothesis-5
+#| tbl-cap: The effect of democratic vote share on color choices for yard sign
+
+names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
+modelsummary(
+  list_fitted[["h_5"]]
+  , stat = "conf.int"
+  , conf_level = 0.9
+  , metrics = c("n.obs", "RMSE")
+  , coef_map = c(
+    "b_intercept" = "Intercept"
+    , "b_dem_vote_share" = "Democratic vote share (%)"
+  )
+)
+
+```

### 2023-06-23 chapter_2/src/manuscript.qmd
study 2 models done for CH2git add -A! Just need to write

@@
 ## Study 2
+
+[Study 1](#sec-study-1) presents evidence in support of the idea that the colors red and blue matter to politics -- they convey information to people.
+Second, the evidence from [Study 1](#sec-study-1) suggests that the information can shape the attitudes of voters.
+What remains unclear is whether or not these patterns have large enough impacts that it shapes how campaigns market themselves.
+In informal conversations with a campaign marketing firm which specializes in campaign marketing, I was told:
+
+> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
+We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
+> The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right etc.
+
+While this was good information to hear that seemed to align with what I found in [Study 1](#sec-study-1), I wasn't sure how much this actually influenced strategy. It appears it does, however.
+
+> Beyond that,  I generally suggest that considering associations with party is generally a good place to start.
+For example, if you're running in a Democratic primary and that's the race that's going to most likely decide who ultimately gets elected, then blues are a good place to start.
+
+While there is some qualification in that there are other colors that can be useful beyond red and blue.
+The value of colors associated with a particular place can be a way for candidates to communicate attachment to the district and to the constituents.
+Though, there is a preference for campaigns to use as few colors as possible to save on costs - simpler is better.
+What particularly stood out to me was when I was told
+
+> You want voters to be able to look at whatever collateral you have, including lawn signs, and be able to identify that it's your material without ever having to read it.
+If you do one thing long enough, voters tend to start to associate specific color schemes with specific candidates.
+
+So, unsurprisingly, campaigns care about how they market themselves.
+And it seems as though campaigns want to tap into quick and efficient information processing for voters and potential voters.
+However, as noted during the conversation
+
+> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
+
+The goal for the second peice of empirical evidence in the chapter is to explore whether there is any evidence not from the "lab" suggesting that campaigns use the colors red and blue systematically.
+If the color of a yard sign does indeed matter and its electoral effects depend on the perceptions of potential voters, we should expect that campaigns are less likely to place yard signs with a large amount of Red or Blue in more moderate districts.
+However, in districts where there is a strong partisan base, we should expect that the candidate of the popular party will use the party's color more, while the disadvantaged candidate will use their party's color less as a way to either play up or down their loyalty to their party.
+
+First, I collect data from the MIT Election Lab that reports the electoral results of House of Representative elections from the years 1970-2020.
+The data here tell me which candidate got how many votes in each House election across the United States.
+With this data, I calculate the rolling 5-year average of the Democratic party's vote share for each district.
+
+Next, I download around 900 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design.
+I use the `OpenCV` library from python to examine the proportion of the colors near the "Republican Red"^[lower values: 93, 9, 12; upper values 236, 69, 75] and "Democratic Blue"^[lower values: 0, 18, 26; upper values: 102, 212, 255] in each of these yard signs.
+
+For example, I downloaded the GOP logo used on their official Twitter account during the 2022 midterm election cycle.
+What `OpenCV` does is it loads the image and converts it to a three-dimensional `numpy` array that contains the GBR (reverse of RBG) values for the pixels in the image.
+I standardize the image to be 224 $\times$ 224 pixels.
+The color is trained to detect the range of Republican Red and Democrat Blue colors.
+Once trained, the computer detects the pixels that do not contain values within the pre-specified range and converts those pixels to be black.
+
+```{python}
+#| label: example detection
+#| echo: false
+
+from sys import path # for path management
+from cv2 import imread, imwrite # for color detection
+    #* user-defined
+#path.append("../")
+from PY.helper import colorDetector
+
+# Define colors to detect
+    #* White
+        #** Not defined. Default for colorDetector()
+    #* Red
+republican_red = [232, 27, 35] # target color
+red_lower = [93, 9, 12] # lower end of spectrum for red
+red_higher = [237, 69, 75] # higher end of spectrum for red
+
+# Load gop image to read
+img = imread("./assets/img/gop_2022.png")
+
+# Detect colors
+percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
+
+transformed= imwrite("../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
+
+masked= imwrite("../data/temp/study_2/gop_2022_detected.png", result) # save masked image
+```
+
+::: {#fig-color-detection-example layout-ncol="2"}
+![Resized original image](../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
+
+![Masked](../data/temp/study_2/gop_2022_detected.png){#fig-masked}
+
+Detecting colors in the GOP logo
+:::
+
+I then extract the non-black pixels in the array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$]
+
+```{python}
+#| output: asis
+# Print calculated percentage of example
+print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
+```
+
+With the data on the proportion of each of the yard signs using the red and blue colors, I merge this data with the MIT Election Lab Data.
+This leaves me with data from the House elections between 2016 and 2020.
+While the data are limited in the number of elections it reflects, it allows me to hold the district composition constant as redistricting occurs after the Census every 10 years.
+However, each election cycle is different and are often different depending on current events.
+With these data, I estimate a mixed effect model with partial pooling of the intercepts at the district level and no pooling of the intercepts for the election year level.
+For less technical readers, this allows me to explore whether the district and within election year differences between choices in yard sign color use.
+What I am trying to do with this analysis is explore whether or not campaigns in districts that are more partisan will use more red or blue while campaigns in districts that are more moderate will use fewer of those traditionally partisan colors.
+
+```{r}
+#| label: fig-study-2-pred
+#| layout-ncol: 1
+#| fig-cap: More blue on the yard signs in Democratic strongholds
+#| fig-subcap:
+#|   - Proportion of red
+#|   - Proportion of blue
+red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["red"]]
+  , treatment = "Red"
+  , hypothesis = "H5"
+)
+blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["blue"]]
+  , treatment = "Blue"
+  , hypothesis = "H5"
+)
+red
+blue
+```

### 2023-06-23 chapter_2/src/.vdoc.py

@@ -1,0 +1,572 @@
+# type: ignore
+# flake8: noqa
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
[…]

### 2023-06-23 chapter_2/src/R/predicted_prob_bar.R

@@ -20,20 +20,19 @@ predicted_prob_bar <- function(
   , x_axis
   , treatment = "Red"
   , hypothesis = "H2"
-  , level = 0.95
+  , level = 0.90
   , x_label = "Color of yard sign"
   , y_label = "Pr(Party of candidate)"
   , legend_title = "Party of candidate"
 ) {
-  # Calculate the predicted probabilities for the model
-  df_pred_prob <- marginaleffects::predictions(
-    model = fitted_model
-    , conf_level = level
-  )|>
-  data.table::as.data.table() # convert it to a data.table
   # If this is for a ordered logit, I'll have to do some stacked
-  # barplots
   if (hypothesis == "H2") {
+    #* Calculate the predicted probabilities for the model
+    df_pred_prob <- marginaleffects::predictions(
+      model = fitted_model
+      , conf_level = level
+    )|>
+    data.table::as.data.table() # convert it to a data.table
     #* Need to clean up the pred prob data.frame some
     df_pred_prob_cleaned <- df_pred_prob[
       #** aggregate the estimate, conf.low, and conf.high columns with
@@ -132,15 +131,78 @@ predicted_prob_bar <- function(
         , linetype = legend_title
         , fill = legend_title
       ) +
-      ggplot2::theme_minimal() 
-    # If it is a logistic regression with binary outcome
+      ggplot2::theme_minimal()
+  # If this is for a ordered beta regression
+  } else if (hypothesis == "H5") {
+    df_pred_prob <- marginaleffects::predictions(
+      model = fitted_model
+      , newdata = marginaleffects::datagrid(
+        model = fitted_model
+        , dem_vote_share = c(
+          0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9
+        )
+        , year = c(
+          2018, 2020, 2022
+        )
+      )
+      , re_formula = NA
+    ) |>
+    marginaleffects::posterior_draws()
+    #* make predictions
+      #** define plot
+    plot <- ggplot2::ggplot(
+      data = df_pred_prob
+      , ggplot2::aes(
+        x = dem_vote_share
+        , y = draw
+      )
+    ) +
+      #** plot the change in predicted values
+    tidybayes::stat_lineribbon(
+      .width = level
+      , alpha = 0.6
+    ) +
+      #** split this up by year
+    ggplot2::facet_wrap(
+      ~ year
+      , ncol = 2
+    ) +
[…]

### 2023-06-23 chapter_2/src/models/study_1_fitting.R

@@ -9,31 +9,50 @@
         #** dcr
 
 # Setup
-    #* set working directory
+  #* set seed
+set.seed(12102022)
+  #* set working directory
 setwd("./chapter_2/src")
-    #* execute cleaning script
+  #* execute cleaning script
 source("./eda/study_1/cleaning.R")
-    #* load helpful functions
+  #* load in cleaned study-2 data 
+  #* (need to run each python script individually)
+df_study_2 <- read.csv("../data/clean/study_2.csv") |>
+  as.data.table()
+  #* convert state_district and year variables  to factors
+df_study_2 <- df_study_2[
+  , year := tstrsplit(year, "-", keep = 1)
+][
+  , year := as.numeric(year)
+][
+  , state_district := factor(state_district)
+][
+  , blue_prop := blue_percent/100
+][
+  , red_prop := red_percent/100
+]
+  #* load helpful functions
 box::use(
-    data.table[...]
-    , brms[...]
+  data.table[...]
+  , brms[...]
+  , ordbetareg[...]
 )
     #* make an empty model list object
 list_fitted <- list(
-    h_1 = list()
-    , h_2 = list()
-    , h_2a = list()
-    , h_3 = list()
-    , h_4 = list()
-    , h_5 = list()
+  h_1 = list()
+  , h_2 = list()
+  , h_2a = list()
+  , h_3 = list()
+  , h_4 = list()
+  , h_5 = list()
 )
 list_ppc <- list(
-    h_1 = list()
-    , h_2 = list()
-    , h_2a = list()
-    , h_3 = list()
-    , h_4 = list()
-    , h_5 = list()
+  h_1 = list()
+  , h_2 = list()
+  , h_2a = list()
+  , h_3 = list()
+  , h_4 = list()
+  , h_5 = list()
 )
 
 # Hypothesis 1
@@ -219,6 +238,35 @@ list_ppc[["h_4"]][["red"]] <- pp_check(
 )
 list_ppc[["h_4"]][["blue"]] <- pp_check(
   list_fitted[["h_4"]][["blue"]]
+)
+# Hypothesis 5
+  #* Fit models
+list_fitted[["h_5"]][["red"]] <- ordbetareg(
+  formula = red_prop ~ dem_vote_share + (1 | state + district)
+  , data = df_study_2
+  , threads = 4
+  , backend = "cmdstanr"
+  , control = list(
[…]

### 2023-06-23 chapter_2/src/appendix.qmd
oops, forgot ppc's

@@
 
+<!-- 
+NOTE TO SELF
+
+NEED TO REWRITE SOME OF THIS TO ACCOUNT FOR BETTER PERFORMANCE AFTER LOCATION-FXS
+-->
+
 As I mention in the main text of the book, I note that I regress the 5-year rolling average of the democratic vote share in a state upon the proportion of the color red and blue on the yard signs downloaded from the Center for American Political Design.
@@
 )
+```
 
+### Posterior predictive checks
+
+```{r}
+#| label: fig-hypothesis-5-ppc
+#| tbl-cap: Posterior Predictive checks for $H_5$
+
+list_ppc[["h_5"]][["red"]]
+list_ppc[["h_5"]][["blue"]]
 ```

### 2023-06-23 chapter_2/src/appendix.qmd
fix weird ppc graph thing

@@
 #| label: fig-hypothesis-5-ppc
-#| tbl-cap: Posterior Predictive checks for $H_5$
+#| layout-ncol: 2
+#| fig-cap: Posterior Predictive checks for $H_5$
+#| fig-subcap:
+#|   - Proportion of yard signs red
+#|   - Proprotion of yard signs blue
 
-list_ppc[["h_5"]][["red"]]
-list_ppc[["h_5"]][["blue"]]
+list_ppc[["h_5"]][["red"]]$continuous
+list_ppc[["h_5"]][["blue"]]$continuous
 ```

### 2023-06-24 chapter_2/src/R/predicted_prob_bar.R
draft sent to advisor. Sweet

@@ -141,9 +141,6 @@ predicted_prob_bar <- function(
         , dem_vote_share = c(
           0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9
         )
-        , year = c(
-          2018, 2020, 2022
-        )
       )
       , re_formula = NA
     ) |>
@@ -161,11 +158,6 @@ predicted_prob_bar <- function(
     tidybayes::stat_lineribbon(
       .width = level
       , alpha = 0.6
-    ) +
-      #** split this up by year
-    ggplot2::facet_wrap(
-      ~ year
-      , ncol = 2
     ) +
       #** use the minimal theme
     ggplot2::theme_minimal() +

### 2023-06-24 chapter_2/src/models/study_1_fitting.R

@@ -242,7 +242,7 @@ list_ppc[["h_4"]][["blue"]] <- pp_check(
 # Hypothesis 5
   #* Fit models
 list_fitted[["h_5"]][["red"]] <- ordbetareg(
-  formula = red_prop ~ dem_vote_share + (1 | state + district)
+  formula = red_prop ~ dem_vote_share + (1 | state_district)
   , data = df_study_2
   , threads = 4
   , backend = "cmdstanr"
@@ -252,7 +252,7 @@ list_fitted[["h_5"]][["red"]] <- ordbetareg(
   , coef_prior_SD = 2
 )
 list_fitted[["h_5"]][["blue"]] <- ordbetareg(
-  formula = blue_prop ~ dem_vote_share + (1 | state + district)
+  formula = blue_prop ~ dem_vote_share + (1 | state_district)
   , data = df_study_2
   , threads = 4
   , backend = "cmdstanr"

### 2023-06-24 chapter_2/src/appendix.qmd

@@
 ```
+
+## A note about discrepancies between the main text and the pre-registered report
+
+I posted a pre-registration of my hypotheses [on OSF.](https://osf.io/e9gk8/) The pre-registration allows me to offer transparency about what I expect to find before I analyze any data.
+This reduces the amount of post-hoc rationalization of any findings pulled from the data.
+The pre-registered hypotheses are the same as those that are tested here.
+Despite the similarities between my pre-registered hypotheses and research design, there are a few subtle differences between what I pre-registered and what I ended up doing.
+In the spirit of complete transparancy, I wanted to make a note of these differences.
+
+Again, the hypotheses that I pre-registered remain the same as what is presented in the main text.
+The research design also remained the same.
+During the IRB process, I had to make some decisions about space considerations as I was concerned about participants taking longer than the advertised time (6 minutes).
+Due to these concerns, I removed some questions.
+Namely, I no longer asked participants about the color of the yard sign after viewing it nor did I include a battery for political knowledge.
+These were changes that I made during the IRB process, but did not change in my pre-registered report.
+In full transparency, mostly because I forgot to make the update as well as having some issues with Dropbox at the time.
+Removing these questions also had principled reasons.
+First, I did not want to inflate the treatment effect by asking participants to reflect and tell me the color they saw and then report the partisanship of the candidate.
+I wanted to get as close to a snap-judgment as I could get and I wanted to immediately ask participants about the partisanship of the candidate after viewing the yard sign to accomplish this goal.
+For the political knowledge battery, I discuss why I elected to use attention over knowledge in the main text of the chapter.
+But further, the prevailing questions on political knowledge are suspect as they provide factual information that can be googled participants during the study.
+Given the length of time it would take for participants to respond to these additional questions and concerns about what value they provide, I did not include them.
+Those who would like to confirm, I have the IRB materials posted on [my github](https://github.com/DamonCharlesRoberts/color_as_political_information/tree/30508e8f4100c7e19382611fe046ed936c1fdb42/src/assets/irb) which you can see the history of these files.
+
+Another set of discrepancies is some of my modeling strategies.
+As I note in the main text, some of the data from the mouseview exercise are not exactly what I had expected initially.
+I do not have much information about the size of the screen participants had nor do I have precise data for when participants were able to view the yard sign during those 5 seconds that it was up.
+The data for each trial began recording on an instruction screen that I used to standardize cursor starting position and when they finished the trial.
+As there is a lot of variation between when participants stopped viewing the instructions, I can't be sure which cursor movements were during the display of the yard sign.
+Because of the noisiness of the mouseview data, I simplified some of my analyses for $H_1$ and $H_4$.
+
+For $H_5$, I had mentioned that I would include an analysis with a synthetic control.
+However, the district-level data available at the time of writing is not yet available.
+Because of this, I cannot leverage redistricting patterns for better causal identification of the question of whether campaigns respond to district characteristics or if they anticipate them.
+Therefore, I stick with the more descriptive task.
+Relatedly, I had indicated I would use a multilevel model by using intercepts that partially pool at the district level and intercepts that are not pooled at the state level.
+Upon further reflection on this strategy, this seemed inappropriate for the question at hand as I did not have clear expectations about variation within states but rather more generally was asking a question about districts at large.
+Further, I did not specify that I would be using a beta regression for these models so many may read my pre-registration as me implying that I would use ordinary least squares.
+This is totally reasonable.
+However, out of concern with reporting results that are extremely unstable because of poor choice in estimator as I discuss in the main text and later in the appendix, the ordered beta regression provides more stable results that I am comfortable making inferences with.
 
@@
   , statistic = "conf.int"
+  , conf_level = 0.9
   , gof_map = gm 
@@
   , statistic = "conf.int"
+  , conf_level = 0.9
   , gof_map = gm
@@
   )
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , "of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , "of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  , output = "latex"
 )

### 2023-06-24 chapter_2/src/manuscript.qmd
oops, forgot ppc's

@@
 
-Are colors important to politics?
-I argue that they convey information that matters to campaigns and voters.
-People rely on more than information about policy positions to understand politics [see @pietraszewski_et-al_2015_c;@perez_tavits_2022_pup as examples].
-To reduce cognitive load, the affiliation detection system allows for efficient social behavior prediction by associating various cues with a group.
-In politics, associating Black voters with the Democratic party and White voters with the Republican party is one example [@pietraszewski_et-al_2015_c].
-As Americans consistently link the colors red and blue with the Republican and Democratic parties [@elving_2014_npr;@williams_et-al_2022_jomp], as well as their connection to ideology [see @maestre_medero_2022_pr for example], we should explore the degree to which color not only acts as an affiliative cue, but whether it is strong enough to drive individual behavior, and whether it is a strong enough shift to shape electoral strategy.
+Now that I have presented some background and have introduced the snap-judgment model of politically-relevant visual information, this chapter is a first attempt to tackle the question at hand.
+Do colors provide political information that shape attitudes?
+There are two goals that I am hoping to achieve in this chapter.
+The first is to convince the reader that the colors red and blue convey affiliative information.
+Second, that these connections between colors and political groups can shape political outcomes.
 
-As a simple yet ubiquitous piece of visual information, color may have more influence over shaping political views than we have given it credit thus far.
-As visual information is processed automatically and faster than other forms of information [see @ames_et-al_2012_ohsn], in this chapter I argue that it triggers associated neurological pathways and leads us to form a snap-judgment (an attitude without subsequent, more complex, information) that we rely upon for attitudinal and behavioral outcomes.
-Later chapters will explore the degree to which the inclusion of subsequent substantive policy information overrides this snap-judgement.
+This chapter applies the snap-judgment model to a simple case.
+The use of color on yard signs used by campaigns in elections.
+I focus on yard signs as they are a common form of campaign marketing and evidence suggests that they can shape individual behavior [@makse_et-al_2019_oup] and electoral outcomes [@green_et-al_2016_es].
+Additionally, I start by examining the colors red and blue.
+While there are other colors that may provide political information -- black and white for Black Lives Matter and Blue Lives Matter movements, the overarching goal of this book is to lay the foundation for a larger research agenda in visual political psychology [see @bucy_joo_2021_ijpp].
+Without such foundations, we are studying complex cases and circumstances upon assumptions without a grasp of how, and if they even do, occur in the cases that might seem trivial to some.
+While there indeed is empirical and experiential evidence suggesting that the Republicans use the color red and Democrats use the color blue [@schloss_palmer_2014_pbr;@williams_et-al_2022_jomp], there is yet to be a theoretical framework that explains how these connections happen at the individual level.
+It may also be unsatisfying that I do not address *how* these connections came about.
+While the connections between Republicans with the color red and Democrats with the color blue seemed to quicken after the 2000 Presidential election where news networks covering the election began to consistently use those colors [@elving_2014_npr], it is not clear if this was a deliberate choice or whether this was yet another symptom of an increasingly polarized public who just want easily digestable information about politics so they can move on to other matters in their lives.
+An undertaking to address such a question is for a different book, perhaps.
 
 To give a preview for this chapter, I propose two studies to explore the claims I make in this chapter.
-Yard signs are a simple yet effective source of campaign branding for political candidates.
-They shape the attitudes of those who view them [@makse_et-al_2019_oup], and have enough of an individual-level effect that they shape aggregate attitudes in the form of electoral outcomes [@green_et-al_2016_es].
+Yard signs are a simple yet effective source of campaign branding for political candidates as they convey information that is often useful for voters -- partisanship [@campbell_et-al_1960_jws].
 As yard signs are a simple and static form of campaign advertising, they cannot rely heavily on more complicated forms of information.
 However, one form of information they rely on and vary in is their color.
-With these characteristics, yard signs are an ideal candidate both from a statistical standpoint and also substantive.
+With these characteristics, yard signs are an ideal candidate both from a statistical standpoint and also substantive for an experimental test of my claims in this chapter.
 From a statistical standpoint, as they are static forms of party branding they have fewer moving parts, which help isolate the effect that color has on shaping attitudes.
@@
 Voters support candidates who signal strong allegiance to the party to increase their chances for electoral success [@utych_2020_es] and the parties are motivated to distinguish themselves [@lee_2009;@clifford_2020_pb] as a result of their high levels of ideological and affective polarization [@dietrich_2021_pa;@enders_2021_jop].
+Again, to tease out the direction of blame is more appropriate for another time.
 
-From the first study, I find that individuals do shift their perceptions of political candidates in response to the use of the colors red and blue, they consistently and strongly associate Republicans with the color red and Democrats with the color blue, and their willingness to vote for a candidate can be dramatically different depending on whether the color used aligns with the individual's partisan identification.
+In the first study, I find that individuals do shift their perceptions of political candidates in response to the use of the colors red and blue, they consistently and strongly associate Republicans with the color red and Democrats with the color blue, and their willingness to vote for a candidate can be dramatically different depending on whether the color used aligns with the individual's partisan identification.
+The second study suggests that candidates in districts where Democrats have a higher vote share use more blue on their yard signs while also using less red.
+The implications of this are that the colors red and blue convey political information.
+More generally, I suspect other colors and more complex forms of visual information such as symbols are capable of conveying political information as well.
+Perhaps most interesting among these results is that the color red and blue alone can make individuals willing to vote for a candidate.
+The association between the colors red and blue are strong enough that individuals express a willingness to cast a vote for a candidate based on the color of their yard sign without confirming any of their policy stances or their partisan affiliation.
+These tendencies, even if based on a hunch for the folks on the ground, seem to lead to descriptive differences in the use of these colors as it guides strategy.
+The following chapters dig a bit deeper into the idea that colors can shape attitudes by pitting the information individuals get from color against information gleaned from explicit policy stances.
 
@@
 
-<!--
 A central theme of an edited issue of *The International Journal of Press/Politics* is that visual politics is important and understudied [@lilleker_2019_pm].
@@
 Scholars need to make this transition to integrate the role of simple visual information into our theories of political information processing (abbreviated as *pip*) and attitude formation.
--->
 
@@
 
-What remains unclear is whether these patterns are just simply patterns or whether there are identifiable causes to these patterns.
+In western Europe, voters are better at connecting the ideological positioning of a party with the color they use in their branding [@casiraghi_et-al_2022_pp].
+The ability to do so is strengthened when the party is longer-surviving and is more prominent [@casiraghi_et-al_2022_pp].
+The use of politically-relevant colors activates biases toward pre-existing ideological and partisan preferences among voters in a Spanish sample [@maestre_medero_2022_pr].
+And male and female candidates in the United States use different colors -- among other things such as fonts -- in their campaign branding to convey distinguishing information about themselves [@williams_et-al_2022_jomp].
+What remains unclear is whether these patterns in the United States are just simply patterns or whether there are identifiable causes to these patterns.
 While political psychologists are increasingly interdisciplinary and rely on psychology and neuroscience, it is relatively unclear how color can convey information as complex as politics.
@@
 
-<!--
-In western Europe, voters are better at connecting the ideological positioning of a party with the color they use in their branding [@casiraghi_et-al_2022_pp].
-The ability to do so is strengthened when the party is longer-surviving and is more prominent [@casiraghi_et-al_2022_pp].
-The use of politically-relevant colors activates biases toward pre-existing ideological and partisan preferences among voters in a Spanish sample [@maestre_medero_2022_pr].
-And male and female candidates in the United States use different colors -- among other things such as fonts -- in their campaign branding to convey distinguishing information about themselves [@williams_et-al_2022_jomp].
-Despite the existing evidence, the particular psychological mechanisms driving this remain unclear.
-For example, it is unclear how colors may be organized into a cognitive schema that enables voters to quickly access and connect these colors to more complex political attitudes.
-Furthermore, it is unclear from existing evidence how colors may not just be associated with complex attitudes, but how they may enable political attitude formation and may strengthen existing connections between different political objects.
-As a jumping-off point, we can use the literature of political information processing (abbreviated as *pip*)\index{political information processing} to establish a common understanding of how political information is processed and how attitudes are formed by the processing of political information.
-
-The first prominent model of *pip* derives from rational choice perspectives.
-The memory-based model of *pip* views attitudes as a weighted collection of prior information [see @zaller_1992_cup].
-As individuals receive new information, they organize it into a schema that is relative to prior objects they already have encoded.
-By encoding this new information, the model predicts that individuals incorporate this new object with similar objects to form an attitude.
-This schema then may be more accessible in similar contexts and may then sample from its elements when prompted to express a political attitude.
-While the Receive-Accept-Sample (RAS) model accepts the view that expressed attitudes are a weighting of information most accessible at the time of attitude expression [@zaller_feldman_1992_ajps], it still presupposes that the weighting is an average of prior information.
-
-The second prominent model challenges this latter point.
-The online model of *pip* contends that individuals do not evenly weigh information, but that whether they even store it in their long-term memory to access later is biased in the direction of supporting pre-existing attitudes [@lodge_taber_2013_cup]; this phenomenon is referred to as motivated reasoning by the psychology literature [@kunda_1990_pb].
-This model suggests that people ignore new information that goes against their prior beliefs and that information confirmatory of their preferences is quicker to access -- referred to as hot cognition [@lodge_taber_2013_cup].
-
-The online model conceptualizes this underlying information encoding and attitude retrieval mechanism as automatic [@lodge_taber_2013_cup].
-This occurs due to the information's strong associations with valanced appraisals of the information guiding the attitude [@lodge_taber_2013_cup].
-This brings political scientists closer to the dominant conceptualizations among neuroscientists and psychologists concerned with memory retrieval, encoding, and attitude formation [see @fazio_2007_sc].
-Namely, that memories are encoded and retrieved quickly based on associations due to their association with valanced appraisals [@kensinger_fields_2022_ohhum].
-What remains unexplored is how visual information such as color may prime individuals to engage in motivated reasoning pre-consciously.
-If they keep their attention on the object, what paths are activated by such information?
-
--->
 ## Integrating color into a model of political information processing
@@
 I include those questions in the questionnaire due to expectations that they may act as confounds in my hypotheses.
-As political knowledge intertwines with the strength to which an individual identifies with a political party [@delli-carpini_keeter_1996_yup], I expect that political knowledge is an important confounder in my tests of $H_2$, $H_3$, and $H_4$.
-Therefore, I include a standard battery (the American National Election Study's battery) for assessing political knowledge.[^color_influence_pre-reg_anon-5] As political knowledge is shaped by levels of interest in politics as well [@delli-carpini_keeter_1996_yup], I include the American National Election Study's question to assess levels of self-reported interest in politics.
-I additionally include some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these are correlates with partisan identification [see @campbell_et-al_1960_jws; @mason_2018_cup].
-
-[^color_influence_pre-reg_anon-5]: A table including the wording of this, and all, measures are included in the Supplementary Information.
+I include some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these are correlates with partisan identification [see @campbell_et-al_1960_jws; @mason_2018_cup].
+Though political knowledge does predict the strength of an individual's partisan identification [@lodge_taber_2013_cup], attention paid to politics is likely a more important confounding variable here.
+The purpose of color in politics is to act as a heuristic for people (a cognitive shortcut).
+If individuals are aware of the tendency for Republicans to use and be associated with the color red and Democrats with the color blue, the degree to which they know factual information about politics is not entirely relevant.
+On the other hand, those that pay no attention to politics, whatsoever, may be less likely to be aware of such associations.
+Additionally, those who express less interest in politics are also likely to identify as more moderate when asked about their ideology and partisan identity [@klar_krupnikov_2016_cup].
 
@@
 Examples of all of these yard signs are included in the appendix.
-For readers interested in the more technical details, the appendix acommpanying this chapter also includes a table of the data collected in the experiment -- @tbl-study-1-measures; reports full results, posterior predictive checks, and more detailed discussions for all of the models used in the remainder of this section.
+For readers interested in the more technical details, the appendix acommpanying this chapter also includes a table of the data collected in the experiment -- @tbl-study-1-measures; reports full results, posterior predictive checks, and more detailed discussions for all of the models used in the remainder of this section.^[Unless noted otherwise, the reflection of uncertainty in the models are credible intervals at the 90% level.
+This should not be equated with the frequentist practice of often reporting confidence intervals at the 95% level as credible intervals at this level often are extremely unstable and, more importantly, are interpreted differently.
+For example, a credible interval at the 90% level can be interpreted as: the probability that the true effect is in that interval.
+This contrasts with a confidence interval used in the frequentist framework which is interpreted as: upon repeated samples, 90% of the confidence intervals contain the true effect.
+As I am using two-sided credible intervals here, at the 90% level, the probability that 0 would be the true value given the data would be less than 5% as it would be on one side of my posterior distribution.]
 
@@
 Now, I turn to exploring how features about the subjects themselves may shape the way they interact and respond to this visual information on the yard signs.
+Though, I will note that the data on the timing and cursor location is much more noisy than I had originally anticipated.
+However, as the tests of the next few questions demonstrate, there seem to be systematic differences between individuals that saw either a red, white, or blue yard sign despite holding everything else but the color constant between them.
+While I am a bit skeptical of the data here as it is noisy, I think the next peices of empirical evidence suggest support for this hypothesis as well.
 
@@
 I examine differences in respondents' reported perceptions of the candidate's partisan affiliation.
-As participants are asked this question for each treatment they view, the estimand of interest reflects the difference in perceptions of the candidate's partisan affiliation between the yard sign that they saw averaged across respondents.
+Evidence supporting $H_2$ would appear as differences between those who saw the white yard signs and the "partisan color" yard signs in reported perceptions of the partisanship of the candidates on average.
 I estimate two ordered logistic regression where the main independent variables of interest are two indicator variables for whether respondents received the "red yard sign" or the "blue yard sign" in each round of Trial 1.
@@
 The results do not suggest that they are.
-However, given that I had a very small number of respondents reporting colorblindness, the lack of substantive or statistical effects here are likely because I do not have enough participants with colorblindness in each group to compare.
+However, given that I had a very small number of respondents reporting colorblindness in my sample, the lack of substantive or statistical effects here are likely because I do not have enough participants with colorblindness in each group to compare.
 
@@
 With the data on the proportion of each of the yard signs using the red and blue colors, I merge this data with the MIT Election Lab Data.
-This leaves me with data from the House elections between 2016 and 2020.
+This leaves me with data from the House elections between 2018 and 2022.
 While the data are limited in the number of elections it reflects, it allows me to hold the district composition constant as redistricting occurs after the Census every 10 years.
-However, each election cycle is different and are often different depending on current events.
-With these data, I estimate a mixed effect model with partial pooling of the intercepts at the district level and no pooling of the intercepts for the election year level.
-For less technical readers, this allows me to explore whether the district and within election year differences between choices in yard sign color use.
-What I am trying to do with this analysis is explore whether or not campaigns in districts that are more partisan will use more red or blue while campaigns in districts that are more moderate will use fewer of those traditionally partisan colors.
+However, each district and state is different in their laws surrounding elections and are different in terms of political context.
+I want to examine whether there are meaningful differences between districts that are partisan "strongholds" (Democrats or Republicans tend to get elected in a district) relative to districts that are much less so.
+To do this, I include a model with intercepts with no pooling.
+That is a model that includes an intercept for each state-district unit.
+Though my outcomes of interest (proportion of the yard sign that is red or blue) are continous (the outcomes can take any real number, so not an integer), the outcomes are bounded between 0 and 1.
+While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit and introduce systematic error into my model and lead to results that are quite unstable.
+To not bog down readers with a lot of technical jargon, the model that I end up using is called a ordered beta regression which allows me to efficiently and accurately predict outcomes that can be 0 or 1 or any real number between 0 and 1 [@kubinec_2022_pa].
+For readers in a more technical discussion about why I chose this over other techniques in the beta regression family, I encourage you to look at the appendix.
+
+Once I have fit these models, I use the `marginaleffects` [@marginaleffects] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs as explained by the 5-year rolling average Democratic candidates' vote share.
+The grand mean here just reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather I am just averaging across all of those to provide a single line.
+These results are included in @fig-study-2-pred.
 
@@
 ```
+
+The results demonstrate that districts where Democrats are historically more successful see yard signs with a lower proportion of red on them, while those same districts see more Blue on them.
+Again, these results do not claim that campaigns are doing this either because voters are encouraging them to take this strategy or that they are doing it as a way to proactively get voters to do it.
+To tease out which of those questions is the right one requires more sophisticated approaches and data that could allow me to leverage redistricting to see how these outcomes change due to some unrelated, external shock.
+The data available to me do not allow me to do that at this time.
+Furthermore, teasing out such an association is not a primary goal of this chapter.
+
+## Conclusions
+
+This chapter argues that the colors red and blue provide useful information to voters about politics.
+Specifically, the colors red and blue provide information about a candidates' partisanship.
+Second, the chapter argues that the information gleaned from these colors can shape how people engage with politics.
+While I had a number of other sets of expectations from this chapter, these were the two primary questions I wanted to address in the chapter.
+
+Evidence from my experiment suggests that the use of the colors red and blue convey partisan information, while a third color like white provides very little useful political information.
+The experiment provides evidence that individuals see candidates that use red on a yard sign as more Republican and candidates that use blue as more Democratic.
+Evidence from the experiment also suggested that using less of these partisan colors and using both partisan colors do make it a bit harder for individuals to make those same associations.
+Further, the experiment demonstrated that these associations that we make with color and partisanship are powerful enough that they can shape whether people express a willingness to vote for a candidate.
+That is, individuals that identify with the Republican party are much more likely to vote for a candidate with a red yard sign than a white yard sign and Democrats are much more likely to vote for a candidate with a blue yard sign than yard signs with other colors.
+
+Since it appears that colors can influence vote choice, I turn to data that capture the real world messiness to examine whether or not campaigns are responsive to such patterns.
+It appears that they are.
+The empirical evidence suggest that campaigns use more blue on their yard signs if it is a district that has a higher vote share for Democrats the five previous years and use red much less often in those same circumstances.
+This fits with strategies communicated to me by a campaign marketing firm.
+
+What this chapter demonstrates is that the colors red and blue convey information and they shape outcomes.
+It appears as though that it does not simply shape outcomes for individuals such as their personal attitudes or their vote choice in a lab, but that it has enough of an aggregative effect that can shape strategy for campaigns.
+The next chapter seeks to dig into this latter claim a bit more.
+The next chapter examines whether the snap-judgment model holds up in more complex settings.
+Specifically, the next chapter examines whether color can shape whether and how we have conversations about politics with others and the degree to which color can be a tool inhibiting political persuasion.

### 2023-07-09 chapter_3/src/slides/slides.qmd
add ISPP slides

@@
   - does it have pre-conscious effects on information that comes later?
+- The goal here is to start off by building up some exepectations in simple cases with a psychological model.
+Other complications are certainly interesting and will be saved for future projects.
+For now, want to start simple.
 :::
@@
 
-# Sensitivity of conclusions to sample size, research design, and modeling strategies
+# References
+
+::: {#refs}
+:::
+
+::: footer
+:::
+
+# Sensitivity of conclusions to sample size, research design, and modeling strategies {.appendix}
 
@@
 :::
-
-# References
-
-::: {#refs}
-:::
-
-::: footer
-:::

### 2023-07-09 chapter_3/src/slides/slides.qmd
make some extra additions to slides

@@
 
+---
+
+- Prime condition: political attitudes questionnaire before treatment vs. after
+- Person wearing shirt might be White Female (but would like some feedback on this)
+
+::: footer
+:::
+
+---
+
 ## Study 2
@@
 
+---
+
+- Congruency is whether or not policy attitudes after image matches with presumed partisanship from color of shirt
+  - Policy positions will be on: Support for Gun Control, whether pro-choice or pro-life, support for Universal Basic Income
+
+::: footer
+:::
+
+---
+
+## Outcomes
+
+- $H_1$: What color shirt was your political discussion partner wearing?
+- $H_2$ \& $H_3$: To what extent are you willing to have a conversation with this person? (5-item response)
+
+::: footer
+:::
+
 # References
@@
 
-# Sensitivity of conclusions to sample size, research design, and modeling strategies {.appendix}
+# Appendix {.appendix}
+
+## Sensitivity of conclusions to sample size, research design, and modeling strategies {.appendix}
 
@@
 
-## Fitting the models on the simulated data
+### Fitting the models on the simulated data
 
@@
 
-### Model 1
+#### Model 1
 
@@
 
-### Model 2
+#### Model 2
 
@@
 
-### Model 2 (alternate)
+#### Model 2 (alternate)
 
@@
 
-## Performance
+### Performance
 
@@
 
-### Model 1
+#### Model 1
 ```{r}

### 2023-08-07 chapter_2/src/appendix.qmd
update years for empirical chapter 1, study 2

@@
     "b_intercept" = "Intercept"
-    , "b_dem_vote_share" = "Democratic vote share (%)"
+    , "b_dem_vote_share" = "Democratic vote share (percent)"
   )
   , notes = c(
-    "Data source: Pavlovia"
+    "Data source: Center for Political Design and MIT Election Lab"
     , "Positive coefficients reflect the logged-odds"

### 2023-08-07 chapter_2/src/eda/study_1/cleaning.R

@@ -8,7 +8,7 @@
     #** duplicated rows based on session_id, then converts
     #** columns to correct data types.
   #* Updated:
-    #** 2023-06-16
+    #** 2023-08-07
     #** dcr
 
 # Setup
@@ -17,7 +17,6 @@ box::use(
   data.table[...]
   , ./R/clean_data[clean_data]
 )
-
 # Cleaning
   #* Do basic cleaning to return a minimally usable data.frame
 list_df <- list() # create an empty list for my data_frames
@@ -197,7 +196,7 @@ list_df[["cleaned"]] <- list_df[["cleaned"]][
   , trial_1_vote := factor(trial_1_vote, ordered = TRUE)
 ]
 
-# Store the cleaned data in a RData temp file
+# Store the cleaned data in a csv temp file
 write.csv(
   list_df[["cleaned"]]
   , file = "../data/clean/cleaned_pavlovia.csv"

### 2023-08-07 chapter_2/src/study_2/05_mit_election_lab_merge.py

@@ -121,7 +121,7 @@ df = pl.read_csv(
 yard_sign = df.join(
         election_lab_merge, 
         on = ["year", "state_district", "last_name"], 
-        how = "left"
+        how = "inner"
     )
 
 # Save stored dataset

### 2023-08-08 chapter_2/src/appendix.qmd
update citations and fix a couple of typos

@@
 Despite the similarities between my pre-registered hypotheses and research design, there are a few subtle differences between what I pre-registered and what I ended up doing.
-In the spirit of complete transparancy, I wanted to make a note of these differences.
+In the spirit of complete transparency, I wanted to make a note of these differences.
 
@@
 
-To confirm that these models return sensical predictions, I again plot the posterior predictions.
+To confirm that these models return logical predictions, I again plot the posterior predictions.
 @fig-h-3-ppc seems to suggest that both models do a pretty good job at returning a distribution fo predicted outcomes in terms of differences between those values and outcomes measured in my sample.
@@
 As I mention in the main text of the book, I note that I regress the 5-year rolling average of the democratic vote share in a state upon the proportion of the color red and blue on the yard signs downloaded from the Center for American Political Design.
-The outcome is a continous and bounded variable between the value of 0 and 1.
+The outcome is a continuous and bounded variable between the value of 0 and 1.
 I note in the main text that I use a ordered beta regression, but here I provide more specifics.
-As the outcome is continuous but bounded between 0 and 1, treating the outcome variable as a continous variable with no finite bounding as I would with a OLS would be inappropriate.
+As the outcome is continuous but bounded between 0 and 1, treating the outcome variable as a continuous variable with no finite bounding as I would with a OLS would be inappropriate.
 To ensure that I am using the most appropriate estimator to explain the outcome of interest, I elect to use an ordered beta regression.
@@
 I could elect to use a zero-inflated beta regression which would allow me to appropriately model this outcome.
-However, @kubinec_2022_pa demonstrates that the ordered beta regression is a much more efficient and accurate (in terms of a number of various metrics) approach to dealing with outcomes that can equal either 0 or 1.
+However, @kubinec_ordered_2022 demonstrates that the ordered beta regression is a much more efficient and accurate (in terms of a number of various metrics) approach to dealing with outcomes that can equal either 0 or 1.
 
-The default priors for $\beta_i$ is $N(0, 5)$ in the $ordbetareg$ [@kubinec_2022_pa] package that I use to fit the model.
+The default priors for $\beta_i$ is $N(0, 5)$ in the $ordbetareg$ [@kubinec_ordered_2022] package that I use to fit the model.
 However, I receive warnings indicating that there are divergent transitions.

### 2023-08-08 chapter_2/src/manuscript.qmd
update years for empirical chapter 1, study 2

@@
 The use of color on yard signs used by campaigns in elections.
-I focus on yard signs as they are a common form of campaign marketing and evidence suggests that they can shape individual behavior [@makse_et-al_2019_oup] and electoral outcomes [@green_et-al_2016_es].
+I focus on yard signs as they are a common form of campaign marketing and evidence suggests that they can shape individual behavior [@makse_politics_2019] and electoral outcomes [@green_effects_2016].
 Additionally, I start by examining the colors red and blue.
-While there are other colors that may provide political information -- black and white for Black Lives Matter and Blue Lives Matter movements, the overarching goal of this book is to lay the foundation for a larger research agenda in visual political psychology [see @bucy_joo_2021_ijpp].
+While there are other colors that may provide political information -- black and white for Black Lives Matter and Blue Lives Matter movements, the overarching goal of this book is to lay the foundation for a larger research agenda in visual political psychology [see @bucy_editors_2021].
 Without such foundations, we are studying complex cases and circumstances upon assumptions without a grasp of how, and if they even do, occur in the cases that might seem trivial to some.
-While there indeed is empirical and experiential evidence suggesting that the Republicans use the color red and Democrats use the color blue [@schloss_palmer_2014_pbr;@williams_et-al_2022_jomp], there is yet to be a theoretical framework that explains how these connections happen at the individual level.
+While there indeed is empirical and experiential evidence suggesting that the Republicans use the color red and Democrats use the color blue [@schloss_politics_2014;@williams_whats_2022], there is yet to be a theoretical framework that explains how these connections happen at the individual level.
 It may also be unsatisfying that I do not address *how* these connections came about.
-While the connections between Republicans with the color red and Democrats with the color blue seemed to quicken after the 2000 Presidential election where news networks covering the election began to consistently use those colors [@elving_2014_npr], it is not clear if this was a deliberate choice or whether this was yet another symptom of an increasingly polarized public who just want easily digestable information about politics so they can move on to other matters in their lives.
+While the connections between Republicans with the color red and Democrats with the color blue seemed to quicken after the 2000 Presidential election where news networks covering the election began to consistently use those colors [@elving_color_2014], it is not clear if this was a deliberate choice or whether this was yet another symptom of an increasingly polarized public who just want easily digestible information about politics so they can move on to other matters in their lives.
 An undertaking to address such a question is for a different book, perhaps.
@@
 To give a preview for this chapter, I propose two studies to explore the claims I make in this chapter.
-Yard signs are a simple yet effective source of campaign branding for political candidates as they convey information that is often useful for voters -- partisanship [@campbell_et-al_1960_jws].
+Yard signs are a simple yet effective source of campaign branding for political candidates as they convey information that is often useful for voters -- partisanship [@campbell_american_1969].
 As yard signs are a simple and static form of campaign advertising, they cannot rely heavily on more complicated forms of information.
@@
 In fact, I believe that there is a necessary feedback loop between the parties and their base of support.
-Voters support candidates who signal strong allegiance to the party to increase their chances for electoral success [@utych_2020_es] and the parties are motivated to distinguish themselves [@lee_2009;@clifford_2020_pb] as a result of their high levels of ideological and affective polarization [@dietrich_2021_pa;@enders_2021_jop].
+Voters support candidates who signal strong allegiance to the party to increase their chances for electoral success [@utych_voter-centric_2020] and the parties are motivated to distinguish themselves [@lee_insecure_2016;@clifford_how_2020] as a result of their high levels of ideological and affective polarization [@dietrich_using_2021;@enders_issues_2021].
 Again, to tease out the direction of blame is more appropriate for another time.
@@
 
-A central theme of an edited issue of *The International Journal of Press/Politics* is that visual politics is important and understudied [@lilleker_2019_pm].
-Those who are engaged in these questions attribute these challenges to methodological sophistication and the difficult task of interdisciplinary theorizing [@gerodimos_2019_pm; @bucy_joo_2021_ijpp].
+A central theme of an edited issue of *The International Journal of Press/Politics* is that visual politics is important and understudied [@lilleker_introduction_2019 ].
+Those who are engaged in these questions attribute these challenges to methodological sophistication and the difficult task of interdisciplinary theorizing [@gerodimos_interdisciplinary_2019; @bucy_editors_2021].
 
-The rise of television consumption changed the focus of the medium in the research for political communication scholars [@hall-jamieson_2014_ohpc].
+The rise of television consumption changed the focus of the medium in the research for political communication scholars [@hall_jamieson_creating_2014].
 In a similar way, so does the rise of image-based social media and has set new agendas.
-For several methodological and disciplinary reasons, the visual aspects of television were of little focus in the literature [@bucy_joo_2021_ijpp].
+For several methodological and disciplinary reasons, the visual aspects of television were of little focus in the literature [@bucy_editors_2021].
 However, the news organizations and politicians are responding to the ubiquitous use of the public to use image-dominant social media platforms like TikTok and Instagram, by joining such platforms.
@@
 How does politically-relevant visual information matter to politics?
-From an evolutionary-biological perspective, visual information has been a common source of information for millions of years that a variety of single-and-multi-cell organisms rely upon to evaluate their environment [see @grabe_bucy_2009_oup, Chapter 1 for a useful discussion].
+From an evolutionary-biological perspective, visual information has been a common source of information for millions of years that a variety of single-and-multi-cell organisms rely upon to evaluate their environment [see @grabe_image_2009, Chapter 1 for a useful discussion].
 Visual information processing, as an ancient biological invention, the human brain is organized around the processing of it.
 Reflecting on this, many scholars of neuroscience argue that visual information is the fastest form of information processing for humans.
-For example, even complex visual information, such as the warmth expressed in someone's facial features, is automatically and pre-consciously processed in only about 33 milliseconds (abbreviated as ms) [@ames_et-al_2012_ohsn].
+For example, even complex visual information, such as the warmth expressed in someone's facial features, is automatically and pre-consciously processed in only about 33 milliseconds (abbreviated as ms) [@ames_impression_2012].
 
-Approached from a different perspective, as humans are cognitive misers \index{cognitive misers}, visual information in the realm of politics provides efficient information to voters about politically-relevant actors and events [@lilleker_2019_pm].
-Evidence suggests that even simple party branding on yard signs has an emotional appeal and encourages a shift in attitudes toward the person who owns the yard sign [@makse_et-al_2019_oup].
+Approached from a different perspective, as humans are cognitive misers \index{cognitive misers}, visual information in the realm of politics provides efficient information to voters about politically-relevant actors and events [@lilleker_power_2019].
+Evidence suggests that even simple party branding on yard signs has an emotional appeal and encourages a shift in attitudes toward the person who owns the yard sign [@makse_politics_2019].
 That is, even branding as simple as yard signs appears to influence the attitudes of those who view them.
@@
 More simple forms of visual information are likely even more efficient forms of information.
-In the context of the United States, the "Republican red" and "Democratic blue" is a relatively recent invention that likely has significant import in an era of significant effort by the parties to distinguish themselves from each other [@clifford_2020_pb] and where voters toe the party line [@utych_2020_es].
-Since the 2000 presidential election, the media have consistently used red on their electoral maps in "horserace" journalism to represent Republicans and blue to represent Democrats [@elving_2014_npr].
-The supposed consequence is that Democrats now report a preference for the color blue over the color red, and Republicans report a preference for the color red over the color blue [@schloss_palmer_2014_pbr].
-Others have demonstrated the strategic choices that candidates make on branding choices -- including color -- based on the types of information they want to convey to voters to distinguish them from their rivals [see @williams_et-al_2022_jomp].
+In the context of the United States, the "Republican red" and "Democratic blue" is a relatively recent invention that likely has significant import in an era of significant effort by the parties to distinguish themselves from each other [@clifford_how_2020] and where voters toe the party line [@utych_voter-centric_2020].
+Since the 2000 presidential election, the media have consistently used red on their electoral maps in "horserace" journalism to represent Republicans and blue to represent Democrats [@elving_color_2014].
+The supposed consequence is that Democrats now report a preference for the color blue over the color red, and Republicans report a preference for the color red over the color blue [@schloss_politics_2014].
+Others have demonstrated the strategic choices that candidates make on branding choices -- including color -- based on the types of information they want to convey to voters to distinguish them from their rivals [see @williams_whats_2022].
 
-In western Europe, voters are better at connecting the ideological positioning of a party with the color they use in their branding [@casiraghi_et-al_2022_pp].
-The ability to do so is strengthened when the party is longer-surviving and is more prominent [@casiraghi_et-al_2022_pp].
-The use of politically-relevant colors activates biases toward pre-existing ideological and partisan preferences among voters in a Spanish sample [@maestre_medero_2022_pr].
-And male and female candidates in the United States use different colors -- among other things such as fonts -- in their campaign branding to convey distinguishing information about themselves [@williams_et-al_2022_jomp].
+In western Europe, voters are better at connecting the ideological positioning of a party with the color they use in their branding [@casiraghi_colors_2022].
+The ability to do so is strengthened when the party is longer-surviving and is more prominent [@casiraghi_colors_2022].
+The use of politically-relevant colors activates biases toward pre-existing ideological and partisan preferences among voters in a Spanish sample [@losada_maestre_color_2022].
+And male and female candidates in the United States use different colors -- among other things such as fonts -- in their campaign branding to convey distinguishing information about themselves [@williams_whats_2022].
 What remains unclear is whether these patterns in the United States are just simply patterns or whether there are identifiable causes to these patterns.
@@
 
-Color and other simple visual information are processed much quicker and occur more frequently than text-based information that may be communicated through a news article [@mehta_zhu_2009_s].
+Color and other simple visual information are processed much quicker and occur more frequently than text-based information that may be communicated through a news article [@mehta_blue_2009].
 As the color and other visual information are processed differently, we should also consider its use as political information.
-As visual information is affectively encoded [@cimbalo_et-al_1978_jgp], it can affect the affective state and processing of more complex information, such as text.
-The visual information provides a snap judgment or an impression of the object through faster processing and activates particular neurological processes that influence subsequent information appraisals [@ames_et-al_2012_ohsn].
+As visual information is affectively encoded [@cimbalo_emotionally_1978], it can affect the affective state and processing of more complex information, such as text.
+The visual information provides a snap judgment or an impression of the object through faster processing and activates particular neurological processes that influence subsequent information appraisals [@ames_impression_2012].
 This implies that snap-judgments from visual forms of political information may have downstream effects that shape the way in which we engage with forms of political information that we traditionally consider.
@@
 An attitude represents an accessible, valanced evaluation of associated prior information and experiences.
-This conceptualization fits with that of the Object-Evaluation Associations Model [@fazio_2007_sc].
+This conceptualization fits with that of the Object-Evaluation Associations Model [@russell_h_fazio_attitudes_2007].
 As opposed to viewing attitudes as a latent collection of memories, it views attitudes as measurable evaluations of memories.
-As memories are at the core of an attitude, the association of memories with its evaluative component [see @kensinger_fields_2022_ohhum] contributes to the perspective that attitudes are affective.
-This implies that we should be able to measure attitudes but that such an operationalization requires careful consideration of the context's role in any given measure of an attitude as they result from memories [@fazio_2007_sc].
+As memories are at the core of an attitude, the association of memories with its evaluative component [see @kensinger_affective_2022] contributes to the perspective that attitudes are affective.
+This implies that we should be able to measure attitudes but that such an operationalization requires careful consideration of the context's role in any given measure of an attitude as they result from memories [@russell_h_fazio_attitudes_2007].
 In this chapter, I consider colors' effect on shaping attitudes about a political object -- a yard sign.
@@
 This means that attitudes may be unstable - not randomly, in any case.
-As attitudes are associative, they manifest slightly differently depending on the associative paths activated [@fazio_2007_sc].
-The retrieval of relevant memories to the attitude depends on many factors, such as the recency of the event, the similarity of the context, and the importance or salience of the memory [@kahana_et-al_2022_ohhum].
+As attitudes are associative, they manifest slightly differently depending on the associative paths activated [@russell_h_fazio_attitudes_2007].
+The retrieval of relevant memories to the attitude depends on many factors, such as the recency of the event, the similarity of the context, and the importance or salience of the memory [@kahana_laws_2022].
 This means that the memories retrieved to contribute to an attitude are quite variable.
@@
 
-Colors are associative and are affectively encoded [@cimbalo_et-al_1978_jgp].
-When individuals access a memory, they do not just recall an object, but they may recall visual information such as the color of an object [@mehta_zhu_2009_s].
-Due to these features, colors can be processed pre-consciously and very quickly [@mehta_zhu_2009_s].
+Colors are associative and are affectively encoded [@cimbalo_emotionally_1978].
+When individuals access a memory, they do not just recall an object, but they may recall visual information such as the color of an object [@mehta_blue_2009].
+Due to these features, colors can be processed pre-consciously and very quickly [@mehta_blue_2009].
 As they are affectively encoded, their associations with particular memory contribute to the evaluative component of the memory.
-For example, individuals associate colors like red with anger and arousal [@valdez_mehrabian_1994], whereas individuals associate blue with things like happiness and pleasure [@dandrade_egan_1974_ae].
+For example, individuals associate colors like red with anger and arousal [@valdez_effects_1994], whereas individuals associate blue with things like happiness and pleasure [@dandrade_colors_1974].
 This means that colors are compelling as contextual information shaping the subsequent processing and integration of "traditional" forms of political information to construct an attitude.
-As the preference for a particular color correlates with political attitudes [@schloss_palmer_2014_pbr], they may have some causal influence upon political attitudes; rather than just a correlation with them.
+As the preference for a particular color correlates with political attitudes [@schloss_politics_2014], they may have some causal influence upon political attitudes; rather than just a correlation with them.
 
-According to the literature in affective neuroscience, visual information is processed in various parts of the brain, such as the visual cortex [@goldstein_brockmole_2017_cl].
+According to the literature in affective neuroscience, visual information is processed in various parts of the brain, such as the visual cortex [@goldstein_sensation_2017].
 These types of processes do not occur in particular areas of the brain as some like to think.
@@
 As a result, the processing of visual information will activate other areas of the brain and will make associated paths "hot." One such area is the amygdala.
-Neuroscientists believe that as visual information is quickly and subconsciously processed, the amygdala takes and appraises it based on the paths it activated; this generates a simple affective response to such information [@winkielman_et-al_2011_ohsn].
-More complex, categorical emotion occurs later in conscious processing [@winkielman_et-al_2011_ohsn].
+Neuroscientists believe that as visual information is quickly and subconsciously processed, the amygdala takes and appraises it based on the paths it activated; this generates a simple affective response to such information [@winkielman_emotion_2011].
+More complex, categorical emotion occurs later in conscious processing [@winkielman_emotion_2011].
 
@@
 With these activated pathways, the brain also attempts to appraise such information based on quick classification.
-For attitude formation, this implies that, as memories are affectively encoded [@kensinger_fields_2022_ohhum], these memories help areas such as the amygdala to appraise the current information.
+For attitude formation, this implies that, as memories are affectively encoded [@kensinger_affective_2022], these memories help areas such as the amygdala to appraise the current information.
 
 These fast affective classifications are valanced rather than the more laborious categorization of specific emotions (e.g., anger, anxiety, fear, happy).
-What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_2000_arps], I conceptualize affect as a more extensive system that considers emotion only as a conscious classification process that occurs later than initial valanced appraisals of an object [@sander_2013_chhan; @ralph_anderson_2018_pup].
+What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_emotions_2000], I conceptualize affect as a more extensive system that considers emotion only as a conscious classification process that occurs later than initial valanced appraisals of an object [@sander_cambridge_2013; @ralph_neuroscience_2018].
 That is, emotion -- the complex classification of appraisals -- is a conscious component of affect.
-The pre-conscious process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_et-al_2011_ohsn; @dror_2017_er].
+The pre-conscious process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_emotion_2011; @dror_deconstructing_2017].
 
-The pre-conscious appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_et-al_2011_jop; @ralph_anderson_2018_pup].
-This has evolutionary roots for survival [@ralph_anderson_2018_pup; @parker_2003_p].
-While affective appraisals can lead to complex motivations, such as anxiety leading to motivations for information seeking [@marcus_2000_arps], affective appraisals are valanced and are more automatic [@winkielman_et-al_2011_ohsn].
-These affective appraisals lead to a desire to either retract or engage more with the object [@valentino_et-al_2011_jop].
+The pre-conscious appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_election_2011; @ralph_neuroscience_2018].
+This has evolutionary roots for survival [@ralph_neuroscience_2018; @parker_blink_2003].
+While affective appraisals can lead to complex motivations, such as anxiety leading to motivations for information seeking [@marcus_emotions_2000], affective appraisals are valanced and are more automatic [@winkielman_emotion_2011].
+These affective appraisals lead to a desire to either retract or engage more with the object [@valentino_election_2011].
 The snap judgment resulting from the automatic processing of politically relevant visual information should likely lead to an affective response that motivates either a desire to engage more with the object or disengage.
 
-While the visual information may encourage a particular immediate reaction to engage or disengage from the information, subsequent information processing and more conscious processing adjusts this initial appraisal generated by the snap judgment [@kensinger_fields_2022_ohhum].
-While subsequent information may amend one's snap-judgment, the snap-judgment nevertheless influences the processing of subsequent information by activating particular paths, which is later encoded as associated with the object as it converts to a memory [@lodge_taber_2013_cup; @kensinger_fields_2022_ohhum].
+While the visual information may encourage a particular immediate reaction to engage or disengage from the information, subsequent information processing and more conscious processing adjusts this initial appraisal generated by the snap judgment [@kensinger_affective_2022].
+While subsequent information may amend one's snap-judgment, the snap-judgment nevertheless influences the processing of subsequent information by activating particular paths, which is later encoded as associated with the object as it converts to a memory [@lodge_rationalizing_2013; @kensinger_affective_2022].
 
-Beyond a motivated backlash effect, the popular application of motivated reasoning to political science finds evidence suggesting that individuals take more time processing information that runs against their pre-existing preferences [@taber_lodge_2006_ajps].
+Beyond a motivated backlash effect, the popular application of motivated reasoning to political science finds evidence suggesting that individuals take more time processing information that runs against their pre-existing preferences [@taber_motivated_2006].
 The explanation for this is that people are finding ways to come up with counterarguments to such information.
@@
 You now are racking your brain to think about who that is.
-If you are politically engaged, you might come to that recognition of the name quickly or it may take you significantly longer if you are less politically engaged [see @kahana_et-al_2022_ohhum].
+If you are politically engaged, you might come to that recognition of the name quickly or it may take you significantly longer if you are less politically engaged [see @kahana_laws_2022].
 You figure out that they are a Republican politician.
@@
 What the snap-judgment model predicts is happening in your head is that as soon as the light that bounces off the sign to produce a particular wavelength hits your eyes, your brain is already trying to make sense of this information.
-This is a valuable tool for survival that biology has optimized for millions of years [@parker_2003_p].
-Rather than slowly processing the visual information and finding yourself in the jaws of a predator or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and subconsciously [@newell_1990_hup].
-To make sense of such information, it accesses familiar information similar to what it is currently attempting to process for efficiency [@kahana_et-al_2022_ohhum].
-This is accessing memories and contains valanced information [@kensinger_fields_2022_ohhum]: should I avoid this, or is it pleasant?
+This is a valuable tool for survival that biology has optimized for millions of years [@parker_blink_2003].
+Rather than slowly processing the visual information and finding yourself in the jaws of a predator or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and subconsciously [@newell_unified_1990].
+To make sense of such information, it accesses familiar information similar to what it is currently attempting to process for efficiency [@kahana_laws_2022].
+This is accessing memories and contains valanced information [@kensinger_affective_2022]: should I avoid this, or is it pleasant?
 Once the brain has finished such processing, it can pass its prediction to your conscious memory.
@@
 You access associative memory to figure out what those particular wavelengths represent: red, white, blue?
-As these colors are associated with different emotional states [see @cimbalo_et-al_1978_jgp] and the resulting behavioral consequences, your brain starts sending signals to the rest of your body to prepare it to react [see @sander_2013_chhan; @dror_2017_er].
+As these colors are associated with different emotional states [see @cimbalo_emotionally_1978] and the resulting behavioral consequences, your brain starts sending signals to the rest of your body to prepare it to react [see @sander_cambridge_2013; @dror_deconstructing_2017].
 You now need to figure out what the rest of that information was.
@@
 Social groupings are not simply abstract concepts invented by social psychologists; our neurobiology reflects them.
-For example, researchers find activation of parts of the brain, such as the anterior insula, when we see someone in our social group outperformed by someone from the out-group [see @zink_barter_2012_ohsn].
-The anterior insula activity is associated with physical and emotional pain, not just for ourselves but also for others [@adolphs_janowski_2011_ohsn].
-Others have also observed that when seeing someone part of a high-status social group, there is an increase in activity in the sensorimotor cortex and supplementary motor area, indicating more activity in the areas of the brain that encourage movement [@zink_et-al_2008_n].
-Visual information about someone in your social group speeds up processing, is more salient, and demands more attention than visual information about an object outside your social group [@zink_barter_2012_ohsn].
+For example, researchers find activation of parts of the brain, such as the anterior insula, when we see someone in our social group outperformed by someone from the out-group [see @zink_neural_2012].
+The anterior insula activity is associated with physical and emotional pain, not just for ourselves but also for others [@adolphs_emotion_2011].
+Others have also observed that when seeing someone part of a high-status social group, there is an increase in activity in the sensorimotor cortex and supplementary motor area, indicating more activity in the areas of the brain that encourage movement [@zink_know_2008].
+Visual information about someone in your social group speeds up processing, is more salient, and demands more attention than visual information about an object outside your social group [@zink_neural_2012].
 
-There is significant evidence supporting the theory that our partisan identification reflects more than just our attitudes about politics but a social identity [see @campbell_et-al_1960_jws; @mason_2018_cup] that guides our attitudes [see @achen_bartels_2016_pup; @white_et-al_2014_apsr; also @bullock_2011_apsr].
-As our political attitudes reflect shared views among co-partisans [@pickup_et-al_2020_pb], the congruence between political information and our partisan identification influences our reactions to such political information.
+There is significant evidence supporting the theory that our partisan identification reflects more than just our attitudes about politics but a social identity [see @campbell_american_1969; @mason_uncivil_2018] that guides our attitudes [see @achen_democracy_2016; @white_selling_2014; also @bullock_elite_2011].
+As our political attitudes reflect shared views among co-partisans [@pickup_expressive_2020], the congruence between political information and our partisan identification influences our reactions to such political information.
 This means that the visual information we glean from politics will likely motivate those neurological features of social groups and explain the resulting behavioral manifestations reacting to such information.
@@
 
-From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that these colors that they notice shape perceptions about the person and ideological symbol represented in the branding -- meaning that they express different levels of preference for receiving more information that is similar to what they saw and their levels of preference for supporting such a campaign ($H_{2}$); that the consistency of information explains more positive perceptions -- simple visual information with more complex "traditional" information ($H_{3}$); this positive and consistent information is processed quicker than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) in line with their primary objective of reelection [@fenno_1973_lb; @mayhew_1974_yup].
+From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that these colors that they notice shape perceptions about the person and ideological symbol represented in the branding -- meaning that they express different levels of preference for receiving more information that is similar to what they saw and their levels of preference for supporting such a campaign ($H_{2}$); that the consistency of information explains more positive perceptions -- simple visual information with more complex "traditional" information ($H_{3}$); this positive and consistent information is processed quicker than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) in line with their primary objective of reelection [@fenno_congressmen_1973; @mayhew_congress_1974].
 A summary of these hypotheses are included in @tbl-hypotheses.
@@
 The purpose of [Study 1](#sec-study-1) is to examine whether the color choices on an almost ubiquitus form of campaign branding -- yard signs -- influence people's perceptions of political candidates.
-Evidence suggests that yard signs *do* matter in shaping political attitudes [@makse_et-al_2019_oup], vote intentions [@makse_et-al_2019_oup], and even electoral outcomes [@green_et-al_2016_es].
+Evidence suggests that yard signs *do* matter in shaping political attitudes [@makse_politics_2019], vote intentions [@makse_politics_2019], and even electoral outcomes [@green_effects_2016].
 As they are simple, cheap, intrusive, and common forms of campaign branding, they provide a conservative test of the effects of color in campaign branding.
@@
 I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia[^color_influence_pre-reg_anon-4] and are provided with a demographics and political attitudes questionnaire.
-As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_et-al_2018_ajps], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
+As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
 This questionnaire includes common questions about the participant's ascriptive and descriptive characteristics and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
@@
 [^color_influence_pre-reg_anon-4]: Pavolovia allows for researchers to host and run open source experiments for about \$0.20 per participant (to cover their server costs).
-I use it primarily to integrate the JavaScript components from the jsPsych package [@jspsych] for my experimental design.
+I use it primarily to integrate the JavaScript components from the jsPsych package [@leeuw_jspsych_2015] for my experimental design.
 
 I include those questions in the questionnaire due to expectations that they may act as confounds in my hypotheses.
-I include some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these are correlates with partisan identification [see @campbell_et-al_1960_jws; @mason_2018_cup].
-Though political knowledge does predict the strength of an individual's partisan identification [@lodge_taber_2013_cup], attention paid to politics is likely a more important confounding variable here.
+I include some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these are correlates with partisan identification [see @campbell_american_1969; @mason_uncivil_2018].
+Though political knowledge does predict the strength of an individual's partisan identification [@lodge_rationalizing_2013], attention paid to politics is likely a more important confounding variable here.
 The purpose of color in politics is to act as a heuristic for people (a cognitive shortcut).
@@
 On the other hand, those that pay no attention to politics, whatsoever, may be less likely to be aware of such associations.
-Additionally, those who express less interest in politics are also likely to identify as more moderate when asked about their ideology and partisan identity [@klar_krupnikov_2016_cup].
+Additionally, those who express less interest in politics are also likely to identify as more moderate when asked about their ideology and partisan identity [@klar_independent_2016].
 
@@
 As some individuals may possess undiagnosed colorblindness, asking about their sex assists in covariate balance.
-I additionally include an open-ended question asking participants to describe their "first memory of a political event." The use of an open-ended question helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [see @kennedy_et-al_2021_poq].
-Given estimates using these exclusion criteria, I would expect that upwards of 40% of my original sample will fail these attention checks [@kennedy_et-al_2021_poq]; thus, the large sample size.
+I additionally include an open-ended question asking participants to describe their "first memory of a political event." The use of an open-ended question helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [see @kennedy_strategies_2021].
+Given estimates using these exclusion criteria, I would expect that upwards of 40% of my original sample will fail these attention checks [@kennedy_strategies_2021]; thus, the large sample size.
 
@@
 
-Rather than use eye-tracking devices and software, I instead use Mouseview.js [see @anwyl-irvine_et-al_2022_brm], which either blocks out or blurs a large portion of the participant's screen and encourages them to move their mouse to view different parts of the screen in isolation.
+Rather than use eye-tracking devices and software, I instead use Mouseview.js [see @anwyl-irvine_mouseviewjs_2022], which either blocks out or blurs a large portion of the participant's screen and encourages them to move their mouse to view different parts of the screen in isolation.
 As the participants move their cursor around the screen, it tracks the coordinates of the cursor along with the "dwell" time of the cursor in that particular coordinate.
-One primary benefit of Mouseview.js is that it allows researchers to field their experiments outside of a lab-based setting -- while providing results that robustly correlate with the results from a design employing eye-tracking hardware [@anwyl-irvine_et-al_2022_brm].
+One primary benefit of Mouseview.js is that it allows researchers to field their experiments outside of a lab-based setting -- while providing results that robustly correlate with the results from a design employing eye-tracking hardware [@anwyl-irvine_mouseviewjs_2022].
 This allows researchers to rely less on convenience samples, which are common with eye-tracking studies.
@@
 When viewing each yard sign in the first trial, there is a blur over a substantial portion of the screen.
-At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_pieters_2008_rmr].[^color_influence_pre-reg_anon-7] Participants move their cursor to explore the yard sign.
+At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].[^color_influence_pre-reg_anon-7] Participants move their cursor to explore the yard sign.
 I allot 5000 ms to perform the exploration until the image goes away to encourage a consistent and short duration to explore the image.[^color_influence_pre-reg_anon-8] After exploring each image, I asked participants what colors were on the yard sign and whether they felt that the candidate represented on the yard sign was a Democrat, a Republican, or Neither.
@@
 This gaussian blur allows participants to see a blurred visual field beyond the cursor.
-This allows participants to see enough to take purposeful action to explore blurred parts of the image that attract them [@anwyl-irvine_et-al_2022_brm].
-The use of the gaussian blur requires that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_et-al_2022_brm].
+This allows participants to see enough to take purposeful action to explore blurred parts of the image that attract them [@anwyl-irvine_mouseviewjs_2022].
+The use of the gaussian blur requires that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_mouseviewjs_2022].
 This will require participants to either switch browsers or to not participate in the study if they are using Safari at the time they are recruited by Prolific to participate in the study.
@@
 
-[^color_influence_pre-reg_anon-8]: In marketing research, some studies give participants about 6000 milliseconds in eye-tracking studies to examine a brand and to formulate an intention to purchase a product or not [@wedel_pieters_2008_rmr].
-With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure-evoking images uses 10000 milliseconds; but is intended to be an extended amount of time [@anwyl-irvine_et-al_2022_brm].
+[^color_influence_pre-reg_anon-8]: In marketing research, some studies give participants about 6000 milliseconds in eye-tracking studies to examine a brand and to formulate an intention to purchase a product or not [@wedel_review_2008].
+With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure-evoking images uses 10000 milliseconds; but is intended to be an extended amount of time [@anwyl-irvine_mouseviewjs_2022].
 
@@
 However, as the tests of the next few questions demonstrate, there seem to be systematic differences between individuals that saw either a red, white, or blue yard sign despite holding everything else but the color constant between them.
-While I am a bit skeptical of the data here as it is noisy, I think the next peices of empirical evidence suggest support for this hypothesis as well.
+While I am a bit skeptical of the data here as it is noisy, I think the next pieces of empirical evidence suggest support for this hypothesis as well.
 
@@
 Everything on the yard signs remains constant except for the color.
-As representations of ideology are associated with more than just political views but things like space [@mills_et-al_2016_bbr] and color [@maestre_medero_2022_pr], differences between respondents on the perceived political affiliations of the candidate should be more than "by chance" differences.
+As representations of ideology are associated with more than just political views but things like space [@mills_political_2016] and color [@losada_maestre_color_2022], differences between respondents on the perceived political affiliations of the candidate should be more than "by chance" differences.
 However, differences occur based on the associations between red and blue with partisanship and the lack of political information that the color white conveys.
@@
 
-I fit two ordered logistic regressions where the independent variables are indicator variables reporting whether the participant received the red (the first model) or they recieved the blue treatment (the second model).
+I fit two ordered logistic regressions where the independent variables are indicator variables reporting whether the participant received the red (the first model) or they received the blue treatment (the second model).
 Those included in the baseline category for both models are those who received the white yard sign treatment.
@@
 Two for each trial.
-Where each model for each trial calculates whether an average subject in the study reported that the yard sign they saw in the trial was a Democrat, Indepdent, or a Republican.
-The predicted probabilities for each outcome occuring under different treatments and for different trials are presented in @fig-h-2a-predictions.
+Where each model for each trial calculates whether an average subject in the study reported that the yard sign they saw in the trial was a Democrat, Independent, or a Republican.
+The predicted probabilities for each outcome occurring under different treatments and for different trials are presented in @fig-h-2a-predictions.
 @tbl-hypothesis-2a and @tbl-hypothesis-2a-cont located in the appendix reports the full results of these models while @fig-h-2a-ppc located in the appendix reports the posterior predictive checks of these models.
@@
 That is, do people process in-group information faster than out-group information?
-There is evidence of these tendencies in political circumstances [@lodge_taber_2013_cup].
+There is evidence of these tendencies in political circumstances [@lodge_rationalizing_2013].
 
@@
 
-The goal for the second peice of empirical evidence in the chapter is to explore whether there is any evidence not from the "lab" suggesting that campaigns use the colors red and blue systematically.
+The goal for the second piece of empirical evidence in the chapter is to explore whether there is any evidence not from the "lab" suggesting that campaigns use the colors red and blue systematically.
 If the color of a yard sign does indeed matter and its electoral effects depend on the perceptions of potential voters, we should expect that campaigns are less likely to place yard signs with a large amount of Red or Blue in more moderate districts.
@@
 With the data on the proportion of each of the yard signs using the red and blue colors, I merge this data with the MIT Election Lab Data.
-This leaves me with data from the House elections between 2018 and 2022.
+This leaves me with data from the House elections between 2018 and 2020.
 While the data are limited in the number of elections it reflects, it allows me to hold the district composition constant as redistricting occurs after the Census every 10 years.
@@
 While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit and introduce systematic error into my model and lead to results that are quite unstable.
-To not bog down readers with a lot of technical jargon, the model that I end up using is called a ordered beta regression which allows me to efficiently and accurately predict outcomes that can be 0 or 1 or any real number between 0 and 1 [@kubinec_2022_pa].
+To not bog down readers with a lot of technical jargon, the model that I end up using is called a ordered beta regression which allows me to efficiently and accurately predict outcomes that can be 0 or 1 or any real number between 0 and 1 [@kubinec_ordered_2022].
 For readers in a more technical discussion about why I chose this over other techniques in the beta regression family, I encourage you to look at the appendix.
 
-Once I have fit these models, I use the `marginaleffects` [@marginaleffects] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs as explained by the 5-year rolling average Democratic candidates' vote share.
+Once I have fit these models, I use the `marginaleffects` [@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs as explained by the 5-year rolling average Democratic candidates' vote share.
 The grand mean here just reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather I am just averaging across all of those to provide a single line.
@@
 #| layout-ncol: 1
-#| fig-cap: More blue on the yard signs in Democratic strongholds
+#| fig-cap: More blue on the yard signs in Democratic strongholdsz
 #| fig-subcap:

### 2023-08-09 chapter_3/src/prr/dcr_color_and_deliberation_prr.qmd
fix typos, add new citation keys, and re-try to figure out how quarto sets working directories work again

@@
 code-repo: |
-  For replication, go to: <https://github.com/DamonCharlesRoberts/visual_information_and_political_participation>.
+  For replication, go to: <https://github.com/DamonCharlesRoberts/book_project/chapter_3>.
 author:
@@
 
-bibliography: "../../../assets/references.bib"
+bibliography: ["../../../assets/deliberation-chapter-references.bib"]
 format:
@@
     fontsize: 12pt
+date: today
 nocite: |
-  @quarto
+  @allaire_quarto_2022
 execute:
@@
 It argues that, as a pre-conscious form of information, they have downstream consequences on our attitude, expression, and behavior.
-This chapter addresses the question, "Well do they influence our attitude expression, and do they influence our behavior?" Demonstrating that people recognize color in politics is not sufficient to say that they matter in politics.
+The previous chapter demonstrated that the colors red and blue act as affiliative information that betrays the partisanship of political candidates and is predictive of vote choice absent other information.
+It is unclear from that chapter whether subsequent politically substantive information can override these initial snap-judgments and whether these same associations are generalized to individuals in the mass public.
+This chapter addresses two primary questions; (1) "How potent are those downstream effects generally and for evaluating individuals in the mass public?" as well as addressing the question, "How do the snap-judgments formed from these colors shape our capacity to be persuaded by new information?"
 
-There is an expansive landscape that captures both formal and informal forms of political behaviors and a vast net to cast when trying to capture attitudes.
-To not turn this chapter into an impossibly long read, I will focus on what attitudes and behaviors I explore.
+Conversations about politics are an essential part of participatory democracy [@huckfeldt_information_2007].
+They encourage many different forms of more formal political engagement [@verba_voice_1995;@klofstad_talk_2007;@eveland_political_2009;@matthes_meta-analysis_2019], and are a helpful resource that people can tap into for information about candidates and current events [@mcclurg_social_2003;@eveland_political_2009], is argued to be capable of buffering animosity towards those in "the other party" [@levendusky_we_2021], and even a source of persuasion [@beck_social_2002;@suhay_persuasion_2020].
 
-Conversations about politics are an essential part of participatory democracy [@huckfeldt_2007_ohpb].
-They encourage many different forms of more formal political engagement [@verba_et-al_1995_hup;@klofstad_2007_prq;@eveland_hively_2009_joc;@matthes_et-al_2019_pc], and are a helpful resource that people can tap into for information about candidates and current events [@mcclurg_2003_prq;@eveland_hively_2009_joc], is argued to be capable of buffering animosity towards those in "the other party" [@levendusky_stecula_2021_cup], and even a source of persuasion [@beck_et-al_2002;@sokhey_stapleton_2020_ohep].
+Though having conversations are important for the Aristotlean conception of a democratic citizen, some evidence suggests that we are relatively reluctant to have conversations where there is disagreement [@mutz_hearing_2006;@carlson_what_2022].
+Though we often experience emotions associated with discomfort when about to talk politics, there is significant support for the idea that these conversations are still helpful as a source of information [see @shapiro_discussion_2020] and as a source of meaningful persuasion [@levendusky_we_2021;see @suhay_persuasion_2020].
 
-Though having conversations are important for the Aristotlean conception of a democratic citizen, some evidence suggests that we are relatively reluctant to have conversations where there is disagreement [@mutz_2006_cup;@carlson_settle_2022_cup].
-Though we often experience emotions associated with discomfort when about to talk politics, there is significant support for the idea that these conversations are still helpful as a source of information [see @shapiro_et-al_2020_oh] and as a source of meaningful persuasion [@levendusky_stecula_2021_cup;see @sokhey_stapleton_2020_ohep].
-
-As others have demonstrated that there are more considerations than just partisan congruency deterimining whether you engage in a conversation before it starts [@wolak_sokhey_2022_apr], color can be one example.
+As others have demonstrated that there are more considerations than just partisan congruency determining whether you engage in a conversation before it starts [@wolak_enraged_2022], color can be one example.
 Fitting with my larger argument, color activates particular pathways in one's cognitive schema, which activate positive or negative feelings (a valanced affective state), which can drive behavior and result in information processing for attitude expression and encoding.
@@
 
-Neuroscientists and psychologists often conceptualize attitudes as an evaluation some external object [@fazio_2007_sc].
-While this is a much more broad conceptualization than the one we often have when we think of political attitudes [see @zaller_1992_cup;@zaller_feldman_1992_ajps], at their core attitudes about politics are much the same -- they are some positive or negative reaction to taxes; to let a woman choose what is best for her physical health, to make it harder for someone to buy a gun.
+Neuroscientists and psychologists often conceptualize attitudes as an evaluation some external object [@fazio_attitudes_2007].
+While this is a much more broad conceptualization than the one we often have when we think of political attitudes [see @zaller_nature_1992;@zaller_simple_1992], at their core attitudes about politics are much the same -- they are some positive or negative reaction to taxes; to let a woman choose what is best for her physical health, to make it harder for someone to buy a gun.
 Conceptualizing attitudes as an object-evaluation simplifies, but, more important, it aids in helping us get a sense of how they work.
@@
 The first foundation I rely upon is that our brain operates through a vast and complex network of connected bits of information.
-Despite popular scientific interpretations of it, the brain is not a compartmentalized file system of memories [@ralph_anderson_2018_pup] -- what I will use as a short-hand to refer to pre-existing information that we have stored in our brain and access to evaluate new information.
+Despite popular scientific interpretations of it, the brain is not a compartmentalized file system of memories [@ralph_neuroscience_2018] -- what I will use as a short-hand to refer to pre-existing information that we have stored in our brain and access to evaluate new information.
 Instead, our brain is a series of interconnected information.
 Some connections are stronger than others.
-Several things determine the strength of these connections [@kahana_et-al_2022_ohhum]; however, we encode sensory information with strong ties to affective responses [see @winkielman_et-al_2011_ohsn].
+Several things determine the strength of these connections [@kahana_laws_2022]; however, we encode sensory information with strong ties to affective responses [see @winkielman_emotion_2011].
 
@@
 That is, experts in this field conceptualize affect as you feeling positive or negative toward something.
-This appraisal happens quickly and is often considered unconscious [@sander_2013_chhan;@ralph_anderson_2018_pup].
-When exposed to new information, we often have a physiological reaction and a valanced appraisal of it [@dror_2017_er].
+This appraisal happens quickly and is often considered unconscious [@sander_cambridge_2013;@ralph_neuroscience_2018].
+When exposed to new information, we often have a physiological reaction and a valanced appraisal of it [@dror_deconstructing_2017].
 This is where attitudes and affective responses to information collide.
-To evaluate some new information to form an attitude about it, we often rely on valanced appraisals of it [@fazio_2007_sc].
-As a result, this information is central to our encoding of this information when forming a memory [@cunningham_et-al_2012_ohsn].
+To evaluate some new information to form an attitude about it, we often rely on valanced appraisals of it [@fazio_attitudes_2007].
+As a result, this information is central to our encoding of this information when forming a memory [@decety_attitudes_2011].
 
@@
 Not only does vision aid in helping us remember what visual characteristics of some plant made us sick and which one did not, but we also store visual information from social interactions.
-Visual forms of information are among the fastest to be processed [see @ames_et-al_2012_ohsn].
+Visual forms of information are among the fastest to be processed [see @ames_impression_2012].
 
 The fourth foundation, which is related to the third: information about social hierarchies, is part of our cognitive schemas.
-As social psychologists have spent more than the past five decades laying out a case for the importance of social groups on how we see our world [see @tajfel_turner_1979_ejsp], social neuroscientists have also been opening up the drywall to explore how we keep that information straight in our heads.
-Another central characteristic of the strength characterizing a connection in our head is how it fits with relevant social groups [@zink_barter_2012_ohsn].
-This explains how social groups lend themselves to such *strong* affective responses to threats [@zahn_et-al_2011_ohsn;@huddy_2001_pp].
+As social psychologists have spent more than the past five decades laying out a case for the importance of social groups on how we see our world [see @turner_social_1979], social neuroscientists have also been opening up the drywall to explore how we keep that information straight in our heads.
+Another central characteristic of the strength characterizing a connection in our head is how it fits with relevant social groups [@zink_neural_2012].
+This explains how social groups lend themselves to such *strong* affective responses to threats [@zahn_neuroscience_2011;@huddy_social_2001].
 
@@
 fans.
-The relevance by which a particular memory matters to evaluate an object depends on more than just these similarities but on factors like the recency by which we engage with the information [@kahana_et-al_2022_ohhum;@zaller_feldman_1992_ajps].
+The relevance by which a particular memory matters to evaluate an object depends on more than just these similarities but on factors like the recency by which we engage with the information [@kahana_laws_2022;@zaller_simple_1992].
 
@@
 We can take relevant features of our existing memories and use those to construct a valanced reaction to the information coming in.
-Though this complicates our ability to construct a genealogy of an attitude's associated memories [@kahana_et-al_2022_ohhum], it enables us to have a coherent imagining of how the brain functions and its tendencies.
+Though this complicates our ability to construct a genealogy of an attitude's associated memories [@kahana_laws_2022], it enables us to have a coherent imagining of how the brain functions and its tendencies.
 
@@
 However, knowing that it could very well be related to politics, you went through your index of red things in politics.
-You connected that the Republican party uses a lot of the color red, particularly more recently [see @elving_2014_npr].
+You connected that the Republican party uses a lot of the color red, particularly more recently [see @elving_color_2014].
 You have strong affective reactions to the Republican party.
 Not because the Republican party is an organism that is a predator of humans, but because you know that you are either opposed to them as a group of people or you like them because you are also Republican.
-This is how many political scientists conceptualize our valanced responses to the political parties [@iyengar_westwood_2015_ajps;@mason_2018_cup].
+This is how many political scientists conceptualize our valanced responses to the political parties [@iyengar_fear_2015;@mason_uncivil_2018].
 
@@
 Second, it argues that we can connect information as simple as color, connect it to a social group and then have our feelings toward that social group come to the forefront of our thought process.
-Beyond politics, evidence suggests that color can be a strong visual cue to identify social group membership [@pietraszewski_et-al_2015_c].
-In politics, the colors red and blue have been used consistently since the 2000 election on electoral maps [@elving_2014_npr], and as previous work has demonstrated, including the previous chapter, the connection between Republicans with the color red and Democrats with the color blue.
-Specifically red with the republican party and blue with the Democratic party [see @williams_et-al_2022_jomp].
+Beyond politics, evidence suggests that color can be a strong visual cue to identify social group membership [@pietraszewski_constituents_2015].
+In politics, the colors red and blue have been used consistently since the 2000 election on electoral maps [@elving_color_2014], and as previous work has demonstrated, including the previous chapter, the connection between Republicans with the color red and Democrats with the color blue.
+Specifically red with the republican party and blue with the Democratic party [see @williams_whats_2022].
 
 Once you have had this reaction, you are motivated to avoid or participate in this conversation.
-This is because we tend to avoid things we evaluate as unfavorable or to approach them [@valentino_et-al_2011_jop].
+This is because we tend to avoid things we evaluate as unfavorable or to approach them [@valentino_election_2011].
 Many take evidence of intense affective polarization among the public on the grounds of partisanship as an intractable societal issue due to these features.
 When we fall into this track of negative or positive thinking and are now motivated to engage with new information in a particular way, depending on whether we are motivated to engage or disengage with the information, many reasonably assume that we cannot learn anything new.
-We either support our pre-existing beliefs, or shut down and limit exposure to countervailing information [@taber_lodge_2006_ajps].
-Partisanship is a social group [@mason_2018_cup] that motivates this behavior for many people [@lodge_taber_2013_cup].
-While some hope that other social groups may provide cross-cutting forces to reduce these impacts, some evidence suggests that partisan identification has become the central politically-relevant social group that guides the rest of them [@mason_2018_cup].
+We either support our pre-existing beliefs, or shut down and limit exposure to countervailing information [@taber_motivated_2006].
+Partisanship is a social group [@mason_uncivil_2018] that motivates this behavior for many people [@lodge_rationalizing_2013].
+While some hope that other social groups may provide cross-cutting forces to reduce these impacts, some evidence suggests that partisan identification has become the central politically-relevant social group that guides the rest of them [@mason_uncivil_2018].
 
 In the context of conversing about politics, many have taken these features as a condemnation of conversations about politics.
-As we seek to avoid disagreeable conversations, particularly with those we are close to [@mutz_2006_cup], evidence of increasing homogeneity in our networks, in terms of partisan identification [@butters_hare_2022_pb], may make it easy to assume that we are always going to avoid conversations with those we disagree with and that we do not change our minds on that.
+As we seek to avoid disagreeable conversations, particularly with those we are close to [@mutz_hearing_2006], evidence of increasing homogeneity in our networks, in terms of partisan identification [@butters_polarized_2022], may make it easy to assume that we are always going to avoid conversations with those we disagree with and that we do not change our minds on that.
 
@@
 From the cognitive architecture standpoint, these tracks are not bowling alleys where you can only go down one way and cannot change course.
-Classic theories on motivated reasoning suggest that we are biased to seek information that fits with our prior beliefs but also seek out accuracy motivations [@kunda_1990_pb].
-Evidence in political science suggests that exposure to a lot of new information that runs counter to our preferred pre-existing beliefs can persuade us [@redlawsk_et-al_2010_pp].
-We can also persuade people under the right emotional conditions [@albertson_et-al_2020_ohep].
+Classic theories on motivated reasoning suggest that we are biased to seek information that fits with our prior beliefs but also seek out accuracy motivations [@kunda_case_1990].
+Evidence in political science suggests that exposure to a lot of new information that runs counter to our preferred pre-existing beliefs can persuade us [@redlawsk_affective_2010].
+We can also persuade people under the right emotional conditions [@suhay_emotional_2020].
 However, a handful of studies may mean something other than this is occurring.
-So, a recent Herculean effort to perform a meta-analysis on existing experiments on persuasion and attitude change in political science demonstrates that persuasion is possible and that these effects are not some coincidence; in fact, they seem to be about the same strength across several contexts [@coppock_2022_ucp].
-One such context is motivating people to collect accurate information [@bayes_et-al_2020_pp].
-Coincidentally, conversations about politics are often motivated by a desire to collect information [@beck_et-al_2002;@huckfeldt_2007_ohpb; see also @gastil_et-al_2002_jop;@shapiro_et-al_2020_oh].
+So, a recent Herculean effort to perform a meta-analysis on existing experiments on persuasion and attitude change in political science demonstrates that persuasion is possible and that these effects are not some coincidence; in fact, they seem to be about the same strength across several contexts [@coppock_persuasion_2022].
+One such context is motivating people to collect accurate information [@bayes_when_2020].
+Coincidentally, conversations about politics are often motivated by a desire to collect information [@beck_social_2002;@huckfeldt_information_2007; see also @gastil_civic_2002;@shapiro_discussion_2020].
 
-Further evidence suggests that the deleterious effects on democratic behavior of political conversation often occur in the context where someone is in the political minority beyond just that conversation as well [@mcclurg_2006_pb].
+Further evidence suggests that the deleterious effects on democratic behavior of political conversation often occur in the context where someone is in the political minority beyond just that conversation as well [@mcclurg_political_2006].
 While we are not particularly motivated to seek out conversations with those we disagree with, it does not necessarily mean that it leads to this motivated backlash where political conversations only act as echo-chambers.
@@
 This means we can adjust our evaluation of the object but do not necessarily forget where we have been.
-From the perspective of existing in political science, which aligns with my more interdisciplinary perspective, we still have strong motivations to protect our pre-existing beliefs and do not necessarily "weigh" or equally consider this new information relative to each other [@zaller_1992_cup].
+From the perspective of existing in political science, which aligns with my more interdisciplinary perspective, we still have strong motivations to protect our pre-existing beliefs and do not necessarily "weigh" or equally consider this new information relative to each other [@zaller_nature_1992].
 The benefits of this new information often have a timestamp on it.
 The persuasive benefits of this new information are not necessarily gone after a predetermined amount of time, but it has diminishing returns.
-A meta-analysis reveals that after about ten days, the positive effects of new information on persuasion are about one-third the size it was initially [@coppock_2022_ucp].
-This fits with evidence suggesting that evaluations often rely upon relatively recently encoded attitudes [@kahana_et-al_2022_ohhum].^[See also @zaller_1992_cup for the political science perspective.] If the new information fits with pre-existing beliefs, we continue down the same path.
+A meta-analysis reveals that after about ten days, the positive effects of new information on persuasion are about one-third the size it was initially [@coppock_persuasion_2022].
+This fits with evidence suggesting that evaluations often rely upon relatively recently encoded attitudes [@kahana_laws_2022].^[See also @zaller_nature_1992 for the political science perspective.] If the new information fits with pre-existing beliefs, we continue down the same path.
 It perhaps gets even more robust because we now have more information to tap into that fits with our prior beliefs.
@@
 However, the interaction term would test whether Democrats and Republicans differ in how they respond to these conditions instead of testing what those differences are.
-What seems more appropriate to me is a test of whether Republicans primed with politics are more willing to talk to people wearing red shirts relative to those who do not recieve the political prime and those wearing blue shirts; as a second question to look at whether Democrats who receive the political prime are more willing to talk to people wearing Blue shirts more than those who do not receive the political prime and those wearing red shirts.
+What seems more appropriate to me is a test of whether Republicans primed with politics are more willing to talk to people wearing red shirts relative to those who do not receive the political prime and those wearing blue shirts; as a second question to look at whether Democrats who receive the political prime are more willing to talk to people wearing Blue shirts more than those who do not receive the political prime and those wearing red shirts.
 I am not claiming whether strength of these relationships operates differently among Republicans and Democrats but rather that it is two separate questions.
@@
 The first reason being that these policies are hot-button issues.
-While some skeptics of my research design may be concerned with me activating strong valenced responses, I argue that these choices increase the external validity of my study in that it is realistic that most people have *some* opinion (support or do not support) on these issues.
+While some skeptics of my research design may be concerned with me activating strong valanced responses, I argue that these choices increase the external validity of my study in that it is realistic that most people have *some* opinion (support or do not support) on these issues.
 These are the things the Jane Q.
@@
 
-I first start by using the `fabricatr` package [@fabricatr] to simulate population data for both studies.
+I first start by using the `fabricatr` package [@blair_fabricatr_2022] to simulate population data for both studies.
 I generate these simulated data from data generating processes that I define.^[I include the particulars of these data generating processes in the supplementary materials.
@@
 
-On each of these samples, I fit the stated models using the `rstan` package [@rstan].
+On each of these samples, I fit the stated models using the `rstan` package [@stan_development_team_rstan_2023].
 For all models, I define my prior distribution as a normal distribution with a mean of 0 and a standard deviation of 1.
@@
 It is important to note that these sample sizes reflect the number of observations included in the models, not the total sample size.
-As many online convenience samples struggle with inattentive respondents, insincere responses, bots, etcetera [see @kennedy_et-al_2021_poq], I am going to be quite conservative and try to recruit at least 800 respondents for these two studies.
+As many online convenience samples struggle with inattentive respondents, insincere responses, bots, etcetera [see @kennedy_strategies_2021], I am going to be quite conservative and try to recruit at least 800 respondents for these two studies.
 

### 2023-08-14 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
initial drafting

---
title: |
  How does visual information influence attitudes and behaviors about groups of people?
code-repo: |
  For replication, go to: <https://github.com/DamonCharlesRoberts/book_project/chapter_4>.
author:
  - name: Damon C. Roberts
    email: damon.roberts-1@colorado.edu
    orcid: 0000-0002-4360-3675
    title: PhD Candidate
    affiliations:
      - id: CU
        name: University of Colorado Boulder
        department: Political Science
        address: 333 UCB
        city: Boulder
        region: CO 
        postal-code: 80309-0333
abstract: |
  Previous chapters of this project demonstrate that the colors red and blue convey information about the partisan affiliation of another individual, and that this information influences a number of attitudes and behaviors. This chapter's goal is to add to these findings in a couple of directions: (1) do these findings generalize to shaping the attitudes and behaviors directed towards groups of people and (2) do these results contribute to the growing literature about the effects of polarization on seemingly non-political attitudes and behaviors?

bibliography: ["../../../assets/neighborhood-chapter-references.bib"]
format:
  hikmah-pdf:
    # Spit out in drafts directory
    latex-output-dir: "../../out/prr"
    # Use biblatex-chicago
    biblatex-chicago: true
    biblio-style: authordate
    biblatexoptions: 
      - backend=biber
      - autolang=hyphen
      - isbn=false
      - uniquename=false
    geometry:
      - top=1in
      - bottom=1in
      - left=1in
      - right=1in
      - heightrounded
    linestretch: 2
    fontsize: 12pt
date: today
nocite: |
  @allaire_quarto_2022
execute:
  echo: false
  warning: false
  message: false
  cache: false
params:
  replicate: false
---
{{< pagebreak >}}

# Introduction

The previous chapters demonstrated that the colors red and blue conveyed information about the partisanship of politicians and about potential discussion partners. The previous chapters also demonstrated that these effects on attitudes also influenced behaviors such as a willingness to vote for the candidate as well as willingness to have a conversation with another about politics. The previous chapter also demonstrated two other pieces to the story: (1) that the group-based information conveyed the colors red and blue are dependent on the context, and (2) that the snap-judgments people form based on this simple visual information can shape attitudes and behaviors even when provided with more clear and explicit information about the partisan affiliation of another person.

This chapter builds on these findings to examine whether these associations between the colors red and blue with the partisanship of another can convey information about groups of people and can guide attitudes and resulting behaviors towards interactions with these groups of people. Specifically, the chapter builds upon a growing set of work suggesting that the politicultural differences between Democrats and Republicans are shaping seemingly non-political attitudes and behaviors such as one's choice in which neighborhood to live in. I argue in this chapter that the prevalence of red and blue cars in the driveways of houses in a neighborhood shift people's perceptions of the partisan composition of the neighborhood and as a result will make people less willing to move to that neighborhood when they perceive they'd be in the political minority of that neighborhood.

The implications of such findings corroborate existing work that suggests that there are an increasing number of cultural signals that people use to guess the partisanship of not just other individuals but groups of people, and that as a result partisanship and polarization are bleeding into our non-political decision-making. The implications of the argument advanced in the chapter build upon these existing findings by providing one causal mechanism as to the connection between cultural cues conveyed visually and the cognitive processing of such information. The chapter not only generalizes findings from the previous chapters to groups of people and to non-political attitudes and behaviors, but it contributes to a literature suggesting that political polarization is pervasive and is approaching universal.

# Politicultural differences and their effects

While political polarization certainly reflects a growing gap and consolidation of two camps of policy preferences and attitudes [@dellaposta_pluralistic_2020;@luders_attitude_2023], it manifests as something more consequential for our every-day experiences. Political polarization has come to reflect social groups that distinguish "us" versus "them" with increasingly fewer and fewer non-political social groups that are not wrapped up in our partisan group [@mason_uncivil_2018]. That is, we are not only holding fewer and fewer cross-cutting attitudes that moderate our political viewpoints [@luders_attitude_2023], but we also have fewer and fewer cross-cutting social groups that encourage interaction and experiences with perspectives of out-partisans [@mason_uncivil_2018]. The consequence of such phenomena is that we are becoming more and more willing to have strong negative reactions to those of the other political party and strong positive reactions to members of our political party [@iyengar_affect_2012;@iyengar_fear_2015].

The consequences of this affective polarization encourages discomfort being around those who identify with the other political party and finding comfort around those that share the same partisanship. In fact, some evidence suggests that it is even more sinister than comfort but rather predicts lower empathy for outpartisans [@allamong_screw_2021], but also a willingness to describe outpartisans as subhuman [@martherus_party_2021]. To communicate the magnitude of this dislike for out-partisans, dehumanizing language is often used by those that hold deeply racially resentful views [@utych_how_2018].

Evidence of this discomfort with out-partisans is piling up. For example, @carlson_what_2022 demonstrates that individuals perceive that they may incur social costs by engaging in a conversation with those they disagree with and expressing that disagreement. Other work corroborate this finding by suggesting that on social media individuals will be less likely to share the posts of political viewpoints they agree with if they perceive that they are in the political minority of those that would see that sharing of the post [@van_der_does_strategic_2022]. As a result, individuals have fewer outpartisans in their group of folks they regularly discuss politics with [@butters_polarized_2022].

One interesting finding of @butters_polarized_2022 is that one cause of the increasing homogeneity of people's discussion partners' partisanship is that individuals often live in counties  that are politically-homogenous. This finding reflects a growing area of research examining the geographical sorting occurring as a result of polarization among the mass public.

### 2023-08-15 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
more drafting of front-half of chapter 4 prr

@@
 The previous chapters also demonstrated that these effects on attitudes also influenced behaviors such as a willingness to vote for the candidate as well as willingness to have a conversation with another about politics.
-The previous chapter also demonstrated two other pieces to the story: (1) that the group-based information conveyed the colors red and blue are dependent on the context, and (2) that the snap-judgments people form based on this simple visual information can shape attitudes and behaviors even when provided with more clear and explicit information about the partisan affiliation of another person.
+The previous chapter also demonstrated two other pieces to the story: (1) that the group-based information conveyed by the colors red and blue are dependent on the context, and (2) that the snap-judgments people form based on this simple visual information can shape attitudes and behaviors even when provided with more clear and explicit information about the partisan affiliation of another person.
 
@@
 Specifically, the chapter builds upon a growing set of work suggesting that the politicultural differences between Democrats and Republicans are shaping seemingly non-political attitudes and behaviors such as one's choice in which neighborhood to live in.
-I argue in this chapter that the prevalence of red and blue cars in the driveways of houses in a neighborhood shift people's perceptions of the partisan composition of the neighborhood and as a result will make people less willing to move to that neighborhood when they perceive they'd be in the political minority of that neighborhood.
+I argue in this chapter that the prevalence of red and blue cars in the driveways of houses in a neighborhood shift people's perceptions of the partisan composition of the neighborhood, and as a result, will make people less willing to move to that neighborhood when they perceive they'd be in the political minority of that neighborhood.
 
@@
 That is, we are not only holding fewer and fewer cross-cutting attitudes that moderate our political viewpoints [@luders_attitude_2023], but we also have fewer and fewer cross-cutting social groups that encourage interaction and experiences with perspectives of out-partisans [@mason_uncivil_2018].
-The consequence of such phenomena is that we are becoming more and more willing to have strong negative reactions to those of the other political party and strong positive reactions to members of our political party [@iyengar_affect_2012;@iyengar_fear_2015].
+The consequence of such phenomena is that we are becoming increasingly willing to harbor strong negative feelings towards those of the other political party and strong positive affectations to members of our political party [@iyengar_affect_2012;@iyengar_fear_2015].
 
 The consequences of this affective polarization encourages discomfort being around those who identify with the other political party and finding comfort around those that share the same partisanship.
-In fact, some evidence suggests that it is even more sinister than comfort but rather predicts lower empathy for outpartisans [@allamong_screw_2021], but also a willingness to describe outpartisans as subhuman [@martherus_party_2021].
-To communicate the magnitude of this dislike for out-partisans, dehumanizing language is often used by those that hold deeply racially resentful views [@utych_how_2018].
+In fact, some evidence suggests that it is even more sinister than comfort but rather predicts lower empathy for outpartisans [@allamong_screw_2021], as well as an increased willingness to describe outpartisans as subhuman [@martherus_party_2021].
+Racists commonly use dehumanizing language to describe racial minorities [@utych_how_2018].
 
-Evidence of this discomfort with out-partisans is piling up.
-For example, @carlson_what_2022 demonstrates that individuals perceive that they may incur social costs by engaging in a conversation with those they disagree with and expressing that disagreement.
-Other work corroborate this finding by suggesting that on social media individuals will be less likely to share the posts of political viewpoints they agree with if they perceive that they are in the political minority of those that would see that sharing of the post [@van_der_does_strategic_2022].
-As a result, individuals have fewer outpartisans in their group of folks they regularly discuss politics with [@butters_polarized_2022].
+Evidence of this discomfort and its manifestations with out-partisans is piling up.
+For example, @carlson_what_2022 demonstrates that individuals perceive that they may incur social costs with friends and neighbors by engaging in a conversation with those they disagree with and expressing that disagreement, and avoid such situations as a result.
+Other work corroborate this finding by suggesting that individuals will be less likely to share the social media posts of political viewpoints they agree with if they perceive that they are in the political minority of those that would see that sharing of the post [@van_der_does_strategic_2022].
+As a result of this tendency to speak out as a political minority in front of a group of people, individuals have fewer outpartisans in their group of folks they regularly discuss politics with [@butters_polarized_2022].
 
-One interesting finding of @butters_polarized_2022 is that one cause of the increasing homogeneity of people's discussion partners' partisanship is that individuals often live in counties  that are politically-homogenous.
-This finding reflects a growing area of research examining the geographical sorting occurring as a result of polarization among the mass public.
+Building on this set of evidence, a growing area of the literature suggests that we are able to make inferences about the partisanship about other individuals, but we are able to do this for groups of people through the increasing politicultural distinctions between Republicans and Democrats.
+@hetherington_prius_2018 demonstrates that Republicans and Democrats are not just different in their policy preferences but rather that they live in different places and have different lifestyles.
+Others have replicated and built upon this work by suggesting that while there are many different types of lifestyles that Republicans and Democrats can take on, there is increasingly clear distinction between Republicans and Democrat archetypes [@rogers_politicultural_2022].
+These politicultural distinctions are clear enough that we train a computer to make accurate guesses (upwards of 80%) of the partisanship by using only images of the cars in a particular neighborhood.
+
+Though not inherently or necessarily political, our communities often act in political ways.
+For example, some evidence suggests despite variation between counties' partisan composition and lockdowns discouraging people from leaving their homes during the COVID-19 pandemic, those living in Republican counties spent more time away from home than those living in Democratic counties[@roberts_polarized_2021].
+Further, we see a place-based identity for rural individuals that predict partisanship [@cramer_politics_2016; see also @lyons_youre_2021] and characteristics like expression of anti-intellectual attitudes [@lunz_trujillo_rural_2022].
+While place-based identities could be separate or informative of partisan identities, some literature argues that partisanship may actually inform which community we choose to make ours.
+
+The consequences of the fewer cross-cutting social groups and increasingly homogenous cultural preferences of Republicans and Democrats manifest as dramatic differences in preferences about the communities that we are part of.
+@gimpel_seeking_2015 demonstrates that describing a neighborhood with explicit and implicit information (e.g., racial composition) about the partisan composition influences whether one expresses a desire or not to move and live there.
+Further work corroborates this finding by providing evidence from a number of studies which demonstrate that not only do people associate particular characteristics of a neighborhood such as the prevalence of churches with Republicans and hybrid cars with Democrats, but also that these features attract copartisans and repulse outpartisans [@motyl_how_2020].
+
+Some work suggests, however, that these expressed preferences to live near copartisans do not carryover to migration patterns [see @iyengar_affect_2012].
+In fact, there is some evidence suggesting that controlling for everything else but a political sorting, we would have less political homogeneity than we had in 2008 [@martin_does_2020].
+Further, evidence by @martin_does_2020 suggests that people switch their party registration after moving as opposed to moving to be more aligned with their party registration.
+
+The goal of the following sections is to discuss one potential mechanism that may help to tease out why there is weak observational empirical evidence for a dearth of theoretical and empirical evidence

### 2023-08-16 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
doing some more thinking

@@
 
+# Goals of chapter
+
+- Demonstrate whether snap-judgments are used and how effective they are for groups of people
+- Demonstrate how snap-judgments may be used even for non-political objects and the consequences
+- Add one potential mechanism for the puzzle of partisan sorting: attitude expression suggests it happens, but behaviorally it does not happen much.
+- Test the boundary conditions for color being a useful partisan cue
+
 # Introduction
@@
 Others have replicated and built upon this work by suggesting that while there are many different types of lifestyles that Republicans and Democrats can take on, there is increasingly clear distinction between Republicans and Democrat archetypes [@rogers_politicultural_2022].
-These politicultural distinctions are clear enough that we train a computer to make accurate guesses (upwards of 80%) of the partisanship by using only images of the cars in a particular neighborhood.
+These politicultural distinctions are clear enough that we train a computer to make accurate guesses (upwards of 80%) of the partisanship by using only images of the cars in a particular neighborhood [@gebru_using_2017].
 
 Though not inherently or necessarily political, our communities often act in political ways.
-For example, some evidence suggests despite variation between counties' partisan composition and lockdowns discouraging people from leaving their homes during the COVID-19 pandemic, those living in Republican counties spent more time away from home than those living in Democratic counties[@roberts_polarized_2021].
+For example, some evidence suggests despite variation between counties' partisan composition and lockdowns discouraging people from leaving their homes during the COVID-19 pandemic, those living in Republican counties spent more time away from home than those living in Democratic counties [@roberts_polarized_2021].
 Further, we see a place-based identity for rural individuals that predict partisanship [@cramer_politics_2016; see also @lyons_youre_2021] and characteristics like expression of anti-intellectual attitudes [@lunz_trujillo_rural_2022].
@@
 Some work suggests, however, that these expressed preferences to live near copartisans do not carryover to migration patterns [see @iyengar_affect_2012].
-In fact, there is some evidence suggesting that controlling for everything else but a political sorting, we would have less political homogeneity than we had in 2008 [@martin_does_2020].
+In fact, there is some evidence suggesting that controlling for everything else but current rates of political sorting, we would have less political homogeneity than we had in 2008 [@martin_does_2020].
 Further, evidence by @martin_does_2020 suggests that people switch their party registration after moving as opposed to moving to be more aligned with their party registration.
 
-The goal of the following sections is to discuss one potential mechanism that may help to tease out why there is weak observational empirical evidence for a dearth of theoretical and empirical evidence
+The literature on partisan sorting seems to conclude that people express a desire to sort into neighborhoods with partisans, but these attitudes do not turn into observable behaviors.
+The remainder of the chapter provides one explanation for this puzzle by demonstrating how the snap-judgment model may be at play.
+Much like the literature on the attitude expression of partisan sorting, the snap-judgment model heavily relies on the ways in which seemingly non-political information comes to be associated with one partisan group or another.
+The model also demonstrates how these snap-judgments are capable of having initial impacts on attitude expression but its effects weaken in light of explicit and countervailing information.
+
+# Snap-judgments explaining the puzzle of political sorting
+
+As discussed thus far in the chapter, non-political objects are often associated with particular partisan leanings.
+For example, the types of cars that we drive are often used and rather effective cues to one's partisanship [@hetherington_prius_2018;@gebru_using_2017].
+In the same spirit as the rest of this book, we do not need to necessarily distinguish between whether someone drives a hybrid sedan and a Ford pickup truck.
+Information giving insight into one's partisanship may even be as subtle as their color choice in car.
+
+Recall the snap-judgment model as depicted in @fig-theory.
+To apply it to the scenario of partisan sorting, absent other information about the neighborhood, the prevalence of particular colors of the cars in a neighborhood may be information that we can use to make guesses about the partisan composition of a neighborhood.
+Just as the other chapters demonstrated, when politics is salient, the associations between the colors red and blue trigger snap-judgments that inform attitude expression as well as behavioral reactions, and these effects appear to exist even once we have been given more explicit, and thus more informative, information about political persuasions.
+
+{{< include ../../../assets/_theory.qmd >}}
+
+# Experiments
+
+- Make real estate flyers that are like a conjoint providing information about the neighborhood. Do something with a "favorite car in the neighborhood" and vary whether it is a red or a blue car.

### 2023-08-17 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
a bit more organizing and drafting. Very slow progress on this one

@@
 
-# Goals of chapter
-
-- Demonstrate whether snap-judgments are used and how effective they are for groups of people
-- Demonstrate how snap-judgments may be used even for non-political objects and the consequences
-- Add one potential mechanism for the puzzle of partisan sorting: attitude expression suggests it happens, but behaviorally it does not happen much.
-- Test the boundary conditions for color being a useful partisan cue
-
 # Introduction
@@
 
-This chapter builds on these findings to examine whether these associations between the colors red and blue with the partisanship of another can convey information about groups of people and can guide attitudes and resulting behaviors towards interactions with these groups of people.
-Specifically, the chapter builds upon a growing set of work suggesting that the politicultural differences between Democrats and Republicans are shaping seemingly non-political attitudes and behaviors such as one's choice in which neighborhood to live in.
+In this chapter, I try to accomplish a few goals.
+First, I want to expand on the previous chapters by examining whether snap-judgments are used to evaluate groups of people.
+Second, I want to expand on the previous chapters by examining whether the previous findings extend to non-political objects.
+That is, this chapter seeks to further push my testing of the boundary conditions of the snap-judgment model.
+The third goal is that this chapter might address an important, but still yet to be solved, puzzle with the literature of partisan sorting that I discuss with more detail in the next section.
+
+To achieve these three goals, the chapter builds upon a growing set of work suggesting that the politicultural differences between Democrats and Republicans are shaping seemingly non-political attitudes and behaviors such as one's choice in which neighborhood to live in.
 I argue in this chapter that the prevalence of red and blue cars in the driveways of houses in a neighborhood shift people's perceptions of the partisan composition of the neighborhood, and as a result, will make people less willing to move to that neighborhood when they perceive they'd be in the political minority of that neighborhood.
+While these snap-judgments influence attitude expression toward reported willingness to move to a neighborhood, subsequent information such as job opportunities, performance of schools, average wages to cost of living ratio, and other information limits the efficacy of these initial judgments.
+This seems to provide one mechanism explaining why partisan sorting is not observationally as extreme as we might expect given extensions of the literature on affective polarization and experimental and self-reported survey evidence.
 
@@
 
-Though not inherently or necessarily political, our communities often act in political ways.
+Though not inherently or necessarily political, our communities often collectively act in political ways.
 For example, some evidence suggests despite variation between counties' partisan composition and lockdowns discouraging people from leaving their homes during the COVID-19 pandemic, those living in Republican counties spent more time away from home than those living in Democratic counties [@roberts_polarized_2021].
@@
 Much like the literature on the attitude expression of partisan sorting, the snap-judgment model heavily relies on the ways in which seemingly non-political information comes to be associated with one partisan group or another.
-The model also demonstrates how these snap-judgments are capable of having initial impacts on attitude expression but its effects weaken in light of explicit and countervailing information.
+The model also demonstrates how these snap-judgments are capable of having initial impacts on attitude expression, but its effects weaken in light of explicit and countervailing information.
 
@@
 As discussed thus far in the chapter, non-political objects are often associated with particular partisan leanings.
-For example, the types of cars that we drive are often used and rather effective cues to one's partisanship [@hetherington_prius_2018;@gebru_using_2017].
+For example, the modal car in a neighborhood conveys the partisan composition of the whole neighborhood [@hetherington_prius_2018;@gebru_using_2017].
 In the same spirit as the rest of this book, we do not need to necessarily distinguish between whether someone drives a hybrid sedan and a Ford pickup truck.
 Information giving insight into one's partisanship may even be as subtle as their color choice in car.
+For a reader who thinks "hypothesizing about car color choice and partisanship is a reach", I agree.
+As stated at the outset of the chapter, the goal of the chapter is to extend past applications of the snap-judgment model to explicitly partisan objects such as yard signs as we did in Chapter 2 and to really challenge the model by looking at non-political objects that many never associate with partisanship.
 
 Recall the snap-judgment model as depicted in @fig-theory.
-To apply it to the scenario of partisan sorting, absent other information about the neighborhood, the prevalence of particular colors of the cars in a neighborhood may be information that we can use to make guesses about the partisan composition of a neighborhood.
-Just as the other chapters demonstrated, when politics is salient, the associations between the colors red and blue trigger snap-judgments that inform attitude expression as well as behavioral reactions, and these effects appear to exist even once we have been given more explicit, and thus more informative, information about political persuasions.
+Extending the literature on partisanship as a superordinate social identity and affective polarization, we should expect that the partisan composition of a neighborhood would matter to people.
+In examining yard signs, @makse_politics_2019 demonstrate that people dislike having neighbors that do not share the same partisan affiliation as them.
+The motivation this comes from a desire to be in the majority of those around you with the same political views [see @van_der_does_strategic_2022].
+While this appears to be something important to people, information about the partisan composition of a neighborhood might be inaccessible to most.
+Therefore, we are motivated to rely on heuristics to help with this [@motyl_how_2020].
+One useful and efficient heuristic to convey partisanship is the use of color as other chapters have demonstrated.
+If we are concerned about the partisanship of our neighbors, we may rely on information such as the color of our potential neighbors' cars to infer their partisanship.
+
+To most of us, we likely do not trust this as a basis to infer partisanship as other forms of information such as whether a potential neighbor is displaying a political yard sign.
+However, these usually only show up every couple of years during the election season and are displayed by those who tend to be highly politically active -- so, they are not universally displayed [@makse_politics_2019].
+Absent explicit information about the partisan composition, we might be willing to accept that the information we are basing our inferences on as
 

### 2023-08-17 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
fix formatting
a little bit more editing between meetings

@@
 Recall the snap-judgment model as depicted in @fig-theory.
+The model suggests that so long as politics is salient, the colors red and blue should act as a symbolic association with Republicans and Democrats, respectively.
+This association will trigger a pre-conscious and potent process that involves an activation of an affective state depending on one's prior experiences with Republicans and Democrats.
+If, when viewing those colors, activates memories of Republicans and Democrats that are negative, then your affective state will have a negative valance.
+If those activated memories are positive, then your affective state will have a positive valance.
+You will associate your affective state with the object that started the process due to the object's association with memories and their associations to Republicans and Democrats.
+This snap-judgment that you form will not only influence your expressed attitudes toward that object, but will influence motivations to engage more with the object or to avoid it.
+With new information, we can refine which memories we use to evaluate the object and can therefore form a response that is better informed.
+However, the snap-judgment persists and will have influences on which memories connected to that new information we are accessing.
+Therefore, the snap-judgment still has effects on our attitude expression and behaviors even with new information.
+
 Extending the literature on partisanship as a superordinate social identity and affective polarization, we should expect that the partisan composition of a neighborhood would matter to people.
@@
 - Make real estate flyers that are like a conjoint providing information about the neighborhood. Do something with a "favorite car in the neighborhood" and vary whether it is a red or a blue car.
+
+{{< pagebreak >}}

### 2023-08-18 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
a little bit more writing

@@
 However, these usually only show up every couple of years during the election season and are displayed by those who tend to be highly politically active -- so, they are not universally displayed [@makse_politics_2019].
-Absent explicit information about the partisan composition, we might be willing to accept that the information we are basing our inferences on as
+Additionally, other decisions such as the color of the house are determined by Homeowners Associations (HOAs).
+The choices of car colors are less constrained by other external factors.
+So, we may reasonably assume that if we see a neighborhood with a significant number of red cars, we may assume that the local sports team color must be red.
+However, if we are searching for cues toward the partisan composition of the neighborhood, we may then assume that the neighborhood has a large number of Republicans, whether that is accurate or not.
 

### 2023-08-21 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
a little bit of drafting of the experimental design

@@
 
-To most of us, we likely do not trust this as a basis to infer partisanship as other forms of information such as whether a potential neighbor is displaying a political yard sign.
-However, these usually only show up every couple of years during the election season and are displayed by those who tend to be highly politically active -- so, they are not universally displayed [@makse_politics_2019].
+To most of us, we likely do not trust the color of a car as a basis to infer partisanship as other forms of information such as whether a potential neighbor is displaying a political yard sign.
+However, political yard signs usually only show up every couple of years during the election season and are displayed by those who tend to be highly politically active -- so, they are not universally displayed [@makse_politics_2019].
 Additionally, other decisions such as the color of the house are determined by Homeowners Associations (HOAs).
@@
 However, if we are searching for cues toward the partisan composition of the neighborhood, we may then assume that the neighborhood has a large number of Republicans, whether that is accurate or not.
+Once we have used that association between the colors red and blue with partisan affiliation, we will form a snap-judgment of our neighbors based on the color of their cars when absent other information.
+That impression will then elicit a positive or negative attitude toward the neighbors and neighborhood as well as encourage a congruent behavioral reaction such as wanting to avoid the neighborhood or an affinity toward it.
+This impression and behavioral reaction forms pre-consciously and is quickly adjusted with new information from other sources of information.
+However, the impression constrains what memories are accessible and therefore constrains the attitude expression and behavioral motivations toward objects even when we collect more information that either fits with or goes against our initial impression.
+
+There are many characteristics of a neighborhood besides car color that can better convey information about the partisanship of a neighborhood such as whether it is mixed use, in an urban or rural setting, whether there are Black Lives Matter flags, and whether the cars tend to be pickup trucks or sedans.
+However, the role of color is to act as a form of pre-conscious impression formation.
+While all of these alternative, and better, cues towards partisanship may be present, they are more complicated forms of visual information that will require more laborious processing before attitude formation.
+The point of the snap-judgment model is to illustrate how extremely simple visual information, such as color, shapes our thinking due to the cognitive processes that underlie impression formation and the effects of impressions after particular neurological paths are made "hot".
 
@@
 
-# Experiments
+# Experimental test
 
-- Make real estate flyers that are like a conjoint providing information about the neighborhood. Do something with a "favorite car in the neighborhood" and vary whether it is a red or a blue car.
+Applying the snap-judgment model to an individual's choice to move to a neighborhood yields the following hypotheses: with all else equal, Republicans that see that the modal color of car is Red are more likely to report wanting to move to the neighborhood than if the modal car color were blue ($H_1$); with all else equal, Democrats that see the modal color of Blue are more likely to report wanting to move to the neighborhood than if the modal car color were red ($H_2$); once we include more information about a neighborhood's partisan composition, then the strength of their desire to live in a neighborhood will increase if congruent with their partisan affiliation ($H_3$) and will weaken if incongruent with their partisan affiliation ($H_4$).
+
+To test these hypotheses, I conduct an experiment involving a fictional real estate posting.
+The treatment involves randomly assigning participants to view one of two versions of a fictional real estate posting.
+The characteristics of the neighborhood are exactly the same between the two conditions except for the "favorite car" in the neighborhood.
+In the first condition the "favorite car" is a red SUV.
+In the second condition, the "favorite car" is the same make and model of SUV as in the first condition, but blue.
+Participants are then given a scale from 0-10 to rate the neighborhood and are presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?" Once the participants have responded to these questions, they are then given a "second page" describing the neighborhood.
+The information subjects sees depends on which of two conditions they are randomly assigned into.
+In one condition, the information indicates that the neighborhood is "40 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition presents the same information but instead describes the neighborhood as "10 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." With this new information, I ask participants "With this new information, please update your rating of the neighborhood" on the 0-10 scale and are again presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?"
 

### 2023-08-23 chapter_2/src/appendix.qmd
doing some editing

@@
-# Chapter 2 Appendix {#sec-2-a}
+## Chapter 2 Appendix {#sec-2-a}
 
@@
 
-## A note about discrepancies between the main text and the pre-registered report
+### A note about discrepancies between the main text and the pre-registered report
 
@@
 
-## Measures
+### Measures
 
@@
 
-## Hypothesis 2
+### Hypothesis 2
 
@@
 
-### Models
+#### Models
 
-These first two models are ordered logistic regressions.
+These first two models are nominal logistic regressions.
 The outcome of interest is a 3-item response of whether they perceived the owner of the yard sign to be a Republican, a Democrat, or neither.
 This variable was recoded to be 1 = Democrat, 2 = Independent, and 3 = Republican.
-In the first ordered logistic regression, I predict this outcome with a indicator variable of whether the participant saw a white yard sign (value of 0) or saw a red yard sign (value of 1).
+In the first nominal logistic regression, I predict this outcome with a indicator variable of whether the participant saw a white yard sign (value of 0) or saw a red yard sign (value of 1).
 
@@
 list_fitted_split_1 <- list(
-  "Red treatment" = list_fitted[["h_2"]][["red"]]
-  , "Blue treatment" = list_fitted[["h_2"]][["blue"]]
+  "Red treatment" = list_fitted[["h_2"]][["red_multinomial"]]
+  , "Blue treatment" = list_fitted[["h_2"]][["blue_multinomial"]]
 )
@@
   list_fitted_split_1
+  , coef_map = c(
+    "b_mu2_trial_1_red_stimuli" = "Red yard sign (Independent)"
+    , "b_mu3_trial_1_red_stimuli" = "Red yard sign (Republican)"
+    , "b_mu2_trial_1_blue_stimuli" = "Blue yard sign (Independent)"
+    , "b_mu3_trial_1_blue_stimuli" = "Blue yard sign (Republican)"
+    , "b_mu2_Intercept" = "Intercept - Independent"
+    , "b_mu3_Intercept" = "Intercept - Republican"
+    )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm 
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , "of claiming candidate is not a Democrat."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , "of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  , output = "latex"
+)
+```
+
+There is also a case to be made about using ordered logistic regressions instead of multinomial logistic regressions if you think of partisanship identification fitting across a continuum and my measure crudely adding break points.
+@tbl-hypothesis-2-ordered demonstrates that my substantive conclusions do not change when interpreting a fitted ordered logistic regression instead of a fitted multinomial logistic regression like in @tbl-hypothesis-2-main.
+
+```{r}
+#| label: tbl-hypothesis-2-ordered
+#| tbl-cap: Full results for reported ordered logistic regression models for $H_2$
+# Redefine names
+list_fitted_split_1_alt <- list(
+  "Red treatment" = list_fitted[["h_2"]][["red_ordinal"]]
+  , "Blue treatment" = list_fitted[["h_2"]][["blue_ordinal"]]
+)
+
+# Change goodness of fit stuff
+gm <- list(
+  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
+  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
+  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
+)
+# Make table
+modelsummary(
+  list_fitted_split_1_alt
   , coef_map = c(
@@
 
-### Posterior Predictive Checks
+#### Posterior Predictive Checks
 
@@
 #| fig-subcap:
-#|   - Red treatment
-#|   - Blue treatment
+#|   - Red treatment (multinomial)
+#|   - Blue treatment (multinomial)
+#|   - Red treatment (ordered)
+#|   - Blue treatment (ordered)
+list_ppc[["h_2"]][["red_multinomial"]]
+list_ppc[["h_2"]][["blue_multinomial"]]
+list_ppc[["h_2"]][["red_ordinal"]]
+list_ppc[["h_2"]][["blue_ordinal"]]
+```
+
+```{r}
+#| label: fig-h-2-ppc-cont
+#| layout-ncol: 2
+#| fig-cap: Posterior predictive checks of models in $H_2$ (cont.)
+#| fig-subcap:
 #|   - Red treatment (Moderated by age)
@@
 #|   - Blue treatment (Moderated by colorblindness)
-
-list_ppc[["h_2"]][["red"]]
-list_ppc[["h_2"]][["blue"]]
 list_ppc[["h_2"]][["red_interact"]]
@@
 
-## $H_{2a}$
+```{r}
+#| label: fig-h-2-ppc-cont-cont
+#| layout-ncol: 2
+#| fig-cap: Posterior predictive checks of models in $H_2$ (cont.)
+#| fig-subcap:
+#|   - Blue treatment (Moderated by colorblindness)
+list_ppc[["h_2"]][["blue_colorblind"]]
+```
 
-An aditional analysis I include is to examine the bounds by which these effects hold if we vary the amount of partisan colors are on a yard sign.
+### $H_{2a}$
+
+An additional analysis I include is to examine the bounds by which these effects hold if we vary the amount of partisan colors are on a yard sign.
 The second and third trials introduce variations of the yard signs in the first trial that include more white and even more color for the opposing political party (if red or blue condition).
@@
 
-### Models
+#### Models
 
@@
 model_names <- list(
-  "Trial 2 - Red treatment" = list_fitted[["h_2a"]][["trial_2_red"]]
-  , "Trial 2 - Blue treatment" = list_fitted[["h_2a"]][["trial_2_blue"]]
+  "Trial 2 - Red treatment" = list_fitted[["h_2a"]][["trial_2_red_multinomial"]]
+  , "Trial 2 - Blue treatment" = list_fitted[["h_2a"]][["trial_2_blue_multinomial"]]
   , "Trial 2 - Single model" = list_fitted[["h_2a"]][["trial_2_single_model"]]
@@
   , coef_map = c(
-    "b_trial_2_red_stimuli" = "Red yard sign"
-    , "b_trial_2_blue_stimuli" = "Blue yard sign"
+    "b_mu2_trial_2_red_stimuli" = "Red yard sign (Independent)"
+    , "b_mu3_trial_2_red_stimuli" = "Red yard sign (Republican)"
+    , "b_mu2_trial_2_blue_stimuli" = "Blue yard sign (Independent)"
+    , "b_mu3_trial_2_blue_stimuli" = "Blue yard sign (Republican)"
     , "b_trial_2_red_stimuli_alt" = "Red yard sign"
     , "b_trial_2_blue_stimuli_alt" = "Blue yard sign"
+    , "b_mu2_Intercept" = "Intercept - Independent"
+    , "b_mu3_Intercept" = "Intercept - Republican"
+    , "b_Intercept[1]" = "Intercept 1"
+    , "b_Intercept[2]" = "Intercept 2"
+    )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is not a Democrat (Columns 1 and 2) or is a Republican (Column 3)."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  , output = "latex"
+)
+```
+
+```{r}
+#| label: tbl-hypothesis-2a-cont
+#| tbl-cap: Full results for models testing bounds of $H_2$ (cont.)
+# Redefine names
+model_names <- list(
+  "Trial 3 - Red treatment" = list_fitted[["h_2a"]][["trial_3_red_multinomial"]]
+  , "Trial 3 - Blue treatment" = list_fitted[["h_2a"]][["trial_3_blue_multinomial"]]
+  , "Trial 3 - Single model" = list_fitted[["h_2a"]][["trial_3_single_model"]]
+)
+
+# Change goodness of fit stuff
+gm <- list(
+  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
+  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
+  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
+)
+# Make table
+modelsummary(
+  model_names
+  , coef_map = c(
+    "b_mu2_trial_3_red_stimuli" = "Red yard sign (Independent)"
+    , "b_mu3_trial_3_red_stimuli" = "Red yard sign (Republican)"
+    , "b_mu2_trial_3_blue_stimuli" = "Blue yard sign (Independent)"
+    , "b_mu3_trial_3_blue_stimuli" = "Blue yard sign (Republican)"
+    , "b_trial_3_red_stimuli_alt" = "Red yard sign"
+    , "b_trial_3_blue_stimuli_alt" = "Blue yard sign"
+    , "b_mu2_Intercept" = "Intercept - Independent"
+    , "b_mu3_Intercept" = "Intercept - Republican"
     , "b_Intercept[1]" = "Intercept 1"
@@
 ```{r}
-#| label: tbl-hypothesis-2a-cont
+#| label: tbl-hypothesis-2a-ordered
+#| tbl-cap: Full results for ordered logistic regressions testing bounds of $H_2$
+# Redefine names
+model_names <- list(
+  "Trial 2 - Red treatment" = list_fitted[["h_2a"]][["trial_2_red_ordinal"]]
+  , "Trial 2 - Blue treatment" = list_fitted[["h_2a"]][["trial_2_blue_ordinal"]]
+)
+
+# Change goodness of fit stuff
+gm <- list(
+  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
+  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
+  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
+)
+# Make table
+modelsummary(
+  model_names
+  , coef_map = c(
+    "b_trial_2_red_stimuli" = "Red yard sign"
+    , "b_trial_2_blue_stimuli" = "Blue yard sign"
+    , "b_Intercept[1]" = "Intercept 1"
+    , "b_Intercept[2]" = "Intercept 2"
+    )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  , output = "latex"
+)
+```
+
+```{r}
+#| label: tbl-hypothesis-2a-cont-ordered
 #| tbl-cap: Full results for models testing bounds of $H_2$ (cont.)
@@
 model_names <- list(
-  "Trial 3 - Red treatment" = list_fitted[["h_2a"]][["trial_3_red"]]
-  , "Trial 3 - Blue treatment" = list_fitted[["h_2a"]][["trial_3_blue"]]
-  , "Trial 3 - Single model" = list_fitted[["h_2a"]][["trial_3_single_model"]]
+  "Trial 3 - Red treatment" = list_fitted[["h_2a"]][["trial_3_red_ordinal"]]
+  , "Trial 3 - Blue treatment" = list_fitted[["h_2a"]][["trial_3_blue_ordinal"]]
 )
@@
     , "b_trial_3_blue_stimuli" = "Blue yard sign"
-    , "b_trial_3_red_stimuli_alt" = "Red yard sign"
-    , "b_trial_3_blue_stimuli_alt" = "Blue yard sign"
     , "b_Intercept[1]" = "Intercept 1"
@@
 #| fig-subcap:
-#|   - Red treatment (Trial 2)
-#|   - Blue treatment (Trial 2)
+#|   - Red treatment (Trial 2 - Multinomial)
+#|   - Blue treatment (Trial 2 - Multinomial)
+#|   - Red treatment (Trial 2 - Ordered)
+#|   - Blue treatment (Trial 2 - Ordered)
+list_ppc[["h_2a"]][["trial_2_red_multinomial"]]
+list_ppc[["h_2a"]][["trial_2_blue_multinomial"]]
+list_ppc[["h_2a"]][["trial_2_red_ordinal"]]
+list_ppc[["h_2a"]][["trial_2_blue_ordinal"]]
+```
+
+```{r}
+#| label: fig-h-2a-ppc-cont
+#| layout-ncol: 2
+#| fig-cap: Posterior predictive checks of models in $H_2$ (cont.)
+#| fig-subcap:
 #|   - Combined model (Trial 2)
-#|   - Red treatment (Trial 3)
-#|   - Blue treatment (Trial 3)
+#|   - Red treatment (Trial 3 - Multinomial)
+#|   - Blue treatment (Trial 3 - Multinomial)
+#|   - Red treatment (Trial 3 - Ordered)
+list_ppc[["h_2a"]][["trial_2_single_model"]]
+list_ppc[["h_2a"]][["trial_3_red_multinomial"]]
+list_ppc[["h_2a"]][["trial_3_blue_multinomial"]]
+list_ppc[["h_2a"]][["trial_3_red_ordinal"]]
+```
+
+```{r}
+#| label: fig-h-2a-ppc-cont-cont
+#| layout-ncol: 2
+#| fig-cap: Posterior predictive checks of models in $H_2$ (cont.)
+#| fig-subcap:
+#|   - Blue treatment (Trial 3 - Ordered)
 #|   - Combined model (Trial 3)
-
-list_ppc[["h_2a"]][["trial_2_red"]]
-list_ppc[["h_2a"]][["trial_2_blue"]]
-list_ppc[["h_2a"]][["trial_2_single_model"]]
-list_ppc[["h_2a"]][["trial_3_red"]]
-list_ppc[["h_2a"]][["trial_3_blue"]]
+list_ppc[["h_2a"]][["trial_3_blue_ordinal"]]
 list_ppc[["h_2a"]][["trial_3_single_model"]]
@@
 
-## Hypothesis 3
+### Hypothesis 3
 
-### Models
+#### Models
 
@@
 
-### Posterior predictive Checks
+#### Posterior predictive Checks
 
@@
 
-## Hypothesis 4
+### Hypothesis 4
 
@@
 
-## Hypothesis 5
+### Hypothesis 5
 
@@
 
-### Models
-
-<!-- 
-NOTE TO SELF
-
-NEED TO REWRITE SOME OF THIS TO ACCOUNT FOR BETTER PERFORMANCE AFTER LOCATION-FXS
--->
+#### Models
 
@@
 
-### Posterior predictive checks
+#### Posterior predictive checks
 

### 2023-08-23 chapter_2/src/manuscript.qmd
doing some editing

@@
 
-Now that I have presented some background and have introduced the snap-judgment model of politically-relevant visual information, this chapter is a first attempt to tackle the question at hand.
-Do colors provide political information that shape attitudes?
-There are two goals that I am hoping to achieve in this chapter.
+Now that I have presented some background and have introduced the snap-judgment model of politically-relevant visual information, this chapter is a first attempt to tackle the question, "Do colors provide political information that shape attitudes?" There are two goals that I am hoping to achieve in this chapter.
 The first is to convince the reader that the colors red and blue convey affiliative information.
-Second, that these connections between colors and political groups can shape political outcomes.
+The second is that these connections between colors and political groups can shape political outcomes.
 
-This chapter applies the snap-judgment model to a simple case.
-The use of color on yard signs used by campaigns in elections.
+This chapter applies the snap-judgment model to a simple case: the use of color on yard signs used by campaigns in elections.
 I focus on yard signs as they are a common form of campaign marketing and evidence suggests that they can shape individual behavior [@makse_politics_2019] and electoral outcomes [@green_effects_2016].
 Additionally, I start by examining the colors red and blue.
-While there are other colors that may provide political information -- black and white for Black Lives Matter and Blue Lives Matter movements, the overarching goal of this book is to lay the foundation for a larger research agenda in visual political psychology [see @bucy_editors_2021].
-Without such foundations, we are studying complex cases and circumstances upon assumptions without a grasp of how, and if they even do, occur in the cases that might seem trivial to some.
-While there indeed is empirical and experiential evidence suggesting that the Republicans use the color red and Democrats use the color blue [@schloss_politics_2014;@williams_whats_2022], there is yet to be a theoretical framework that explains how these connections happen at the individual level.
-It may also be unsatisfying that I do not address *how* these connections came about.
-While the connections between Republicans with the color red and Democrats with the color blue seemed to quicken after the 2000 Presidential election where news networks covering the election began to consistently use those colors [@elving_color_2014], it is not clear if this was a deliberate choice or whether this was yet another symptom of an increasingly polarized public who just want easily digestible information about politics so they can move on to other matters in their lives.
-An undertaking to address such a question is for a different book, perhaps.
+While there are other colors that may provide political information -- black and white for Black Lives Matter and Blue Lives Matter movements, the overarching goal of this book is to lay the foundation for a larger research agenda in visual political psychology [@bucy_editors_2021].
+Without such foundations, we would be jumping into the study of complex cases and circumstances without a firm grasp of how things matter on a more fundamental level.
 
-To give a preview for this chapter, I propose two studies to explore the claims I make in this chapter.
-Yard signs are a simple yet effective source of campaign branding for political candidates as they convey information that is often useful for voters -- partisanship [@campbell_american_1969].
+Before getting into things, it is worth noting that while there indeed is empirical and experiential evidence suggesting that Republicans use the color red and Democrats use the color blue [@schloss_politics_2014;@williams_whats_2022], there is currently no theoretical framework that explains how these connections happen at the individual level.
+As a side note, one might find it unsatisfying that I do not address *how* these associations between color and the parties came about.
+While the connections between Republicans with the color red and Democrats with the color blue seemed to quicken after the 2000 Presidential election (with news networks consistently using those colors in campaign coverage [@elving_color_2014]), it is not clear if this was a deliberate choice, or whether this was yet another symptom of an increasingly polarized public.
+An undertaking to address the specifics of this part of American political history would likely be a different book project.
+
+To preview, in this chapter I propose two studies to evaluate the claims I make about yard signs.
+Yard signs are a simple yet effective source of campaign branding for political candidates as they convey information that is often useful for voters' partisanship [@campbell_american_1969].
 As yard signs are a simple and static form of campaign advertising, they cannot rely heavily on more complicated forms of information.
 However, one form of information they rely on and vary in is their color.
-With these characteristics, yard signs are an ideal candidate both from a statistical standpoint and also substantive for an experimental test of my claims in this chapter.
-From a statistical standpoint, as they are static forms of party branding they have fewer moving parts, which help isolate the effect that color has on shaping attitudes.
+With these characteristics, yard signs are an ideal candidate both from a design and substantive standpoint.
+From a design standpoint, as they are static forms of party branding they have fewer moving parts, which helps isolate the effect that color has on shaping attitudes.
 From a substantive standpoint, while we understand that yard signs matter to campaigns, we have yet to systematically explore more simple design choices such as color.
 
-In [Study 1](#sec-study-1), I conduct an online experiment that examines whether the public notice color and whether their attitudes are shaped by "Republican Red" and "Democratic Blue" on the yard signs of a fictional candidate.
-Based on informal conversations with campaign marketing consultants, it appears that campaigns are aware that the colors red and blue betray the partisanship of a candidate to voter.
-So in [Study 2](#sec-study-2), I examine whether campaigns react to the partisan composition of an electorate as a response to these individual-level patterns.
-I do this by examining how electoral context shapes variation in using these partisan colors.
-While these two studies highlight endogenous processes, I am not necessarily arguing that either of these patterns only flow one way.
-In fact, I believe that there is a necessary feedback loop between the parties and their base of support.
-Voters support candidates who signal strong allegiance to the party to increase their chances for electoral success [@utych_voter-centric_2020] and the parties are motivated to distinguish themselves [@lee_insecure_2016;@clifford_how_2020] as a result of their high levels of ideological and affective polarization [@dietrich_using_2021;@enders_issues_2021].
-Again, to tease out the direction of blame is more appropriate for another time.
+In [Study 1](#study-1), I conduct an online experiment that examines whether the public notice color and whether their attitudes are shaped by "Republican Red" and "Democratic Blue" on the yard signs of a fictional candidate.
+Based on informal conversations with campaign marketing consultants, it appears that campaigns are aware that the colors red and blue betray the partisanship of a candidate to voters.
+Accordingly, in [Study 2](#study-2), I examine whether campaigns react to the partisan composition of an electorate, as a response to these individual-level patterns.
+Specifically, I do this by examining how electoral context shapes variation in the use of these partisan colors.
+While these two studies highlight endogenous processes, to be clear, I am not arguing that either of these patterns only one way.
+In fact, I believe that there is a necessary feedback loop between the parties and their bases of support.
+Voters support candidates who signal strong allegiance to the party to increase their chances for electoral success [@utych_voter-centric_2020], and the parties are motivated to distinguish themselves [@lee_insecure_2016;@clifford_how_2020] as a result of their high levels of ideological and affective polarization [@dietrich_using_2021;@enders_issues_2021].
+I leave teasing out directionality for subsequent analyses.
 
-In the first study, I find that individuals do shift their perceptions of political candidates in response to the use of the colors red and blue, they consistently and strongly associate Republicans with the color red and Democrats with the color blue, and their willingness to vote for a candidate can be dramatically different depending on whether the color used aligns with the individual's partisan identification.
-The second study suggests that candidates in districts where Democrats have a higher vote share use more blue on their yard signs while also using less red.
-The implications of this are that the colors red and blue convey political information.
-More generally, I suspect other colors and more complex forms of visual information such as symbols are capable of conveying political information as well.
-Perhaps most interesting among these results is that the color red and blue alone can make individuals willing to vote for a candidate.
-The association between the colors red and blue are strong enough that individuals express a willingness to cast a vote for a candidate based on the color of their yard sign without confirming any of their policy stances or their partisan affiliation.
-These tendencies, even if based on a hunch for the folks on the ground, seem to lead to descriptive differences in the use of these colors as it guides strategy.
-The following chapters dig a bit deeper into the idea that colors can shape attitudes by pitting the information individuals get from color against information gleaned from explicit policy stances.
+In the [first study](#study-1), I find that individuals do shift their perceptions of political candidates in response to the use of the colors red and blue -- they consistently and strongly associate Republicans with the color red and Democrats with the color blue, and their willingness to vote for a candidate can be dramatically different depending on whether the color used aligns with their partisan identification.
+The [second study](#study-2) suggests that candidates in districts where Democrats have a higher vote share use more blue on their yard signs (wile also using less red).
+
+These findings bring much needed evidence in support of the conventional wisdom that the colors red and blue convey political information.
+Perhaps what is most intriguing about my results is that I find that the colors red and blue alone seem to make individuals willing to vote for a candidate.
+The association between the colors red and blue are strong enough that individuals express a willingness to cast a vote for a candidate based on the color of the candidate's yard sign; this occurs without the individual confirming that the candidate matches their policy stances or partisan affiliation.
+These tendencies, even if only based on a hunch among the professionals on the ground, seem to lead to descriptive differences in the use of these colors with respect to strategy.
+The following chapters dig a bit deeper into the idea that colors can shape attitudes, pitting the information individuals get from color against information gleaned from explicit policy stances.
 
@@
 
-A central theme of an edited issue of *The International Journal of Press/Politics* is that visual politics is important and understudied [@lilleker_introduction_2019 ].
-Those who are engaged in these questions attribute these challenges to methodological sophistication and the difficult task of interdisciplinary theorizing [@gerodimos_interdisciplinary_2019; @bucy_editors_2021].
+A central theme of an edited issue of *The International Journal of Press/Politics* is that visual politics is important, yet understudied [@lilleker_introduction_2019].
+Those who are engaged in these questions attribute these challenges to methodological sophistication and the difficult task of interdisciplinary theorizing [@gerodimos_interdisciplinary_2019].
 
-The rise of television consumption changed the focus of the medium in the research for political communication scholars [@hall_jamieson_creating_2014].
-In a similar way, so does the rise of image-based social media and has set new agendas.
+The rise of television consumption changed the focus on particular mediums for political communication scholars [@hall_jamieson_creating_2014].
+In a similar way, the rise of image-based social media has set new agendas.
 For several methodological and disciplinary reasons, the visual aspects of television were of little focus in the literature [@bucy_editors_2021].
-However, the news organizations and politicians are responding to the ubiquitous use of the public to use image-dominant social media platforms like TikTok and Instagram, by joining such platforms.
-They are relatively active on these platforms as well.
-Scholars need to make this transition to integrate the role of simple visual information into our theories of political information processing (abbreviated as *pip*) and attitude formation.
+However, today news organizations and politicians are responding to the ubiquitous use of image-dominant social media platforms like TikTok and Instagram, by joining and posting on such platforms.
+Scholars need to make this transition as well, integrating the role of simple visual information into theories of political information (abbreviated as *pip*) and attitude formation.
 
 How does politically-relevant visual information matter to politics?
-From an evolutionary-biological perspective, visual information has been a common source of information for millions of years that a variety of single-and-multi-cell organisms rely upon to evaluate their environment [see @grabe_image_2009, Chapter 1 for a useful discussion].
-Visual information processing, as an ancient biological invention, the human brain is organized around the processing of it.
+From an evolutionary-biological perspective, visual information has been a common source of information for millions of years -- information tat a variety of single-and-multi-cell organisms have relied upon to evaluate their environment [@grabe_image_2009, see Chapter 1 for a useful discussion].
+As an ancient biological invention, the human brain is organized around visual information processing.
 Reflecting on this, many scholars of neuroscience argue that visual information is the fastest form of information processing for humans.
@@
 
-Approached from a different perspective, as humans are cognitive misers \index{cognitive misers}, visual information in the realm of politics provides efficient information to voters about politically-relevant actors and events [@lilleker_power_2019].
-Evidence suggests that even simple party branding on yard signs has an emotional appeal and encourages a shift in attitudes toward the person who owns the yard sign [@makse_politics_2019].
-That is, even branding as simple as yard signs appears to influence the attitudes of those who view them.
-However, like all types of party branding, there remain questions about the individual visual components' contribution.
+Approached from a different perspective, as humans are cognitive misers, visual information in the realm of politics provides efficient information to voters about politically-relevant actors and events [@lilleker_power_2019].
+Evidence suggests that even simple party branding on yard signs can have an emotional appeal, potentially encouraging a shift in attitudes toward the person who owns the yard sign [@makse_politics_2019].
+That is, even branding as simple as yard signs appears to influence the attitudes of people who view them.
+However, as with all types of party branding, questions remain about individual visual components' contributions.
 
 More simple forms of visual information are likely even more efficient forms of information.
-In the context of the United States, the "Republican red" and "Democratic blue" is a relatively recent invention that likely has significant import in an era of significant effort by the parties to distinguish themselves from each other [@clifford_how_2020] and where voters toe the party line [@utych_voter-centric_2020].
+In the context of the United States, the "Republican Red" and "Democratic Blue" is a relatively recent invention, but one that likely has significant import in an era where the parties make efforts to distinguish themselves from each other [@clifford_how_2020], and where voters toe the party line [@utych_voter-centric_2020].
 Since the 2000 presidential election, the media have consistently used red on their electoral maps in "horserace" journalism to represent Republicans and blue to represent Democrats [@elving_color_2014].
 The supposed consequence is that Democrats now report a preference for the color blue over the color red, and Republicans report a preference for the color red over the color blue [@schloss_politics_2014].
-Others have demonstrated the strategic choices that candidates make on branding choices -- including color -- based on the types of information they want to convey to voters to distinguish them from their rivals [see @williams_whats_2022].
+Others have demonstrated the strategic choices that candidates make on branding choices -- including color -- based on the types of information they want to convey to voters, and to distinguish themselves from their rivals [@williams_whats_2022].
 
-In western Europe, voters are better at connecting the ideological positioning of a party with the color they use in their branding [@casiraghi_colors_2022].
-The ability to do so is strengthened when the party is longer-surviving and is more prominent [@casiraghi_colors_2022].
+In western Europe, voters are likely better at connecting the ideological positioning of a party with the color they use in their branding [@casiraghi_colors_2022].
+The ability to do so is strengthened when the party is longer-surviving and more prominent [@casiraghi_colors_2022].
 The use of politically-relevant colors activates biases toward pre-existing ideological and partisan preferences among voters in a Spanish sample [@losada_maestre_color_2022].
-And male and female candidates in the United States use different colors -- among other things such as fonts -- in their campaign branding to convey distinguishing information about themselves [@williams_whats_2022].
-What remains unclear is whether these patterns in the United States are just simply patterns or whether there are identifiable causes to these patterns.
-While political psychologists are increasingly interdisciplinary and rely on psychology and neuroscience, it is relatively unclear how color can convey information as complex as politics.
-Further, it is unclear whether such a simple type of information has enough efficacy to shape political outcomes such as voting intention.
+In the United States, male and female candidates use different colors -- among other things such as fonts -- in their campaign branding to convey distinguishing information about themselves [@williams_whats_2022].
+What remains unclear is whether these patterns in the United States are meaningful.
+While political psychologists are increasingly interdisciplinary and rely on insights from fields like neuroscience, it remains relatively unclear whether and how color can convey complex information about politics.
+Further, it remains unclear whether such a simple type of information has enough efficacy to shape political outcomes such as vote intention.
 This chapter is a first cut at addressing these open questions.
@@
 
-Existing models of political information processing (abbreviated here as *pip*) primarily focus on complex forms of political information such as policy positions communicated verbally or through text.
-As individuals process visual information before other sorts of information, we might expect that they may form a snap judgment or the initial appraisal of an object.
+Existing models of political information processing (abbreviated here as *pip*) primarily focus on complex forms of political information, such as policy positions, communicated verbally or through text.
+As individuals process visual information before other sorts of information, we might expect that they may form a snap-judgment or the initial appraisal of an object with visual information as opposed to these more complex forms of information.
 
-Color and other simple visual information are processed much quicker and occur more frequently than text-based information that may be communicated through a news article [@mehta_blue_2009].
-As the color and other visual information are processed differently, we should also consider its use as political information.
-As visual information is affectively encoded [@cimbalo_emotionally_1978], it can affect the affective state and processing of more complex information, such as text.
-The visual information provides a snap judgment or an impression of the object through faster processing and activates particular neurological processes that influence subsequent information appraisals [@ames_impression_2012].
-This implies that snap-judgments from visual forms of political information may have downstream effects that shape the way in which we engage with forms of political information that we traditionally consider.
+Color and other simple visual information are processed much quicker an occur more frequently than text-based information that may be communicated, for example, through a news article [@mehta_blue_2009].
+But as color and other visual information are processed differently, we should also consider their use as political information.
+As visual information is affectively encoded [@cimbalo_emotionally_1978], it can affect the affective state and the latter processing of more complex information, such as text.
+The visual information provides a snap-judgment or an impression of the object through faster processing, and activates particular neurological processes that influence subsequent information appraisals [@ames_impression_2012].
+This implies that snap-judgments from visual forms of political information may have downstream effects that shape the way in which we engage with traditionally considered forms of political information.
 
@@
 An attitude represents an accessible, valanced evaluation of associated prior information and experiences.
-This conceptualization fits with that of the Object-Evaluation Associations Model [@russell_h_fazio_attitudes_2007].
-As opposed to viewing attitudes as a latent collection of memories, it views attitudes as measurable evaluations of memories.
+This conceptualization fits with that of the Object-Evaluations Association Model [@fazio_attitudes_2007].
+As opposed to viewing attitudes as a latent collection of memories, this model views attitudes as measurable evaluations of memories.
 As memories are at the core of an attitude, the association of memories with its evaluative component [see @kensinger_affective_2022] contributes to the perspective that attitudes are affective.
-This implies that we should be able to measure attitudes but that such an operationalization requires careful consideration of the context's role in any given measure of an attitude as they result from memories [@russell_h_fazio_attitudes_2007].
-In this chapter, I consider colors' effect on shaping attitudes about a political object -- a yard sign.
-As I hold this constant in the chapter, concerns about variation in what people are thinking about when seeing the color red and blue is less of a concern in this chapter.
-Later chapters grapple with this consideration.
+This implies that we should be able to measure attitudes, but that such an operationalization requires careful consideration of the context's role in any given measure of an attitude (as they result from memories) [@fazio_attitudes_2007].
+In this chapter, I consider color's effect on shaping attitudes about a political object -- a yard sign.
+As I hold this constant in the chapter, concerns about the variation in what people are thinking about when seeing the color red and blue are less important here, though later chapters grapple with this consideration.
 
 In line with existing theories of *pip*, I conceptualize attitudes as associative.
-This means that attitudes may be unstable - not randomly, in any case.
-As attitudes are associative, they manifest slightly differently depending on the associative paths activated [@russell_h_fazio_attitudes_2007].
+This means that attitudes may be unstable (though not in a random sense).
+That is, as attitudes are associative, they manifest slightly differently depending on the associative paths activated [@fazio_attitudes_2007].
 The retrieval of relevant memories to the attitude depends on many factors, such as the recency of the event, the similarity of the context, and the importance or salience of the memory [@kahana_laws_2022].
@@
 This illustrates my need to build upon the reigning models of *pip*.
-Colors may act as a contextual feature that may lead to this variability in how a given set of political information may shape attitudes.
+Colors may act as a contextual feature that may lead to variability in how a set of political information may shape attitudes.
 
 Colors are associative and are affectively encoded [@cimbalo_emotionally_1978].
-When individuals access a memory, they do not just recall an object, but they may recall visual information such as the color of an object [@mehta_blue_2009].
+When individuals access a memory, they do not just recall an object, but they may recall visual information, such as the color of an object [@mehta_blue_2009].
 Due to these features, colors can be processed pre-consciously and very quickly [@mehta_blue_2009].
-As they are affectively encoded, their associations with particular memory contribute to the evaluative component of the memory.
-For example, individuals associate colors like red with anger and arousal [@valdez_effects_1994], whereas individuals associate blue with things like happiness and pleasure [@dandrade_colors_1974].
-This means that colors are compelling as contextual information shaping the subsequent processing and integration of "traditional" forms of political information to construct an attitude.
-As the preference for a particular color correlates with political attitudes [@schloss_politics_2014], they may have some causal influence upon political attitudes; rather than just a correlation with them.
+As they are affectively encoded, their associations with particular memories contribute to the evaluative component of the memory.
+For example, individuals associate colors like red with anger and arousal [@valdez_effects_1994], whereas they associate blue with things like happiness and pleasure [@dandrade_colors_1974].
+This means that colors are compelling as contextual information that shapes the subsequent processing and integration of "traditional" forms of political information used to construct attitudes.
+As the preference for a particular color correlates with political attitudes [@schloss_politics_2014], colors may have some causal influence upon political attitudes.
 
 According to the literature in affective neuroscience, visual information is processed in various parts of the brain, such as the visual cortex [@goldstein_sensation_2017].
-These types of processes do not occur in particular areas of the brain as some like to think.
-As attitudes are associative, components of our brain works as this complex highway connecting different types of information.
+These types of processes do not occur in discrete regions of the brain, as some like to think.
+As attitudes are associative, components of the brain work as a complex highway connecting different types of information.
 As a result, the processing of visual information will activate other areas of the brain and will make associated paths "hot." One such area is the amygdala.
 Neuroscientists believe that as visual information is quickly and subconsciously processed, the amygdala takes and appraises it based on the paths it activated; this generates a simple affective response to such information [@winkielman_emotion_2011].
-More complex, categorical emotion occurs later in conscious processing [@winkielman_emotion_2011].
 
-To provide a less technical description of the processes occuring here, once politically-relevant visual information is detected, the retina passes it to the brain.
-Once there, the brain attempts to classify the visual information by activating networks of neurons associated with the current information.
+A less technical description of the processes occurring here might look something like this: once politically-relevant visual information is detected, the retina passes it to the brain.
+Once there , the brain attempts to classify the visual information by activating networks of neurons associated with the current information.
 With these activated pathways, the brain also attempts to appraise such information based on quick classification.
@@
 
-These fast affective classifications are valanced rather than the more laborious categorization of specific emotions (e.g., anger, anxiety, fear, happy).
-What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_emotions_2000], I conceptualize affect as a more extensive system that considers emotion only as a conscious classification process that occurs later than initial valanced appraisals of an object [@sander_cambridge_2013; @ralph_neuroscience_2018].
+These fast affective classifications are valanced rather than the more laborious categorization of specific emotions (e.g., anger, anxiety, fear, happiness).
+What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_emotions_2000], I think of affect as a more extensive system -- one that considers emotion a conscious classification process that occurs after the initial valanced appraisals of an object [@sander_cambridge_2013;@ralph_neuroscience_2018].
 That is, emotion -- the complex classification of appraisals -- is a conscious component of affect.
-The pre-conscious process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_emotion_2011; @dror_deconstructing_2017].
+By contrast, the pre-conscious process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_emotion_2011;@dror_deconstructing_2017].
 
-The pre-conscious appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_election_2011; @ralph_neuroscience_2018].
-This has evolutionary roots for survival [@ralph_neuroscience_2018; @parker_blink_2003].
-While affective appraisals can lead to complex motivations, such as anxiety leading to motivations for information seeking [@marcus_emotions_2000], affective appraisals are valanced and are more automatic [@winkielman_emotion_2011].
-These affective appraisals lead to a desire to either retract or engage more with the object [@valentino_election_2011].
-The snap judgment resulting from the automatic processing of politically relevant visual information should likely lead to an affective response that motivates either a desire to engage more with the object or disengage.
+The pre-conscious appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_election_2011;@ralph_neuroscience_2018].
+This has evolutionary roots for survival [@ralph_neuroscience_2018;@parker_blink_2003].
+While affective appraisals can lead to complex motivations, such as anxiety leading to motivations for information seeking [@marcus_emotions_2000], affective appraisals are valanced and more automatic [@winkielman_emotion_2011].
+These affective appraisals lead to a desire to either retract or engage more with an object [@valentino_election_2011].
+The snap-judgment resulting from the automatic processing of politically relevant visual information should likely lead to an affective response that motivates either a desire to engage or disengage further with an object.
 
-While the visual information may encourage a particular immediate reaction to engage or disengage from the information, subsequent information processing and more conscious processing adjusts this initial appraisal generated by the snap judgment [@kensinger_affective_2022].
-While subsequent information may amend one's snap-judgment, the snap-judgment nevertheless influences the processing of subsequent information by activating particular paths, which is later encoded as associated with the object as it converts to a memory [@lodge_rationalizing_2013; @kensinger_affective_2022].
+While the visual information may encourage a particular immediate reaction to engage or disengage from the other information, subsequent information processing and more conscious processing adjusts this initial appraisal generated by the snap-judgment [@kensinger_affective_2022].
+While subsequent information may amend one's snap-judgment, the snap-judgment nevertheless influences the processing of subsequent information by activating particular paths -- this is later encoded as associated with the object as it converts to a memory [@lodge_rationalizing_2013;@kensinger_affective_2022].
 
@@
 The explanation for this is that people are finding ways to come up with counterarguments to such information.
-Therefore, it is possible that we may expect that those interacting with visual information of a political party for which they disagree with spend more time looking at those objects.
+Therefore, we may expect that those interacting with visual information from a political party with which they disagree to possibly spend more time looking at those objects.
 
-@fig-snap-judgement-model presents an illustration of the snap-judgment model.
+@fig-theory presents an illustration of the snap-judgment model.
 
-```{mermaid}
-%%| label: fig-snap-judgement-model
-%%| fig-cap: Snap judgement model
-%%| fig-width: 6
-%%{init: {'theme':'base', 'themeVariables':{'primaryColor':'#ffffff', 'primaryBorderColor': '#000000'}}}%%
-graph TD;
-    A[Detection of politically-relevant visual information] --> B(Activation of retrieval mechanism);
-    B --> C[Memory and contiguous paths hot];
-    C --> D[Appraisal of hot autonomous nervous system];
-    D --> E1[Negative Valence];
-    D --> E2[Positive Valence];
-    E1 --> F1[Disengagement motivation];
-    E2 --> F2[Attention activated];
-    F1 --> |Neg. new information| G1[Encoded as negative];
-    F1 --> |Pos. new information| G2[Encoded as positive];
-    F2 --> |Neg. new information| G3[Encoded as negative];
-    F2 --> |Pos. new information| G4[Encoded as positive];
-    G1 --> H1[Strengthens negative path];
-    G2 --> H2[Weakens negative path];
-    G3 --> H3[Weakens positive path];
-    G4 --> H4[Strengthens positive path];
-    G2 --> |forgotten| H1;
-    H2 --> |reinforced| G2;
-    H3 --> |reinforced| G3;
-    G3 --> |forgotten| H4;
-```
+{{< include ../../assets/_theory.qmd >}}
 
@@
 Say you are driving down a highway.
-At 65 miles an hour, you are traveling at about 95 feet per second at this speed.
+At 65 miles per hour, you are traveling at about 95 feet per second at this speed.
 You split your attention.
@@
 Out of the corner of your eye, you see a sign.
-It is not a road sign because it is not on the familiar white or yellow background with black lettering.
+It is not a road sign because it is not the familiar white or yellow background with black lettering.
 It is election season.
@@
 You now are racking your brain to think about who that is.
-If you are politically engaged, you might come to that recognition of the name quickly or it may take you significantly longer if you are less politically engaged [see @kahana_laws_2022].
-You figure out that they are a Republican politician.
-You may have come to this with the help of the fact that every year you have seen yard signs on this stretch of highway.
-You know that when you see those electoral maps pop up on your news app on your phone that the electoral forecasts always represent Republican support with red and blue for Democrats.
-Once you have figured out who this person is, with the help of this other information, you react: "ugh, that guy is too loyal to Trump" or "yeah!
-He's loyal to Trump".
-You've expressed a political attitude.
+If you are politically engaged, you might come to that recognition of the name quickly, or it may take you significantly longer if you are less politically engaged because it is information you do not have to access often [see @kensinger_affective_2022].
+You figure out that this is a Republican politician.
+You may come to this with the help of the fact that every year you have seen yard signs on this stretch of the highway.
+You know that when you see those red-blue maps pop up on news apps on your phone that the electoral forecasts always represent Republican support with red, and blue for democrats.
+Once you have figured out who this person is with the help of this other information, you react: "ugh, that guy is too loyal to Trump," or "yeah!
+He's loyal to Trump." You've expressed a political attitude.
 
-What the snap-judgment model predicts is happening in your head is that as soon as the light that bounces off the sign to produce a particular wavelength hits your eyes, your brain is already trying to make sense of this information.
+What the snap-judgment model predicts is happening in your head is something like the following: as soon as the light bounces off the sign (to produce a particular wavelength) hits your eyes, your brain is already trying to make sense of this information.
 This is a valuable tool for survival that biology has optimized for millions of years [@parker_blink_2003].
-Rather than slowly processing the visual information and finding yourself in the jaws of a predator or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and subconsciously [@newell_unified_1990].
-To make sense of such information, it accesses familiar information similar to what it is currently attempting to process for efficiency [@kahana_laws_2022].
-This is accessing memories and contains valanced information [@kensinger_affective_2022]: should I avoid this, or is it pleasant?
+Rather than slowly processing the visual information and finding yourself in the jaws of a predator, or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and subconsciously [@newell_unified_1990].
+To make sense of such information, it accesses familiar information similar to what it is currently attempting to process, and it does this for the purposes of efficiency [@kahana_laws_2022].
+This means accessing memories that contain valanced information [@kensinger_affective_2022]: should I avoid this, or is it pleasant?
 Once the brain has finished such processing, it can pass its prediction to your conscious memory.
 Once you form a reflex of avoid or approach, this opens up space for your brain to process the more complex information: to take the patterns of the light as shapes that construct symbols and letters.
-This comes later because this information not only requires access to information about what it *is* but also what it *means*; once you understand what it means, you have the information necessary to evaluate it.
+This comes later because this information not only requires access to information about what it *is*, but also about what it *means*.
+Once you understand what it means, you have the information necessary to evaluate it.
 
 The snap-judgment model predicts that you first process the colors of the yard sign.
-You access associative memory to figure out what those particular wavelengths represent: red, white, blue?
-As these colors are associated with different emotional states [see @cimbalo_emotionally_1978] and the resulting behavioral consequences, your brain starts sending signals to the rest of your body to prepare it to react [see @sander_cambridge_2013; @dror_deconstructing_2017].
+You access associative memory to figure out what those particular wavelengths represent; red, white, blue?
+As these colors are associated with different emotional states [see @cimbalo_emotionally_1978] and the resulting behavioral consequences, your brain starts sending signals to the rest of your body to prepare for reaction [see @sander_cambridge_2013;@dror_deconstructing_2017].
 You now need to figure out what the rest of that information was.
@@
 It appears that there were some white letters on the sign.
-There was an "E," a "L," an "E," a "C," and a "T." That creates the word "ELECT." Meaning to vote for.
-There were some more letters on the sign: an "M," an "I," a "T," a "C," and an "H." A name.
-The full name is "Mitch McConnell".
-Since it is about politics, it must be a politician named Mitch McConnell.
-Now imagine the information was the same, except the color was blue.
-You may take more time to figure out how that Mitch McConnell person is and come to your reaction to seeing their yard sign.
-This is because, without the color red, you first are thinking about Democrats who are named Mitch McConnell.
+There was an "E," an "L," and "E," a "C," and a "T." That creates the word "ELECT." Meaning to vote for.
+There were some more letters on the sign: an "M," and "I," a "T," a "C," and an "H." A name.
+The full name is "Mitch McConnell." Since it is about politics, it must be a politician named Mitch McConnell.
+Now imagine the information was the same, but the color was blue.
+You may take more time to figure out who that Mitch McConnell person is and come to your reaction to seeing the yard sign.
+This is because without  the color red, you are first thinking about Democrats who are named Mitch McConnell.
 Only when you come up empty on your mental Rolodex do you figure out that it is the Republican Mitch McConnell.
@@
 For example, researchers find activation of parts of the brain, such as the anterior insula, when we see someone in our social group outperformed by someone from the out-group [see @zink_neural_2012].
-The anterior insula activity is associated with physical and emotional pain, not just for ourselves but also for others [@adolphs_emotion_2011].
+The anterior insula activity is associated with physical and emotional pain, and not just for ourselves but also for others [@adolphs_emotion_2011].
 Others have also observed that when seeing someone part of a high-status social group, there is an increase in activity in the sensorimotor cortex and supplementary motor area, indicating more activity in the areas of the brain that encourage movement [@zink_know_2008].
@@
 
-There is significant evidence supporting the theory that our partisan identification reflects more than just our attitudes about politics but a social identity [see @campbell_american_1969; @mason_uncivil_2018] that guides our attitudes [see @achen_democracy_2016; @white_selling_2014; also @bullock_elite_2011].
+There is significant evidence supporting the theory that our partisan identification reflects more than just our attitudes about politics, but a social identity [@campbell_american_1969;@mason_uncivil_2018] that guides our attitudes [see @achen_democracy_2016;@white_selling_2014; also @bullock_elite_2011].
 As our political attitudes reflect shared views among co-partisans [@pickup_expressive_2020], the congruence between political information and our partisan identification influences our reactions to such political information.
-This means that the visual information we glean from politics will likely motivate those neurological features of social groups and explain the resulting behavioral manifestations reacting to such information.
-That information is also likely to be processed at different rates as well.
+This means that the visual information we glean from politics will likely motivate the neurological features of social groups, and explain the resulting behavioral manifestations in response to such information.
+That information is also likely to be processed at different rates.
 That is, while visual information carries general affective associations, we should also expect associations between politically-relevant colors with partisan identification.
@@
 
-From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that these colors that they notice shape perceptions about the person and ideological symbol represented in the branding -- meaning that they express different levels of preference for receiving more information that is similar to what they saw and their levels of preference for supporting such a campaign ($H_{2}$); that the consistency of information explains more positive perceptions -- simple visual information with more complex "traditional" information ($H_{3}$); this positive and consistent information is processed quicker than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) in line with their primary objective of reelection [@fenno_congressmen_1973; @mayhew_congress_1974].
-A summary of these hypotheses are included in @tbl-hypotheses.
+From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that colors observed shape perceptions about the person and ideological symbol represented in the branding -- this means that individuals express different levels of preference for receiving more information that is consistent with their preferences ($H_{2}$); that the consistency of information explains more positive perceptions (i.e., simple visual information paired with more complex "traditional" information) ($H_{3}$); positive and consistent information is processed more quickly than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) -- this is inline with their primary objective of reelection [@fenno_congressmen_1973;@mayhew_congress_1974].
+A summary of these hypotheses is presented in @tbl-hypotheses.
 
@@
 
-The purpose of [Study 1](#sec-study-1) is to examine whether the color choices on an almost ubiquitus form of campaign branding -- yard signs -- influence people's perceptions of political candidates.
+The purpose of [Study 1](#sec-study-1) is to examine whether the color choices on an almost ubiquitous form of campaign branding -- yard signs -- influence people's perceptions of political candidates.
 Evidence suggests that yard signs *do* matter in shaping political attitudes [@makse_politics_2019], vote intentions [@makse_politics_2019], and even electoral outcomes [@green_effects_2016].
@@
 Using yard signs in this study, I test the first four hypotheses I derive from the snap-judgment model.
-First, [Study 1](#sec-study-1) tests the claim that individuals do indeed notice the color of electoral yard signs.
-Next, it tests the claim that these colors that individuals detect influence the viewer's evaluations of the yard sign and the candidate represented on it.
-[Study 1](#sec-study-1) then tests the claim that the effects on perception are moderated by how consistent the color is with the more complex information displayed on the yard sign.
-Finally, [Study 1](#sec-study-1) examines whether positive information that contains consistency is processed quicker than negative or inconsistent information.
+First, I test the claim that individuals do indeed notice the color of electoral yard signs.
+Next, I test the claim that these colors that individuals detect influence their evaluations of the yard sign and the candidate represented on it.
+I then test the claim that the effects on perception are moderated by how consistent the color is with the more complex information displayed on the yard sign.
+Finally, [Study 1](#study-1) closes with an examination of whether positive information that contains consistency is processed more quickly than negative or inconsistent information.
 That is, do partisans quickly detect and encode information from a clearly co-partisan political candidate?
@@
 
-I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia[^color_influence_pre-reg_anon-4] and are provided with a demographics and political attitudes questionnaire.
-As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
-This questionnaire includes common questions about the participant's ascriptive and descriptive characteristics and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
+I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where indiiduals are provided with a demographics and political attitudes questionnaire As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
+This questionnaire includes common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
 
@@
 
-I include those questions in the questionnaire due to expectations that they may act as confounds in my hypotheses.
-I include some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these are correlates with partisan identification [see @campbell_american_1969; @mason_uncivil_2018].
-Though political knowledge does predict the strength of an individual's partisan identification [@lodge_rationalizing_2013], attention paid to politics is likely a more important confounding variable here.
+I include those questions due to expectations that they may act as confounds for my hypotheses.
+I include some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these correlates with partisan identification [see @campbell_american_1969;@mason_uncivil_2018].
+Though political knowledge does predict the strength of an individual's partisan identification [@lodge_rationalizing_2013], attention paid to politics is likely a more important confounding variable for my application.
 The purpose of color in politics is to act as a heuristic for people (a cognitive shortcut).
-If individuals are aware of the tendency for Republicans to use and be associated with the color red and Democrats with the color blue, the degree to which they know factual information about politics is not entirely relevant.
-On the other hand, those that pay no attention to politics, whatsoever, may be less likely to be aware of such associations.
+On the one hand, if individuals are aware of the tendency for Republicans to use and be associated with the color red and the degree to which they know factual information about politics is not entirely relevant.
+On the other hand, those that pay no attention to politics whatsoever may be less likely to be aware of such associations.
 Additionally, those who express less interest in politics are also likely to identify as more moderate when asked about their ideology and partisan identity [@klar_independent_2016].
 
-Additionally, I include a question about the respondent's sex assigned at birth and about whether they have received a diagnosis of any color blindness.
+Additionally, I include a question about the respondent's sex assigned at birth, and importantly, about whether they have received a diagnosis of *any color blindness*.
 As some individuals may possess undiagnosed colorblindness, asking about their sex assists in covariate balance.
-I additionally include an open-ended question asking participants to describe their "first memory of a political event." The use of an open-ended question helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [see @kennedy_strategies_2021].
-Given estimates using these exclusion criteria, I would expect that upwards of 40% of my original sample will fail these attention checks [@kennedy_strategies_2021]; thus, the large sample size.
+I additionally include an open-ended question asking participants to describe their "first memory of a political event." The use of open-ended questions helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [@kennedy_strategies_2021].
+Given estimates using these exclusion criteria, I would expect that upwards of 40% of my original sample will fail these attention checks [@kennedy_strategies_2021], thus, the large sample size.
 
 I then present participants with an instruction screen informing them of the task for the experiment.
-In the first trial of the experiment, participants I randomly presented participants with two of three possible yard signs, one at a time.
-These yard signs are simple with the text "Riley Ready to Lead" and a solid background color of either "Republican Red," "Democratic Blue," or White.[^color_influence_pre-reg_anon-6] There is an added component to this, however.
-
-[^color_influence_pre-reg_anon-6]: See the supplementary information to view all of the stimuli used in [Study 1](#sec-study-1).
+In the first trial of the experiment, I randomly presented participants with one of three possible yard signs, one at a time.
+These yard signs are simple, with the text "Riley Ready to Lead" and a solid background color of either "Republican Red," "Democratic Blue," or White.^[See [Appendix](#sec-2-a) to view all of the stimuli used in [Study 1](#study-1).] There is an added component to this, and the other two trials.
 
@@
 As the participants move their cursor around the screen, it tracks the coordinates of the cursor along with the "dwell" time of the cursor in that particular coordinate.
-One primary benefit of Mouseview.js is that it allows researchers to field their experiments outside of a lab-based setting -- while providing results that robustly correlate with the results from a design employing eye-tracking hardware [@anwyl-irvine_mouseviewjs_2022].
-This allows researchers to rely less on convenience samples, which are common with eye-tracking studies.
-For my design, I am particularly concerned about reliance on a convenience sample due to variations in participants' ability to detect and process color in the U.S.
-population relative to a student sample.
+One primary benefit of Mouseview.js is that it allows researchers to field their experiments outside of a lab-based setting, while providing results that robustly correlate with the results from a design employing eye-tracking hardware [@anwyl-irvine_mouseviewjs_2022].
+This allows researchers to rely less on student convenience samples, which are common with eye-tracking studies.
+For my design, I am particularly concerned about reliance on a student convenience sample due to variation in participants' ability to detect and process color in the U.S.
+population.
 This means that Mouseview.js is a handy tool for my study.
-A published pilot version of the experiment used in [Study 1](#sec-study-1) on [Pavlovia](https://run.pavlovia.org/damoncroberts/diss_ch_1_pre-reg/?__pilotToken=c74d97b01eae257e44aa9d5bade97baf&__oauthToken=9a645f267f9b83c8ebb48e60093bae5a746da56a6c824b8343389a9329fa2365).
 
-When viewing each yard sign in the first trial, there is a blur over a substantial portion of the screen.
-At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].[^color_influence_pre-reg_anon-7] Participants move their cursor to explore the yard sign.
-I allot 5000 ms to perform the exploration until the image goes away to encourage a consistent and short duration to explore the image.[^color_influence_pre-reg_anon-8] After exploring each image, I asked participants what colors were on the yard sign and whether they felt that the candidate represented on the yard sign was a Democrat, a Republican, or Neither.
+When viewing each yard sign in each of the three trials, there is a blur over a substantial portion of the screen.
+At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[I include a screenshot providing an example of what the participants are able to see with the blur included in the [Appendix](#sec-2-a).] Participants move their cursor to explore the yard sign.
+I allot 5000 ms to perform the exploration before the image goes away; this is to encourage a consistent and short duration to explore the image.^[In marketing research, some studies give participants about 6000 ms in eye-tracking studies to examine a brand and formulate an intention to purchase a product or not [@wedel_review_2008].
+With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure evoking images uses 1000 ms; but is intended to be an extended amount of time [@anwyl-irvine_mouseviewjs_2022].] After exploring each image, I ask participants what colors were on the yard sign and whether they felt that the candidate supposedly owning the yard sign was a Democrat, a Republican, or Neither.
 After viewing both images, I ask subjects to indicate their preference among the two images.
@@
 The goal is to ensure that variation in where participants explore the image is not dependent on a non-standard starting point for their cursor.
-I additionally utilize a gaussian blur for the overlay of the image rather than a solid overlay obstructing the participant's view.
-This gaussian blur allows participants to see a blurred visual field beyond the cursor.
+I additionally utilize a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
+The gaussian blur allows participants to see a blurred visual field beyond the cursor.
 This allows participants to see enough to take purposeful action to explore blurred parts of the image that attract them [@anwyl-irvine_mouseviewjs_2022].
@@
 
-[^color_influence_pre-reg_anon-7]: I include a screenshot providing an example of what the participants are able to see with the blur included in the supplementary materials.
-
-[^color_influence_pre-reg_anon-8]: In marketing research, some studies give participants about 6000 milliseconds in eye-tracking studies to examine a brand and to formulate an intention to purchase a product or not [@wedel_review_2008].
-With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure-evoking images uses 10000 milliseconds; but is intended to be an extended amount of time [@anwyl-irvine_mouseviewjs_2022].
-
-There are three more trials that are much like the first trial.
-What is different between the two other trials is that I vary the amount of color that is on the yard signs (trials 2 and 3).
-I provide more textual information that deviates from the association of Republicans with red and Democrats with blue (trial 4).
-Examples of all of these yard signs are included in the appendix.
-For readers interested in the more technical details, the appendix acommpanying this chapter also includes a table of the data collected in the experiment -- @tbl-study-1-measures; reports full results, posterior predictive checks, and more detailed discussions for all of the models used in the remainder of this section.^[Unless noted otherwise, the reflection of uncertainty in the models are credible intervals at the 90% level.
-This should not be equated with the frequentist practice of often reporting confidence intervals at the 95% level as credible intervals at this level often are extremely unstable and, more importantly, are interpreted differently.
-For example, a credible interval at the 90% level can be interpreted as: the probability that the true effect is in that interval.
+ There are two more trials that are much like the first trial.
+What is different between the two other trials is that I vary the amount of color that is on the yard sign.
+Examples of all of these yard signs are included in the [Appendix](#sec-2-a).
+For readers interested in the more technical details, the [Appendix](#sec-2-a) accompanying this chapter also includes a table of the data collected in the experiment -- @tbl-study-1-measures; reports full results, posterior predictive checks, and more detailed discussions for all of the models used in the remainder of this section.^[Unless noted otherwise, the reflection of uncertainty in the models are credible intervals at the 90% level.
+This should not be equated with the frequentist practice of reporting confidence intervals at the 95% level, as credible intervals at this level are often extremely unstable and, more importantly, are interpreted differently.
+For example, a credible interval at the 90% level can be interpreted as: the probability that the true effect is within that interval.
 This contrasts with a confidence interval used in the frequentist framework which is interpreted as: upon repeated samples, 90% of the confidence intervals contain the true effect.
@@
  @tbl-study-1-descriptives presents some characteristics of the sample on the whole.
-The sample is relatively young with a mean age of 36.6 years old, few report being diagnosed with colorblindness, about 40% of the sample identifies as female, 70% of the sample identifies as White while only 10% report being Hispanic and Black.
+The sample is relatively young (mean age of 36.6 years old), and with few reporting having been diagnosed with colorblindness.
+About 40% of the sample identifies as female, and about 70% of the sample identifies as White (while only 10% report being Hispanic and Black).
 The average respondent in the sample reports leaning Democratic.
@@
 I collect the first measure through recording the movement of the subjects' cursors along the x-and-y-axes.
-The second measure accounts for the amount of time participants' cursor lingers over a particular coordinate on their screen.
+The second measure accounts for the amount of time participants' cursors linger over a particular coordinate on their screen.
 Presumably, the more participants explore the yard sign, the more they are finding visual information that they can use to evaluate the candidate.
-While these two measures are simple proxies and are not sufficient measures of "noticing the yard sign," they allow us to get a sense of the patterns by which people explore the yard signs across treatment conditions.
-It also helps with my confidence in the degree to which variation between the treatments among different groups of participants are due to actual differences in how people processed these treatments and not due to random chance.
+While these two measures are simple proxies and are not direct measures of "noticing the yard sign," they allow us to get a sense of the patterns by which people explore the yard signs across treatment conditions.
+This also bolsters my confidence in the degree to which variation between the treatments among different groups of participants is due to actual differences in how people processed these treatments, and not due to random chance.
 
@@
 
-@tbl-h1-trial-1, @tbl-h1-trial-2, and @tbl-h1-trial-3 report the average difference in milliseconds and pixels along the x-and-y-axis of the subjects' screen when exploring the yard signs.
+@tbl-h1-trial-1, @tbl-h1-trial-2, and @tbl-h1-trial-3 report the average difference in milliseconds and pixels along the x-and-y-axis of the subjects' screens.
 These tables demonstrate a few things.
@@
 Overall, it appears that people viewed the yard signs differently depending on which yard sign they were looking at.
-Now, I turn to exploring how features about the subjects themselves may shape the way they interact and respond to this visual information on the yard signs.
-Though, I will note that the data on the timing and cursor location is much more noisy than I had originally anticipated.
-However, as the tests of the next few questions demonstrate, there seem to be systematic differences between individuals that saw either a red, white, or blue yard sign despite holding everything else but the color constant between them.
-While I am a bit skeptical of the data here as it is noisy, I think the next pieces of empirical evidence suggest support for this hypothesis as well.
+Now, I turn to exploring how features about the subjects themselves may shape the way that individuals interact and respond to this visual information on the yard signs.
+The data on the timing and cursor location is much more noisy than I had originally anticipated.
+However, as the tests of the next few questions demonstrate, the evidence supports the general conclusion of the systematic differences between individuals that saw either a red, white, or blue yard sign (despite holding everything else but the color constant).
 
@@
 
-To address the question of whether the colors affect perceptions of the candidate and the yard sign, I ask participants to report whether they perceived the candidate to be a partisan -- either Republican, Democrat, or as non-partisan immediately after viewing each image.
-Everything on the yard signs remains constant except for the color.
-As representations of ideology are associated with more than just political views but things like space [@mills_political_2016] and color [@losada_maestre_color_2022], differences between respondents on the perceived political affiliations of the candidate should be more than "by chance" differences.
-However, differences occur based on the associations between red and blue with partisanship and the lack of political information that the color white conveys.
+To address the question of whether colors affect perceptions of the candidate and the yard sign, I ask participants to report whether they perceived the candidate to be a partisan -- either a Republican, Democrat, or as non-partisan -- immediately after viewing each image.
+Everything on the yard sign remains constant except for the color.
+As representations of ideology are associated with more than just political views, but also things like space [@mills_political_2016] and color [@losada_maestre-color_2022], differences between respondents on the perceived political affiliations of the candidate should be more than "by chance" differences.
 
 I examine differences in respondents' reported perceptions of the candidate's partisan affiliation.
-Evidence supporting $H_2$ would appear as differences between those who saw the white yard signs and the "partisan color" yard signs in reported perceptions of the partisanship of the candidates on average.
-I estimate two ordered logistic regression where the main independent variables of interest are two indicator variables for whether respondents received the "red yard sign" or the "blue yard sign" in each round of Trial 1.
-The baseline category for both of those indicator variables is if they instead saw the "white yard sign".
+Evidence supporting $H_2$ would appear as differences between those who saw the white yard signs and the "partisan color" yard signs in reported perceptions of the partisanship of the candidates.
+I estimate two multinomial logistic regressions where the main independent variables of interest are two indicator variables for whether respondents received the Red yard sign or the Blue yard sign in Trial 1.^[In @tbl-hypothesis-2-ordered located in the [Appendix](#sec-2-a) I report the results of these regressions as fitted ordered logistic regressions, rather than multinomial.
+I come to the same substantive conclusions regardless of whether I fit a multinomial or ordinal logistic regression.] The baseline category for both of these indicator variables is if they instead saw the White yard sign.
 
-@fig-h-2-predictions present the predicted probabilities of an average subject reporting the candidate was either a Democrat, Independent, or Republican when viewing the different yard signs.
-The error bars reflect the high density credible interval for 95% of my posterior draws.
-Each bar reflects the predicted probability of an outcome -- listing the candidate is either a Democrat, Independent, or Republican.
+@fig-h-2 predictions presents the predicted probabilities of an average subject reporting the candidate as either a Democrat, Independent, or Republican when viewing the different yard signs.
+The error bars reflect the high density credible interval for 90% of my posterior draws.
+Each bar reflects the predicted probability of an outcome -- listing the candidate as either a Democrat, Independent, or Republican.
 When interpreting the error bars, you will want to look at the difference in the error bars *between* yard sign treatments rather than *within* treatment.
@@
 That is, the red and blue yard signs did shift people's perceptions of the partisanship of the candidate relative to the white yard sign.
-The credible intervals of these models are reported in the appendix in @tbl-hypothesis-2-main which contains the rest of the results from these models.
+The credible intervals of these models are reported in the [Appendix](#sec-2-a) in @tbl-hypothesis-2-main which contains the rest of the results from these models.
 
-Digging in a little bit more about what these perceptions were, the predicted probability that subjects perceive the candidate with a Red yard sign to be Republican is almost 70%, whereas it is only about 30% when viewing a white yard sign.
-When given a red yard sign, the predicted probability the candidate is marked to be an independent is less than 30% and less than 5% to be a Democrat.
-However, when viewing a blue yard sign, the predicted probability of a subject perceiving the candidate to be a Democrat is at about 50% whereas it is less than 20% with a white yard sign.
-When viewing a blue yard sign, the predicted probability of subjects perceiving the candidate to be a Republican is less than 10% and about 45% to be an Independent.
-The full results are reported in @tbl-hypothesis-2-main in the appendix.
+Digging in a little bit more about what these perceptions were, the predicted probability that subjects perceive the candidate with a red yard sign to be Republican is around 70%, whereas it is only about 30% when viewing a white yard sign.
+When given a red yard sign, the predicted probability the candidate is marked to be an independent is about 30% and less than 5% to be a Democrat.
+However, when viewing a blue yard sign, the predicted probability of a subject perceiving the candidate to be a Democrat is at about 50% whereas it is less at about 10% with a white yard sign.
+When viewing a blue yard sign, the predicted probability of subjects perceiving the candidate to be a Republican is less than 20% and about 45% to be an Independent.
+The full results are reported in @tbl-hypothesis-2-main in the [Appendix](#sec-2-a).
 
@@
 red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2"]][["red"]]
+  fitted_model = list_fitted[["h_2"]][["red_multinomial"]]
   , x_axis = "trial_1_red_stimuli"
@@
 blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2"]][["blue"]]
+  fitted_model = list_fitted[["h_2"]][["blue_multinomial"]]
   , x_axis = "trial_1_blue_stimuli"
@@
 As the consistency by which the parties have used either the color red or blue has increased since the 2000's, I suspect that the age of my subjects may moderate this relationship.
-That is, the tendency for subjects to label red yard signs as a Republican candidate versus a different color may be stronger for those who are younger as the consistency in branding is the political environment they have been around more.
+That is, the tendency for subjects to label red yard signs as a Republican candidate versus a different color may be stronger for those who are younger as the consistency in branding is the political environment they have been around longer.
 I expect this particular relationship may be weaker for older subjects as they may place current branding strategies in a larger political context where this was not always the case.
@@
 Though my pre-registered expectations were that age would moderate this effect, these models suggest that there are not substantive or statistically meaningful differences in how older and younger participants responded to these treatments.
-The results of these models are included in the appendix in @tbl-hypothesis-2-main.
+The results of these models included in the [Appendix](#sec-2-a) in [@tbl-hypothesis-2-ordered].
 
 I also explore whether these effects may be weaker for those with colorblindness.
-The results of this model is reported @tbl-colorblindness, which is located in the appendix.
+The results of this model is reported in [@tbl-colorblindness], which is located in the [Appendix](#sec-2-a).
 The results do not suggest that they are.
-However, given that I had a very small number of respondents reporting colorblindness in my sample, the lack of substantive or statistical effects here are likely because I do not have enough participants with colorblindness in each group to compare.
+However, given that I had a very small number of respondents reporting colorblindness in my sample, the lack of substantive or statistical effects may be due to the fact that I do not have enough participants with colorblindness in each group to compare.
 
 I also test whether my effects here are sensitive to my choice to run two separate regression models -- one for each treatment.
-I fit a single ordered logistic regression with two indicator variables for the treatment coded as: 0 did not receive red/blue treatment, 1 did receive treatment.
-The full results of this alternative model specification is included in @tbl-robustness-alt-specification-h-2 This means that the intercept term for the regression would be the predicted probability of the average respondent labeling the owner of the yard sign as either Democrat, Independent, or Republican.
-The conclusions I draw from this regression model do not change the ones I make here with @fig-h-2-predictions.
+I fit a single ordered logistic regression with two indicator variables for the treatment coded as: 0 did not receive the red/blue treatment, 1 did receive treatment.
+The full results of this alternative model specification are included in [@tbl-tbl-robustness-alt-specification-h-2].
+This means that the intercept term for the regression would be the predicted probability of the average respondent labeling the owner of the yard sign as either Democrat, Independent, or Republican.
+The conclusions I draw from this regression model do no0t change the ones I make here with @fig-h-2-predictions.
 
 In summary, I find that subjects perceive candidates with red yard signs as Republican, candidates with blue yard signs as Democratic, and candidates with white yard signs as being neither -- an Independent.
-These yard signs are *very* red and blue, however.
-In the next section, I examine how these effects may be weaker when we use less red or blue and include more blue or red.
-That is, see if using both colors on the yard signs has the capacity to increase uncertainty about the perception of partisan affiliation.
+However, these yard signs are *very* red and blue.
+In the next section, I examine how these effects may be weaker when we use less red or blue/include more blue or red.
+That is, I consider if using both colors on the yard signs has the capacity to increase uncertainty about the perception of partisan affiliation.
 
@@
 
-The design of the latter trials in the study presents yard signs with mixtures of non-partisan and out-partisan colors.
-For example, primarily red and presumably Republican yard signs, but has some blue or white in them.
-I should expect that the trials that use less "consistent" visual information demonstrate more ambivalence among respondents in their reported perceptions of the politician's positions.
-Specifically, I expect that participants will perceive the yard signs that have both red and blue on them as more moderate and that the higher proportion of the color red or blue among the two colors will lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic.
-This is not to say that I expect the results to change significantly, but rather that the certainty by which I can predict individuals' guesses of the candidate's partisan affiliation to be weaker.
+The design of the latter two trials in the study presents yard signs with mixtures of non-partisan and out-partisan colors.
+For example, I present primarily red (and presumably Republican) yard signs, but with some blue or white in them.
+I expect that the trials that use less "consistent" visual information demonstrate more uncertainty among respondents in their reported perceptions of the candidate's positions.
+Specifically, I expect that participants will perceive the yard signs that have both red and blue on them as more moderate, and that the higher proportion of the color red or blue among the two colors will lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic, respectively.
+This is not to say that I expect the results to change significantly, but rather, that the certainty by which I can predict individuals' guesses of the candidate's partisan affiliation will weaken.
 
-I fit four ordered logistic regression models.
-Two for each trial.
-Where each model for each trial calculates whether an average subject in the study reported that the yard sign they saw in the trial was a Democrat, Independent, or a Republican.
+I fit four multinomial logistic regression models, two for each trial.^[I also report the results of these four models as ordered logistic regressions in @tbl-hypothesis-2a-ordered and @tbl-hypothesis-2a-cont-ordered which are located in the [Appendix](#sec-2-a).] Each model for the trial calculates whether an average subject in the study reported that the yard sign they saw in the trial was for a Democrat, Independent, or a Republican.
 The predicted probabilities for each outcome occurring under different treatments and for different trials are presented in @fig-h-2a-predictions.
-@tbl-hypothesis-2a and @tbl-hypothesis-2a-cont located in the appendix reports the full results of these models while @fig-h-2a-ppc located in the appendix reports the posterior predictive checks of these models.
+@tbl-hypothesis-2a and @tbl-hypothesis-2a-cont located in the [Appendix](#sec-2-a) reports the full results of these models while @fig-h-2a-ppc located in the [Appendix](#sec-2-a) reports the posterior predictive checks of these models.
 
@@
 plot_trial_2_red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_2_red"]]
+  fitted_model = list_fitted[["h_2a"]][["trial_2_red_multinomial"]]
   , x_axis = "trial_2_red_stimuli"
@@
 plot_trial_2_blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_2_blue"]]
+  fitted_model = list_fitted[["h_2a"]][["trial_2_blue_multinomial"]]
   , x_axis = "trial_2_blue_stimuli"
@@
 plot_trial_3_red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_3_red"]]
+  fitted_model = list_fitted[["h_2a"]][["trial_3_red_multinomial"]]
   , x_axis = "trial_3_red_stimuli"
@@
 plot_trial_3_blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_3_blue"]]
+  fitted_model = list_fitted[["h_2a"]][["trial_3_blue_multinomial"]]
   , x_axis = "trial_3_blue_stimuli"
@@
 The results from these models offer partial support for my expectations.
-First, I see that yard signs using less blue are not as distinguishably Democratic as the white yard sign.
-In other words, voters are not meaningfully more likely to report that the yard sign with less blue on it belongs to a Democratic candidate as a white and black yard sign.
-So, the strength of using a blue yard sign to communicate alignment with the Democratic party weakens if you use less blue relative to white or include red on it.
-With red yard signs, however, we see that voters still see them to be belonging to Republican candidates even when we reduce the amount of red on the yard sign and even include blue.
+First I see that yard signs using less blue are not as distinguishably Democratic as the white yard sign.
+In other words, voters are not meaningfully more likely to report that the yard sign with less blue on it belongs to a Democratic candidate versus a white and black yard sign.
+So the strength of using a blue yard sign to communicate alignment with the Democratic party weakens if you use less blue relative to white, or if you include red on it.
+With red yard signs, however, we see that voters still see them as belonging to Republican candidates, even when we reduce the amount of red on the yard sign and even when we include blue.
 
-One potential reason for this may be the association of the American flag when using all three colors.
-Particularly given the Republican party's tendency to condemn those who do not adhere to social norms about showing respect to the American flag.
-This, however, is untestable based on the data I did not collect for this study.
-So, this explanation is speculation.
+One potential reason for this may be the association of the American flag when using all three colors given the Republican party's tendency to condemn those who do not adhere to social norms about showing respect to the American flag.
+This, however, is untestable based on the design of the present study.
 However, what we do see is that there are bounds by which at least the color blue on a yard sign indicates to voters that the candidate is a Democrat.
-What remains unclear is whether these perceptions of ownership by a partisan candidate influences people's willingness to support that candidate or to express favoritism towards it ($H_3$).
+What remains unclear is whether these perceptions of ownership by a partisan candidate influence people's willingness to support that candidate or express favoritism toward them ($H_3$).
 
-### Does the color of a yard sign explain support for a candidate?
+### Does the color of a yard sign explain support for a candidate
 
-An important implication of the snap-judgment model suggests that if individuals perceive candidates using the color red as Republican while candidates using the color blue as Democratic, that partisans may be more attracted to yard signs displaying the color that fits with these associations.
+An important implication of the snap-judgment model is that if individuals perceive candidates using the color red as Republican while candidates using the color blue as Democratic, that partisans may be more attracted to yard signs displaying the color that fits with these associations.
 That is, if the color red conveys group membership to the Republican party, we should expect that Republican individuals should like the red yard signs more and be more willing to vote for candidates using those colors in their campaign materials.
 We should expect a similar thing with Democrats but with blue yard signs.
-Another expectation is that we should expect these relationships to be relatively strong despite little substantive information (e.g., policy positions and name recognition) about the candidate if color does indeed matter as a form of political information.
+Another expectation is that if color does indeed matter as a form of political communication, we should expect these relationships to be relatively strong, despite little substantive information (e.g., policy positions and name recognition) about the candidate.
 
-After the three trials, I asked participants which of the three yard signs they would vote for.
-I create an indicator variable from this question that documents whether participants would vote for the candidate that owns the first yard sign (1) or not (0).
+After the three trials, I asked participants which of the candidates for the three yard signs they would vote for.
+I create an indicator variable from this question that documents whether participants would vote for the candidate that owns the first yard sign (1) or not(0).
+
 I fit two logistic regression models with the vote variable as the outcome I am trying to explain.
 In the first of the two logistic regression models, I examine whether the effect that receiving a red versus a white stimuli is moderated by the participants' partisanship.
-As partisanship and its moderating effect on the treatment is of interest here while not being randomly assigned, I control for a number of confounding variables such as attention paid to politics, age, gender identification, and racial identification.
+As partisanship and its moderating effect on the treatment is of interest here (and partisanship is not being randomly assigned), I control for a number of confounding variables such as attention paid to politics, age, gender identification, and racial identification.
 The second logistic regression model is much like the first.
@@
 As I am still interested in examining how partisan identification modifies the relationship between support for the candidate when comparing a blue versus a white yard sign, I include the same controls as I did with the first logistic regression model.
-I include the full table of results for both of these models in @tbl-h-3-main which is located in the appendix.
+I include the full table of results for both of these models in @tbl-h-3-main ([Appendix](#sec-2-a)).
 
@@
 
-@fig-h-3-predictions presents the average predicted probability that respondents who vary on treatment assignment and partisan identification would support the candidate.
+@fig-h-3-predictions presents the average predicted probability of supporting a candidate.
 The results fit with my expectations.
-First, I see that the predicted probability that a strong Democrat would vote for a candidate with a red yard sign is less than 10% while for strong Republicans it is at about 70%.
-Likewise, we see that strong Democrats much prefer a candidate with a blue yard sign than a candidate with a white yard sign; 80% relative to 40%, respectively.
-Strong Republicans are unlikely to vote for a candidate with a blue yard sign and a white yard sign with their predicted probability of voting for either of those candidates below 30%.
+First, I see that the predicted probability that a strong Democrat would vote for a candidate with a red yard sign is less than 10% (while for strong republicans it is at about 70%).
+Likewise, we see that strong Democrats much prefer a candidate with a blue yard sign than a candidate with a white yard sign, 80% relative to 40%, respectively.
+Strong Republicans are unlikely to vote for a candidate with a blue yard sign and a white yard sign, with their predicted probability of voting for either of those candidates below 30%.
 
@@
 That is, do people process in-group information faster than out-group information?
-There is evidence of these tendencies in political circumstances [@lodge_rationalizing_2013].
+There is, of course, evidence of these tendencies in political circumstances [@lodge_rationalizing_2013].
 
-To examine whether motivated reasoning is also active with the processing of politically-relevant color, I examine the difference between the amount of time between the start of viewing a stimulus and clicking "Next" to stop viewing the stimulus among those who were viewing a presumed co-partisan yard sign relative to those viewing a presumed out-partisan yard sign.
-As the outcome is a count of the amount of time participants spent looking at a yard sign, I turn to a class of regression models that work well for explaining outcomes measured as count data.
-By the nature of my measure, I do not believe that participants can record a value of 0 as time elapsed is measured in milliseconds.
-Additionally, I expect that there will be what is referred to over-dispersion as I expect to have a large bulk of participants recording a very small time elapsed while there may be others who may record quite a large time elapsed.
-In the appendix, I include @tbl-h-4-dispersion which summarizes the time elapsed outcome variable; which indeed demonstrates over-dispersion in this variable with the outcome being the time elapsed.
-Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.
-I therefore fit two poisson-gamma models (sometimes referred to as negative binomial regression).
-I am interested in testing whether time elapsed can be explained by not only the color of the yard sign that the subject was viewing, but also that this effect is moderated by their partisanship.
+To examine whether motivated reasoning is also present in the processing of politically-relevant color, I examine the following: the difference in the amount of time between the start of viewing a stimulus and clicking "Next" to stop viewing the stimulus, among those who were viewing a presumed co-partisan yard sign relative to those viewing a presumed out-partisan yard sign.
+As the outcome is a count of the amount of time participants spent looking at a yard sign, I turn to a class of regression models that work well for explaining outcomes measured as count data.^[By the nature of my measure, I do not believe that participants can record a value of 0 as time elapsed is measured in milliseconds.
+Additionally, I expect over-dispersion, as I expect to observe a large bulk of participants recording a very small time elapsed, while for others I expect to record a quite large amount of elapsed time.
+In the appendix, @tbl-h-4-dispersion summarizes the time elapsed outcome variable; this demonstrates over-dispersion.
+Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.] I therefor fit two poisson-gamma models (sometimes referred to as negative binomial regressions).
+I am interested in testing whether time elapsed can be explained by not only the color of the yard sign that the subject is viewing, but also whether this effect is moderated by an individual's partisanship.
 I therefore include an interaction term between stimuli and the partisan identification of the respondent.
 Like before, as partisan identification is not randomly assigned, I control for confounds such as attention paid to politics, age, gender identity, and racial identity.
-@tbl-h-4 located in the appendix is the full table of results for these two poisson-gamma regression models.
+@tbl-h-4 ([Appendix](#sec-2-a)) presents the full table of results for these two poisson-gamma regression models.
 @fig-h-4-ppc also indicates that the model does a quite good job at predicting the distribution of the time elapsed outcome variable.
@@
 @fig-h-4 presents the average predicted elapsed time for participants in different contexts.
-Overall, these results communicate that I do not find conclusive support for my expectations on $H_4$ in either regression model.
-Strong Democrats do appear to spend more time looking at red yard signs than white ones, once I account for the variation in the data, I cannot be sure that these differences are not due to random chance.
-I also see that there are not really any differences (substantive or statistical) between partisans looking at blue versus white yard signs.
+Overall, these results communicate inconclusive support for my expectations on $H_4$ in either regression model.
+Strong Democrats do not appear to spend more time looking at red yard signs than white ones, but once I account for the variation in the data, I cannot be sure that these differences are not due to random chance.
+I also observe that there are not really any differences (substantive or statistical) between partisans looking at blue versus white yard signs.
 
@@
 
-[Study 1](#sec-study-1) presents evidence in support of the idea that the colors red and blue matter to politics -- they convey information to people.
-Second, the evidence from [Study 1](#sec-study-1) suggests that the information can shape the attitudes of voters.
-What remains unclear is whether or not these patterns have large enough impacts that it shapes how campaigns market themselves.
+[Study 1](#study-1) presents evidence in support of the idea that the colors red and blue matter to politics -- they convey information to people.
+The evidence from [Study 1](#study-1) also suggests that the information may shape the attitudes of voters.
+One thing that remains unclear is whether or not these patterns potentially have large enough impacts that they shape how campaigns market themselves.
 In informal conversations with a campaign marketing firm which specializes in campaign marketing, I was told:
@@
 We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
-> The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right etc.
+The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
 
-While this was good information to hear that seemed to align with what I found in [Study 1](#sec-study-1), I wasn't sure how much this actually influenced strategy. It appears it does, however.
+While this was good information to hear (that seemed to align with what I found in [Study 1](#study-1)), I wasn't sure how much this actually influenced strategy. It appears it does, however:
 
@@
 
-While there is some qualification in that there are other colors that can be useful beyond red and blue.
-The value of colors associated with a particular place can be a way for candidates to communicate attachment to the district and to the constituents.
-Though, there is a preference for campaigns to use as few colors as possible to save on costs - simpler is better.
-What particularly stood out to me was when I was told
+In the comments above, we see some qualification in that there are other colors that can be useful beyond red and blue.
+Still, a potential implication is that the value of colors associated with a particular place can be a way for candidates to communicate attachment to a district and its constituents.
+Still, there is a preference for campaigns to use as few colors as possible to save on costs -- simpler is better.
+What particularly stood out to me was when I was told:
 
@@
 And it seems as though campaigns want to tap into quick and efficient information processing for voters and potential voters.
-However, as noted during the conversation
+However, as also noted during the conversation:
 
@@
 
-The goal for the second piece of empirical evidence in the chapter is to explore whether there is any evidence not from the "lab" suggesting that campaigns use the colors red and blue systematically.
-If the color of a yard sign does indeed matter and its electoral effects depend on the perceptions of potential voters, we should expect that campaigns are less likely to place yard signs with a large amount of Red or Blue in more moderate districts.
+Thus, the goal for the second piece of empirical evidence in this chapter is to explore whether there is any evidence -- outside of the "lab" -- suggesting that campaigns use the colors red and blue systematically.
+If the color of a yard sign does indeed matter, and its electoral effects depend on the perceptions of potential voters, we should expect that campaigns are less likely to place yard signs with a large amount of red or blue in more moderate districts.
 However, in districts where there is a strong partisan base, we should expect that the candidate of the popular party will use the party's color more, while the disadvantaged candidate will use their party's color less as a way to either play up or down their loyalty to their party.
 
-First, I collect data from the MIT Election Lab that reports the electoral results of House of Representative elections from the years 1970-2020.
+To evaluate this, I begin by collecting data from the MIT Election Lab that reports the electoral results of the House of Representative elections from the years 1970-2020.
 The data here tell me which candidate got how many votes in each House election across the United States.
-With this data, I calculate the rolling 5-year average of the Democratic party's vote share for each district.
+With these data, I calculate the rolling 5-year average of the Democratic party's vote share for each district.
 
-Next, I download around 900 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design.
-I use the `OpenCV` library from python to examine the proportion of the colors near the "Republican Red"^[lower values: 93, 9, 12; upper values 236, 69, 75] and "Democratic Blue"^[lower values: 0, 18, 26; upper values: 102, 212, 255] in each of these yard signs.
+Next, I download around 1,000 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design.
+I use the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.
 
-For example, I downloaded the GOP logo used on their official Twitter account during the 2022 midterm election cycle.
-What `OpenCV` does is it loads the image and converts it to a three-dimensional `numpy` array that contains the GBR (reverse of RBG) values for the pixels in the image.
-I standardize the image to be 224 $\times$ 224 pixels.
-The color is trained to detect the range of Republican Red and Democrat Blue colors.
+This approach to measure of the proportion of the Republican red and Democrat blue colors takes a lot of the guess work out of manually coding this.
+For example, I downloaded the GOP logo used on the GOP's official Twitter account during the 2022 midterm election cycle.
+To What `OpenCV` does is it loads the image and converts it to a three-dimensional `numpy` array that contains the GBR (reverse of RGB) values for the pixels in the image.
+I standardize the image to be 224 $times$ 2234 pixels.
+The computer is trained to detect the range of the Republican red and Democrat blue colors.
 Once trained, the computer detects the pixels that do not contain values within the pre-specified range and converts those pixels to be black.
@@
 This leaves me with data from the House elections between 2018 and 2020.
-While the data are limited in the number of elections it reflects, it allows me to hold the district composition constant as redistricting occurs after the Census every 10 years.
-However, each district and state is different in their laws surrounding elections and are different in terms of political context.
+While the data are limited in the number of elections they reflect, they allow me to hold the district composition constant, as redistricting occurs after the Census every 10 years.
+However, each district and state is different in their laws surrounding elections, and are different in terms of political context.
 I want to examine whether there are meaningful differences between districts that are partisan "strongholds" (Democrats or Republicans tend to get elected in a district) relative to districts that are much less so.
 To do this, I include a model with intercepts with no pooling.
-That is a model that includes an intercept for each state-district unit.
-Though my outcomes of interest (proportion of the yard sign that is red or blue) are continous (the outcomes can take any real number, so not an integer), the outcomes are bounded between 0 and 1.
-While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit and introduce systematic error into my model and lead to results that are quite unstable.
-To not bog down readers with a lot of technical jargon, the model that I end up using is called a ordered beta regression which allows me to efficiently and accurately predict outcomes that can be 0 or 1 or any real number between 0 and 1 [@kubinec_ordered_2022].
-For readers in a more technical discussion about why I chose this over other techniques in the beta regression family, I encourage you to look at the appendix.
+That is, a model that includes an intercept for each state-district unit.
+Though my outcome of interest (porportion of the yard sign that is red or blue) are continuous (it can take any real number, so not an integer), the outcome is bounded between 0 and 1.
+While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit, introduce systematic error, and lead to results that are quite unstable.
+To not bog down readers with a lot of technical jargon, the model that I end up using is called an ordered beta regression which allows me to efficiently and accurately predict outcomes that can be 0 or 1, or any real number between 0 and 1 [@kubinec_ordered_2022].
+For a more technical discussion about why I choose this over other techniques in the beta regression family, please see the [Appendix](#sec-2-a).
 
-Once I have fit these models, I use the `marginaleffects` [@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs as explained by the 5-year rolling average Democratic candidates' vote share.
-The grand mean here just reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather I am just averaging across all of those to provide a single line.
+Once I have fit these models, I use the `marginaleffects` [@@arel-bundock_marginaleffects_2022] packae to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as explained by the 5-year rolling average Democratic candidates' vote share.
+The grand mean here reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather that I am averaging across all districts to provide a single line in my figure.
 These results are included in @fig-study-2-pred.
@@
 
-The results demonstrate that districts where Democrats are historically more successful see yard signs with a lower proportion of red on them, while those same districts see more Blue on them.
-Again, these results do not claim that campaigns are doing this either because voters are encouraging them to take this strategy or that they are doing it as a way to proactively get voters to do it.
-To tease out which of those questions is the right one requires more sophisticated approaches and data that could allow me to leverage redistricting to see how these outcomes change due to some unrelated, external shock.
+The results demonstrate that districts where Democrats are historically more successful see yard signs with a lower proportion of red on them, while those same districts see more blue on them.
+Again, these results do not claim that campaigns are doing this either because voters are encouraging them to take this strategy, or that they are doing it as a way to proactively get voters to do it.
+To tease out which of those questions is the right one requires more sophisticated approaches and data that could allow me to leverage redistricting (to see how these outcomes change due to some unrelated, external shock).
 The data available to me do not allow me to do that at this time.
-Furthermore, teasing out such an association is not a primary goal of this chapter.
+Rather, these data provide evidence consistent with the story I have relaayed, and motivate further the study of color as it relates to politics.
 
@@
 
-This chapter argues that the colors red and blue provide useful information to voters about politics.
-Specifically, the colors red and blue provide information about a candidates' partisanship.
-Second, the chapter argues that the information gleaned from these colors can shape how people engage with politics.
-While I had a number of other sets of expectations from this chapter, these were the two primary questions I wanted to address in the chapter.
+In this chapter I argue that the colors red and blue provide useful information to voters about politics.
+Specifically, the colors red and blue provide information about candidates' partisanship.
+Second, I argue that the information gleaned from these colors can shape how people engage with politics.
+While I had a number of other expectations this chapter, these were the two primary questions I wanted to address.
 
@@
 The experiment provides evidence that individuals see candidates that use red on a yard sign as more Republican and candidates that use blue as more Democratic.
-Evidence from the experiment also suggested that using less of these partisan colors and using both partisan colors do make it a bit harder for individuals to make those same associations.
-Further, the experiment demonstrated that these associations that we make with color and partisanship are powerful enough that they can shape whether people express a willingness to vote for a candidate.
-That is, individuals that identify with the Republican party are much more likely to vote for a candidate with a red yard sign than a white yard sign and Democrats are much more likely to vote for a candidate with a blue yard sign than yard signs with other colors.
+Evidence from the experiment also suggests that using less of those partisan colors and using both colors makes it a bit harder for individuals to make partisan associations.
+Further, the experiment demonstrates that these associations that we make with color and partisanship are powerful enough that they can shape whether people express a willingness to vote for a candidate.
+That is, individuals that identify with the Republican party are much more likely to vote for a candidate with a red yard sign than a white yard sign, and Democrats are much more liekly to vote for a candidate with a blue yard sign than yard signs with other colors.
 
-Since it appears that colors can influence vote choice, I turn to data that capture the real world messiness to examine whether or not campaigns are responsive to such patterns.
+Since it appears that colors can influence vote choice, I then turn to data that incorporate real world messiness to examine whether or not campaigns are responsive to such patterns.
 It appears that they are.
-The empirical evidence suggest that campaigns use more blue on their yard signs if it is a district that has a higher vote share for Democrats the five previous years and use red much less often in those same circumstances.
+The empirical evidence suggest that campaigns use more blue on their yard signs if it is a district that has a higher vote share for Democrats the five previous years, and use red much less often in those same circumstances.
 This fits with strategies communicated to me by a campaign marketing firm.
 
-What this chapter demonstrates is that the colors red and blue convey information and they shape outcomes.
-It appears as though that it does not simply shape outcomes for individuals such as their personal attitudes or their vote choice in a lab, but that it has enough of an aggregative effect that can shape strategy for campaigns.
-The next chapter seeks to dig into this latter claim a bit more.
-The next chapter examines whether the snap-judgment model holds up in more complex settings.
-Specifically, the next chapter examines whether color can shape whether and how we have conversations about politics with others and the degree to which color can be a tool inhibiting political persuasion.
+Having established some baseline findings, in the next chapter I examine whether the snap-judgment model holds up in more complex settings.
+Specifically, I next move to consider whether color can shape how we have conversations about politics with others, as well as the degree to which color can be a tool inhibiting political persuasion.

### 2023-08-23 chapter_2/src/models/study_1_fitting.R

@@ -59,14 +59,28 @@ list_ppc <- list(
 
 # Hypothesis 2
     #* Fit models
-list_fitted[["h_2"]][["red"]] <- brm(
+list_fitted[["h_2"]][["red_multinomial"]] <- brm(
+  formula = trial_1_party ~ trial_1_red_stimuli
+  , data = list_df[["cleaned"]]
+  , family = categorical(link = "logit")
+  , prior = set_prior("normal(0, 1)", class = "b")
+  , backend = "cmdstanr"
+)
+list_fitted[["h_2"]][["blue_multinomial"]] <- brm(
+  formula = trial_1_party ~ trial_1_blue_stimuli
+  , data = list_df[["cleaned"]]
+  , family = categorical(link = "logit")
+  , prior = set_prior("normal(0, 1)", class = "b")
+  , backend = "cmdstanr"
+)
+list_fitted[["h_2"]][["red_ordinal"]] <- brm(
   formula = trial_1_party ~ trial_1_red_stimuli
   , data = list_df[["cleaned"]]
   , family = cumulative(link = "logit")
   , prior = set_prior("normal(0, 1)", class = "b")
   , backend = "cmdstanr"
 )
-list_fitted[["h_2"]][["blue"]] <- brm(
+list_fitted[["h_2"]][["blue_ordinal"]] <- brm(
   formula = trial_1_party ~ trial_1_blue_stimuli
   , data = list_df[["cleaned"]]
   , family = cumulative(link = "logit")
@@ -109,11 +123,17 @@ list_fitted[["h_2"]][["blue_colorblind"]] <- brm(
   , backend = "cmdstanr"
 )
     #* Posterior predictive checks
-list_ppc[["h_2"]][["red"]] <- pp_check(
-  list_fitted[["h_2"]][["red"]]
+list_ppc[["h_2"]][["red_multinomial"]] <- pp_check(
+  list_fitted[["h_2"]][["red_multinomial"]]
 )
-list_ppc[["h_2"]][["blue"]] <- pp_check(
-  list_fitted[["h_2"]][["blue"]]
+list_ppc[["h_2"]][["blue_multinomial"]] <- pp_check(
+  list_fitted[["h_2"]][["blue_multinomial"]]
+)
+list_ppc[["h_2"]][["red_ordinal"]] <- pp_check(
+  list_fitted[["h_2"]][["red_ordinal"]]
+)
[…]

### 2023-08-23 chapter_2/src/appendix.qmd
doing some drafting

@@
     , " of claiming candidate is Republican."
-    , "Numbers inside brakcets reflect the 5th and 95th percentile"
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
     , " of the draws from the posterior distribution."
@@
 Finally, I check to see if the results reported in @tbl-hypothesis-2-main are moderated by subjects that are colorblind.
-Though, I have reasons to beleive they are, the sample does not really lend itself to a robust test of this.
+Though, I have reasons to believe they are, the sample does not really lend itself to a robust test of this.
 The sample does not have a large number of respondents who indicated that they were diagnosed with some type of colorblindness.
@@
 As the hypothesis goes beyond saying that I think subjects in the red/blue treatment will spend more time looking at the yard sign than in the white, but instead say that I think this will be moderated by partisanship, I include a interaction term in each of these models.
-Additionally, as partisan identification is a key explantory variable here and is not experimentally treated, I control for a numbe of potential confounds such as attention to politics, age, gender identity, and racial identity.
+Additionally, as partisan identification is a key explanatory variable here and is not experimentally treated, I control for a number of potential confounds such as attention to politics, age, gender identity, and racial identity.
 The results of these models are recorded in @tbl-h-4.
@@
 
-As I made a modeling choice based on the overdispersion of the outcome variable, I want to confirm that these models did an adequate job at returning predicted values based on my posterior distribution relative to the actual data in the sample.
+As I made a modeling choice based on the over-dispersion of the outcome variable, I want to confirm that these models did an adequate job at returning predicted values based on my posterior distribution relative to the actual data in the sample.
 The posterior predictive checks suggest that it did indeed do a pretty good job.
@@
 This is a pretty complex problem.
-Especially givent the estimator that I am using here.
+Especially given the estimator that I am using here.
 More troubling still is that my $\hat{R}$ values are not equal to 1 for either model.
@@
 #|   - Proportion of yard signs red
-#|   - Proprotion of yard signs blue
+#|   - Proportion of yard signs blue
 

### 2023-08-23 chapter_2/src/manuscript.qmd
doing some drafting

@@
 
-# Load some handy functons
+# Load some handy functions
 box::use(
@@
 
-I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where indiiduals are provided with a demographics and political attitudes questionnaire As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
+I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where individuals are provided with a demographics and political attitudes questionnaire As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
 This questionnaire includes common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
@@
 Everything on the yard sign remains constant except for the color.
-As representations of ideology are associated with more than just political views, but also things like space [@mills_political_2016] and color [@losada_maestre-color_2022], differences between respondents on the perceived political affiliations of the candidate should be more than "by chance" differences.
+As representations of ideology are associated with more than just political views, but also things like space [@mills_political_2016] and color [@losada_maestre_color_2022], differences between respondents on the perceived political affiliations of the candidate should be more than "by chance" differences.
 
@@
 
-@fig-h-2 predictions presents the predicted probabilities of an average subject reporting the candidate as either a Democrat, Independent, or Republican when viewing the different yard signs.
+@fig-h-2-predictions presents the predicted probabilities of an average subject reporting the candidate as either a Democrat, Independent, or Republican when viewing the different yard signs.
 The error bars reflect the high density credible interval for 90% of my posterior draws.
@@
 I fit a single ordered logistic regression with two indicator variables for the treatment coded as: 0 did not receive the red/blue treatment, 1 did receive treatment.
-The full results of this alternative model specification are included in [@tbl-tbl-robustness-alt-specification-h-2].
+The full results of this alternative model specification are included in [@tbl-robustness-alt-specification-h-2].
 This means that the intercept term for the regression would be the predicted probability of the average respondent labeling the owner of the yard sign as either Democrat, Independent, or Republican.
@@
 That is, a model that includes an intercept for each state-district unit.
-Though my outcome of interest (porportion of the yard sign that is red or blue) are continuous (it can take any real number, so not an integer), the outcome is bounded between 0 and 1.
+Though my outcome of interest (proportion of the yard sign that is red or blue) are continuous (it can take any real number, so not an integer), the outcome is bounded between 0 and 1.
 While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit, introduce systematic error, and lead to results that are quite unstable.
@@
 
-Once I have fit these models, I use the `marginaleffects` [@@arel-bundock_marginaleffects_2022] packae to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as explained by the 5-year rolling average Democratic candidates' vote share.
+Once I have fit these models, I use the `marginaleffects` [@@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as explained by the 5-year rolling average Democratic candidates' vote share.
 The grand mean here reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather that I am averaging across all districts to provide a single line in my figure.
@@
 #| layout-ncol: 1
-#| fig-cap: More blue on the yard signs in Democratic strongholdsz
+#| fig-cap: More blue on the yard signs in Democratic strongholds
 #| fig-subcap:
@@
 The data available to me do not allow me to do that at this time.
-Rather, these data provide evidence consistent with the story I have relaayed, and motivate further the study of color as it relates to politics.
+Rather, these data provide evidence consistent with the story I have relayed, and motivate further the study of color as it relates to politics.
 
@@
 Further, the experiment demonstrates that these associations that we make with color and partisanship are powerful enough that they can shape whether people express a willingness to vote for a candidate.
-That is, individuals that identify with the Republican party are much more likely to vote for a candidate with a red yard sign than a white yard sign, and Democrats are much more liekly to vote for a candidate with a blue yard sign than yard signs with other colors.
+That is, individuals that identify with the Republican party are much more likely to vote for a candidate with a red yard sign than a white yard sign, and Democrats are much more likely to vote for a candidate with a blue yard sign than yard signs with other colors.
 

### 2023-08-23 chapter_2/src/models/study_1_fitting.R

@@ -15,7 +15,7 @@ set.seed(12102022)
 setwd("./chapter_2/src")
   #* execute cleaning script
 source("./eda/study_1/cleaning.R")
-  #* load in cleaned study-2 data 
+  #* load in cleaned study-2 data
   #* (need to run each python script individually)
 df_study_2 <- read.csv("../data/clean/study_2.csv") |>
   as.data.table()
@@ -27,9 +27,9 @@ df_study_2 <- df_study_2[
 ][
   , state_district := factor(state_district)
 ][
-  , blue_prop := blue_percent/100
+  , blue_prop := blue_percent / 100
 ][
-  , red_prop := red_percent/100
+  , red_prop := red_percent / 100
 ]
   #* load helpful functions
 box::use(
@@ -95,28 +95,28 @@ list_fitted[["h_2"]][["single_model"]] <- brm(
   , backend = "cmdstanr"
 )
 list_fitted[["h_2"]][["red_interact"]] <- brm(
-  formula = trial_1_party ~ trial_1_red_stimuli + age + trial_1_red_stimuli * age
+  formula = trial_1_party ~ trial_1_red_stimuli + age + trial_1_red_stimuli * age # nolint
   , data = list_df[["cleaned"]]
   , family = cumulative(link = "logit")
   , prior = set_prior("normal(0, 1)", class = "b")
   , backend = "cmdstanr"
 )
 list_fitted[["h_2"]][["blue_interact"]] <- brm(
-  formula = trial_1_party ~ trial_1_blue_stimuli + age + trial_1_blue_stimuli * age
+  formula = trial_1_party ~ trial_1_blue_stimuli + age + trial_1_blue_stimuli * age # nolint: line_length_linter.
   , data = list_df[["cleaned"]]
   , family = cumulative(link = "logit")
   , prior = set_prior("normal(0 , 1)", class = "b")
   , backend = "cmdstanr"
 )
 list_fitted[["h_2"]][["red_colorblind"]] <- brm(
-  formula = trial_1_party ~ trial_1_red_stimuli + color_blind_dummy + trial_1_red_stimuli * color_blind_dummy
+  formula = trial_1_party ~ trial_1_red_stimuli + color_blind_dummy + trial_1_red_stimuli * color_blind_dummy # nolint: line_length_linter.
   , data = list_df[["cleaned"]]
   , family = cumulative(link = "logit")
[…]

### 2023-08-23 chapter_2/src/appendix.qmd
update appendix to include treatments

@@
 {{< pagebreak >}}
+
+### Treatments
+
+::: {#fig-treatments-trial1 layout-ncol=2}
+
+![Red treatment](./study_1/assets/rep_yard_sign_round_1.png)
+![Blue treatment](./study_1/assets/dem_yard_sign_round_1.png)
+![White treatment](./study_1/assets/cont_yard_sign_round_1.png)
+
+Trial 1 Treatments
+:::
+
+::: {#fig-treatments-trial2 layout-ncol=2}
+![Red treatment](./study_1/assets//rep_yard_sign_round_2.png)
+![Blue treatment](./study_1/assets/dem_yard_sign_round_2.png)
+![White treatment](./study_1/assets/cont_yard_sign_round_2_3.png)
+
+Trial 2 Treatments
+:::
+
+::: {#fig-treatments-trial3 layout-ncol=2}
+![Red treatment](./study_1/assets/rep_yard_sign_round_3.png)
+![Blue treatment](./study_1/assets/dem_yard_sign_round_3.png)
+![White treatment](./study_1/assets/cont_yard_sign_round_2_3.png)
+
+Trial 3 Treatments
+:::
+
+![Treatment example](./assets/img/example_of_treatment.png)
 

### 2023-08-23 chapter_2/src/appendix.qmd
some final edits of the second chapter

@@
 
+{{< pagebreak >}}
+
 ### Hypothesis 2
@@
 
-These first two models are nominal logistic regressions.
+These first two models are multinomial logistic regressions.
 The outcome of interest is a 3-item response of whether they perceived the owner of the yard sign to be a Republican, a Democrat, or neither.
 This variable was recoded to be 1 = Democrat, 2 = Independent, and 3 = Republican.
-In the first nominal logistic regression, I predict this outcome with a indicator variable of whether the participant saw a white yard sign (value of 0) or saw a red yard sign (value of 1).
+In the first multinomial logistic regression, I predict this outcome with a indicator variable of whether the participant saw a white yard sign (value of 0) or saw a red yard sign (value of 1).
 
@@
 
+{{< pagebreak >}}
+
 ### $H_{2a}$
@@
 
-### Hypothesis 3
+### $H_3$
 
@@
 
-### Hypothesis 4
+### $H_4$
 
@@
 
-### Hypothesis 5
+### $H_5$
 
@@
 However, I receive warnings indicating that there are divergent transitions.
-For HMC, divergent transitions indicate that the sampler is having problems with the curvature of your posterior distribution.
+For Hamiltonian Monte Carlo, divergent transitions indicate that the sampler is having problems with the curvature of your posterior distribution.
 As I note in the main text of the book, I am using a multilevel model that includes a partially pooled parameter for the districts and use two non-pooled parameters for the state and the election year.

### 2023-08-23 chapter_2/src/manuscript.qmd
some final edits of the second chapter

@@
 How does politically-relevant visual information matter to politics?
-From an evolutionary-biological perspective, visual information has been a common source of information for millions of years -- information tat a variety of single-and-multi-cell organisms have relied upon to evaluate their environment [@grabe_image_2009, see Chapter 1 for a useful discussion].
+From an evolutionary-biological perspective, visual information has been a common source of information for millions of years -- information that a variety of single-and-multi-cell organisms have relied upon to evaluate their environment [@grabe_image_2009, see Chapter 1 for a useful discussion].
 As an ancient biological invention, the human brain is organized around visual information processing.
@@
 In the United States, male and female candidates use different colors -- among other things such as fonts -- in their campaign branding to convey distinguishing information about themselves [@williams_whats_2022].
+
 What remains unclear is whether these patterns in the United States are meaningful.
@@
 
-Color and other simple visual information are processed much quicker an occur more frequently than text-based information that may be communicated, for example, through a news article [@mehta_blue_2009].
+Color and other simple visual information are processed much quicker and occur more frequently than text-based information that may be communicated, for example, through a news article [@mehta_blue_2009].
 But as color and other visual information are processed differently, we should also consider their use as political information.
@@
 The retrieval of relevant memories to the attitude depends on many factors, such as the recency of the event, the similarity of the context, and the importance or salience of the memory [@kahana_laws_2022].
-This means that the memories retrieved to contribute to an attitude are quite variable.
+This means that the memories retrieved to contribute to an attitude that is quite variable.
 However, to understand where that variability comes from, we must understand the deeper processes influencing how information is encoded and later retrieved.
@@
 Colors may act as a contextual feature that may lead to variability in how a set of political information may shape attitudes.
+Let me explain how colors might do this.
 
@@
 A less technical description of the processes occurring here might look something like this: once politically-relevant visual information is detected, the retina passes it to the brain.
-Once there , the brain attempts to classify the visual information by activating networks of neurons associated with the current information.
+Once there, the brain attempts to classify the visual information by activating networks of neurons associated with the current information.
 With these activated pathways, the brain also attempts to appraise such information based on quick classification.
@@
 
-What the snap-judgment model predicts is happening in your head is something like the following: as soon as the light bounces off the sign (to produce a particular wavelength) hits your eyes, your brain is already trying to make sense of this information.
+What the snap-judgment model predicts is happening in your head is something like the following: as soon as the light bounces off the sign (to produce a particular wavelength) and reaches your eyes, your brain is already trying to make sense of this information.
 This is a valuable tool for survival that biology has optimized for millions of years [@parker_blink_2003].
@@
 As they are simple, cheap, intrusive, and common forms of campaign branding, they provide a conservative test of the effects of color in campaign branding.
+
 Using yard signs in this study, I test the first four hypotheses I derive from the snap-judgment model.
@@
 
-I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where individuals are provided with a demographics and political attitudes questionnaire As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
+I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where individuals are provided with a demographics and political attitudes questionnaire.
+As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
 This questionnaire includes common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
@@
 I allot 5000 ms to perform the exploration before the image goes away; this is to encourage a consistent and short duration to explore the image.^[In marketing research, some studies give participants about 6000 ms in eye-tracking studies to examine a brand and formulate an intention to purchase a product or not [@wedel_review_2008].
-With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure evoking images uses 1000 ms; but is intended to be an extended amount of time [@anwyl-irvine_mouseviewjs_2022].] After exploring each image, I ask participants what colors were on the yard sign and whether they felt that the candidate supposedly owning the yard sign was a Democrat, a Republican, or Neither.
-After viewing both images, I ask subjects to indicate their preference among the two images.
+With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure evoking images uses 1000 ms; but is intended to be an extended amount of time [@anwyl-irvine_mouseviewjs_2022].]
+
+After exploring the image in each trial, I ask participants whether they felt that the candidate supposedly owning the yard sign was a Democrat, a Republican, or Neither.
+After completing the three trials, I ask subjects to indicate their preference among the three images (one from each trial).
+
 To ensure that participants have a standardized initial placement of their cursor, I display a blank page before viewing the yard sign that requires participants to click a "Next" button.
@@
 There are two more trials that are much like the first trial.
-What is different between the two other trials is that I vary the amount of color that is on the yard sign.
+What is different between the two latter trials is that I vary the amount of color that is on the yard sign.
 Examples of all of these yard signs are included in the [Appendix](#sec-2-a).
@@
 This should not be equated with the frequentist practice of reporting confidence intervals at the 95% level, as credible intervals at this level are often extremely unstable and, more importantly, are interpreted differently.
-For example, a credible interval at the 90% level can be interpreted as: the probability that the true effect is within that interval.
+For example, a credible interval at the 90% level can be interpreted as: the probability that the true effect is within that interval, given the data.
+This interval reflects the degree of uncertainty I have about my point estimate as opposed to being primarily used to interpret levels of statistical significance in a strict null hypothesis test.
 This contrasts with a confidence interval used in the frequentist framework which is interpreted as: upon repeated samples, 90% of the confidence intervals contain the true effect.
-As I am using two-sided credible intervals here, at the 90% level, the probability that 0 would be the true value given the data would be less than 5% as it would be on one side of my posterior distribution.]
+To bridge methodological approaches, for those interpreting my credible intervals, I am using two-sided credible intervals here, at the 90% level, the probability that 0 would be the true value given the data would be less than 5% as it would be on one side of my posterior distribution.]
 
@@
 In the appendix, @tbl-h-4-dispersion summarizes the time elapsed outcome variable; this demonstrates over-dispersion.
-Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.] I therefor fit two poisson-gamma models (sometimes referred to as negative binomial regressions).
+Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.] I therefore fit two poisson-gamma models (sometimes referred to as negative binomial regressions).
 I am interested in testing whether time elapsed can be explained by not only the color of the yard sign that the subject is viewing, but also whether this effect is moderated by an individual's partisanship.
@@
 To What `OpenCV` does is it loads the image and converts it to a three-dimensional `numpy` array that contains the GBR (reverse of RGB) values for the pixels in the image.
-I standardize the image to be 224 $times$ 2234 pixels.
+I standardize the image to be 224 $\times$ 224 pixels.
 The computer is trained to detect the range of the Republican red and Democrat blue colors.
@@
 
-Once I have fit these models, I use the `marginaleffects` [@@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as explained by the 5-year rolling average Democratic candidates' vote share.
+Once I have fit these models, I use the `marginaleffects` [@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as explained by the 5-year rolling average Democratic candidates' vote share.
 The grand mean here reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather that I am averaging across all districts to provide a single line in my figure.

### 2023-08-23 chapter_2/src/R/predicted_prob_bar.R
doing a couple of other edits... fixing some issues

@@ -1,21 +1,21 @@
 #' @title make barplots for predicted probabilities from ordered logit
-#' 
+#'
 #' @description
 #' This is a function that makes ggplot2 barplots by taking a fitted
 #' ordered logit model, calculating the predicted probabilities,
 #' and then plotting it with barplots and including error bars.
-#' 
+#'
 #' @details
 #' This function takes a brmsfit object. It uses the marginalefffects
 #' package to calculate the predicted probabilities.
-#' 
+#'
 #' @param
-#' 
+#'
 #' @return plot A ggplot2 object.
-#' 
+#'
 #' @example
-#' 
-predicted_prob_bar <- function(
+#'
+predicted_prob_bar <- function( # nolint: object_usage_linter.
   fitted_model
   , x_axis
   , treatment = "Red"
@@ -37,10 +37,10 @@ predicted_prob_bar <- function(
     df_pred_prob_cleaned <- df_pred_prob[
       #** aggregate the estimate, conf.low, and conf.high columns with
       #** a mean to calculate the average conditional predicted probabilities
-      , .(
-        estimate = mean(estimate)
-        , conf.low = mean(conf.low)
-        , conf.high = mean(conf.high)
+      , .( # nolint: object_usage_linter.
+        estimate = mean(estimate) # nolint: object_usage_linter.
+        , conf.low = mean(conf.low) # nolint: object_usage_linter.
+        , conf.high = mean(conf.high) # nolint: object_usage_linter.
       )
       #** this needs to be done by the group column and the
       #** independent variable
@@ -50,10 +50,10 @@ predicted_prob_bar <- function(
       )
     ][
       #** convert the x-axis to a factor
-      , x_axis_temp := factor(get(x_axis))
+      , x_axis_temp := factor(get(x_axis)) # nolint: object_usage_linter.
     ][
       #** convert the group column to a factor
-      , group := factor(group)
+      , group := factor(group) # nolint: object_usage_linter.
     ]
     # Make plot
       #* take the cleaned pred_prob dataframe
@@ -67,9 +67,9 @@ predicted_prob_bar <- function(
           #** and change the fill color based on group
           #** column which reflects the value of the outcome
           #** variable
-          x = x_axis_temp
-          , y = estimate
-          , fill = group
+          x = x_axis_temp # nolint: object_usage_linter.
+          , y = estimate # nolint: object_usage_linter.
+          , fill = group # nolint: object_usage_linter.
         )
           #** take the raw y value
[…]

### 2023-08-24 chapter_2/src/manuscript.qmd
final touches before sending out second chapter as jmp

@@
 
-In [Study 1](#study-1), I conduct an online experiment that examines whether the public notice color and whether their attitudes are shaped by "Republican Red" and "Democratic Blue" on the yard signs of a fictional candidate.
+In [Study 1](#study-1), I conduct an online experiment that examines whether the public notice color and whether their attitudes are shaped by "Republican red" and "Democratic Blue" on the yard signs of a fictional candidate.
 Based on informal conversations with campaign marketing consultants, it appears that campaigns are aware that the colors red and blue betray the partisanship of a candidate to voters.
@@
 In the [first study](#study-1), I find that individuals do shift their perceptions of political candidates in response to the use of the colors red and blue -- they consistently and strongly associate Republicans with the color red and Democrats with the color blue, and their willingness to vote for a candidate can be dramatically different depending on whether the color used aligns with their partisan identification.
-The [second study](#study-2) suggests that candidates in districts where Democrats have a higher vote share use more blue on their yard signs (wile also using less red).
+The [second study](#study-2) suggests that candidates in districts where Democrats have a higher vote share use more blue on their yard signs (while also using less red).
 
@@
 More simple forms of visual information are likely even more efficient forms of information.
-In the context of the United States, the "Republican Red" and "Democratic Blue" is a relatively recent invention, but one that likely has significant import in an era where the parties make efforts to distinguish themselves from each other [@clifford_how_2020], and where voters toe the party line [@utych_voter-centric_2020].
+In the context of the United States, the "Republican red" and "Democratic blue" is a relatively recent invention, but one that likely has significant import in an era where the parties make efforts to distinguish themselves from each other [@clifford_how_2020], and where voters toe the party line [@utych_voter-centric_2020].
 Since the 2000 presidential election, the media have consistently used red on their electoral maps in "horserace" journalism to represent Republicans and blue to represent Democrats [@elving_color_2014].
@@
 I then present participants with an instruction screen informing them of the task for the experiment.
-In the first trial of the experiment, I randomly presented participants with one of three possible yard signs, one at a time.
-These yard signs are simple, with the text "Riley Ready to Lead" and a solid background color of either "Republican Red," "Democratic Blue," or White.^[See [Appendix](#sec-2-a) to view all of the stimuli used in [Study 1](#study-1).] There is an added component to this, and the other two trials.
+In the first trial of the experiment, I randomly presented participants with one of three possible yard signs.
+These yard signs are simple, with the text "Riley Ready to Lead" and a solid background color of either "Republican red," "Democratic Blue," or White.^[See [Appendix](#sec-2-a) to view all of the stimuli used in [Study 1](#study-1).] There is an added component to this, as well as in the other two trials.
 
@@
 There are two more trials that are much like the first trial.
-What is different between the two latter trials is that I vary the amount of color that is on the yard sign.
+What is different between the two latter trials and the first is that I vary the amount of color that is on the yard sign.
 Examples of all of these yard signs are included in the [Appendix](#sec-2-a).
@@
 First, the average participant in each treatment condition appear to be spending more time exploring the yard signs when there are more "conflicting" colors (trials 2 and 3).
-Second, we see that, for the most part, the average participant in the Red and Blue yard sign conditions spend more time exploring those yard signs than the participants viewing the White yard sign.
+Second, we see that, for the most part, the average participant in the red and blue yard sign conditions spend more time exploring those yard signs than the participants viewing the white yard sign.
 
@@
 Evidence supporting $H_2$ would appear as differences between those who saw the white yard signs and the "partisan color" yard signs in reported perceptions of the partisanship of the candidates.
-I estimate two multinomial logistic regressions where the main independent variables of interest are two indicator variables for whether respondents received the Red yard sign or the Blue yard sign in Trial 1.^[In @tbl-hypothesis-2-ordered located in the [Appendix](#sec-2-a) I report the results of these regressions as fitted ordered logistic regressions, rather than multinomial.
-I come to the same substantive conclusions regardless of whether I fit a multinomial or ordinal logistic regression.] The baseline category for both of these indicator variables is if they instead saw the White yard sign.
+I estimate two multinomial logistic regressions where the main independent variables of interest are two indicator variables for whether respondents received the red yard sign or the blue yard sign in Trial 1.^[In @tbl-hypothesis-2-ordered located in the [Appendix](#sec-2-a) I report the results of these regressions as fitted ordered logistic regressions, rather than multinomial.
+I come to the same substantive conclusions regardless of whether I fit a multinomial or ordinal logistic regression.] The baseline category for both of these indicator variables is if they instead saw the white yard sign.
 

### 2023-08-24 chapter_2/src/appendix.qmd

@@
   , coef_map = c(
-    "b_intercept" = "Intercept"
-    , "b_dem_vote_share" = "Democratic vote share (percent)"
+    "b_dem_vote_share" = "Democratic vote share (percent)"
+    , "b_Intercept" = "Intercept"
   )
@@
   , escape = FALSE
-  , output = "latex"
+  #, output = "latex"
 )

### 2023-08-28 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
doing a little bit more thinking on this chapter

@@
 That is, we are not only holding fewer and fewer cross-cutting attitudes that moderate our political viewpoints [@luders_attitude_2023], but we also have fewer and fewer cross-cutting social groups that encourage interaction and experiences with perspectives of out-partisans [@mason_uncivil_2018].
-The consequence of such phenomena is that we are becoming increasingly willing to harbor strong negative feelings towards those of the other political party and strong positive affectations to members of our political party [@iyengar_affect_2012;@iyengar_fear_2015].
+The consequence of such phenomena is that we are becoming increasingly willing to harbor strong negative feelings towards those of the other political party and strong positive affectations for members of our political party [@iyengar_affect_2012;@iyengar_fear_2015].
 
 The consequences of this affective polarization encourages discomfort being around those who identify with the other political party and finding comfort around those that share the same partisanship.
-In fact, some evidence suggests that it is even more sinister than comfort but rather predicts lower empathy for outpartisans [@allamong_screw_2021], as well as an increased willingness to describe outpartisans as subhuman [@martherus_party_2021].
-Racists commonly use dehumanizing language to describe racial minorities [@utych_how_2018].
+In fact, some evidence suggests that it is even more sinister than comfort but rather predicts lower empathy for out-partisans [@allamong_screw_2021], as well as an increased willingness to describe out-partisans as subhuman [@martherus_party_2021].
 
@@
 For example, @carlson_what_2022 demonstrates that individuals perceive that they may incur social costs with friends and neighbors by engaging in a conversation with those they disagree with and expressing that disagreement, and avoid such situations as a result.
-Other work corroborate this finding by suggesting that individuals will be less likely to share the social media posts of political viewpoints they agree with if they perceive that they are in the political minority of those that would see that sharing of the post [@van_der_does_strategic_2022].
-As a result of this tendency to speak out as a political minority in front of a group of people, individuals have fewer outpartisans in their group of folks they regularly discuss politics with [@butters_polarized_2022].
+Other work corroborates this finding by suggesting that individuals will be less likely to share the social media posts of political viewpoints they agree with if they perceive that they are in the political minority of those that would see that sharing of the post [@van_der_does_strategic_2022].
+As a result of this tendency to speak out as a political minority in front of a group of people, individuals have fewer out-partisans in their group of folks they regularly discuss politics with [@butters_polarized_2022].
 
@@
 @gimpel_seeking_2015 demonstrates that describing a neighborhood with explicit and implicit information (e.g., racial composition) about the partisan composition influences whether one expresses a desire or not to move and live there.
-Further work corroborates this finding by providing evidence from a number of studies which demonstrate that not only do people associate particular characteristics of a neighborhood such as the prevalence of churches with Republicans and hybrid cars with Democrats, but also that these features attract copartisans and repulse outpartisans [@motyl_how_2020].
+Further work corroborates this finding by providing evidence from a number of studies which demonstrate that not only do people associate particular characteristics of a neighborhood such as the prevalence of churches with Republicans and hybrid cars with Democrats, but also that these features attract co-partisans and repulse out-partisans [@motyl_how_2020].
 
-Some work suggests, however, that these expressed preferences to live near copartisans do not carryover to migration patterns [see @iyengar_affect_2012].
+Some work suggests, however, that these expressed preferences to live near co-partisans do not carryover to migration patterns [see @iyengar_affect_2012].
 In fact, there is some evidence suggesting that controlling for everything else but current rates of political sorting, we would have less political homogeneity than we had in 2008 [@martin_does_2020].
@@
 Information giving insight into one's partisanship may even be as subtle as their color choice in car.
-For a reader who thinks "hypothesizing about car color choice and partisanship is a reach", I agree.
+For a reader who thinks "hypothesizing about car color choice and partisanship is a reach," I agree.
 As stated at the outset of the chapter, the goal of the chapter is to extend past applications of the snap-judgment model to explicitly partisan objects such as yard signs as we did in Chapter 2 and to really challenge the model by looking at non-political objects that many never associate with partisanship.
@@
 
-Applying the snap-judgment model to an individual's choice to move to a neighborhood yields the following hypotheses: with all else equal, Republicans that see that the modal color of car is Red are more likely to report wanting to move to the neighborhood than if the modal car color were blue ($H_1$); with all else equal, Democrats that see the modal color of Blue are more likely to report wanting to move to the neighborhood than if the modal car color were red ($H_2$); once we include more information about a neighborhood's partisan composition, then the strength of their desire to live in a neighborhood will increase if congruent with their partisan affiliation ($H_3$) and will weaken if incongruent with their partisan affiliation ($H_4$).
+Applying the snap-judgment model to an individual's choice to move to a neighborhood yields the following hypotheses: with all else equal, Republicans that see that the modal color of car is red are more likely to report wanting to move to the neighborhood than if the modal car color were blue ($H_1$); with all else equal, Democrats that see the modal color of blue are more likely to report wanting to move to the neighborhood than if the modal car color were red ($H_2$); once we include more information about a neighborhood's partisan composition, then the strength of their desire to live in a neighborhood will increase if congruent with their partisan affiliation ($H_3$) and will weaken if incongruent with their partisan affiliation ($H_4$).
 
@@
 In the second condition, the "favorite car" is the same make and model of SUV as in the first condition, but blue.
-Participants are then given a scale from 0-10 to rate the neighborhood and are presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?" Once the participants have responded to these questions, they are then given a "second page" describing the neighborhood.
+Participants are then given a scale from 0-10 to rate the neighborhood and are presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?"
+
+Once the participants have responded to these questions, they are then given a "second page" describing the neighborhood.
 The information subjects sees depends on which of two conditions they are randomly assigned into.

### 2023-09-07 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
a mockup of the treatments
a little bit more editing

@@
 
-The implications of such findings corroborate existing work that suggests that there are an increasing number of cultural signals that people use to guess the partisanship of not just other individuals but groups of people, and that as a result partisanship and polarization are bleeding into our non-political decision-making.
+The implications of such findings corroborate existing work that suggests that there are an increasing number of cultural signals that people use to infer the partisanship of not just other individuals but groups of people, and consequently partisanship and polarization are bleeding into our non-political decision-making.
 The implications of the argument advanced in the chapter build upon these existing findings by providing one causal mechanism as to the connection between cultural cues conveyed visually and the cognitive processing of such information.
-The chapter not only generalizes findings from the previous chapters to groups of people and to non-political attitudes and behaviors, but it contributes to a literature suggesting that political polarization is pervasive and is approaching universal.
+The chapter not only generalizes findings from the previous chapters to groups of people and to non-political attitudes and behaviors, but it contributes to a literature suggesting that political polarization is pervasive as a basis of forming attitudes and is approaching universal.
 
@@
 
-While political polarization certainly reflects a growing gap and consolidation of two camps of policy preferences and attitudes [@dellaposta_pluralistic_2020;@luders_attitude_2023], it manifests as something more consequential for our every-day experiences.
-Political polarization has come to reflect social groups that distinguish "us" versus "them" with increasingly fewer and fewer non-political social groups that are not wrapped up in our partisan group [@mason_uncivil_2018].
-That is, we are not only holding fewer and fewer cross-cutting attitudes that moderate our political viewpoints [@luders_attitude_2023], but we also have fewer and fewer cross-cutting social groups that encourage interaction and experiences with perspectives of out-partisans [@mason_uncivil_2018].
+While political polarization certainly reflects a growing gap and consolidation of two groups of policy preferences and attitudes [@dellaposta_pluralistic_2020;@luders_attitude_2023], it manifests as something more consequential for our every-day experiences.
+Political polarization has come to reflect social groups that distinguish "us" versus "them" with increasingly fewer non-political social groups that are not wrapped up in our partisan group [@mason_uncivil_2018].
+That is, we are not only holding fewer cross-cutting attitudes that moderate our political viewpoints [@luders_attitude_2023], but we also have fewer cross-cutting social groups that we identify with to encourage interaction and experiences with perspectives of out-partisans [@mason_uncivil_2018].
 The consequence of such phenomena is that we are becoming increasingly willing to harbor strong negative feelings towards those of the other political party and strong positive affectations for members of our political party [@iyengar_affect_2012;@iyengar_fear_2015].
@@
 
-Building on this set of evidence, a growing area of the literature suggests that we are able to make inferences about the partisanship about other individuals, but we are able to do this for groups of people through the increasing politicultural distinctions between Republicans and Democrats.
+Building on this set of evidence, a growing area of the literature suggests that we are not just able to make inferences about the partisanship about other individuals, but we are also able to do this for groups of people through the increasing politicultural distinctions between Republicans and Democrats.
 @hetherington_prius_2018 demonstrates that Republicans and Democrats are not just different in their policy preferences but rather that they live in different places and have different lifestyles.
@@
 For example, the modal car in a neighborhood conveys the partisan composition of the whole neighborhood [@hetherington_prius_2018;@gebru_using_2017].
-In the same spirit as the rest of this book, we do not need to necessarily distinguish between whether someone drives a hybrid sedan and a Ford pickup truck.
+In the same spirit as the rest of this book, we do not need to necessarily distinguish between complex forms of information such as whether someone drives a hybrid sedan and a Ford pickup truck.
 Information giving insight into one's partisanship may even be as subtle as their color choice in car.
 For a reader who thinks "hypothesizing about car color choice and partisanship is a reach," I agree.
-As stated at the outset of the chapter, the goal of the chapter is to extend past applications of the snap-judgment model to explicitly partisan objects such as yard signs as we did in Chapter 2 and to really challenge the model by looking at non-political objects that many never associate with partisanship.
+As stated at the outset of the chapter, the goal of the chapter is to extend past applications of the snap-judgment model to explicitly partisan objects such as yard signs as we did in Chapter 2 and to really challenge the model by looking at non-political objects that we do not readily associate with partisanship.
 
@@
 This association will trigger a pre-conscious and potent process that involves an activation of an affective state depending on one's prior experiences with Republicans and Democrats.
-If, when viewing those colors, activates memories of Republicans and Democrats that are negative, then your affective state will have a negative valance.
+If, when viewing those colors, activated memories of Republicans and Democrats that are negative, then your affective state will have a negative valance.
 If those activated memories are positive, then your affective state will have a positive valance.
@@
 The treatment involves randomly assigning participants to view one of two versions of a fictional real estate posting.
-The characteristics of the neighborhood are exactly the same between the two conditions except for the "favorite car" in the neighborhood.
-In the first condition the "favorite car" is a red SUV.
-In the second condition, the "favorite car" is the same make and model of SUV as in the first condition, but blue.
+The characteristics of the neighborhood are exactly the same between the two conditions except for the "favorite color of car" in the neighborhood.
+In the first condition the "favorite color of car" is reported by displaying a red swatch.
+In the second condition, the "favorite color of car" reported by displaying a blue swatch.
 Participants are then given a scale from 0-10 to rate the neighborhood and are presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?"
+
+::: {#fig-treatments layout-ncol=2}
+
+![Blue treatment](./assets/treatments/blue_mockup.png){#fig-blue-treatment}
+
+![Red treatment](./assets/treatments/red_mockup.png){#fig-red-treatment}
+
+Treatments
+:::
 
@@
 
+## Modeling strategy
+
+## Simulations
+
 {{< pagebreak >}}

### 2023-09-08 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
weak attempt to write

@@
 In the second condition, the "favorite color of car" reported by displaying a blue swatch.
-Participants are then given a scale from 0-10 to rate the neighborhood and are presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?"
+Participants are presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?"
 
@@
 The information subjects sees depends on which of two conditions they are randomly assigned into.
-In one condition, the information indicates that the neighborhood is "40 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition presents the same information but instead describes the neighborhood as "10 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." With this new information, I ask participants "With this new information, please update your rating of the neighborhood" on the 0-10 scale and are again presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?"
+In one condition, the information indicates that the neighborhood is "40 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition presents the same information but instead describes the neighborhood as "10 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." With this new information, I ask participants "How much would [they] like to live in this neighborhood?" and are given a 5-item Likert scale to record their response.
 
 ## Modeling strategy
+
+The outcome of interest is a 5-item Likert scale.
+So the following models will be ordered logistic regressions.
+$H_1$ and $H_2$ would expect that when viewing the first page of the real estate flyer that Democratic participants would report a higher desire to move to a neighborhood with a blue swatch as opposed to a red swatch; the inverse would be true for Republican participants.
 

### 2023-09-08 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
some more weak attempts to draft

@@
 
-Applying the snap-judgment model to an individual's choice to move to a neighborhood yields the following hypotheses: with all else equal, Republicans that see that the modal color of car is red are more likely to report wanting to move to the neighborhood than if the modal car color were blue ($H_1$); with all else equal, Democrats that see the modal color of blue are more likely to report wanting to move to the neighborhood than if the modal car color were red ($H_2$); once we include more information about a neighborhood's partisan composition, then the strength of their desire to live in a neighborhood will increase if congruent with their partisan affiliation ($H_3$) and will weaken if incongruent with their partisan affiliation ($H_4$).
+Applying the snap-judgment model to an individual's choice to move to a neighborhood yields the following hypotheses: when primed to think about politics, participants will perceive the neighborhood to be more Republican when the favorite car color is red and to be more Democratic when the favorite car color is blue, relative to those that are not primed to think about politics ($H_1$); with all else equal, Republicans that see that the modal color of car is red are more likely to report wanting to move to the neighborhood than if the modal car color were blue ($H_2$); with all else equal, Democrats that see the modal color of blue are more likely to report wanting to move to the neighborhood than if the modal car color were red ($H_3$); once we include more information about a neighborhood's partisan composition, then the strength of their desire to live in a neighborhood will increase if congruent with their partisan affiliation ($H_4$) and will weaken if incongruent with their partisan affiliation ($H_5$).
 

### 2023-09-15 chapter_2/src/slides/index.qmd
slide drafting

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs: 
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: true
    slide-number: true
    toc: true
    toc-depth: 2
    slide-level: 3
    bibliography: ../../../assets/references.bib
    footer: |
        <span class="faux-block">{{< fa brands creative-commons >}} 2021-2023 Damon Charles Roberts</span>
        <span class="faux-block"><br>All content licensed under {{< fa brands creative-commons >}} {{< fa brands creative-commons-by >}} {{< fa brands creative-commons-sa >}} [Creative Commons CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/)</span>
    self-contained: true
    output-file: color_and_conversation.html
execute:
  echo: false
---

```{r}
#| label: setup-block
box::use(
  ggplot2[
    ggplot
    , aes
    , geom_density
    , theme_minimal
    , geom_abline
  ]
)
```

## Visual politics is not new politics, but "hot" politics

---

[![1860s Ballots](../../assets/slides/imgs/ballots.avif){#fig-ballots}](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)

---

::: {#fig-1980-convention layout-ncol=2}

[![Democratic National Convention](../../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem height=100}](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)

[![Republican National Convention](../../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep height=100}](https://reuther.wayne.edu/node/9207)

1980 Presidential Party National Conventions
:::

---

[![2000 Presidential Election map](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=200}](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)

---

::: {#fig-party-brand layout-ncol=2}

![Republicans pre-2000](../assets/img/rnc_logo_pre-2000.png){#fig-republican}

![Democrats pre-2000](../assets/img/dnc_logo_1960.png){#fig-democrat}

![Republicans 2023](../assets/img/rnc_logo_2023.png){#fig-republican-post}

![Democrats 2023](../assets/img/dnc_logo_2023.png){#fig-democrat-post}

Party logos
:::

---

[![The public](../../assets/slides/imgs/division.webp){#fig-public}](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)

## Question guiding the project

Is color a source of political information that shapes the public's behaviors and attitudes?

## De-mystifying some of the jargon I might use

- Object
  - refers to anything out in the world that we are interacting with
  - here, these objects are political
- Affect $\noeq$ emotion
  - refers to the larger state of being
  - emotion refers to consciously labeled reactions
  - valance refers to pre-consciously 
- "Hot Cognition"
  - refers to the idea that some memories and experiences are more accessible or come to the top of the mind quicker.
  - this coincides with memories and experiences that are affect-laden

## Dominant models of information processing

### Zaller's [- @zaller_1992_cup] Memory model

---

```{r}
#| label: sim-visualization

df <- fabricatr::fabricate(
  N = 10000,
  pop = rnorm(n = N, mean = 2, sd = 1),
  sample = rnorm(n = N, mean = 2, sd = 0.5),
  updated = rnorm(n = N, mean = 1.9, sd = 1)
)
```

```{r}
#| label: fig-pre-existing-info
#| fig-cap: Set of pre-existing attitudes
ggplot(data = df) +
  geom_density(aes(x = pop)) +
  theme_minimal()
```

---

```{r}
#| label: fig-sample-pre-existing-info
#| fig-cap: Pre-existing attitudes used

ggplot(data = df) +
  geom_density(aes(x = sample)) +
  theme_minimal()
```

---

```{mermaid}
graph TD;
A[Sampled pre-existing info] --> C[Updated attitudes]
B[New info] --> C
```

---

```{r}
#| label: fig-new-attitude
#| fig-cap: Updated set of attitudes
ggplot(data = df) +
  geom_density(aes(x = updated)) +
  theme_minimal()
```

### Lodge and Taber's [- @lodge_taber_2013_cup] Online model

## Amending those models with the Snap-judgment model

### 2023-09-18 chapter_2/src/slides.qmd
a weak draft of jt slide deck

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs: 
    embed-resources: true
    theme: [dark, ../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: true
    slide-number: true
    toc: true
    toc-depth: 2
    slide-level: 3
    bibliography: ../../assets/references.bib   
    self-contained: true
    output-file: color_and_conversation.html
execute:
  echo: false
---

```{r}
#| label: setup-block
# Set seed
set.seed(12102023)
# Load libraries
box::use(
  ggplot2[
    ggplot
    , aes
    , geom_density
    , theme_minimal
    , geom_vline
  ]
  , data.table[...]
  , modelsummary[
    datasummary_skim
    , datasummary_balance
  ]
  , ./R/predicted_prob_bar[...]
)
# Execute the cleaning script
source("./eda/study_1/cleaning.R")
# Load fitted models
load("../data/temp/models/study_1_fitted.RData")
```

## Visual politics is not new politics, but "hot" politics

---

[![1860s Ballots](../assets/slides/imgs/ballots.avif){#fig-ballots}](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)

---

::: {#fig-1980-convention layout-ncol=2}

[![Democratic National Convention](../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem height=100}](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)

[![Republican National Convention](../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep height=100}](https://reuther.wayne.edu/node/9207)

1980 Presidential Party National Conventions
:::

---

[![2000 Presidential Election map](../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=200}](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)

---

::: {#fig-party-brand layout-ncol=2}

![Republicans pre-2000](./assets/img/rnc_logo_pre-2000.png){#fig-republican}

![Democrats pre-2000](./assets/img/dnc_logo_1960.png){#fig-democrat}

![Republicans 2023](./assets/img/rnc_logo_2023.png){#fig-republican-post}

![Democrats 2023](./assets/img/dnc_logo_2023.png){#fig-democrat-post}

Party logos
:::

---

[![The public](../assets/slides/imgs/division.webp){#fig-public}](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)

## Question guiding the project

Is color a source of political information that shapes the public's behaviors and attitudes?

## De-mystifying some of the jargon I might use

- Object
  - refers to anything out in the world that we are interacting with
  - here, these objects are political
- Affect $\neq$ emotion
  - refers to the larger state of being
  - emotion refers to consciously labeled reactions
  - valance refers to pre-consciously 
- "Hot Cognition"
  - refers to the idea that some memories and experiences are more accessible or come to the top of the mind quicker.
  - this coincides with memories and experiences that are affect-laden

## Dominant models of information processing

### Zaller's [-@zaller_1992_cup] Memory model

```{mermaid}
%%| label: fig-zaller
%%| fig-cap: Memory model of info processing
graph TD;
A[Sampled pre-existing info] -->|Stronger impacts when less pre-existing knowledge| C[Updated attitudes]
B[New info] --> C
```

---

```{r}
#| label: sim-visualization

df <- fabricatr::fabricate(
  N = 10000,
  pop = rnorm(n = N, mean = 2, sd = 1),
  sample_strong = rnorm(n = N, mean = 2, sd = 0.5),
  updated_strong = rnorm(n = N, mean = 1.9, sd = 1),
  sample_weak = rnorm(n = N, mean = 2, sd = 2),
  updated_weak = rnorm(n = N, mean = 1.5, sd = 1)
)
```

```{r}
#| label: fig-pre-existing-info
#| fig-cap: Set of pre-existing attitudes
ggplot(data = df) +
  geom_density(aes(x = pop)) +
  geom_vline(aes(xintercept = 2), linetype = 1) +
  theme_minimal()
```

---

```{r}
#| label: fig-sample-pre-existing-info
#| fig-cap: Pre-existing attitudes used
#| fig-subcap:
#|   - Unknowledgeable person
#|   - Knowledgeable person
ggplot(data = df) +
  geom_density(aes(x = sample_weak)) +
  geom_vline(aes(xintercept =  2), linetype = 1) +
  theme_minimal()
ggplot(data = df) +
  geom_density(aes(x = sample_strong)) +
  geom_vline(aes(xintercept =  2), linetype = 1) +
  theme_minimal()
```

---

```{r}
#| label: fig-new-attitude
#| fig-cap: Updated set of attitudes
#| fig-subcap:
#|   - Unknowledgeable person
#|   - Knowledgeable person
ggplot(data = df) +
  geom_density(aes(x = updated_weak)) +
  geom_vline(aes(xintercept =  2), linetype = 1) +
  geom_vline(aes(xintercept =  1.5), linetype = 2) +
  theme_minimal()
ggplot(data = df) +
  geom_density(aes(x = updated_strong)) +
  geom_vline(aes(xintercept =  2), linetype = 1) +
  geom_vline(aes(xintercept =  1.9), linetype = 2) +
  theme_minimal()
```

### Lodge and Taber's [-@lodge_taber_2013_cup] Online model

```{mermaid}
%%| label: fig-online-model
%%| fig-cap: Online model of info processing
graph TD;
A[Pre-existing beliefs] --> C[Updated beliefs]
B[New information] -->|If it aligns with current beliefs| C
```

---

```{r}
#| label: sim-visualization-online

df <- fabricatr::fabricate(
  N = 10000,
  pop = rnorm(n = N, mean = 2, sd = 1),
  sample_strong = rnorm(n = N, mean = 2, sd = 0.5),
  updated_strong = rnorm(n = N, mean = 2, sd = 1),
  sample_weak = rnorm(n = N, mean = 2, sd = 2),
  updated_weak = rnorm(n = N, mean = 1.5, sd = 1)
)
```

---

```{r}
#| label: fig-pre-existing
#| fig-cap: Pre-existing beliefs
#| fig-subcap:
#|   - Weak accuracy, strong pre-existing
#|   - Strong accuracy, weak pre-existing

ggplot(data = df) +
  geom_density(aes(x = sample_strong)) +
  geom_vline(aes(xintercept =  2), linetype = 1) +
  theme_minimal()

ggplot(data = df) +
  geom_density(aes(x = sample_weak)) +
  geom_vline(aes(xintercept =  2), linetype = 1) +
  theme_minimal()
```

---

```{r}
#| label: fig-updated
#| fig-cap: Updated beliefs
#| fig-subcap:
#|   - Weak accuracy, strong pre-existing
#|   - Strong accuracy, weak pre-existing

ggplot(data = df) +
  geom_density(aes(x = updated_strong)) +
  geom_vline(aes(xintercept =  2), linetype = 1) +
  geom_vline(aes(xintercept =  2), linetype = 2) +
  theme_minimal()

ggplot(data = df) +
  geom_density(aes(x = updated_weak)) +
  geom_vline(aes(xintercept =  2), linetype = 1) +
  geom_vline(aes(xintercept =  1.5), linetype = 2) +
  theme_minimal()
```

## Amending those models with the Snap-judgment model

---

{{< include ../../assets/_theory.qmd >}}

---

```{r}
#| label: sim-snap-judgment

df <- fabricatr::fabricate(
  N = 10000,
  pop = rnorm(n = N, mean = 2, sd = 1),
  sample_strong = rnorm(n = N, mean = 2.5, sd = 0.5),
  updated_strong = rnorm(n = N, mean = 2.5, sd = 1),
  sample_weak = rnorm(n = N, mean = 2.5, sd = 2),
  updated_weak = rnorm(n = N, mean = 1.5, sd = 1)
)
```

```{r}
#| label: fig-snap-sample
#| fig-cap: Pre-existing beliefs based on visual information
#| fig-subcap:
#|   - Weak accuracy, strong pre-existing
#|   - Strong accuracy, weak pre-existing

ggplot(data = df) +
  geom_density(aes(x = sample_strong)) +
  geom_vline(aes(xintercept = 2.5), linetype = 1) +
  theme_minimal()
ggplot(data = df) +
  geom_density(aes(x = sample_weak)) +
  geom_vline(aes(xintercept = 2.5), linetype = 1) +
  theme_minimal()
```

---

```{r}
#| label: fig-snap-updated
#| fig-cap: Updated beliefs with visual information
#| fig-subcap:
#|   - Weak accuracy, strong pre-existing
#|   - Strong accuracy, weak pre-existing

ggplot(data = df) +
  geom_density(aes(x = updated_strong)) +
  geom_vline(aes(xintercept = 2.5), linetype = 1) +
  geom_vline(aes(xintercept = 2.5), linetype = 2) +
  theme_minimal()
ggplot(data = df) +
  geom_density(aes(x = updated_weak)) +
  geom_vline(aes(xintercept = 2.5), linetype = 1) +
  geom_vline(aes(xintercept = 1.5), linetype = 2) +
  theme_minimal()
```

---

- Implications
  - Refines existing info. processing models to consider pre-conscious influences.
  - Outlines the cognitive processes undergirding how we:
    - have made associations between the colors red and blue with the two parties.
    - form attitudes and behaviors based on less substantive information (e.g., policy stances).

## Study 1

### Motivation of the experiment

- Do we associate the color red with Republicans and the color blue with Democrats?
- Do these associations provide information that the public act on in politics?

### Setup of the experiment

---

#### Background information

- Age
- Education
- Gender Identity
- Sex
- Visual impairments
  - Including colorblindness
- Party Identification

---

#### Treatment

- Three trials

---

::: {#fig-trial-1}

![Red condition](./study_1/assets/rep_yard_sign_round_1.png)
![Blue condition](./study_1/assets/dem_yard_sign_round_1.png)
![White condition](./study_1/assets/cont_yard_sign_round_1.png)

Trial 1
:::

---

::: {#fig-trial-2}

![Red condition](./study_1/assets/rep_yard_sign_round_2.png)
![Blue condition](./study_1/assets/dem_yard_sign_round_2.png)
![White condition](./study_1/assets/cont_yard_sign_round_2_3.png)

Trial 2
:::

---

::: {#fig-trial-3}

![Red condition](./study_1/assets/rep_yard_sign_round_3.png)
![Blue condition](./study_1/assets/dem_yard_sign_round_3.png)
![White condition](./study_1/assets/cont_yard_sign_round_2_3.png)

Trial 3
:::

#### Design

- Recruited 1,000 participants from Prolific
- Counterbalance treatment and background information ($\frac{1}{2}$ see treatment first; other $\frac{1}{2}$ see background questions first)
- Within each trial, participants have $\frac{1}{3}$ chance of seeing any given yard sign.
- MouseView.js

---

![Example of treatment](../assets/slides/imgs/treatment.gif){#fig-treatment-example}

### Do people make these associations?

---

```{r}
#| label: fig-h-2-predictions
#| layout-nrow: 1
#| fig-cap: The partisanship of candidates change depending on the color of the yard sign
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["red_multinomial"]]
  , x_axis = "trial_1_red_stimuli"
)
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["blue_multinomial"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
)
red
blue
```

### What does conflicting colors do to these associations?

---

```{r}
#| label: fig-h-2a-predictions
#| layout-nrow: 2
#| fig-cap: Mixing red and blue in a yard sign increases uncertainty about partisanship
#| fig-subcap:
#|   - Trial 2 Red treatment
#|   - Trial 2 Blue treatment
#|   - Trial 3 Red treatment
#|   - Trial 3 Blue treatment
plot_trial_2_red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_2_red_multinomial"]]
  , x_axis = "trial_2_red_stimuli"
)
plot_trial_2_blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_2_blue_multinomial"]]
  , x_axis = "trial_2_blue_stimuli"
  , treatment = "Blue"
)
plot_trial_3_red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_3_red_multinomial"]]
  , x_axis = "trial_3_red_stimuli"
)
plot_trial_3_blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_3_blue_multinomial"]]
  , x_axis = "trial_3_blue_stimuli"
  , treatment = "Blue"
)
plot_trial_2_red
plot_trial_2_blue
plot_trial_3_red
plot_trial_3_blue
```

### Do these associations inform important political behavior?

```{r}
#| label: fig-h-3-predictions
#| layout-nrow: 1
#| fig-cap: Probability of voting for candidate with yard sign
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_3"]][["red"]]
  , x_axis = "trial_1_red_stimuli"
  , treatment = "Red"
  , hypothesis = "H3"
  , x_label = "Party ID"
  , y_label = "Pr(Vote for candidate)"
  , legend_title = "Treatment"
)
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_3"]][["blue"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
  , hypothesis = "H3"
  , x_label = "Party ID"
  , y_label = "Pr(Vote for candidate)"
  , legend_title = "Treatment"
)
red
blue
```

## Study 2

### Motivation of Study

---

> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party. We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades. The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.

---

> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.

---

- Do these associations have systematic influences on campaign strategy?

### Outcome variable - How much red and blue do campaigns use?

- Collect around 1,000 yard signs from House elections
  - 2016-2024
- Measuring the colors used on a yard sign:
  - Use a machine learning Python Library, `OpenCV`, that reads images and classifies their components.
    - Trained to classify each pixel in the image
    - Classifies it based on BGR value (reverse of RGB)
    - Looks for a range of values around the "Republican red" and "Democratic blue"

---

```{python}
#| label: example detection
#| echo: false

from sys import path # for path management
from cv2 import imread, imwrite # for color detection
    #* user-defined
#path.append("../")
from PY.helper import colorDetector

# Define colors to detect
    #* White
        #** Not defined. Default for colorDetector()
    #* Red
republican_red = [232, 27, 35] # target color
red_lower = [93, 9, 12] # lower end of spectrum for red
red_higher = [237, 69, 75] # higher end of spectrum for red

# Load gop image to read
img = imread("./assets/img/gop_2022.png")

# Detect colors
percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)

transformed= imwrite("../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image

masked= imwrite("../data/temp/study_2/gop_2022_detected.png", result) # save masked image
```

::: {#fig-color-detection-example layout-ncol="2"}
![Resized original image](../data/temp/study_2/gop_2022_transformed.png){#fig-resized}

![Masked](../data/temp/study_2/gop_2022_detected.png){#fig-masked}

Detecting colors in the GOP logo
:::

```{python}
#| output: asis
# Print calculated percentage of example
print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
```

### Predictor variable - What is the partisan composition of the district?
- MIT Election Lab data
  - House election results
  - 1970-2020
- Measuring partisan composition of district:
  - Calculate rolling 5-year average of the Democratic party's vote share for each district

### Do campaigns use a different proportion of the colors red and blue based on partisan composition?

---

```{r}
#| label: fig-study-2-pred
#| layout-ncol: 1
#| fig-cap: More blue on the yard signs in Democratic strongholds
#| fig-subcap:
#|   - Proportion of red
#|   - Proportion of blue
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_5"]][["red"]]
  , treatment = "Red"
  , hypothesis = "H5"
)
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_5"]][["blue"]]
  , treatment = "Blue"
  , hypothesis = "H5"
)
red
blue
```

## References

::: {#refs}
:::

## Appendix

### Study 1

---

#### Characteristics of sample

---

#### $H_1$

```{r}
#| label: tbl-h1-trial-1
#| tbl-cap: Average time between cursor movements (Trial 1)
df_movement_trial_1 <- list_df[["cleaned"]][
  , .(
    trial_1_difference_Time
    , trial_1_stimulus
    , trial_1_difference_X
    , trial_1_difference_Y
  )
]
setnames(
  df_movement_trial_1
  , old = c(
    "trial_1_difference_Time"
    , "trial_1_difference_X"
    , "trial_1_difference_Y"
  )
  , new = c(
    "$\\Delta_{t}$ (milliseconds)"
    , "$\\Delta_{x}$ (pixels)"
    , "$\\Delta_{y}$ (pixels)"
  )
)

datasummary_balance(
  ~trial_1_stimulus
  , data = df_movement_trial_1
  , notes = "Data source: Prolific sample."
  , escape = FALSE
  , output = "latex"
)
```

---

#### $H_5$

```{r}
#| label: fig-h-4
#| fig-cap: The effect of party congruency on time spent looking at yard sign
#| layout-ncol: 2
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment

red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_4"]][["red"]]
  , x_axis = "trial_1_red_stimuli"
  , treatment = "Red"
  , hypothesis = "H4"
  , x_label = "Party ID"
  , y_label = "Predicted amount of time elapsed"
  , legend_title = "Treatment"
)
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_4"]][["blue"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
  , hypothesis = "H4"
  , x_label = "Party ID"
  , y_label = "Predicted amount of time elapsed"
  , legend_title = "Treatment"
)
red
blue
```

## Copyright Information

<span class="faux-block">{{< fa brands creative-commons >}} 2021-2023 Damon Charles Roberts</span>
<span class="faux-block"><br>All content licensed under {{< fa brands creative-commons >}} {{< fa brands creative-commons-by >}} {{< fa brands creative-commons-sa >}} [Creative Commons CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/)</span>

### 2023-09-18 chapter_2/src/slides.qmd
adding some robustness stuff to the appendix

@@
     toc-depth: 2
-    slide-level: 3
+    slide-level: 5
     bibliography: ../../assets/references.bib   
@@
   ]
-  , data.table[...]
   , modelsummary[
@@
     , datasummary_balance
+    , modelsummary
   ]
   , ./R/predicted_prob_bar[...]
+  , data.table[...]
 )
+
 # Execute the cleaning script
 source("./eda/study_1/cleaning.R")
+# Load cleaned data
+list_df <- list()
+list_df[["cleaned"]] <- read.csv(
+  file = "../data/clean/cleaned_pavlovia.csv"
+)
 # Load fitted models
@@
 
+---
+
 - Collect around 1,000 yard signs from House elections
@@
 ### Predictor variable - What is the partisan composition of the district?
+
+---
+
 - MIT Election Lab data
@@
 
+```{r}
+#| label: tbl-study-1-descriptives
+#| tbl-cap: Descriptive statistics of Prolific sample
+
+df_demographics_subset <- list_df[["cleaned"]][
+    , c(
+        "Age" = "age"
+        , `Color blind` = "color_blind_dummy"
+        , "Female" = "female_sex"
+        , "White" = "white"
+        , "Hispanic" = "hispanic"
+        , "Black" = "black"
+        , `Party ID` = "pid_7"
+    )
+] |> 
+as.data.frame()
+
+datasummary_skim(
+    df_demographics_subset
+    , histogram = FALSE
+    , notes = c(
+      "Data source: Prolific."
+      , "Sample characteristics."
+    )
+
+)
+```
+
+---
+
+#### Measures
+
+---
+
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Measure                     | Question                                                                                                                                                                                                                                                                                                  | Coded as                                                                                                                                                           |
++=============================+:=========================================================================================================================================================================================================================================================================================================:+:==================================================================================================================================================================:+
+| Age                         | Confirm your age                                                                                                                                                                                                                                                                                          | Text entry                                                                                                                                                         |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Gender                      | What is your gender identity?
+| Non-binary, Female, Male, Prefer not to choose, Other                                                                                                              |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Sex                         | What is your sex assigned at birth?
+| Female, Male, Other                                                                                                                                                |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Race                        | Which ethnic or racial category best describes you?
+| White, non-Hispanic; Black, non-Hispanic; Hispanic; Asian or Native Hawaiian/other Pacific Islander; Native American/Alaska Native or other race; Multiple races   |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Color blind                 | Have you been diagnosed with any of the following visual impairments that are not treated with corrective lenses?
+| Color blindness (any form); Blurred vision (not treatable by corrective lenses); Macular degeneration; Glaucoma; Cataract; Diabetic retinopathy; None of the above |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Attention                   | How often do you pay attention to what is going on in government and politics?
+| Always; Most of the time; About half the time; Some of the time; Never                                                                                             |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Party ID                    | Generally speaking, do you usually think of yourself as a Democrat, a Republican, an Independent, or what?; Would you say that you are a strong [Republican/Democrat] or not a very strong [Republican/Democrat]?; Do you think of yourself as closer to the Republican party or to the Democratic party?
+| Republican, Democrat, Independent, Other; Strong, Not very strong; Closer to the Republican party, Neither, Closer to Democratic                                   |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Attn.
+Check                 | In a few words describe what is your first memory of a political event.
+| Text entry                                                                                                                                                         |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Trial stimuli               | Yard sign assigned                                                                                                                                                                                                                                                                                        | 0 = White, 1 = Red/Blue                                                                                                                                            |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Trial stimuli alt           | Yard sign assigned                                                                                                                                                                                                                                                                                        | 0 = Not red/blue, 1 = Red/Blue                                                                                                                                     |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Time elapsed                | NA                                                                                                                                                                                                                                                                                                        | Difference between time at start of trial and stop                                                                                                                 |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| $\Delta_{t}$ (milliseconds) | NA                                                                                                                                                                                                                                                                                                        | Time elapsed between cursor movements                                                                                                                              |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| $\Delta_{x}$ (pixels)       | NA                                                                                                                                                                                                                                                                                                        | Number of pixels moved along x-axis                                                                                                                                |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| $\Delta_{y}$ (pixels)       | NA                                                                                                                                                                                                                                                                                                        | Number of pixels moved along y-axis                                                                                                                                |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Candidate party             | Is this candidate a Republican, a Democrat, or Neither?
+| Republican, Democrat, Neither                                                                                                                                      |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Candidate vote              | Of the three candidates who would you most likely vote for?
+| The first yard sign, The second yard sign, The third yard sign                                                                                                     |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Candidate vote indicator    | NA                                                                                                                                                                                                                                                                                                        | 0 = Would not vote for first yard sign, 1 = Would vote for first yard sign                                                                                         |
++-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+
+: Study 1 Measures {#tbl-study-1-measures}
+
 #### $H_1$
@@
 df_movement_trial_1 <- list_df[["cleaned"]][
-  , .(
-    trial_1_difference_Time
-    , trial_1_stimulus
-    , trial_1_difference_X
-    , trial_1_difference_Y
+  , c(
+    "trial_1_difference_Time"
+    , "trial_1_stimulus"
+    , "trial_1_difference_X"
+    , "trial_1_difference_Y"
   )
@@
   , new = c(
-    "$\\Delta_{t}$ (milliseconds)"
-    , "$\\Delta_{x}$ (pixels)"
-    , "$\\Delta_{y}$ (pixels)"
+    "Δ<sub>t</sub> (milliseconds)"
+    , "Δ<sub>x</sub> (pixels)"
+    , "Δ<sub>y</sub> (pixels)"
   )
@@
   , escape = FALSE
+)
+```
+
+---
+
+#### $H_2$
+
+---
+
+##### Multinomial Logit
+
+```{r}
+#| label: tbl-hypothesis-2-main
+#| tbl-cap: Full results for reported models in $H_2$
+# Redefine names
+list_fitted_split_1 <- list(
+  "Red treatment" = list_fitted[["h_2"]][["red_multinomial"]]
+  , "Blue treatment" = list_fitted[["h_2"]][["blue_multinomial"]]
+)
+
+# Change goodness of fit stuff
+gm <- list(
+  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
+  , list("raw" = "r.squared", "clean" = "R<sup>2</sup>", "fmt" = 2)
+  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
+)
+# Make table
+modelsummary(
+  list_fitted_split_1
+  , coef_map = c(
+    "b_mu2_trial_1_red_stimuli" = "Red yard sign (Independent)"
+    , "b_mu3_trial_1_red_stimuli" = "Red yard sign (Republican)"
+    , "b_mu2_trial_1_blue_stimuli" = "Blue yard sign (Independent)"
+    , "b_mu3_trial_1_blue_stimuli" = "Blue yard sign (Republican)"
+    , "b_mu2_Intercept" = "Intercept - Independent"
+    , "b_mu3_Intercept" = "Intercept - Republican"
+    )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm 
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , "of claiming candidate is not a Democrat."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , "of the draws from the posterior distribution."
+  )
+  , escape = TRUE
+
+)
+```
+
+---
+
+```{r}
+#| label: fig-h-2-ppc-multinomial
+#| fig-cap: Posterior predictive check of Multinomial models for $H_2$
+#| fig-subcap:
+#|   - Red treatment
+#|   - Blue treatment
+
+list_ppc[["h_2"]][["red_multinomial"]]
+list_ppc[["h_2"]][["blue_multinomial"]]
+```
+
+##### Ordered Logit
+
+```{r}
+#| label: tbl-hypothesis-2-ordered
+#| tbl-cap: Full results for reported ordered logistic regression models for $H_2$
+# Redefine names
+list_fitted_split_1_alt <- list(
+  "Red treatment" = list_fitted[["h_2"]][["red_ordinal"]]
+  , "Blue treatment" = list_fitted[["h_2"]][["blue_ordinal"]]
+)
+
+# Change goodness of fit stuff
+gm <- list(
+  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
+  , list("raw" = "r.squared", "clean" = "R<sup>2</sup>", "fmt" = 2)
+  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
+)
+# Make table
+modelsummary(
+  list_fitted_split_1_alt
+  , coef_map = c(
+    "b_trial_1_red_stimuli" = "Red yard sign"
+    , "b_trial_1_blue_stimuli" = "Blue yard sign"
+    , "b_Intercept[1]" = "Intercept 1"
+    , "b_Intercept[2]" = "Intercept 2"
+    )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm 
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , "of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , "of the draws from the posterior distribution."
+  )
+  , escape = TRUE
+
+)
+```
+
+---
+
+```{r}
+#| label: fig-h-2-ppc-ordered
+#| fig-cap: Posterior predictive checks of Ordered Logit models in $H_2$
+#| fig-subcap:
+#|   - Red treatment
+#|   - Blue treatment
+
+list_ppc[["h_2"]][["red_ordinal"]]
+list_ppc[["h_2"]][["blue_ordinal"]]
+```
+
+##### Single model
+
+```{r}
+#| label: tbl-robustness-alt-specification-h-2
+#| tbl-cap: $H_2$ models with alternative specification
+# Redefine names
+list_fitted_split_3 <- list(
+  "Single model" = list_fitted[["h_2"]][["single_model"]]
+)
+
+# Make table
+modelsummary(
+  list_fitted_split_3
+  , coef_map = c(
+    "b_trial_1_red_stimuli_alt" = "Red yard sign"
+    , "b_trial_1_blue_stimuli_alt" = "Blue yard sign"
+    , "b_Intercept[1]" = "Intercept 1"
+    , "b_Intercept[2]" = "Intercept 2"
+  )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = TRUE
+
+)
+```
+
+---
+
+```{r}
+#| label: fig-h-2-ppc-single
+#| fig-cap: Posterior predictive checks of single model specification for $H_2$
+
+list_ppc[["h_2"]][["single_model"]]
+
+```
+
+##### Moderated by age
+
+```{r}
+#| label: tbl-interacted-models-h-2
+#| tbl-cap: $H_2$ models moderated by age
+# Redefine names
+list_fitted_split_2 <- list(
+  "Red treatment - Age moderating" = list_fitted[["h_2"]][["red_interact"]]
+  , "Blue treatment - Age moderating" = list_fitted[["h_2"]][["blue_interact"]]
+)
+
+# Make table
+modelsummary(
+  list_fitted_split_2
+  , coef_map = c(
+    "b_trial_1_red_stimuli" = "Red yard sign"
+    , "b_trial_1_blue_stimuli" = "Blue yard sign"
+    , "b_age" = "Age"
+    , "b_trial_1_red_stimuli:age" = "Red yard sign × Age"
+    , "b_trial_1_blue_stimuli:age" = "Blue yard sign × Age"
+    , "b_Intercept[1]" = "Intercept 1"
+    , "b_Intercept[2]" = "Intercept 2"
+    )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm 
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = TRUE
+
+)
+```
+
+---
+
+```{r}
+#| label: fig-h-2-ppc-age
+#| fig-cap: Posterior predictive checks of models in $H_2$ moderated by age
+#| fig-subcap:
+#|   - Red treatment moderated by age
+#|   - Blue treatment moderated by age
+
+list_ppc[["h_2"]][["red_interact"]]
+list_ppc[["h_2"]][["blue_interact"]]
+```
+
+##### Moderated by colorblindness
+
+```{r}
+#| label: tbl-colorblindness
+#| tbl-cap: $H_2$ moderated by colorblindness
+
+# Redefine names
+list_fitted_split_4 <- list(
+  "Red - Color blindness moderating" = list_fitted[["h_2"]][["red_colorblind"]]
+  , "Blue - Color blindness moderating" = list_fitted[["h_2"]][["blue_colorblind"]]
+)
+# Make table
+modelsummary(
+  list_fitted_split_4
+  , coef_map = c(
+    "b_trial_1_red_stimuli" = "Red yard sign"
+    , "b_trial_1_blue_stimuli" = "Blue yard sign"
+    , "b_trial_1_red_stimuli:color_blind_dummy" = "Red yard sign × Color blind"
+    , "b_trial_1_blue_stimuli:color_blind_dummy" = "Blue yard sign × Color blind"
+    , "b_Intercept[1]" = "Intercept 1"
+    , "b_Intercept[2]" = "Intercept 2"
+  )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm 
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = TRUE
+
+)
+```
+
+---
+
+```{r}
+#| label: fig-h-2-ppc-colorblind
+#| fig-cap: Posterior predictive checks of models in $H_2$ moderated by colorblindness
+#| fig-subcap:
+#|   - Red treatment moderated by colorblindness
+#|   - Blue treatment moderated by colorblindness
+
+list_ppc[["h_2"]][["red_colorblind"]]
+list_ppc[["h_2"]][["blue_colorblind"]]
+```
+
+#### $H_{2a}$
+
+##### Multinomial
+
+```{r}
+#| label: tbl-hypothesis-2a
+#| tbl-cap: Full results for models testing bounds of $H_2$
+# Redefine names
+model_names <- list(
+  "Trial 2 - Red treatment" = list_fitted[["h_2a"]][["trial_2_red_multinomial"]]
+  , "Trial 2 - Blue treatment" = list_fitted[["h_2a"]][["trial_2_blue_multinomial"]]
+  , "Trial 2 - Single model" = list_fitted[["h_2a"]][["trial_2_single_model"]]
+)
+
+# Change goodness of fit stuff
+gm <- list(
+  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
+  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
+  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
+)
+# Make table
+modelsummary(
+  model_names
+  , coef_map = c(
+    "b_mu2_trial_2_red_stimuli" = "Red yard sign (Independent)"
+    , "b_mu3_trial_2_red_stimuli" = "Red yard sign (Republican)"
+    , "b_mu2_trial_2_blue_stimuli" = "Blue yard sign (Independent)"
+    , "b_mu3_trial_2_blue_stimuli" = "Blue yard sign (Republican)"
+    , "b_trial_2_red_stimuli_alt" = "Red yard sign"
+    , "b_trial_2_blue_stimuli_alt" = "Blue yard sign"
+    , "b_mu2_Intercept" = "Intercept - Independent"
+    , "b_mu3_Intercept" = "Intercept - Republican"
+    , "b_Intercept[1]" = "Intercept 1"
+    , "b_Intercept[2]" = "Intercept 2"
+    )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is not a Democrat (Columns 1 and 2) or is a Republican (Column 3)."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = FALSE
   , output = "latex"
@@
 
-#### $H_5$
+```{r}
+#| label: tbl-hypothesis-2a-cont
+#| tbl-cap: Full results for models testing bounds of $H_2$ (cont.)
+# Redefine names
+model_names <- list(
+  "Trial 3 - Red treatment" = list_fitted[["h_2a"]][["trial_3_red_multinomial"]]
+  , "Trial 3 - Blue treatment" = list_fitted[["h_2a"]][["trial_3_blue_multinomial"]]
+  , "Trial 3 - Single model" = list_fitted[["h_2a"]][["trial_3_single_model"]]
+)
+
+# Change goodness of fit stuff
+gm <- list(
+  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
+  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
+  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
+)
+# Make table
+modelsummary(
+  model_names
+  , coef_map = c(
+    "b_mu2_trial_3_red_stimuli" = "Red yard sign (Independent)"
+    , "b_mu3_trial_3_red_stimuli" = "Red yard sign (Republican)"
+    , "b_mu2_trial_3_blue_stimuli" = "Blue yard sign (Independent)"
+    , "b_mu3_trial_3_blue_stimuli" = "Blue yard sign (Republican)"
+    , "b_trial_3_red_stimuli_alt" = "Red yard sign"
+    , "b_trial_3_blue_stimuli_alt" = "Blue yard sign"
+    , "b_mu2_Intercept" = "Intercept - Independent"
+    , "b_mu3_Intercept" = "Intercept - Republican"
+    , "b_Intercept[1]" = "Intercept 1"
+    , "b_Intercept[2]" = "Intercept 2"
+    )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm 
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  , output = "latex"
+)
+```
+
+---
 
 ```{r}
-#| label: fig-h-4
-#| fig-cap: The effect of party congruency on time spent looking at yard sign
+#| label: tbl-hypothesis-2a-ordered
+#| tbl-cap: Full results for ordered logistic regressions testing bounds of $H_2$
+# Redefine names
+model_names <- list(
+  "Trial 2 - Red treatment" = list_fitted[["h_2a"]][["trial_2_red_ordinal"]]
+  , "Trial 2 - Blue treatment" = list_fitted[["h_2a"]][["trial_2_blue_ordinal"]]
+)
+
+# Change goodness of fit stuff
+gm <- list(
+  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
+  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
+  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
+)
+# Make table
+modelsummary(
+  model_names
+  , coef_map = c(
+    "b_trial_2_red_stimuli" = "Red yard sign"
+    , "b_trial_2_blue_stimuli" = "Blue yard sign"
+    , "b_Intercept[1]" = "Intercept 1"
+    , "b_Intercept[2]" = "Intercept 2"
+    )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  , output = "latex"
+)
+```
+
+```{r}
+#| label: tbl-hypothesis-2a-cont-ordered
+#| tbl-cap: Full results for models testing bounds of $H_2$ (cont.)
+# Redefine names
+model_names <- list(
+  "Trial 3 - Red treatment" = list_fitted[["h_2a"]][["trial_3_red_ordinal"]]
+  , "Trial 3 - Blue treatment" = list_fitted[["h_2a"]][["trial_3_blue_ordinal"]]
+)
+
+# Change goodness of fit stuff
+gm <- list(
+  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
+  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
+  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
+)
+# Make table
+modelsummary(
+  model_names
+  , coef_map = c(
+    "b_trial_3_red_stimuli" = "Red yard sign"
+    , "b_trial_3_blue_stimuli" = "Blue yard sign"
+    , "b_Intercept[1]" = "Intercept 1"
+    , "b_Intercept[2]" = "Intercept 2"
+    )
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm 
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  , output = "latex"
+)
+```
+
+##### Posterior predictive checks
+
+```{r}
+#| label: fig-h-2a-ppc
 #| layout-ncol: 2
+#| fig-cap: Posterior predictive checks of models in $H_2$
+#| fig-subcap:
+#|   - Red treatment (Trial 2 - Multinomial)
+#|   - Blue treatment (Trial 2 - Multinomial)
+#|   - Red treatment (Trial 2 - Ordered)
+#|   - Blue treatment (Trial 2 - Ordered)
+list_ppc[["h_2a"]][["trial_2_red_multinomial"]]
+list_ppc[["h_2a"]][["trial_2_blue_multinomial"]]
+list_ppc[["h_2a"]][["trial_2_red_ordinal"]]
+list_ppc[["h_2a"]][["trial_2_blue_ordinal"]]
+```
+
+```{r}
+#| label: fig-h-2a-ppc-cont
+#| layout-ncol: 2
+#| fig-cap: Posterior predictive checks of models in $H_2$ (cont.)
+#| fig-subcap:
+#|   - Combined model (Trial 2)
+#|   - Red treatment (Trial 3 - Multinomial)
+#|   - Blue treatment (Trial 3 - Multinomial)
+#|   - Red treatment (Trial 3 - Ordered)
+list_ppc[["h_2a"]][["trial_2_single_model"]]
+list_ppc[["h_2a"]][["trial_3_red_multinomial"]]
+list_ppc[["h_2a"]][["trial_3_blue_multinomial"]]
+list_ppc[["h_2a"]][["trial_3_red_ordinal"]]
+```
+
+```{r}
+#| label: fig-h-2a-ppc-cont-cont
+#| layout-ncol: 2
+#| fig-cap: Posterior predictive checks of models in $H_2$ (cont.)
+#| fig-subcap:
+#|   - Blue treatment (Trial 3 - Ordered)
+#|   - Combined model (Trial 3)
+list_ppc[["h_2a"]][["trial_3_blue_ordinal"]]
+list_ppc[["h_2a"]][["trial_3_single_model"]]
+```
+
+#### $H_3$
+
+##### Main results
+
+```{r}
+#| label: tbl-h-3-main
+#| tbl-cap: Support of candidate based on partisanship
+
+# Redefine names
+model_names <- list(
+  "Red stimuli" = list_fitted[["h_3"]][["red"]]
+  , "Blue stimuli" = list_fitted[["h_3"]][["blue"]]
+)
+
+# Make table
+modelsummary(
+  model_names
+  , coef_map = c(
+    "b_trial_1_red_stimuli" = "Red yard sign"
+    , "b_trial_1_blue_stimuli" = "Blue yard sign"
+    , "b_pid_7" = "Party ID"
+    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
+    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
+    , "b_attention" = "Attention"
+    , "b_age" = "Age"
+    , "b_gender_idMale" = "Gender - Male"
+    , "b_gender_idNonMbinary" = "Gender - Non-binary"
+    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
+    , "b_race_idBlacknonMhispanic" = "Black"
+    , "b_race_idHispanice" = "Hispanic"
+    , "b_race_idMultipleraces" = "Multiple races"
+    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
+    , "b_race_idWhitenonMhispanic" = "White"
+  )  
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm 
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  , output = "latex"
+)
+```
+
+##### Posterior Predictive Checks
+
+```{r}
+#| label: fig-h-3-ppc
+#| layout-ncol: 2
+#| fig-cap: Posterior Predictive checks for $H_3$ models
 #| fig-subcap:
@@
 #|   - Blue treatment
+list_ppc[["h_3"]][["red"]]
+list_ppc[["h_3"]][["blue"]]
+```
 
-red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_4"]][["red"]]
-  , x_axis = "trial_1_red_stimuli"
-  , treatment = "Red"
-  , hypothesis = "H4"
-  , x_label = "Party ID"
-  , y_label = "Predicted amount of time elapsed"
-  , legend_title = "Treatment"
+#### $H_4$
+
+##### ✅ for over-dispersion
+
+```{r}
+#| label: tbl-h-4-dispersion
+#| tbl-cap: Checking for over-dispersion of data
+df_over_dispersed <- list_df[["cleaned"]][, c("trial_1_time_elapsed")]
+names(df_over_dispersed)[names(df_over_dispersed) == 'trial_1_time_elapsed'] <- 'Time Elapsed'
+datasummary_skim(
+  df_over_dispersed
+  , notes = "Data source: Prolific sample."
+  , histogram = FALSE
 )
-blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_4"]][["blue"]]
-  , x_axis = "trial_1_blue_stimuli"
-  , treatment = "Blue"
-  , hypothesis = "H4"
-  , x_label = "Party ID"
-  , y_label = "Predicted amount of time elapsed"
-  , legend_title = "Treatment"
+```
+
+##### Main results
+
+```{r}
+#| label: tbl-h-4
+#| tbl-cap: The effect of partisan congruency on time spent looking at a yard sign
+# Redefine names
+model_names <- list(
+  "Red stimuli" = list_fitted[["h_4"]][["red"]]
+  , "Blue stimuli" = list_fitted[["h_4"]][["blue"]]
 )
-red
-blue
+
+# Make table
+modelsummary(
+  model_names
+  , coef_map = c(
+    "b_trial_1_red_stimuli" = "Red yard sign"
+    , "b_trial_1_blue_stimuli" = "Blue yard sign"
+    , "b_pid_7" = "Party ID"
+    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
+    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
+    , "b_attention" = "Attention"
+    , "b_age" = "Age"
+    , "b_gender_idMale" = "Gender - Male"
+    , "b_gender_idNonMbinary" = "Gender - Non-binary"
+    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
+    , "b_race_idBlacknonMhispanic" = "Black"
+    , "b_race_idHispanice" = "Hispanic"
+    , "b_race_idMultipleraces" = "Multiple races"
+    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
+    , "b_race_idWhitenonMhispanic" = "White"
+  )  
+  , statistic = "conf.int"
+  , conf_level = 0.9
+  , gof_map = gm 
+  , notes = c(
+    "Data source: Pavlovia"
+    , "Positive coefficients reflect the logged-odds"
+    , " of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , " of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  , output = "latex"
+)
+```
+
+##### Posterior Predictive Checks
+
+```{r}
+#| label: fig-h-4-ppc
+#| layout-ncol: 2
+#| fig-cap: Posterior predictive checks of $H_4$ models
+#| fig-subcap:
+#|   - Red
+#|   - Blue
+list_ppc[["h_4"]][["red"]]
+list_ppc[["h_4"]][["blue"]]
+```
+
+#### $H_5$
+
+##### Main results
+
+```{r}
+#| label: tbl-hypothesis-5
+#| tbl-cap: The effect of democratic vote share on color choices for yard sign
+
+names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
+modelsummary(
+  list_fitted[["h_5"]]
+  , stat = "conf.int"
+  , conf_level = 0.9
+  , metrics = c("n.obs", "RMSE")
+  , coef_map = c(
+    "b_dem_vote_share" = "Democratic vote share (percent)"
+    , "b_Intercept" = "Intercept"
+  )
+  , notes = c(
+    "Data source: Center for Political Design and MIT Election Lab"
+    , "Positive coefficients reflect the logged-odds"
+    , "of claiming candidate is Republican."
+    , "Numbers inside brackets reflect the 5th and 95th percentile"
+    , "of the draws from the posterior distribution."
+  )
+  , escape = FALSE
+  #, output = "latex"
+)
+```
+
+##### Posterior Predictive Checks
+
+```{r}
+#| label: fig-hypothesis-5-ppc
+#| layout-ncol: 2
+#| fig-cap: Posterior Predictive checks for $H_5$
+#| fig-subcap:
+#|   - Proportion of yard signs red
+#|   - Proportion of yard signs blue
+
+list_ppc[["h_5"]][["red"]]$continuous
+list_ppc[["h_5"]][["blue"]]$continuous
 ```

### 2023-09-18 chapter_2/src/slides.qmd
update site

@@
 
+## Questions and Comments
+
 ## References
@@
   )
-  , escape = TRUE
+  , escape = FALSE
 
@@
 ```
+
+---
 
@@
 
+---
+
 #### $H_{2a}$
+
+---
 
@@
   list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
-  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
+  , list("raw" = "r.squared", "clean" = "R<sup>2</sup>", "fmt" = 2)
   , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
@@
   , escape = FALSE
-  , output = "latex"
-)
+
+)
+```
+
+---
+
+```{r}
+#| label: fig-h-2a-multinomial-trial-2-ppc
+#| fig-cap: Posterior Predictive Checks for Multinomial models testing $H_{2a}$, Trial 2
+#| fig-subcap:
+#|   - Red treatment
+#|   - Blue treatment
+#|   - Single model
+
+list_ppc[["h_2a"]][["trial_2_red_multinomial"]]
+list_ppc[["h_2a"]][["trial_2_blue_multinomial"]]
+list_ppc[["h_2a"]][["trial_2_single_model"]]
 ```
@@
   , escape = FALSE
-  , output = "latex"
-)
-```
-
----
+
+)
+```
+
+---
+
+```{r}
+#| label: fig-h-2a-multinomial-trial-3-ppc
+#| fig-cap: Posterior Predictive Checks for Multinomial models testing $H_{2a}$, Trial 3
+#| fig-subcap:
+#|   - Red treatment
+#|   - Blue treatment
+#|   - Single model
+
+list_ppc[["h_2a"]][["trial_3_red_multinomial"]]
+list_ppc[["h_2a"]][["trial_3_blue_multinomial"]]
+list_ppc[["h_2a"]][["trial_3_single_model"]]
+```
+
+---
+
+##### Ordinal model
 
@@
   , escape = FALSE
-  , output = "latex"
-)
-```
+
+)
+```
+
+---
+
+```{r}
+#| label: fig-h-2a-ordinal-trial-2-ppc
+#| fig-cap: Posterior Predictive Checks for Ordinal models testing $H_{2a}$, Trial 2
+#| fig-subcap:
+#|   - Red treatment
+#|   - Blue treatment
+
+list_ppc[["h_2a"]][["trial_2_red_ordinal"]]
+list_ppc[["h_2a"]][["trial_2_blue_ordinal"]]
+```
+---
 
@@
   , escape = FALSE
-  , output = "latex"
-)
-```
-
-##### Posterior predictive checks
-
-```{r}
-#| label: fig-h-2a-ppc
-#| layout-ncol: 2
-#| fig-cap: Posterior predictive checks of models in $H_2$
-#| fig-subcap:
-#|   - Red treatment (Trial 2 - Multinomial)
-#|   - Blue treatment (Trial 2 - Multinomial)
-#|   - Red treatment (Trial 2 - Ordered)
-#|   - Blue treatment (Trial 2 - Ordered)
-list_ppc[["h_2a"]][["trial_2_red_multinomial"]]
-list_ppc[["h_2a"]][["trial_2_blue_multinomial"]]
-list_ppc[["h_2a"]][["trial_2_red_ordinal"]]
-list_ppc[["h_2a"]][["trial_2_blue_ordinal"]]
-```
-
-```{r}
-#| label: fig-h-2a-ppc-cont
-#| layout-ncol: 2
-#| fig-cap: Posterior predictive checks of models in $H_2$ (cont.)
-#| fig-subcap:
-#|   - Combined model (Trial 2)
-#|   - Red treatment (Trial 3 - Multinomial)
-#|   - Blue treatment (Trial 3 - Multinomial)
-#|   - Red treatment (Trial 3 - Ordered)
-list_ppc[["h_2a"]][["trial_2_single_model"]]
-list_ppc[["h_2a"]][["trial_3_red_multinomial"]]
-list_ppc[["h_2a"]][["trial_3_blue_multinomial"]]
+
+)
+```
+
+---
+```{r}
+#| label: fig-h-2a-ordinal-trial-3-ppc
+#| fig-cap: Posterior Predictive Checks for Ordinal models testing $H_{2a}$, Trial 3
+#| fig-subcap:
+#|   - Red treatment
+#|   - Blue treatment
+
 list_ppc[["h_2a"]][["trial_3_red_ordinal"]]
-```
-
-```{r}
-#| label: fig-h-2a-ppc-cont-cont
-#| layout-ncol: 2
-#| fig-cap: Posterior predictive checks of models in $H_2$ (cont.)
-#| fig-subcap:
-#|   - Blue treatment (Trial 3 - Ordered)
-#|   - Combined model (Trial 3)
 list_ppc[["h_2a"]][["trial_3_blue_ordinal"]]
-list_ppc[["h_2a"]][["trial_3_single_model"]]
-```
+```
+
+---
 
@@
     , "b_pid_7" = "Party ID"
-    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
-    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
+    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign × Party ID"
+    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign × Party ID"
     , "b_attention" = "Attention"
@@
   , escape = FALSE
-  , output = "latex"
-)
-```
-
-##### Posterior Predictive Checks
+
+)
+```
+
+---
 
@@
 #| label: fig-h-3-ppc
-#| layout-ncol: 2
 #| fig-cap: Posterior Predictive checks for $H_3$ models
@@
 
+---
+
 #### $H_4$
+
+---
 
@@
 #| label: fig-h-4-ppc
-#| layout-ncol: 2
 #| fig-cap: Posterior predictive checks of $H_4$ models
@@
   , escape = FALSE
-  #, output = "latex"
-)
-```
-
-##### Posterior Predictive Checks
+
+)
+```
+
+---
 

### 2023-09-18 chapter_2/src/slides/slides 2.qmd
think I missed some files on last pr

--- 2023-09-18 chapter_2/src/slides.qmd
@@
     embed-resources: true
-    theme: [dark, ../assets/slides/custom.scss]
+    theme: [dark, ../../assets/slides/custom.scss]
     transition: slide
@@
     slide-level: 5
-    bibliography: ../../assets/references.bib   
+    bibliography: ../../../assets/references.bib   
     self-contained: true
-    output-file: color_and_conversation.html
+    output-file: color-book.html
 execute:
@@
   ]
-  , ./R/predicted_prob_bar[...]
+  , ../R/predicted_prob_bar[...]
   , data.table[...]
@@
 
-# Execute the cleaning script
-source("./eda/study_1/cleaning.R")
 # Load cleaned data
@@
 list_df[["cleaned"]] <- read.csv(
-  file = "../data/clean/cleaned_pavlovia.csv"
+  file = "../../data/clean/cleaned_pavlovia.csv"
 )
 # Load fitted models
-load("../data/temp/models/study_1_fitted.RData")
+load("../../data/temp/models/study_1_fitted.RData")
 ```
@@
 
-[![1860s Ballots](../assets/slides/imgs/ballots.avif){#fig-ballots}](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)
+[![1860s Ballots](../../assets/slides/imgs/ballots.avif){#fig-ballots}](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)
 
@@
 
-[![Democratic National Convention](../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem height=100}](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)
-
-[![Republican National Convention](../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep height=100}](https://reuther.wayne.edu/node/9207)
+[![Democratic National Convention](../../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem height=100}](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)
+
+[![Republican National Convention](../../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep height=100}](https://reuther.wayne.edu/node/9207)
 
@@
 
-[![2000 Presidential Election map](../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=200}](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)
+[![2000 Presidential Election map](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=200}](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)
 
@@
 
-![Republicans pre-2000](./assets/img/rnc_logo_pre-2000.png){#fig-republican}
-
-![Democrats pre-2000](./assets/img/dnc_logo_1960.png){#fig-democrat}
-
-![Republicans 2023](./assets/img/rnc_logo_2023.png){#fig-republican-post}
-
-![Democrats 2023](./assets/img/dnc_logo_2023.png){#fig-democrat-post}
+![Republicans pre-2000](../assets/img/rnc_logo_pre-2000.png){#fig-republican}
+
+![Democrats pre-2000](../assets/img/dnc_logo_1960.png){#fig-democrat}
+
+![Republicans 2023](../assets/img/rnc_logo_2023.png){#fig-republican-post}
+
+![Democrats 2023](../assets/img/dnc_logo_2023.png){#fig-democrat-post}
 
@@
 
-[![The public](../assets/slides/imgs/division.webp){#fig-public}](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)
+[![The public](../../assets/slides/imgs/division.webp){#fig-public}](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)
 
@@
 %%| fig-cap: Memory model of info processing
+%%| fig-width: 6.5
 graph TD;
@@
 %%| fig-cap: Online model of info processing
+%%| fig-width: 6.5
 graph TD;
@@
 
-{{< include ../../assets/_theory.qmd >}}
+{{< include ../../../assets/_theory.qmd >}}
 
@@
 
-![Red condition](./study_1/assets/rep_yard_sign_round_1.png)
-![Blue condition](./study_1/assets/dem_yard_sign_round_1.png)
-![White condition](./study_1/assets/cont_yard_sign_round_1.png)
+![Red condition](../study_1/assets/rep_yard_sign_round_1.png)
+![Blue condition](../study_1/assets/dem_yard_sign_round_1.png)
+![White condition](../study_1/assets/cont_yard_sign_round_1.png)
 
@@
 
-![Red condition](./study_1/assets/rep_yard_sign_round_2.png)
-![Blue condition](./study_1/assets/dem_yard_sign_round_2.png)
-![White condition](./study_1/assets/cont_yard_sign_round_2_3.png)
+![Red condition](../study_1/assets/rep_yard_sign_round_2.png)
+![Blue condition](../study_1/assets/dem_yard_sign_round_2.png)
+![White condition](../study_1/assets/cont_yard_sign_round_2_3.png)
 
@@
 
-![Red condition](./study_1/assets/rep_yard_sign_round_3.png)
-![Blue condition](./study_1/assets/dem_yard_sign_round_3.png)
-![White condition](./study_1/assets/cont_yard_sign_round_2_3.png)
+![Red condition](../study_1/assets/rep_yard_sign_round_3.png)
+![Blue condition](../study_1/assets/dem_yard_sign_round_3.png)
+![White condition](../study_1/assets/cont_yard_sign_round_2_3.png)
 
@@
 
-![Example of treatment](../assets/slides/imgs/treatment.gif){#fig-treatment-example}
+![Example of treatment](../../assets/slides/imgs/treatment.gif){#fig-treatment-example}
 
@@
     #* user-defined
-#path.append("../")
+sys.path.append("../")
 from PY.helper import colorDetector
@@
 # Load gop image to read
-img = imread("./assets/img/gop_2022.png")
+img = imread("../assets/img/gop_2022.png")
 
@@
 
-transformed= imwrite("../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
-
-masked= imwrite("../data/temp/study_2/gop_2022_detected.png", result) # save masked image
+transformed= imwrite("../../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
+
+masked= imwrite("../../data/temp/study_2/gop_2022_detected.png", result) # save masked image
 ```
@@
 ::: {#fig-color-detection-example layout-ncol="2"}
-![Resized original image](../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
-
-![Masked](../data/temp/study_2/gop_2022_detected.png){#fig-masked}
+![Resized original image](../../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
+
+![Masked](../../data/temp/study_2/gop_2022_detected.png){#fig-masked}
 

### 2023-09-19 grants/ddirg/src/roberts_biographical_sketch.qmd
adding drafts of grant applications for DDIRG

---
subtitle: Biographical sketch
format:
  fancy-doc-pdf:
    toc: false
    latex-output-dir: ../out/
    biblatex: true
    filters:
      #- "_extensions/andrewheiss/wordcount/citeproc.lua"
      - "_extensions/andrewheiss/wordcount/wordcount.lua"
author:
  - name: Damon C. Roberts
    affiliations:
      - name: Univeristy of Colorado Boulder
    email: damon.roberts-1@colorado.edu
bibliography: ../../../assets/references.bib
---

I have a track record of successfully earning and using awarded research grants for my projects. I have earned grants from The Time-Sharing Experiments for the Social Science Short Studies Program (TESS), grants from my department, and a grant from the Elections, Voting, Public Opinion, and Behavior (EVOPB) Section of the American Political Science Association. I have published multiple peer-reviewed papers from these grants and have presented over 14 times at academic conferences.

Since the fall of 2019, I have published five peer-reviewed academic papers; on four of these I have been the first author. My research has appeared in Political Behavior, Political Research Quarterly, Social Science Quarterly, and twice in American Politics Research. I have several other papers at various stages of the publishing process. I am committed to expanding the reach of my work beyond academia, and have also engaged in a significant amount of public scholarship in the past year. I have co-authored a public piece discussing my research in the [*Washington Post's Monkey Cage Blog*](https://www.washingtonpost.com/politics/2022/07/21/biden-trump-president-age-2024-election/) and have agreed to a number of interviews about my research -- this includes a recorded interview with Colorado Public Radio and an interview written up in the New York Times.

In conjunction with my research, I have also been the instructor of record for two under-graduate statistics courses focused on introductory material for quantitative political science, as well as more advanced discussions of research design and causal inference. I have been a teaching assistant tasked with grading and leading discussion sections in introductory American Politics, formal modeling, campaigns and elections, and introductory research methodology.

All of these experiences have contributed to my development as a producer of research, but also as an academic who both values and has experience communicating my work to a wide array of audiences within and beyond academia. [An itemized CV is on my website](https://damoncroberts.com/cv/dcr_cv.pdf)
<!--
I have a track record of successfully earning and using awarded research grants for my projects. I have earned grants from The Time-Sharing Experiments for the Social Science Short Studies Program (TESS), research grants from my department five times, and a grant from the Elections, Voting, Public Opinion, and Behavior (EVOPB) Section of the American Political Science Association. I have published multiple peer-reviewed papers from these grants and presented over 14 times at an academic conference.

Since the fall of 2019, I have published five peer-reviewed academic papers, four of which I have been the first author. My research has appeared in Political Behavior, Political Research Quarterly, Social Science Quarterly, and twice in American Politics Research. I have several other papers at various stages of the publishing process. I am committed to expanding the reach of my work beyond academia and have also engaged in a significant amount of public scholarship in the past year. I have co-authored a public piece discussing my research in the [*Washington Post's Monkey Cage Blog*](https://www.washingtonpost.com/politics/2022/07/21/biden-trump-president-age-2024-election/) and have agreed to a number of interviews about my research which includes a recorded interview with Colorado Public Radio and an interview written up in the New York Times.

In conjunction with my research, I have also been the instructor of record for two undergraduate statistics courses focused on introductory material for quantitative political science and more advanced discussions of research design and causal inference. I have been a teaching assistant tasked with grading and leading discussion sections in introductory American Politics, formal modeling, campaigns and elections, and introductory research methodology.

All of these experiences have contributed to my development as a producer of research but also as an academic who has experience completing and publishing research and communicating my work to a wide array of audiences within and beyond academia. [An itemized CV is on my website.](https://damoncroberts.com/cv/dcr_cv.pdf)
-->

### 2023-09-19 grants/ddirg/src/roberts_description_and_plan.qmd
adding drafts of grant applications for DDIRG

---
subtitle: Project description & research plan
format:
  fancy-doc-pdf:
    toc: false
    latex-output-dir: ../out/
    biblatex: true
    filters:
      #- "_extensions/andrewheiss/wordcount/citeproc.lua"
      - "_extensions/andrewheiss/wordcount/wordcount.lua"
author:
  - name: Damon C. Roberts
    affiliations:
      - name: Univeristy of Colorado Boulder
    email: damon.roberts-1@colorado.edu
bibliography: ../../../assets/references.bib
---

# General discription of project and impact

Since the 2000 Presidential primary the use of the colors red and blue have seemingly become synonymous with the Republican and Democratic parties, respectively [@elving_2014_npr]. Though the two parties seemingly have leaned into the colors the media use to depict them on electoral maps (@williams_et-al_2022_jomp;see also @fig-party-brand), it is a bit less clear whether these associations are strong for the public and whether these associations influence a variety of significant political outcomes through attitude expression and behaviors.^[There certainly is a branching area of work that should be done here to examine why the two political parties have gone with these two colors. This is especially true given that in other countries the color red is often picked up by left-leaning paries while the color blue is picked up by right-leaning parties [see @maestre_medero_2022_pr]. I imagine that there is a feedback loop between the parties and the public that continue to strengthen the association between these particular colors and the parties. The goal of this project is to first establish what the psychological mechanisms are for the public to make these associations. This work can then be helpful for those that want to build upon these ideas to explore the motivations for the parties to continue to use these colors.] This project addresses these questions.

::: {#fig-party-brand layout-ncol=2}

![Republicans pre-2000](../../../chapter_2/src/assets/img/rnc_logo_pre-2000.png){#fig-republican}

![Democrats pre-2000](../../../chapter_2/src/assets/img/dnc_logo_1960.png){#fig-democrat}

![Republicans 2023](../../../chapter_2/src/assets/img/rnc_logo_2023.png){#fig-republican-post}

![Democrats 2023](../../../chapter_2/src/assets/img/dnc_logo_2023.png){#fig-democrat-post}

Party logos
:::

Though colors may appear to be small in the grand scheme of politics, this project argues that they are in-fact not. This dissertation lays out a cognitive model that explains how colors have potent consequences for perceptions of political candidate's, other individual's, and a group of people's partisan affiliation as well as how it influences significant political outcomes such as vote choice in low information environments, willingness to have a conversation with another person about politics, the conditions under which persuasion can occur, and where people choose to live.

While the outcomes of interest for this project vary, the goal of this project is to examine the ways in which visual information -- and even one of the most simple forms of visual information, color -- influences outcomes that those studying political behavior and political psychology have long been asking by outlining a cognitive model of visual information processing.

@fig-theory provides a visual depiction of my model that I refer to as the snap-judgment model of information processing. Rather than going into all of the affective and social neuroscience and psychology theories used in this model, I'll provide a couple of hypothetical to illustrate it and to explain a number of predictions I derive from it in the project.

{{< include ../../../assets/_theory.qmd >}}

In the first empirical chapter, I want to explore whether the use of the colors red and blue convey information about the partisanship of the candidate to voters. Some descriptive evidence [@williams_et-al_2022_jomp], evidence from my own data-collection efforts, and some informal conversations I have had with consultants employed in political marketing firms suggest that candidates use the colors red and blue to convey their affiliation to either the Republican or Democratic parties. It is unclear, however, whether this actually has any effect on the mass public. In the first empirical chapter, I argue that these colors do indeed provide such information.

When someone is driving down a highway and see a yard sign in a split second, the neuroscience literature would suggest that the color may be processed before any text-based information [see @ames_et-al_2012_ohsn]. This is a rather intuitive idea. It takes longer to connect the letters together to form a word and then to figure out what that word is connected to. Instead, there are fewer connections you have to make in your brain between colors and what they represent. As you are seeing a political yard sign, your brain is going to seek out connections between the color red or blue and how those are relevant in politics. Given that there seem to be descriptive differences between the parties in their usage of the colors red and blue, we should expect that people will first assume that a red yard sign was for a Republican candidate and a blue yard sign was for a Democratic canddiate. This is the snap-judgment we form. Now we are going to have some sort of valanced response to that information: a negative or a positive reaction. Theories of hot cognition would then suggest we are on a track. New information that comes in such as the name of the candidate, if we recognize it, will still be processed and will still have an impact on our final impression, however, our snap-judgment already set the perspective we are coming from. For example, if you see a blue yard sign but you recognize it was for Mitch McConnell, you may be confused once you realize it's for *that* Mitch McConnell -- the prominent Republican. Now, say that you don't recognize the name: you might then just assume that the candidate must be a Republican. After all, for years when you think of Republicans you think of the color red from their logo, from election night maps, etcetera. What this hypothetical example demonstrates is that I have theoretical expectations that Republicans are associated with the color red and that Democrats are associated with the color blue. Secondly, and perhaps most important, is the idea that the information that these colors provide puts our mind down a particular path and the way we express our attitudes are shaped by these colors. In the first example with the Mitch McConnell yard sign you feel confused about the conflicting information. In the situation where you do not recognize the name, the color seems to tell you what you need to know. As a voter with limited time, you may cast your vote based on the combination of the name and the color of the yard sign. This means that colors do have potent and downstream consequences.

For brevity's sake, I'll provide another analogy but examining a different set of political outcomes. Say you are watching the news on your phone while waiting at the gate for your flight. You see someone about to sit next to you and they are wearing a red hat -- you don't see at first what logos or writing is on the hat, you just see it is a red hat. Now, since you are watching the news, the most accessible context where red hats matter is in politics. You therefore may assume that they are a supporter of Donald Trump's. Your comfort with sitting next to that person or having them start up a converstation will undoubtedly be shaped by whether you are also a Republican. We often are reluctant to have conversations in politics with those that are outpartisans [@carlson_settle_2022_cup]. Often times though, we cannot control the actions of others and they may start talking to you when they notice that you are watching a CNN segment on the recent *Dobbs* decision which allowed states to pass laws restricting abortion access. Say that they tell you, "yeah, the *Dobbs* decision was the right call." In that situation, you feel just the same as you did when the conversation started, perhaps even more strongly but in the same direction. What if instead they tell you, "yeah, I might like Trump, but the *Dobbs* decision is allowing state governments to do whatever they want to tell us what we can do with our own bodies. And that is wrong." You may instead have this internal reaction of, "What? Really?" Instead of making you dig into your initial snap-judgment, you may now be more or less willing have a conversation with this person despite them clearly telling you that they are a Trump supporter. Months after this interaction, however, those feelings that change your impressions of the average Trump supporter may weaken. That is to say, that because you run into a pro-choice Trump supporter once it does not continue to drive more moderate views about who Trump supporters are; those effects will weaken over time without other similar instances. Say instead of watching CNN, you were watching ESPN -- you may instead assume that they are a Cardinal's fan and this information is much less relevant to shaping your conversations about political matters.

What these two examples highlight, and hopefully in an intuitive way due to the familiarity of these situations, is that this model of snap-judgments formed from visual information provides an intuitive set of predictions about how people should respond to color as a source of information under a number of different circumstances drawing on a number of theories from the affective and social neuroscience and psychological disciplines. Further, the model outlines a set of predictions for how this visual information has downstream consequences on the way in which we process more substantive political information such as a candidate's or a discussion partner's policy positions as has been done in studies relying on dominant theories of political information processing. The goal of this project is to make a broader argument about the importance of considering visual and other forms of information as political information and how this information shapes the processing of substantive information. While the partisan association of the colors red and blue may change (though, I am somewhat skeptical of that occuring given the hyper-polarized environment the United States finds itself in), the model relies on theories about how people cognitively tie visual information to more complex ideas and to social groups. Therefore, I expect that the overall argument and the model can plug in different colors, be tweaked for different circumstances, and can still produce useful predictions for political attitude expression and behavior. That is, while the focus is on the colors red and blue, the goal of the project is to set the ground work for a theoretical framework of visual inforamtion processing by which scholars can continue to build upon.

# Research activities in the project

## Existing data-collection

At this point, I have collected and analyzed the data to the first empirical chapter. In this chapter, I used a survey experiment to examine the degree to which the colors red and blue (at different amounts) shape perceptions of the candidate and subjects' reported willingness to vote for these candidates. In doing so, I collected data on the cursor movements of participants' screens while blurring most of the yard sign to emulate an eye-tracking experiment. In this study, I found that participants assigned to the red and blue yard sign conditions spent less time exploring the yard sign than participants assigned to a white yard sign condition indicating that they did not need to spend as much time exploring the text-based elements of the yard sign to evaluate it. It also demonstrated that a fictional candidate with more red on their yard sign were often presumed to be more Republican whereas candidates with moreblue on their yard sign were often presumed to be more Democratic. Yard signs that used less red or used a combination of red and blue often produced more ambivalence between subjects. Finally, the study demonstrated that Republicans who saw a red yard sign were more likely to report supporting that candidate than Republicans who saw a blue or white yard sign. Similarly, Republicans who saw blue or white yard signs were not likely to report supporting those candidates. Democrats who saw a blue yard sign were much more likely to vote for that candidate than those with red or white yard signs.

To demonstrate that these perceptions have real-world influences on campaigns' decisions about the colors included on their yard signs, I collected yard sign images from the Center for American Political Design website and used a machine learning library to calculate the proportion of the colors red and blue on their yard signs. I then merged these data with data from the MIT Election Lab to examine whether candidates for the House of Representatives that are running within competitive congressional districts were less likely to use the color red and blue than if they were in a district where they'd be motivated to use one partisan color over another. The results from this study supported my hypothesis: candidates running in districts where Republicans have historically been more electorally successful used more red than those running in districts where Republicans are less electorally succesful. I find similar effects for the use of the color blue and historically Democratic-leaning districts.

## A research plan and timeline

The remainder of the project seeks to build on this existing work to examine how this affiliation between the colors red and blue with Republicans and Democrats in political settings influences deliberation, persuasion, and perceptions of a neighborhood (a whole group of people as opposed to individual political actors). The timeline for completing the remainder of these studies would be to have them complete by the end of Spring (May 2024).

While it would be nice to study these with a combination of observational and experimental research designs, the outcomes of study for these remaining chapters are much less easy to collect observational data on. For example, of the handful of common observational studies used in the United States, few ask questions about people's conversations with others in politics. Further, none that I am aware of ask people to describe the visual and physical characteristics of the people that they are having conversations with. If I were to collect my own survey data on this, I am highly suspicious of people's memory about the color of the clothing that they are wearing despite its importance. This is because color is important as a form of information to form a snap-judgment, however, it is a form of subtle information that people may use only initially and forget later. Therefore, the use of this grant will be to help with the cost of performing experimental studies for both in-person samples as well as online samples.

I want to perform experimental designs with both in-person and online samples to accomplish a coupld of tasks. First, the online samples are designed to capture a more representative sample and to have a larger sample. However, the online samples are a bit more limited in terms of the treatments that I can assign subjects to. The in-person studies are meant to provide slightly more realistic treatments to my participants as well as making it less clear to participants that they have been introduced to a treatment in the first place. For example, in one of my in-person studies, I will have participants meet at a building on the University of Colorado's campus. As they are entering the building, there will be a canvasser asking people to sign a petition. I will vary whether the color of the shirt that the person is wearing. While doing so, the behavior of the participants will be recorded to see whether they stop to talk to the person and whether they sign the petition. In the online experiment, instead participants will be shown an image of a person that they have been "matched to have a conversation with." Each of these treatments have advantages and disadvantages, and so do the samples. The goal is to perform these with different samples and slightly different designs in hopes of being able to replicate the conclusions I draw from them.

To perform multiple studies to replicate findings is quite costly for a graduate student at a public university. The grant would be a significant help to allow me to run these studies for the chapter on deliberation and on environmental cues in both in-person and online settings. It would also help me hire an RA to stand-in as the people they are interacting with in the in-person version of the studies as well as a "model" for the images in the online studies. Without this grant, I would likely be limited to a one-shot sample for each chapter and will need to do it with an online sample. The added ability for replication and to test it with both internally consistent and externally valid treatments would be a significant boost to the remaining chapters' empirical evidence. It would also allow me to include more treatment conditions to test how the effects of color on the outcomees are conditioned on whether the colors are presented in a way where politics is primed or for example if they seem irrelevant such as the color for a sports team instead. Adding these additional treatment conditions would help with directly testing the scope conditions of the way that color conveys political information.

### 2023-09-19 grants/ddirg/src/roberts_proposal_summary.qmd
adding drafts of grant applications for DDIRG

---
subtitle: Proposal Summary
format:
  fancy-doc-pdf:
    toc: false
    latex-output-dir: ../out/
    biblatex: true
    filters:
      #- "_extensions/andrewheiss/wordcount/citeproc.lua"
      - "_extensions/andrewheiss/wordcount/wordcount.lua"
author:
  - name: Damon C. Roberts
    affiliations:
      - name: Univeristy of Colorado Boulder
    email: damon.roberts-1@colorado.edu
bibliography: ../../../assets/references.bib
---

The use of the colors red and blue to distinguish the two dominant political parties in the United States started during the 2000 Presidential Election with the electoral maps [@elving_2014_npr]. Since then, the two political party's logos have changed rather dramatically in that now the Republican party uses the color red, and the Democratic party only uses the color blue. @fig-party-brand nicely illustrates this point. Some existing descriptive research demonstrates that these clear distinctions in color are not limited to party logos but that Democrats use more blue than Republicans. In contrast, Republicans use more red on their campaign's yard signs [@williams_et-al_2022_jomp].^[The first empirical chapter of this dissertation replicates this finding when exploring the rates of color usage among partisans in districts that have more or less electoral competition.] There are two primary questions for this dissertation and book project. The first question seeks to answer whether the colors red and blue carry affiliative information for voters to use as a heuristic. The second question asks whether this affiliative information that these colors may provide influence attitude expression and behavior, even in the face of more traditional substantive political information.

::: {#fig-party-brand layout-ncol=2}

![Republicans pre-2000](../../../chapter_2/src/assets/img/rnc_logo_pre-2000.png){#fig-republican}

![Democrats pre-2000](../../../chapter_2/src/assets/img/dnc_logo_1960.png){#fig-democrat}

![Republicans 2023](../../../chapter_2/src/assets/img/rnc_logo_2023.png){#fig-republican-post}

![Democrats 2023](../../../chapter_2/src/assets/img/dnc_logo_2023.png){#fig-democrat-post}

Party logos
:::

The primary contribution of this project is the cognitive model of visual information that it provides. Existing work on the visual aspects of politics is a newer area of work and comes from several different academic disciplines. This leaves us with a somewhat fragmented theory of how visual information affects mass attitudes and behavior. This project lays out a model that not only illustrates how visual information like color may be a source of information in politics; but as visual information is often processed faster than more symbolic information such as substantive political information, it also illustrates that the first-order information explaining an individual's attitude expression is visual information, such as color. The empirical chapters of the project discuss how this influences our understanding of vote choice and the value of yard signs to campaigns, discuss how this informs the degree to which people engage in conversations about politics, provides a typology of when persuasion can occur, and explains how we can make guesses about the partisanship of a group of people based on the way they have curated the environment in which they reside.

This grant would be a significant help with the costs of data collection. While I have performed the data collection for the first of the three primary empirical chapters, the last two require several experiments that require both online surveys and in-person experiments. Therefore, financial assistance with recruiting sufficiently powered and representative samples, along with adequately paying these participants for participating in these studies, would be a tremendous help for the completion of this dissertation and will remove the need for me to redo a number of these studies when working on the book project after defending the dissertation.

### 2023-09-19 grants/ddirg/src/roberts_description_and_plan.qmd
update draft of files

@@
 
-# General discription of project and impact
+# General description of project and impact
 
-Since the 2000 Presidential primary the use of the colors red and blue have seemingly become synonymous with the Republican and Democratic parties, respectively [@elving_2014_npr].
-Though the two parties seemingly have leaned into the colors the media use to depict them on electoral maps (@williams_et-al_2022_jomp;see also @fig-party-brand), it is a bit less clear whether these associations are strong for the public and whether these associations influence a variety of significant political outcomes through attitude expression and behaviors.^[There certainly is a branching area of work that should be done here to examine why the two political parties have gone with these two colors.
-This is especially true given that in other countries the color red is often picked up by left-leaning paries while the color blue is picked up by right-leaning parties [see @maestre_medero_2022_pr].
-I imagine that there is a feedback loop between the parties and the public that continue to strengthen the association between these particular colors and the parties.
-The goal of this project is to first establish what the psychological mechanisms are for the public to make these associations.
+Since the 2000 Presidential election the use of the color red has become synonymous with the Republican party, while the use of the color blue has become synonymous with the Democratic party [@elving_2014_npr].
+Though the two parties have leaned into the colors used in media depicitions of electoral maps [@williams_et-al_2022_jomp; see also @fig-party-brand], it remains unclear whether these associations are strong for the public, and whether these associations influence a political outcomes, including attitude expression and behaviors.^[Additional work should be done here to examine why the two political parties have gone with these two colors.
+This is especially true given that in other countries the color red is often picked up by left-leaning parties while the color blue is picked up by right-leaning parties [see @maestre_medero_2022_pr].
+I imagine that there is a feedback loop between the parties and the public that continues to strengthen the association between these particular colors and the parties.
+The goal of this project is to first establish what the cognitive mechanisms are for the public to establish these associations.
 This work can then be helpful for those that want to build upon these ideas to explore the motivations for the parties to continue to use these colors.] This project addresses these questions.
@@
 
-Though colors may appear to be small in the grand scheme of politics, this project argues that they are in-fact not.
-This dissertation lays out a cognitive model that explains how colors have potent consequences for perceptions of political candidate's, other individual's, and a group of people's partisan affiliation as well as how it influences significant political outcomes such as vote choice in low information environments, willingness to have a conversation with another person about politics, the conditions under which persuasion can occur, and where people choose to live.
+Though some may consider color a small concern in the grand scheme of politics, this project argues the opposite.
+This dissertation lays out a cognitive model that explains how colors may have potent consequences for perceptions of the political affiliations of candidates, individuals, and groups.
+In the project I also consider how color influences a variety of significant (political) outcomes -- these include vote choice in low information environments, the willingness to have a conversation with another person about politics, the conditions under which persuasion can occur, and where people choose to live.
 
-While the outcomes of interest for this project vary, the goal of this project is to examine the ways in which visual information -- and even one of the most simple forms of visual information, color -- influences outcomes that those studying political behavior and political psychology have long been asking by outlining a cognitive model of visual information processing.
+While the outcomes of this project vary, the underlying goal is to examine the ways in which visual information -- and even one of the most simple forms of visual information, color -- influences long-studied outcomes in political behavior and political psychology.
+I do this by developing a cognitive model of visual information processing.
 
-@fig-theory provides a visual depiction of my model that I refer to as the snap-judgment model of information processing.
-Rather than going into all of the affective and social neuroscience and psychology theories used in this model, I'll provide a couple of hypothetical to illustrate it and to explain a number of predictions I derive from it in the project.
+@fig-theory provides a visual depiction of what I refer to as the snap-judgment model of visual information processing.
+Given space constraints, rather than going into all of the affective and social neuroscience and psychology theories used in this model, here I provide a couple of hypotheticals to illustrate it and to explain a number of predictions I derive from the model.
 
@@
 
-In the first empirical chapter, I want to explore whether the use of the colors red and blue convey information about the partisanship of the candidate to voters.
+In the first empirical chapter, I explore whether the use of the colors red and blue convey information about the partisanship of a candidate to voters.
 Some descriptive evidence [@williams_et-al_2022_jomp], evidence from my own data-collection efforts, and some informal conversations I have had with consultants employed in political marketing firms suggest that candidates use the colors red and blue to convey their affiliation to either the Republican or Democratic parties.
 It is unclear, however, whether this actually has any effect on the mass public.
-In the first empirical chapter, I argue that these colors do indeed provide such information.
+In the first empirical chapter of my dissertation, I argue that these colors do indeed provide such information.
 
-When someone is driving down a highway and see a yard sign in a split second, the neuroscience literature would suggest that the color may be processed before any text-based information [see @ames_et-al_2012_ohsn].
+When someone is driving down a highway and sees a yard sign in a split second, the neuroscience literature would suggest that the color may be processed before any text- based information [see @ames_et-al_2012_ohsn].
 This is a rather intuitive idea.
 It takes longer to connect the letters together to form a word and then to figure out what that word is connected to.
-Instead, there are fewer connections you have to make in your brain between colors and what they represent.
+That is, there are fewer connections you have to make in your brain between colors and what they represent.
 As you are seeing a political yard sign, your brain is going to seek out connections between the color red or blue and how those are relevant in politics.
-Given that there seem to be descriptive differences between the parties in their usage of the colors red and blue, we should expect that people will first assume that a red yard sign was for a Republican candidate and a blue yard sign was for a Democratic canddiate.
+Given that there seem to be descriptive differences between the parties in their usage of the colors red and blue, we should expect that people will first assume that a red yard sign is for a Republican candidate and a blue yard sign is for a Democratic candidate.
 This is the snap-judgment we form.
 Now we are going to have some sort of valanced response to that information: a negative or a positive reaction.
-Theories of hot cognition would then suggest we are on a track.
-New information that comes in such as the name of the candidate, if we recognize it, will still be processed and will still have an impact on our final impression, however, our snap-judgment already set the perspective we are coming from.
-For example, if you see a blue yard sign but you recognize it was for Mitch McConnell, you may be confused once you realize it's for *that* Mitch McConnell -- the prominent Republican.
-Now, say that you don't recognize the name: you might then just assume that the candidate must be a Republican.
-After all, for years when you think of Republicans you think of the color red from their logo, from election night maps, etcetera.
+Theories of hot cognition would suggest we are on a track.
+New information that comes in such as the name of the candidate, if we recognize it, will still be processed and will still have an impact on our final impression.
+However, our snap-judgment already set the perspective we are coming from.
+For example, if you see a blue yard sign but you recognize it was for Mitch McConnell, you may be confused once you realize it’s for that Mitch McConnell – the prominent Republican.
+Now, say that you don’t recognize the name: you might then just assume that the candidate must be a Republican.
+After all, for years when you think of Republicans you think of the color red from their logo, from election night maps, *et cetera*.
+
 What this hypothetical example demonstrates is that I have theoretical expectations that Republicans are associated with the color red and that Democrats are associated with the color blue.
-Secondly, and perhaps most important, is the idea that the information that these colors provide puts our mind down a particular path and the way we express our attitudes are shaped by these colors.
-In the first example with the Mitch McConnell yard sign you feel confused about the conflicting information.
+But secondly, and perhaps more importantly, this example communicates the idea that the information that these colors provide puts our mind down a particular path, and that the way we express our attitudes is potentially shaped by these colors.
+In the first example with the Mitch McConnell yard sign, you feel confused in your assessment that it is conflicting information.
 In the situation where you do not recognize the name, the color seems to tell you what you need to know.
@@
 
-For brevity's sake, I'll provide another analogy but examining a different set of political outcomes.
+For brevity’s sake, I’ll provide another example, this time examining a different set of political outcomes.
 Say you are watching the news on your phone while waiting at the gate for your flight.
-You see someone about to sit next to you and they are wearing a red hat -- you don't see at first what logos or writing is on the hat, you just see it is a red hat.
+You see someone about to sit next to you and they are wearing a red hat – you don’t see at first what logos or writing is on the hat, you just see it is a red hat.
 Now, since you are watching the news, the most accessible context where red hats matter is in politics.
-You therefore may assume that they are a supporter of Donald Trump's.
-Your comfort with sitting next to that person or having them start up a converstation will undoubtedly be shaped by whether you are also a Republican.
+You therefore may assume that they are a supporter of Donald Trump.
+Your comfort with sitting next to that person or having them start up a conversation will undoubtedly be shaped by whether you are also a Republican.
 We often are reluctant to have conversations in politics with those that are outpartisans [@carlson_settle_2022_cup].
-Often times though, we cannot control the actions of others and they may start talking to you when they notice that you are watching a CNN segment on the recent *Dobbs* decision which allowed states to pass laws restricting abortion access.
-Say that they tell you, "yeah, the *Dobbs* decision was the right call." In that situation, you feel just the same as you did when the conversation started, perhaps even more strongly but in the same direction.
-What if instead they tell you, "yeah, I might like Trump, but the *Dobbs* decision is allowing state governments to do whatever they want to tell us what we can do with our own bodies.
-And that is wrong." You may instead have this internal reaction of, "What?
-Really?" Instead of making you dig into your initial snap-judgment, you may now be more or less willing have a conversation with this person despite them clearly telling you that they are a Trump supporter.
+Often times though, we cannot control the actions of others -- e.g., someone may start talking to you when they notice that you are watching a CNN segment on the recent *Dobbs* decision.
+Say a person tells you, “yeah, the *Dobbs* decision was the right call.” In that situation, you feel just the same as you did when the conversation started, perhaps even more strongly but in the same direction.
+But what if instead they tell you, “yeah, I might like Trump, but the *Dobbs* decision is allowing state governments to tell us what we can do with our own bodies.
+And that is wrong.” You may instead have this internal reaction of, “What?
+Really?” Instead of making you dig into your initial snap- judgment, you may now be more willing to have a conversation with this person despite
+them clearly telling you that they are a Trump supporter.
 Months after this interaction, however, those feelings that change your impressions of the average Trump supporter may weaken.
 That is to say, that because you run into a pro-choice Trump supporter once it does not continue to drive more moderate views about who Trump supporters are; those effects will weaken over time without other similar instances.
-Say instead of watching CNN, you were watching ESPN -- you may instead assume that they are a Cardinal's fan and this information is much less relevant to shaping your conversations about political matters.
+Another wrinkle in my model is that say instead of watching CNN, you were watching ESPN – you may instead assume that they are a Cardinal’s fan, and this information is much less relevant to shaping your conversations about political matters.
+The same red hat will have differential effects on our initial impression depending on what is most accessible to our heads.
+In this case politics versus baseball.
+This is to say that this model does not predict that color will always matter, but that it matters when politics is a salient concern.
 
-What these two examples highlight, and hopefully in an intuitive way due to the familiarity of these situations, is that this model of snap-judgments formed from visual information provides an intuitive set of predictions about how people should respond to color as a source of information under a number of different circumstances drawing on a number of theories from the affective and social neuroscience and psychological disciplines.
-Further, the model outlines a set of predictions for how this visual information has downstream consequences on the way in which we process more substantive political information such as a candidate's or a discussion partner's policy positions as has been done in studies relying on dominant theories of political information processing.
-The goal of this project is to make a broader argument about the importance of considering visual and other forms of information as political information and how this information shapes the processing of substantive information.
-While the partisan association of the colors red and blue may change (though, I am somewhat skeptical of that occuring given the hyper-polarized environment the United States finds itself in), the model relies on theories about how people cognitively tie visual information to more complex ideas and to social groups.
-Therefore, I expect that the overall argument and the model can plug in different colors, be tweaked for different circumstances, and can still produce useful predictions for political attitude expression and behavior.
-That is, while the focus is on the colors red and blue, the goal of the project is to set the ground work for a theoretical framework of visual inforamtion processing by which scholars can continue to build upon.
+What these two examples highlight, and hopefully in an intuitive way due to the familiarity of these situations, is that this model of snap-judgments formed from visual information provides an intuitive set of predictions about how people should respond to color as a source of information under a number of different circumstances (and drawing on a number of theories from the affective and social neuroscience, and psychological disciplines).
+Further, the model outlines a set of predictions for how this visual information may have downstream consequences for how we process more substantive political information such as a candidate’s or a discussion partner’s policy positions; this mirrors what has been done in studies relying on dominant theories of political information processing.
+The goal of this project is to make a broader argument about the importance of considering visual and other forms of information as political information -- I aim to focus attention on how this information shapes the processing of substantive information.
+While the partisan association of the colors red and blue may change (though, I am somewhat skeptical of that occurring given the hyper-polarized environment of the United States), the model relies on theories about how people cognitively tie visual information to more complex ideas and to social groups.
+Therefore, I expect that the overall argument and the model to be able to work with different colors, be tweaked for different circumstances, and still produce useful predictions for political attitude expression and behavior.
+That is, while the focus at present is on the colors red and blue, the goal of the project is to lay the ground work for a theoretical framework of visual information processing which other scholars can continue to build upon.
 
@@
 
-## Existing data-collection
+## Existing data collection
 
-At this point, I have collected and analyzed the data to the first empirical chapter.
-In this chapter, I used a survey experiment to examine the degree to which the colors red and blue (at different amounts) shape perceptions of the candidate and subjects' reported willingness to vote for these candidates.
-In doing so, I collected data on the cursor movements of participants' screens while blurring most of the yard sign to emulate an eye-tracking experiment.
-In this study, I found that participants assigned to the red and blue yard sign conditions spent less time exploring the yard sign than participants assigned to a white yard sign condition indicating that they did not need to spend as much time exploring the text-based elements of the yard sign to evaluate it.
-It also demonstrated that a fictional candidate with more red on their yard sign were often presumed to be more Republican whereas candidates with moreblue on their yard sign were often presumed to be more Democratic.
-Yard signs that used less red or used a combination of red and blue often produced more ambivalence between subjects.
+At this point, I have collected and analyzed the data for the first empirical chapter.
+In this chapter, I use a survey experiment to examine the degree to which the colors red and blue (in different amounts) shape perceptions of a candidate and subjects’ reported willingness to vote for a candidates In this study, I collected data on the cursor movements of participants’ screens while blurring most of the yard sign to emulate an eye-tracking experiment.
+I found that participants assigned to the red and blue yard sign conditions spent less time exploring the yard sign than participants assigned to a white yard sign condition; this indicates that respondents did not need to spend as much time exploring the text-based elements of the yard sign to evaluate it.
+My findings also indicate that a fictional candidate with more red on their yard sign is presumed to be more Republican, whereas candidates with more blue on their yard sign are presumed to be more Democratic.
+Yard signs that used less red or used a combination of red and blue produced more ambivalence between subjects.
 Finally, the study demonstrated that Republicans who saw a red yard sign were more likely to report supporting that candidate than Republicans who saw a blue or white yard sign.
 Similarly, Republicans who saw blue or white yard signs were not likely to report supporting those candidates.
-Democrats who saw a blue yard sign were much more likely to vote for that candidate than those with red or white yard signs.
+Democrats who saw a blue yard sign were much more likely to vote for that candidate than for candidates with red or white yard signs.
 
-To demonstrate that these perceptions have real-world influences on campaigns' decisions about the colors included on their yard signs, I collected yard sign images from the Center for American Political Design website and used a machine learning library to calculate the proportion of the colors red and blue on their yard signs.
-I then merged these data with data from the MIT Election Lab to examine whether candidates for the House of Representatives that are running within competitive congressional districts were less likely to use the color red and blue than if they were in a district where they'd be motivated to use one partisan color over another.
-The results from this study supported my hypothesis: candidates running in districts where Republicans have historically been more electorally successful used more red than those running in districts where Republicans are less electorally succesful.
+To demonstrate that these perceptions have real-world influences on campaigns’ decisions about the colors included on yard signs, I collected yard sign images from the Center for American Political Design website and used a machine learning library to classify the color for each pixel to calculate the proportion of the colors red and blue on their yard signs.
+I then merged these data with data from the MIT Election Lab to examine whether candidates for the House of Representatives running within competitive congressional districts were less likely to use mixes of the colors red and blue than if they were in a district where they’d be motivated to use one partisan color over another.
+The results from this study supported my hypothesis: candidates running in districts where Republicans have historically been more electorally successful used more red than those running in districts where Republicans have been less electorally successful.
 I find similar effects for the use of the color blue and historically Democratic-leaning districts.
@@
 
-The remainder of the project seeks to build on this existing work to examine how this affiliation between the colors red and blue with Republicans and Democrats in political settings influences deliberation, persuasion, and perceptions of a neighborhood (a whole group of people as opposed to individual political actors).
-The timeline for completing the remainder of these studies would be to have them complete by the end of Spring (May 2024).
+The remainder of the project seeks to build on this existing work to examine how this affiliation between the color and the parties in political settings influences deliberation, persuasion, and perceptions of neighborhoods (a whole group of people as opposed to individual political actors).
+The timeline for completing the remainder of these studies is the end of next Spring (May 2024).
 
-While it would be nice to study these with a combination of observational and experimental research designs, the outcomes of study for these remaining chapters are much less easy to collect observational data on.
-For example, of the handful of common observational studies used in the United States, few ask questions about people's conversations with others in politics.
-Further, none that I am aware of ask people to describe the visual and physical characteristics of the people that they are having conversations with.
-If I were to collect my own survey data on this, I am highly suspicious of people's memory about the color of the clothing that they are wearing despite its importance.
-This is because color is important as a form of information to form a snap-judgment, however, it is a form of subtle information that people may use only initially and forget later.
-Therefore, the use of this grant will be to help with the cost of performing experimental studies for both in-person samples as well as online samples.
+While it would be nice to study all my questions with a combination of observational and experimental research designs, the outcomes in my remaining chapters are less easy to collect observational data on.
+For example, of the handful of common observational studies used in the United States, few ask detailed questions about people’s conversations with others in politics.
+Moreover, no available studies that I am aware of ask people to describe the visual and physical characteristics of the people that they are having conversations with.
+If I were to collect my own survey data on these characteristics, I would be highly suspicious of peoples' memories about the color of the clothing that others were wearing, due to memory decay.
+While color is important as a form of information to form snap-judgments, it is a form of subtle information that people may use only initially and then forget later.
+Because experimental designs are preferred (for the previously mentioned reasons), this grant will greatly improve my ability to complete the project.
 
-I want to perform experimental designs with both in-person and online samples to accomplish a coupld of tasks.
-First, the online samples are designed to capture a more representative sample and to have a larger sample.
-However, the online samples are a bit more limited in terms of the treatments that I can assign subjects to.
-The in-person studies are meant to provide slightly more realistic treatments to my participants as well as making it less clear to participants that they have been introduced to a treatment in the first place.
-For example, in one of my in-person studies, I will have participants meet at a building on the University of Colorado's campus.
-As they are entering the building, there will be a canvasser asking people to sign a petition.
-I will vary whether the color of the shirt that the person is wearing.
-While doing so, the behavior of the participants will be recorded to see whether they stop to talk to the person and whether they sign the petition.
-In the online experiment, instead participants will be shown an image of a person that they have been "matched to have a conversation with." Each of these treatments have advantages and disadvantages, and so do the samples.
-The goal is to perform these with different samples and slightly different designs in hopes of being able to replicate the conclusions I draw from them.
+I am currently in the process of implementing a study to examine this model on the effects of these associations on deliberation in an upcoming module of the Cooperative Election Study.
+For a second study for that chapter, I am considering alternative internal funding sources.
 
-To perform multiple studies to replicate findings is quite costly for a graduate student at a public university.
-The grant would be a significant help to allow me to run these studies for the chapter on deliberation and on environmental cues in both in-person and online settings.
-It would also help me hire an RA to stand-in as the people they are interacting with in the in-person version of the studies as well as a "model" for the images in the online studies.
-Without this grant, I would likely be limited to a one-shot sample for each chapter and will need to do it with an online sample.
-The added ability for replication and to test it with both internally consistent and externally valid treatments would be a significant boost to the remaining chapters' empirical evidence.
-It would also allow me to include more treatment conditions to test how the effects of color on the outcomees are conditioned on whether the colors are presented in a way where politics is primed or for example if they seem irrelevant such as the color for a sports team instead.
-Adding these additional treatment conditions would help with directly testing the scope conditions of the way that color conveys political information.
+For the third chapter, I would like to recruit an online sample to examine how the effects of these associations influence our perceptions of residents in a neighborhood.
+Some research suggests that under experimental and survey conditions that people do care about the partisan composition of a prospective neighborhood to move to.
+These findings build on a growing body of work demonstrating how political polarization is not simply a distinct set of policy preferences, but it shapes many different facets of our lives.
+The conclusions from such data are that people report that they are unwilling to move to neighborhoods where they feel they may be in the partisan minority.
+However, other work has used observational evidence suggesting that these preferences do not appear in actual behavior.
+
+The goal of the study in the third empirical chapter is to use the snap-judgment model to address an open substantive question: Why is it that people report a preference to live in a neighborhood or to avoid one based on inferred partisan composition, but do not do so in practice?
+Using the snap-judgment model, I argue in the third empirical chapter that these sources of information to infer partisan composition are too noisy as information signals in practice and that individuals would rather base decisions on weightier factors that are considered more often such as quality of school, cost, *et cetera*.
+That is, even though politics may be at the top of people's minds (based on the self-reported data) and they may be motivated to infer the partisan composition of a neighborhood, the information they have is not conclusive enough to outweigh information that they are more sure about.
+
+To examine this argument, I will use the color of the cars in a neighborhood as an example of "noisy" information about the partisan composition of a neighborhood.
+There is some existing evidence demonstrating that we can make relatively accurate inferences about the partisanship of an individual an a neighborhood based on the cars parked there.
+This evidence is often limited to examining the make of a car (e.g., sedan versus pick-up truck).
+However, the snap-judgment model suggests that it doesn't even need to be that complex as information.
+Therefore, The study for the chapter, will see whether people will assume that a neighborhood is more Republican if the modal car color is red as opposed to blue or more Democratic if the modal car color is blue based on a real-estate flyer.
+I will vary wither I prime participants to think of politics or not to see whether there are differences between inferred partisan composition depend on the degree to which politics is salient and important to someone when making decisions to move there.
+Finally, I will vary whether participants see a real estate flyer reporting a modal car as being red or blue to see whether it matters in the face of more substantive information such as the ratio of cost to wages, distance from basic goods such as grocery stores, and quality of school.
+While this cannot get me a direct test of behaviors, the experimental design for the chapter directly pits inferred partisan composition up against other factors that are argued to matter more to the public than the politics of the neighborhood.
+
+An APSA grant would be a significant help for me to complete this chapter.
+As I have received support for some of the other chapters, it is quite hard to find resources to fund a sample with sufficient power for the remainder of the dissertation.
+The grant support would help me complete that study and to complete the dissertation as I have many of the other pieces completed (or in progress).
+In addition, with support from this grant this study would be one thatI would not need to re-do as I would be able to include all of the treatment conditions that I need to sufficiently test my argument on a high quality sample.

### 2023-09-19 grants/ddirg/src/roberts_data_management.qmd
data management drafting

---
subtitle: Data Management Plan
format:
  fancy-doc-pdf:
    toc: false
    latex-output-dir: ../out/
    biblatex: true
    filters:
      #- "_extensions/andrewheiss/wordcount/citeproc.lua"
      - "_extensions/andrewheiss/wordcount/wordcount.lua"
author:
  - name: Damon C. Roberts
    affiliations:
      - name: Univeristy of Colorado Boulder
    email: damon.roberts-1@colorado.edu
bibliography: ../../../assets/references.bib
---

# IRB

I am currently in the process of putting together materials for IRB approval for this component of the project. The specifics of the study are somewhat dependent on funding sources for this chapter and so I have not submitted and received approval by IRB for the study in my third empirical chapter (the study I am seeking funding for).

I anticipate that I should be able to have the study approved as I have successfully had approval for the studies in the other chapters (that collected quite similar and in the case of the first empirical chapter data with more privacy concerns given the cursor tracking component which will not be present in this chapter).

# Data to be collected

I am to collect a sample of at least 1,500 participants. The following is the plan for the data that I will collect and what the participants will be exposed to during the study.

Upon providing their informed consent, $\frac{1}{2}$ of the participants are randomly assigned at the start of the study to answer questions about their background and their political attitudes. The other half will be randomly assigned into treatment conditions that I will explain in more detail below.

## Background and political attitude data

Participants will be asked to report their age, gender identity, sex assigned at birth, racial and ethnic identification, level of education, their family income, and whether they have been diagnosed with any of the following visual impairments: any form of color blindness, blurred vision (not treatable by corrective lenses), macular degeneration, glaucoma, cataract, or diabetic retinopothy. The purpose of asking these questions is to use them as moderators and confounds for my primary analyses.

I will also ask them a number of questions about politics. First, they will be asked about how often they pay attention to what is going on in government and politics. They will then be asked about their partisan identification on a 7-point scale. I will also ask them to respond to an open-ended question about their earliest memory of a political event to detect any duplicate or insincere responses.

## Treatments

Participants will be assigned randomly into one of two conditions with an equal probability. They will see one of two versions of a fictional real estate posting. The characteristics of the neighborhood are exactly the same between the two conditions except for the "favorite car color". In the first condition, the "favorite color of car" is red. In the second condition, it is blue. Participants are then given a scale from 0-10 to rate the neighborhood and are presented with a 5-item Likert scale to indicate, "How much would [they] like to live in this neighborhood?"

Once the participants have responded to these questions, they are then given a second page describing the neighborhood with more detail. The information subjects see on this second page is exactly the same. It reports that the neighborhood is, "Easily accessible to nearby shopping and community centers", that the "Average monthly housing costs comprise 25% of a family's average take home pay", and that the "School district is rated as exceptional by the State School board based on test scores."

With this new information, I ask participants, "With this new information, please update your rating of the neighborhood" on the 0-10 scale and are again presented with a 5-item Likert scale to indicate, "How much would [they] like to live in this neighborhood?"

A mockup of the flyers used in these treatments is are included in @fig-mockup.

::: {#fig-mockup}

![Red treatment flyer](../../../chapter_4/assets/irb/red_treatment_mockup.pdf){#fig-red height=300}

![Blue treatment flyer](../../../chapter_4/assets/irb/blue_treatment_mockup.pdf){#fig-blue height=300}

Treatment Mockups
:::

## Data management plan

The data that I will collect in the study are all based on self-reported responses to questions I outline here. To maintain the privacy of the participants, none of them will be compelled to provide any data that they do not wish to share.

As I am committed to open science, I am fully committed to sharing all materials for this project through my Github account. However, I will de-identify the data (remove any information provided by the vendor such as time taken to complete the study, any response or session ID's) before sharing the data publicly for replication purposes. The sample is a national sample, and since most of the descriptive and ascriptive data that I am collecting should be sufficient to maintain the confidentiality of my participants.

All of the materials for this project and studies have been licensed by me with the provisions outlined [here.](http://creativecommons.org/licenses/by/4.0/)

### 2023-09-19 grants/ddirg/src/roberts_data_management.qmd
research ethics draft

@@
 
-A mockup of the flyers used in these treatments is are included in @fig-mockup.
+A mockup of the first page of the flyers used in these treatments is are included in @fig-mockup.
 
@@
 To maintain the privacy of the participants, none of them will be compelled to provide any data that they do not wish to share.
+The platform that I intend to recruit participants on will depend on funding sources, but recruitment and the administration of the study is likely to be done through Prolific.
 

### 2023-09-20 chapter_2/src/slides/slides.qmd

--- 2023-09-18 chapter_2/src/slides/slides 2.qmd
@@
   echo: false
+  freeze: true
+  cache: true
 ---
@@
 
-[![1860s Ballots](../../assets/slides/imgs/ballots.avif){#fig-ballots}](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)
+[![1860s Ballots](../../assets/slides/imgs/ballots.avif){#fig-ballots width=6.5in}](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)
 
@@
 
-[![Democratic National Convention](../../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem height=100}](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)
-
-[![Republican National Convention](../../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep height=100}](https://reuther.wayne.edu/node/9207)
+[![Democratic National Convention](../../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem width=6.5in}](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)
+
+[![Republican National Convention](../../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep width=6.5in}](https://reuther.wayne.edu/node/9207)
 
@@
 
-[![2000 Presidential Election map](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=200}](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)
+[![2000 Presidential Election map](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=6.5in}](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)
 
@@
 
-[![The public](../../assets/slides/imgs/division.webp){#fig-public}](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)
+[![The public](../../assets/slides/imgs/division.webp){#fig-public width=6.5in}](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)
 
@@
 ## De-mystifying some of the jargon I might use
+
+---
 
@@
 
+---
+
 ```{mermaid}
@@
 %%| fig-cap: Memory model of info processing
-%%| fig-width: 6.5
 graph TD;
@@
 ```
-
----
 
@@
 
-![Red condition](../study_1/assets/rep_yard_sign_round_1.png)
-![Blue condition](../study_1/assets/dem_yard_sign_round_1.png)
-![White condition](../study_1/assets/cont_yard_sign_round_1.png)
+![Red condition](../study_1/assets/rep_yard_sign_round_1.png){#fig-red-1 width="6.5in"}
+
+![Blue condition](../study_1/assets/dem_yard_sign_round_1.png){#fig-blue-1 width="6.5in"}
+
+![White condition](../study_1/assets/cont_yard_sign_round_1.png){#fig-white-1 width="6.5in"}
 
@@
 
-![Red condition](../study_1/assets/rep_yard_sign_round_2.png)
-![Blue condition](../study_1/assets/dem_yard_sign_round_2.png)
-![White condition](../study_1/assets/cont_yard_sign_round_2_3.png)
+![Red condition](../study_1/assets/rep_yard_sign_round_2.png){#fig-red-2 width=6.5in}
+
+![Blue condition](../study_1/assets/dem_yard_sign_round_2.png){#fig-blue-2 width=6.5in}
+
+![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){#fig-white-2 width=6.5in}
 
@@
 
-![Red condition](../study_1/assets/rep_yard_sign_round_3.png)
-![Blue condition](../study_1/assets/dem_yard_sign_round_3.png)
-![White condition](../study_1/assets/cont_yard_sign_round_2_3.png)
+![Red condition](../study_1/assets/rep_yard_sign_round_3.png){#fig-red-3 width=6.5in}
+
+![Blue condition](../study_1/assets/dem_yard_sign_round_3.png){#fig-blue-3 width=6.5in}
+
+![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){#fig-white-3 width=6.5in}
 
@@
 
-![Example of treatment](../../assets/slides/imgs/treatment.gif){#fig-treatment-example}
+![Example of treatment](../../assets/slides/imgs/treatment.gif){#fig-treatment-example width=6.5in}
 

### 2023-09-20 grants/ddirg/src/roberts_professional_development.qmd

---
subtitle: Professional development plan
format:
  fancy-doc-pdf:
    toc: false
    latex-output-dir: ../out/
    biblatex: true
    filters:
      #- "_extensions/andrewheiss/wordcount/citeproc.lua"
      - "_extensions/andrewheiss/wordcount/wordcount.lua"
author:
  - name: Damon C. Roberts
    affiliations:
      - name: Univeristy of Colorado Boulder
    email: damon.roberts-1@colorado.edu
bibliography: ../../../assets/references.bib
---

After completing my dissertation, I plan to continue researching visual information in politics as a Post-Doctoral researcher and an Assistant Professor. So far, I have presented parts of this dissertation project at the International Society of Political Psychology's annual conference, and at the Front Range American Political Science Association's annual conference. I intend to present this research in other workshops and outlets in the coming year.

I also have long-term goals for this project to be the start of a career-long effort to study this topic. I plan to publish this dissertation as a book project. While the project, in its current form, focuses on  the colors red and blue, the goal is to turn this into a broader treatment of visual information in politics. To do this, I want to examine other types of related visual information, such as other colors that are less tied to the current political parties (e.g., the use of the colors black and white). That is, I plan to examine the use of these (and other) colors in Black Lives Matter and Blue Lives  Matter organizations, and to further examine symbols in politics/how symbols interact with color. I have discussed alternative projects with Gijs Schumacher at the Hot Politics Lab located at the University of Amsterdam.

In this dissertation I aim to outline a psychological and cognitive framework for exploring simple forms of politically-relevant information. Ideally, I hope to organize/collaborate with a lab of scholars interested in studying the role of visual information in politics. Further, I intend to share this work with several consultants working at political marketing firms who have shared their experiences with me about how candidates make decisions about things like yard signs.

<!--
After my degree, I plan to continue researching visual information in politics as a Post-Doctoral researcher and an Assistant Professor at another institution. So far, I have presented parts of this dissertation project at the International Society of Political Psychology's annual conference and the Front Range American Political Science Association's annual conference. I intend to present this research in other workshops and outlets in the coming year.

I also have long-term goals for this project to be the start of a career-long effort to study this topic. I plan to publish this project as a book project. While the project, in its current form, focuses on the colors red and blue, the goal is to turn this into a broader research agenda. To do this, I want to examine other types of related visual information, such as other colors that are less tied to the current political parties, such as the use of the colors black and white, to examine their use in Black Lives Matter and Blue Lives Matter organizations, to examine symbols in politics and how they interact with color and have discussed alternative projects with Gijs Schumacher at the Hot Politics Lab located at the University of Amsterdam. This dissertation aims to provide an early attempt to outline a psychological and cognitive framework to explore simple forms of politically-relevant political information. Ideally, I can organize a lab of scholars interested in studying the role of visual information in politics. Further, I intend to share this work with several consultants working at political marketing firms who have helped me in the project so far by sharing their experiences about how candidates make decisions with colors on their yard signs.
-->

### 2023-09-20 grants/ddirg/src/roberts_proposal_summary.qmd

@@
 
+The use of the colors red and blue to distinguish the two dominant political parties in the United States started with the electoral maps displayed during the 2000 presidential election [@elving_2014_npr].
+Since then, the two political party's logos have changed rather dramatically in that now the Republican party only uses the color red, and the Democratic party only uses the color blue.
+@fig-party-brand illustrates this point.
+Some existing descriptive research demonstrates these clear distinctions in color are not limited  to party logos, but that Democrats use more blue than Republicans.
+In contrast, Republicans use more red on their campaign's yard signs [@williams_et-al_2022_jomp].^[The first empirical chapter of this dissertation replicates and extends this finding by exploring the rates of color usage among partisans in districts that have more/less electoral competition.] There are two primary questions for this dissertation and book project.
+I address the first question by laying out a theory of the cognitive processes explaining how these associations have crystallized for the mass public.
+I then explore the second question by examining what the consequences are of these affiliations for political attitude expression and behavior, even in the face of more traditional substantive political information (e.g., policy preferences).
+
+::: {#fig-party-brand layout-ncol=2}
+
+![Republicans pre-2000](../../../chapter_2/src/assets/img/rnc_logo_pre-2000.png){#fig-republican}
+
+![Democrats pre-2000](../../../chapter_2/src/assets/img/dnc_logo_1960.png){#fig-democrat}
+
+![Republicans 2023](../../../chapter_2/src/assets/img/rnc_logo_2023.png){#fig-republican-post}
+
+![Democrats 2023](../../../chapter_2/src/assets/img/dnc_logo_2023.png){#fig-democrat-post}
+
+Party logos
+:::
+
+A primary contribution of this project comes in its development of a cognitive model of visual information processing.
+Existing work on the visual aspects of politics is a newer area of work and comes from several different academic disciplines.
+Work to date leaves us with a somewhat fragmented theory of how visual information affects mass attitudes and behavior.
+This project lays out a model that illustrates how visual information, such as color, may be a source of information in politics; visual information is often processed faster than more symbolic information (e.g., substantive political information), so the first-order information explaining an individual's attitude expression may be visual information, such as color.
+The empirical chapters of the project discuss how these things influence our understanding of vote choice and the value of yard signs to campaigns, and how these things inform the degree to which people engage in conversations about politics.
+The project also provides a typology of when persuasion can occur, and it explains how we can make inferences about the partisanship of a group of people based on the way they have curated their environment.
+
+This grant would be a significant help with the costs of data collection.
+While I have performed the data collection for the first of the three primary empirical chapters, the last two incorporate several experiments that require online samples.
+An APSA grant would help me recruit sufficiently powered and representative samples (and adequately pay participants for participation).
+The support offered by such a grant would not only help me complete the dissertation in the short term, but would give me a head start on the book version of the project (by eliminating the need for me to re-do the studies with higher quality samples after defending my dissertation).
+<!--
 The use of the colors red and blue to distinguish the two dominant political parties in the United States started during the 2000 Presidential Election with the electoral maps [@elving_2014_npr].
@@
 Therefore, financial assistance with recruiting sufficiently powered and representative samples, along with adequately paying these participants for participating in these studies, would be a tremendous help for the completion of this dissertation and will remove the need for me to redo a number of these studies when working on the book project after defending the dissertation.
+-->

### 2023-09-20 grants/ddirg/src/roberts_research_ethics.qmd

---
subtitle: Research and Professional Ethics Requirements
format:
  fancy-doc-pdf:
    toc: false
    latex-output-dir: ../out/
    biblatex: true
    filters:
      #- "_extensions/andrewheiss/wordcount/citeproc.lua"
      - "_extensions/andrewheiss/wordcount/wordcount.lua"
author:
  - name: Damon C. Roberts
    affiliations:
      - name: Univeristy of Colorado Boulder
    email: damon.roberts-1@colorado.edu
bibliography: ../../../assets/references.bib
---

# IRB

I am currently in the process of putting together materials for IRB approval for this component of the project. The specifics of the study are somewhat dependent on funding sources for this chapter and so I have not submitted and received approval by IRB for the study in my third empirical chapter (the study I am seeking funding for).

I anticipate that I should be able to have the study approved as I have successfully had approval for the studies in the other chapters (that collected quite similar and in the case of the first empirical chapter data with more privacy concerns given the cursor tracking component which will not be present in this chapter). Once approved by IRB, I am happy to share confirmation.

# Protecting subject privacy and confidentiality

I am deeply committed to respecting the rights of my research participants. I committed to maintaining the privacy and confidentiality of my research participants by not requiring them to answer any question they are uncomfortable answering as well as using a platform that does not collect data that can directly identify participants.

Even though I take these steps to help protect their privacy and confidentiality, I am also deeply aware of the power differentials that are created when participants engage in a study. This puts them in a vulnerable position to perhaps answer questions or to view a treatment that may make them deeply uncomfortable but fearful of the monetary ramifications for not fully participating. As a result, I am careful about my design choices and the questions that I ask participants to ensure that there is minimal risk and potential for harm. I also will assure participants that they do not have to answer every question to receive payment for their time to participate in the study.

I am also sympathetic to needs for adequate compensation of our study participants. As a result, I intend to pay my participants a competitive wage at the rate of $12.00 per hour for the 6 minutes that I anticipate it will take them to complete the study.

# Conflicts of interest

I do not have any conflicts of interest to report.

# Scientific integrity

I am deeply committed to open science and will share all materials publicly so that independent researchers are allowed to and encouraged to replicate my results.

### 2023-09-22 chapter_2/src/prr/si_color_influence_pre-reg_anon.qmd
init gh-pages branch

---
title: |
  Supplementary information to a Pre-analysis plan
subtitle: |
  How do colors convey political information and affect individual attitudes?
#code-repo: |
#  For replication, go to: <https://github.com/DamonCharlesRoberts/dissertation>.
author:
  - name: Anonymized for peer review
  #- name: Damon C. Roberts
  #  email: damon.roberts-1@colorado.edu
  #  orcid: 0000-0002-4360-3675
  #  title: PhD Candidate
  #  affiliations:
  #    - id: CU
  #      name: University of Colorado Boulder
  #      department: Political Science
  #      address: 333 UCB
  #      city: Boulder
  #      region: CO 
  #      postal-code: 80309-0333
abstract: |
  Colors are important to politics as a form of political information. Building upon existing theories of political information processing, attitude formation, and affect in neuroscience, I present a snap-judgement model of political information processing. In this model, colors provide automatic information about a politically-relevant object that may shape subsequent processing of more complex information. The model has important implications for how we consider the role that visual information has on political information processing and attitude formation. The model additionally provides clarity on motivations behind party branding and the ways in which information may activate partisan biases pre-consciously. I test this model using a survey experiment tracking participants' mouse movements to view different parts of yard signs that vary the use of partisan and non-partisan colors. I additionally leverage congressional redistricting to examine changes in color use for political yard signs as a strategic choice for attracting voters by communicating partisanship.
bibliography: "../../../assets/references.bib"
format:
  hikmah-pdf:
    # Spit out in drafts directory
    latex-output-dir: "../../out/prr"
    # Use biblatex-chicago
    biblatex-chicago: true
    biblio-style: authordate
    biblatexoptions: 
      - backend=biber
      - autolang=hyphen
      - isbn=false
      - uniquename=false
code-overflow: wrap
nocite: |
  @quarto
execute:
  echo: false
  warning: false
  message: false
  cache: false
---

# Pre-test

## Stimuli

![Blue](../../data/prr/pre-test/blue_treatment.jpg)

![Red](../../data/prr/pre-test/red_treatment.jpg)

![White](../../data/prr/pre-test/white_treatment.jpg)

{{< pagebreak >}}

## Measures

+-----------------+--------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------+-------------------------------------------------+
| Measure         | Question                                                                                                                                   | Response options                                 | Coded as                                        |
+================:+:==========================================================================================================================================:+:================================================:+:===============================================:+
| PartyId         | -   pid = Generally speaking, do you usually think of yourself as a Republican, a Democrat, an Independent or what?                        | -   1 = Republican                               | -   -3 = Strong democrat                        |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 | -   dem1\[rep1\] (if pid == 2\[1\]) = Would you call yourself a strong Democrat\[Republican\] or a not very strong Democrat\[Republican\]? | -   2 = Democrat                                 |     -   pid == 2 & dem1 == 3                    |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 | -   ind1 (if pid == 3 \| 4) = Do you think of yourself as closer to the Republican or Democratic party?                                    | -   3 = Independent                              | -   -2 = Democrat                               |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            | -   4 = Other                                    |     -   pid == 2 & dem1 == 2                    |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            | -   1 = Strong Democrat\[Republican\]            | -   -1 = Leans Democratic                       |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            | -   2 = Not a very strong Democrat\[Republican\] |     -   pid == 3 & ind1 == 2                    |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            | -   1 = Republican party                         | -   0 = Independent                             |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            | -   2 = Democratic party                         |     -   pid == 3 & ind1 == 3                    |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            | -   3 = Neither party                            | -   1 = Leans Republican                        |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            |                                                  |     -   pid == 3 & ind1 == 1                    |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            |                                                  | -   2 = Republican                              |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            |                                                  |     -   pid == 1 & rep == 2                     |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            |                                                  | -   3 = Strong Republican                       |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            |                                                  |     -   pid == 1 & rep == 1                     |
+-----------------+--------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------+-------------------------------------------------+
| Party           | -   dr_pid = If you had to guess, is the politician who owns this yard sign a Republican, a Democrat or neither?                           | -   1 = Republican                               | -   1 = Democrat                                |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            | -   2 = Democrat                                 | -   2 = Neither - An independent or Third party |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            | -   3 = Neither - An independent or Third party  | -   3 = Republican                              |
+-----------------+--------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------+-------------------------------------------------+
| Vote            | -   dr_info_4 = When you see this yard sign do you want to: Vote for this candidate?                                                       | -   1 = Yes                                      | -   1 = dr_info_4 == No & dr_info_5 == Yes      |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 | -   dr_info_5 = When you see this yard sign do you want to: Avoid this candidate?                                                          | -   2 = No                                       | -   2 = dr_info_4 == Yes & dr_info_5 == No      |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            |                                                  | -   2 = dr_info_4 == No & dr_info_5 == No       |
|                 |                                                                                                                                            |                                                  |                                                 |
|                 |                                                                                                                                            |                                                  | -   3 = dr_info_4 == Yes & dr_info_5 == No      |
+-----------------+--------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------+-------------------------------------------------+

: Pre-test measures

## Results

```{r}
#| label: setup-block

box::use(
    modelsummary=modelsummary[modelsummary],
    tibble=tibble[tribble]
)
```

```{r}
#| label: load models

load(
    file="../../data/models/prr/pre-test/pre-test_party_model.RDS"
  )
load(
    file="../../data/models/prr/pre-test/pre-test_vote_model.RDS"
  )
```

```{r}
#| label: tbl-pre-test-table
#| tbl-cap: Color on Yard Signs shape perceptions and vote intentions of candidate
# Table for models
  #* Set up non-coefficient related information from models 
gm = list(
    list('raw' = 'nobs', 'clean' = 'N', fmt = 0)
)
  #* Store models in list object
table_contents = list(
    'Party' = PartyModel,
    'Candidate evaluation' = VotePreTestModel
)
  #* Add row for sectioning out threshold estimates
rows = tribble(~term, ~`Party`, ~`Candidate evaluation`, 'Intercepts', " ", " ",)
attr(rows, 'position') = c(11)
  #* Generate table
modelsummary(table_contents, statistic = 'conf.int', coef_map = c('b_BlueTreatment' = 'Blue treatment', 'b_RedTreatment' = 'Red treatment', 'b_PartyId' = 'Party ID', 'b_BlueTreatment:PartyId' = 'Blue treatment $\\times$ Party ID', 'b_RedTreatment:PartyId' = 'Red treatment $\\times$ Party ID', 'b_Intercept[1]' = 'Threshold 1', 'b_Intercept[2]' = 'Threshold 2'), gof_map = gm, add_rows = rows, notes = c('95-percent credible intervals in brackets.', 'Median estimate from fitted model with 6 chains and 2000 iterations.', 'Data source: Pre-test experiment.'), escape = FALSE)
```

{{< pagebreak >}}

# Study 1

## Stimuli

![Example of treatment with blur](../../assets/img/example_of_treatment.png)

## Trial 1

![Blue](../study_1/assets/dem_yard_sign_round_1.png)

![Red](../study_1/assets/rep_yard_sign_round_1.png)

![White](../study_1/assets/cont_yard_sign_round_1.png)

{{< pagebreak >}}

### Trial 2

![Blue](../study_1/assets/dem_yard_sign_round_2.png)

![Red](../study_1/assets/rep_yard_sign_round_2.png)

![White](../study_1/assets/cont_yard_sign_round_2_3.png)

{{< pagebreak >}}

### Trial 3

![Blue](../study_1/assets/dem_yard_sign_round_3.png)

![Red](../study_1/assets/rep_yard_sign_round_3.png)

![White](../study_1/assets/cont_yard_sign_round_2_3.png)

{{< pagebreak >}}

## Measures

+---------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------+
| Measure             | Question                                                                                                                                                                                                                                                                                                                                               | Response options                                                | Coded as                                                                                                                 |
+=====================+:======================================================================================================================================================================================================================================================================================================================================================:+:===============================================================:+:========================================================================================================================:+
| age                 | Confirm your age                                                                                                                                                                                                                                                                                                                                       | Any integer                                                     | Any integer                                                                                                              |
+---------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------+
| gender              | gender_id = What is your gender identity?                                                                                                                                                                                                                                                                                                              | 1 = Non-binary                                                  | 1 = Male                                                                                                                 |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 2 = Transgender                                                 | 2 = Non-binary, prefer not to choose,other                                                                               |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 3 = Female                                                      | 3 = Female                                                                                                               |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 4 = Male                                                        |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 5 = Prefer not to choose                                        |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 6 = Other                                                       |                                                                                                                          |
+---------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------+
| Sex                 | sex = What is your sex assigned at birth?                                                                                                                                                                                                                                                                                                              | 1 = Female                                                      | 0 = Female/Other                                                                                                         |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 2 = Male                                                        | 1 = Male                                                                                                                 |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 3 = Other                                                       |                                                                                                                          |
+---------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------+
| White               | race_id = Which ethnic or racial category best describes you?                                                                                                                                                                                                                                                                                          | 1 = White, non-Hispanic                                         | 0 = Black, non-Hispanic \| Hispanic \| Asian or Native Hawaiian/other Pacific Islander \| Multiple Races                 |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 2 = Black, non-Hispanic                                         | 1 = White, non-Hispanic                                                                                                  |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 3 = Hispanic                                                    |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 4 = Asian or Native Hawaiian/other Pacific Islander             |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 5 = Native American/Alaska Native or other race                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 6 = Multiple races                                              |                                                                                                                          |
+---------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------+
| ColorBlind          | -   color_blind = Have you been diagnosed with any of the following visual impairments?                                                                                                                                                                                                                                                                | 1 = Blurred vision                                              | 0 = None of the above                                                                                                    |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 2 = Macular degeneration                                        | 1 = Blurred vision \| Macular degeneration \| Glaucoma \| Cataract \| Diabetic retinopathy \| Color blindness (any form) |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 3 = Glaucoma                                                    |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 4 = Cataract                                                    |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 5 = Diabetic retinopathy                                        |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 6 = Color blindness (any form)                                  |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 7 = None of the above                                           |                                                                                                                          |
+---------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------+
| AttentionFlipped    | -   attention = How often do you pay attention to what is going on in government and politics                                                                                                                                                                                                                                                          | 1 = Always                                                      | 1 = Never                                                                                                                |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 2 = Most of the time                                            | 2 = Some of the time                                                                                                     |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 3 = About half the time                                         | 3 = About half the time                                                                                                  |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 4 = Some of the time                                            | 4 = Most of the time                                                                                                     |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | 5 = Never                                                       | 5 = Always                                                                                                               |
+---------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------+
| Knowledge           | -   know_promise =                                                                                                                                                                                                                                                                                                                                     | -   1 = I promise to try my best without looking up any answers | For each question:                                                                                                       |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |     We are interested in the guesses people make when they do not know the answer to a question. We will ask you several questions. Some may be easy, but some are meant to be so difficult that you will have to guess.\</p\>\<p\> In fact, for some of these questions, if you answer correctly, we will know that you probably looked up the answer | -   2 = I do not want to make the promise                       | 0 = Incorrect                                                                                                            |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |     Please do not look up the answers you do not know. Instead, please just make your best guess.                                                                                                                                                                                                                                                      | -   Any integer                                                 | 1 = Correct                                                                                                              |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |     Will you please promise to try your best without looking up any answers? Or do you not want to make that promise?                                                                                                                                                                                                                                  | -   1 = Foreign aid                                             | Average of correct responses                                                                                             |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     | -   know_senate = For how many years is a United States Senator elected \-- that is, how many years are there in one full term of office for a U.S. Senator?                                                                                                                                                                                           | -   2 = Medicare                                                |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     | -   know_spend = On which of the following does the U.S. federal government currently spend the least?                                                                                                                                                                                                                                                 | -   3 = National defense                                        |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     | -   know_house = Do you happen to know which party currently has the most members in the U.S. House of representatives in Washington?                                                                                                                                                                                                                  | -   4 = Social security                                         |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     | -   know_catch = In what year did the Supreme Court of the united states decide Geer v. Connecticut?                                                                                                                                                                                                                                                   | -   1 = Democrats                                               |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | -   2 = Republicans                                             |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | -   Any integer                                                 |                                                                                                                          |
+---------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------+
| PartyId             | -   pid_3 = Generally speaking, do you usually think of yourself as a Republican, a Democrat, an Independent or what?                                                                                                                                                                                                                                  | -   1 = Republican                                              | -   -3 = Strong democrat                                                                                                 |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     | -   pid_d\_str\[pid_r\_str\] (if pid == 2\[1\]) = Would you call yourself a strong Democrat\[Republican\] or a not very strong Democrat\[Republican\]?                                                                                                                                                                                                 | -   2 = Democrat                                                |     -   pid == 2 & dem1 == 3                                                                                             |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     | -   ind_lean (if pid == 3 \| 4) = Do you think of yourself as closer to the Republican or Democratic party?                                                                                                                                                                                                                                            | -   3 = Independent                                             | -   -2 = Democrat                                                                                                        |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | -   4 = Other                                                   |     -   pid == 2 & dem1 == 2                                                                                             |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | -   1 = Strong Democrat\[Republican\]                           | -   -1 = Leans Democratic                                                                                                |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | -   2 = Not a very strong Democrat\[Republican\]                |     -   pid == 3 & ind1 == 2                                                                                             |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | -   1 = Republican party                                        | -   0 = Independent                                                                                                      |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | -   2 = Democratic party                                        |     -   pid == 3 & ind1 == 3                                                                                             |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | -   3 = Neither party                                           | -   1 = Leans Republican                                                                                                 |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |     -   pid == 3 & ind1 == 1                                                                                             |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 | -   2 = Republican                                                                                                       |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |     -   pid == 1 & rep == 2                                                                                              |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 | -   3 = Strong Republican                                                                                                |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |     -   pid == 1 & rep == 1                                                                                              |
+---------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------+
| Party               | After viewing each image in each trial:                                                                                                                                                                                                                                                                                                                | -   1 = Republican                                              | 1 = Democrat                                                                                                             |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     | Is this candidate a Republican, a Democrat, or Neither?                                                                                                                                                                                                                                                                                                | -   2 = Democrat                                                | 2 = neither                                                                                                              |
|                     |                                                                                                                                                                                                                                                                                                                                                        |                                                                 |                                                                                                                          |
|                     |                                                                                                                                                                                                                                                                                                                                                        | -   3 = Neither                                                 | 3 = Republican                                                                                                           |
+---------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------+

: Study 1 Measures

{{< pagebreak >}}

## Results

{{< pagebreak >}}

### 2023-09-22 chapter_2/src/slides/slides.qmd
init gh-pages branch

@@
   revealjs:
+    multiplex: true
     embed-resources: true

### 2023-09-22 grants/ddirg/src/roberts_other_sources_of_support.qmd
init gh-pages branch

---
subtitle: Other Sources of Support
format:
  fancy-doc-pdf:
    toc: false
    latex-output-dir: ../out/
    biblatex: true
    filters:
      #- "_extensions/andrewheiss/wordcount/citeproc.lua"
      - "_extensions/andrewheiss/wordcount/wordcount.lua"
author:
  - name: Damon C. Roberts
    affiliations:
      - name: Univeristy of Colorado Boulder
    email: damon.roberts-1@colorado.edu
bibliography: ../../../assets/references.bib
---

The first empirical chapter of this project has received a grant amounting to $2,054 to conduct the online experiment used in that component. This funding came from the Department of Political Science at the University of Colorado Boulder -- specifically, the Large Research Grant Fund.

### 2023-09-22 chapter_2/src/PY/helper.py

@@ -1,0 +1,103 @@
+"""
+Title: Functions for dissertation
+
+Notes:
+    - Description: Script containing all the functions used in dissertation
+    - Updated: 2023-03-10
+    - Updated by: dcr
+
+Importing dependencies
+"""
+import numpy as np # for array management
+import cv2 # for image detection
+
+
+# Study 2
+#* Dealing with names
+def names(col):
+    """
+    names
+
+    Description
+    ----
+    Function to extract last names of candidate
+
+    Parameters
+    ----
+    df(pd.DataFrame)
+
+    Depends on
+    ----
+    - pandas
+    - re
+    """
+    Name = col.str.replace(r"Jr\.|Sr\.|Jr|Sr|JR|SR|III|\sIV|\sVI", "")
+    Stripped = Name.str.rstrip()
+    lastName = Stripped.str.split(" ").list.get(-1)
+    return lastName
+
+#* image pre-processing
+def preProcess(img,inter,size=[224,224]):
+    """
+    preProcess
+
+    Description
+    ----
+    Function to do the resizing of the images
+    
+    Parameters
+    ----
+    - img: source image
+    - inter: interpolate pixels
+    - size(tuple): size of resized image
+
+    Depends on
+    ----
+    cv2
+    """
+    resized = cv2.resize(img,size,inter)
+    return resized
+    
+#** Color detection
+def colorDetector(img,color_upper=[255,255,255],color_lower=[255,255,255]):
+    """
+    colorDetector
+
+    Description
+    ----
+    Function that preprocesses the image and calculates the percentage of a particular color in it.
+    
+    Parameters
+    ----
+    img:Original img
+    color_upper(tuple): RBG upper value. Default to white
+    color_lower(tuple): RGB lower value. Default to white
+    
+    Depends on
+    ----
+    - helper.preProcess
+    - cv2
+    """
+    # create boundaries 
+    boundaries = [(
+        [color_lower[2], color_lower[1], color_lower[0]],
+        [color_upper[2], color_upper[1], color_upper[0]])]
+    # Transform image
+    img_transformed = preProcess(img=img,inter=cv2.INTER_AREA)
+    # calculate scale
+    #scale = ((img_transformed.shape[0]/img.shape[0]) + (img_transformed.shape[1]/img.shape[1]))/2
+    for (lower, upper) in boundaries:
+    # adjust color_upper and color_lower to specific type
+        lower = np.array(lower, dtype = np.uint8)
+        upper = np.array(upper, dtype = np.uint8)
[…]

### 2023-09-22 chapter_2/src/R/clean_data.R

@@ -1,0 +1,450 @@
+#' @title stimuli extractor
+#' 
+#' @description
+#' This is a function that extracts information about what stimuli was used
+#' for the mouseview trials.
+#' 
+#' @details
+#' This function takes a data.table object from the raw csv loading.
+#' It takes the tasks column, takes the stimulus column,
+#' and parses out the information to then return a named list of strings
+#' with the information about whether the treatment was Red, Blue, or White
+#' and which trial that was.
+#' 
+#' @param data_frame A data.table object containing data from the raw csv
+#' 
+#' @return list_str A named list of which trial and which stimulus was used.
+#' 
+#' @examples
+#' 
+stimuli_extractor <- function(data_frame = df_stimuli) {
+  # Make a list of trials recorded (not all trials for folks who skipped)
+    #* Initial list
+  list_trials <- data_frame[["task"]] |> # find the task column
+    as.list() # and record the trials as a list
+    #* Take the list of trials and put it in the format of trial_#_stimulus
+  list_trials <- base::lapply(
+    list_trials
+    , FUN = function(x) {
+      shortened <- gsub(" ", "_", x)
+      specific <- paste(shortened, "_stimulus", sep = "")
+    }
+  )
+  # Take the data frame, find the stimulus column and record whether it was
+  # red, white, or blue
+  list_str <- base::apply(
+    data_frame
+    , 1
+    , function(x) {
+      # Grab the cell for the correct trial
+      str <- x["stimulus"]
+      # Then change the character to Red, White, or Blue 
+      # depending on stimuli filename
+      if (base::grepl("rep", str) == TRUE) {
+        str <- "Red"
+      } else if (base::grepl("cont", str) == TRUE) {
+        str <- "White"
+      } else if (base::grepl("dem", str) == TRUE) {
+        str <- "Blue"
+      } else {
+        str <- "NULL"
+      }
+      # Return updated str
+      return(str)
+    }
+  ) |>
+  base::as.list() # covert this to a list
+  # Add names to the list based off of the trial
+  base::names(list_str) <- list_trials
+  # Return list
+  return(list_str)
+}
+
+#' @title mouseview data handler
+#' 
+#' @description
+#' This is a function that takes the data reported from mouseview
+#' converts it to a vector, takes the absolute difference between
+#' positions on that vector, and then calculates the average
+#' movement for that vector.
+#' 
+#' @details
+#' The mouseview data comes in as an array but stored as character
[…]

### 2023-09-22 chapter_2/src/R/predicted_prob_bar.R

@@ -1,0 +1,257 @@
+#' @title make barplots for predicted probabilities from ordered logit
+#'
+#' @description
+#' This is a function that makes ggplot2 barplots by taking a fitted
+#' ordered logit model, calculating the predicted probabilities,
+#' and then plotting it with barplots and including error bars.
+#'
+#' @details
+#' This function takes a brmsfit object. It uses the marginalefffects
+#' package to calculate the predicted probabilities.
+#'
+#' @param
+#'
+#' @return plot A ggplot2 object.
+#'
+#' @example
+#'
+predicted_prob_bar <- function( # nolint: object_usage_linter.
+  fitted_model
+  , x_axis
+  , treatment = "Red"
+  , hypothesis = "H2"
+  , level = 0.90
+  , x_label = "Color of yard sign"
+  , y_label = "Pr(Party of candidate)"
+  , legend_title = "Party of candidate"
+) {
+  # If this is for a ordered logit, I'll have to do some stacked
+  if (hypothesis == "H2") {
+    #* Calculate the predicted probabilities for the model
+    df_pred_prob <- marginaleffects::predictions(
+      model = fitted_model
+      , conf_level = level
+    )|>
+    data.table::as.data.table() # convert it to a data.table
+    #* Need to clean up the pred prob data.frame some
+    df_pred_prob_cleaned <- df_pred_prob[
+      #** aggregate the estimate, conf.low, and conf.high columns with
+      #** a mean to calculate the average conditional predicted probabilities
+      , .( # nolint: object_usage_linter.
+        estimate = mean(estimate) # nolint: object_usage_linter.
+        , conf.low = mean(conf.low) # nolint: object_usage_linter.
+        , conf.high = mean(conf.high) # nolint: object_usage_linter.
+      )
+      #** this needs to be done by the group column and the
+      #** independent variable
+      , by = c(
+        "group"
+        , x_axis
+      )
+    ][
+      #** convert the x-axis to a factor
+      , x_axis_temp := factor(get(x_axis)) # nolint: object_usage_linter.
+    ][
+      #** convert the group column to a factor
+      , group := factor(group) # nolint: object_usage_linter.
+    ]
+    # Make plot
+      #* take the cleaned pred_prob dataframe
+    plot <- ggplot2::ggplot(
+      data = df_pred_prob_cleaned
+    ) +
+      #* make a barplot
+      ggplot2::geom_bar(
+        ggplot2::aes(
+          #** put the IV on the x-axis, estimate on y
+          #** and change the fill color based on group
[…]

### 2023-09-22 chapter_2/src/eda/study_1/cleaning.R

@@ -1,0 +1,203 @@
+# Title: cleaning script for pavlovia data
+
+# Notes
+  #* Description
+    #**This is a cleaning script for the pavlovia data.
+    #** It takes the csv files, extracts some data from them,
+    #** merges in the prolific demographic data, then removes
+    #** duplicated rows based on session_id, then converts
+    #** columns to correct data types.
+  #* Updated:
+    #** 2023-08-07
+    #** dcr
+
+# Setup
+  #* Load useful functions
+box::use(
+  data.table[...]
+  , ./R/clean_data[clean_data]
+)
+# Cleaning
+  #* Do basic cleaning to return a minimally usable data.frame
+list_df <- list() # create an empty list for my data_frames
+list_df[["original"]] <- clean_data(
+  folder = "../data/original/study_1/data"
+  , prolific_data = "../data/clean/prolific_demographic_data.csv"
+)
+  #* Create measures
+list_df[["cleaned"]] <- list_df[["original"]][
+    #** Generate 7-item pid measure
+    #** Coded as -3 = Strong Democrat, 3 = Strong republican
+  , pid_7 := fcase(
+    pid_3 == "Democrat" & pid_d_str == "Strong", -3
+    , pid_3 == "Democrat" & pid_d_str == "Not very strong", -2
+    , pid_3 == "Democrat" & is.na(pid_d_str), -1
+    , pid_3 == "Independent" & ind_lean == "Closer to Democratic", -1
+    , pid_3 == "Other" & ind_lean == "Closer to Democratic", -1
+    , pid_3 == "Independent" | pid_3 == "Other" & ind_lean == "Neither", 0
+    , pid_3 == "Other" & ind_lean == "Closer to Republican party", 1
+    , pid_3 == "Independent" & ind_lean == "Closer to Republican party", 1
+    , pid_3 == "Republican" & is.na(pid_r_str), 1
+    , pid_3 == "Republican" & pid_r_str == "Not very strong", 2
+    , pid_3 == "Republican" & pid_r_str == "Strong", 3
+  )
+]
+#* Recoding/adding factors
+list_df[["cleaned"]] <- list_df[["cleaned"]][
+  #** convert age to numeric
+  , age := as.numeric(age)
+][
+  #** convert attention to numeric
+  , attention := fcase(
+    attention == "Never", 0
[…]

### 2023-09-22 chapter_2/src/study_2/01_capd_text_scraping.py

@@ -1,0 +1,84 @@
+# Title: CAPD Text scraping 
+
+# Notes:
+    #* Description: Jupyter Notebook to scrape CAPD site for yard signs in 2018-2022 national elections
+    #* Updated: 2023-06-20
+    #* Updated by: dcr 
+
+# Load Modules
+import time # library to help with sleep and wait times
+from selenium import webdriver # to setup the driver
+from selenium.webdriver.chrome.options import Options # to specify options for my chrome webdriver
+from selenium.webdriver.chrome.service import Service as ChromeService
+from webdriver_manager.chrome import ChromeDriverManager # use the driver manager so that I don't have to download it and keep track of versions myself
+from selenium.webdriver.support.ui import WebDriverWait # use this so that I can wait on my driver to load the page completely before searching
+from selenium.webdriver.common.by import By # using the By function to help with the xpath searching
+from selenium.webdriver.support import expected_conditions as EC # load the expected_conditions function to make sure all elements matching the xpath happen before the driver stops waiting on the loading
+import polars as pl # need the pandas package for dataFrames
+#import duckdb # need to store data into database
+
+# Scraping of CAPD site
+
+## Driver and scraping
+options = Options() # set webdriver options
+options.add_argument("start-maximized") # set an option for the webdriver to automatically open chrome browser that I can interact with the page
+
+driver = webdriver.Chrome() # setup chrome webdriver
+
+wait = WebDriverWait(driver, 100000) # specify wait time for the page before stopping it from collecting links in xpath
+
+url = "https://www.politicsanddesign.com/"
+
+driver.get(url) # Make sure to turn off year filter on page that pops up and scroll all the way down
+
+wait.until(EC.presence_of_all_elements_located((By.XPATH, "//div[@class='candidate-card-text']/ul"))) # tell driver to search along this path, but to not stop the search until it everything has been collected
+time.sleep(10) # add an some extra time incase needed 
+txt_url = driver.find_elements(By.XPATH, "//div[@class='candidate-card-text']/ul") # go ahead and collect all the elements
+txt_url2 = [] # make empty list object to store urls in
+for i in txt_url:
+    txt_url2.append(i.text) # grab the text for each of the sessions
+
+driver.close() # close the driver
+
+# Data wrangling
+txt_url4 = [i for i in txt_url2 if i] # take the elements of txt_url2 and place them in a list
+
+yard_signs = pl.DataFrame({
[…]

### 2023-09-22 chapter_2/src/study_2/02_capd_img_scraping.py

@@ -1,0 +1,65 @@
+# Title: CAPD Image Scraping
+
+# Notes:
+    #* Description: Jupyter Notebook to scrape CAPD site for yard signs in 2018-2022 national elections
+    #* Updated: 2022-11-28
+    #* Updated by: dcr 
+    #* Other notes:
+        #** First run 01_capd_text_scraping.py. This should be executed interactively.
+
+# Load Modules
+import time # library to help with sleep and wait times
+from selenium import webdriver # to setup the driver
+from selenium.webdriver.chrome.options import Options # to specify options for my chrome webdriver
+from selenium.webdriver.chrome.service import Service as ChromeService
+from webdriver_manager.chrome import ChromeDriverManager # use the driver manager so that I don't have to download it and keep track of versions myself
+from selenium.webdriver.support.ui import WebDriverWait # use this so that I can wait on my driver to load the page completely before searching
+from selenium.webdriver.common.by import By # using the By function to help with the xpath searching
+from selenium.webdriver.support import expected_conditions as EC # load the expected_conditions function to make sure all elements matching the xpath happen before the driver stops waiting on the loading
+import polars as pl # need the pandas package for dataFrames
+#import duckdb # need to store data into database
+
+# Scraping of CAPD Site
+
+## Driver and Scraping
+
+options = Options() # set options for driver
+options.add_argument("start-maximized") # specify the option to open chrome browser when sent to driver
+
+driver = webdriver.Chrome() # create ChromeDriver
+
+wait = WebDriverWait(driver, 10000) # set wait time for driver when searching XPATH
+
+url = "https://www.politicsanddesign.com/" # site of url to go to
+
+driver.get(url) # go to url
+
+wait.until(EC.presence_of_all_elements_located((By.XPATH, "//picture[@class='responsive-image-wrapper']/img"))) # search xpath on url. Need to first remove 2020 filter and scroll all the way to the bottom
+time.sleep(10) # set sleep timer just in case driver needs more time
+img_url = driver.find_elements(By.XPATH, "//picture[@class='responsive-image-wrapper']/img") # search xpath on url
+
+img_url2 = [] # create empty list
+for element in img_url:
[…]

### 2023-09-22 chapter_2/src/study_2/03_capd_downloading_images.py

@@ -1,0 +1,34 @@
+# Title: CAPD Image Downloading
+
+# Notes:
+    #* Description: Script to open links to images and downloading them from CAPD site
+    #* Updated: 2022-11-28
+    #* Updated by: dcr
+    #* Other notes:
+        #** Should execute at end of 02_capd_img_scraping.py
+
+
+# Importing modules 
+    #* From environment
+#import duckdb # for database management
+import polars as pl # for dataFrame management
+import urllib.request # to access site
+import sys # to deal with paths
+
+    #* User-defined
+from chapter_2.src.PY.helper import names
+
+# Loading database
+
+df = pl.read_csv(
+    source = "./chapter_2/data/temp/study_2/02_output.csv"
+)
+
+links_df = df.with_columns(
+    names(pl.col("candidate_name")).alias("last_name")
+).to_pandas()
+
+# Downloading the images
+
+for index, row in links_df.iterrows():
+    urllib.request.urlretrieve(row["Img_URL"], "./chapter_2/data/original/study_2/capd_yard_signs/" + row["last_name"] + "_" + str(row["year"]) + ".png")

### 2023-09-22 chapter_2/src/study_2/04_color_detection.py

@@ -1,0 +1,103 @@
+# Title: CAPD detecting colors
+
+# Notes: 
+    #* Description: Script to detect the colors on the yard signs
+    #* Updated: 2022-11-28
+    #* Updated by: dcr
+
+# Load modules
+    #* From visual_env 
+#import duckdb # to access the database
+import numpy as np # to wrangle arrays
+import polars as pl # to wrangle dataFrames
+import re # to wrangle strings
+import cv2 # to do color detection
+import os # to wrangle local files
+    #* User defined
+from chapter_2.src.PY.helper import names, colorDetector
+
+# Define colors to detect
+    #* White
+        #** Not defined. Default for colorDetector()
+    #* Red
+republican_red = [232, 27, 35] # target color
+red_lower = [93, 9, 12] # lower end of spectrum for red
+red_higher = [237, 69, 75] # higher end of spectrum for red
+    #* Blue
+democrat_blue = [0, 174, 243] # target color
+blue_lower = [0, 18, 26] # lower end of spectrum for blue
+blue_higher = [102, 212, 255] # higher end of spectrum for blue
+
+# Detect colors
+    #* Create an empty dataframe to store them in
+df = pl.DataFrame({
+                    "last_name": ["Test"],
+                    "year": ["2023"],
+                    "white_percent": [1.2],
+                    "blue_percent": [1.2],
+                    "red_percent": [1.2]
+})
+
+for filename in os.listdir("./chapter_2/data/original/study_2/capd_yard_signs"):
+    #* check to make sure the file is a png file
+    if filename.endswith('.png'):
+    #* join the directory to the file name
+            f = os.path.join("./chapter_2/data/original/study_2/capd_yard_signs", filename)
+            print("read file")
+    #* split the file name and store the information
+            lastName, year, file = re.split(r'[_.]', filename)
+            print("split file name")
+    #* open the image's file
+            #pil = Image.open(f).convert('RGB')
+            #pilCv = np.array(pil)
+            #img = pilCv[:,:,::-1].copy()
+            img = cv2.imdecode(np.fromfile(f, dtype=np.uint8), cv2.IMREAD_COLOR)
+            print("load file")
+    #* calculate the percent of the image that is white
+            whitePercent, _, _ = colorDetector(img = img, color_lower = [255,255,255], color_upper = [255,255,255])
+            print("calculated whitePercent")
+    #* calculate the percent of the image that is blue
+            bluePercent, _, _ = colorDetector(img = img, color_upper = blue_higher, color_lower = blue_lower)
[…]

### 2023-09-22 chapter_2/src/study_2/05_mit_election_lab_merge.py

@@ -1,0 +1,130 @@
+# Title: Merging MIT Election Lab Data to Yard Signs dataset
+
+# Notes:
+    #* Description: Script to merge MIT Election Lab US House 1976-2020 Election Returns dataset to Yard signs table
+    #* Updated: 2022-11-28
+    #* Updated by: dcr
+    #* Other notes:
+        #** To access dataset go to:
+        #** https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/IG0UN2
+
+# Load modules
+    #* from env
+#import duckdb # for database access
+import polars as pl # for DataFrame management
+import numpy as np # for array management
+    #* User-defined
+from chapter_2.src.PY.helper import names
+
+# Check out the election lab data
+election_lab = pl.read_csv(
+    #* lazy load the csv file
+    "./chapter_2/data/original/study_2/1976-2020-house.csv",
+    null_values=""
+    ).select([
+    #* select the following columns
+        "year",
+        "state",
+        "district",
+        "candidate",
+        "party",
+        "candidatevotes",
+        "totalvotes"
+    ]).with_columns([
+    #* convert state column to lowercase
+        pl.col("state").str.to_lowercase().alias("state"),
+    #* create candidate_Name column
+        #pl.col("candidate").str.to_lowercase().alias("Candidate_Name")
+    ]).with_columns(
+        pl.concat_str(["state", "district"], separator = "-").alias("state_district")
+    ).with_columns(
+        pl.when(pl.col("state_district") == "alaska-0")
+        .then("alaska-1")
+        .otherwise(pl.col("state_district")).alias("state_district")
+    ).with_columns(
+        pl.when(pl.col("state_district") == "vermont-0")
+       .then("vermont-1")
+       .otherwise(pl.col("state_district")).alias("state_district") 
+    ).with_columns(
+        pl.when(pl.col("state_district") == "montana-0")
+        .then("montana-1")
+        .otherwise(pl.col("state_district")).alias("state_district")
+    ).with_columns(
+        pl.when(pl.col("state_district") == "wyoming-0")
+        .then("wyoming-1")
+        .otherwise(pl.col("state_district")).alias("state_district")
+    ).with_columns(
+        pl.when(pl.col("state_district") == "south dakota-0")
+        .then("south dakota-1")
[…]

### 2023-09-22 chapter_3/src/prr/R/plot.R

@@ -1,0 +1,52 @@
+'.__module__.' #nolint
+#' @title plot true positive rate
+#'
+#' @description
+#' This is a function that takes the calculated true positive rate
+#' from `true_positive()` for each sample size and plots it
+#' with a histogram.
+#'
+#' @param data_frame A data.table object returned from `true_positive()`.
+#' @param var Which variable to calculate the true positive rate for.
+#' @param new_names A list of names to put on the x-axis
+#'
+#' @returns plot A ggplot2 object.
+#'
+#' @examples
+#'
+true_positive_plot <- function(
+  data_frame
+  , var = "Parameter"
+) {
+  # split the datatable by variable
+  list_true_positive <- base::split(
+    data_frame
+    , f = data_frame[[var]]
+  )
+  # Plot each list element
+  list_plots <- base::lapply(
+    list_true_positive
+    , function(x) {
+      plot <- ggplot2::ggplot(
+        data = x
+      ) +
+      ggplot2::geom_bar(
+        ggplot2::aes(
+          y = true_positive
+          , x = factor(sample_size)
+        )
+        , stat = "summary"
+        , fun = "mean"
+      ) +
+      ggplot2::labs(
+        x = "Sample size"
+        , y = "True positive rate"
+      ) +
+      ggplot2::theme_minimal()
+      # return plot
+      return(plot)
+    }
+  )
+  # return list of plots
+  return(list_plots)
+}

### 2023-09-22 chapter_2/src/.vdoc.py
Built site for gh-pages

@@ -1,572 +1,0 @@
-# type: ignore
-# flake8: noqa
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
[…]

### 2023-09-22 chapter_2/src/PY/helper.py

@@ -1,103 +1,0 @@
-"""
-Title: Functions for dissertation
-
-Notes:
-    - Description: Script containing all the functions used in dissertation
-    - Updated: 2023-03-10
-    - Updated by: dcr
-
-Importing dependencies
-"""
-import numpy as np # for array management
-import cv2 # for image detection
-
-
-# Study 2
-#* Dealing with names
-def names(col):
-    """
-    names
-
-    Description
-    ----
-    Function to extract last names of candidate
-
-    Parameters
-    ----
-    df(pd.DataFrame)
-
-    Depends on
-    ----
-    - pandas
-    - re
-    """
-    Name = col.str.replace(r"Jr\.|Sr\.|Jr|Sr|JR|SR|III|\sIV|\sVI", "")
-    Stripped = Name.str.rstrip()
-    lastName = Stripped.str.split(" ").list.get(-1)
-    return lastName
-
-#* image pre-processing
-def preProcess(img,inter,size=[224,224]):
-    """
-    preProcess
-
-    Description
-    ----
-    Function to do the resizing of the images
-    
-    Parameters
-    ----
-    - img: source image
-    - inter: interpolate pixels
-    - size(tuple): size of resized image
-
-    Depends on
-    ----
-    cv2
-    """
-    resized = cv2.resize(img,size,inter)
-    return resized
-    
-#** Color detection
-def colorDetector(img,color_upper=[255,255,255],color_lower=[255,255,255]):
-    """
-    colorDetector
-
-    Description
-    ----
-    Function that preprocesses the image and calculates the percentage of a particular color in it.
-    
-    Parameters
-    ----
-    img:Original img
-    color_upper(tuple): RBG upper value. Default to white
-    color_lower(tuple): RGB lower value. Default to white
-    
-    Depends on
-    ----
-    - helper.preProcess
-    - cv2
-    """
-    # create boundaries 
-    boundaries = [(
-        [color_lower[2], color_lower[1], color_lower[0]],
-        [color_upper[2], color_upper[1], color_upper[0]])]
-    # Transform image
-    img_transformed = preProcess(img=img,inter=cv2.INTER_AREA)
-    # calculate scale
-    #scale = ((img_transformed.shape[0]/img.shape[0]) + (img_transformed.shape[1]/img.shape[1]))/2
-    for (lower, upper) in boundaries:
-    # adjust color_upper and color_lower to specific type
-        lower = np.array(lower, dtype = np.uint8)
-        upper = np.array(upper, dtype = np.uint8)
[…]

### 2023-09-22 chapter_2/src/R/clean_data.R

@@ -1,450 +1,0 @@
-#' @title stimuli extractor
-#' 
-#' @description
-#' This is a function that extracts information about what stimuli was used
-#' for the mouseview trials.
-#' 
-#' @details
-#' This function takes a data.table object from the raw csv loading.
-#' It takes the tasks column, takes the stimulus column,
-#' and parses out the information to then return a named list of strings
-#' with the information about whether the treatment was Red, Blue, or White
-#' and which trial that was.
-#' 
-#' @param data_frame A data.table object containing data from the raw csv
-#' 
-#' @return list_str A named list of which trial and which stimulus was used.
-#' 
-#' @examples
-#' 
-stimuli_extractor <- function(data_frame = df_stimuli) {
-  # Make a list of trials recorded (not all trials for folks who skipped)
-    #* Initial list
-  list_trials <- data_frame[["task"]] |> # find the task column
-    as.list() # and record the trials as a list
-    #* Take the list of trials and put it in the format of trial_#_stimulus
-  list_trials <- base::lapply(
-    list_trials
-    , FUN = function(x) {
-      shortened <- gsub(" ", "_", x)
-      specific <- paste(shortened, "_stimulus", sep = "")
-    }
-  )
-  # Take the data frame, find the stimulus column and record whether it was
-  # red, white, or blue
-  list_str <- base::apply(
-    data_frame
-    , 1
-    , function(x) {
-      # Grab the cell for the correct trial
-      str <- x["stimulus"]
-      # Then change the character to Red, White, or Blue 
-      # depending on stimuli filename
-      if (base::grepl("rep", str) == TRUE) {
-        str <- "Red"
-      } else if (base::grepl("cont", str) == TRUE) {
-        str <- "White"
-      } else if (base::grepl("dem", str) == TRUE) {
-        str <- "Blue"
-      } else {
-        str <- "NULL"
-      }
-      # Return updated str
-      return(str)
-    }
-  ) |>
-  base::as.list() # covert this to a list
-  # Add names to the list based off of the trial
-  base::names(list_str) <- list_trials
-  # Return list
-  return(list_str)
-}
-
-#' @title mouseview data handler
-#' 
-#' @description
-#' This is a function that takes the data reported from mouseview
-#' converts it to a vector, takes the absolute difference between
-#' positions on that vector, and then calculates the average
-#' movement for that vector.
-#' 
-#' @details
-#' The mouseview data comes in as an array but stored as character
[…]

### 2023-09-22 chapter_2/src/R/predicted_prob_bar.R

@@ -1,257 +1,0 @@
-#' @title make barplots for predicted probabilities from ordered logit
-#'
-#' @description
-#' This is a function that makes ggplot2 barplots by taking a fitted
-#' ordered logit model, calculating the predicted probabilities,
-#' and then plotting it with barplots and including error bars.
-#'
-#' @details
-#' This function takes a brmsfit object. It uses the marginalefffects
-#' package to calculate the predicted probabilities.
-#'
-#' @param
-#'
-#' @return plot A ggplot2 object.
-#'
-#' @example
-#'
-predicted_prob_bar <- function( # nolint: object_usage_linter.
-  fitted_model
-  , x_axis
-  , treatment = "Red"
-  , hypothesis = "H2"
-  , level = 0.90
-  , x_label = "Color of yard sign"
-  , y_label = "Pr(Party of candidate)"
-  , legend_title = "Party of candidate"
-) {
-  # If this is for a ordered logit, I'll have to do some stacked
-  if (hypothesis == "H2") {
-    #* Calculate the predicted probabilities for the model
-    df_pred_prob <- marginaleffects::predictions(
-      model = fitted_model
-      , conf_level = level
-    )|>
-    data.table::as.data.table() # convert it to a data.table
-    #* Need to clean up the pred prob data.frame some
-    df_pred_prob_cleaned <- df_pred_prob[
-      #** aggregate the estimate, conf.low, and conf.high columns with
-      #** a mean to calculate the average conditional predicted probabilities
-      , .( # nolint: object_usage_linter.
-        estimate = mean(estimate) # nolint: object_usage_linter.
-        , conf.low = mean(conf.low) # nolint: object_usage_linter.
-        , conf.high = mean(conf.high) # nolint: object_usage_linter.
-      )
-      #** this needs to be done by the group column and the
-      #** independent variable
-      , by = c(
-        "group"
-        , x_axis
-      )
-    ][
-      #** convert the x-axis to a factor
-      , x_axis_temp := factor(get(x_axis)) # nolint: object_usage_linter.
-    ][
-      #** convert the group column to a factor
-      , group := factor(group) # nolint: object_usage_linter.
-    ]
-    # Make plot
-      #* take the cleaned pred_prob dataframe
-    plot <- ggplot2::ggplot(
-      data = df_pred_prob_cleaned
-    ) +
-      #* make a barplot
-      ggplot2::geom_bar(
-        ggplot2::aes(
-          #** put the IV on the x-axis, estimate on y
-          #** and change the fill color based on group
[…]

### 2023-09-22 chapter_2/src/eda/study_1/cleaning.R

@@ -1,203 +1,0 @@
-# Title: cleaning script for pavlovia data
-
-# Notes
-  #* Description
-    #**This is a cleaning script for the pavlovia data.
-    #** It takes the csv files, extracts some data from them,
-    #** merges in the prolific demographic data, then removes
-    #** duplicated rows based on session_id, then converts
-    #** columns to correct data types.
-  #* Updated:
-    #** 2023-08-07
-    #** dcr
-
-# Setup
-  #* Load useful functions
-box::use(
-  data.table[...]
-  , ./R/clean_data[clean_data]
-)
-# Cleaning
-  #* Do basic cleaning to return a minimally usable data.frame
-list_df <- list() # create an empty list for my data_frames
-list_df[["original"]] <- clean_data(
-  folder = "../data/original/study_1/data"
-  , prolific_data = "../data/clean/prolific_demographic_data.csv"
-)
-  #* Create measures
-list_df[["cleaned"]] <- list_df[["original"]][
-    #** Generate 7-item pid measure
-    #** Coded as -3 = Strong Democrat, 3 = Strong republican
-  , pid_7 := fcase(
-    pid_3 == "Democrat" & pid_d_str == "Strong", -3
-    , pid_3 == "Democrat" & pid_d_str == "Not very strong", -2
-    , pid_3 == "Democrat" & is.na(pid_d_str), -1
-    , pid_3 == "Independent" & ind_lean == "Closer to Democratic", -1
-    , pid_3 == "Other" & ind_lean == "Closer to Democratic", -1
-    , pid_3 == "Independent" | pid_3 == "Other" & ind_lean == "Neither", 0
-    , pid_3 == "Other" & ind_lean == "Closer to Republican party", 1
-    , pid_3 == "Independent" & ind_lean == "Closer to Republican party", 1
-    , pid_3 == "Republican" & is.na(pid_r_str), 1
-    , pid_3 == "Republican" & pid_r_str == "Not very strong", 2
-    , pid_3 == "Republican" & pid_r_str == "Strong", 3
-  )
-]
-#* Recoding/adding factors
-list_df[["cleaned"]] <- list_df[["cleaned"]][
-  #** convert age to numeric
-  , age := as.numeric(age)
-][
-  #** convert attention to numeric
-  , attention := fcase(
-    attention == "Never", 0
[…]

### 2023-09-22 chapter_2/src/eda/study_1/descriptive_stats.R

@@ -1,48 +1,0 @@
-# Title: descriptive stats of pavlovia data
-
-# Notes
-    #* Description
-        #** A R file that generates some descriptive statistics of the sample
-    #* Updated
-        #** 2023-06-16
-        #** dcr
-
-# Setup
-    #* Set working directory
-setwd("./src")
-    #* execute cleaning script
-source("./eda/study_1/cleaning.R")
-        #** check to make sure it ran right
-ls()
-str(list_df)
-    #* load handy functions
-box::use(
-    data.table[...]
-    , modelsummary[
-        datasummary_skim
-    ]
-)
-
-# Select columns to summarize
-    #* Demographics
-df_demographics_subset <- list_df[["cleaned"]][
-    , c("age", "color_blind_dummy", "gender_id", "white", "hispanic", "black")
-]
-datasummary_skim(df_demographics_subset)
-    #* Politics
-df_politics_subset <- list_df[["cleaned"]][
-    , c("pid_7", "attention")
-]
-datasummary_skim(df_politics_subset)
-    #* Treatments
-df_treatments_subset <- list_df[["cleaned"]][
-    , c(
-        "trial_1_red_stimuli"
-        , "trial_2_red_stimuli"
-        , "trial_3_red_stimuli"
-        , "vote"
-        , "trial_1_party"
-        , "trial_2_party"
-        , "trial_3_party")
-]
-datasummary_skim(df_treatments_subset)

### 2023-09-22 chapter_2/src/models/study_1_fitting.R

@@ -1,336 +1,0 @@
-# Title: Preliminary analyses of pavlovia data
-
-# Notes
-    #* Description
-        #** This is a R file that performs some preliminary analyses of
-        #** the pavlovia data for study 1
-    #* Updated
-        #** 2023-06-16
-        #** dcr
-
-# Setup
-  #* set seed
-set.seed(12102022)
-  #* set working directory
-setwd("./chapter_2/src")
-  #* execute cleaning script
-source("./eda/study_1/cleaning.R")
-  #* load in cleaned study-2 data
-  #* (need to run each python script individually)
-df_study_2 <- read.csv("../data/clean/study_2.csv") |>
-  as.data.table()
-  #* convert state_district and year variables  to factors
-df_study_2 <- df_study_2[
-  , year := tstrsplit(year, "-", keep = 1)
-][
-  , year := as.numeric(year)
-][
-  , state_district := factor(state_district)
-][
-  , blue_prop := blue_percent / 100
-][
-  , red_prop := red_percent / 100
-]
-  #* load helpful functions
-box::use(
-  data.table[...]
-  , brms[...]
-  , ordbetareg[...]
-)
-    #* make an empty model list object
-list_fitted <- list(
-  h_1 = list()
-  , h_2 = list()
-  , h_2a = list()
-  , h_3 = list()
-  , h_4 = list()
-  , h_5 = list()
-)
-list_ppc <- list(
-  h_1 = list()
-  , h_2 = list()
-  , h_2a = list()
-  , h_3 = list()
-  , h_4 = list()
-  , h_5 = list()
-)
-
-# Hypothesis 1
-
-# Hypothesis 2
-    #* Fit models
-list_fitted[["h_2"]][["red_multinomial"]] <- brm(
-  formula = trial_1_party ~ trial_1_red_stimuli
-  , data = list_df[["cleaned"]]
-  , family = categorical(link = "logit")
-  , prior = set_prior("normal(0, 1)", class = "b")
-  , backend = "cmdstanr"
-)
-list_fitted[["h_2"]][["blue_multinomial"]] <- brm(
-  formula = trial_1_party ~ trial_1_blue_stimuli
-  , data = list_df[["cleaned"]]
[…]

### 2023-09-22 chapter_2/src/study_2/01_capd_text_scraping.py

@@ -1,84 +1,0 @@
-# Title: CAPD Text scraping 
-
-# Notes:
-    #* Description: Jupyter Notebook to scrape CAPD site for yard signs in 2018-2022 national elections
-    #* Updated: 2023-06-20
-    #* Updated by: dcr 
-
-# Load Modules
-import time # library to help with sleep and wait times
-from selenium import webdriver # to setup the driver
-from selenium.webdriver.chrome.options import Options # to specify options for my chrome webdriver
-from selenium.webdriver.chrome.service import Service as ChromeService
-from webdriver_manager.chrome import ChromeDriverManager # use the driver manager so that I don't have to download it and keep track of versions myself
-from selenium.webdriver.support.ui import WebDriverWait # use this so that I can wait on my driver to load the page completely before searching
-from selenium.webdriver.common.by import By # using the By function to help with the xpath searching
-from selenium.webdriver.support import expected_conditions as EC # load the expected_conditions function to make sure all elements matching the xpath happen before the driver stops waiting on the loading
-import polars as pl # need the pandas package for dataFrames
-#import duckdb # need to store data into database
-
-# Scraping of CAPD site
-
-## Driver and scraping
-options = Options() # set webdriver options
-options.add_argument("start-maximized") # set an option for the webdriver to automatically open chrome browser that I can interact with the page
-
-driver = webdriver.Chrome() # setup chrome webdriver
-
-wait = WebDriverWait(driver, 100000) # specify wait time for the page before stopping it from collecting links in xpath
-
-url = "https://www.politicsanddesign.com/"
-
-driver.get(url) # Make sure to turn off year filter on page that pops up and scroll all the way down
-
-wait.until(EC.presence_of_all_elements_located((By.XPATH, "//div[@class='candidate-card-text']/ul"))) # tell driver to search along this path, but to not stop the search until it everything has been collected
-time.sleep(10) # add an some extra time incase needed 
-txt_url = driver.find_elements(By.XPATH, "//div[@class='candidate-card-text']/ul") # go ahead and collect all the elements
-txt_url2 = [] # make empty list object to store urls in
-for i in txt_url:
-    txt_url2.append(i.text) # grab the text for each of the sessions
-
-driver.close() # close the driver
-
-# Data wrangling
-txt_url4 = [i for i in txt_url2 if i] # take the elements of txt_url2 and place them in a list
-
-yard_signs = pl.DataFrame({
[…]

### 2023-09-22 chapter_2/src/study_2/02_capd_img_scraping.py

@@ -1,65 +1,0 @@
-# Title: CAPD Image Scraping
-
-# Notes:
-    #* Description: Jupyter Notebook to scrape CAPD site for yard signs in 2018-2022 national elections
-    #* Updated: 2022-11-28
-    #* Updated by: dcr 
-    #* Other notes:
-        #** First run 01_capd_text_scraping.py. This should be executed interactively.
-
-# Load Modules
-import time # library to help with sleep and wait times
-from selenium import webdriver # to setup the driver
-from selenium.webdriver.chrome.options import Options # to specify options for my chrome webdriver
-from selenium.webdriver.chrome.service import Service as ChromeService
-from webdriver_manager.chrome import ChromeDriverManager # use the driver manager so that I don't have to download it and keep track of versions myself
-from selenium.webdriver.support.ui import WebDriverWait # use this so that I can wait on my driver to load the page completely before searching
-from selenium.webdriver.common.by import By # using the By function to help with the xpath searching
-from selenium.webdriver.support import expected_conditions as EC # load the expected_conditions function to make sure all elements matching the xpath happen before the driver stops waiting on the loading
-import polars as pl # need the pandas package for dataFrames
-#import duckdb # need to store data into database
-
-# Scraping of CAPD Site
-
-## Driver and Scraping
-
-options = Options() # set options for driver
-options.add_argument("start-maximized") # specify the option to open chrome browser when sent to driver
-
-driver = webdriver.Chrome() # create ChromeDriver
-
-wait = WebDriverWait(driver, 10000) # set wait time for driver when searching XPATH
-
-url = "https://www.politicsanddesign.com/" # site of url to go to
-
-driver.get(url) # go to url
-
-wait.until(EC.presence_of_all_elements_located((By.XPATH, "//picture[@class='responsive-image-wrapper']/img"))) # search xpath on url. Need to first remove 2020 filter and scroll all the way to the bottom
-time.sleep(10) # set sleep timer just in case driver needs more time
-img_url = driver.find_elements(By.XPATH, "//picture[@class='responsive-image-wrapper']/img") # search xpath on url
-
-img_url2 = [] # create empty list
-for element in img_url:
[…]

### 2023-09-22 chapter_2/src/study_2/03_capd_downloading_images.py

@@ -1,34 +1,0 @@
-# Title: CAPD Image Downloading
-
-# Notes:
-    #* Description: Script to open links to images and downloading them from CAPD site
-    #* Updated: 2022-11-28
-    #* Updated by: dcr
-    #* Other notes:
-        #** Should execute at end of 02_capd_img_scraping.py
-
-
-# Importing modules 
-    #* From environment
-#import duckdb # for database management
-import polars as pl # for dataFrame management
-import urllib.request # to access site
-import sys # to deal with paths
-
-    #* User-defined
-from chapter_2.src.PY.helper import names
-
-# Loading database
-
-df = pl.read_csv(
-    source = "./chapter_2/data/temp/study_2/02_output.csv"
-)
-
-links_df = df.with_columns(
-    names(pl.col("candidate_name")).alias("last_name")
-).to_pandas()
-
-# Downloading the images
-
-for index, row in links_df.iterrows():
-    urllib.request.urlretrieve(row["Img_URL"], "./chapter_2/data/original/study_2/capd_yard_signs/" + row["last_name"] + "_" + str(row["year"]) + ".png")

### 2023-09-22 chapter_2/src/study_2/04_color_detection.py

@@ -1,103 +1,0 @@
-# Title: CAPD detecting colors
-
-# Notes: 
-    #* Description: Script to detect the colors on the yard signs
-    #* Updated: 2022-11-28
-    #* Updated by: dcr
-
-# Load modules
-    #* From visual_env 
-#import duckdb # to access the database
-import numpy as np # to wrangle arrays
-import polars as pl # to wrangle dataFrames
-import re # to wrangle strings
-import cv2 # to do color detection
-import os # to wrangle local files
-    #* User defined
-from chapter_2.src.PY.helper import names, colorDetector
-
-# Define colors to detect
-    #* White
-        #** Not defined. Default for colorDetector()
-    #* Red
-republican_red = [232, 27, 35] # target color
-red_lower = [93, 9, 12] # lower end of spectrum for red
-red_higher = [237, 69, 75] # higher end of spectrum for red
-    #* Blue
-democrat_blue = [0, 174, 243] # target color
-blue_lower = [0, 18, 26] # lower end of spectrum for blue
-blue_higher = [102, 212, 255] # higher end of spectrum for blue
-
-# Detect colors
-    #* Create an empty dataframe to store them in
-df = pl.DataFrame({
-                    "last_name": ["Test"],
-                    "year": ["2023"],
-                    "white_percent": [1.2],
-                    "blue_percent": [1.2],
-                    "red_percent": [1.2]
-})
-
-for filename in os.listdir("./chapter_2/data/original/study_2/capd_yard_signs"):
-    #* check to make sure the file is a png file
-    if filename.endswith('.png'):
-    #* join the directory to the file name
-            f = os.path.join("./chapter_2/data/original/study_2/capd_yard_signs", filename)
-            print("read file")
-    #* split the file name and store the information
-            lastName, year, file = re.split(r'[_.]', filename)
-            print("split file name")
-    #* open the image's file
-            #pil = Image.open(f).convert('RGB')
-            #pilCv = np.array(pil)
-            #img = pilCv[:,:,::-1].copy()
-            img = cv2.imdecode(np.fromfile(f, dtype=np.uint8), cv2.IMREAD_COLOR)
-            print("load file")
-    #* calculate the percent of the image that is white
-            whitePercent, _, _ = colorDetector(img = img, color_lower = [255,255,255], color_upper = [255,255,255])
-            print("calculated whitePercent")
-    #* calculate the percent of the image that is blue
-            bluePercent, _, _ = colorDetector(img = img, color_upper = blue_higher, color_lower = blue_lower)
[…]

### 2023-09-22 chapter_2/src/study_2/05_mit_election_lab_merge.py

@@ -1,130 +1,0 @@
-# Title: Merging MIT Election Lab Data to Yard Signs dataset
-
-# Notes:
-    #* Description: Script to merge MIT Election Lab US House 1976-2020 Election Returns dataset to Yard signs table
-    #* Updated: 2022-11-28
-    #* Updated by: dcr
-    #* Other notes:
-        #** To access dataset go to:
-        #** https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/IG0UN2
-
-# Load modules
-    #* from env
-#import duckdb # for database access
-import polars as pl # for DataFrame management
-import numpy as np # for array management
-    #* User-defined
-from chapter_2.src.PY.helper import names
-
-# Check out the election lab data
-election_lab = pl.read_csv(
-    #* lazy load the csv file
-    "./chapter_2/data/original/study_2/1976-2020-house.csv",
-    null_values=""
-    ).select([
-    #* select the following columns
-        "year",
-        "state",
-        "district",
-        "candidate",
-        "party",
-        "candidatevotes",
-        "totalvotes"
-    ]).with_columns([
-    #* convert state column to lowercase
-        pl.col("state").str.to_lowercase().alias("state"),
-    #* create candidate_Name column
-        #pl.col("candidate").str.to_lowercase().alias("Candidate_Name")
-    ]).with_columns(
-        pl.concat_str(["state", "district"], separator = "-").alias("state_district")
-    ).with_columns(
-        pl.when(pl.col("state_district") == "alaska-0")
-        .then("alaska-1")
-        .otherwise(pl.col("state_district")).alias("state_district")
-    ).with_columns(
-        pl.when(pl.col("state_district") == "vermont-0")
-       .then("vermont-1")
-       .otherwise(pl.col("state_district")).alias("state_district") 
-    ).with_columns(
-        pl.when(pl.col("state_district") == "montana-0")
-        .then("montana-1")
-        .otherwise(pl.col("state_district")).alias("state_district")
-    ).with_columns(
-        pl.when(pl.col("state_district") == "wyoming-0")
-        .then("wyoming-1")
-        .otherwise(pl.col("state_district")).alias("state_district")
-    ).with_columns(
-        pl.when(pl.col("state_district") == "south dakota-0")
-        .then("south dakota-1")
[…]

### 2023-09-22 chapter_2/test/test_clean_data.R

@@ -1,31 +1,0 @@
-# Title: test clean_data function
-
-# Notes:
-    #* Description
-        #** testing of the clean_data funciton
-    #* Updated
-        #** 2023-06-12
-        #** dcr
-
-# Setup
-    #* set working directory
-#setwd("../src/")
-setwd("./src/")
-    #* load relevat packages
-box::use(
-    ./R/clean_data[...]
-    , data.table[...]
-)
-    #* examples
-        #** load single file
-df_temp <- read.csv(
-    file = "/Users/dcr/Library/CloudStorage/Dropbox/current_projects/dissertation/chapter_2/data/original/study_1/data/diss_ch_1_pre-reg_PARTICIPANT_SESSION_2023-06-12_10h09.02.63.csv"
-)
-
-df_test <- extract_file(df_temp)
-
-      #** Full test
-df_test <- clean_data(
-    folder = "../data/original/study_1/data"
-    , prolific_data = "../data/clean/prolific_demographic_data.csv"
-)

### 2023-09-22 chapter_3/src/prr/R/model.R

@@ -1,141 +1,0 @@
-'.__module__.' # nolint
-#' @title fit a model
-#'
-#' @description
-#' This is a function that takes some information about a rstan model
-#' and then fits the model depending on that information.
-#'
-#' @details
-#' This function is designed to take one data.frame
-#' and to fit a model on that one data.frame.
-#' There are higher level functions in here that rely upon this function.
-#'
-#' @param list_data Should be a stan compatible list of your data.
-#' Can use `brms::make_standata` to do this.
-#' @param compiled_stan_model Should be a compiled stan model.
-#' @param ci_level Should be a float indicating what level do you want credible
-#' intervals calculated at.
-#' @param parameters Should be a list of strings to indicate what parameters you
-#' you want to calculate the true positive rate for.
-#'
-#' @returns df_discrepancy A data.table saying whether the model's posterior
-#' would indicate a non-zero result.
-#'
-#' @examples
-#'
-fit_sim_model <- function( # nolint
-  list_data = NULL
-  , compiled_stan_model = NULL
-  , ci_level = 0.95
-  , parameters = c("b[1]")
-) {
-  # fit the stan model
-  stan_fitted <- rstan::sampling(
-    compiled_stan_model
-    , data = list_data
-    , chains = 1
-    , iter = 100
-    , refresh = 0
-    , verbose = FALSE
-  )
-  # turn it into a  data.frame
-  df_fitted <- data.table::as.data.table(stan_fitted)
-  # calculate credible intervals at pre-specified value
-  df_ci <- data.table::as.data.table(
-    bayestestR::hdi(
-      df_fitted
-      , parameters = c("b")
-      , ci = ci_level
-    )
-  )[
-    Parameter %in% parameters # nolint
-  ]
-    # calculate whether there was a discrepancy
-  df_discrepancy <- df_ci[
-    , true_positive := data.table::fifelse( # nolint
-        CI_low > 0 & CI_high > 0, 1, # nolint
-        data.table::fifelse(
-            CI_low < 0 & CI_high < 0, 1, 0
-        )
-    )
-  ]
-    ## return fitted model
-    return(df_discrepancy)
-}
-
-#' @title fit model on multiple simulated samples
-#'
-#' @description
-#' This is a function that takes the `fit_sim_model()` function
-#' and performs it iteratively on a large data.table that contains
-#' data from many simulated samples that are grouped by a ID column
-#' indicating which sample that data is from.
-#'
[…]

### 2023-09-22 chapter_3/src/prr/R/plot.R

@@ -1,52 +1,0 @@
-'.__module__.' #nolint
-#' @title plot true positive rate
-#'
-#' @description
-#' This is a function that takes the calculated true positive rate
-#' from `true_positive()` for each sample size and plots it
-#' with a histogram.
-#'
-#' @param data_frame A data.table object returned from `true_positive()`.
-#' @param var Which variable to calculate the true positive rate for.
-#' @param new_names A list of names to put on the x-axis
-#'
-#' @returns plot A ggplot2 object.
-#'
-#' @examples
-#'
-true_positive_plot <- function(
-  data_frame
-  , var = "Parameter"
-) {
-  # split the datatable by variable
-  list_true_positive <- base::split(
-    data_frame
-    , f = data_frame[[var]]
-  )
-  # Plot each list element
-  list_plots <- base::lapply(
-    list_true_positive
-    , function(x) {
-      plot <- ggplot2::ggplot(
-        data = x
-      ) +
-      ggplot2::geom_bar(
-        ggplot2::aes(
-          y = true_positive
-          , x = factor(sample_size)
-        )
-        , stat = "summary"
-        , fun = "mean"
-      ) +
-      ggplot2::labs(
-        x = "Sample size"
-        , y = "True positive rate"
-      ) +
-      ggplot2::theme_minimal()
-      # return plot
-      return(plot)
-    }
-  )
-  # return list of plots
-  return(list_plots)
-}

### 2023-09-22 chapter_3/src/prr/R/sample.R

@@ -1,315 +1,0 @@
-#' @title define breaks
-#'
-#' @description
-#' This function takes the standard deviation
-#' of the latent variables and creates quiltiles
-#' for those variables to define as the
-#' break values
-#'
-#' @param vector A column from a data.frame object.
-#'
-#' @param cuts A integer value of how many ordered outcomes are expected.
-#'
-#' @returns numeric A numeric class listing cut points.
-#'
-#' @examples
-#' df <- data.frame(A = c(1, 2, 3, 4, 5))
-#' define_break(vector = df$A, cuts = 5)
-#
-define_break <- function(
-  vector = NULL
-  , cuts = 5
-) {
-  # find the cuts in the data based on pre-specified number
-  quintile <- stats::quantile(
-    x = vector
-    , probs = seq(
-      0
-      , 1
-      , 1 / (cuts - 1)
-    )
-  )
-  # Take the cuts and put it into a list of buckets
-  if (cuts == 5) {
-    list_quintile <- c(
-      -Inf
-      , quintile[[1]]
-      , quintile[[2]]
-      , quintile[[3]]
-      , quintile[[4]]
-      , Inf
-    )
-  } else if (cuts == 7) {
-     list_quintile <- c(
-      -Inf
-      , quintile[[1]]
-      , quintile[[2]]
-      , quintile[[3]]
-      , quintile[[4]]
-      , quintile[[5]]
-      , quintile[[6]]
-      , Inf
-     )
-  } else {
-    print(
-      "
-      Invalid number of cuts entered.
-      Specify the 'cuts' option as either 5 or 7.
-      "
-    )
-  }
-  # Return the list of buckets
-  return(list_quintile)
-}
-#' @title generate a single sample
-#'
-#' @description
-#' This is a funciton that generates a single sample
-#' based on characteristics of the study design
-#'
-#' @details
-#'
-#' The characteristics of the sample depends on which study I am doing
-#'
-#' @param study An integer specifying whether this is for study 1 or study 2.
-#' @param seed A integer specifying which seed to use.
-#'
-#' @returns sample A data.frame object.
-#'
-#' @examples
-#' df <- single_sample()
-#' df_alt <- single_sample(study = 1, seed = 121022)
-#'
-single_sample <- function(
-  study = 1 # study 1 or study 2
-  , seed = 121022 # seed
-) {
-  # Set seed
-  set.seed(seed)
-  # Likert break labels
[…]

### 2023-09-22 chapter_3/test/test_model.R

@@ -1,143 +1,0 @@
-# Title: testing the functions in model.R
-
-# Notes:
-    #* Description
-        #** Unit tests for the functions in model.R
-    #* Updated
-        #** 2023-06-13
-        #** dcr
-
-# Setup
-  #* Set working directory
-setwd("../src/prr")
-  #* Load relevant functions
-box::use(
-  testthat[...]
-  , data.table[...]
-  , ./R/sample[...]
-  , ./R/model[...]
-)
-  #* examples
-    #** define a list of different sample sizes
-list_sample_size <- c(100, 150, 200, 250)
-    #** sample the data at different sample sizes
-list_simulated <- lapply(
-  list_sample_size
-  , function(x) {
-    df_sample <- study_simulator(
-      study = 1
-      , n = x
-      , n_samples = 10
-      , seed = 121022
-    )
-    # Return df_sample
-    return(df_sample)
-  }
-)
-    #** default arguments
-formula_study_1_model_1 <- brms::brmsformula(
-  notice ~ prime
-)
-family_study_1_model_1 <- brms::bernoulli(link = "logit")
-prior_study_1_model_1 <- brms::set_prior(
-  "normal(0, 1)"
-  , class = "b"
-)
-stan_compiled_model <- rstan::stan_model(
-  file = "./STAN/study_1_model_1.stan"
-  , model_name = "study_1_model_1"
-)
-    #** fitting a single model
-df_example <- list_simulated[[1]][
-  sample == 1,
-]
-standata_example <- brms::make_standata(
-  formula = formula_study_1_model_1
-  , data = df_example
-  , family = family_study_1_model_1
-  , prior = prior_study_1_model_1
-)
-stan_single_fitted <- fit_sim_model(
-  list_data = standata_example
-  , compiled_stan_model = stan_compiled_model
-  , parameters = c("b[1]")
-)
-    #** fitting multiple models
-df_example_2 <- list_simulated[[1]]
-
-stan_multiple_fitted <- fit_sims(
-  data_frame = df_example_2
-  , compiled_stan_model = stan_compiled_model
-  , formula = formula_study_1_model_1
-  , family = family_study_1_model_1
-  , prior = prior_study_1_model_1
-)
-  #** fitting multiple models at different sample sizes
-list_multiple_sample_sizes <- base::lapply(
-  list_simulated
-  , function(x) {
-    fit_sims(
-      data_frame = x
[…]

### 2023-09-22 chapter_3/test/test_plot.R

@@ -1,87 +1,0 @@
-# Title: test of plot functions
-
-# Notes:
-    #* Description
-        #** unit tests for plot functions
-        #** NEED TO MANUALLY RUN THIS ONE
-    #* Updated
-        #** 2023-06-13
-        #** dcr
-
-# Setup
-    #* Set working directory
-setwd("../src/prr")
-    #* Load relevant functions
-box::use(
-  testthat[...]
-  , data.table[...]
-  , ./R/sample[...]
-  , ./R/model[...]
-  , ./R/plot[...]
-)
-  #* Create example
-    #** define sample sizes
-list_sample_size <- c(100, 150, 200, 250)
-    #** sample the data at different sample sizes
-list_simulated <- lapply(
- list_sample_size
- , function(x) {
-   df_sample <- study_simulator(
-     study = 1
-     , n = x
-     , n_samples = 10
-     , seed = 121022
-   )
-   # Return df_sample
-   return(df_sample)
- }
-)
-    #** default model arguments
-      #*** formula
-formula_study_1_model_1 <- brms::brmsformula(
-  notice ~ prime
-)
-      #*** family
-family_study_1_model_1 <- brms::bernoulli(link = "logit")
-      #*** priors
-prior_study_1_model_1 <- brms::set_prior(
-  "normal(0, 1)"
-  , class = "b"
-)
-      #** compiled model
-stan_compiled_model <- rstan::stan_model(
-  file = "./STAN/study_1_model_1.stan"
-  , model_name = "study_1_model_1"
-)
-    #** fit models
-list_multiple_sample_sizes <- base::lapply(
-  list_simulated
-  , function(x) {
-    fit_sims(
-      data_frame = x
-      , compiled_stan_model = stan_compiled_model
-      , formula = formula_study_1_model_1
-      , family = family_study_1_model_1
-      , prior = prior_study_1_model_1
-    )
-  }
-)
-names(list_multiple_sample_sizes) <- list_sample_size
-df_example <- rbindlist(
-  list_multiple_sample_sizes
-  , idcol = "sample_size"
-)[
-  , sample_size := factor(sample_size)
-]
-    #** generate plot
-plot_test <- true_positive_plot(
-  data_frame = df_example
-)
-
-# Tests
-test_that(
-  "make sure it returns one plot"
-  , expect_length(
-    plot_test, 1
-  )
-)

### 2023-09-22 chapter_3/test/test_sample.R

@@ -1,152 +1,0 @@
-# Title: test of sample.R functions
-
-# Notes:
-  #* Description
-    #** Unit test of functions from sample.R
-  #* Updated
-    #** 2023-06-12
-    #** dcr
-
-# Setup
-  #* set working directory
-setwd("../src/prr")
-#setwd("./src/prr")
-  #* Modularly load functions
-box::use(
-  testthat[...]
-  , ./R/sample[...]
-)
-  #* example
-    #** study 1
-      #** single sample
-df_sample_study_1 <- single_sample()
-      #** 10 samples
-df_multi_study_1 <- study_simulator(study = 1, n = 100, n_samples = 10)
-    #* study 2
-      #** single sample
-df_sample_study_2 <- single_sample(study = 2)
-      #** 10 samples
-df_multi_study_1 <- study_simulator(study = 1, n = 100, n_samples = 10)
-# Tests
-  #* Study 1
-    #** single sample
-test_that(
-  "check class of study 1 single sample"
-  , {
-    expect_s3_class(
-      df_sample_study_1
-      , "data.frame"
-    )
-  }
-)
-test_that(
-  "check ncol of study 1 single sample"
-  , {
-    expect_true(
-      ncol(df_sample_study_1) == 13
-    )
-  }
-)
-test_that(
-  "check to make sure nrow equals 100000 for single sample study 1"
-  , {
-    expect_true(
-      nrow(df_sample_study_1) == 100000
-    )
-  }
-)
-test_that(
-  "if study does not equal 1 or two, expect error"
-  , {
-    expect_error(
-      single_sample(study = 3)
-    )
-  }
-)
-    #** multiple samples
-test_that(
-  "check class of study 1 multi sample"
-  , {
-    expect_s3_class(
-      df_multi_study_1
-      , "data.frame"
-    )
-  }
-)
-test_that(
-  "check ncol of study 1 multi sample"
-  , {
-    expect_true(
-      ncol(df_multi_study_1) == 14
-    )
-  }
-)
-test_that(
-  "check to make sure nrow equals 1000 for multi sample study 1"
-  , {
-    expect_true(
-      nrow(df_multi_study_1) == 1000
-    )
-  }
-)
-test_that(
-  "if sample is not greater than one, expect error"
-  , {
-    expect_error(
-      study_simulator(study = 1, sample = 0)
-    )
-  }
-)
-  #* Study 2
-    #** single sample
-test_that(
[…]

### 2023-09-22 chapter_2/src/slides/slides.qmd
successfully published on github pages with the gh-pages branch

--- 2023-09-20 chapter_2/src/slides/slides.qmd
@@
   freeze: true
-  cache: true
 ---

### 2023-09-25 chapter_2/src/roberts_empirical_chapter_1.qmd
integrated a bunch of them, not sure about the others. Will keep it open for now

--- 2023-08-24 chapter_2/src/manuscript.qmd
@@
-# Does color convey political information?
-<!--
-    - Description: QMD script for empirical chapter 1
-    - Updated: 2023-07-16
-    - Notes:
-        * Code:
-        * Writing:
--->
+---
+title: |
+  Does Color Convey Political Information?
+short-title: Color as Political Information
+published: "Manuscript draft: please do not share without author permission."
+code-repo: "For replication, go to: <https:://github.com/DamonCharlesRoberts/book_project>."
+author:
+  - name: Damon C. Roberts
+    email: damon.roberts-1@colorado.edu
+    orcid: 0000-0002-4360-3675
+    title: PhD Candidate
+    affiliations:
+      - id: CU
+        name: University of Colorado Boulder
+        department: Political Science
+        address: 333 UCB
+        city: Boulder
+        region: CO 
+        postal-code: 80309-0333
+abstract: |
+  Do the colors red and blue convey political information?
+If so, how do they shape candidate preferences and vote choice?
+Political psychologists rely on interdisciplinary approaches to construct theories of how we process political information.
+Likewise, those who study visual political information come from a number of disciplinary traditions to study how politics may be conveyed visually.
+As these groups of scholars are working in parallel, they have yet to fully integrate their work to construct a theory explaining the cognitive and behavioral consequences of visual information on political attitude expression and behavior.
+In this chapter, I present a snap-judgment model of visual information processing to demonstrate how visual information efficiently conveys substantive political information.
+Specifically, I focus on a simple but obvious case that we only have anecdotal and descriptive evidence of: the association between Republicans with the color red and Democrats with the color blue.
+First, I use supervised machine learning that does a pixel-by-pixel classification of the color on yard signs used by campaigns for the U.S.
+House of Representatives from 2016 to 2020 and merge this with election return data from the MIT Election Labs.
+From these data, I find that systematic descriptive evidence of campaigns using more red in their yard signs in districts that are safe for Republicans and campaigns using more blue in their yard signs in districts that are safe for Democrats.
+Next, I turn to an experiment to examine whether these associations of the colors red and blue with Republicans and Democrats exist among voters and whether it shapes attitude expression and behavior.
+I find that these associations of the color red with Republicans and the color blue with Democrats do exist among the public and that these associations are strong enough to shape support for political candidates.
+This chapter advances our understanding in a few areas: that visual information is a pre-conscious form of information that we should integrate with our models of information processing that consider more traditional forms of political information, provides a cognitive mechanism to explain how the public have come to associate the colors red and blue with the two dominant political parties, as well as demonstrates that these cognitive processes are capable of influencing behavior as important as vote choice.
+additional-info: |
+  I have no known conflict of interest to disclose.
+keywords:
+  - visual information
+  - information processing
+  - partisanship
+date: today
+bibliography: "../../assets/candidate_support_chapter_references.bib"
+format:
+  hikmah-pdf:
+    cite-method: citeproc
+    latex-output-dir: ../out/
+    geometry:
+      - top=1in
+      - bottom=1in
+      - left=1in
+      - right=1in
+      - heightrounded
+    linestretch: 2
+    fontsize: 12pt
+    appendix-style: default
+    include-in-header:
+      text: |
+        \usepackage{pdflscape}
+        \newcommand{\blandscape}{\begin{landscape}}
+        \newcommand{\elandscape}{\end{landscape}}
+linestretch: 2
+execute:
+  echo: false
+  warning: false
+  message: false
+params:
+  replicate: false
+---
+
+```{r}
+#| label: r-setup-block
+
+# Load some handy functions
+box::use(
+    data.table[...]
+    , modelsummary[
+        datasummary_skim
+        , datasummary_balance
+    ]
+    , ./R/predicted_prob_bar[...]
+)
+
+# Execute the cleaning script
+source("./eda/study_1/cleaning.R")
+# Load fitted models
+load("../data/temp/models/study_1_fitted.RData")
+```
 
@@
 
-In [Study 1](#study-1), I conduct an online experiment that examines whether the public notice color and whether their attitudes are shaped by "Republican red" and "Democratic Blue" on the yard signs of a fictional candidate.
-Based on informal conversations with campaign marketing consultants, it appears that campaigns are aware that the colors red and blue betray the partisanship of a candidate to voters.
-Accordingly, in [Study 2](#study-2), I examine whether campaigns react to the partisan composition of an electorate, as a response to these individual-level patterns.
-Specifically, I do this by examining how electoral context shapes variation in the use of these partisan colors.
-While these two studies highlight endogenous processes, to be clear, I am not arguing that either of these patterns only one way.
+In [Study 1](#study-1), I find descriptive evidence suggesting that campaigns use the colors red and blue on their yard signs at different rates depending on the success of Republicans and Democrats according to previous election returns.
+It is unclear, however, whether these patterns are based on elite perceptions of how to communicate partisanship to voters or whether campaigns have successfully identified a cognitive process linking the colors red and blue with Republicans and Democrats.
+Accordingly, in [Study 2](#study-2), I conduct an online experiment that examines whether the public notice color and whether their attitudes are shaped by the presence of "Republican red" and "Democratic blue" on the yard signs of a political candidate.
+I find that these associations do exist among the public.
+Specifically, individuals consistently and strongly associate Republicans with the color red and the Democrats with the color Blue.
+As a result, partisan individuals' willingness to vote for a candidate can be dramatically different depending on whether the color used in the yard sign aligns with their partisan identification.
+
+While these two studies highlight endogenous processes between campaigns and voters, to be clear, I am not arguing that either of these patterns only one way.
 In fact, I believe that there is a necessary feedback loop between the parties and their bases of support.
@@
 I leave teasing out directionality for subsequent analyses.
-
-In the [first study](#study-1), I find that individuals do shift their perceptions of political candidates in response to the use of the colors red and blue -- they consistently and strongly associate Republicans with the color red and Democrats with the color blue, and their willingness to vote for a candidate can be dramatically different depending on whether the color used aligns with their partisan identification.
-The [second study](#study-2) suggests that candidates in districts where Democrats have a higher vote share use more blue on their yard signs (while also using less red).
 
@@
 
-```{r}
-#| label: study-1-setup
+In [Study 1](#study-1) I start with testing $H_5$.
+In some informal conversations that I had with political campaign professionals, it became clear that the descriptive evidence connecting the colors red and blue with Republicans and Democrats is still very much based on experience.
 
-# Load some handy functions
-box::use(
-    data.table[...]
-    , modelsummary[
-        datasummary_skim
-        , datasummary_balance
-    ]
-    , ./R/predicted_prob_bar[...]
-)
+> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
+We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
+The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
 
-# Execute the cleaning script
-source("./eda/study_1/cleaning.R")
-# Load fitted models
-load("../data/temp/models/study_1_fitted.RData")
+It appears that campaigns recognize that these are not simply patterns that journalists [see @elving_color_2014] and researchers [see @williams_whats_2022] have picked up on, bit that they are associations held by voters and campaigns respond accordingly:
+
+> Beyond that, I generally suggest that considering associations with party is generally a good place to start.
+For example, if you're running in a Democratic primary and that's the race that's going to most likely decide who ultimately gets elected, then blues are a good place to start.
+
+In the comments above, we see some qualification in that there are other colors that can be useful beyond red and blue.
+Still, a potential implication is that the value of colors associated with a particular place can be a way for candidates to communicate attachment to a district and its constituents.
+Still, there is a preference for campaigns to use as few colors as possible to save on costs -- simpler is better.
+What particularly stood out to me was when I was told:
+
+> You want voters to be able to look at whatever collateral you have, including lawn signs, and be able to identify that it's your material without ever having to read it.
+If you do one thing long enough, voters tend to start to associate specific color schemes with specific candidates.
+
+So, unsurprisingly, campaigns care about how they market themselves.
+And it seems as though campaigns want to tap into quick and efficient information processing for voters and potential voters.
+However, as also noted during the conversation:
+
+> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
+
+Though it appears that at least one consulting firm of campaign marketing professionals recognize the potential value of using the colors red and blue to cue to the partisanship of a candidate, there is still significant uncertainty about how widespread these patterns are with political campaigns in the United States and whether voters actually do make these associations.
+The first piece of empirical evidence in this chapter examines whether we observe systematic patterns between campaigns in the use of the colors red and blue on their yard signs.
+[Study 2](#study-2) then takes my predictions from the snap-judgment model to examine whether these associations exist among voters and what the consequences are.
+
+To gather evidence generalizing the belief that campaigns strategically use the colors red and blue to tap into possible associations of these colors with partisanship, I began by collecting data from the MIT Election Lab that reports the electoral results of the House of Representative elections from the years 1970-2020.
+The data tell me which candidate got how many votes in each House election across the United States.
+With these data, I calculate the rolling 5-year average of the Democratic party's vote share for each district.
+
+Next, I downloaded around 1,000 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design.
+I used the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.
+
+This approach to measure of the proportion of the Republican red and Democrat blue colors takes a lot of the guess work out of manually coding this.
+For example, I downloaded the GOP logo used on the GOP's official Twitter account during the 2022 midterm election cycle.
+To What `OpenCV` does is it loads the image and converts it to a three-dimensional `numpy` array that contains the GBR (reverse of RGB) values for the pixels in the image.
+I standardize the image to be 224 $\times$ 224 pixels.
+The computer is trained to detect the range of the Republican red and Democrat blue colors.
+Once trained, the computer detects the pixels that do not contain values within the pre-specified range and converts those pixels to be black.
+
+```{python}
+#| label: example detection
+#| echo: false
+
+from sys import path # for path management
+from cv2 import imread, imwrite # for color detection
+    #* user-defined
+#path.append("../")
+from PY.helper import colorDetector
+
+# Define colors to detect
+    #* White
+        #** Not defined. Default for colorDetector()
+    #* Red
+republican_red = [232, 27, 35] # target color
+red_lower = [93, 9, 12] # lower end of spectrum for red
+red_higher = [237, 69, 75] # higher end of spectrum for red
+
+# Load gop image to read
+img = imread("./assets/img/gop_2022.png")
+
+# Detect colors
+percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
+
+transformed= imwrite("../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
+
+masked= imwrite("../data/temp/study_2/gop_2022_detected.png", result) # save masked image
 ```
 
-The purpose of [Study 1](#sec-study-1) is to examine whether the color choices on an almost ubiquitous form of campaign branding -- yard signs -- influence people's perceptions of political candidates.
+::: {#fig-color-detection-example layout-ncol="2"}
+![Resized original image](../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
+
+![Masked](../data/temp/study_2/gop_2022_detected.png){#fig-masked}
+
+Detecting colors in the GOP logo
+:::
+
+I then extract the non-black pixels in the array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$]
+
+```{python}
+#| output: asis
+# Print calculated percentage of example
+print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
+```
+
+With the data on the proportion of each of the yard signs using the red and blue colors, I merged these data with the MIT Election Lab Data.
+This left me with data from the House elections between 2018 and 2020.
+While the data are limited in the number of elections they reflect, they allow me to hold the district composition constant, as redistricting occurs after the Census every 10 years.
+However, each district and state is different in their laws surrounding elections, and are different in terms of political context.
+I wanted to examine whether there are meaningful differences between districts that are partisan "strongholds" (Democrats or Republicans tend to get elected in a district) relative to districts that are much less so.
+To do this, I included a model with intercepts with no pooling.
+That is, a model that includes an intercept for each state-district unit.
+Though my outcome of interest (proportion of the yard sign that is red or blue) are continuous (it can take any real number, so not an integer), the outcome is bounded between 0 and 1.
+While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit, introduce systematic error, and lead to results that are quite unstable.
+To not bog down readers with a lot of technical jargon, the model that I end up using is called an ordered beta regression which allows me to efficiently and accurately predict outcomes that can be 0 or 1, or any real number between 0 and 1 [@kubinec_ordered_2022].
+For a more technical discussion about why I choose this over other techniques in the beta regression family, please see the [Appendix](#sec-2-a).
+
+Once I fit these models, I used the `marginaleffects` [@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as explained by the 5-year rolling average Democratic candidates' vote share.
+The grand mean here reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather that I am averaging across all districts to provide a single line in my figure.
+These results are included in @fig-study-2-pred.
+
+```{r}
+#| label: fig-study-2-pred
+#| layout-ncol: 1
+#| fig-cap: More blue on the yard signs in Democratic strongholds
+#| fig-subcap:
+#|   - Proportion of red
+#|   - Proportion of blue
+red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["red"]]
+  , treatment = "Red"
+  , hypothesis = "H5"
+)
+blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["blue"]]
+  , treatment = "Blue"
+  , hypothesis = "H5"
+)
+red
+blue
+```
+
+The results demonstrate that districts where Democrats are historically more successful see yard signs with a lower proportion of red on them, while those same districts see more blue on them.
+Again, these results do not claim that campaigns are doing this either because voters are encouraging them to take this strategy, or that they are doing it as a way to proactively get voters to make these associations.
+To tease out which of those questions is the right one requires more sophisticated approaches and data that could allow me to leverage redistricting (to see how these outcomes change due to some unrelated, external shock).
+The data available to me do not allow me to do that at this time.
+Rather, these data provide evidence consistent with the story I have relayed and the one provided to me in my informal conversations with practitioners.
+
+## Study 2
+
+The purpose of [Study 2](#sec-study-2) is to examine whether the color choices on an almost ubiquitous form of campaign branding -- yard signs -- influence people's perceptions of political candidates.
 Evidence suggests that yard signs *do* matter in shaping political attitudes [@makse_politics_2019], vote intentions [@makse_politics_2019], and even electoral outcomes [@green_effects_2016].
@@
 
-Using yard signs in this study, I test the first four hypotheses I derive from the snap-judgment model.
-First, I test the claim that individuals do indeed notice the color of electoral yard signs.
-Next, I test the claim that these colors that individuals detect influence their evaluations of the yard sign and the candidate represented on it.
-I then test the claim that the effects on perception are moderated by how consistent the color is with the more complex information displayed on the yard sign.
-Finally, [Study 1](#study-1) closes with an examination of whether positive information that contains consistency is processed more quickly than negative or inconsistent information.
+Using yard signs in this study, I test the first four hypotheses I derived from the snap-judgment model.
+First, I tested the claim that individuals do indeed notice the color of electoral yard signs.
+Next, I tested the claim that these colors that individuals detect influence their evaluations of the yard sign and the candidate represented on it.
+I then tested the claim that the effects on perception are moderated by how consistent the color is with the more complex information displayed on the yard sign.
+Finally, [Study 2](#study-2) closes with an examination of whether positive information that contains consistency is processed more quickly than negative or inconsistent information.
 That is, do partisans quickly detect and encode information from a clearly co-partisan political candidate?
@@
 
-I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where individuals are provided with a demographics and political attitudes questionnaire.
-As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
+I recruited participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where individuals are provided with a demographics and political attitudes questionnaire.
+As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly selected half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
 This questionnaire includes common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
@@
 
-I include those questions due to expectations that they may act as confounds for my hypotheses.
-I include some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these correlates with partisan identification [see @campbell_american_1969;@mason_uncivil_2018].
+I included those questions due to expectations that they may act as confounds for my hypotheses.
+I included some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these correlates with partisan identification [see @campbell_american_1969;@mason_uncivil_2018].
 Though political knowledge does predict the strength of an individual's partisan identification [@lodge_rationalizing_2013], attention paid to politics is likely a more important confounding variable for my application.
@@
 
-Additionally, I include a question about the respondent's sex assigned at birth, and importantly, about whether they have received a diagnosis of *any color blindness*.
+Additionally, I included a question about the respondent's sex assigned at birth, and importantly, about whether they have received a diagnosis of *any color blindness*.
 As some individuals may possess undiagnosed colorblindness, asking about their sex assists in covariate balance.
-I additionally include an open-ended question asking participants to describe their "first memory of a political event." The use of open-ended questions helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [@kennedy_strategies_2021].
-Given estimates using these exclusion criteria, I would expect that upwards of 40% of my original sample will fail these attention checks [@kennedy_strategies_2021], thus, the large sample size.
+I additionally included an open-ended question asking participants to describe their "first memory of a political event." The use of open-ended questions helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [@kennedy_strategies_2021].
+Given estimates using these exclusion criteria, I expected that upwards of 40% of my original sample will fail these attention checks [@kennedy_strategies_2021], thus, the large target sample size.
 
-I then present participants with an instruction screen informing them of the task for the experiment.
+I then presented participants with an instruction screen informing them of the task for the experiment.
 In the first trial of the experiment, I randomly presented participants with one of three possible yard signs.
@@
 
-Rather than use eye-tracking devices and software, I instead use Mouseview.js [see @anwyl-irvine_mouseviewjs_2022], which either blocks out or blurs a large portion of the participant's screen and encourages them to move their mouse to view different parts of the screen in isolation.
+Rather than use eye-tracking devices and software, I instead used Mouseview.js [see @anwyl-irvine_mouseviewjs_2022], which either blocks out or blurs a large portion of the participant's screen and encourages them to move their mouse to view different parts of the screen in isolation.
 As the participants move their cursor around the screen, it tracks the coordinates of the cursor along with the "dwell" time of the cursor in that particular coordinate.
@@
 population.
-This means that Mouseview.js is a handy tool for my study.
+This means that Mouseview.js was a handy tool for my study.
 
 When viewing each yard sign in each of the three trials, there is a blur over a substantial portion of the screen.
-At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[I include a screenshot providing an example of what the participants are able to see with the blur included in the [Appendix](#sec-2-a).] Participants move their cursor to explore the yard sign.
-I allot 5000 ms to perform the exploration before the image goes away; this is to encourage a consistent and short duration to explore the image.^[In marketing research, some studies give participants about 6000 ms in eye-tracking studies to examine a brand and formulate an intention to purchase a product or not [@wedel_review_2008].
+At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[I include a screenshot providing an example of what the participants were able to see with the blur included in the [Appendix](#sec-2-a).] Participants move their cursor to explore the yard sign.
+I alloted 5000 ms to perform the exploration before the image disappears; I did this to encourage a consistent and short duration to explore the image.^[In marketing research, some studies give participants about 6000 ms in eye-tracking studies to examine a brand and formulate an intention to purchase a product or not [@wedel_review_2008].
 With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure evoking images uses 1000 ms; but is intended to be an extended amount of time [@anwyl-irvine_mouseviewjs_2022].]
 
-After exploring the image in each trial, I ask participants whether they felt that the candidate supposedly owning the yard sign was a Democrat, a Republican, or Neither.
-After completing the three trials, I ask subjects to indicate their preference among the three images (one from each trial).
+After exploring the image in each trial, I asked participants whether they felt that the candidate supposedly owning the yard sign was a Democrat, a Republican, or Neither.
+After completing the three trials, I asked subjects to indicate their preference among the three images (one from each trial).
 
-To ensure that participants have a standardized initial placement of their cursor, I display a blank page before viewing the yard sign that requires participants to click a "Next" button.
-Immediately after clicking "Next," participants are shown the yard sign.
+To ensure that participants have a standardized initial placement of their cursor, I displayed a blank page before viewing the yard sign that requires participants to click a "Next" button.
+Immediately after clicking "Next," participants were shown the yard sign.
 The goal is to ensure that variation in where participants explore the image is not dependent on a non-standard starting point for their cursor.
-I additionally utilize a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
-The gaussian blur allows participants to see a blurred visual field beyond the cursor.
-This allows participants to see enough to take purposeful action to explore blurred parts of the image that attract them [@anwyl-irvine_mouseviewjs_2022].
-The use of the gaussian blur requires that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_mouseviewjs_2022].
-This will require participants to either switch browsers or to not participate in the study if they are using Safari at the time they are recruited by Prolific to participate in the study.
+I additionally utilized a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
+The gaussian blur allowed participants to see a blurred visual field beyond the cursor.
+This allowed participants to see enough to take purposeful action to explore blurred parts of the image that attract them [@anwyl-irvine_mouseviewjs_2022].
+The use of the gaussian blur required that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_mouseviewjs_2022].
+This required participants to either switch browsers or to not participate in the study if they are using Safari at the time they are recruited by Prolific to participate in the study.
 As this requirement is enforced *before* joining the study, this should not have an effect on the number of excluded participants from my original sample.
@@
 There are two more trials that are much like the first trial.
-What is different between the two latter trials and the first is that I vary the amount of color that is on the yard sign.
+What is different between the two latter trials and the first is that I varied the amount of color that is on the yard sign.
 Examples of all of these yard signs are included in the [Appendix](#sec-2-a).
@@
 To address this first question, I use a couple of proxy measures for people's attention paid to the yard signs.
-I collect the first measure through recording the movement of the subjects' cursors along the x-and-y-axes.
+I collected the first measure through recording the movement of the subjects' cursors along the x-and-y-axes.
 The second measure accounts for the amount of time participants' cursors linger over a particular coordinate on their screen.
@@
 Now, I turn to exploring how features about the subjects themselves may shape the way that individuals interact and respond to this visual information on the yard signs.
-The data on the timing and cursor location is much more noisy than I had originally anticipated.
+The data on the timing and cursor location is much more noisy than I originally anticipated.
 However, as the tests of the next few questions demonstrate, the evidence supports the general conclusion of the systematic differences between individuals that saw either a red, white, or blue yard sign (despite holding everything else but the color constant).
@@
 
-To address the question of whether colors affect perceptions of the candidate and the yard sign, I ask participants to report whether they perceived the candidate to be a partisan -- either a Republican, Democrat, or as non-partisan -- immediately after viewing each image.
+To address the question of whether colors affect perceptions of the candidate and the yard sign, I asked participants to report whether they perceived the candidate to be a partisan -- either a Republican, Democrat, or as non-partisan -- immediately after viewing each image.
 Everything on the yard sign remains constant except for the color.
@@
 When interpreting the error bars, you will want to look at the difference in the error bars *between* yard sign treatments rather than *within* treatment.
-We see that the models indicate statistically meaningful differences between the yard sign treatments for each outcome.
+We see that the models indicate substantive and statistically meaningful differences between the yard sign treatments for each outcome.
 That is, the red and blue yard signs did shift people's perceptions of the partisanship of the candidate relative to the white yard sign.
@@
 
-Digging in a little bit more about what these perceptions were, the predicted probability that subjects perceive the candidate with a red yard sign to be Republican is around 70%, whereas it is only about 30% when viewing a white yard sign.
+Digging in a little bit more about what these perceptions were, the predicted probability that subjects perceived the candidate with a red yard sign to be Republican is around 70%, whereas it is only about 30% when viewing a white yard sign.
 When given a red yard sign, the predicted probability the candidate is marked to be an independent is about 30% and less than 5% to be a Democrat.
@@
 
-As the consistency by which the parties have used either the color red or blue has increased since the 2000's, I suspect that the age of my subjects may moderate this relationship.
+As the consistency by which the parties have used either the color red or blue has increased since the 2000's, I suspected that the age of my subjects may moderate this relationship.
 That is, the tendency for subjects to label red yard signs as a Republican candidate versus a different color may be stronger for those who are younger as the consistency in branding is the political environment they have been around longer.
-I expect this particular relationship may be weaker for older subjects as they may place current branding strategies in a larger political context where this was not always the case.
+I expected this particular relationship may be weaker for older subjects as they may place current branding strategies in a larger political context where this was not always the case.
 
@@
 Those included in the baseline category for both models are those who received the white yard sign treatment.
-Since I believe that age may moderate this effect, I include an interaction term for both of these models that multiplies these treatment indicator variables with age.
+Since I believed that age may moderate this effect, I include an interaction term for both of these models that multiplies these treatment indicator variables with age.
 
@@
 The results do not suggest that they are.
-However, given that I had a very small number of respondents reporting colorblindness in my sample, the lack of substantive or statistical effects may be due to the fact that I do not have enough participants with colorblindness in each group to compare.
+However, given that I had a very small number of respondents reporting colorblindness in my sample, the lack of substantive or statistical effects may be due to the fact that I did recruit enough participants with colorblindness in each group to compare.
 
@@
 This means that the intercept term for the regression would be the predicted probability of the average respondent labeling the owner of the yard sign as either Democrat, Independent, or Republican.
-The conclusions I draw from this regression model do no0t change the ones I make here with @fig-h-2-predictions.
+The conclusions I draw from this regression model do not change the ones I make here with @fig-h-2-predictions.
 
@@
 The design of the latter two trials in the study presents yard signs with mixtures of non-partisan and out-partisan colors.
-For example, I present primarily red (and presumably Republican) yard signs, but with some blue or white in them.
-I expect that the trials that use less "consistent" visual information demonstrate more uncertainty among respondents in their reported perceptions of the candidate's positions.
-Specifically, I expect that participants will perceive the yard signs that have both red and blue on them as more moderate, and that the higher proportion of the color red or blue among the two colors will lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic, respectively.
-This is not to say that I expect the results to change significantly, but rather, that the certainty by which I can predict individuals' guesses of the candidate's partisan affiliation will weaken.
+For example, I presented participants with primarily red (and presumably Republican) yard signs, but with some blue or white in them.
+I expected that the trials that use less "consistent" visual information demonstrate more uncertainty among respondents in their reported perceptions of the candidate's positions.
+Specifically, I expected that participants would perceive the yard signs that have both red and blue on them as more moderate, and that the higher proportion of the color red or blue among the two colors will lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic, respectively.
+This is not to say that I expected the results to change significantly, but rather, that the certainty by which I can predict individuals' guesses of the candidate's partisan affiliation will weaken.
 
@@
 
-The results from these models offer partial support for my expectations.
+The results from these models offer partial support for my pre-registered expectations.
 First I see that yard signs using less blue are not as distinguishably Democratic as the white yard sign.
@@
 One potential reason for this may be the association of the American flag when using all three colors given the Republican party's tendency to condemn those who do not adhere to social norms about showing respect to the American flag.
-This, however, is untestable based on the design of the present study.
+This, however, is untestable based on the design of the study.
 However, what we do see is that there are bounds by which at least the color blue on a yard sign indicates to voters that the candidate is a Democrat.
@@
 @fig-h-3-predictions presents the average predicted probability of supporting a candidate.
-The results fit with my expectations.
+The results fit with my pre-registered expectations.
 First, I see that the predicted probability that a strong Democrat would vote for a candidate with a red yard sign is less than 10% (while for strong republicans it is at about 70%).
@@
 
-The other analytical tasks do not examine expectations derived from the motivated reasoning portion of the model.
+The other analytical tasks do not examine my pre-registered expectations derived from the motivated reasoning portion of the model.
 That is, do people process in-group information faster than out-group information?
@@
 
-To examine whether motivated reasoning is also present in the processing of politically-relevant color, I examine the following: the difference in the amount of time between the start of viewing a stimulus and clicking "Next" to stop viewing the stimulus, among those who were viewing a presumed co-partisan yard sign relative to those viewing a presumed out-partisan yard sign.
+To examine whether my pre-registered expectation that motivated reasoning is also present in the processing of politically-relevant color, I examine the following: the difference in the amount of time between the start of viewing a stimulus and clicking "Next" to stop viewing the stimulus, among those who were viewing a presumed co-partisan yard sign relative to those viewing a presumed out-partisan yard sign.
 As the outcome is a count of the amount of time participants spent looking at a yard sign, I turn to a class of regression models that work well for explaining outcomes measured as count data.^[By the nature of my measure, I do not believe that participants can record a value of 0 as time elapsed is measured in milliseconds.
-Additionally, I expect over-dispersion, as I expect to observe a large bulk of participants recording a very small time elapsed, while for others I expect to record a quite large amount of elapsed time.
+Additionally, I suspect over-dispersion, as I expect to observe a large bulk of participants recording a very small time elapsed, while for others I expect to record a quite large amount of elapsed time.
 In the appendix, @tbl-h-4-dispersion summarizes the time elapsed outcome variable; this demonstrates over-dispersion.
 Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.] I therefore fit two poisson-gamma models (sometimes referred to as negative binomial regressions).
-I am interested in testing whether time elapsed can be explained by not only the color of the yard sign that the subject is viewing, but also whether this effect is moderated by an individual's partisanship.
+I am interested in explaining whether time elapsed can comes not only from the color of the yard sign that the subject is viewing, but also whether this effect is moderated by an individual's partisanship.
 I therefore include an interaction term between stimuli and the partisan identification of the respondent.
@@
 
-## Study 2
-
-[Study 1](#study-1) presents evidence in support of the idea that the colors red and blue matter to politics -- they convey information to people.
-The evidence from [Study 1](#study-1) also suggests that the information may shape the attitudes of voters.
-One thing that remains unclear is whether or not these patterns potentially have large enough impacts that they shape how campaigns market themselves.
-In informal conversations with a campaign marketing firm which specializes in campaign marketing, I was told:
-
-> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
-We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
-The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
-
-While this was good information to hear (that seemed to align with what I found in [Study 1](#study-1)), I wasn't sure how much this actually influenced strategy. It appears it does, however:
-
-> Beyond that, I generally suggest that considering associations with party is generally a good place to start.
-For example, if you're running in a Democratic primary and that's the race that's going to most likely decide who ultimately gets elected, then blues are a good place to start.
-
-In the comments above, we see some qualification in that there are other colors that can be useful beyond red and blue.
-Still, a potential implication is that the value of colors associated with a particular place can be a way for candidates to communicate attachment to a district and its constituents.
-Still, there is a preference for campaigns to use as few colors as possible to save on costs -- simpler is better.
-What particularly stood out to me was when I was told:
-
-> You want voters to be able to look at whatever collateral you have, including lawn signs, and be able to identify that it's your material without ever having to read it.
-If you do one thing long enough, voters tend to start to associate specific color schemes with specific candidates.
-
-So, unsurprisingly, campaigns care about how they market themselves.
-And it seems as though campaigns want to tap into quick and efficient information processing for voters and potential voters.
-However, as also noted during the conversation:
-
-> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
-
-Thus, the goal for the second piece of empirical evidence in this chapter is to explore whether there is any evidence -- outside of the "lab" -- suggesting that campaigns use the colors red and blue systematically.
-If the color of a yard sign does indeed matter, and its electoral effects depend on the perceptions of potential voters, we should expect that campaigns are less likely to place yard signs with a large amount of red or blue in more moderate districts.
-However, in districts where there is a strong partisan base, we should expect that the candidate of the popular party will use the party's color more, while the disadvantaged candidate will use their party's color less as a way to either play up or down their loyalty to their party.
-
-To evaluate this, I begin by collecting data from the MIT Election Lab that reports the electoral results of the House of Representative elections from the years 1970-2020.
-The data here tell me which candidate got how many votes in each House election across the United States.
-With these data, I calculate the rolling 5-year average of the Democratic party's vote share for each district.
-
-Next, I download around 1,000 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design.
-I use the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.
-
-This approach to measure of the proportion of the Republican red and Democrat blue colors takes a lot of the guess work out of manually coding this.
-For example, I downloaded the GOP logo used on the GOP's official Twitter account during the 2022 midterm election cycle.
-To What `OpenCV` does is it loads the image and converts it to a three-dimensional `numpy` array that contains the GBR (reverse of RGB) values for the pixels in the image.
-I standardize the image to be 224 $\times$ 224 pixels.
-The computer is trained to detect the range of the Republican red and Democrat blue colors.
-Once trained, the computer detects the pixels that do not contain values within the pre-specified range and converts those pixels to be black.
-
-```{python}
-#| label: example detection
-#| echo: false
-
-from sys import path # for path management
-from cv2 import imread, imwrite # for color detection
-    #* user-defined
-#path.append("../")
-from PY.helper import colorDetector
-
-# Define colors to detect
-    #* White
-        #** Not defined. Default for colorDetector()
-    #* Red
-republican_red = [232, 27, 35] # target color
-red_lower = [93, 9, 12] # lower end of spectrum for red
-red_higher = [237, 69, 75] # higher end of spectrum for red
-
-# Load gop image to read
-img = imread("./assets/img/gop_2022.png")
-
-# Detect colors
-percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
-
-transformed= imwrite("../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
-
-masked= imwrite("../data/temp/study_2/gop_2022_detected.png", result) # save masked image
-```
-
-::: {#fig-color-detection-example layout-ncol="2"}
-![Resized original image](../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
-
-![Masked](../data/temp/study_2/gop_2022_detected.png){#fig-masked}
-
-Detecting colors in the GOP logo
-:::
-
-I then extract the non-black pixels in the array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$]
-
-```{python}
-#| output: asis
-# Print calculated percentage of example
-print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
-```
-
-With the data on the proportion of each of the yard signs using the red and blue colors, I merge this data with the MIT Election Lab Data.
-This leaves me with data from the House elections between 2018 and 2020.
-While the data are limited in the number of elections they reflect, they allow me to hold the district composition constant, as redistricting occurs after the Census every 10 years.
-However, each district and state is different in their laws surrounding elections, and are different in terms of political context.
-I want to examine whether there are meaningful differences between districts that are partisan "strongholds" (Democrats or Republicans tend to get elected in a district) relative to districts that are much less so.
-To do this, I include a model with intercepts with no pooling.
-That is, a model that includes an intercept for each state-district unit.
-Though my outcome of interest (proportion of the yard sign that is red or blue) are continuous (it can take any real number, so not an integer), the outcome is bounded between 0 and 1.
-While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit, introduce systematic error, and lead to results that are quite unstable.
-To not bog down readers with a lot of technical jargon, the model that I end up using is called an ordered beta regression which allows me to efficiently and accurately predict outcomes that can be 0 or 1, or any real number between 0 and 1 [@kubinec_ordered_2022].
-For a more technical discussion about why I choose this over other techniques in the beta regression family, please see the [Appendix](#sec-2-a).
-
-Once I have fit these models, I use the `marginaleffects` [@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as explained by the 5-year rolling average Democratic candidates' vote share.
-The grand mean here reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather that I am averaging across all districts to provide a single line in my figure.
-These results are included in @fig-study-2-pred.
-
-```{r}
-#| label: fig-study-2-pred
-#| layout-ncol: 1
-#| fig-cap: More blue on the yard signs in Democratic strongholds
-#| fig-subcap:
-#|   - Proportion of red
-#|   - Proportion of blue
-red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["red"]]
-  , treatment = "Red"
-  , hypothesis = "H5"
-)
-blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["blue"]]
-  , treatment = "Blue"
-  , hypothesis = "H5"
-)
-red
-blue
-```
-
-The results demonstrate that districts where Democrats are historically more successful see yard signs with a lower proportion of red on them, while those same districts see more blue on them.
-Again, these results do not claim that campaigns are doing this either because voters are encouraging them to take this strategy, or that they are doing it as a way to proactively get voters to do it.
-To tease out which of those questions is the right one requires more sophisticated approaches and data that could allow me to leverage redistricting (to see how these outcomes change due to some unrelated, external shock).
-The data available to me do not allow me to do that at this time.
-Rather, these data provide evidence consistent with the story I have relayed, and motivate further the study of color as it relates to politics.
-
 ## Conclusions
@@
 
+Campaigns appear to systematically use the colors red and blue at different rates depending on whether the district is more "up for grabs" or whether it is a partisan stronghold.
+Specifically, my first study suggests that campaigns use more blue on their yard signs in districts that have a higher vote share for Democrats in the five previous years, and use red much less often in these same circumstances.
+This fits with the strategies communicated to me by a campaign marketing firm.
+Another question coming from that conversation and the existing literature was whether voters actually make these associations.
+
 Evidence from my experiment suggests that the use of the colors red and blue convey partisan information, while a third color like white provides very little useful political information.
@@
 
-Since it appears that colors can influence vote choice, I then turn to data that incorporate real world messiness to examine whether or not campaigns are responsive to such patterns.
-It appears that they are.
-The empirical evidence suggest that campaigns use more blue on their yard signs if it is a district that has a higher vote share for Democrats the five previous years, and use red much less often in those same circumstances.
-This fits with strategies communicated to me by a campaign marketing firm.
-
 Having established some baseline findings, in the next chapter I examine whether the snap-judgment model holds up in more complex settings.
 Specifically, I next move to consider whether color can shape how we have conversations about politics with others, as well as the degree to which color can be a tool inhibiting political persuasion.
+
+# References
+
+::: {#refs}
+
+:::
+
+{{< include appendix.qmd >}}

### 2023-09-27 chapter_2/src/slides/slides.qmd
updating slides

--- 2023-09-20 chapter_2/src/slides/slides.qmd
@@
 
+### Borrowing concepts from social neuroscience and psychology
+
+---
+
+- Memories:
+  -  are multi-dimensional encodings of previous experiences [CITATION]
+    - e.g., remember giving your first job talk
+      - the layout of the room
+      - the colors of the chairs
+      - what the room smelled like
+      - what ambient sounds were there
+      - how you felt
+  - affectively laden [CITATION]
+  - easier retrieved when recent and/or shares multiple commonalities with current object
+
 ### Zaller's [-@zaller_1992_cup] Memory model
@@
 
+### Motivation of Study
+
+---
+
+> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
+We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
+The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
+
+---
+
+> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
+
+---
+
+- Do these associations have systematic influences on campaign strategy? (Study 1)
+- Are these hunches correct that these colors can reliably cue partisanship? (Study 2)
+
+### Outcome variable - How much red and blue do campaigns use?
+
+---
+
+- Collect around 1,000 yard signs from House elections
+  - 2016-2024
+- Measuring the colors used on a yard sign:
+  - Use a machine learning Python Library, `OpenCV`, that reads images and classifies their components.
+    - Trained to classify each pixel in the image
+    - Classifies it based on BGR value (reverse of RGB)
+    - Looks for a range of values around the "Republican red" and "Democratic blue"
+
+---
+
+```{python}
+#| label: example detection
+#| echo: false
+
+from sys import path # for path management
+from cv2 import imread, imwrite # for color detection
+    #* user-defined
+sys.path.append("../")
+from PY.helper import colorDetector
+
+# Define colors to detect
+    #* White
+        #** Not defined. Default for colorDetector()
+    #* Red
+republican_red = [232, 27, 35] # target color
+red_lower = [93, 9, 12] # lower end of spectrum for red
+red_higher = [237, 69, 75] # higher end of spectrum for red
+
+# Load gop image to read
+img = imread("../assets/img/gop_2022.png")
+
+# Detect colors
+percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
+
+transformed= imwrite("../../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
+
+masked= imwrite("../../data/temp/study_2/gop_2022_detected.png", result) # save masked image
+```
+
+::: {#fig-color-detection-example layout-ncol="2"}
+![Resized original image](../../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
+
+![Masked](../../data/temp/study_2/gop_2022_detected.png){#fig-masked}
+
+Detecting colors in the GOP logo
+:::
+
+```{python}
+#| output: asis
+# Print calculated percentage of example
+print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
+```
+
+### Predictor variable - What is the partisan composition of the district?
+
+---
+
+- MIT Election Lab data
+  - House election results
+  - 1970-2020
+- Measuring partisan composition of district:
+  - Calculate rolling 5-year average of the Democratic party's vote share for each district
+
+### Do campaigns use a different proportion of the colors red and blue based on partisan composition?
+
+---
+
+```{r}
+#| label: fig-study-2-pred
+#| layout-ncol: 1
+#| fig-cap: More blue on the yard signs in Democratic strongholds
+#| fig-subcap:
+#|   - Proportion of red
+#|   - Proportion of blue
+red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["red"]]
+  , treatment = "Red"
+  , hypothesis = "H5"
+)
+blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["blue"]]
+  , treatment = "Blue"
+  , hypothesis = "H5"
+)
+red
+blue
+```
+
+## Study 2
+
 ### Motivation of the experiment
@@
   , legend_title = "Treatment"
-)
-red
-blue
-```
-
-## Study 2
-
-### Motivation of Study
-
----
-
-> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
-We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
-The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
-
----
-
-> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
-
----
-
-- Do these associations have systematic influences on campaign strategy?
-
-### Outcome variable - How much red and blue do campaigns use?
-
----
-
-- Collect around 1,000 yard signs from House elections
-  - 2016-2024
-- Measuring the colors used on a yard sign:
-  - Use a machine learning Python Library, `OpenCV`, that reads images and classifies their components.
-    - Trained to classify each pixel in the image
-    - Classifies it based on BGR value (reverse of RGB)
-    - Looks for a range of values around the "Republican red" and "Democratic blue"
-
----
-
-```{python}
-#| label: example detection
-#| echo: false
-
-from sys import path # for path management
-from cv2 import imread, imwrite # for color detection
-    #* user-defined
-sys.path.append("../")
-from PY.helper import colorDetector
-
-# Define colors to detect
-    #* White
-        #** Not defined. Default for colorDetector()
-    #* Red
-republican_red = [232, 27, 35] # target color
-red_lower = [93, 9, 12] # lower end of spectrum for red
-red_higher = [237, 69, 75] # higher end of spectrum for red
-
-# Load gop image to read
-img = imread("../assets/img/gop_2022.png")
-
-# Detect colors
-percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
-
-transformed= imwrite("../../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
-
-masked= imwrite("../../data/temp/study_2/gop_2022_detected.png", result) # save masked image
-```
-
-::: {#fig-color-detection-example layout-ncol="2"}
-![Resized original image](../../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
-
-![Masked](../../data/temp/study_2/gop_2022_detected.png){#fig-masked}
-
-Detecting colors in the GOP logo
-:::
-
-```{python}
-#| output: asis
-# Print calculated percentage of example
-print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
-```
-
-### Predictor variable - What is the partisan composition of the district?
-
----
-
-- MIT Election Lab data
-  - House election results
-  - 1970-2020
-- Measuring partisan composition of district:
-  - Calculate rolling 5-year average of the Democratic party's vote share for each district
-
-### Do campaigns use a different proportion of the colors red and blue based on partisan composition?
-
----
-
-```{r}
-#| label: fig-study-2-pred
-#| layout-ncol: 1
-#| fig-cap: More blue on the yard signs in Democratic strongholds
-#| fig-subcap:
-#|   - Proportion of red
-#|   - Proportion of blue
-red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["red"]]
-  , treatment = "Red"
-  , hypothesis = "H5"
-)
-blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["blue"]]
-  , treatment = "Blue"
-  , hypothesis = "H5"
 )

### 2023-09-27 chapter_2/src/slides/slides.qmd
a slight tweak to the slides and updating gitignore

--- 2023-09-22 chapter_2/src/slides/slides.qmd
@@
   revealjs: 
-    multiplex: true
     embed-resources: true
@@
   freeze: true
+  cache: true
+nocite: |
+  @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017,
 ---
@@
 
+### Borrowing concepts from social neuroscience and psychology
+
+---
+
+- Memories:
+  -  are multi-dimensional encodings of previous experiences [@fazio_attitudes_2007]
+    - e.g., remember giving your first job talk
+      - the layout of the room
+      - the colors of the chairs
+      - what the room smelled like
+      - what ambient sounds were there
+      - how you felt
+  - affectively laden [@fazio_attitudes_2007;@winkielman_emotion_2011; @kensinger_affective_2022]
+  - easier retrieved when recent and/or shares multiple commonalities with current object
+
 ### Zaller's [-@zaller_1992_cup] Memory model
@@
 
+### Motivation of Study
+
+---
+
+> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
+We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
+The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
+
+---
+
+> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
+
+---
+
+- Do these associations have systematic influences on campaign strategy? (Study 1)
+- Are these hunches correct that these colors can reliably cue partisanship? (Study 2)
+
+### Outcome variable - How much red and blue do campaigns use?
+
+---
+
+- Collect around 1,000 yard signs from House elections
+  - 2016-2024
+- Measuring the colors used on a yard sign:
+  - Use a machine learning Python Library, `OpenCV` [@bradski_opencv_2000], that reads images and classifies their components.
+    - Trained to classify each pixel in the image
+    - Classifies it based on BGR value (reverse of RGB)
+    - Looks for a range of values around the "Republican red" and "Democratic blue"
+
+---
+
+```{python}
+#| label: example detection
+#| echo: false
+
+from sys import path # for path management
+from cv2 import imread, imwrite # for color detection
+    #* user-defined
+sys.path.append("../")
+from PY.helper import colorDetector
+
+# Define colors to detect
+    #* White
+        #** Not defined. Default for colorDetector()
+    #* Red
+republican_red = [232, 27, 35] # target color
+red_lower = [93, 9, 12] # lower end of spectrum for red
+red_higher = [237, 69, 75] # higher end of spectrum for red
+
+# Load gop image to read
+img = imread("../assets/img/gop_2022.png")
+
+# Detect colors
+percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
+
+transformed= imwrite("../../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
+
+masked= imwrite("../../data/temp/study_2/gop_2022_detected.png", result) # save masked image
+```
+
+::: {#fig-color-detection-example layout-ncol="2"}
+![Resized original image](../../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
+
+![Masked](../../data/temp/study_2/gop_2022_detected.png){#fig-masked}
+
+Detecting colors in the GOP logo
+:::
+
+```{python}
+#| output: asis
+# Print calculated percentage of example
+print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
+```
+
+### Predictor variable - What is the partisan composition of the district?
+
+---
+
+- MIT Election Lab data
+  - House election results
+  - 1970-2020
+- Measuring partisan composition of district:
+  - Calculate rolling 5-year average of the Democratic party's vote share for each district
+
+### Do campaigns use a different proportion of the colors red and blue based on partisan composition?
+
+---
+
+```{r}
+#| label: fig-study-2-pred
+#| layout-ncol: 1
+#| fig-cap: More blue on the yard signs in Democratic strongholds
+#| fig-subcap:
+#|   - Proportion of red
+#|   - Proportion of blue
+red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["red"]]
+  , treatment = "Red"
+  , hypothesis = "H5"
+)
+blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["blue"]]
+  , treatment = "Blue"
+  , hypothesis = "H5"
+)
+red
+blue
+```
+
+## Study 2
+
 ### Motivation of the experiment
@@
 - Within each trial, participants have $\frac{1}{3}$ chance of seeing any given yard sign.
-- MouseView.js
+- MouseView.js [@anwyl-irvine_mouseviewjs_2022]
 

### 2023-09-27 chapter_2/src/slides/slides.qmd
updating some theming stuff with the slides

@@
     slide-level: 5
-    bibliography: ../../../assets/references.bib   
+    bibliography: ../../../assets/candidate_support_chapter_references.bib   
     self-contained: true
@@
 
-### Zaller's [-@zaller_1992_cup] Memory model
+### Zaller's [-@zaller_nature_1992] Memory model
 
@@
 
-### Lodge and Taber's [-@lodge_taber_2013_cup] Online model
+### Lodge and Taber's [-@lodge_rationalizing_2013] Online model
 

### 2023-09-27 chapter_2/src/slides/slides.qmd
update slides

@@
 
+## Follow-along
+
+![QR Code](../../assets/slides/imgs/qr-code.png){#fig-qr}
+
 ## Visual politics is not new politics, but "hot" politics
@@
 
-[![1860s Ballots](../../assets/slides/imgs/ballots.avif){#fig-ballots width=6.5in}](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)
+![[1860s Ballots](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)](../../assets/slides/imgs/ballots.avif){#fig-1860-ballot}
 
@@
 
-[![Democratic National Convention](../../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem width=6.5in}](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)
-
-[![Republican National Convention](../../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep width=6.5in}](https://reuther.wayne.edu/node/9207)
+![[Democratic National Convention](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)](../../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem width=6.5in}
+
+![[Republican National Convention]((../../assets/slides/imgs/1980_rep_convention.jpg))](../../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep width=6.5in}
 
@@
 
-[![2000 Presidential Election map](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=6.5in}](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)
+![[2000 Presidential Election Map](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=6.5in}
 
@@
 
-[![The public](../../assets/slides/imgs/division.webp){#fig-public width=6.5in}](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)
+![[The public](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)](../../assets/slides/imgs/division.webp){#fig-public width=6.5in}
 

### 2023-09-28 chapter_2/src/manuscript.qmd

@@
 -->
+
+```{r}
+#| label: r-setup-block
+
+# Load some handy functions
+box::use(
+    data.table[...]
+    , modelsummary[
+        datasummary_skim
+        , datasummary_balance
+    ]
+    , ./R/predicted_prob_bar[...]
+)
+
+# Execute the cleaning script
+source("./eda/study_1/cleaning.R")
+# Load fitted models
+load("../data/temp/models/study_1_fitted.RData")
+```
 
@@
 
-From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that colors observed shape perceptions about the person and ideological symbol represented in the branding -- this means that individuals express different levels of preference for receiving more information that is consistent with their preferences ($H_{2}$); that the consistency of information explains more positive perceptions (i.e., simple visual information paired with more complex "traditional" information) ($H_{3}$); positive and consistent information is processed more quickly than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) -- this is inline with their primary objective of reelection [@fenno_congressmen_1973;@mayhew_congress_1974].
+From this discussion, I developed the following pre-registered hypotheses: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that colors observed shape perceptions about the person and ideological symbol represented in the branding -- this means that individuals express different levels of preference for receiving more information that is consistent with their preferences ($H_{2}$); that the consistency of information explains more positive perceptions (i.e., simple visual information paired with more complex "traditional" information) ($H_{3}$); positive and consistent information is processed more quickly than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) -- this is inline with their primary objective of reelection [@fenno_congressmen_1973;@mayhew_congress_1974].
 A summary of these hypotheses is presented in @tbl-hypotheses.
@@
 
-```{r}
-#| label: study-1-setup
+In [Study 1](#study-1) I start with testing $H_5$.
+In some informal conversations that I had with political campaign professionals, it became clear that the descriptive evidence connecting the colors red and blue with Republicans and Democrats is still very much based on experience.
 
-# Load some handy functions
-box::use(
-    data.table[...]
-    , modelsummary[
-        datasummary_skim
-        , datasummary_balance
-    ]
-    , ./R/predicted_prob_bar[...]
-)
+> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
+We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
+The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
 
-# Execute the cleaning script
-source("./eda/study_1/cleaning.R")
-# Load fitted models
-load("../data/temp/models/study_1_fitted.RData")
+It appears that campaigns recognize that these are not simply patterns that journalists [see @elving_color_2014] and researchers [see @williams_whats_2022] have picked up on, bit that they are associations held by voters and campaigns respond accordingly:
+
+> Beyond that, I generally suggest that considering associations with party is generally a good place to start.
+For example, if you're running in a Democratic primary and that's the race that's going to most likely decide who ultimately gets elected, then blues are a good place to start.
+
+In the comments above, we see some qualification in that there are other colors that can be useful beyond red and blue.
+Still, a potential implication is that the value of colors associated with a particular place can be a way for candidates to communicate attachment to a district and its constituents.
+Still, there is a preference for campaigns to use as few colors as possible to save on costs -- simpler is better.
+What particularly stood out to me was when I was told:
+
+> You want voters to be able to look at whatever collateral you have, including lawn signs, and be able to identify that it's your material without ever having to read it.
+If you do one thing long enough, voters tend to start to associate specific color schemes with specific candidates.
+
+So, unsurprisingly, campaigns care about how they market themselves.
+And it seems as though campaigns want to tap into quick and efficient information processing for voters and potential voters.
+However, as also noted during the conversation:
+
+> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
+
+Though it appears that at least one consulting firm of campaign marketing professionals recognize the potential value of using the colors red and blue to cue to the partisanship of a candidate, there is still significant uncertainty about how widespread these patterns are with political campaigns in the United States and whether voters actually do make these associations.
+The first piece of empirical evidence in this chapter examines whether we observe systematic patterns between campaigns in the use of the colors red and blue on their yard signs.
+[Study 2](#study-2) then takes my predictions from the snap-judgment model to examine whether these associations exist among voters and what the consequences are.
+
+To gather evidence generalizing the belief that campaigns strategically use the colors red and blue to tap into possible associations of these colors with partisanship, I began by collecting data from the MIT Election Lab that reports the electoral results of the House of Representative elections from the years 1970-2020.
+The data tell me which candidate got how many votes in each House election across the United States.
+With these data, I calculated the rolling 5-year average of the Democratic party's vote share for each district.
+
+Next, I downloaded around 1,000 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design.
+I used the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.
+
+This approach to measure of the proportion of the Republican red and Democrat blue colors takes a lot of the guess work out of manually coding this.
+For example, I downloaded the GOP logo used on the GOP's official Twitter account during the 2022 midterm election cycle.
+To What `OpenCV` does is it loads the image and converts it to a three-dimensional `numpy` array that contains the GBR (reverse of RGB) values for the pixels in the image.
+I standardize the image to be 224 $\times$ 224 pixels.
+The computer is trained to detect the range of the Republican red and Democrat blue colors.
+Once trained, the computer detects the pixels that do not contain values within the pre-specified range and converts those pixels to be black.
+
+```{python}
+#| label: example detection
+#| echo: false
+
+from sys import path # for path management
+from cv2 import imread, imwrite # for color detection
+    #* user-defined
+#path.append("../")
+from PY.helper import colorDetector
+
+# Define colors to detect
+    #* White
+        #** Not defined. Default for colorDetector()
+    #* Red
+republican_red = [232, 27, 35] # target color
+red_lower = [93, 9, 12] # lower end of spectrum for red
+red_higher = [237, 69, 75] # higher end of spectrum for red
+
+# Load gop image to read
+img = imread("./assets/img/gop_2022.png")
+
+# Detect colors
+percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
+
+transformed= imwrite("../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
+
+masked= imwrite("../data/temp/study_2/gop_2022_detected.png", result) # save masked image
 ```
 
-The purpose of [Study 1](#sec-study-1) is to examine whether the color choices on an almost ubiquitous form of campaign branding -- yard signs -- influence people's perceptions of political candidates.
+::: {#fig-color-detection-example layout-ncol="2"}
+![Resized original image](../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
+
+![Masked](../data/temp/study_2/gop_2022_detected.png){#fig-masked}
+
+Detecting colors in the GOP logo
+:::
+
+I then extract the non-black pixels in the array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$]
+
+```{python}
+#| output: asis
+# Print calculated percentage of example
+print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
+```
+
+With the data on the proportion of each of the yard signs using the red and blue colors, I merged these data with the MIT Election Lab Data.
+This left me with data from the House elections between 2018 and 2020.
+While the data are limited in the number of elections they reflect, they allow me to hold the district composition constant, as redistricting occurs after the Census every 10 years.
+However, each district and state is different in their laws surrounding elections, and are different in terms of political context.
+I wanted to examine whether there are meaningful differences between districts that are partisan "strongholds" (Democrats or Republicans tend to get elected in a district) relative to districts that are much less so.
+To do this, I included a model with intercepts with no pooling.
+That is, a model that includes an intercept for each state-district unit.
+Though my outcome of interest (proportion of the yard sign that is red or blue) are continuous (it can take any real number, so not an integer), the outcome is bounded between 0 and 1.
+While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit, introduce systematic error, and lead to results that are quite unstable.
+To not bog down readers with a lot of technical jargon, the model that I end up using is called an ordered beta regression which allows me to efficiently and accurately predict outcomes that can be 0 or 1, or any real number between 0 and 1 [@kubinec_ordered_2022].
+For a more technical discussion about why I choose this over other techniques in the beta regression family, please see the [Appendix](#sec-2-a).
+
+Once I fit these models, I used the `marginaleffects` [@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as explained by the 5-year rolling average Democratic candidates' vote share.
+The grand mean here reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather that I am averaging across all districts to provide a single line in my figure.
+These results are included in @fig-study-2-pred.
+
+```{r}
+#| label: fig-study-2-pred
+#| layout-ncol: 1
+#| fig-cap: More blue on the yard signs in Democratic strongholds
+#| fig-subcap:
+#|   - Proportion of red
+#|   - Proportion of blue
+red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["red"]]
+  , treatment = "Red"
+  , hypothesis = "H5"
+)
+blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["blue"]]
+  , treatment = "Blue"
+  , hypothesis = "H5"
+)
+red
+blue
+```
+
+The results demonstrate that districts where Democrats are historically more successful see yard signs with a lower proportion of red on them, while those same districts see more blue on them.
+Again, these empirical results do not claim that campaigns are doing this either because voters are encouraging them to take this strategy, or that they are doing it as a way to proactively get voters to make these associations.
+My informal conversation does seem to indicate that campaigns are responding to associations that exist in the brains of voters already as opposed to undertaking efforts to generate such associations or to strengthen them.
+Though my empirical evidence is consistent with the argument that campaigns systematically vary in their use of color depending on electoral context, it remains descriptive and I cannot directly test "strategy." To tease out which of those questions is the right one requires more sophisticated approaches and data that could allow me to leverage redistricting (to see how these outcomes change due to some unrelated, external shock).
+The data available to me do not allow me to do that at this time.
+While this is a useful way to understand how these associations of the colors red and blue with Republicans and Democrats exist at a macro-level, this project is fundamentally curious about how these associations have come to be formed among the public and what their consequences are for attitude expression and behavior.
+[Study 2](#study-2) is a test of these central questions in the context of elections.
+
+## Study 2
+
+The purpose of [Study 2](#sec-study-2) is to examine whether the color choices on an almost ubiquitous form of campaign branding -- yard signs -- influence people's perceptions of political candidates.
 Evidence suggests that yard signs *do* matter in shaping political attitudes [@makse_politics_2019], vote intentions [@makse_politics_2019], and even electoral outcomes [@green_effects_2016].
@@
 
-Using yard signs in this study, I test the first four hypotheses I derive from the snap-judgment model.
+Using yard signs in this study, I test the first four hypotheses I derived from the snap-judgment model.
 First, I test the claim that individuals do indeed notice the color of electoral yard signs.
@@
 I then test the claim that the effects on perception are moderated by how consistent the color is with the more complex information displayed on the yard sign.
-Finally, [Study 1](#study-1) closes with an examination of whether positive information that contains consistency is processed more quickly than negative or inconsistent information.
+Finally, [Study 2](#study-2) closes with an examination of whether positive information that contains consistency is processed more quickly than negative or inconsistent information.
 That is, do partisans quickly detect and encode information from a clearly co-partisan political candidate?
@@
 
-I recruit participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where individuals are provided with a demographics and political attitudes questionnaire.
-As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly select half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
-This questionnaire includes common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
+I recruited participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where individuals are provided with a demographics and political attitudes questionnaire.
+As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly selected half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
+This questionnaire included common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
 
-[^color_influence_pre-reg_anon-3]: I pay subjects a rate of \$12.00 per hour. On top of the price per participant, Prolific charges a 30% servicing fee.
+[^color_influence_pre-reg_anon-3]: I paid subjects a rate of \$12.00 per hour. On top of the price per participant, Prolific charged a 30% servicing fee.
 
 [^color_influence_pre-reg_anon-4]: Pavolovia allows for researchers to host and run open source experiments for about \$0.20 per participant (to cover their server costs).
-I use it primarily to integrate the JavaScript components from the jsPsych package [@leeuw_jspsych_2015] for my experimental design.
+I used it primarily to integrate the JavaScript components from the jsPsych package [@leeuw_jspsych_2015] for my experimental design.
 
-I include those questions due to expectations that they may act as confounds for my hypotheses.
-I include some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these correlates with partisan identification [see @campbell_american_1969;@mason_uncivil_2018].
+I included those questions due to expectations that they may act as confounds for my hypotheses.
+I included some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these correlates with partisan identification [see @campbell_american_1969;@mason_uncivil_2018].
 Though political knowledge does predict the strength of an individual's partisan identification [@lodge_rationalizing_2013], attention paid to politics is likely a more important confounding variable for my application.
@@
 population.
-This means that Mouseview.js is a handy tool for my study.
+This means that Mouseview.js was a handy tool for my study.
 
-When viewing each yard sign in each of the three trials, there is a blur over a substantial portion of the screen.
-At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[I include a screenshot providing an example of what the participants are able to see with the blur included in the [Appendix](#sec-2-a).] Participants move their cursor to explore the yard sign.
-I allot 5000 ms to perform the exploration before the image goes away; this is to encourage a consistent and short duration to explore the image.^[In marketing research, some studies give participants about 6000 ms in eye-tracking studies to examine a brand and formulate an intention to purchase a product or not [@wedel_review_2008].
+When viewing each yard sign in each of the three trials, I placed a blur over a substantial portion of the screen.
+At any given point in time, participants could view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[I include a screenshot providing an example of what the participants were able to see with the blur included in the [Appendix](#sec-2-a).] Participants moved their cursor to explore the yard sign.
+I alloted 5000 ms to perform the exploration before the image disappears; I did this to encourage a consistent and short duration to explore the image.^[In marketing research, some studies give participants about 6000 ms in eye-tracking studies to examine a brand and formulate an intention to purchase a product or not [@wedel_review_2008].
 With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure evoking images uses 1000 ms; but is intended to be an extended amount of time [@anwyl-irvine_mouseviewjs_2022].]
 
-After exploring the image in each trial, I ask participants whether they felt that the candidate supposedly owning the yard sign was a Democrat, a Republican, or Neither.
-After completing the three trials, I ask subjects to indicate their preference among the three images (one from each trial).
+After exploring the image in each trial, I asked participants whether they felt that the candidate supposedly owning the yard sign was a Democrat, a Republican, or Neither.
+After completing the three trials, I asked subjects to indicate their preference among the three images (one from each trial).
 
-To ensure that participants have a standardized initial placement of their cursor, I display a blank page before viewing the yard sign that requires participants to click a "Next" button.
-Immediately after clicking "Next," participants are shown the yard sign.
+To ensure that participants have a standardized initial placement of their cursor, I displayed a blank page before viewing the yard sign that requires participants to click a "Next" button.
+Immediately after clicking "Next," participants were shown the yard sign.
 The goal is to ensure that variation in where participants explore the image is not dependent on a non-standard starting point for their cursor.
-I additionally utilize a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
-The gaussian blur allows participants to see a blurred visual field beyond the cursor.
-This allows participants to see enough to take purposeful action to explore blurred parts of the image that attract them [@anwyl-irvine_mouseviewjs_2022].
-The use of the gaussian blur requires that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_mouseviewjs_2022].
-This will require participants to either switch browsers or to not participate in the study if they are using Safari at the time they are recruited by Prolific to participate in the study.
+I additionally utilized a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
+The gaussian blur allowed participants to see a blurred visual field beyond the cursor.
+This allowed participants to see enough to take purposeful action to explore blurred parts of the image that attracted them [@anwyl-irvine_mouseviewjs_2022].
+The use of the gaussian blur required that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_mouseviewjs_2022].
+This required participants to either switch browsers or to not participate in the study if they are using Safari at the time they are recruited by Prolific to participate in the study.
 As this requirement is enforced *before* joining the study, this should not have an effect on the number of excluded participants from my original sample.
 
-There are two more trials that are much like the first trial.
-What is different between the two latter trials and the first is that I vary the amount of color that is on the yard sign.
+There were two more trials that are much like the first trial.
+What was different between the two latter trials and the first is that I varied the amount of color that is on the yard sign.
 Examples of all of these yard signs are included in the [Appendix](#sec-2-a).
@@
 About 40% of the sample identifies as female, and about 70% of the sample identifies as White (while only 10% report being Hispanic and Black).
-The average respondent in the sample reports leaning Democratic.
+The average respondent in the sample reported leaning Democratic.
 
@@
 
-To address this first question, I use a couple of proxy measures for people's attention paid to the yard signs.
-I collect the first measure through recording the movement of the subjects' cursors along the x-and-y-axes.
-The second measure accounts for the amount of time participants' cursors linger over a particular coordinate on their screen.
+To address this first question, I used a couple of proxy measures for people's attention paid to the yard signs.
+I collected the first measure through recording the movement of the subjects' cursors along the x-and-y-axes.
+The second measure accounted for the amount of time participants' cursors linger over a particular coordinate on their screen.
 Presumably, the more participants explore the yard sign, the more they are finding visual information that they can use to evaluate the candidate.
@@
 
-Since it appears that colors can influence vote choice, I then turn to data that incorporate real world messiness to examine whether or not campaigns are responsive to such patterns.
-It appears that they are.
-The empirical evidence suggest that campaigns use more blue on their yard signs if it is a district that has a higher vote share for Democrats the five previous years, and use red much less often in those same circumstances.
-This fits with strategies communicated to me by a campaign marketing firm.
-
 Having established some baseline findings, in the next chapter I examine whether the snap-judgment model holds up in more complex settings.

### 2023-09-28 chapter_2/src/slides/slides.qmd
removing an extra return

@@
   freeze: true
-  cache: true
 nocite: |

### 2023-10-03 chapter_2/src/slides/slides.qmd
updating the slides some more

@@
 
-## Follow-along
-
 ![QR Code](../../assets/slides/imgs/qr-code.png){#fig-qr}
 
-## Visual politics is not new politics, but "hot" politics
+---
+
+```{r}
+#| label: fig-hook-1
+#| fig-cap: Probability of voting for candidate with red yard sign versus white
+#| 
+red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_3"]][["red"]]
+  , x_axis = "trial_1_red_stimuli"
+  , treatment = "Red"
+  , hypothesis = "H3"
+  , x_label = "Party ID"
+  , y_label = "Pr(Vote for candidate)"
+  , legend_title = "Treatment"
+)
+
+red
+```
+
+---
+
+```{r}
+#| label: fig-hook-2
+#| fig-cap: Probability of voting for candidate with blue yard sign versus white
+blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_3"]][["blue"]]
+  , x_axis = "trial_1_blue_stimuli"
+  , treatment = "Blue"
+  , hypothesis = "H3"
+  , x_label = "Party ID"
+  , y_label = "Pr(Vote for candidate)"
+  , legend_title = "Treatment"
+)
+blue
+```
+
+## How are colors used in politics?
 
@@
 
----
-
-```{r}
-#| label: sim-visualization-online
-
-df <- fabricatr::fabricate(
-  N = 10000,
-  pop = rnorm(n = N, mean = 2, sd = 1),
-  sample_strong = rnorm(n = N, mean = 2, sd = 0.5),
-  updated_strong = rnorm(n = N, mean = 2, sd = 1),
-  sample_weak = rnorm(n = N, mean = 2, sd = 2),
-  updated_weak = rnorm(n = N, mean = 1.5, sd = 1)
-)
-```
-
-```{r}
-#| label: fig-pre-existing
-#| fig-cap: Pre-existing beliefs
-#| fig-subcap:
-#|   - Weak accuracy, strong pre-existing
-#|   - Strong accuracy, weak pre-existing
-
-ggplot(data = df) +
-  geom_density(aes(x = sample_strong)) +
-  geom_vline(aes(xintercept =  2), linetype = 1) +
-  theme_minimal()
-
-ggplot(data = df) +
-  geom_density(aes(x = sample_weak)) +
-  geom_vline(aes(xintercept =  2), linetype = 1) +
-  theme_minimal()
-```
-
----
-
-```{r}
-#| label: fig-updated
-#| fig-cap: Updated beliefs
-#| fig-subcap:
-#|   - Weak accuracy, strong pre-existing
-#|   - Strong accuracy, weak pre-existing
-
-ggplot(data = df) +
-  geom_density(aes(x = updated_strong)) +
-  geom_vline(aes(xintercept =  2), linetype = 1) +
-  geom_vline(aes(xintercept =  2), linetype = 2) +
-  theme_minimal()
-
-ggplot(data = df) +
-  geom_density(aes(x = updated_weak)) +
-  geom_vline(aes(xintercept =  2), linetype = 1) +
-  geom_vline(aes(xintercept =  1.5), linetype = 2) +
-  theme_minimal()
-```
-
 ## Amending those models with the Snap-judgment model
@@
 {{< include ../../../assets/_theory.qmd >}}
-
----
-
-```{r}
-#| label: sim-snap-judgment
-
-df <- fabricatr::fabricate(
-  N = 10000,
-  pop = rnorm(n = N, mean = 2, sd = 1),
-  sample_strong = rnorm(n = N, mean = 2.5, sd = 0.5),
-  updated_strong = rnorm(n = N, mean = 2.5, sd = 1),
-  sample_weak = rnorm(n = N, mean = 2.5, sd = 2),
-  updated_weak = rnorm(n = N, mean = 1.5, sd = 1)
-)
-```
-
-```{r}
-#| label: fig-snap-sample
-#| fig-cap: Pre-existing beliefs based on visual information
-#| fig-subcap:
-#|   - Weak accuracy, strong pre-existing
-#|   - Strong accuracy, weak pre-existing
-
-ggplot(data = df) +
-  geom_density(aes(x = sample_strong)) +
-  geom_vline(aes(xintercept = 2.5), linetype = 1) +
-  theme_minimal()
-ggplot(data = df) +
-  geom_density(aes(x = sample_weak)) +
-  geom_vline(aes(xintercept = 2.5), linetype = 1) +
-  theme_minimal()
-```
-
----
-
-```{r}
-#| label: fig-snap-updated
-#| fig-cap: Updated beliefs with visual information
-#| fig-subcap:
-#|   - Weak accuracy, strong pre-existing
-#|   - Strong accuracy, weak pre-existing
-
-ggplot(data = df) +
-  geom_density(aes(x = updated_strong)) +
-  geom_vline(aes(xintercept = 2.5), linetype = 1) +
-  geom_vline(aes(xintercept = 2.5), linetype = 2) +
-  theme_minimal()
-ggplot(data = df) +
-  geom_density(aes(x = updated_weak)) +
-  geom_vline(aes(xintercept = 2.5), linetype = 1) +
-  geom_vline(aes(xintercept = 1.5), linetype = 2) +
-  theme_minimal()
-```
-
----
 
@@
 ```{r}
-#| label: fig-study-2-pred
-#| layout-ncol: 1
+#| label: fig-study-2-pred-1
 #| fig-cap: More blue on the yard signs in Democratic strongholds
-#| fig-subcap:
-#|   - Proportion of red
-#|   - Proportion of blue
+
+blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["blue"]]
+  , treatment = "Blue"
+  , hypothesis = "H5"
+)
+
+blue
+```
+
+---
+
+```{r}
+#| label: fig-study-2-pred-2
+#| fig-cap: Less red on the yard signs in Democratic strongholds
+
 red <- predicted_prob_bar(
@@
 )
-blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["blue"]]
-  , treatment = "Blue"
-  , hypothesis = "H5"
-)
 red
-blue
 ```
@@
 ```{r}
-#| label: fig-h-2-predictions
-#| layout-nrow: 1
-#| fig-cap: The partisanship of candidates change depending on the color of the yard sign
-#| fig-subcap:
-#|   - Red treatment
-#|   - Blue treatment
+#| label: fig-h-2-predictions-1
+#| fig-cap: Red yard signs = Republican candidate
 red <- predicted_prob_bar(
@@
 )
+red
+```
+
+---
+
+```{r}
+#| label: fig-h-2-predictions-2
 blue <- predicted_prob_bar(
@@
 )
-red
 blue
@@
 ```{r}
-#| label: fig-h-3-predictions
-#| layout-nrow: 1
-#| fig-cap: Probability of voting for candidate with yard sign
-#| fig-subcap:
-#|   - Red treatment
-#|   - Blue treatment
+#| label: fig-h-3-predictions-1
+#| fig-cap: Republicans are more likely to vote for candidate with red yard sign, Democrats less likely
 red <- predicted_prob_bar(
@@
 )
+
+red
+```
+
+```{r}
+#| label: fig-h-3-predictions-2
+#| fig-cap: Democrats are more likely to vote for candidate with blue yard signs, Republicans less likely
 blue <- predicted_prob_bar(
@@
 )
-red
+
 blue

### 2023-10-03 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
copying over the prr simulation stuff, will need to actually run it though

@@
 For a reader who thinks "hypothesizing about car color choice and partisanship is a reach," I agree.
-As stated at the outset of the chapter, the goal of the chapter is to extend past applications of the snap-judgment model to explicitly partisan objects such as yard signs as we did in Chapter 2 and to really challenge the model by looking at non-political objects that we do not readily associate with partisanship.
+As stated at the outset of the chapter, the goal of the chapter is to extend past applications of the snap-judgment model to explicitly partisan objects such as yard signs as we did in [Chapter 2](../../../chapter_2/src/manuscript.qmd) and to really challenge the model by looking at non-political objects that we do not readily associate with partisanship.
 
@@
 In the second condition, the "favorite color of car" reported by displaying a blue swatch.
-Participants are presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?"
+Participants are presented with a feeling thermometer ranging from 0-100 where participants are asked to "Rate their feelings toward the neighborhood as warm (100) or cold (0)".
+They are also presented with a 5-item Likert scale to indicate, "How much would [they] like to live in this neighborhood?"
 
@@
 The information subjects sees depends on which of two conditions they are randomly assigned into.
-In one condition, the information indicates that the neighborhood is "40 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition presents the same information but instead describes the neighborhood as "10 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." With this new information, I ask participants "How much would [they] like to live in this neighborhood?" and are given a 5-item Likert scale to record their response.
+In one condition, the information indicates that the neighborhood is "40 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition presents the same information but instead describes the neighborhood as "10 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." With this new information, I ask participants "Rate their feelings toward the neighborhood as warm (100) or cold (0)" and are given a feeling thermometer scale to record their response.
+I also ask them "How much would [they] like to live in this neighborhood?" and are given a 5-item Likert scale to record their response.
 
@@
 
+The first outcome of interest is the reported feeling thermometer that ranges from 0-100.
+I divide the response to this outcome variable by 10 and fit an ordered beta regressions [see @kubinec_ordered_2022].
+As I am interested in examining how these treatments impact perceptions and resulting preferences based on partisanship, I interact the treatment with the self-reported partisan identity of the participant to examine how a participants' preference for that neighborhood is moderated by the treatment.
+As I am unable to randomly assign my participants' self-reported partisan identity, I want to ensure that I isolate the main and conditional effects of self-reported partisan identification from confounders such as age, education, and gender identity.
+I also want to hold constant potential confounders of the treatment's effect on a participant outside of their partisanship such as sex and colorblindness, as well as attention paid to politics.
+Using these models will allow me to test the first hypothesis which predicts that people will report liking the neighborhood more when the favorite car color aligns with their partisan group -- red with Republicans and blue with Democrats, as they project the association between the colors red and blue with their partisan group onto the neighborhood.
+I then examine the second hypothesis which predicts that updating this information with consistent cultural stereotypes of partisan preferences for neighborhood features strengthens one's affect towards the neighborhood as a result of this new information strengthening my participants' certainty about the partisan composition of the neighborhood.
+These tests do not examine whether it influences one's willingness to move to the neighborhood, only one's preferences toward it.
+In this way, these tests are much like the outcomes examined in the common experimental tests of the observed positive affect toward neighborhoods with a partisan composition aligned with your own identity.
+The next outcome of interest examines the degree to which someone is willing to move to the neighborhood on this same information.
+
 The outcome of interest is a 5-item Likert scale.
 So the following models will be ordered logistic regressions.
-$H_1$ and $H_2$ would expect that when viewing the first page of the real estate flyer that Democratic participants would report a higher desire to move to a neighborhood with a blue swatch as opposed to a red swatch; the inverse would be true for Republican participants.
+Much like I did with the previous models, I fit a model that includes an interaction term so that I can test whether the effect of self-reported partisan identity on a preference to live in a particular neighborhood is moderated by the reported favorite car color in that neighborhood and whether these effects are strengthened (in either direction) once we follow-up with more information.
+As the modeling strategy is the same, I include the same confounding variables.
 
@@
 
+As I am using interactive models to test my hypotheses as well as using a quasi-pre-post design, I want to be sure that my sample size will be large enough to override any effects of my modeling choices (such as choice in priors and including interaction terms) as well as design choices (quasi-pre-post-design) so that I may draw conclusions aligned with the truth -- whether those confirm or run counter to my hypotheses.
+To help with this, I will generate simulated samples where I know what the true parameter is and will estimate at what sample size does my modeling and research design choices have a small enough weight that I am able to draw the correct inferences.
+
+Using the `fabricatr` [@fabricatr] package, I simulate a population with an N of 1,000,000.
+The specified data generating processes for each of the variables are included in @lst-sim-dgp and @lst-sim-dgp-2.
+I then generate 500 random samples for each sample size of 200, 400, 600, and 800 participants.
+This sample size is not the size of the total sample I intend to recruit but is the total sample that I have data on after excluding those who fail attention checks and those who provide duplicate responses.
+Some estimate that insincere responses account for about 40% of a researcher's original sample [@kennedy_et-al_2021_poq].
+However, it is important to note that this is a quite conservative estimate of the proportion of insincere responses as this estimate comes from platforms that are notorious for poor convenience samples such as MTURK.
+
+``` {#lst-sim-dgp .r lst-cap="Code to generate simulated population data"}
+
+dgp <- fabricate(
+    N = 1000000, # N in the population
+    E = rnorm(N), # epsilon term
+    age = round( # define age variable
+        runif(N, 18, 85)
+    ),
+    gender = draw_binary( # define binary gender identity variable
+        N,
+        prob = 0.5
+    ),
+    white = draw_binary( # define white indicator variable
+        N,
+        prob = 0.6
+    ),
+    PartyId = draw_ordered( # define party identity variable as 3-item ordinal
+        x = rnorm(
+            N,
+            mean = 0.4 * age - 0.6 * gender + 0.7 * white + E
+        ),
+        breaks = c(
+            -Inf, 20.14, 23.01, Inf
+        )
+    ),
+    Attention = draw_ordered( # define Attention variable as 5-item ordinal
+        x = rnorm(
+            N,
+            mean = 0.5 * age - 0.3 * gender + 0.1 * white + E
+        ),
+        breaks = c(
+            -Inf, 16.5, 28.26, 36.54, 43.82, Inf
+        )
+    ),
+    ...
+```
+
+``` {#lst-sim-dgp-2 .r lst-cap="Code to generate simulated population data (continued)"}
+  ...
+    RedTreatment = draw_binary( # Simulate treatment assignment with prob 1/3
+        N,
+        prob = 1/2
+    ),
+    preference = draw_binary( # Define Preference outcome variable as 3-item ordinal
+        x = rnorm(
+            N,
+            prob = (
+              E + 1.5 * RedTreatment + 1.5 * PartyId + 2 * RedTreatment * PartyId + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+            )
+        )
+    ),
+    move = draw_ordered( # Define move outcome variable as Likert variable
+        x = rnorm(
+            N,
+            mean = (
+              E + 1 * RedTreatment + 1 * PartyId + 2 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+            )
+        ),
+        breaks = c(
+            -Inf, -3, -1, 1, 3, Inf
+        )
+    ),
+    preference_post = draw_binary( # Define Preference (post new information) outcome variable as 3-item ordinal
+      x = rnorm(
+        N,
+        prob = (
+          E + 1 * RedTreatment + 2 * PartyID + 2.5 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+        )
+      )
+    ),
+    move_post = draw_ordered(# Define move outcome variable as Likert variable
+      x = rnorm(
+        N,
+        mean = (
+          E + 0.5 * RedTreatment + 1.5 * PartyId + 2.5 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+        )
+      ),
+      breaks = c(
+        -Inf, -3, -1, 1, 3, Inf
+      )
+    )
+)
+```
+
 {{< pagebreak >}}

### 2023-10-03 chapter_4/src/prr/R/discrepancy.R

@@ -1,0 +1,103 @@
+'.__module__.'
+#' get discrepancy between pt.estimates and parameters
+#'
+#' dependencies
+#'
+#' discrepancy
+#' @param compiled
+#' @param data
+#' @param formula
+#' @param family
+#' @param model
+#' @return data.table
+#' @export
+discrepancy <- function (
+    compiled
+    , data
+    , formula
+    , family
+    , priors
+    , model
+) {
+    # Define parameters
+    parameters <- c(
+        "b[1]"
+        , "b[2]"
+        , "b[3]"
+        , "b[4]"
+        , "b[5]"
+        , "b[6]"
+        , "b[7]"
+    )
+    # Define a empty data.table
+    rejectDF <- stats::setNames(
+        data.table::data.table(
+            base::matrix(
+                nrow=0
+                ,ncol=7
+            )
+        ),
+        parameters
+    )
+    # Fit the model for each sample
+    sumList <- base::lapply(
+        data,
+        function (x) {
+            # Define the stan data object
+            dfList <- brms::make_standata(
+                formula
+                , data = x
+                , family = family
+                , priors = priors
+            )
+            # fit the stan model
+            fitted <- rstan::sampling(
+                compiled
+                , dfList
+                , chains = 1
+                , iter = 100
+                , refresh = 0
+                , show_messages = FALSE
+            )
+            # convert it to a data.table object
+            fittedDF <- data.table::as.data.table(fitted)
+            # calculate the credible intervals
+            cI <- data.table::as.data.table(
+                bayestestR::hdi(
+                    fittedDF
+                    , parameters = c("b")
+                    , ci = 0.90
+                )
+            )[
+                Parameter %in% parameters
+            ]
+            # determine whether pt.estimate is outside of credible interval
+            pos <- data.table::transpose(
+                cI[
+                    , pos := data.table::fifelse(
+                        cI$CI_low > 0 && cI$CI_high > 0, 1,
+                        data.table::fifelse(
+                            cI$CI_low < 0 && cI$CI_high < 0, 1, 0
+                        )
+                    )
+                ][
+                    , list(Parameter, pos)
+                ]
+            )
+            colnames(pos) <- parameters
+            pos <- pos[-1, ]
+            pos <- data.table::as.data.table(
+                base::lapply(pos, as.numeric)
+            )
+            # Update the dataframe on whether to reject or not
+            rejectDF <- base::rbind(
+                rejectDF
[…]

### 2023-10-03 chapter_4/src/prr/R/true_positive.R

@@ -1,0 +1,27 @@
+'.__module__'
+#' calculate the true positive rate
+#'
+#' dependencies
+#'
+#' @param df vector to calculate the true positive rate for
+#' @param new_names
+#' @return data.table
+#' @export
+true_positive <- function(
+    df
+    , new_names
+) {
+    rate <- data.table::as.data.table(
+        base::lapply(
+            df
+            , function(x) {
+                base::mean(
+                    x
+                    , na.rm = TRUE
+                ) * 100
+            }
+        )
+    )
+    names(rate) <- new_names
+    return(rate)
+}

### 2023-10-03 chapter_4/test/prr/test_discrepancy.R

@@ -1,0 +1,86 @@
+# Title: test_discrepancy
+
+# Notes:
+    #* Description
+        #** test of discrepancy function
+    #* Updated
+        #** 2023-05-09
+        #** dcr
+
+# Setup
+    #* set working directory
+setwd("../src/prr/R")
+    #* load functions
+box::use(
+    ./discrepancy[discrepancy]
+    , ./generate_samples[generate_samples]
+    , brms[
+        brmsformula
+        , cumulative
+        , prior
+    ]
+    , rstan[stan_model]
+    , testthat[...]
+)
+
+base::suppressWarnings({
+    #* execute function
+        #** define compiled stan model
+partyCompiled <- stan_model(
+    "../STAN/vote_guess_simulated_model.stan"
+)
+        #** define brms formula
+partyFormula <- brmsformula(
+    PartyGuess ~ RedTreatment + BlueTreatment + age + RedTreatment:age + BlueTreatment:age + Attention + Knowledge
+)
+        #** create sample data
+exampleSamples <- generate_samples(n = 100, num_samples = 2)
+        #** calculate discrepancy
+result <- discrepancy(
+    compiled = partyCompiled
+    , data = exampleSamples
+    , formula = partyFormula
+    , family = cumulative(link = "logit")
+    , priors = prior(
+        Normal(0, 1)
+        , class = b
+    )
+    , model = "partyGuess"
+)
+})
+# Tests
+    #* check to make sure it returns a data.frame
+test_that(
+    "check class"
+    , {
+        expect_s3_class(
+            result
+            , "data.table"
+        )
+    }
+)
+    #* check to make sure that there are seven columns
+test_that(
+    "check num of columns"
+    , {
+        expect_true(
+            ncol(result) == 7
+        )
+    }
+)
+    #* check to make sure that there are two rows
+test_that(
+    "check num of rows"
+    , {
+        expect_true(
+            nrow(result) == 2
+        )
+    }
+)
+    #* expect warning
+#test_that(
+#    "expect warning"
+#    ,{
+#        expect_warning(result)
+#    }
+#)

### 2023-10-03 chapter_4/test/prr/test_discrepancy_df.R

@@ -1,0 +1,61 @@
+# Title: test_discrepancy_df
+
+# Notes:
+    #* Description
+        #** Test of discrepancy_df function
+    #* Updated
+        #** 2023-05-10
+        #** dcr
+
+# Setup
+    #* set working directory
+setwd("chapter_4/test")
+setwd("../src/prr/R")
+    #* load functions
+box::use(
+    ./discrepancy_df[discrepancy_df]
+    ,testthat[...]
+)
+    #* load example list
+load(
+    file="../../../data/models/prr/sim/sim.RDS"
+)
+   #* specify args
+new_names <- c(
+  "Red treatment"
+  , "Blue treatment"
+  , "Age"
+  , "Red treatment x Age"
+  , "Blue treatment x Age"
+  , "Attention"
+  , "Knowledge"
+)
+
+# Tests
+    #* expect data.table
+test_that(
+    "expect data.table"
+    , {
+        expect_s3_class(
+            discrepancy_df(
+                list = modelDiscrepancies
+                , new_names = new_names
+            )
+            , "data.table"
+        )
+    }
+)
+    #* expect four rows
+test_that(
+    "expect four rows"
+    , {
+        expect_true(
+            nrow(
+                discrepancy_df(
+                    list = modelDiscrepancies
+                    , new_names = new_names
+                )
+            ) == 4
+        )
+    }
+)

### 2023-10-03 chapter_4/test/prr/test_generate_samples.R

@@ -1,0 +1,130 @@
+# Title: test_generate_samples
+
+# Notes:
+    #* Description:
+        #** Test the generate_samples function
+    #* Updated
+        #** 2023-05-08
+        #** dcr
+
+# Setup
+setwd("../src/prr/R/")
+    #* load functions
+box::use(
+    ./generate_samples[generate_samples]
+    , testthat[...]
+)
+    #* execute function
+result_one_sample <- generate_samples(
+    n = 100
+)
+result_one_sample_two_size <- generate_samples(
+    n = c(100, 200)
+)
+result_multiple_sample_one_size <- generate_samples(
+    n = 100
+    , num_samples = 2
+)
+result_multiple_sample_multiple_size <- generate_samples(
+    n = c(100, 200)
+    , num_samples = 2
+)
+
+# tests
+    #* check classes
+        #** for one sample of one size
+test_that(
+    "check data.frame"
+    , {
+        expect_s3_class(
+            result_one_sample
+            , "data.frame"
+        )
+    }
+)
+        #** for one sample of two sizes
+test_that(
+    "check list two sizes"
+    , {
+        expect_type(
+            result_one_sample_two_size
+            , "list"
+        )
+    }
+)
+        #** for two samples of one size
+test_that(
+    "check list two samples"
+    , {
+        expect_type(
+            result_multiple_sample_one_size
+            , "list"
+        )
+    }
+)
+        #** for two samples of two sizes
+test_that(
+    "check list two samples of multiple sizes"
+    , {
+        expect_type(
+            result_multiple_sample_multiple_size
+            , "list"
+        )
+    }
+)
+    #* check dimensions
+        #** for one sample one size
+test_that(
+    "check size of one sample one size"
+    , {
+        expect_true(
+            nrow(result_one_sample) == 100
+        )
+    }
+)
+        #** for one sample two sizes
+test_that(
+    "check size of one sample two sizes"
+    , {
+        expect_true(
+            length(result_one_sample_two_size) == 2
+        )
+    }
+)
+        #** for two sample one size
+test_that(
+    "check size of two sample one size"
+    , {
+        expect_true(
+            length(result_multiple_sample_one_size) == 2
+        )
+    }
+)
+        #** for two samples two sizes
+test_that(
+    "check size of two sample two size"
+    , {
+        expect_true(
+            length(result_multiple_sample_multiple_size) == 4
+        )
+    }
+)
+    #* check that data.frames are inside lists
[…]

### 2023-10-03 chapter_4/test/prr/test_one_sample.R

@@ -1,0 +1,49 @@
+# Title: test_one_sample
+
+# Notes:
+    #* Description:
+        #** Test the one_sample function
+    #* Updated
+        #** 2023-05-08
+        #** dcr
+
+# Setup
+    #* set working directory
+setwd("../src/prr/R")
+    #* load functions
+box::use(
+    ./one_sample[one_sample]
+    , testthat[...]
+)
+    #* execute example function
+result <- one_sample(n = 100)
+
+# tests
+    #* check to make sure data.frame object
+test_that(
+    "check dataframe"
+    , {
+        expect_s3_class(
+            result
+            , "data.frame"
+        )
+    }
+)
+    #* check to make sure it has 100 rows
+test_that(
+    "check length"
+    , {
+        expect_true(
+            nrow(result) == 100
+        )
+    }
+)
+    #* check to make sure it has 14 columns
+test_that(
+    "check columns"
+    , {
+        expect_true(
+            ncol(result) == 14
+        )
+    }
+)

### 2023-10-03 chapter_4/test/prr/test_sim_all.R

@@ -1,0 +1,182 @@
+# Title: test_sim_all
+
+# Notes:
+    #* Description
+        #** test the sim_all function
+    #* Updated
+        #** 2023-05-09
+        #** dcr
+
+# Setup
+    #* set working directory
+setwd("../src/prr/R")
+    #* load functions
+box::use(
+    ./sim_all[sim_all]
+    ,brms[
+        brmsformula
+        , cumulative
+        , prior
+    ]
+    , rstan[stan_model]
+    , testthat[...]
+)
+    #* define some arguments
+formula <- brmsformula(
+    PartyGuess ~ RedTreatment + BlueTreatment + age +
+    RedTreatment:age + BlueTreatment:age +
+    Attention + Knowledge
+)
+base::suppressWarnings({
+    compiled <- stan_model(
+            "../STAN/vote_guess_simulated_model.stan"
+            , model_name = "partyGuess"
+    )
+})
+family <- cumulative(link="logit")
+priors <- prior(
+    stats::Normal(0,1)
+    , class = b
+)
+# tests
+    #* if I specify a model with 2 samples at 100 rows each...
+    #* should expect 1 list with with dataframe in it with two rows
+test_that(
+    "expect list"
+    , {
+        expect_type(
+            base::suppressWarnings({
+                sim_all(
+                    n = 100
+                    , num_samples = 2
+                    , formula = formula
+                    , compiled = compiled
+                    , family = family
+                    , priors = priors
+                    , model = "1List"
+                )
+            })
+            , "list"
+        )
+    }
+)
+test_that(
+    "1 list"
+    , {
+        expect_true(
+            base::suppressWarnings({
+                length(
+                    sim_all(
+                        n = 100
+                        , num_samples = 2
+                        , formula = formula
+                        , compiled = compiled
+                        , family = family
+                        , priors = priors
+                        , model = "1List"
+                    )
+                ) == 1
+            })
+        )
+    }
+)
+test_that(
+    "expect data.frames"
+    , {
+        expect_s3_class(
+            base::suppressWarnings({
+                sim_all(
+                    n = 100
+                    , num_samples = 2
+                    , formula = formula
+                    , compiled = compiled
+                    , family = family
+                    , priors = priors
+                    , model = "1List"
+                )[[1]]
+            })
+            , "data.table"
+        )
+    }
+)
+test_that(
+    "expect 2 data.frames"
+    , {
+        expect_true(
+            base::suppressWarnings({
+                nrow(
+                    sim_all(
[…]

### 2023-10-03 chapter_4/test/prr/test_true_positive.R

@@ -1,0 +1,52 @@
+# Title: test_true_positive
+
+# Notes:
+    #* Description 
+        #** test true_positive function
+    #* Updated
+        #** 2023-05-10
+        #** dcr
+
+# Setup
+    #* set working directory
+setwd("../src/prr/R")
+    #* load functions
+box::use(
+    ./true_positive[true_positive]
+    , testthat[...]
+)
+    #* define vector
+vector <- data.frame(
+    a = c(0, 0, 0, 0)
+    , b = c(0, 0, 0, 1)
+    , c = c(0, 0, 1, 1)
+    , d = c(0, 1, 1, 1)
+    , e = c(1, 1, 1, 1)
+)
+new_names <- c("none", "quarter", "half", "three_quarters", "full")
+# Test
+    #* check to make sure it returns a digit
+test_that(
+    "return list"
+    , {
+        expect_type(
+            true_positive(
+                vector
+                , new_names = new_names
+            )
+            , "list"
+        )
+    }
+)
+    #* check to make sure it returns the right number
+test_that(
+    "return right number"
+    , {
+        expect_true(
+            true_positive(
+                vector
+                , new_names = new_names
+            )[, 1] == 0.0
+        )
+    }
+)

### 2023-10-04 chapter_4/src/prr/R/discrepancy.R
updating the code, now to see if it all can produce my final prr

@@ -28,13 +28,14 @@ discrepancy <- function (
         , "b[5]"
         , "b[6]"
         , "b[7]"
+        , "b[8]"
     )
     # Define a empty data.table
     rejectDF <- stats::setNames(
         data.table::data.table(
             base::matrix(
-                nrow=0
-                ,ncol=7
+                nrow = 0
+                , ncol = 8
             )
         ),
         parameters

### 2023-10-04 chapter_4/src/prr/R/helper.R

@@ -1,0 +1,354 @@
+#' generate a single random sample
+#' @param N size of sample.
+#' @param seed seed
+#' @return data.table
+#' @export
+one_sample <- function(N = 100, seed = 121022) {
+  base::set.seed(seed)
+  #* define population
+  dgp <- fabricatr::fabricate(
+    N = 1000000 # N in the population
+    , E = stats::rnorm(N) # epsilon term
+    , age = base::round( # define age variable
+      stats::runif(N, 18, 85)
+    )
+    , gender = fabricatr::draw_binary( # define binary gender identity variable
+      N
+      , prob = 0.5
+    )
+    , white = fabricatr::draw_binary( # define white indicator variable
+      N
+      , prob = 0.6
+    )
+    , PartyID = fabricatr::draw_ordered( # define party identity variable as 3-item ordinal
+      x = stats::rnorm(
+        N
+        , mean = 0.4 * age - 0.6 * gender + 0.7 * white + E
+      )
+      , breaks = base::c(
+        -Inf, 20.14, 23.01, Inf
+      )
+    )
+    , attention = fabricatr::draw_likert( # define Attention variable as 5-item ordinal
+      x = stats::rnorm(
+        N
+        , mean = 0.5 * age - 0.3 * gender + 0.1 * white + E
+      )
+      , min = 0
+      , max = 100
+      , bins = 5
+    )
+    , RedTreatment = fabricatr::draw_binary( # Simulate treatment assignment with prob 1/3
+      N
+      , prob = 0.5
+    )
+    , preference = fabricatr::draw_likert( # Define Preference outcome variable as 5-item ordinal
+        x = stats::rnorm(
+          N
+          , mean = E + 1.5 * RedTreatment + 1.5 * PartyID + 2 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+        )
+        , min = 0
+        , max = 100
+        , bins = 2
+      )
+    , move = fabricatr::draw_likert( # Define move outcome variable as Likert variable
+      x = stats::rnorm(
+        N
+        , mean = (
+          E + 1 * RedTreatment + 1 * PartyID + 2 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+        )
+      )
+      , min = 0
+      , max = 100
+      , bins = 5
+    )
[…]

### 2023-10-04 chapter_4/test/prr/01_test_one_sample.R

@@ -12,11 +12,11 @@
 setwd("../src/prr/R")
     #* load functions
 box::use(
-    ./one_sample[one_sample]
+    ./helper[one_sample]
     , testthat[...]
 )
     #* execute example function
-result <- one_sample(n = 100)
+result <- one_sample(N = 100)
 
 # tests
     #* check to make sure data.frame object
@@ -43,7 +43,7 @@ test_that(
     "check columns"
     , {
         expect_true(
-            ncol(result) == 14
+            ncol(result) == 12
         )
     }
 )

### 2023-10-04 chapter_4/test/prr/02_test_generate_samples.R

@@ -11,7 +11,7 @@
 setwd("../src/prr/R/")
     #* load functions
 box::use(
-    ./generate_samples[generate_samples]
+    ./helper[generate_samples]
     , testthat[...]
 )
     #* execute function
@@ -128,3 +128,4 @@ test_that(
         )
     }
 )
+

### 2023-10-04 chapter_4/test/prr/03_test_discrepancy.R

@@ -12,8 +12,10 @@
 setwd("../src/prr/R")
     #* load functions
 box::use(
-    ./discrepancy[discrepancy]
-    , ./generate_samples[generate_samples]
+    ./helper[
+      generate_samples
+      , discrepancy
+    ]
     , brms[
         brmsformula
         , cumulative
@@ -26,26 +28,26 @@ box::use(
 base::suppressWarnings({
     #* execute function
         #** define compiled stan model
-partyCompiled <- stan_model(
-    "../STAN/vote_guess_simulated_model.stan"
+moveCompiled <- stan_model(
+    "../STAN/move_model.stan"
 )
         #** define brms formula
-partyFormula <- brmsformula(
-    PartyGuess ~ RedTreatment + BlueTreatment + age + RedTreatment:age + BlueTreatment:age + Attention + Knowledge
+formula <- brmsformula(
+    move ~ RedTreatment + PartyID + RedTreatment * PartyID + age + gender + white + attention
 )
         #** create sample data
 exampleSamples <- generate_samples(n = 100, num_samples = 2)
         #** calculate discrepancy
 result <- discrepancy(
-    compiled = partyCompiled
+    compiled = moveCompiled
     , data = exampleSamples
-    , formula = partyFormula
+    , formula = formula
     , family = cumulative(link = "logit")
     , priors = prior(
         Normal(0, 1)
         , class = b
     )
-    , model = "partyGuess"
+    , model = "moveModel"
 )
 })
 # Tests

### 2023-10-04 chapter_4/test/prr/04_test_sim_all.R

@@ -12,7 +12,7 @@
 setwd("../src/prr/R")
     #* load functions
 box::use(
-    ./sim_all[sim_all]
+    ./helper[sim_all]
     ,brms[
         brmsformula
         , cumulative
@@ -23,14 +23,12 @@ box::use(
 )
     #* define some arguments
 formula <- brmsformula(
-    PartyGuess ~ RedTreatment + BlueTreatment + age +
-    RedTreatment:age + BlueTreatment:age +
-    Attention + Knowledge
+    move ~ RedTreatment + PartyID + RedTreatment * PartyID + age + gender + white + attention
 )
 base::suppressWarnings({
     compiled <- stan_model(
-            "../STAN/vote_guess_simulated_model.stan"
-            , model_name = "partyGuess"
+            "../STAN/move_model.stan"
+            , model_name = "moveModel"
     )
 })
 family <- cumulative(link="logit")

### 2023-10-04 chapter_4/test/prr/05_test_true_positive.R

@@ -9,10 +9,10 @@
 
 # Setup
     #* set working directory
-setwd("../src/prr/R")
+setwd("./chapter_4/src/prr/R")
     #* load functions
 box::use(
-    ./true_positive[true_positive]
+    ./helper[true_positive]
     , testthat[...]
 )
     #* define vector

### 2023-10-04 chapter_4/test/prr/06_test_discrepancy_df.R

@@ -9,11 +9,10 @@
 
 # Setup
     #* set working directory
-setwd("chapter_4/test")
-setwd("../src/prr/R")
+setwd("./chapter_4/src/prr/R")
     #* load functions
 box::use(
-    ./discrepancy_df[discrepancy_df]
+    ./helper[discrepancy_df]
     ,testthat[...]
 )
     #* load example list

### 2023-10-04 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
major chunk of chapter 3 prr done

@@
 params:
-  replicate: false
+  replicate: true
 ---
@@
 As I am interested in examining how these treatments impact perceptions and resulting preferences based on partisanship, I interact the treatment with the self-reported partisan identity of the participant to examine how a participants' preference for that neighborhood is moderated by the treatment.
-As I am unable to randomly assign my participants' self-reported partisan identity, I want to ensure that I isolate the main and conditional effects of self-reported partisan identification from confounders such as age, education, and gender identity.
+As I am unable to randomly assign my participants' self-reported partisan identity, I want to ensure that I isolate the main and conditional effects of self-reported partisan identification from confounders such as age, and education.
 I also want to hold constant potential confounders of the treatment's effect on a participant outside of their partisanship such as sex and colorblindness, as well as attention paid to politics.
@@
 
+```{r}
+#| label: setup-block
+
+# Set seed
+set.seed(12102022)
+
+if (params$replicate == TRUE) {
+  box::use(
+    parallel[
+      detectCores
+    ]
+    , brms[
+      brmsformula
+      , cumulative
+      , prior
+    ]
+    , rstan[stan_model]
+    , ./R/helper[
+      sim_all
+      , discrepancy_df
+      , true_positive_hist
+    ]
+  )
+  cores <- detectCores()-1
+} else {
+  box::use(
+   .R/helper[
+    true_positive_hist
+   ] 
+  )
+}
+
+# Default tails
+options("marginaleffects_posterior_interval" = "hdi")
+```
+
 As I am using interactive models to test my hypotheses as well as using a quasi-pre-post design, I want to be sure that my sample size will be large enough to override any effects of my modeling choices (such as choice in priors and including interaction terms) as well as design choices (quasi-pre-post-design) so that I may draw conclusions aligned with the truth -- whether those confirm or run counter to my hypotheses.
@@
 
-Using the `fabricatr` [@fabricatr] package, I simulate a population with an N of 1,000,000.
+Using the `fabricatr` [@blair_fabricatr_2022] package, I simulate a population with an N of 1,000,000.
 The specified data generating processes for each of the variables are included in @lst-sim-dgp and @lst-sim-dgp-2.
@@
 This sample size is not the size of the total sample I intend to recruit but is the total sample that I have data on after excluding those who fail attention checks and those who provide duplicate responses.
-Some estimate that insincere responses account for about 40% of a researcher's original sample [@kennedy_et-al_2021_poq].
+Some estimate that insincere responses account for about 40% of a researcher's original sample [@kennedy_strategies_2021].
 However, it is important to note that this is a quite conservative estimate of the proportion of insincere responses as this estimate comes from platforms that are notorious for poor convenience samples such as MTURK.
@@
 
+To examine whether my design and modeling choices allow for the convergence on the population's data generating process, I specify an ordinal logistic regression where I set relatively constrained priors upon the $\beta$ coefficients, as depicted in @eq-party-guess-priors.
+
+$$
+\begin{split}
+  \alpha \sim Student-T(3,0,2.5) \\
+  \beta_i \sim Normal(0, 1) \\
+  \hat{Move_i} = Cumulative(logit^{-1}(\alpha_1 + \alpha_2 + \alpha_3 + \alpha_4 \\ 
+   + \beta_1 \times Red Treatment + \beta_2 \times Partisanship \\
+   + \beta_3 \times Red treatment \times Partisanship \\ 
+   + \beta_4 \times Age + \beta_5 \times Gender \\
+   + \beta_6 \times White + \beta_7 \times Attention))
+\end{split}
+$$ {#eq-party-guess-priors}
+
+These priors suggest that I believe 68% of my beta coefficients on a logged-odds scale, given the data, should be between -1 and 1; with the median of the estimates at 0.
+This is quite a conservative estimate given that the primary $\beta$ coefficients of interest are both at 0.1 on the logged-odds scale.
+
+After fitting each model, I construct 95% high density interval credible intervals from the model's posterior draws.
+I then record a value of 1 if the credible interval does not contain zero (true positive) and a value of 0 if the credible interval does (false negative) for each parameter.
+Once I have run each of my models for the specified sample size, I calculate the average of true positive and false negatives.
+This gives me a percentage of the time that I would come to the correct conclusion that there is a non-zero effect on that parameter.
+@fig-true-positive-rate documents these calculations for each sample size.
+
+```{r}
+#| label: load-simulation-results
+
+if (params$replicate == TRUE) {
+  # Define model arguments
+  formula <- brmsformula(
+    move ~ RedTreatment + PartyID + RedTreatment * PartyID + age + gender + white + attention
+  )
+  compiled <- stan_model(
+    "./STAN/move_model.stan"
+    ,model_name = "moveModel"
+  )
+  family <- cumulative(link = "logit")
+  priors <- prior(
+    stats::Normal(0,1)
+    ,class = b
+  )
+    # Run model
+  modelDiscrepancies <- sim_all(
+    n=c(200, 400, 600, 800)
+    , num_samples = 500
+    , formula = formula
+    , compiled = compiled
+    , family = family
+    , priors = priors
+    , cores = cores
+    , model = "moveModel"
+  )
+    # store model
+  save(
+      modelDiscrepancies
+      , file = "../../data/models/prr/sim/sim.RDS"
+  )
+} else {
+  load(
+    file = "../../data/models/prr/sim/sim.RDS"
+  )
+}
+```
+
+```{r}
+#| label: fig-true-positive-rate
+#| layout-nrow: 4
+#| fig-width: 6
+#| fig-cap: True positive rate
+#| fig-subcap: 
+#|  - "Red treatment"
+#|  - "Party Identification"
+#|  - "Red treatment x Party Identification"
+#|  - "Age"
+#|  - "Gender"
+#|  - "White"
+#|  - "Attention"
+cleanNames <- c(
+  "Sample size"
+  , "Red treatment"
+  , "Partisanship"
+  , "Red treatment x Partisanship"
+  , "Age"
+  , "Gender"
+  , "White"
+  , "Attention"
+)
+truePositiveDF <- discrepancy_df(
+  list = modelDiscrepancies
+  , new_names = cleanNames
+)
+plotList <- lapply(
+  cleanNames
+  , true_positive_hist
+  , df = truePositiveDF
+)
+plotList[[2]]
+plotList[[3]]
+plotList[[4]]
+plotList[[5]]
+plotList[[6]]
+plotList[[7]]
+```
+
 {{< pagebreak >}}

### 2023-10-04 chapter_4/src/prr/R/helper.R

@@ -133,6 +133,7 @@ discrepancy <- function (
     , family
     , priors
     , model
+    , cores
 ) {
     # Define parameters
     parameters <- base::c(
@@ -172,6 +173,7 @@ discrepancy <- function (
                 , chains = 1
                 , iter = 100
                 , refresh = 0
+                , cores = cores
                 , show_messages = FALSE
             )
             # convert it to a data.table object
@@ -235,6 +237,7 @@ sim_all <- function(
     , family
     , priors
     , model
+    , cores
 ) {
     # generate samples
     samplesList <- base::lapply(
@@ -258,6 +261,7 @@ sim_all <- function(
                 , family = family
                 , priors = priors
                 , model = model
+                , cores = cores
             )
             return(model)
         }

### 2023-10-05 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
drafting a little bit more

@@
 params:
-  replicate: true
+  replicate: false
 ---
@@
 In this chapter, I try to accomplish a few goals.
-First, I want to expand on the previous chapters by examining whether snap-judgments are used to evaluate groups of people.
-Second, I want to expand on the previous chapters by examining whether the previous findings extend to non-political objects.
+First, I want to expand upon the previous chapters by examining whether snap-judgments are used to evaluate groups of people.
+Second, I want to expand upon the previous chapters by examining whether the previous findings extend to non-political objects.
 That is, this chapter seeks to further push my testing of the boundary conditions of the snap-judgment model.
@@
 Others have replicated and built upon this work by suggesting that while there are many different types of lifestyles that Republicans and Democrats can take on, there is increasingly clear distinction between Republicans and Democrat archetypes [@rogers_politicultural_2022].
-These politicultural distinctions are clear enough that we train a computer to make accurate guesses (upwards of 80%) of the partisanship by using only images of the cars in a particular neighborhood [@gebru_using_2017].
+These politicultural distinctions are clear enough that some scholars trained a computer to make accurate inferences (upwards of 80%) of the partisan composition of a neighborhood by using only Google images of the cars parked there [@gebru_using_2017].
 
@@
 For example, some evidence suggests despite variation between counties' partisan composition and lockdowns discouraging people from leaving their homes during the COVID-19 pandemic, those living in Republican counties spent more time away from home than those living in Democratic counties [@roberts_polarized_2021].
-Further, we see a place-based identity for rural individuals that predict partisanship [@cramer_politics_2016; see also @lyons_youre_2021] and characteristics like expression of anti-intellectual attitudes [@lunz_trujillo_rural_2022].
+Further, we see a place-based identity for rural individuals that predict partisanship [@cramer_politics_2016; see also @lyons_youre_2021] and characteristics like expression of anti-intellectual attitudes [@lunz_trujillo_rural_2022] as well as racism among rural Whites and white grievance among urban and suburban Whites on behalf of ruralites [@dawkins_place_2023].
 While place-based identities could be separate or informative of partisan identities, some literature argues that partisanship may actually inform which community we choose to make ours.
@@
 
-Some work suggests, however, that these expressed preferences to live near co-partisans do not carryover to migration patterns [see @iyengar_affect_2012].
+Some work suggests, however, that these expressed preferences to live near co-partisans do not appear in migration patterns [see @iyengar_affect_2012].
 In fact, there is some evidence suggesting that controlling for everything else but current rates of political sorting, we would have less political homogeneity than we had in 2008 [@martin_does_2020].
@@
 The literature on partisan sorting seems to conclude that people express a desire to sort into neighborhoods with partisans, but these attitudes do not turn into observable behaviors.
-The remainder of the chapter provides one explanation for this puzzle by demonstrating how the snap-judgment model may be at play.
+The remainder of the chapter applies the snap-judgment model to examine this puzzle.
 Much like the literature on the attitude expression of partisan sorting, the snap-judgment model heavily relies on the ways in which seemingly non-political information comes to be associated with one partisan group or another.
@@
 For a reader who thinks "hypothesizing about car color choice and partisanship is a reach," I agree.
-As stated at the outset of the chapter, the goal of the chapter is to extend past applications of the snap-judgment model to explicitly partisan objects such as yard signs as we did in [Chapter 2](../../../chapter_2/src/manuscript.qmd) and to really challenge the model by looking at non-political objects that we do not readily associate with partisanship.
+As stated at the outset of the chapter, the goal of the chapter is to extend past applications of the snap-judgment model to explicitly partisan objects such as yard signs as we did in [Chapter 2](../../../chapter_2/src/manuscript.qmd) and to really challenge the model by looking at non-political objects that we may not readily associate with partisanship.
+
+{{< include ../../../assets/_theory.qmd >}}
 
@@
 Therefore, we are motivated to rely on heuristics to help with this [@motyl_how_2020].
-One useful and efficient heuristic to convey partisanship is the use of color as other chapters have demonstrated.
-If we are concerned about the partisanship of our neighbors, we may rely on information such as the color of our potential neighbors' cars to infer their partisanship.
+As the other chapters demonstrate, one useful and efficient heuristic to convey partisanship is the use of color.
+If we are concerned about the partisanship of our neighbors, we may rely on information such as the color of our potential neighbors' cars (or other pieces of their property for that matter) to infer their partisanship.
 
@@
 So, we may reasonably assume that if we see a neighborhood with a significant number of red cars, we may assume that the local sports team color must be red.
-However, if we are searching for cues toward the partisan composition of the neighborhood, we may then assume that the neighborhood has a large number of Republicans, whether that is accurate or not.
+However, in line with predictions from Affective Intelligence Theory, states of uncertainty and anxiety predict information seeking behavior [see @marcus_anxiety_1993].
+That is, if we are searching for cues toward the partisan composition of the neighborhood, we may then assume that the neighborhood has a large number of Republicans, whether that is accurate or not.
 Once we have used that association between the colors red and blue with partisan affiliation, we will form a snap-judgment of our neighbors based on the color of their cars when absent other information.
@@
 However, the role of color is to act as a form of pre-conscious impression formation.
-While all of these alternative, and better, cues towards partisanship may be present, they are more complicated forms of visual information that will require more laborious processing before attitude formation.
+While all of these alternative, and perhaps more accurate, cues towards partisanship may be present, they are more complicated forms of visual information that will require more laborious processing before attitude formation.
 The point of the snap-judgment model is to illustrate how extremely simple visual information, such as color, shapes our thinking due to the cognitive processes that underlie impression formation and the effects of impressions after particular neurological paths are made "hot".
@@
 The first outcome of interest is the reported feeling thermometer that ranges from 0-100.
-I divide the response to this outcome variable by 10 and fit an ordered beta regressions [see @kubinec_ordered_2022].
+I divide the response to this outcome variable by 10 and fit an ordered beta regression [see @kubinec_ordered_2022].
 As I am interested in examining how these treatments impact perceptions and resulting preferences based on partisanship, I interact the treatment with the self-reported partisan identity of the participant to examine how a participants' preference for that neighborhood is moderated by the treatment.
@@
   box::use(
-   .R/helper[
+   ./R/helper[
     true_positive_hist
+    , discrepancy_df
    ] 
@@
 
+From these simulations, we can see that the true positive rate for the estimate of interest (the interaction term) holds up across different sample sizes.
+To be safe, however, I am going to strive to recruit more than 600 participants total which should give me a sufficient sample to work with even once I have to apply exclusion criteria.
+
 {{< pagebreak >}}

### 2023-10-09 grants/ddirg/src/roberts_budget_justification.qmd

---
subtitle: Budget Justification
format:
  fancy-doc-pdf:
    toc: false
    latex-output-dir: ../out/
    biblatex: true
    filters:
      #- "_extensions/andrewheiss/wordcount/citeproc.lua"
      - "_extensions/andrewheiss/wordcount/wordcount.lua"
author:
  - name: Damon C. Roberts
    affiliations:
      - name: Univeristy of Colorado Boulder
    email: damon.roberts-1@colorado.edu
bibliography: ../../../assets/references.bib
---

# Justification of Cost for Participants

For the study, I am anticipating that I will pay each participant about $1.20 for their time. As I am anticipating that it will take participants approximately 6 minutes to complete the study on average. I would like to pay participants at the rate of $12.00 per hour for their time. This is above the national minimum wage and seems to be a reasonable hourly rate. It is also a recommended rate to attract participants according to the Prolific Platform.

Given power calculations for the study design, my goal is to recruit about 1300 participants for my study as I anticipate that once I account for insincere responses and those who may fail attention checks ^[Given some estimates by @kennedy_et-al_2021_poq that suggest upwards of 40% of a sample should be discarded from many online samples, I want to over-estimate the recruited sample to have a sufficiently large analyzed sample.], I should have a sufficient sample to detect effects if they indeed exist.

Total cost for participant payment will be $1,500.

I have more details about the research design that may help assessors evaluate my timing estimates as well as the number of treatment conditions that I am using in my response for the Data Management Plan. I am including the mockups of my treatment that I discuss in the Data Management Plan here in @fig-mockup. I apologize putting these in slightly different places, but I was unable to add images to my response for the Data Management Plan.

::: {#fig-mockup}

![Red treatment flyer](../../../chapter_4/assets/irb/red_treatment_mockup.pdf){#fig-red height=300}

![Blue treatment flyer](../../../chapter_4/assets/irb/blue_treatment_mockup.pdf){#fig-blue height=300}

Treatment Mockups
:::

# Justification of Prolific Fees

Prolific assigns a fee to cover their cost for managing the panel as well as for the use of their platform for recruiting participants. Given my sample size, their fee is $500.00.

To ensure that my results are generalizable to the American public and do not suffer from inferential problems with conveniences samples, I am electing to ask Prolific to recruit a nationally representative sample for me based on their own algorithm but indicates that it is based on census track data. Their fee for recruiting such a sample is $1,032.67.

### 2023-10-09 chapter_2/src/slides/slides.qmd
a few more edits

@@
     , geom_vline
+    , labs
+    , scale_y_discrete
+    , scale_x_discrete
+  ]
+  , ggdist[
+    stat_halfeye
   ]
@@
   ]
+  , marginaleffects[
+    avg_slopes
+    , posterior_draws
+  ]
   , ../R/predicted_prob_bar[...]
@@
 # Load fitted models
+  #* Pre-test
+load(
+    file="../../data/models/prr/pre-test/pre-test_party_model.RDS"
+  )
+  #* Main studies
 load("../../data/temp/models/study_1_fitted.RData")
@@
 #| label: fig-hook-1
-#| fig-cap: Probability of voting for candidate with red yard sign versus white
-#| 
-red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_3"]][["red"]]
-  , x_axis = "trial_1_red_stimuli"
-  , treatment = "Red"
-  , hypothesis = "H3"
-  , x_label = "Party ID"
-  , y_label = "Pr(Vote for candidate)"
-  , legend_title = "Treatment"
-)
-
-red
-```
-
----
-
-```{r}
-#| label: fig-hook-2
-#| fig-cap: Probability of voting for candidate with blue yard sign versus white
-blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_3"]][["blue"]]
-  , x_axis = "trial_1_blue_stimuli"
-  , treatment = "Blue"
-  , hypothesis = "H3"
-  , x_label = "Party ID"
-  , y_label = "Pr(Vote for candidate)"
-  , legend_title = "Treatment"
-)
-blue
+#| fig-cap: Perceptions of candidate's party affiliation based on color of yard sign
+
+partyAMES <- avg_slopes(
+  PartyModel,
+  type = "link"
+) |>
+posterior_draws()
+
+ggplot(
+  data = partyAMES,
+  aes(
+    x = draw,
+    y = term
+  )
+) +
+stat_halfeye(
+  slab_alpha = 0.45
+) +
+theme_minimal() +
+labs(
+  x = "Average Marginal Effect",
+  y = "",
+  caption = "Data source: Pre-test.\n Distribution of AME's for model posterior draws using HDI's.\n Interpreted as the logged odds of labelling the candidate as a partisan\n given whether they viewed a red yard sign or blue yard sign\n while holding all other variables at their mean value.\n Dot reflects median posterior draw where bars reflect 90% and 95% credible intervals."
+) +
+scale_y_discrete(
+  labels = c(
+    "Blue Treatment",
+    "Red Treatment"
+  )
+) +
+ggplot2::scale_x_continuous(
+  breaks = c(-3, 0, 3)
+  , labels = c(
+    "Strong Democrat", "Independent", "Strong Republican"
+  )
+)
 ```
@@
 
-## Question guiding the project
+# Question guiding the project
 
@@
 
-## De-mystifying some of the jargon I might use
-
----
-
-- Object
-  - refers to anything out in the world that we are interacting with
-  - here, these objects are political
-- Affect $\neq$ emotion
-  - refers to the larger state of being
-  - emotion refers to consciously labeled reactions
-  - valance refers to pre-consciously 
-- "Hot Cognition"
-  - refers to the idea that some memories and experiences are more accessible or come to the top of the mind quicker.
-  - this coincides with memories and experiences that are affect-laden
-
-## Dominant models of information processing
-
-### Borrowing concepts from social neuroscience and psychology
-
----
-
-- Memories:
-  -  are multi-dimensional encodings of previous experiences [@fazio_attitudes_2007]
-    - e.g., remember giving your first job talk
-      - the layout of the room
-      - the colors of the chairs
-      - what the room smelled like
-      - what ambient sounds were there
-      - how you felt
-  - affectively laden [@fazio_attitudes_2007;@winkielman_emotion_2011; @kensinger_affective_2022]
-  - easier retrieved when recent and/or shares multiple commonalities with current object
-
-### Zaller's [-@zaller_nature_1992] Memory model
-
----
-
-```{mermaid}
-%%| label: fig-zaller
-%%| fig-cap: Memory model of info processing
-graph TD;
-A[Sampled pre-existing info] -->|Stronger impacts when less pre-existing knowledge| C[Updated attitudes]
-B[New info] --> C
-```
-
----
-
-```{r}
-#| label: sim-visualization
-
-df <- fabricatr::fabricate(
-  N = 10000,
-  pop = rnorm(n = N, mean = 2, sd = 1),
-  sample_strong = rnorm(n = N, mean = 2, sd = 0.5),
-  updated_strong = rnorm(n = N, mean = 1.9, sd = 1),
-  sample_weak = rnorm(n = N, mean = 2, sd = 2),
-  updated_weak = rnorm(n = N, mean = 1.5, sd = 1)
-)
-```
-
-```{r}
-#| label: fig-pre-existing-info
-#| fig-cap: Set of pre-existing attitudes
-ggplot(data = df) +
-  geom_density(aes(x = pop)) +
-  geom_vline(aes(xintercept = 2), linetype = 1) +
-  theme_minimal()
-```
-
----
-
-```{r}
-#| label: fig-sample-pre-existing-info
-#| fig-cap: Pre-existing attitudes used
-#| fig-subcap:
-#|   - Unknowledgeable person
-#|   - Knowledgeable person
-ggplot(data = df) +
-  geom_density(aes(x = sample_weak)) +
-  geom_vline(aes(xintercept =  2), linetype = 1) +
-  theme_minimal()
-ggplot(data = df) +
-  geom_density(aes(x = sample_strong)) +
-  geom_vline(aes(xintercept =  2), linetype = 1) +
-  theme_minimal()
-```
-
----
-
-```{r}
-#| label: fig-new-attitude
-#| fig-cap: Updated set of attitudes
-#| fig-subcap:
-#|   - Unknowledgeable person
-#|   - Knowledgeable person
-ggplot(data = df) +
-  geom_density(aes(x = updated_weak)) +
-  geom_vline(aes(xintercept =  2), linetype = 1) +
-  geom_vline(aes(xintercept =  1.5), linetype = 2) +
-  theme_minimal()
-ggplot(data = df) +
-  geom_density(aes(x = updated_strong)) +
-  geom_vline(aes(xintercept =  2), linetype = 1) +
-  geom_vline(aes(xintercept =  1.9), linetype = 2) +
-  theme_minimal()
-```
-
-### Lodge and Taber's [-@lodge_rationalizing_2013] Online model
-
----
-
-```{mermaid}
-%%| label: fig-online-model
-%%| fig-cap: Online model of info processing
-%%| fig-width: 6.5
-graph TD;
-A[Pre-existing beliefs] --> C[Updated beliefs]
-B[New information] -->|If it aligns with current beliefs| C
-```
-
-## Amending those models with the Snap-judgment model
+# What do we know so far?
+
+## The study of visuals in politics
+
+---
+
+![[@bucy_editors_2021]](../../assets/slides/imgs/bucy_joo.png)
+
+---
+
+![](../../assets/slides/imgs/dan_arendt.png){.absolute bottom=0 left=0}
+![](../../assets/slides/imgs/lindholm_et-al.png){.absolute top=200 left=0}
+![](../../assets/slides/imgs/nina_et-al.png){.absolute top=0 left=0}
+
+---
+
+![[@schloss_politics_2014]](../../assets/slides/imgs/schloss_palmer.png){.absolute top=0 height=400}
+![[@williams_whats_2022]](../../assets/slides/imgs/williams_et-al.png){.absolute bottom=200 right=0 height=400}
+![[@casiraghi_colors_2022]](../../assets/slides/imgs/casiraghi_et-al.png){.absolute bottom=0 right=0 height=400}
+
+## Canonical models of **political** information processing
+
+---
+
+## Integrating key perspectives from the cognitive sciences
+
+---
+
+![[@collins_spreading-activation_1975]](../../assets/slides/imgs/collins_loftus.png){.absolute top=100}
+![[@fazio_attitudes_2007]](../../assets/slides/imgs/fazio.png){.absolute bottom=100}
+
+---
+
+![[@sander_cambridge_2013]](../../assets/slides/imgs/affective_neuro.jpg){.absolute top=100 height=600}
+![[@adolphs_emotion_2011]](../../assets/slides/imgs/affective_neuroscience.webp){.absolute bottom=100 right=0}
+
+---
+
+![[@zajonc_feeling_1980]](../../assets/slides/imgs/zajonc.png){.absolute top=50 right=50 height=300}
+![](../../assets/slides/imgs/erisen_et-al.png){.absolute bottom=50 left=50}
+
+## Canonical models of **political** information processing
+
+---
+
+![[@zaller_nature_1992]](../../assets/slides/imgs/zaller.jpg){.absolute left=0}
+![](../../assets/slides/imgs/zaller_feldman.png){.absolute right=0}
+![[@taber_motivated_2006]](../../assets/slides/imgs/taber_lodge.png){.absolute top=200 right=0}
+![[@lodge_rationalizing_2013]](../../assets/slides/imgs/lodge_taber.jpg){.absolute top=100}
+![[@taber_illusion_2016]](../../assets/slides/imgs/taber_lodge_2016.png){.absolute top=400}
+
+## A snap-judgment model of **visual** political information processing
 
@@
 {{< include ../../../assets/_theory.qmd >}}
+
+---
 

### 2023-10-12 chapter_2/src/slides/slides.qmd
updating the slides some more

@@
     scrollable: true
-    incremental: true
+    incremental: false
     slide-number: true
-    toc: true
-    toc-depth: 2
+    toc: false
+    #toc-depth: 2
     slide-level: 5
@@
 
-# Question guiding the project
-
-Is color a source of political information that shapes the public's behaviors and attitudes?
-
 # What do we know so far?
@@
 ![[@casiraghi_colors_2022]](../../assets/slides/imgs/casiraghi_et-al.png){.absolute bottom=0 right=0 height=400}
-
-## Canonical models of **political** information processing
-
----
 
@@
 - Collect around 1,000 yard signs from House elections
-  - 2016-2024
+  - 2016-2022
 - Measuring the colors used on a yard sign:
@@
 
-::: {#fig-trial-1}
-
-![Red condition](../study_1/assets/rep_yard_sign_round_1.png){#fig-red-1 width="6.5in"}
-
-![Blue condition](../study_1/assets/dem_yard_sign_round_1.png){#fig-blue-1 width="6.5in"}
-
-![White condition](../study_1/assets/cont_yard_sign_round_1.png){#fig-white-1 width="6.5in"}
+::: {.r-stack #fig-trial-1}
+
+![Red condition](../study_1/assets/rep_yard_sign_round_1.png){.fragment #fig-red-1 width="6.5in"}
+
+![Blue condition](../study_1/assets/dem_yard_sign_round_1.png){.fragment #fig-blue-1 width="6.5in"}
+
+![White condition](../study_1/assets/cont_yard_sign_round_1.png){.fragment #fig-white-1 width="6.5in"}
 
@@
 
-::: {#fig-trial-2}
-
-![Red condition](../study_1/assets/rep_yard_sign_round_2.png){#fig-red-2 width=6.5in}
-
-![Blue condition](../study_1/assets/dem_yard_sign_round_2.png){#fig-blue-2 width=6.5in}
-
-![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){#fig-white-2 width=6.5in}
+::: {.r-stack #fig-trial-2}
+
+![Red condition](../study_1/assets/rep_yard_sign_round_2.png){.fragment #fig-red-2 width=6.5in}
+
+![Blue condition](../study_1/assets/dem_yard_sign_round_2.png){.fragment #fig-blue-2 width=6.5in}
+
+![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment #fig-white-2 width=6.5in}
 
@@
 
-::: {#fig-trial-3}
-
-![Red condition](../study_1/assets/rep_yard_sign_round_3.png){#fig-red-3 width=6.5in}
-
-![Blue condition](../study_1/assets/dem_yard_sign_round_3.png){#fig-blue-3 width=6.5in}
-
-![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){#fig-white-3 width=6.5in}
+::: {.stack #fig-trial-3}
+
+![Red condition](../study_1/assets/rep_yard_sign_round_3.png){.fragment #fig-red-3 width=6.5in}
+
+![Blue condition](../study_1/assets/dem_yard_sign_round_3.png){.fragment #fig-blue-3 width=6.5in}
+
+![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment #fig-white-3 width=6.5in}
 
@@
 #| label: fig-h-2-predictions-2
+#| fig-cap: Blue yard signs = Democratic candidate
 blue <- predicted_prob_bar(
@@
 
+---
+
 ```{r}

### 2023-10-12 chapter_2/src/slides/slides.qmd
update a new draft of slides

@@
 
+---
+
+![[Kirkland Signature]()](../../assets/slides/imgs/kirkland.svg){#fig-kirkland width=6.5in}
+
+---
+
+![[BP]()](../../assets/slides/imgs/bp.png){#fig-bp width=6.5in}
+
+---
+
+![[Example of brand UI]()](../../assets/slides/imgs/green_bubble.jpeg){.absolute left=100 width=4.5in #fig-brand-ui}
+![[The great divide]()](../../assets/slides/imgs/green_bubble_funny.png){.absolute right=100 width=4.5in #fig-brand-divide}
+
 ## How are colors used in politics?
@@
 ![[@casiraghi_colors_2022]](../../assets/slides/imgs/casiraghi_et-al.png){.absolute bottom=0 right=0 height=400}
-
-## Integrating key perspectives from the cognitive sciences
-
----
-
-![[@collins_spreading-activation_1975]](../../assets/slides/imgs/collins_loftus.png){.absolute top=100}
-![[@fazio_attitudes_2007]](../../assets/slides/imgs/fazio.png){.absolute bottom=100}
-
----
-
-![[@sander_cambridge_2013]](../../assets/slides/imgs/affective_neuro.jpg){.absolute top=100 height=600}
-![[@adolphs_emotion_2011]](../../assets/slides/imgs/affective_neuroscience.webp){.absolute bottom=100 right=0}
-
----
-
-![[@zajonc_feeling_1980]](../../assets/slides/imgs/zajonc.png){.absolute top=50 right=50 height=300}
-![](../../assets/slides/imgs/erisen_et-al.png){.absolute bottom=50 left=50}
-
-## Canonical models of **political** information processing
-
----
-
-![[@zaller_nature_1992]](../../assets/slides/imgs/zaller.jpg){.absolute left=0}
-![](../../assets/slides/imgs/zaller_feldman.png){.absolute right=0}
-![[@taber_motivated_2006]](../../assets/slides/imgs/taber_lodge.png){.absolute top=200 right=0}
-![[@lodge_rationalizing_2013]](../../assets/slides/imgs/lodge_taber.jpg){.absolute top=100}
-![[@taber_illusion_2016]](../../assets/slides/imgs/taber_lodge_2016.png){.absolute top=400}
 

### 2023-10-12 chapter_2/src/roberts_empirical_chapter_1.qmd
doing a little bit of drafting to the article format of empirical chapter 1

@@
 I find that these associations of the color red with Republicans and the color blue with Democrats do exist among the public and that these associations are strong enough to shape support for political candidates.
-This chapter advances our understanding in a few areas: that visual information is a pre-conscious form of information that we should integrate with our models of information processing that consider more traditional forms of political information, provides a cognitive mechanism to explain how the public have come to associate the colors red and blue with the two dominant political parties, as well as demonstrates that these cognitive processes are capable of influencing behavior as important as vote choice.
+This chapter advances our understanding in a few areas: that visual information is a pre-cognitive form of information that we should integrate with our models of information processing that consider more traditional forms of political information, provides a cognitive mechanism to explain how the public have come to associate the colors red and blue with the two dominant political parties, as well as demonstrates that these cognitive processes are capable of influencing behavior as important as vote choice.
 additional-info: |
@@
 Reflecting on this, many scholars of neuroscience argue that visual information is the fastest form of information processing for humans.
-For example, even complex visual information, such as the warmth expressed in someone's facial features, is automatically and pre-consciously processed in only about 33 milliseconds (abbreviated as ms) [@ames_impression_2012].
+For example, even complex visual information, such as the warmth expressed in someone's facial features, is automatically and pre-cognitively processed in only about 33 milliseconds (abbreviated as ms) [@ames_impression_2012].
 
@@
 Existing models of political information processing (abbreviated here as *pip*) primarily focus on complex forms of political information, such as policy positions, communicated verbally or through text.
-As individuals process visual information before other sorts of information, we might expect that they may form a snap-judgment or the initial appraisal of an object with visual information as opposed to these more complex forms of information.
+As individuals process visual information pre-cognitively, we might expect that they may form a snap-judgment or the initial appraisal of an object with visual information as opposed to these more complex forms of information that often require more cognitive effort by varying orders of magnitude.
 
@@
 The visual information provides a snap-judgment or an impression of the object through faster processing, and activates particular neurological processes that influence subsequent information appraisals [@ames_impression_2012].
-This implies that snap-judgments from visual forms of political information may have downstream effects that shape the way in which we engage with traditionally considered forms of political information.
+This implies that snap-judgments from visual political information may have downstream effects that shape the way in which we engage with traditionally considered forms of political information.
 
@@
 
-In line with existing theories of *pip*, I conceptualize attitudes as associative.
-This means that attitudes may be unstable (though not in a random sense).
+In line with existing theories of *pip*, I use a popular conceptualization of attitudes as emerging from accessed associated memories [see @lodge_rationalizing_2013; see also @collins_spreading-activation_1975 for a perspective in a different application].
+The implication of such a conceptualization is that attitudes may be unstable (though not in a random sense).
 That is, as attitudes are associative, they manifest slightly differently depending on the associative paths activated [@fazio_attitudes_2007].
@@
 When individuals access a memory, they do not just recall an object, but they may recall visual information, such as the color of an object [@mehta_blue_2009].
-Due to these features, colors can be processed pre-consciously and very quickly [@mehta_blue_2009].
+Due to these features, colors are processed pre-cognitively [@mehta_blue_2009].
 As they are affectively encoded, their associations with particular memories contribute to the evaluative component of the memory.
 For example, individuals associate colors like red with anger and arousal [@valdez_effects_1994], whereas they associate blue with things like happiness and pleasure [@dandrade_colors_1974].
-This means that colors are compelling as contextual information that shapes the subsequent processing and integration of "traditional" forms of political information used to construct attitudes.
-As the preference for a particular color correlates with political attitudes [@schloss_politics_2014], colors may have some causal influence upon political attitudes.
 
-According to the literature in affective neuroscience, visual information is processed in various parts of the brain, such as the visual cortex [@goldstein_sensation_2017].
-These types of processes do not occur in discrete regions of the brain, as some like to think.
+The implication of such a process is that colors are compelling as contextual information that shapes the subsequent processing and integration of "traditional" forms of political information used to construct attitudes.
+As theories of affect transfer suggest, the affective reactions to our pre-cognitive processing of information persist when we transition to cognitive and post-cognitive states [@morris_activation_2003; see @taber_illusion_2016].
+As the preference for a particular color correlates with political attitudes [@schloss_politics_2014], I expect that colors may have a causal influence on post-cognitive expressions of political attitudes.
+
+According to the literature in affective neuroscience, visual information is processed in more than one region of the brain, such as the visual cortex [@goldstein_sensation_2017].
+That is, these types of processes do not occur in discrete regions of the brain, as some like to think.
 As attitudes are associative, components of the brain work as a complex highway connecting different types of information.
 As a result, the processing of visual information will activate other areas of the brain and will make associated paths "hot." One such area is the amygdala.
-Neuroscientists believe that as visual information is quickly and subconsciously processed, the amygdala takes and appraises it based on the paths it activated; this generates a simple affective response to such information [@winkielman_emotion_2011].
+Neuroscientists believe that as visual information is quickly and pre-cognitively processed, the amygdala takes and appraises it based on the paths it activated; this generates a simple affective response to such information [@winkielman_emotion_2011].
 
+<!--
 A less technical description of the processes occurring here might look something like this: once politically-relevant visual information is detected, the retina passes it to the brain.
@@
 For attitude formation, this implies that, as memories are affectively encoded [@kensinger_affective_2022], these memories help areas such as the amygdala to appraise the current information.
+-->
 
 These fast affective classifications are valanced rather than the more laborious categorization of specific emotions (e.g., anger, anxiety, fear, happiness).
-What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_emotions_2000], I think of affect as a more extensive system -- one that considers emotion a conscious classification process that occurs after the initial valanced appraisals of an object [@sander_cambridge_2013;@ralph_neuroscience_2018].
-That is, emotion -- the complex classification of appraisals -- is a conscious component of affect.
-By contrast, the pre-conscious process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_emotion_2011;@dror_deconstructing_2017].
+What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_emotions_2000], I conceptualize affect as a more extensive system -- one that considers emotion a cognitive classification process that occurs after the initial valanced appraisals of an object [@sander_cambridge_2013;@ralph_neuroscience_2018].
+That is, emotion -- the complex classification of appraisals -- is a cognitive component of affect.
+By contrast, the pre-cognitive process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_emotion_2011;@dror_deconstructing_2017].
 
-The pre-conscious appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_election_2011;@ralph_neuroscience_2018].
+The pre-cognitive appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_election_2011;@ralph_neuroscience_2018].
 This has evolutionary roots for survival [@ralph_neuroscience_2018;@parker_blink_2003].
@@
 
-While the visual information may encourage a particular immediate reaction to engage or disengage from the other information, subsequent information processing and more conscious processing adjusts this initial appraisal generated by the snap-judgment [@kensinger_affective_2022].
+While the visual information may encourage a particular immediate reaction to engage or disengage from the other information, subsequent information processing and more cognitive processing adjusts this initial appraisal generated by the snap-judgment [@kensinger_affective_2022].
 While subsequent information may amend one's snap-judgment, the snap-judgment nevertheless influences the processing of subsequent information by activating particular paths -- this is later encoded as associated with the object as it converts to a memory [@lodge_rationalizing_2013;@kensinger_affective_2022].
@@
 This is a valuable tool for survival that biology has optimized for millions of years [@parker_blink_2003].
-Rather than slowly processing the visual information and finding yourself in the jaws of a predator, or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and subconsciously [@newell_unified_1990].
+Rather than slowly processing the visual information and finding yourself in the jaws of a predator, or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and pre-cognitively [@newell_unified_1990].
 To make sense of such information, it accesses familiar information similar to what it is currently attempting to process, and it does this for the purposes of efficiency [@kahana_laws_2022].
 This means accessing memories that contain valanced information [@kensinger_affective_2022]: should I avoid this, or is it pleasant?
-Once the brain has finished such processing, it can pass its prediction to your conscious memory.
+Once the brain has finished such processing, it can pass its prediction to your cognitive memory.
 Once you form a reflex of avoid or approach, this opens up space for your brain to process the more complex information: to take the patterns of the light as shapes that construct symbols and letters.
@@
 There was an "E," an "L," and "E," a "C," and a "T." That creates the word "ELECT." Meaning to vote for.
-There were some more letters on the sign: an "M," and "I," a "T," a "C," and an "H." A name.
+There were some more letters on the sign.
+A name.
 The full name is "Mitch McConnell." Since it is about politics, it must be a politician named Mitch McConnell.
@@
 Social groupings are not simply abstract concepts invented by social psychologists; our neurobiology reflects them.
-For example, researchers find activation of parts of the brain, such as the anterior insula, when we see someone in our social group outperformed by someone from the out-group [see @zink_neural_2012].
+For example, researchers find activation of the anterior insula when we observe an instance of an in-group member outperformed by a member of an out-group [see @zink_neural_2012].
 The anterior insula activity is associated with physical and emotional pain, and not just for ourselves but also for others [@adolphs_emotion_2011].
-Others have also observed that when seeing someone part of a high-status social group, there is an increase in activity in the sensorimotor cortex and supplementary motor area, indicating more activity in the areas of the brain that encourage movement [@zink_know_2008].
+Others have also observed that when perceiving someone as part of a high-status social group, there is an increase in activity in the sensorimotor cortex and supplementary motor area, indicating more activity in the areas of the brain that encourage movement [@zink_know_2008].
 Visual information about someone in your social group speeds up processing, is more salient, and demands more attention than visual information about an object outside your social group [@zink_neural_2012].
@@
 
-In the comments above, we see some qualification in that there are other colors that can be useful beyond red and blue.
+In the comments above, we see some qualification that there are other colors which betray ideological positions.
 Still, a potential implication is that the value of colors associated with a particular place can be a way for candidates to communicate attachment to a district and its constituents.
 Still, there is a preference for campaigns to use as few colors as possible to save on costs -- simpler is better.
-What particularly stood out to me was when I was told:
+What particularly stood out was:
 
@@
 To gather evidence generalizing the belief that campaigns strategically use the colors red and blue to tap into possible associations of these colors with partisanship, I began by collecting data from the MIT Election Lab that reports the electoral results of the House of Representative elections from the years 1970-2020.
-The data tell me which candidate got how many votes in each House election across the United States.
-With these data, I calculate the rolling 5-year average of the Democratic party's vote share for each district.
+The data report the number of votes for each candidate in any given race.
+With these data, I calculate the rolling 5-year average of the Democratic party's vote share for each district to account for particularly unique electoral events.
 
-Next, I downloaded around 1,000 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design.
+Next, I use a combination of HTML and XML tags to identify then download around 1,000 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design.
 I used the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.
@@
 For example, I downloaded the GOP logo used on the GOP's official Twitter account during the 2022 midterm election cycle.
-To What `OpenCV` does is it loads the image and converts it to a three-dimensional `numpy` array that contains the GBR (reverse of RGB) values for the pixels in the image.
+`OpenCV` loads the image and converts it to a three-dimensional `numpy` array that contains the BGR (reverse of RGB) values for the pixels in the image.
 I standardize the image to be 224 $\times$ 224 pixels.
-The computer is trained to detect the range of the Republican red and Democrat blue colors.
+The computer is trained to detect the "Republican red" and "Democrat blue" colors.
 Once trained, the computer detects the pixels that do not contain values within the pre-specified range and converts those pixels to be black.
+To validate this classification and transformation of the pixels, I include the original image next to the transformed image in @fig-color-detection-example.
 
@@
 
-I then extract the non-black pixels in the array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$]
+I then extract the non-black pixels from my array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$]
 
@@
 I wanted to examine whether there are meaningful differences between districts that are partisan "strongholds" (Democrats or Republicans tend to get elected in a district) relative to districts that are much less so.
-To do this, I included a model with intercepts with no pooling.
-That is, a model that includes an intercept for each state-district unit.
-Though my outcome of interest (proportion of the yard sign that is red or blue) are continuous (it can take any real number, so not an integer), the outcome is bounded between 0 and 1.
+To do this, I specify a model that includes an intercept for each state-district unit.
+Though my outcome of interest (proportion of the yard sign that is red or blue) are continuous (it can take any real number), the outcome is bounded between 0 and 1.
 While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit, introduce systematic error, and lead to results that are quite unstable.
-To not bog down readers with a lot of technical jargon, the model that I end up using is called an ordered beta regression which allows me to efficiently and accurately predict outcomes that can be 0 or 1, or any real number between 0 and 1 [@kubinec_ordered_2022].
-For a more technical discussion about why I choose this over other techniques in the beta regression family, please see the [Appendix](#sec-2-a).
+To account for these concerns, I use an ordered beta regression which specifies a link function constraining the conditional distribution of the outcome to be between 0 and 1; as well as inducing cut-points akin to the fractional logistic regression which allows for the outcome to also appear as strictly equal to 0 or 1 [@kubinec_ordered_2022].
+Interested readers can find a discussion of how the ordered beta regression compares to other estimators in the beta regression family in [Appendix](#sec-2-a).
 
-Once I fit these models, I used the `marginaleffects` [@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as explained by the 5-year rolling average Democratic candidates' vote share.
-The grand mean here reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather that I am averaging across all districts to provide a single line in my figure.
+Once I fit these models, I used the `marginaleffects` [@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as it correlates with the 5-year rolling average Democratic candidates' vote share.
 These results are included in @fig-study-2-pred.
@@
 
-The results demonstrate that districts where Democrats are historically more successful see yard signs with a lower proportion of red on them, while those same districts see more blue on them.
-Again, these results do not claim that campaigns are doing this either because voters are encouraging them to take this strategy, or that they are doing it as a way to proactively get voters to make these associations.
-To tease out which of those questions is the right one requires more sophisticated approaches and data that could allow me to leverage redistricting (to see how these outcomes change due to some unrelated, external shock).
-The data available to me do not allow me to do that at this time.
-Rather, these data provide evidence consistent with the story I have relayed and the one provided to me in my informal conversations with practitioners.
+The results suggest a correlation between districts where Democrats are historically more electorally successful and a lower proportion of red on them.
+Inversely, those same districts tend to have yard signs with a higher proportion of blue on them.
+It is important to note that these results are strictly correlational.
+These results do not claim that campaigns are doing this either because voters are encouraging them to take this strategy, or that they are doing it as a way to proactively get voters to make these associations.
+Though I do control for unobserved confounds through removing district and year level pooling, there are a number of contextual features that may be unique to that particular district in a particular election year that I do not account for and can threaten claims of causal direction.
+Though the data available to me limit my ability make a causal claim, these data nonetheless provide evidence consistent with the story I have relayed and the one provided to me in my informal conversations with practitioners.
+
+Determining how political operatives formulate branding strategies for candidates is not the main focus of this story.
+While it helps me understand how the colors red and blue factor into decisions made on the ground by professional political marketers, like the existing evidence in other research, it does not answer my questions about whether these impressions about voters making these associations exist, nor does it tell me much about the cognitive mechanisms explaining these association.
+Further, the observational evidence also does not support any causal claim about the electoral ramifications of such processes.
 
@@
 
-I recruited participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where individuals are provided with a demographics and political attitudes questionnaire.
-As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly selected half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
+I recruited participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where I provided participants with a demographics and political attitudes questionnaire.
+Due to concerns about priming effects introduced by these questions as well as concerns of bias introduced by post-treatment control [@montgomery_how_2018], I randomly selected half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
 This questionnaire includes common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
@@
 I additionally included an open-ended question asking participants to describe their "first memory of a political event." The use of open-ended questions helps provide an attention check and identify duplicated responses for those spoofing IP addresses with a VPN [@kennedy_strategies_2021].
-Given estimates using these exclusion criteria, I expected that upwards of 40% of my original sample will fail these attention checks [@kennedy_strategies_2021], thus, the large target sample size.
 
@@
 In the first trial of the experiment, I randomly presented participants with one of three possible yard signs.
-These yard signs are simple, with the text "Riley Ready to Lead" and a solid background color of either "Republican red," "Democratic Blue," or White.^[See [Appendix](#sec-2-a) to view all of the stimuli used in [Study 1](#study-1).] There is an added component to this, as well as in the other two trials.
+These yard signs are simple, with the text "Riley Ready to Lead" and a solid background color of either "Republican red," "Democratic blue," or White.^[See [Appendix](#sec-2-a) to view all of the stimuli used in [Study 1](#study-1).] There is an added component to this, as well as in the other two trials.
 
@@
 population.
-This means that Mouseview.js was a handy tool for my study.
+As a result, Mouseview.js enabled me to take advantage of a survey experiment while capturing information about how participants explored the yard signs.
+
+To ensure that participants have a standardized initial placement of their cursor for each trial, I displayed a blank page before viewing the yard sign that requires participants to click a "Next" button.
+Immediately after clicking "Next," participants were shown the yard sign.
+The goal is to ensure that variation in where participants explore the image is not dependent on a non-standard starting point for their cursor.
 
 When viewing each yard sign in each of the three trials, there is a blur over a substantial portion of the screen.
-At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[I include a screenshot providing an example of what the participants were able to see with the blur included in the [Appendix](#sec-2-a).] Participants move their cursor to explore the yard sign.
-I alloted 5000 ms to perform the exploration before the image disappears; I did this to encourage a consistent and short duration to explore the image.^[In marketing research, some studies give participants about 6000 ms in eye-tracking studies to examine a brand and formulate an intention to purchase a product or not [@wedel_review_2008].
-With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure evoking images uses 1000 ms; but is intended to be an extended amount of time [@anwyl-irvine_mouseviewjs_2022].]
-
-After exploring the image in each trial, I asked participants whether they felt that the candidate supposedly owning the yard sign was a Democrat, a Republican, or Neither.
-After completing the three trials, I asked subjects to indicate their preference among the three images (one from each trial).
-
-To ensure that participants have a standardized initial placement of their cursor, I displayed a blank page before viewing the yard sign that requires participants to click a "Next" button.
-Immediately after clicking "Next," participants were shown the yard sign.
-The goal is to ensure that variation in where participants explore the image is not dependent on a non-standard starting point for their cursor.
-I additionally utilized a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
+At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[I include a screenshot providing an example of what the participants were able to see with the blur included in the [Appendix](#sec-2-a).] For the obstruction, I utilized a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
 The gaussian blur allowed participants to see a blurred visual field beyond the cursor.
@@
 As this requirement is enforced *before* joining the study, this should not have an effect on the number of excluded participants from my original sample.
+
+Participants move their cursor to explore the yard sign.
+I alloted 5000 ms to perform the exploration before the image disappears; I did this to encourage a consistent and short duration to explore the image and to formulate an impression of the candidate.^[In marketing research, some studies give participants about 6000 ms in eye-tracking studies to examine a brand and formulate an intention to purchase a product or not [@wedel_review_2008].
+With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure evoking images uses 1000 ms; but is intended to be an extended amount of time [@anwyl-irvine_mouseviewjs_2022].]
+
+After exploring the image in each trial, I asked participants whether they felt that the candidate supposedly owning the yard sign was a Democrat, a Republican, or Neither.
+After completing the three trials, I asked subjects to indicate their preference among the three signs (one from each trial).
 
@@
 Presumably, the more participants explore the yard sign, the more they are finding visual information that they can use to evaluate the candidate.
-While these two measures are simple proxies and are not direct measures of "noticing the yard sign," they allow us to get a sense of the patterns by which people explore the yard signs across treatment conditions.
+While these two measures are simple proxies and are not direct measures of "noticing the yard sign," they allow for one to get a sense of the patterns by which people explore the yard signs across treatment conditions.
 This also bolsters my confidence in the degree to which variation between the treatments among different groups of participants is due to actual differences in how people processed these treatments, and not due to random chance.
@@
 When interpreting the error bars, you will want to look at the difference in the error bars *between* yard sign treatments rather than *within* treatment.
+
 We see that the models indicate substantive and statistically meaningful differences between the yard sign treatments for each outcome.
 That is, the red and blue yard signs did shift people's perceptions of the partisanship of the candidate relative to the white yard sign.
-The credible intervals of these models are reported in the [Appendix](#sec-2-a) in @tbl-hypothesis-2-main which contains the rest of the results from these models.
-
-Digging in a little bit more about what these perceptions were, the predicted probability that subjects perceived the candidate with a red yard sign to be Republican is around 70%, whereas it is only about 30% when viewing a white yard sign.
-When given a red yard sign, the predicted probability the candidate is marked to be an independent is about 30% and less than 5% to be a Democrat.
-However, when viewing a blue yard sign, the predicted probability of a subject perceiving the candidate to be a Democrat is at about 50% whereas it is less at about 10% with a white yard sign.
-When viewing a blue yard sign, the predicted probability of subjects perceiving the candidate to be a Republican is less than 20% and about 45% to be an Independent.
-The full results are reported in @tbl-hypothesis-2-main in the [Appendix](#sec-2-a).
+Specifically, the evidence suggests that predicted probability of a subject perceiving the candidate with a red yard sign as a Republican is 70%, whereas it is only about 30% when viewing a white yard sign.
+The predicted probability that a participant perceived the candidate with the red yard sign as a Democrat is less than 5%.
+However, when viewing a blue yard sign, the predicted probability that a participant reports the candidate to be a Democrat is at about 50% whereas it is only about 10% if the yard sign is white.
+As we saw with the association between a Democratic candidate and a red yard sign, we see that the predicted probability that a participant perceived a candidate with a blue yard sign as a Republican is less than 20% and about 45% as an Independent.
+The full table of results for these models are reported in the [Appendix](#sec-2-a) in @tbl-hypothesis-2-main which contains the rest of the results from these models.
 
@@
 For example, I presented participants with primarily red (and presumably Republican) yard signs, but with some blue or white in them.
-I expected that the trials that use less "consistent" visual information demonstrate more uncertainty among respondents in their reported perceptions of the candidate's positions.
+I pre-registered that the trials that use less "consistent" visual information demonstrate more uncertainty among respondents in their reported perceptions of the candidate's positions.
 Specifically, I expected that participants would perceive the yard signs that have both red and blue on them as more moderate, and that the higher proportion of the color red or blue among the two colors will lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic, respectively.
@@
 In the appendix, @tbl-h-4-dispersion summarizes the time elapsed outcome variable; this demonstrates over-dispersion.
-Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.] I therefore fit two poisson-gamma models (sometimes referred to as negative binomial regressions).
+Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.] I therefore fit two poisson-gamma models (also referred to as negative binomial regressions).
 I am interested in explaining whether time elapsed can comes not only from the color of the yard sign that the subject is viewing, but also whether this effect is moderated by an individual's partisanship.
@@
 @fig-h-4 presents the average predicted elapsed time for participants in different contexts.
-Overall, these results communicate inconclusive support for my expectations on $H_4$ in either regression model.
+Overall, these results communicate inconclusive support for my pre-registered expectations on $H_4$ in either regression model.
 Strong Democrats do not appear to spend more time looking at red yard signs than white ones, but once I account for the variation in the data, I cannot be sure that these differences are not due to random chance.

### 2023-10-14 chapter_2/src/roberts_empirical_chapter_1.qmd
drafting some changes

@@
 
-Now that I have presented some background and have introduced the snap-judgment model of politically-relevant visual information, this chapter is a first attempt to tackle the question, "Do colors provide political information that shape attitudes?" There are two goals that I am hoping to achieve in this chapter.
+Do colors provide political information that shape attitudes among the mass public?
+There are two goals that I am hoping to achieve in this chapter.
 The first is to convince the reader that the colors red and blue convey affiliative information.
@@
 
+Many understand that colors are influential to shaping attitudes and behaviors in a number of ways.
+Color theorists and scholars of marketing understand color as having important implications for reactions to a product and resulting consumer behavior.
+For example, @kuo_impact_2023 demonstrate that hotel rooms that use more "cool colors" (blues, greens, etc.) evoke positive affect for potential customers and that these positive affective responses are predictive of their eventual choice to book the room.
+Colors mean a varying number of things, however.
+As a gross, yet intelligible example, yellow sweaters relative to yellow bodily fluids can elicit strong and very different responses.
+
+The role of visuals in politics is receiving more attention among interdisciplinary scholars in fields like communication, political science, and the psychological sciences.
+While many of these studies examine fascinating but complicated forms of visual information such as symbology [@williams_whats_2022] and visual framing [@grabe_image_2009], we have yet to integrate these interdisciplinary perspectives with existing models of political information processing to understand how these visual forms of information act as cues [see @lilleker_power_2019] but also what the consequences are for political behavior among the mass public.
+
+Building upon descriptive evidence suggesting that Democratic campaigns use the color blue more than Republican campaigns [@williams_whats_2022] and that Republican voters express a preference for red during election season [@schloss_politics_2014], I present a snap-judgment model of politically-relevant visual information processing that outlines the cognitive processes that drive these associations and how those associations drive important political outcomes.
+I use theories of associative memory and spreading activation [see @collins_spreading-activation_1975] to conceptualize the association of the colors red and blue with Republicans and Democrats as two interconnected nodes.
+Informed by conceptualizations of these connections as carrying affective information informed by perspectives on biological survival reaching back to Darwin [@ralph_neuroscience_2018], I argue that when these nodes are activated by exposure to these colors in political contexts, other related nodes become active and contain affective information.
+As partisanship evokes strong affective reactions for many members of the public [@iyengar_affect_2012], this activation elicits an affective reaction.
+Considering that most visual information and that these processes of association occur pre-consciously [@ames_impression_2012;@fazio_2007;@sander_cambridge_2013], I argue that the elicited affective response to such information can be "transferred" [see @morris_activation_2003;@taber_illusion_2016] to later post-cognitive processing of more traditional forms of political information such as stated policy positions.
+The implication being that these associations can inform reactions to political information and thus political behavior subconsciously.
+<!--
 This chapter applies the snap-judgment model to a simple case: the use of color on yard signs used by campaigns in elections.
@@
 An undertaking to address the specifics of this part of American political history would likely be a different book project.
+-->
 

### 2023-10-16 chapter_2/src/roberts_empirical_chapter_1.qmd
doing a bit more writing

@@
   Do the colors red and blue convey political information?
-If so, how do they shape candidate preferences and vote choice?
-Political psychologists rely on interdisciplinary approaches to construct theories of how we process political information.
-Likewise, those who study visual political information come from a number of disciplinary traditions to study how politics may be conveyed visually.
-As these groups of scholars are working in parallel, they have yet to fully integrate their work to construct a theory explaining the cognitive and behavioral consequences of visual information on political attitude expression and behavior.
-In this chapter, I present a snap-judgment model of visual information processing to demonstrate how visual information efficiently conveys substantive political information.
-Specifically, I focus on a simple but obvious case that we only have anecdotal and descriptive evidence of: the association between Republicans with the color red and Democrats with the color blue.
-First, I use supervised machine learning that does a pixel-by-pixel classification of the color on yard signs used by campaigns for the U.S.
-House of Representatives from 2016 to 2020 and merge this with election return data from the MIT Election Labs.
-From these data, I find that systematic descriptive evidence of campaigns using more red in their yard signs in districts that are safe for Republicans and campaigns using more blue in their yard signs in districts that are safe for Democrats.
-Next, I turn to an experiment to examine whether these associations of the colors red and blue with Republicans and Democrats exist among voters and whether it shapes attitude expression and behavior.
-I find that these associations of the color red with Republicans and the color blue with Democrats do exist among the public and that these associations are strong enough to shape support for political candidates.
-This chapter advances our understanding in a few areas: that visual information is a pre-cognitive form of information that we should integrate with our models of information processing that consider more traditional forms of political information, provides a cognitive mechanism to explain how the public have come to associate the colors red and blue with the two dominant political parties, as well as demonstrates that these cognitive processes are capable of influencing behavior as important as vote choice.
+While decisions of political branding are assumed to be significant for electoral outcomes, we have few theories about the cognitive processes underlying the processing of such information and whether these decisions influence realized political behavior.
+Building upon interdisciplinary perspectives, this chapter introduces the snap-judgment model of visual political information processing.
+The theory argues that color allows individuals to form pre-cognitive attitudes of a political object and that these pre-cognitive attitudes shape latter and more cognitively laborious information processing and behavior.
+Meaning, that we can activate partisan attachments automatically through information as simple as color.
+In the first study, I talk to a political marketing firm and use a pixel-by-pixel classification of images from over 1000 yard signs for elections in the U.S.
+House of Representatives.
+Evidence suggests that in districts where Democrats have an electoral advantage, there is more blue on the yard signs in the district.
+To examine the cognitive processes, I use a novel experimental design by tracking cursor movements and limiting participant's ability to view a yard sign to only 5000ms.
+I find that participants do make these associations when features of the yard sign are held constant and find that Republicans prefer candidates with red yard signs and that Democrats prefer candidates with blue yard signs.
 additional-info: |
@@
 ---
+
+{{< pagebreak >}}
 
@@
 As partisanship evokes strong affective reactions for many members of the public [@iyengar_affect_2012], this activation elicits an affective reaction.
-Considering that most visual information and that these processes of association occur pre-consciously [@ames_impression_2012;@fazio_2007;@sander_cambridge_2013], I argue that the elicited affective response to such information can be "transferred" [see @morris_activation_2003;@taber_illusion_2016] to later post-cognitive processing of more traditional forms of political information such as stated policy positions.
-The implication being that these associations can inform reactions to political information and thus political behavior subconsciously.
+Considering that most visual information and that these processes of association occur pre-cognitively [@ames_impression_2012;@fazio_attitudes_2007;@sander_cambridge_2013], I argue that the elicited affective response to such information can be "transferred" [see @morris_activation_2003;@taber_illusion_2016] to later post-cognitive processing of more traditional forms of political information such as stated policy positions.
+The implication being that these associations can inform reactions to political information and thus political behavior pre-cognitively.
 <!--
@@
 These findings bring much needed evidence in support of the conventional wisdom that the colors red and blue convey political information.
-Perhaps what is most intriguing about my results is that I find that the colors red and blue alone seem to make individuals willing to vote for a candidate.
-The association between the colors red and blue are strong enough that individuals express a willingness to cast a vote for a candidate based on the color of the candidate's yard sign; this occurs without the individual confirming that the candidate matches their policy stances or partisan affiliation.
-These tendencies, even if only based on a hunch among the professionals on the ground, seem to lead to descriptive differences in the use of these colors with respect to strategy.
-The following chapters dig a bit deeper into the idea that colors can shape attitudes, pitting the information individuals get from color against information gleaned from explicit policy stances.
+The implication of the theory and these findings are that partisan attachments are automatically activated through things as seemingly simple and ubiquitous as color.
+These activated partisan attachments then have causal effects for attitude expression and political behavior.
+Given the existing literature demonstrating low-levels of political engagement among the mass public [see @hibbing_stealth_2002] as well as the current hyper-polarized era [see @iyengar_affect_2012], this chapter's argument and findings suggests that voters need not consume any substantive political information before expressing a willingness to cast a vote for a candidate.
 
@@
 
-In line with existing theories of *pip*, I use a popular conceptualization of attitudes as emerging from accessed associated memories [see @lodge_rationalizing_2013; see also @collins_spreading-activation_1975 for a perspective in a different application].
+I use a popular conceptualization of attitudes as emerging from accessed associated memories [see @lodge_rationalizing_2013; see also @collins_spreading-activation_1975].
 The implication of such a conceptualization is that attitudes may be unstable (though not in a random sense).
@@
 
-What the snap-judgment model predicts is happening in your head is something like the following: as soon as the light bounces off the sign (to produce a particular wavelength) and reaches your eyes, your brain is already trying to make sense of this information.
+What the snap-judgment model predicts is happening in your head would be the following: as soon as the light bounces off the sign (to produce a particular wavelength) and reaches your eyes, your brain is already trying to make sense of this information.
 This is a valuable tool for survival that biology has optimized for millions of years [@parker_blink_2003].
@@
 In [Study 1](#study-1) I start with testing $H_5$.
-In some informal conversations that I had with political campaign professionals, it became clear that the descriptive evidence connecting the colors red and blue with Republicans and Democrats is still very much based on experience.
+Though my focus is on the cognitive mechanisms for individuals, I first wanted to examine whether practitioners of political marketing also perceive that these associations exist and are influential.
+In some informal conversations that I had with political campaign professionals, it became clear that the descriptive evidence connecting the colors red and blue with Republicans and Democrats is still very much based on instinct rather than empirical evidence.
 
@@
 
-It appears that campaigns recognize that these are not simply patterns that journalists [see @elving_color_2014] and researchers [see @williams_whats_2022] have picked up on, bit that they are associations held by voters and campaigns respond accordingly:
+It appears that campaigns recognize that these are not simply patterns that journalists [see @elving_color_2014] and researchers [see @williams_whats_2022] have picked up on, but that they are associations held by voters and campaigns respond accordingly:
 

### 2023-10-18 chapter_2/src/roberts_empirical_chapter_1.qmd
adding the summary stats of the measure for proportion of colors on yard signs

@@
 
-Next, I use a combination of HTML and XML tags to identify then download around 1,000 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design.
+Next, I use a combination of HTML and XML tags to identify then download around 1,000 yard signs from House elections from the years 2016 to 2022 from the website provided by the Center for American Politics and Design.
 I used the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.
@@
 
-I then extract the non-black pixels from my array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$]
+I then extract the non-black pixels from my array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$] Summary statistics of these calculated proportions for red and blue are included in the [Appendix](#tbl-yard-sign-summary).
 

### 2023-10-18 chapter_2/src/slides/slides.qmd
adding the summary stats of the measure for proportion of colors on yard signs

@@
     incremental: false
-    slide-number: true
+    slide-number: false
+    progress: false
+    menu: false
     toc: false
@@
     output-file: color-book.html
+    fig-responsive: false
+    margin: 0.1
 execute:
@@
   freeze: true
+  eval: true
+  cache: true
 nocite: |
@@
 load("../../data/temp/models/study_1_fitted.RData")
+# Load data for study 2
+df_study_2 <- read.csv("../../data/clean/study_2.csv") |>
+  as.data.table()
+  #* convert state_district and year variables  to factors
+df_study_2 <- df_study_2[
+  , year := tstrsplit(year, "-", keep = 1)
+][
+  , year := as.numeric(year)
+][
+  , state_district := factor(state_district)
+][
+  , blue_prop := blue_percent / 100
+][
+  , red_prop := red_percent / 100
+]
 ```
@@
 
+![[Shell]()](../../assets/slides/imgs/shell.png){#fig-shell width=6.5in}
+
+---
+
+---
+
+```{mermaid}
+%%| label: fig-shell-color
+%%| fig-cap: Associative memory
+%%| eval: true
+flowchart LR;
+
+A["Yellow"]
+A --> B["Banana"]
+A --> C["Rubber duck"]
+A --> D["Shell"]
+A --> E["Leaves"]
+```
+
+---
+
+```{mermaid}
+%%| label: fig-shell-affect
+%%| fig-cap: Object evaluation
+%%| eval: true
+flowchart LR;
+
+A["Yellow"]
+A -.-> B["Banana"]
+A -.-> C["Rubber duck"]
+A --> D["Shell"]
+A -.-> E["Leaves"]
+D --> F["Avoid"]
+```
+
+---
+
+<!--
+---
+
 ![[Kirkland Signature]()](../../assets/slides/imgs/kirkland.svg){#fig-kirkland width=6.5in}
@@
 
+-->
 ![[Example of brand UI]()](../../assets/slides/imgs/green_bubble.jpeg){.absolute left=100 width=4.5in #fig-brand-ui}
@@
 
-### Outcome variable - How much red and blue do campaigns use?
+### Measurement: How much red and blue do campaigns use?
 
@@
 
-### Predictor variable - What is the partisan composition of the district?
+---
+
+```{r}
+#| label: tbl-yard-sign-summary
+#| tbl-cap: Summary statistics
+names(df_study_2)[names(df_study_2) == 'red_percent'] <- '% Red'
+names(df_study_2)[names(df_study_2) == 'blue_percent'] <- '% Blue'
+names(df_study_2)[names(df_study_2) == 'white_percent'] <- '% White'
+
+df_study_2_subset <- df_study_2[, c('% Red', '% Blue', '% White')]
+datasummary_skim(
+  df_study_2_subset
+  , notes = "Data source: CAPD Yard Signs."
+  , histogram = FALSE
+)
+
+```
+
+### Measurement: What is the partisan composition of the district?
 
@@
 
-### Do campaigns use a different proportion of the colors red and blue based on partisan composition?
+### Do campaigns use a different proportion of the colors red and blue in different constituency compositions?
 
@@
 
-::: {.r-stack #fig-trial-1}
-
-![Red condition](../study_1/assets/rep_yard_sign_round_1.png){.fragment #fig-red-1 width="6.5in"}
-
-![Blue condition](../study_1/assets/dem_yard_sign_round_1.png){.fragment #fig-blue-1 width="6.5in"}
-
-![White condition](../study_1/assets/cont_yard_sign_round_1.png){.fragment #fig-white-1 width="6.5in"}
-
-Trial 1
+::: {.r-stack}
+
+![](../study_1/assets/rep_yard_sign_round_1.png){.fragment width="6.5in"}
+
+![](../study_1/assets/dem_yard_sign_round_1.png){.fragment width="6.5in"}
+
+![](../study_1/assets/cont_yard_sign_round_1.png){.fragment width="6.5in"}
+
 :::
@@
 
-::: {.r-stack #fig-trial-2}
-
-![Red condition](../study_1/assets/rep_yard_sign_round_2.png){.fragment #fig-red-2 width=6.5in}
-
-![Blue condition](../study_1/assets/dem_yard_sign_round_2.png){.fragment #fig-blue-2 width=6.5in}
-
-![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment #fig-white-2 width=6.5in}
-
-Trial 2
+::: {.r-stack}
+
+![](../study_1/assets/rep_yard_sign_round_2.png){.fragment width=6.5in}
+
+![](../study_1/assets/dem_yard_sign_round_2.png){.fragment width=6.5in}
+
+![](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment width=6.5in}
+
 :::
@@
 
-::: {.stack #fig-trial-3}
-
-![Red condition](../study_1/assets/rep_yard_sign_round_3.png){.fragment #fig-red-3 width=6.5in}
-
-![Blue condition](../study_1/assets/dem_yard_sign_round_3.png){.fragment #fig-blue-3 width=6.5in}
-
-![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment #fig-white-3 width=6.5in}
-
-Trial 3
+::: {.r-stack}
+
+![](../study_1/assets/rep_yard_sign_round_3.png){.fragment width=6.5in}
+
+![](../study_1/assets/dem_yard_sign_round_3.png){.fragment width=6.5in}
+
+![](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment width=6.5in}
+
 :::

### 2023-10-23 chapter_2/src/slides/slides.qmd
updating the slides a bit

@@
 format:
-  revealjs:
+    simpledarkjs-revealjs:
         multiplex: true
-    embed-resources: true
-    theme: [dark, ../../assets/slides/custom.scss]
-    transition: slide
-    scrollable: true
-    incremental: false
-    slide-number: false
-    progress: false
-    menu: false
-    toc: false
-    #toc-depth: 2
+        output-file: color-book.html
         slide-level: 5
+        transition: none
 bibliography: ../../../assets/candidate_support_chapter_references.bib
-    self-contained: true
-    output-file: color-book.html
-    fig-responsive: false
-    margin: 0.1
 execute:
@@
 nocite: |
-  @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017,
+    @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017
 ---
@@
 
+![Aaron Bashir (R), PA-3](../../assets/slides/imgs/bashir.webp){#fig-bashir .absolute left=0 top=100}
+![Dwight Evans (D), PA-2](../../assets/slides/imgs/evans.webp){#fig-evans .absolute right=0 bottom=100}
+
+---
+
 ```{r}
@@
 
-![[Shell]()](../../assets/slides/imgs/shell.png){#fig-shell width=6.5in}
-
----
-
----
-
-```{mermaid}
-%%| label: fig-shell-color
-%%| fig-cap: Associative memory
-%%| eval: true
-flowchart LR;
-
-A["Yellow"]
-A --> B["Banana"]
-A --> C["Rubber duck"]
-A --> D["Shell"]
-A --> E["Leaves"]
-```
-
----
-
-```{mermaid}
-%%| label: fig-shell-affect
-%%| fig-cap: Object evaluation
-%%| eval: true
-flowchart LR;
-
-A["Yellow"]
-A -.-> B["Banana"]
-A -.-> C["Rubber duck"]
-A --> D["Shell"]
-A -.-> E["Leaves"]
-D --> F["Avoid"]
-```
-
----
-
-<!--
----
-
-![[Kirkland Signature]()](../../assets/slides/imgs/kirkland.svg){#fig-kirkland width=6.5in}
-
----
-
-![[BP]()](../../assets/slides/imgs/bp.png){#fig-bp width=6.5in}
-
----
-
--->
-![[Example of brand UI]()](../../assets/slides/imgs/green_bubble.jpeg){.absolute left=100 width=4.5in #fig-brand-ui}
-![[The great divide]()](../../assets/slides/imgs/green_bubble_funny.png){.absolute right=100 width=4.5in #fig-brand-divide}
+![Nebraska](../../assets/slides/imgs/nebraska.jpg){#fig-nebraska width=6.5in}
+
+---
+
+![[Example of brand UI]](../../assets/slides/imgs/green_bubble.jpeg){.absolute left=100 width=4.5in #fig-brand-ui}
+![[The great divide]](../../assets/slides/imgs/green_bubble_funny.png){.absolute right=100 width=4.5in #fig-brand-divide}
 
@@
 
+![[1924 Election Map](https://collections.leventhalmap.org/search/commonwealth:q524n296b)](../../assets/slides/imgs/election_map.jpg){#fig-1924-map}
+
+---
+
+![[1976 Election Map](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.washingtonpost.com%2Fnews%2Fthe-fix%2Fwp%2F2016%2F11%2F08%2Fred-vs-blue-a-brief-history-of-how-we-use-political-colors%2F&psig=AOvVaw1tL5UeACMye7NTm5hvZG-A&ust=1698159827386000&source=images&cd=vfe&opi=89978449&ved=0CBIQjhxqFwoTCKil57-4jIIDFQAAAAAdAAAAABAI)](../../assets/slides/imgs/1976_map.webp){#fig-1976-map}
+
+---
+
 ![[2000 Presidential Election Map](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=6.5in}
@@
 # What do we know so far?
+
+---
 
@@
 
-{{< include ../../../assets/_theory.qmd >}}
+```{mermaid}
+%%| label: fig-snap-judgment-model
+%%| fig-cap: Overview of model
+
+flowchart TD;
+A[Detection of color] --> B[Activation of associated memories]
+B --> C[Negative Valence]
+B --> D[Positive Valence]
+C -.-> E[Policy stance]
+D -.-> F[Policy stance]
+E -.-> G[Negative Valence]
+E -.-> H[Positive Valence]
+F -.-> I[Negative Valence]
+F -.-> J[Positive Valence]
+```
 
@@
 red_lower = [93, 9, 12] # lower end of spectrum for red
-red_higher = [237, 69, 75] # higher end of spectrum for red
+red_higher = [255, 170, 170] # higher end of spectrum for red
 

### 2023-10-23 chapter_2/src/slides/simple.qmd
updating the slides again

--- 2023-10-18 chapter_2/src/slides/slides.qmd
@@
 ---
-title: "The Shape and Color of Politics"
+title: The Shape and Color of Politics
 author: 
@@
 format:
-  revealjs:
+    simpledarkjs-revealjs:
         multiplex: true
-    embed-resources: true
-    theme: [dark, ../../assets/slides/custom.scss]
-    transition: slide
-    scrollable: true
-    incremental: false
-    slide-number: false
-    progress: false
-    menu: false
-    toc: false
-    #toc-depth: 2
-    slide-level: 5
+        output-file: color-book.html
 bibliography: ../../../assets/candidate_support_chapter_references.bib
-    self-contained: true
-    output-file: color-book.html
-    fig-responsive: false
-    margin: 0.1
 execute:
@@
 
+![Aaron Bashir (R), PA-3](../../assets/slides/imgs/bashir.webp){#fig-bashir .absolute left=0 top=100}
+![Dwight Evans (D), PA-2](../../assets/slides/imgs/evans.webp){#fig-bashir .absolute right=0 bottom=100}
+
+---
+
 ```{r}
@@
 
-![[Shell]()](../../assets/slides/imgs/shell.png){#fig-shell width=6.5in}
+![Nebraska](../../assets/slides/imgs/nebraska.jpg)
 
 ---
-
----
-
-```{mermaid}
-%%| label: fig-shell-color
-%%| fig-cap: Associative memory
-%%| eval: true
-flowchart LR;
-
-A["Yellow"]
-A --> B["Banana"]
-A --> C["Rubber duck"]
-A --> D["Shell"]
-A --> E["Leaves"]
-```
-
----
-
-```{mermaid}
-%%| label: fig-shell-affect
-%%| fig-cap: Object evaluation
-%%| eval: true
-flowchart LR;
-
-A["Yellow"]
-A -.-> B["Banana"]
-A -.-> C["Rubber duck"]
-A --> D["Shell"]
-A -.-> E["Leaves"]
-D --> F["Avoid"]
-```
-
----
-
-<!--
----
-
-![[Kirkland Signature]()](../../assets/slides/imgs/kirkland.svg){#fig-kirkland width=6.5in}
-
----
-
-![[BP]()](../../assets/slides/imgs/bp.png){#fig-bp width=6.5in}
-
----
-
--->
-![[Example of brand UI]()](../../assets/slides/imgs/green_bubble.jpeg){.absolute left=100 width=4.5in #fig-brand-ui}
-![[The great divide]()](../../assets/slides/imgs/green_bubble_funny.png){.absolute right=100 width=4.5in #fig-brand-divide}
-
-## How are colors used in politics?
-
----
-
-![[1860s Ballots](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)](../../assets/slides/imgs/ballots.avif){#fig-1860-ballot}
-
----
-
-::: {#fig-1980-convention layout-ncol=2}
-
-![[Democratic National Convention](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)](../../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem width=6.5in}
-
-![[Republican National Convention]((../../assets/slides/imgs/1980_rep_convention.jpg))](../../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep width=6.5in}
-
-1980 Presidential Party National Conventions
-:::
-
----
-
-![[2000 Presidential Election Map](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=6.5in}
-
----
-
-::: {#fig-party-brand layout-ncol=2}
-
-![Republicans pre-2000](../assets/img/rnc_logo_pre-2000.png){#fig-republican}
-
-![Democrats pre-2000](../assets/img/dnc_logo_1960.png){#fig-democrat}
-
-![Republicans 2023](../assets/img/rnc_logo_2023.png){#fig-republican-post}
-
-![Democrats 2023](../assets/img/dnc_logo_2023.png){#fig-democrat-post}
-
-Party logos
-:::
-
----
-
-![[The public](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)](../../assets/slides/imgs/division.webp){#fig-public width=6.5in}
-
-# What do we know so far?
-
-## The study of visuals in politics
-
----
-
-![[@bucy_editors_2021]](../../assets/slides/imgs/bucy_joo.png)
-
----
-
-![](../../assets/slides/imgs/dan_arendt.png){.absolute bottom=0 left=0}
-![](../../assets/slides/imgs/lindholm_et-al.png){.absolute top=200 left=0}
-![](../../assets/slides/imgs/nina_et-al.png){.absolute top=0 left=0}
-
----
-
-![[@schloss_politics_2014]](../../assets/slides/imgs/schloss_palmer.png){.absolute top=0 height=400}
-![[@williams_whats_2022]](../../assets/slides/imgs/williams_et-al.png){.absolute bottom=200 right=0 height=400}
-![[@casiraghi_colors_2022]](../../assets/slides/imgs/casiraghi_et-al.png){.absolute bottom=0 right=0 height=400}
-
-## A snap-judgment model of **visual** political information processing
-
----
-
-{{< include ../../../assets/_theory.qmd >}}
-
----
-
-- Implications
-  - Refines existing info. processing models to consider pre-conscious influences.
-  - Outlines the cognitive processes undergirding how we:
-    - have made associations between the colors red and blue with the two parties.
-    - form attitudes and behaviors based on less substantive information (e.g., policy stances).
-
-## Study 1
-
-### Motivation of Study
-
----
-
-> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
-We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
-The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
-
----
-
-> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
-
----
-
-- Do these associations have systematic influences on campaign strategy? (Study 1)
-- Are these hunches correct that these colors can reliably cue partisanship? (Study 2)
-
-### Measurement: How much red and blue do campaigns use?
-
----
-
-- Collect around 1,000 yard signs from House elections
-  - 2016-2022
-- Measuring the colors used on a yard sign:
-  - Use a machine learning Python Library, `OpenCV` [@bradski_opencv_2000], that reads images and classifies their components.
-    - Trained to classify each pixel in the image
-    - Classifies it based on BGR value (reverse of RGB)
-    - Looks for a range of values around the "Republican red" and "Democratic blue"
-
----
-
-```{python}
-#| label: example detection
-#| echo: false
-
-from sys import path # for path management
-from cv2 import imread, imwrite # for color detection
-    #* user-defined
-sys.path.append("../")
-from PY.helper import colorDetector
-
-# Define colors to detect
-    #* White
-        #** Not defined. Default for colorDetector()
-    #* Red
-republican_red = [232, 27, 35] # target color
-red_lower = [93, 9, 12] # lower end of spectrum for red
-red_higher = [237, 69, 75] # higher end of spectrum for red
-
-# Load gop image to read
-img = imread("../assets/img/gop_2022.png")
-
-# Detect colors
-percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
-
-transformed= imwrite("../../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
-
-masked= imwrite("../../data/temp/study_2/gop_2022_detected.png", result) # save masked image
-```
-
-::: {#fig-color-detection-example layout-ncol="2"}
-![Resized original image](../../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
-
-![Masked](../../data/temp/study_2/gop_2022_detected.png){#fig-masked}
-
-Detecting colors in the GOP logo
-:::
-
-```{python}
-#| output: asis
-# Print calculated percentage of example
-print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
-```
-
----
-
-```{r}
-#| label: tbl-yard-sign-summary
-#| tbl-cap: Summary statistics
-names(df_study_2)[names(df_study_2) == 'red_percent'] <- '% Red'
-names(df_study_2)[names(df_study_2) == 'blue_percent'] <- '% Blue'
-names(df_study_2)[names(df_study_2) == 'white_percent'] <- '% White'
-
-df_study_2_subset <- df_study_2[, c('% Red', '% Blue', '% White')]
-datasummary_skim(
-  df_study_2_subset
-  , notes = "Data source: CAPD Yard Signs."
-  , histogram = FALSE
-)
-
-```
-
-### Measurement: What is the partisan composition of the district?
-
----
-
-- MIT Election Lab data
-  - House election results
-  - 1970-2020
-- Measuring partisan composition of district:
-  - Calculate rolling 5-year average of the Democratic party's vote share for each district
-
-### Do campaigns use a different proportion of the colors red and blue in different constituency compositions?
-
----
-
-```{r}
-#| label: fig-study-2-pred-1
-#| fig-cap: More blue on the yard signs in Democratic strongholds
-
-blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["blue"]]
-  , treatment = "Blue"
-  , hypothesis = "H5"
-)
-
-blue
-```
-
----
-
-```{r}
-#| label: fig-study-2-pred-2
-#| fig-cap: Less red on the yard signs in Democratic strongholds
-
-red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["red"]]
-  , treatment = "Red"
-  , hypothesis = "H5"
-)
-red
-```
-
-## Study 2
-
-### Motivation of the experiment
-
-- Do we associate the color red with Republicans and the color blue with Democrats?
-- Do these associations provide information that the public act on in politics?
-
-### Setup of the experiment
-
----
-
-#### Background information
-
-- Age
-- Education
-- Gender Identity
-- Sex
-- Visual impairments
-  - Including colorblindness
-- Party Identification
-
----
-
-#### Treatment
-
-- Three trials
-
----
-
-::: {.r-stack}
-
-![](../study_1/assets/rep_yard_sign_round_1.png){.fragment width="6.5in"}
-
-![](../study_1/assets/dem_yard_sign_round_1.png){.fragment width="6.5in"}
-
-![](../study_1/assets/cont_yard_sign_round_1.png){.fragment width="6.5in"}
-
-:::
-
----
-
-::: {.r-stack}
-
-![](../study_1/assets/rep_yard_sign_round_2.png){.fragment width=6.5in}
-
-![](../study_1/assets/dem_yard_sign_round_2.png){.fragment width=6.5in}
-
-![](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment width=6.5in}
-
-:::
-
----
-
-::: {.r-stack}
-
-![](../study_1/assets/rep_yard_sign_round_3.png){.fragment width=6.5in}
-
-![](../study_1/assets/dem_yard_sign_round_3.png){.fragment width=6.5in}
-
-![](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment width=6.5in}
-
-:::
-
-#### Design
-
-- Recruited 1,000 participants from Prolific
-- Counterbalance treatment and background information ($\frac{1}{2}$ see treatment first; other $\frac{1}{2}$ see background questions first)
-- Within each trial, participants have $\frac{1}{3}$ chance of seeing any given yard sign.
-- MouseView.js [@anwyl-irvine_mouseviewjs_2022]
-
----
-
-![Example of treatment](../../assets/slides/imgs/treatment.gif){#fig-treatment-example width=6.5in}
-
-### Do people make these associations?
-
----
-
-```{r}
-#| label: fig-h-2-predictions-1
-#| fig-cap: Red yard signs = Republican candidate
-red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2"]][["red_multinomial"]]
-  , x_axis = "trial_1_red_stimuli"
-)
-red
-```
-
----
-
-```{r}
-#| label: fig-h-2-predictions-2
-#| fig-cap: Blue yard signs = Democratic candidate
-blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2"]][["blue_multinomial"]]
-  , x_axis = "trial_1_blue_stimuli"
-  , treatment = "Blue"
-)
-blue
-```
-
-### What does conflicting colors do to these associations?
-
----
-
-```{r}
-#| label: fig-h-2a-predictions
-#| layout-nrow: 2
-#| fig-cap: Mixing red and blue in a yard sign increases uncertainty about partisanship
-#| fig-subcap:
-#|   - Trial 2 Red treatment
-#|   - Trial 2 Blue treatment
-#|   - Trial 3 Red treatment
-#|   - Trial 3 Blue treatment
-plot_trial_2_red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_2_red_multinomial"]]
-  , x_axis = "trial_2_red_stimuli"
-)
-plot_trial_2_blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_2_blue_multinomial"]]
-  , x_axis = "trial_2_blue_stimuli"
-  , treatment = "Blue"
-)
-plot_trial_3_red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_3_red_multinomial"]]
-  , x_axis = "trial_3_red_stimuli"
-)
-plot_trial_3_blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_3_blue_multinomial"]]
-  , x_axis = "trial_3_blue_stimuli"
-  , treatment = "Blue"
-)
-plot_trial_2_red
-plot_trial_2_blue
-plot_trial_3_red
-plot_trial_3_blue
-```
-
-### Do these associations inform important political behavior?
-
----
-
-```{r}
-#| label: fig-h-3-predictions-1
-#| fig-cap: Republicans are more likely to vote for candidate with red yard sign, Democrats less likely
-red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_3"]][["red"]]
-  , x_axis = "trial_1_red_stimuli"
-  , treatment = "Red"
-  , hypothesis = "H3"
-  , x_label = "Party ID"
-  , y_label = "Pr(Vote for candidate)"
-  , legend_title = "Treatment"
-)
-
-red
-```
-
----
-
-```{r}
-#| label: fig-h-3-predictions-2
-#| fig-cap: Democrats are more likely to vote for candidate with blue yard signs, Republicans less likely
-blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_3"]][["blue"]]
-  , x_axis = "trial_1_blue_stimuli"
-  , treatment = "Blue"
-  , hypothesis = "H3"
-  , x_label = "Party ID"
-  , y_label = "Pr(Vote for candidate)"
-  , legend_title = "Treatment"
-)
-
-blue
-```
-
-## Questions and Comments
 
@@
 
-## Appendix
+## License
 
-### Study 1
+Shield: [![CC BY 4.0][cc-by-shield]][cc-by]
 
----
+This work is licensed under a
+[Creative Commons Attribution 4.0 International License][cc-by].
 
-#### Characteristics of sample
+[![CC BY 4.0][cc-by-image]][cc-by]
 
----
-
-```{r}
-#| label: tbl-study-1-descriptives
-#| tbl-cap: Descriptive statistics of Prolific sample
-
-df_demographics_subset <- list_df[["cleaned"]][
-    , c(
-        "Age" = "age"
-        , `Color blind` = "color_blind_dummy"
-        , "Female" = "female_sex"
-        , "White" = "white"
-        , "Hispanic" = "hispanic"
-        , "Black" = "black"
-        , `Party ID` = "pid_7"
-    )
-] |> 
-as.data.frame()
-
-datasummary_skim(
-    df_demographics_subset
-    , histogram = FALSE
-    , notes = c(
-      "Data source: Prolific."
-      , "Sample characteristics."
-    )
-
-)
-```
-
----
-
-#### Measures
-
----
-
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Measure                     | Question                                                                                                                                                                                                                                                                                                  | Coded as                                                                                                                                                           |
-+=============================+:=========================================================================================================================================================================================================================================================================================================:+:==================================================================================================================================================================:+
-| Age                         | Confirm your age                                                                                                                                                                                                                                                                                          | Text entry                                                                                                                                                         |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Gender                      | What is your gender identity?
-| Non-binary, Female, Male, Prefer not to choose, Other                                                                                                              |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Sex                         | What is your sex assigned at birth?
-| Female, Male, Other                                                                                                                                                |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Race                        | Which ethnic or racial category best describes you?
-| White, non-Hispanic; Black, non-Hispanic; Hispanic; Asian or Native Hawaiian/other Pacific Islander; Native American/Alaska Native or other race; Multiple races   |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Color blind                 | Have you been diagnosed with any of the following visual impairments that are not treated with corrective lenses?
-| Color blindness (any form); Blurred vision (not treatable by corrective lenses); Macular degeneration; Glaucoma; Cataract; Diabetic retinopathy; None of the above |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Attention                   | How often do you pay attention to what is going on in government and politics?
-| Always; Most of the time; About half the time; Some of the time; Never                                                                                             |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Party ID                    | Generally speaking, do you usually think of yourself as a Democrat, a Republican, an Independent, or what?; Would you say that you are a strong [Republican/Democrat] or not a very strong [Republican/Democrat]?; Do you think of yourself as closer to the Republican party or to the Democratic party?
-| Republican, Democrat, Independent, Other; Strong, Not very strong; Closer to the Republican party, Neither, Closer to Democratic                                   |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Attn.
-Check                 | In a few words describe what is your first memory of a political event.
-| Text entry                                                                                                                                                         |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Trial stimuli               | Yard sign assigned                                                                                                                                                                                                                                                                                        | 0 = White, 1 = Red/Blue                                                                                                                                            |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Trial stimuli alt           | Yard sign assigned                                                                                                                                                                                                                                                                                        | 0 = Not red/blue, 1 = Red/Blue                                                                                                                                     |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Time elapsed                | NA                                                                                                                                                                                                                                                                                                        | Difference between time at start of trial and stop                                                                                                                 |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| $\Delta_{t}$ (milliseconds) | NA                                                                                                                                                                                                                                                                                                        | Time elapsed between cursor movements                                                                                                                              |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| $\Delta_{x}$ (pixels)       | NA                                                                                                                                                                                                                                                                                                        | Number of pixels moved along x-axis                                                                                                                                |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| $\Delta_{y}$ (pixels)       | NA                                                                                                                                                                                                                                                                                                        | Number of pixels moved along y-axis                                                                                                                                |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Candidate party             | Is this candidate a Republican, a Democrat, or Neither?
-| Republican, Democrat, Neither                                                                                                                                      |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Candidate vote              | Of the three candidates who would you most likely vote for?
-| The first yard sign, The second yard sign, The third yard sign                                                                                                     |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| Candidate vote indicator    | NA                                                                                                                                                                                                                                                                                                        | 0 = Would not vote for first yard sign, 1 = Would vote for first yard sign                                                                                         |
-+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-
-: Study 1 Measures {#tbl-study-1-measures}
-
-#### $H_1$
-
-```{r}
-#| label: tbl-h1-trial-1
-#| tbl-cap: Average time between cursor movements (Trial 1)
-df_movement_trial_1 <- list_df[["cleaned"]][
-  , c(
-    "trial_1_difference_Time"
-    , "trial_1_stimulus"
-    , "trial_1_difference_X"
-    , "trial_1_difference_Y"
-  )
-]
-setnames(
-  df_movement_trial_1
-  , old = c(
-    "trial_1_difference_Time"
-    , "trial_1_difference_X"
-    , "trial_1_difference_Y"
-  )
-  , new = c(
-    "Δ<sub>t</sub> (milliseconds)"
-    , "Δ<sub>x</sub> (pixels)"
-    , "Δ<sub>y</sub> (pixels)"
-  )
-)
-
-datasummary_balance(
-  ~trial_1_stimulus
-  , data = df_movement_trial_1
-  , notes = "Data source: Prolific sample."
-  , escape = FALSE
-)
-```
-
----
-
-#### $H_2$
-
----
-
-##### Multinomial Logit
-
-```{r}
-#| label: tbl-hypothesis-2-main
-#| tbl-cap: Full results for reported models in $H_2$
-# Redefine names
-list_fitted_split_1 <- list(
-  "Red treatment" = list_fitted[["h_2"]][["red_multinomial"]]
-  , "Blue treatment" = list_fitted[["h_2"]][["blue_multinomial"]]
-)
-
-# Change goodness of fit stuff
-gm <- list(
-  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
-  , list("raw" = "r.squared", "clean" = "R<sup>2</sup>", "fmt" = 2)
-  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
-)
-# Make table
-modelsummary(
-  list_fitted_split_1
-  , coef_map = c(
-    "b_mu2_trial_1_red_stimuli" = "Red yard sign (Independent)"
-    , "b_mu3_trial_1_red_stimuli" = "Red yard sign (Republican)"
-    , "b_mu2_trial_1_blue_stimuli" = "Blue yard sign (Independent)"
-    , "b_mu3_trial_1_blue_stimuli" = "Blue yard sign (Republican)"
-    , "b_mu2_Intercept" = "Intercept - Independent"
-    , "b_mu3_Intercept" = "Intercept - Republican"
-    )
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm 
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , "of claiming candidate is not a Democrat."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , "of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-h-2-ppc-multinomial
-#| fig-cap: Posterior predictive check of Multinomial models for $H_2$
-#| fig-subcap:
-#|   - Red treatment
-#|   - Blue treatment
-
-list_ppc[["h_2"]][["red_multinomial"]]
-list_ppc[["h_2"]][["blue_multinomial"]]
-```
-
-##### Ordered Logit
-
-```{r}
-#| label: tbl-hypothesis-2-ordered
-#| tbl-cap: Full results for reported ordered logistic regression models for $H_2$
-# Redefine names
-list_fitted_split_1_alt <- list(
-  "Red treatment" = list_fitted[["h_2"]][["red_ordinal"]]
-  , "Blue treatment" = list_fitted[["h_2"]][["blue_ordinal"]]
-)
-
-# Change goodness of fit stuff
-gm <- list(
-  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
-  , list("raw" = "r.squared", "clean" = "R<sup>2</sup>", "fmt" = 2)
-  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
-)
-# Make table
-modelsummary(
-  list_fitted_split_1_alt
-  , coef_map = c(
-    "b_trial_1_red_stimuli" = "Red yard sign"
-    , "b_trial_1_blue_stimuli" = "Blue yard sign"
-    , "b_Intercept[1]" = "Intercept 1"
-    , "b_Intercept[2]" = "Intercept 2"
-    )
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm 
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , "of claiming candidate is Republican."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , "of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-h-2-ppc-ordered
-#| fig-cap: Posterior predictive checks of Ordered Logit models in $H_2$
-#| fig-subcap:
-#|   - Red treatment
-#|   - Blue treatment
-
-list_ppc[["h_2"]][["red_ordinal"]]
-list_ppc[["h_2"]][["blue_ordinal"]]
-```
-
-##### Single model
-
-```{r}
-#| label: tbl-robustness-alt-specification-h-2
-#| tbl-cap: $H_2$ models with alternative specification
-# Redefine names
-list_fitted_split_3 <- list(
-  "Single model" = list_fitted[["h_2"]][["single_model"]]
-)
-
-# Make table
-modelsummary(
-  list_fitted_split_3
-  , coef_map = c(
-    "b_trial_1_red_stimuli_alt" = "Red yard sign"
-    , "b_trial_1_blue_stimuli_alt" = "Blue yard sign"
-    , "b_Intercept[1]" = "Intercept 1"
-    , "b_Intercept[2]" = "Intercept 2"
-  )
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , " of claiming candidate is Republican."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , " of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-h-2-ppc-single
-#| fig-cap: Posterior predictive checks of single model specification for $H_2$
-
-list_ppc[["h_2"]][["single_model"]]
-
-```
-
----
-
-##### Moderated by age
-
-```{r}
-#| label: tbl-interacted-models-h-2
-#| tbl-cap: $H_2$ models moderated by age
-# Redefine names
-list_fitted_split_2 <- list(
-  "Red treatment - Age moderating" = list_fitted[["h_2"]][["red_interact"]]
-  , "Blue treatment - Age moderating" = list_fitted[["h_2"]][["blue_interact"]]
-)
-
-# Make table
-modelsummary(
-  list_fitted_split_2
-  , coef_map = c(
-    "b_trial_1_red_stimuli" = "Red yard sign"
-    , "b_trial_1_blue_stimuli" = "Blue yard sign"
-    , "b_age" = "Age"
-    , "b_trial_1_red_stimuli:age" = "Red yard sign × Age"
-    , "b_trial_1_blue_stimuli:age" = "Blue yard sign × Age"
-    , "b_Intercept[1]" = "Intercept 1"
-    , "b_Intercept[2]" = "Intercept 2"
-    )
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm 
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , " of claiming candidate is Republican."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , " of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-h-2-ppc-age
-#| fig-cap: Posterior predictive checks of models in $H_2$ moderated by age
-#| fig-subcap:
-#|   - Red treatment moderated by age
-#|   - Blue treatment moderated by age
-
-list_ppc[["h_2"]][["red_interact"]]
-list_ppc[["h_2"]][["blue_interact"]]
-```
-
----
-
-##### Moderated by colorblindness
-
-```{r}
-#| label: tbl-colorblindness
-#| tbl-cap: $H_2$ moderated by colorblindness
-
-# Redefine names
-list_fitted_split_4 <- list(
-  "Red - Color blindness moderating" = list_fitted[["h_2"]][["red_colorblind"]]
-  , "Blue - Color blindness moderating" = list_fitted[["h_2"]][["blue_colorblind"]]
-)
-# Make table
-modelsummary(
-  list_fitted_split_4
-  , coef_map = c(
-    "b_trial_1_red_stimuli" = "Red yard sign"
-    , "b_trial_1_blue_stimuli" = "Blue yard sign"
-    , "b_trial_1_red_stimuli:color_blind_dummy" = "Red yard sign × Color blind"
-    , "b_trial_1_blue_stimuli:color_blind_dummy" = "Blue yard sign × Color blind"
-    , "b_Intercept[1]" = "Intercept 1"
-    , "b_Intercept[2]" = "Intercept 2"
-  )
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm 
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , " of claiming candidate is Republican."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , " of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-h-2-ppc-colorblind
-#| fig-cap: Posterior predictive checks of models in $H_2$ moderated by colorblindness
-#| fig-subcap:
-#|   - Red treatment moderated by colorblindness
-#|   - Blue treatment moderated by colorblindness
-
-list_ppc[["h_2"]][["red_colorblind"]]
-list_ppc[["h_2"]][["blue_colorblind"]]
-```
-
----
-
-#### $H_{2a}$
-
----
-
-##### Multinomial
-
-```{r}
-#| label: tbl-hypothesis-2a
-#| tbl-cap: Full results for models testing bounds of $H_2$
-# Redefine names
-model_names <- list(
-  "Trial 2 - Red treatment" = list_fitted[["h_2a"]][["trial_2_red_multinomial"]]
-  , "Trial 2 - Blue treatment" = list_fitted[["h_2a"]][["trial_2_blue_multinomial"]]
-  , "Trial 2 - Single model" = list_fitted[["h_2a"]][["trial_2_single_model"]]
-)
-
-# Change goodness of fit stuff
-gm <- list(
-  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
-  , list("raw" = "r.squared", "clean" = "R<sup>2</sup>", "fmt" = 2)
-  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
-)
-# Make table
-modelsummary(
-  model_names
-  , coef_map = c(
-    "b_mu2_trial_2_red_stimuli" = "Red yard sign (Independent)"
-    , "b_mu3_trial_2_red_stimuli" = "Red yard sign (Republican)"
-    , "b_mu2_trial_2_blue_stimuli" = "Blue yard sign (Independent)"
-    , "b_mu3_trial_2_blue_stimuli" = "Blue yard sign (Republican)"
-    , "b_trial_2_red_stimuli_alt" = "Red yard sign"
-    , "b_trial_2_blue_stimuli_alt" = "Blue yard sign"
-    , "b_mu2_Intercept" = "Intercept - Independent"
-    , "b_mu3_Intercept" = "Intercept - Republican"
-    , "b_Intercept[1]" = "Intercept 1"
-    , "b_Intercept[2]" = "Intercept 2"
-    )
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , " of claiming candidate is not a Democrat (Columns 1 and 2) or is a Republican (Column 3)."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , " of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-h-2a-multinomial-trial-2-ppc
-#| fig-cap: Posterior Predictive Checks for Multinomial models testing $H_{2a}$, Trial 2
-#| fig-subcap:
-#|   - Red treatment
-#|   - Blue treatment
-#|   - Single model
-
-list_ppc[["h_2a"]][["trial_2_red_multinomial"]]
-list_ppc[["h_2a"]][["trial_2_blue_multinomial"]]
-list_ppc[["h_2a"]][["trial_2_single_model"]]
-```
-
----
-
-```{r}
-#| label: tbl-hypothesis-2a-cont
-#| tbl-cap: Full results for models testing bounds of $H_2$ (cont.)
-# Redefine names
-model_names <- list(
-  "Trial 3 - Red treatment" = list_fitted[["h_2a"]][["trial_3_red_multinomial"]]
-  , "Trial 3 - Blue treatment" = list_fitted[["h_2a"]][["trial_3_blue_multinomial"]]
-  , "Trial 3 - Single model" = list_fitted[["h_2a"]][["trial_3_single_model"]]
-)
-
-# Change goodness of fit stuff
-gm <- list(
-  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
-  , list("raw" = "r.squared", "clean" = "R<sup>2</sup>", "fmt" = 2)
-  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
-)
-# Make table
-modelsummary(
-  model_names
-  , coef_map = c(
-    "b_mu2_trial_3_red_stimuli" = "Red yard sign (Independent)"
-    , "b_mu3_trial_3_red_stimuli" = "Red yard sign (Republican)"
-    , "b_mu2_trial_3_blue_stimuli" = "Blue yard sign (Independent)"
-    , "b_mu3_trial_3_blue_stimuli" = "Blue yard sign (Republican)"
-    , "b_trial_3_red_stimuli_alt" = "Red yard sign"
-    , "b_trial_3_blue_stimuli_alt" = "Blue yard sign"
-    , "b_mu2_Intercept" = "Intercept - Independent"
-    , "b_mu3_Intercept" = "Intercept - Republican"
-    , "b_Intercept[1]" = "Intercept 1"
-    , "b_Intercept[2]" = "Intercept 2"
-    )
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm 
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , " of claiming candidate is Republican."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , " of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-h-2a-multinomial-trial-3-ppc
-#| fig-cap: Posterior Predictive Checks for Multinomial models testing $H_{2a}$, Trial 3
-#| fig-subcap:
-#|   - Red treatment
-#|   - Blue treatment
-#|   - Single model
-
-list_ppc[["h_2a"]][["trial_3_red_multinomial"]]
-list_ppc[["h_2a"]][["trial_3_blue_multinomial"]]
-list_ppc[["h_2a"]][["trial_3_single_model"]]
-```
-
----
-
-##### Ordinal model
-
-```{r}
-#| label: tbl-hypothesis-2a-ordered
-#| tbl-cap: Full results for ordered logistic regressions testing bounds of $H_2$
-# Redefine names
-model_names <- list(
-  "Trial 2 - Red treatment" = list_fitted[["h_2a"]][["trial_2_red_ordinal"]]
-  , "Trial 2 - Blue treatment" = list_fitted[["h_2a"]][["trial_2_blue_ordinal"]]
-)
-
-# Change goodness of fit stuff
-gm <- list(
-  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
-  , list("raw" = "r.squared", "clean" = "R<sup>2</sup>", "fmt" = 2)
-  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
-)
-# Make table
-modelsummary(
-  model_names
-  , coef_map = c(
-    "b_trial_2_red_stimuli" = "Red yard sign"
-    , "b_trial_2_blue_stimuli" = "Blue yard sign"
-    , "b_Intercept[1]" = "Intercept 1"
-    , "b_Intercept[2]" = "Intercept 2"
-    )
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , " of claiming candidate is Republican."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , " of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-h-2a-ordinal-trial-2-ppc
-#| fig-cap: Posterior Predictive Checks for Ordinal models testing $H_{2a}$, Trial 2
-#| fig-subcap:
-#|   - Red treatment
-#|   - Blue treatment
-
-list_ppc[["h_2a"]][["trial_2_red_ordinal"]]
-list_ppc[["h_2a"]][["trial_2_blue_ordinal"]]
-```
----
-
-```{r}
-#| label: tbl-hypothesis-2a-cont-ordered
-#| tbl-cap: Full results for models testing bounds of $H_2$ (cont.)
-# Redefine names
-model_names <- list(
-  "Trial 3 - Red treatment" = list_fitted[["h_2a"]][["trial_3_red_ordinal"]]
-  , "Trial 3 - Blue treatment" = list_fitted[["h_2a"]][["trial_3_blue_ordinal"]]
-)
-
-# Change goodness of fit stuff
-gm <- list(
-  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
-  , list("raw" = "r.squared", "clean" = "R<sup>2</sup>", "fmt" = 2)
-  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
-)
-# Make table
-modelsummary(
-  model_names
-  , coef_map = c(
-    "b_trial_3_red_stimuli" = "Red yard sign"
-    , "b_trial_3_blue_stimuli" = "Blue yard sign"
-    , "b_Intercept[1]" = "Intercept 1"
-    , "b_Intercept[2]" = "Intercept 2"
-    )
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm 
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , " of claiming candidate is Republican."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , " of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-```{r}
-#| label: fig-h-2a-ordinal-trial-3-ppc
-#| fig-cap: Posterior Predictive Checks for Ordinal models testing $H_{2a}$, Trial 3
-#| fig-subcap:
-#|   - Red treatment
-#|   - Blue treatment
-
-list_ppc[["h_2a"]][["trial_3_red_ordinal"]]
-list_ppc[["h_2a"]][["trial_3_blue_ordinal"]]
-```
-
----
-
-#### $H_3$
-
-##### Main results
-
-```{r}
-#| label: tbl-h-3-main
-#| tbl-cap: Support of candidate based on partisanship
-
-# Redefine names
-model_names <- list(
-  "Red stimuli" = list_fitted[["h_3"]][["red"]]
-  , "Blue stimuli" = list_fitted[["h_3"]][["blue"]]
-)
-
-# Make table
-modelsummary(
-  model_names
-  , coef_map = c(
-    "b_trial_1_red_stimuli" = "Red yard sign"
-    , "b_trial_1_blue_stimuli" = "Blue yard sign"
-    , "b_pid_7" = "Party ID"
-    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign × Party ID"
-    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign × Party ID"
-    , "b_attention" = "Attention"
-    , "b_age" = "Age"
-    , "b_gender_idMale" = "Gender - Male"
-    , "b_gender_idNonMbinary" = "Gender - Non-binary"
-    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
-    , "b_race_idBlacknonMhispanic" = "Black"
-    , "b_race_idHispanice" = "Hispanic"
-    , "b_race_idMultipleraces" = "Multiple races"
-    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
-    , "b_race_idWhitenonMhispanic" = "White"
-  )  
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm 
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , " of claiming candidate is Republican."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , " of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-h-3-ppc
-#| fig-cap: Posterior Predictive checks for $H_3$ models
-#| fig-subcap:
-#|   - Red treatment
-#|   - Blue treatment
-list_ppc[["h_3"]][["red"]]
-list_ppc[["h_3"]][["blue"]]
-```
-
----
-
-#### $H_4$
-
----
-
-##### ✅ for over-dispersion
-
-```{r}
-#| label: tbl-h-4-dispersion
-#| tbl-cap: Checking for over-dispersion of data
-df_over_dispersed <- list_df[["cleaned"]][, c("trial_1_time_elapsed")]
-names(df_over_dispersed)[names(df_over_dispersed) == 'trial_1_time_elapsed'] <- 'Time Elapsed'
-datasummary_skim(
-  df_over_dispersed
-  , notes = "Data source: Prolific sample."
-  , histogram = FALSE
-)
-```
-
-##### Main results
-
-```{r}
-#| label: tbl-h-4
-#| tbl-cap: The effect of partisan congruency on time spent looking at a yard sign
-# Redefine names
-model_names <- list(
-  "Red stimuli" = list_fitted[["h_4"]][["red"]]
-  , "Blue stimuli" = list_fitted[["h_4"]][["blue"]]
-)
-
-# Make table
-modelsummary(
-  model_names
-  , coef_map = c(
-    "b_trial_1_red_stimuli" = "Red yard sign"
-    , "b_trial_1_blue_stimuli" = "Blue yard sign"
-    , "b_pid_7" = "Party ID"
-    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign × Party ID"
-    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign × Party ID"
-    , "b_attention" = "Attention"
-    , "b_age" = "Age"
-    , "b_gender_idMale" = "Gender - Male"
-    , "b_gender_idNonMbinary" = "Gender - Non-binary"
-    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
-    , "b_race_idBlacknonMhispanic" = "Black"
-    , "b_race_idHispanice" = "Hispanic"
-    , "b_race_idMultipleraces" = "Multiple races"
-    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
-    , "b_race_idWhitenonMhispanic" = "White"
-  )  
-  , statistic = "conf.int"
-  , conf_level = 0.9
-  , gof_map = gm 
-  , notes = c(
-    "Data source: Pavlovia"
-    , "Positive coefficients reflect the logged-odds"
-    , " of claiming candidate is Republican."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , " of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-h-4-ppc
-#| fig-cap: Posterior predictive checks of $H_4$ models
-#| fig-subcap:
-#|   - Red
-#|   - Blue
-list_ppc[["h_4"]][["red"]]
-list_ppc[["h_4"]][["blue"]]
-```
-
-#### $H_5$
-
-##### Main results
-
-```{r}
-#| label: tbl-hypothesis-5
-#| tbl-cap: The effect of democratic vote share on color choices for yard sign
-
-names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
-modelsummary(
-  list_fitted[["h_5"]]
-  , stat = "conf.int"
-  , conf_level = 0.9
-  , metrics = c("n.obs", "RMSE")
-  , coef_map = c(
-    "b_dem_vote_share" = "Democratic vote share (percent)"
-    , "b_Intercept" = "Intercept"
-  )
-  , notes = c(
-    "Data source: Center for Political Design and MIT Election Lab"
-    , "Positive coefficients reflect the logged-odds"
-    , "of claiming candidate is Republican."
-    , "Numbers inside brackets reflect the 5th and 95th percentile"
-    , "of the draws from the posterior distribution."
-  )
-  , escape = FALSE
-
-)
-```
-
----
-
-```{r}
-#| label: fig-hypothesis-5-ppc
-#| layout-ncol: 2
-#| fig-cap: Posterior Predictive checks for $H_5$
-#| fig-subcap:
-#|   - Proportion of yard signs red
-#|   - Proportion of yard signs blue
-
-list_ppc[["h_5"]][["red"]]$continuous
-list_ppc[["h_5"]][["blue"]]$continuous
-```
-
-## Copyright Information
-
-<span class="faux-block">{{< fa brands creative-commons >}} 2021-2023 Damon Charles Roberts</span>
-<span class="faux-block"><br>All content licensed under {{< fa brands creative-commons >}} {{< fa brands creative-commons-by >}} {{< fa brands creative-commons-sa >}} [Creative Commons CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/)</span>
+[cc-by]: http://creativecommons.org/licenses/by/4.0/
+[cc-by-image]: https://i.creativecommons.org/l/by/4.0/88x31.png
+[cc-by-shield]: https://img.shields.io/badge/License-CC%20BY%204.0-lightgrey.svg

### 2023-10-24 chapter_2/src/slides/slides.qmd
making some more edits to job talk slides

@@
 
+![[@zaller_simple_1992]](../../assets/slides/imgs/zaller_feldman.png){.absolute right=100 top=0}
+![[@zaller_nature_1992]](../../assets/slides/imgs/zaller.jpg){.absolute right=100 bottom=0}
+![[@lodge_rationalizing_2013]](../../assets/slides/imgs/lodge_taber.jpg){.absolute left=100 top=0}
+![[@taber_illusion_2016]](../../assets/slides/imgs/taber_lodge_2016.png){.absolute left=100 bottom=0}
+
+---
+
+But what about visual information?
+
+<!--
 ## The study of visuals in politics
@@
 
+-->
 ## A snap-judgment model of **visual** political information processing
@@
 We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
-The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
-
 ---
@@
 
+## How this fits in with the rest of the book?
+
+---
+
+- <span style="color: #616A6B"> How do colors convey political information and effect individual attitudes? </span>
+- How do colors influence political deliberation?
+- How do colors influence neighborhood evaluations?
+
+## How my book fits in with the rest of my work?
+
+---
+
+:::: {.columns}
+
+::: {.column width="50%"}
+How identity is communicated; its effects
+
+- Party Identification (this book)
+- Gender and politics
+- Racial and ethnic politics
+:::
+
+::: {.column width="50%"}
+Methodological
+
+- Text as data
+- Images as data
+- Data munging
+- Multiple imputation
+:::
+
+::::
+
 ## Questions and Comments
@@
 ## Appendix
+
+### Full snap-judgment model
+
+---
+
+{{< include ../../../assets/_theory.qmd >}}
+
+---
 
@@
 : Study 1 Measures {#tbl-study-1-measures}
+
+---
+
+#### List of model specifications for Study 2
+
+---
+
+- [Moderated by age](#moderated-by-age)
+- [Moderated by colorblindness](#moderated-by-colorblindness)
+- [Dependent on the amount of the color red and blue](#h_2a)
+- [Include treatment indicator variables in the same model](#single-model)
+
+---
 

### 2023-10-25 chapter_2/src/study_2/03_capd_downloading_images.py
updating some stuff

@@ -16,7 +16,9 @@ import urllib.request # to access site
 import sys # to deal with paths
 
     #* User-defined
-from chapter_2.src.PY.helper import names
+from sys import path
+path.append("./chapter_2/src/")
+from PY.helper import names
 
 # Loading database
 

### 2023-10-25 chapter_2/src/study_2/05_mit_election_lab_merge.py

@@ -14,7 +14,9 @@
 import polars as pl # for DataFrame management
 import numpy as np # for array management
     #* User-defined
-from chapter_2.src.PY.helper import names
+from sys import path
+path.append("./chapter_2/src/")
+from PY.helper import names
 
 # Check out the election lab data
 election_lab = pl.read_csv(

### 2023-10-25 chapter_2/src/models/model_fitting.R
updating file names

@@ -1,0 +1,336 @@
+# Title: Preliminary analyses of pavlovia data
+
+# Notes
+    #* Description
+        #** This is a R file that performs some preliminary analyses of
+        #** the pavlovia data for study 1
+    #* Updated
+        #** 2023-06-16
+        #** dcr
+
+# Setup
+  #* set seed
+set.seed(12102022)
+  #* set working directory
+setwd("./chapter_2/src")
+  #* execute cleaning script
+source("./eda/study_1/cleaning.R")
+  #* load in cleaned study-2 data
+  #* (need to run each python script individually)
+df_study_2 <- read.csv("../data/clean/study_2.csv") |>
+  as.data.table()
+  #* convert state_district and year variables  to factors
+df_study_2 <- df_study_2[
+  , year := tstrsplit(year, "-", keep = 1)
+][
+  , year := as.numeric(year)
+][
+  , state_district := factor(state_district)
+][
+  , blue_prop := blue_percent / 100
+][
+  , red_prop := red_percent / 100
+]
+  #* load helpful functions
+box::use(
+  data.table[...]
+  , brms[...]
+  , ordbetareg[...]
+)
+    #* make an empty model list object
+list_fitted <- list(
+  h_1 = list()
+  , h_2 = list()
+  , h_2a = list()
+  , h_3 = list()
+  , h_4 = list()
+  , h_5 = list()
+)
+list_ppc <- list(
+  h_1 = list()
+  , h_2 = list()
+  , h_2a = list()
+  , h_3 = list()
+  , h_4 = list()
+  , h_5 = list()
+)
+
+# Hypothesis 1
+
+# Hypothesis 2
+    #* Fit models
+list_fitted[["h_2"]][["red_multinomial"]] <- brm(
+  formula = trial_1_party ~ trial_1_red_stimuli
+  , data = list_df[["cleaned"]]
+  , family = categorical(link = "logit")
+  , prior = set_prior("normal(0, 1)", class = "b")
+  , backend = "cmdstanr"
+)
+list_fitted[["h_2"]][["blue_multinomial"]] <- brm(
+  formula = trial_1_party ~ trial_1_blue_stimuli
+  , data = list_df[["cleaned"]]
[…]

### 2023-10-27 chapter_2/src/roberts_empirical_chapter_1.qmd
grant application stuff

@@
 abstract: |
-  Do the colors red and blue convey political information?
+  We are used to seeing red and blue everywhere in campaign seasons, but do these colors actually convey political information?
 While decisions of political branding are assumed to be significant for electoral outcomes, we have few theories about the cognitive processes underlying the processing of such information and whether these decisions influence realized political behavior.
-Building upon interdisciplinary perspectives, this chapter introduces the snap-judgment model of visual political information processing.
-The theory argues that color allows individuals to form pre-cognitive attitudes of a political object and that these pre-cognitive attitudes shape latter and more cognitively laborious information processing and behavior.
-Meaning, that we can activate partisan attachments automatically through information as simple as color.
-In the first study, I talk to a political marketing firm and use a pixel-by-pixel classification of images from over 1000 yard signs for elections in the U.S.
+Building upon interdisciplinary perspectives, in this chapter I first introduce the snap-judgment model of visual political information processing.
+The theory argues that color allows individuals to form pre-cognitive attitudes of a political object, and that these pre-cognitive attitudes shape latter and more cognitively laborious information processing and behavior -- that is, that individuals can activate partisan attachments automatically through information as simple as color.
+I then present two studies in dialogue with this theory, both of which are inspired by conversations with political marketing professionals.
+Study one focuses on what we might expect neighborhoods and communities to look like, consistent with my theory; I use a pixel-by-pixel classification of images from over 1000 yard signs for elections in the U.S.
 House of Representatives.
-Evidence suggests that in districts where Democrats have an electoral advantage, there is more blue on the yard signs in the district.
-To examine the cognitive processes, I use a novel experimental design by tracking cursor movements and limiting participant's ability to view a yard sign to only 5000ms.
-I find that participants do make these associations when features of the yard sign are held constant and find that Republicans prefer candidates with red yard signs and that Democrats prefer candidates with blue yard signs.
+My findings suggest that in districts where Democrats have an electoral advantage, that there is more blue on the yard signs in the district.
+Study two takes aim at cognitive processes via a controlled experimental setting.
+I use a novel design, tracking cursor movements and limiting participants' abilities to view a treatment image to only 5000ms.
+I find that participants make color associations when features of a yard sign are held constant, and that Republicans prefer candidates with red yard signs, and Democrats prefer candidates with blue yard signs.
 additional-info: |
@@
 
-Do colors provide political information that shape attitudes among the mass public?
+Do colors actually shape political attitudes among the mass public?
 There are two goals that I am hoping to achieve in this chapter.
-The first is to convince the reader that the colors red and blue convey affiliative information.
-The second is that these connections between colors and political groups can shape political outcomes.
+The first is to convince the reader that the colors red and blue convey consistent, affiliative information.
+The second is that these connections between colors and political groups can indeed affect political outcomes.
 
-Many understand that colors are influential to shaping attitudes and behaviors in a number of ways.
+Many understand -- in a general sense -- that "colors matter" when it comes to attitudes and behaviors.
 Color theorists and scholars of marketing understand color as having important implications for reactions to a product and resulting consumer behavior.
@@
 Colors mean a varying number of things, however.
-As a gross, yet intelligible example, yellow sweaters relative to yellow bodily fluids can elicit strong and very different responses.
 
 The role of visuals in politics is receiving more attention among interdisciplinary scholars in fields like communication, political science, and the psychological sciences.
-While many of these studies examine fascinating but complicated forms of visual information such as symbology [@williams_whats_2022] and visual framing [@grabe_image_2009], we have yet to integrate these interdisciplinary perspectives with existing models of political information processing to understand how these visual forms of information act as cues [see @lilleker_power_2019] but also what the consequences are for political behavior among the mass public.
+While many of these studies examine fascinating but complicated forms of visual information such as symbology [@williams_whats_2022] and visual framing [@grabe_image_2009], we have yet to integrate these interdisciplinary perspectives with existing models of political information processing -- this will enable us to better understand how these visual forms of information act as cues [see @lilleker_power_2019], and what their potential consequences might be for political behavior among the mass public.
 
-Building upon descriptive evidence suggesting that Democratic campaigns use the color blue more than Republican campaigns [@williams_whats_2022] and that Republican voters express a preference for red during election season [@schloss_politics_2014], I present a snap-judgment model of politically-relevant visual information processing that outlines the cognitive processes that drive these associations and how those associations drive important political outcomes.
-I use theories of associative memory and spreading activation [see @collins_spreading-activation_1975] to conceptualize the association of the colors red and blue with Republicans and Democrats as two interconnected nodes.
-Informed by conceptualizations of these connections as carrying affective information informed by perspectives on biological survival reaching back to Darwin [@ralph_neuroscience_2018], I argue that when these nodes are activated by exposure to these colors in political contexts, other related nodes become active and contain affective information.
+In this chapter, I build upon descriptive evidence suggesting that Democratic campaigns use the color blue more than Republican campaigns [@williams_whats_2022] and that Republican voters express a preference for red during election season [@schloss_politics_2014].
+I present a snap-judgment model of politically-relevant visual information processing that outlines a) the cognitive processes that drive these associations and b) notes how those associations drive important political outcomes.
+I draw upon theories of associative memory and spreading activation [see @collins_spreading-activation_1975] to conceptualize the association of the colors red and blue with Republicans and Democrats, thinking of them as as two interconnected nodes.
+I conceptualize these connections as carrying affective information -- an idea informed by perspectives on biological survival reaching back to Darwin [@ralph_neuroscience_2018].
+When these nodes are activated by exposure to these colors in political contexts, other related nodes become active and contain affective information.
 As partisanship evokes strong affective reactions for many members of the public [@iyengar_affect_2012], this activation elicits an affective reaction.
-Considering that most visual information and that these processes of association occur pre-cognitively [@ames_impression_2012;@fazio_attitudes_2007;@sander_cambridge_2013], I argue that the elicited affective response to such information can be "transferred" [see @morris_activation_2003;@taber_illusion_2016] to later post-cognitive processing of more traditional forms of political information such as stated policy positions.
-The implication being that these associations can inform reactions to political information and thus political behavior pre-cognitively.
-<!--
-This chapter applies the snap-judgment model to a simple case: the use of color on yard signs used by campaigns in elections.
-I focus on yard signs as they are a common form of campaign marketing and evidence suggests that they can shape individual behavior [@makse_politics_2019] and electoral outcomes [@green_effects_2016].
-Additionally, I start by examining the colors red and blue.
-While there are other colors that may provide political information -- black and white for Black Lives Matter and Blue Lives Matter movements, the overarching goal of this book is to lay the foundation for a larger research agenda in visual political psychology [@bucy_editors_2021].
-Without such foundations, we would be jumping into the study of complex cases and circumstances without a firm grasp of how things matter on a more fundamental level.
-
-Before getting into things, it is worth noting that while there indeed is empirical and experiential evidence suggesting that Republicans use the color red and Democrats use the color blue [@schloss_politics_2014;@williams_whats_2022], there is currently no theoretical framework that explains how these connections happen at the individual level.
-As a side note, one might find it unsatisfying that I do not address *how* these associations between color and the parties came about.
-While the connections between Republicans with the color red and Democrats with the color blue seemed to quicken after the 2000 Presidential election (with news networks consistently using those colors in campaign coverage [@elving_color_2014]), it is not clear if this was a deliberate choice, or whether this was yet another symptom of an increasingly polarized public.
-An undertaking to address the specifics of this part of American political history would likely be a different book project.
--->
+Considering that most visual information -- including these processes of association -- occur pre-cognitively [@ames_impression_2012;@fazio_attitudes_2007;@sander_cambridge_2013], I argue that the elicited affective response to such information can be "transferred" [see @morris_activation_2003;@taber_illusion_2016] to later post-cognitive processing of more traditional forms of political information such as stated policy positions.
+The implication of this is that these associations can *pre-cognitively* inform reactions to political information and political behavior
 
 To preview, in this chapter I propose two studies to evaluate the claims I make about yard signs.
-Yard signs are a simple yet effective source of campaign branding for political candidates as they convey information that is often useful for voters' partisanship [@campbell_american_1969].
+Yard signs are a simple yet effective source of campaign branding for political candidates, as they convey information that is often useful for voters' partisanship [@campbell_american_1969].
 As yard signs are a simple and static form of campaign advertising, they cannot rely heavily on more complicated forms of information.
@@
 With these characteristics, yard signs are an ideal candidate both from a design and substantive standpoint.
-From a design standpoint, as they are static forms of party branding they have fewer moving parts, which helps isolate the effect that color has on shaping attitudes.
+From a design standpoint, as a static form of party branding they have fewer moving parts, which helps isolate the effect that color has on shaping attitudes.
 From a substantive standpoint, while we understand that yard signs matter to campaigns, we have yet to systematically explore more simple design choices such as color.
 
-In [Study 1](#study-1), I find descriptive evidence suggesting that campaigns use the colors red and blue on their yard signs at different rates depending on the success of Republicans and Democrats according to previous election returns.
-It is unclear, however, whether these patterns are based on elite perceptions of how to communicate partisanship to voters or whether campaigns have successfully identified a cognitive process linking the colors red and blue with Republicans and Democrats.
-Accordingly, in [Study 2](#study-2), I conduct an online experiment that examines whether the public notice color and whether their attitudes are shaped by the presence of "Republican red" and "Democratic blue" on the yard signs of a political candidate.
-I find that these associations do exist among the public.
-Specifically, individuals consistently and strongly associate Republicans with the color red and the Democrats with the color Blue.
-As a result, partisan individuals' willingness to vote for a candidate can be dramatically different depending on whether the color used in the yard sign aligns with their partisan identification.
+In [Study 1](#study-1), I find descriptive evidence suggesting that campaigns use the colors red and blue on their yard signs -- in districts -- at different rates depending on the success of Republicans and Democrats in previous elections.
+This paints a picture of the outside world that is consistent with my theory.
+However, this study does not make clear whether these patterns are based on elite perceptions of how to communicate partisanship to voters, or whether campaigns have successfully identified a cognitive process linking the colors red and blue with Republicans and Democrats.
+Accordingly, in [Study 2](#study-2), I conduct an online experiment that examines whether individuals notice color, and whether their attitudes are shaped by the presence of "Republican red" and "Democratic blue" on the yard signs of a political candidate.
+I find that these associations do exist among respondents.
+Specifically, individuals consistently and strongly associate Republicans with the color red and the Democrats with the color blue.
+I present experimental evidence that partisan individuals' willingness to vote for a candidate may be different depending on whether the color used in a yard sign aligns with their partisan identification.
 
-While these two studies highlight endogenous processes between campaigns and voters, to be clear, I am not arguing that either of these patterns only one way.
-In fact, I believe that there is a necessary feedback loop between the parties and their bases of support.
+While these two studies highlight endogenous processes between campaigns and voters, to be clear, I wish to be clear that I am not arguing that either of these patterns works in one direction.
+Rather, in all likelihood there is a necessary feedback loop between the parties and their bases of support.
 Voters support candidates who signal strong allegiance to the party to increase their chances for electoral success [@utych_voter-centric_2020], and the parties are motivated to distinguish themselves [@lee_insecure_2016;@clifford_how_2020] as a result of their high levels of ideological and affective polarization [@dietrich_using_2021;@enders_issues_2021].
-I leave teasing out directionality for subsequent analyses.
 
-These findings bring much needed evidence in support of the conventional wisdom that the colors red and blue convey political information.
+Still, together, the findings bring much needed evidence in support of the conventional wisdom that the colors red and blue convey political information.
 The implication of the theory and these findings are that partisan attachments are automatically activated through things as seemingly simple and ubiquitous as color.
 These activated partisan attachments then have causal effects for attitude expression and political behavior.
-Given the existing literature demonstrating low-levels of political engagement among the mass public [see @hibbing_stealth_2002] as well as the current hyper-polarized era [see @iyengar_affect_2012], this chapter's argument and findings suggests that voters need not consume any substantive political information before expressing a willingness to cast a vote for a candidate.
+Given the existing literature demonstrating low-levels of political engagement among the mass public [see @hibbing_stealth_2002], as well as the hyper-polarized nature of contemporary politics [see @iyengar_affect_2012], this chapter's argument and findings reinforce the idea that voters need not consume any substantive political information before expressing a willingness to cast a vote for a candidate.
 
@@
 For several methodological and disciplinary reasons, the visual aspects of television were of little focus in the literature [@bucy_editors_2021].
-However, today news organizations and politicians are responding to the ubiquitous use of image-dominant social media platforms like TikTok and Instagram, by joining and posting on such platforms.
+However, today news organizations and politicians are responding to the ubiquitous use of image-dominant social media platforms like TikTok and Instagram by joining and posting on such platforms.
 Scholars need to make this transition as well, integrating the role of simple visual information into theories of political information (abbreviated as *pip*) and attitude formation.
@@
 What remains unclear is whether these patterns in the United States are meaningful.
-While political psychologists are increasingly interdisciplinary and rely on insights from fields like neuroscience, it remains relatively unclear whether and how color can convey complex information about politics.
-Further, it remains unclear whether such a simple type of information has enough efficacy to shape political outcomes such as vote intention.
-This chapter is a first cut at addressing these open questions.
+While political psychologists are increasingly interdisciplinary and rely on insights from fields like neuroscience, we have little systematic evidence about whether and how color can convey complex information about politics.
+Further, it remains to be seen whether such a simple type of information has enough potency to shape political outcomes such as vote intention.
+This chapter is a first cut at addressing these open and important questions.
 

### 2023-10-30 chapter_2/src/slides/color-book.qmd
updating slides

--- 2023-10-24 chapter_2/src/slides/slides.qmd
@@
 
----
-
-```{r}
-#| label: tbl-yard-sign-summary
-#| tbl-cap: Summary statistics
-names(df_study_2)[names(df_study_2) == 'red_percent'] <- '% Red'
-names(df_study_2)[names(df_study_2) == 'blue_percent'] <- '% Blue'
-names(df_study_2)[names(df_study_2) == 'white_percent'] <- '% White'
-
-df_study_2_subset <- df_study_2[, c('% Red', '% Blue', '% White')]
-datasummary_skim(
-  df_study_2_subset
-  , notes = "Data source: CAPD Yard Signs."
-  , histogram = FALSE
-)
-
-```
-
 ### Measurement: What is the partisan composition of the district?
@@
 
-- <span style="color: #616A6B"> How do colors convey political information and effect individual attitudes? </span>
+- <span style="color: #616A6B">How do colors convey political information and effect individual attitudes? </span>
 - How do colors influence political deliberation?
@@
 
-### Study 1
-
----
-
-#### Characteristics of sample
+### Study 2
+
+---
+
+#### Characteristics of experimental sample
 
@@
 
-#### List of model specifications for Study 2
+### List of model specifications for Study 2
 
@@
 
-#### $H_1$
+### $H_1$
 
@@
 
-#### $H_2$
-
----
-
-##### Multinomial Logit
+### $H_2$
+
+---
+
+#### Multinomial Logit
 
@@
 
-##### Ordered Logit
+#### Ordered Logit
 
@@
 
-##### Single model
+#### Single model
 
@@
 
-##### Moderated by age
+#### Moderated by age
 
@@
 
-##### Moderated by colorblindness
+#### Moderated by colorblindness
 
@@
 
-#### $H_{2a}$
-
----
-
-##### Multinomial
+### $H_{2a}$
+
+---
+
+#### Multinomial
 
@@
 
-##### Ordinal model
+#### Ordinal model
 
@@
 
-#### $H_3$
-
-##### Main results
+### $H_3$
+
+---
+
+#### Main results
 
@@
 
-#### $H_4$
-
----
-
-##### ✅ for over-dispersion
+### $H_4$
+
+---
+
+#### ✅ for over-dispersion
 
@@
 
-##### Main results
+#### Main results
 
@@
 
-#### $H_5$
-
-##### Main results
+### $H_5$
+
+---
+
+#### Color proportion descriptive statistics
+
+---
+
+```{r}
+#| label: tbl-yard-sign-summary
+#| tbl-cap: Summary statistics
+names(df_study_2)[names(df_study_2) == 'red_percent'] <- '% Red'
+names(df_study_2)[names(df_study_2) == 'blue_percent'] <- '% Blue'
+names(df_study_2)[names(df_study_2) == 'white_percent'] <- '% White'
+
+df_study_2_subset <- df_study_2[, c('% Red', '% Blue', '% White')]
+datasummary_skim(
+  df_study_2_subset
+  , notes = "Data source: CAPD Yard Signs."
+  , histogram = FALSE
+)
+
+```
+
+#### Main results
 

### 2023-10-31 chapter_2/src/slides/color-book.qmd
working on the slides some more

@@
 
-![Aaron Bashir (R), PA-3](../../assets/slides/imgs/bashir.webp){#fig-bashir .absolute left=0 top=100}
-![Dwight Evans (D), PA-2](../../assets/slides/imgs/evans.webp){#fig-evans .absolute right=0 bottom=100}
-
----
+- Motivation of the project
+- A snap-judgment model of politically-relevant information processing
+- An experiment
+- Is the world consistent with the snap-judgement model?
+- The broader book project
+- Q&A
+
+### Yard signs are simple, yet effective forms of information
+
+![Highway Yard Sign](../assets/img/highway_yardsign.jpg)
+
+### Pre-test: Perceptions of candidate's party affiliation depends on the color of the yard sign
 
@@
 
----
+### Colors can convey identity
 
@@
 
-![[1860s Ballots](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)](../../assets/slides/imgs/ballots.avif){#fig-1860-ballot}
+![[1860's Republican Ballots](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)](../../assets/slides/imgs/ballots.avif){#fig-1860-ballot}
 
@@
 
-# What do we know so far?
-
----
+# What do we know so far about how we process political information?
+
+### Evaluation of political information happens automatically, and in a motivated manner
 
@@
 
-<!--
-## The study of visuals in politics
-
----
-
-![[@bucy_editors_2021]](../../assets/slides/imgs/bucy_joo.png)
-
----
-
-![](../../assets/slides/imgs/dan_arendt.png){.absolute bottom=0 left=0}
-![](../../assets/slides/imgs/lindholm_et-al.png){.absolute top=200 left=0}
-![](../../assets/slides/imgs/nina_et-al.png){.absolute top=0 left=0}
-
----
-
-![[@schloss_politics_2014]](../../assets/slides/imgs/schloss_palmer.png){.absolute top=0 height=400}
-![[@williams_whats_2022]](../../assets/slides/imgs/williams_et-al.png){.absolute bottom=200 right=0 height=400}
-![[@casiraghi_colors_2022]](../../assets/slides/imgs/casiraghi_et-al.png){.absolute bottom=0 right=0 height=400}
-
--->
 ## A snap-judgment model of **visual** political information processing
@@
 
-## Study 1
-
-### Motivation of Study
-
----
-
-> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
-We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
----
-
-> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
-
----
-
-- Do these associations have systematic influences on campaign strategy? (Study 1)
-- Are these hunches correct that these colors can reliably cue partisanship? (Study 2)
-
-### Measurement: How much red and blue do campaigns use?
-
----
-
-- Collect around 1,000 yard signs from House elections
-  - 2016-2022
-- Measuring the colors used on a yard sign:
-  - Use a machine learning Python Library, `OpenCV` [@bradski_opencv_2000], that reads images and classifies their components.
-    - Trained to classify each pixel in the image
-    - Classifies it based on BGR value (reverse of RGB)
-    - Looks for a range of values around the "Republican red" and "Democratic blue"
-
----
-
-```{python}
-#| label: example detection
-#| echo: false
-
-from sys import path # for path management
-from cv2 import imread, imwrite # for color detection
-    #* user-defined
-sys.path.append("../")
-from PY.helper import colorDetector
-
-# Define colors to detect
-    #* White
-        #** Not defined. Default for colorDetector()
-    #* Red
-republican_red = [232, 27, 35] # target color
-red_lower = [93, 9, 12] # lower end of spectrum for red
-red_higher = [255, 170, 170] # higher end of spectrum for red
-
-# Load gop image to read
-img = imread("../assets/img/gop_2022.png")
-
-# Detect colors
-percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
-
-transformed= imwrite("../../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
-
-masked= imwrite("../../data/temp/study_2/gop_2022_detected.png", result) # save masked image
-```
-
-::: {#fig-color-detection-example layout-ncol="2"}
-![Resized original image](../../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
-
-![Masked](../../data/temp/study_2/gop_2022_detected.png){#fig-masked}
-
-Detecting colors in the GOP logo
-:::
-
-```{python}
-#| output: asis
-# Print calculated percentage of example
-print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
-```
-
-### Measurement: What is the partisan composition of the district?
-
----
-
-- MIT Election Lab data
-  - House election results
-  - 1970-2020
-- Measuring partisan composition of district:
-  - Calculate rolling 5-year average of the Democratic party's vote share for each district
-
-### Do campaigns use a different proportion of the colors red and blue in different constituency compositions?
-
----
-
-```{r}
-#| label: fig-study-2-pred-1
-#| fig-cap: More blue on the yard signs in Democratic strongholds
-
-blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["blue"]]
-  , treatment = "Blue"
-  , hypothesis = "H5"
-)
-
-blue
-```
-
----
-
-```{r}
-#| label: fig-study-2-pred-2
-#| fig-cap: Less red on the yard signs in Democratic strongholds
-
-red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["red"]]
-  , treatment = "Red"
-  , hypothesis = "H5"
-)
-red
-```
-
-## Study 2
+---
+
+- <span style="color: #616A6B">Motivation of the project</span>
+- <span style="color: #616A6B">A snap-judgment model of politically-relevant information processing</span>
+- An experiment
+- Is the world consistent with the snap-judgement model?
+- The broader book project
+- Q&A
+
+## Experiment
 
@@
 blue
+```
+
+## Study 2
+
+### Do practitioners think of color when designing yard signs?
+
+> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
+We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
+---
+
+> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
+
+### Campaigns use the colors more or less red and blue depending on partisan composition of electoral district
+
+#### DV: the amount of red and blue in political yard signs
+
+- Collect around 1,000 yard signs from House elections
+  - 2016-2022
+- Measuring the colors used on a yard sign:
+  - Use a machine learning Python Library, `OpenCV` [@bradski_opencv_2000], that reads images and classifies their components.
+    - Trained to classify each pixel in the image
+    - Classifies it based on BGR value (reverse of RGB)
+    - Looks for a range of values around the "Republican red" and "Democratic blue"
+
+---
+
+```{python}
+#| label: example detection
+#| echo: false
+
+from sys import path # for path management
+from cv2 import imread, imwrite # for color detection
+    #* user-defined
+sys.path.append("../")
+from PY.helper import colorDetector
+
+# Define colors to detect
+    #* White
+        #** Not defined. Default for colorDetector()
+    #* Red
+republican_red = [232, 27, 35] # target color
+red_lower = [93, 9, 12] # lower end of spectrum for red
+red_higher = [255, 170, 170] # higher end of spectrum for red
+
+# Load gop image to read
+img = imread("../assets/img/gop_2022.png")
+
+# Detect colors
+percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
+
+transformed= imwrite("../../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
+
+masked= imwrite("../../data/temp/study_2/gop_2022_detected.png", result) # save masked image
+```
+
+::: {#fig-color-detection-example layout-ncol="2"}
+![Resized original image](../../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
+
+![Masked](../../data/temp/study_2/gop_2022_detected.png){#fig-masked}
+
+Detecting colors in the GOP logo
+:::
+
+```{python}
+#| output: asis
+# Print calculated percentage of example
+print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
+```
+
+#### IV: partisan composition of the district
+
+---
+
+- MIT Election Lab data
+  - House election results
+  - 1970-2020
+- Measuring partisan composition of district:
+  - Calculate rolling 5-year average of the Democratic party's vote share for each district
+
+### More blue on the yard signs in Democratic strongholds
+
+```{r}
+#| label: fig-study-2-pred-1
+#| fig-cap: More blue on the yard signs in Democratic strongholds
+
+blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["blue"]]
+  , treatment = "Blue"
+  , hypothesis = "H5"
+)
+
+blue
+```
+
+### More red on the yard signs in Republican strongholds
+
+```{r}
+#| label: fig-study-2-pred-2
+#| fig-cap: Less red on the yard signs in Democratic strongholds
+
+red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["red"]]
+  , treatment = "Red"
+  , hypothesis = "H5"
+)
+red
 ```

### 2023-11-01 chapter_2/src/slides/color-book.qmd
updating the slides a bit more

@@
 ---
-title: "The Shape and Color of Politics"
+title: "The Shape and <span style='color: #b70000'>Co</span><span style='color: #00AEF3'>lor</span> of Politics"
 author:
@@
         transition: none
+        slide-number: c
 bibliography: ../../../assets/candidate_support_chapter_references.bib
@@
 nocite: |
-    @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017
+    @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017, @zaller_simple_1992, @zaller_nature_1992, @lodge_rationalizing_2013, @taber_illusion_2016
 ---
@@
 ]
-```
+
+# Set default for plot color scheme
+
+plot_color_scheme <- FALSE
+```
+
+## Available to you to follow along and view more
 
@@
 
-- Motivation of the project
+- <span style="color: #b70000"> Motivation of the project</span>
 - A snap-judgment model of politically-relevant information processing
@@
 
-### Yard signs are simple, yet effective forms of information
+## Yard signs are simple, yet effective forms of information
 
@@
 
-### Pre-test: Perceptions of candidate's party affiliation depends on the color of the yard sign
+### Pre-test: Perceptions of candidate's party affiliation depends on the <span style='color: #b70000'>co</span><span style='color: #00AEF3'>lor</span> of the yard sign
 
@@
 
-### Colors can convey identity
+### <span style='color: #b70000'>Col</span><span style='color: #00AEF3'>ors</span> can convey identity
 
@@
 
-## How are colors used in politics?
+## How are <span style='color: #b70000'>col</span><span style='color: #00AEF3'>ors</span> used in politics?
 
@@
 
-# What do we know so far about how we process political information?
-
-### Evaluation of political information happens automatically, and in a motivated manner
-
-![[@zaller_simple_1992]](../../assets/slides/imgs/zaller_feldman.png){.absolute right=100 top=0}
-![[@zaller_nature_1992]](../../assets/slides/imgs/zaller.jpg){.absolute right=100 bottom=0}
-![[@lodge_rationalizing_2013]](../../assets/slides/imgs/lodge_taber.jpg){.absolute left=100 top=0}
-![[@taber_illusion_2016]](../../assets/slides/imgs/taber_lodge_2016.png){.absolute left=100 bottom=0}
+## What do we know so far about how we process political information?
+
+### Political information is <span style='color: #b70000'>identity-based</span> and <span style='color: #00AEF3'>evokes affect</span>
+
+::::: {.columns}
+
+:::: {.column width="60%"}
+::: {#fig-pip layout-ncol=2}
+![](../../assets/slides/imgs/zaller.jpg){width=1.46in}
+![](../../assets/slides/imgs/lodge_taber.jpg){width=1.46in}
+
+Dominant models of political information processing
+:::
+::::
+
+::::{.column width="40%"}
+
+A key takeaway is that we are being pushed to react to information to before we even realize it.
+::::
+
+:::::
 
@@
 
-## A snap-judgment model of **visual** political information processing
-
----
-
-```{mermaid}
-%%| label: fig-snap-judgment-model
-%%| fig-cap: Overview of model
-
-flowchart TD;
-A[Detection of color] --> B[Activation of associated memories]
-B --> C[Negative Valence]
-B --> D[Positive Valence]
-C -.-> E[Policy stance]
-D -.-> F[Policy stance]
-E -.-> G[Negative Valence]
-E -.-> H[Positive Valence]
-F -.-> I[Negative Valence]
-F -.-> J[Positive Valence]
-```
-
----
-
-- Implications
-  - Refines existing info. processing models to consider pre-conscious influences.
-  - Outlines the cognitive processes undergirding how we:
-    - have made associations between the colors red and blue with the two parties.
-    - form attitudes and behaviors based on less substantive information (e.g., policy stances).
+## [<span style='color: #b70000'>A snap-judgment model of</span> <span style='color: #00aef3'>visual political information processing</span>](#full-snap-judgment-model)
+
+### Visual information is primitive
+
+- We can process it faster, and automatically
+- It is ubiquitous
+- It can carry a significant amount of information
+    - E.g., the color <span style='color: #FFCD00'>yellow</span> has associations with bananas, with our favorite sweater, with the Iowa Hawkeys, etc.
+    - We have positive and negative affect with all of these.
+
+### So, how can it be for politics?
+
+- These associations have been strengthened over time as the consistent usage associating Republicans and Democrats.
+- Our feelings toward the object that is associated with those colors can be activated because of those colors and the association.
+- Because of the centrality of vision for many living organisms, our brain is designed around this. It happens first.
+    - <span style='color: #b70000'>We process and re</span><span style='color: #00aef3'>act to color first.</span>
+- Given this, we are already in a state of mind. We have made a snap-judgment that can be updated with new information, but nonetheless are influenced by it.
+
+### Implications
+
+:::: {.columns}
+
+::: {.column width="50%"}
+
+**Substantive Innovations**
+
+- Presents a cognitive model that builds upon existing info. processing models to consider pre-conscious influences.
+    - All of these steps happen <span style='color: #b70000'>bef</span><span style='color: #00aef3'>ore</span> the pre-existing info. processing models
+:::
+
+::: {.column width="50%"}
+
+**Methodological Innovations**
+
+- Using mousetracking with a survey experiment to examine pre-conscious motivations.
+- Use image-based classification
+:::
+
+::::
 
@@
 - <span style="color: #616A6B">A snap-judgment model of politically-relevant information processing</span>
-- An experiment
+- <span style="color: #b70000">A survey experiment</span>
 - Is the world consistent with the snap-judgement model?
@@
 
-- Do we associate the color red with Republicans and the color blue with Democrats?
+- Do we associate the color <span style='color: #b70000'>red</span> with Republicans and the color <span style='color: #00aef3'>blue</span> with Democrats?
 - Do these associations provide information that the public act on in politics?
+- How do we interact with visual information?
 
@@
 
----
-
-#### Background information
+#### [Background information](#tbl-study-1-measures)
 
@@
 
----
-
 #### Treatment
@@
 
-- Recruited 1,000 participants from Prolific
+- Recruited [1,000 participants](#tbl-study-1-descriptives) from an online survey experiment platform; Prolific.
 - Counterbalance treatment and background information ($\frac{1}{2}$ see treatment first; other $\frac{1}{2}$ see background questions first)
@@
 - MouseView.js [@anwyl-irvine_mouseviewjs_2022]
+    - Use this instead of eye-tracking.
+    - Do not need to use a convenience sample of students.
 
@@
 
-### Do people make these associations?
-
----
+### A pre-registered expectation
+
+- People associate the colors <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> with Republicans and Democrats, respectively.
+  - Replicating the pre-test
+
+#### [Red yard signs = Republican candidate](#h_2)
 
@@
   , x_axis = "trial_1_red_stimuli"
+  , gray = plot_color_scheme
 )
@@
 
----
+#### [<span style='color: #00aef3'>Blue yard signs = Democratic candidate</span>](#h_2)
 
@@
   , treatment = "Blue"
+  , gray = plot_color_scheme
 )
@@
 
-### What does conflicting colors do to these associations?
-
----
-
-```{r}
-#| label: fig-h-2a-predictions
-#| layout-nrow: 2
-#| fig-cap: Mixing red and blue in a yard sign increases uncertainty about partisanship
-#| fig-subcap:
-#|   - Trial 2 Red treatment
-#|   - Trial 2 Blue treatment
-#|   - Trial 3 Red treatment
-#|   - Trial 3 Blue treatment
-plot_trial_2_red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_2_red_multinomial"]]
-  , x_axis = "trial_2_red_stimuli"
-)
-plot_trial_2_blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_2_blue_multinomial"]]
-  , x_axis = "trial_2_blue_stimuli"
-  , treatment = "Blue"
-)
-plot_trial_3_red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_3_red_multinomial"]]
-  , x_axis = "trial_3_red_stimuli"
-)
-plot_trial_3_blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_2a"]][["trial_3_blue_multinomial"]]
-  , x_axis = "trial_3_blue_stimuli"
-  , treatment = "Blue"
-)
-plot_trial_2_red
-plot_trial_2_blue
-plot_trial_3_red
-plot_trial_3_blue
-```
-
-### Do these associations inform important political behavior?
-
----
+### A pre-registered expectation
+
+Subjects will use color as a basis for making a decision on whom they should vote for.
+
+- Republican subjects will express preference for a candidate with a pre-dominantly <span style='color: #b70000'>red</span> yard sign.
+- Democratic subjects will express preference for a candidate with a pre-dominantly <span style='color: #00aef3'>blue</span> yard sign.
+
+#### [Republicans are more likely to vote for a candidate with a red yard sign, Democrats are less likely](#h_3)
 
@@
   , legend_title = "Treatment"
+  , gray = plot_color_scheme
 )
@@
 
----
+#### [<span style='color: #00aef3'>Democrats are more likely to vote for a candidate with a blue yard sign, Republicans less likely</span>](#h_3)
 
@@
 
-## Study 2
-
-### Do practitioners think of color when designing yard signs?
+### A pre-registered expectation
+
+When you include conflicting information (<span style='color: #00aef3'>blue</span> on a <span style='color: #b70000'>red</span> yard sign; <span style='color: #b70000'>red</span> on a <span style='color: #00aef3'>blue</span> yard sign), subjects will be less certain about the partisanship of the candidate
+
+#### [Mixing red and blue in a yard sign <span style='color: #00aef3'>increases uncertainty about partisanship</span>](#h_2a)
+
+```{r}
+#| label: fig-h-2a-predictions-trial-2
+#| layout-ncol: 2
+#| fig-cap: Mixing red and blue in a yard sign increases uncertainty about partisanship
+#| fig-subcap:
+#|   - Trial 2 Red treatment
+#|   - Trial 2 Blue treatment
+plot_trial_2_red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_2a"]][["trial_2_red_multinomial"]]
+  , x_axis = "trial_2_red_stimuli"
+  , gray = plot_color_scheme
+)
+plot_trial_2_blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_2a"]][["trial_2_blue_multinomial"]]
+  , x_axis = "trial_2_blue_stimuli"
+  , treatment = "Blue"
+  , gray = plot_color_scheme
+)
+plot_trial_3_red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_2a"]][["trial_3_red_multinomial"]]
+  , x_axis = "trial_3_red_stimuli"
+  , gray = plot_color_scheme
+)
+plot_trial_3_blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_2a"]][["trial_3_blue_multinomial"]]
+  , x_axis = "trial_3_blue_stimuli"
+  , treatment = "Blue"
+  , gray = plot_color_scheme
+)
+plot_trial_2_red
+plot_trial_2_blue
+```
+
+---
+
+```{r}
+#| label: fig-h-2a-predictions-trial-3
+#| layout-ncol: 2
+#| fig-cap: Mixing red and blue in a yard sign increases uncertainty about partisanship (cont.)
+#| fig-subcap:
+#|   - Trial 3 Red treatment
+#|   - Trial 3 Blue treatment
+
+plot_trial_3_red
+plot_trial_3_blue
+```
+
+### A pre-registered expectation
+
+Subjects will spend more time and will move their cursor more when looking at <span style='color: #00aef3'>blue</span> and <span style='color: #b70000'>red</span> yard signs
+
+#### When viewing a white yard sign, subjects explored the image more.
+
+```{r}
+#| label: tbl-h1-trial-1
+#| tbl-cap: Average time between cursor movements (Trial 1)
+df_movement_trial_1 <- list_df[["cleaned"]][
+  , c(
+    "trial_1_difference_Time"
+    , "trial_1_stimulus"
+    , "trial_1_difference_X"
+    , "trial_1_difference_Y"
+  )
+]
+setnames(
+  df_movement_trial_1
+  , old = c(
+    "trial_1_difference_Time"
+    , "trial_1_difference_X"
+    , "trial_1_difference_Y"
+  )
+  , new = c(
+    "&#x394<sub>t</sub> (milliseconds)"
+    , "&#x394<sub>x</sub> (pixels)"
+    , "&#x394<sub>y</sub> (pixels)"
+  )
+)
+
+datasummary_balance(
+  ~trial_1_stimulus
+  , data = df_movement_trial_1
+  , notes = "Data source: Prolific sample."
+  , escape = FALSE
+)
+```
+
+#### A pre-registered expectation
+
+Subjects will take longer than they did in trial 1 to explore the yard signs when there are conflicting colors on the yard sign
+
+#### The average subject in trial 2 explored the image more than the average participant in trial 1 for <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> yard signs
+
+```{r}
+#| label: tbl-h1-trial-2
+#| tbl-cap: Average time between cursor movements (Trial 2)
+df_movement_trial_2 <- list_df[["cleaned"]][
+  , c(
+    "trial_2_difference_Time"
+    , "trial_2_stimulus"
+    , "trial_2_difference_X"
+    , "trial_2_difference_Y"
+  )
+]
+setnames(
+  df_movement_trial_2
+  , old = c(
+    "trial_2_difference_Time"
+    , "trial_2_difference_X"
+    , "trial_2_difference_Y"
+  )
+  , new = c(
+    "&#x394<sub>t</sub> (milliseconds)"
+    , "&#x394<sub>x</sub> (pixels)"
+    , "&#x394<sub>y</sub> (pixels)"
+  )
+)
+modelsummary::datasummary_balance(
+  ~trial_2_stimulus
+  , data = df_movement_trial_2
+  , notes = "Data source: Prolific sample."
+  , escape = FALSE
+)
+```
+
+#### The average subject in trial 3 spent more time exploring the <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> yard signs than the average participant in trial 1
+
+```{r}
+#| label: tbl-h1-trial-3
+#| tbl-cap: Average time between cursor movements (Trial 3)
+df_movement_trial_3 <- list_df[["cleaned"]][
+  , c(
+    "trial_3_difference_Time"
+    , "trial_3_stimulus"
+    , "trial_3_difference_X"
+    , "trial_3_difference_Y"
+  )
+]
+setnames(
+  df_movement_trial_3
+  , old = c(
+    "trial_3_difference_Time"
+    , "trial_3_difference_X"
+    , "trial_3_difference_Y"
+  )
+  , new = c(
+    "&#x394<sub>t</sub> (milliseconds)"
+    , "&#x394<sub>x</sub> (pixels)"
+    , "&#x394<sub>y</sub> (pixels)"
+  )
+)
+
+modelsummary::datasummary_balance(
+  ~trial_3_stimulus
+  , data = df_movement_trial_3
+  , notes = "Data source: Prolific sample."
+  , escape = FALSE
+)
+```
+
+---
+
+- <span style="color: #616A6B">Motivation of the project</span>
+- <span style="color: #616A6B">A snap-judgment model of politically-relevant information processing</span>
+- <span style="color: #616A6B">A survey experiment</span>
+- <span style="color: #b70000">Is the world consistent with the snap-judgement model?</span>
+- The broader book project
+- Q&A
+
+## Study 2 - Is the world consistent with my theory?
+
+### A pre-registered expectation
+
+Campaigns use the colors more or less <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> depending on partisan composition of electoral district
+
+####  Talking to practitioners
 
@@
 We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
+
 ---
@@
 
-### Campaigns use the colors more or less red and blue depending on partisan composition of electoral district
-
-#### DV: the amount of red and blue in political yard signs
+---
+
+It remains unclear whether this is just ***one*** group of practitioners, however.
+
+#### [<span style='color: #b70000'>D</span><span style='color: #00aef3'>V</span>: the amount of red <span style='color: #00aef3'>and blue in political yard signs</span>](#tbl-yard-sign-summary)
 
@@
 
----
-
 - MIT Election Lab data
@@
 
-### More blue on the yard signs in Democratic strongholds
+### [<span style='color: #00aef3'>More blue on the yard signs in Democratic strongholds</span>](#h_5)
 
@@
   , hypothesis = "H5"
+  , gray = plot_color_scheme
 )
@@
 
-### More red on the yard signs in Republican strongholds
+### [More red on the yard signs in Republican strongholds](#h_5)
 
@@
 
+---
+
+- <span style="color: #616A6B">Motivation of the project</span>
+- <span style="color: #616A6B">A snap-judgment model of politically-relevant information processing</span>
+- <span style="color: #616A6B">A survey experiment</span>
+- <span style="color: #616A6b">Is the world consistent with the snap-judgement model?</span>
+- <span style="color: #b70000">The broader book project</span>
+- Q&A
+
 ## How this fits in with the rest of the book?
-
----
 
@@
 
----
-
-:::: {.columns}
-
-::: {.column width="50%"}
-How identity is communicated; its effects
-
-- Party Identification (this book)
-- Gender and politics
-- Racial and ethnic politics
-:::
-
-::: {.column width="50%"}
-Methodological
-
-- Text as data
-- Images as data
-- Data munging
-- Multiple imputation
-:::
-
-::::
+![](../../assets/slides/imgs/roberts_gs.png)
 
@@
 
----
-
 {{< include ../../../assets/_theory.qmd >}}
 
----
-
-### Study 2
-
----
+### Experiment
 
 #### Characteristics of experimental sample
-
----
 
@@
 
----
-
 #### Measures
-
----
 
@@
 
----
-
-### List of model specifications for Study 2
-
----
+### List of model specifications for Experiment
 
@@
 - [Include treatment indicator variables in the same model](#single-model)
-
----
-
-### $H_1$
-
-```{r}
-#| label: tbl-h1-trial-1
-#| tbl-cap: Average time between cursor movements (Trial 1)
-df_movement_trial_1 <- list_df[["cleaned"]][
-  , c(
-    "trial_1_difference_Time"
-    , "trial_1_stimulus"
-    , "trial_1_difference_X"
-    , "trial_1_difference_Y"
-  )
-]
-setnames(
-  df_movement_trial_1
-  , old = c(
-    "trial_1_difference_Time"
-    , "trial_1_difference_X"
-    , "trial_1_difference_Y"
-  )
-  , new = c(
-    "Δ<sub>t</sub> (milliseconds)"
-    , "Δ<sub>x</sub> (pixels)"
-    , "Δ<sub>y</sub> (pixels)"
-  )
-)
-
-datasummary_balance(
-  ~trial_1_stimulus
-  , data = df_movement_trial_1
-  , notes = "Data source: Prolific sample."
-  , escape = FALSE
-)
-```
-
----
+- [Multinomial (main) versus Ordered logistic regressions](#h_2)
 
 ### $H_2$
-
----
 
@@
 
----
+##### Posterior Predictive Check
 
@@
 
----
-
 ### $H_{2a}$
-
----
 
@@
 
----
+#### Multinomial Cont.
 
@@
 ```
----
+
+#### Ordered Cont.
 
@@
 
----
+##### Posterior Predictive Check
+
 ```{r}
@@
 
----
-
 ### $H_3$
-
----
 
@@
 
----
-
 ### $H_4$
-
----
 
@@
 
----
-
 #### Color proportion descriptive statistics
-
----
 

### 2023-11-01 chapter_2/src/models/model_fitting.R

@@ -30,6 +30,8 @@ df_study_2 <- df_study_2[
   , blue_prop := blue_percent / 100
 ][
   , red_prop := red_percent / 100
+][
+  , party := factor(party)
 ]
   #* load helpful functions
 box::use(
@@ -301,6 +303,7 @@ list_ppc[["h_4"]][["blue"]] <- pp_check(
 )
 # Hypothesis 5
   #* Fit models
+    #** AME's
 list_fitted[["h_5"]][["red"]] <- ordbetareg(
   formula = red_prop ~ dem_vote_share + (1 | state_district)
   , data = df_study_2
@@ -321,12 +324,42 @@ list_fitted[["h_5"]][["blue"]] <- ordbetareg(
   )
   , coef_prior_SD = 2
 )
+    #** CME's
+list_fitted[["h_5"]][["red_party"]] <- ordbetareg(
+    formula = red_prop ~ dem_vote_share + party + dem_vote_share * party + (1 | state_district)
+    , data = df_study_2
+    , threads = 4
+    , backend = "cmdstanr"
+    , control = list(
+      adapt_delta = 0.95
+    )
+    , coef_prior_SD = 2
+)
+
+list_fitted[["h_5"]][["blue_party"]] <- ordbetareg(
+    formula = red_prop ~ dem_vote_share + party + dem_vote_share * party + (1 | state_district)
+    , data = df_study_2
+    , threads = 4
+    , backend = "cmdstanr"
+    , control = list(
+      adapt_delta = 0.95
+    )
+    , coef_prior_SD = 2
+)
   #* Posterior predictive checks
+    #** AME's
 list_ppc[["h_5"]][["red"]] <- pp_check_ordbeta(
   list_fitted[["h_5"]][["red"]]
 )
 list_ppc[["h_5"]][["blue"]] <- pp_check_ordbeta(
   list_fitted[["h_5"]][["blue"]]
+)
+    #** CME's
+list_ppc[["h_5"]][["red_party"]] <- pp_check_ordbeta(
+  list_fitted[["h_5"]][["red_party"]]
+)
+list_ppc[["h_5"]][["blue_party"]] <- pp_check_ordbeta(
+  list_fitted[["h_5"]][["blue_party"]]
 )
 # Store model results
 save(

### 2023-11-05 chapter_2/src/slides/color-book.qmd
update slides

@@
 
-A key takeaway is that we are being pushed to react to information to before we even realize it.
+A key takeaway is that we are being pushed to react to information before we even realize it.
 ::::
@@
 - Presents a cognitive model that builds upon existing info. processing models to consider pre-conscious influences.
-    - All of these steps happen <span style='color: #b70000'>bef</span><span style='color: #00aef3'>ore</span> the pre-existing info. processing models
+    - All of these steps happen <span style='color: #b70000'>be</span><span style='color: #00aef3'>fore</span> the pre-existing info. processing models
 :::
@@
 
-Campaigns use the colors more or less <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> depending on partisan composition of electoral district
+Campaigns use the colors <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> more or less depending on partisan composition of electoral district
 
@@
 
-- <span style="color: #616A6B">How do colors convey political information and effect individual attitudes? </span>
+- <span style="color: #616A6B">How do colors convey political information and affect individual attitudes? </span>
 - How do colors influence political deliberation?
@@
 
+list_fitted[["h_5"]] <- list(
+    list_fitted[["h_5"]][["red"]]
+    , list_fitted[["h_5"]][["blue"]]
+)
 names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")

### 2023-12-04 chapter_2/src/slides/slides.qmd
updating some stuff

--- 2023-10-18 chapter_2/src/slides/slides.qmd
@@
     incremental: false
-    slide-number: false
-    progress: false
-    menu: false
+    slide-number: true
     toc: false
@@
     fig-responsive: false
-    margin: 0.1
+    margin: 0
 execute:
@@
 load("../../data/temp/models/study_1_fitted.RData")
-# Load data for study 2
-df_study_2 <- read.csv("../../data/clean/study_2.csv") |>
-  as.data.table()
-  #* convert state_district and year variables  to factors
-df_study_2 <- df_study_2[
-  , year := tstrsplit(year, "-", keep = 1)
-][
-  , year := as.numeric(year)
-][
-  , state_district := factor(state_district)
-][
-  , blue_prop := blue_percent / 100
-][
-  , red_prop := red_percent / 100
-]
 ```
@@
 print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
-```
-
----
-
-```{r}
-#| label: tbl-yard-sign-summary
-#| tbl-cap: Summary statistics
-names(df_study_2)[names(df_study_2) == 'red_percent'] <- '% Red'
-names(df_study_2)[names(df_study_2) == 'blue_percent'] <- '% Blue'
-names(df_study_2)[names(df_study_2) == 'white_percent'] <- '% White'
-
-df_study_2_subset <- df_study_2[, c('% Red', '% Blue', '% White')]
-datasummary_skim(
-  df_study_2_subset
-  , notes = "Data source: CAPD Yard Signs."
-  , histogram = FALSE
-)
-
 ```

### 2023-12-04 chapter_2/src/appendix.qmd
init gh-pages branch

@@
 )
+df_study_2 <- read.csv("../data/clean/study_2.csv") |>
+  as.data.table()
+  #* convert state_district and year variables  to factors
+df_study_2 <- df_study_2[
+  , year := tstrsplit(year, "-", keep = 1)
+][
+  , year := as.numeric(year)
+][
+  , state_district := factor(state_district)
+][
+  , blue_prop := blue_percent / 100
+][
+  , red_prop := red_percent / 100
+]
 ```
@@
 
-### Hypothesis 2
+### $H_2$
 
@@
 
+#### Summary Statistics of yard sign color measure
+
+```{r}
+#| label: tbl-yard-sign-summary
+#| tbl-cap: Summary statistics of proportion of colors present on yard signs
+names(df_study_2)[names(df_study_2) == 'red_percent'] <- '% Red'
+names(df_study_2)[names(df_study_2) == 'blue_percent'] <- '% Blue'
+names(df_study_2)[names(df_study_2) == 'white_percent'] <- '% White'
+
+df_study_2_subset <- df_study_2[, c('% Red', '% Blue', '% White')]
+datasummary_skim(
+  df_study_2_subset
+  , notes = "Data source: CAPD Yard Signs."
+  , histogram = FALSE
+)
+
+```
+
 #### Models

### 2023-12-04 chapter_2/src/roberts_empirical_chapter_1.qmd

@@
 Existing models of political information processing (abbreviated here as *pip*) primarily focus on complex forms of political information, such as policy positions, communicated verbally or through text.
-As individuals process visual information pre-cognitively, we might expect that they may form a snap-judgment or the initial appraisal of an object with visual information as opposed to these more complex forms of information that often require more cognitive effort by varying orders of magnitude.
+As individuals process visual information pre-cognitively, we might expect that they may form a snap-judgment about it -- this is in contrast to complex forms of information that often require (orders of magnitude) moree cognitive effort.
 
-Color and other simple visual information are processed much quicker and occur more frequently than text-based information that may be communicated, for example, through a news article [@mehta_blue_2009].
-But as color and other visual information are processed differently, we should also consider their use as political information.
-As visual information is affectively encoded [@cimbalo_emotionally_1978], it can affect the affective state and the latter processing of more complex information, such as text.
-The visual information provides a snap-judgment or an impression of the object through faster processing, and activates particular neurological processes that influence subsequent information appraisals [@ames_impression_2012].
-This implies that snap-judgments from visual political information may have downstream effects that shape the way in which we engage with traditionally considered forms of political information.
+Colors and other simple pieces of visual information are processed much more quickly; these actually occur more frequently than text-based information that may be communicated, for example, via a news article [@mehta_blue_2009].
+And, it is because color and other visual information are processed differently that their roles in communicating political information need to be considered.
+As visual information is affectively encoded [@cimbalo_emotionally_1978], it can affect the affective state and the latter processing of more complex information that scholars typically consider (e.g., text).
+That is, the visual information provides a snap-judgment -- an impression of the object through faster processing -- and activates particular neurological processes that influence subsequent information appraisals [@ames_impression_2012].
+In other words, this means that snap-judgments from visual political information may have downstream effects that shape the way in which we engage with traditionally considered forms of political information.
 
-Before expanding upon the role of colors in shaping political attitudes, let me first define an attitude as a concept.
+Before expanding upon the role of colors in shaping political attitudes, let's first define attitudes.
 An attitude represents an accessible, valanced evaluation of associated prior information and experiences.
@@
 This implies that we should be able to measure attitudes, but that such an operationalization requires careful consideration of the context's role in any given measure of an attitude (as they result from memories) [@fazio_attitudes_2007].
-In this chapter, I consider color's effect on shaping attitudes about a political object -- a yard sign.
-As I hold this constant in the chapter, concerns about the variation in what people are thinking about when seeing the color red and blue are less important here, though later chapters grapple with this consideration.
+In this chapter, I consider color's effect when it comes to shaping attitudes about a political object -- a yard sign.
+As I hold certain features constant in my studies, concerns about potential variation in what people are thinking about when seeing the color red and blue are less important for present purposes (though later chapters grapple with this consideration).
 
 I use a popular conceptualization of attitudes as emerging from accessed associated memories [see @lodge_rationalizing_2013; see also @collins_spreading-activation_1975].
-The implication of such a conceptualization is that attitudes may be unstable (though not in a random sense).
+The implication of such a conceptualization is that attitudes may be unstable (though not in the sense that they are random).
 That is, as attitudes are associative, they manifest slightly differently depending on the associative paths activated [@fazio_attitudes_2007].
 The retrieval of relevant memories to the attitude depends on many factors, such as the recency of the event, the similarity of the context, and the importance or salience of the memory [@kahana_laws_2022].
-This means that the memories retrieved to contribute to an attitude that is quite variable.
+This means that the memories retrieved to contribute to an attitude may be quite variable.
 However, to understand where that variability comes from, we must understand the deeper processes influencing how information is encoded and later retrieved.
@@
 Colors may act as a contextual feature that may lead to variability in how a set of political information may shape attitudes.
-Let me explain how colors might do this.
+How might colors do this?
 
@@
 
-<!--
-A less technical description of the processes occurring here might look something like this: once politically-relevant visual information is detected, the retina passes it to the brain.
-Once there, the brain attempts to classify the visual information by activating networks of neurons associated with the current information.
-With these activated pathways, the brain also attempts to appraise such information based on quick classification.
-For attitude formation, this implies that, as memories are affectively encoded [@kensinger_affective_2022], these memories help areas such as the amygdala to appraise the current information.
--->
-
 These fast affective classifications are valanced rather than the more laborious categorization of specific emotions (e.g., anger, anxiety, fear, happiness).
@@
 That is, emotion -- the complex classification of appraisals -- is a cognitive component of affect.
-By contrast, the pre-cognitive process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_emotion_2011;@dror_deconstructing_2017].
+*By contrast, the pre-cognitive process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_emotion_2011;@dror_deconstructing_2017].*
 
@@
 Say you are driving down a highway.
-At 65 miles per hour, you are traveling at about 95 feet per second at this speed.
+At 65 miles per hour, you are traveling at about 95 feet per second.
 You split your attention.
@@
 You may come to this with the help of the fact that every year you have seen yard signs on this stretch of the highway.
-You know that when you see those red-blue maps pop up on news apps on your phone that the electoral forecasts always represent Republican support with red, and blue for democrats.
+You know that when you see those red-blue maps pop up on news apps on your phone that the electoral forecasts always represent Republican support with red, and blue for Democrats.
 Once you have figured out who this person is with the help of this other information, you react: "ugh, that guy is too loyal to Trump," or "yeah!
@@
 The snap-judgment model predicts that you first process the colors of the yard sign.
-You access associative memory to figure out what those particular wavelengths represent; red, white, blue?
+You access associative memory to figure out what those particular wavelengths represent: red, white, blue?
 As these colors are associated with different emotional states [see @cimbalo_emotionally_1978] and the resulting behavioral consequences, your brain starts sending signals to the rest of your body to prepare for reaction [see @sander_cambridge_2013;@dror_deconstructing_2017].
@@
 
-From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that colors observed shape perceptions about the person and ideological symbol represented in the branding -- this means that individuals express different levels of preference for receiving more information that is consistent with their preferences ($H_{2}$); that the consistency of information explains more positive perceptions (i.e., simple visual information paired with more complex "traditional" information) ($H_{3}$); positive and consistent information is processed more quickly than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) -- this is inline with their primary objective of reelection [@fenno_congressmen_1973;@mayhew_congress_1974].
+From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that colors observed shape perceptions about the person and ideological symbol represented in the branding -- this means that individuals express different levels of preference for receiving more information that is consistent with their preferences ($H_{2}$); that the consistency of information explains more positive perceptions (i.e., simple visual information paired with more complex "traditional" information) ($H_{3}$); positive and consistent information is processed more quickly than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) -- this is in line with their primary objective of reelection [@fenno_congressmen_1973;@mayhew_congress_1974].
 A summary of these hypotheses is presented in @tbl-hypotheses.
@@
 In [Study 1](#study-1) I start with testing $H_5$.
-Though my focus is on the cognitive mechanisms for individuals, I first wanted to examine whether practitioners of political marketing also perceive that these associations exist and are influential.
+Though my focus is on the cognitive mechanisms for individuals, I first want to examine whether practitioners of political marketing also perceive that these associations exist and are influential.
 In some informal conversations that I had with political campaign professionals, it became clear that the descriptive evidence connecting the colors red and blue with Republicans and Democrats is still very much based on instinct rather than empirical evidence.
@@
 
-It appears that campaigns recognize that these are not simply patterns that journalists [see @elving_color_2014] and researchers [see @williams_whats_2022] have picked up on, but that they are associations held by voters and campaigns respond accordingly:
+Comments from practitioners like this suggest that campaigns recognize that these are not simply patterns that journalists [see @elving_color_2014] and researchers [see @williams_whats_2022] have picked up on; they are associations held by voters, and campaigns respond accordingly:
 
@@
 
-In the comments above, we see some qualification that there are other colors which betray ideological positions.
+In the comments like these, we see some qualification that there are other colors which betray ideological positions.
 Still, a potential implication is that the value of colors associated with a particular place can be a way for candidates to communicate attachment to a district and its constituents.
-Still, there is a preference for campaigns to use as few colors as possible to save on costs -- simpler is better.
-What particularly stood out was:
+That said, there is a preference for campaigns to use as few colors as possible to save on costs -- simpler is better.
+A comment that particularly stood out was:
 
@@
 
-So, unsurprisingly, campaigns care about how they market themselves.
+So, unsurprisingly, a conversation with a practitioner reveals that campaigns care about how they market themselves.
 And it seems as though campaigns want to tap into quick and efficient information processing for voters and potential voters.
@@
 
-Though it appears that at least one consulting firm of campaign marketing professionals recognize the potential value of using the colors red and blue to cue to the partisanship of a candidate, there is still significant uncertainty about how widespread these patterns are with political campaigns in the United States and whether voters actually do make these associations.
+Comments like this suggest the following: although it appears that at least once consulting firm of campaign marketing professionals recognize the potential value of using the colors red and blue to cue to the partisanship of a candidate, there is still significant uncertainty about how widespread these patterns are with political campaigns in the United States, and whether voters actually do make these associations.
+Do districts in campaign seasons take on a look that is consistent with my theory?
 The first piece of empirical evidence in this chapter examines whether we observe systematic patterns between campaigns in the use of the colors red and blue on their yard signs.
-[Study 2](#study-2) then takes my predictions from the snap-judgment model to examine whether these associations exist among voters and what the consequences are.
+[Study 2](#study-2) then takes my predictions from the snap-judgment model to examine whether these associations exist among voters, and investigates possible consequences.
 
-To gather evidence generalizing the belief that campaigns strategically use the colors red and blue to tap into possible associations of these colors with partisanship, I began by collecting data from the MIT Election Lab that reports the electoral results of the House of Representative elections from the years 1970-2020.
+To gather evidence generalizing the belief that campaigns strategically use the colors red and blue to tap into possible associations of these colors with partisanship, I began by collecting data from the MIT Election Lab -- specifically, I gathered data on the electoral results of the House of Representative elections from the years 1970-2020.
 The data report the number of votes for each candidate in any given race.
@@
 
-Next, I use a combination of HTML and XML tags to identify then download around 1,000 yard signs from House elections from the years 2016 to 2022 from the website provided by the Center for American Politics and Design.
+Next, I use a combination of HTML and XML tags to identify and then download around 1,000 yard signs from House elections from the years 2016 to 2022; these were taken from the website of the Center for American Politics and Design.
 I used the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.
 
-This approach to measure of the proportion of the Republican red and Democrat blue colors takes a lot of the guess work out of manually coding this.
+This approach to measuring the proportion of the Republican red and Democratic blue colors takes a lot of the guess work out of manually coding this.
 For example, I downloaded the GOP logo used on the GOP's official Twitter account during the 2022 midterm election cycle.
@@
 I standardize the image to be 224 $\times$ 224 pixels.
-The computer is trained to detect the "Republican red" and "Democrat blue" colors.
+The computer is trained to detect the "Republican red" and "Democratic blue" colors.
 Once trained, the computer detects the pixels that do not contain values within the pre-specified range and converts those pixels to be black.
@@
 
-With the data on the proportion of each of the yard signs using the red and blue colors, I merged these data with the MIT Election Lab Data.
-This left me with data from the House elections between 2018 and 2020.
+With the data on the proportion of each of the yard signs using the red and blue colors, I then merge these data with the MIT Election Lab Data.
+This leaves me with data from the House elections between 2018 and 2020.
 While the data are limited in the number of elections they reflect, they allow me to hold the district composition constant, as redistricting occurs after the Census every 10 years.
@@
 To do this, I specify a model that includes an intercept for each state-district unit.
-Though my outcome of interest (proportion of the yard sign that is red or blue) are continuous (it can take any real number), the outcome is bounded between 0 and 1.
-While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit, introduce systematic error, and lead to results that are quite unstable.
-To account for these concerns, I use an ordered beta regression which specifies a link function constraining the conditional distribution of the outcome to be between 0 and 1; as well as inducing cut-points akin to the fractional logistic regression which allows for the outcome to also appear as strictly equal to 0 or 1 [@kubinec_ordered_2022].
-Interested readers can find a discussion of how the ordered beta regression compares to other estimators in the beta regression family in [Appendix](#sec-2-a).
+Though my outcome of interest (proportion of the yard sign that is red or blue) is continuous (it can take any real number), the outcome is bounded between 0 and 1.
+While the traditional approach may be to use ordinary least squares, such a technique often can result in poor model fit, introduce systematic error, and lead to results that are quite unstable.
+To account for these concerns, I use an ordered beta regression which specifies a link function constraining the conditional distribution of the outcome to be between 0 and 1; I also induce cut-points akin to the fractional logistic regression which allows for the outcome to also appear as strictly equal to 0 or 1 [@kubinec_ordered_2022].
+Interested readers can find a discussion of how the ordered beta regression compares to other estimators in the beta regression family in the [Appendix](#sec-2-a).
 
@@
 
-The results suggest a correlation between districts where Democrats are historically more electorally successful and a lower proportion of red on them.
+The results suggest a correlation between districts where Democrats are historically more electorally successful and a lower proportion of red on their yard signs.
 Inversely, those same districts tend to have yard signs with a higher proportion of blue on them.
 It is important to note that these results are strictly correlational.
-These results do not claim that campaigns are doing this either because voters are encouraging them to take this strategy, or that they are doing it as a way to proactively get voters to make these associations.
-Though I do control for unobserved confounds through removing district and year level pooling, there are a number of contextual features that may be unique to that particular district in a particular election year that I do not account for and can threaten claims of causal direction.
+From these results I do not claim that campaigns are doing this either because voters are encouraging them to take this strategy, or that they are doing it as a way to proactively get voters to make these associations.
+Though I do control for unobserved confounds through removing district and year level pooling, there are a number of contextual features that may be unique to a particular district in a particular election year that I do not account for and that threaten claims of causal direction.
 Though the data available to me limit my ability make a causal claim, these data nonetheless provide evidence consistent with the story I have relayed and the one provided to me in my informal conversations with practitioners.
 
-Determining how political operatives formulate branding strategies for candidates is not the main focus of this story.
-While it helps me understand how the colors red and blue factor into decisions made on the ground by professional political marketers, like the existing evidence in other research, it does not answer my questions about whether these impressions about voters making these associations exist, nor does it tell me much about the cognitive mechanisms explaining these association.
-Further, the observational evidence also does not support any causal claim about the electoral ramifications of such processes.
+It appears that Congressional districts take on a look that is consistent with my theory.
+However, determining how political operatives formulate branding strategies for candidates is not the main focus of my story.
+While it helps me understand ow the colors red and blue factor into decisions made on the ground by professional political marketers, this imagery coding does not answer my more central questions about 1) whether voters make these associations, 2) about what kinds of cognitive mechanisms potentially undergird such associations, and 3) whether there is evidence to support causal claims about the electoral ramifications of such processes.
 
@@
 Using yard signs in this study, I test the first four hypotheses I derived from the snap-judgment model.
-First, I tested the claim that individuals do indeed notice the color of electoral yard signs.
-Next, I tested the claim that these colors that individuals detect influence their evaluations of the yard sign and the candidate represented on it.
-I then tested the claim that the effects on perception are moderated by how consistent the color is with the more complex information displayed on the yard sign.
+First, I test the claim that individuals do indeed notice the color of electoral yard signs.
+Next, I test the claim that these colors that individuals detect influence their evaluations of the yard sign and the candidate represented on it.
+I then test the claim that the effects on perception are moderated by how consistent the color is with the more complex information displayed on the yard sign.
 Finally, [Study 2](#study-2) closes with an examination of whether positive information that contains consistency is processed more quickly than negative or inconsistent information.
@@
 Due to concerns about priming effects introduced by these questions as well as concerns of bias introduced by post-treatment control [@montgomery_how_2018], I randomly selected half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
-This questionnaire includes common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
+This questionnaire includes common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, and political knowledge.
 
@@
 I included those questions due to expectations that they may act as confounds for my hypotheses.
-I included some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these correlates with partisan identification [see @campbell_american_1969;@mason_uncivil_2018].
+I included some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these correlate with partisan identification [see @campbell_american_1969;@mason_uncivil_2018].
 Though political knowledge does predict the strength of an individual's partisan identification [@lodge_rationalizing_2013], attention paid to politics is likely a more important confounding variable for my application.
 The purpose of color in politics is to act as a heuristic for people (a cognitive shortcut).
-On the one hand, if individuals are aware of the tendency for Republicans to use and be associated with the color red and the degree to which they know factual information about politics is not entirely relevant.
+On the one hand, if individuals are aware of the tendency for Republicans to use and be associated with the color red, and the degree to which they know factual information about politics is not entirely relevant.
 On the other hand, those that pay no attention to politics whatsoever may be less likely to be aware of such associations.
@@
 In the first trial of the experiment, I randomly presented participants with one of three possible yard signs.
-These yard signs are simple, with the text "Riley Ready to Lead" and a solid background color of either "Republican red," "Democratic blue," or White.^[See [Appendix](#sec-2-a) to view all of the stimuli used in [Study 1](#study-1).] There is an added component to this, as well as in the other two trials.
+These yard signs are simple, with the text "Riley Ready to Lead" and a solid background color of either "Republican red," "Democratic blue," or white.^[See [Appendix](#sec-2-a) to view all of the stimuli used in [Study 1](#study-1).] There is an added component to this, as well as in the other two trials.
 
@@
 population.
-As a result, Mouseview.js enabled me to take advantage of a survey experiment while capturing information about how participants explored the yard signs.
+As a result, Mouseview.js enables me to take advantage of a survey experiment format (and a better sample) while capturing information about how participants explored the yard signs.
 
@@
 When viewing each yard sign in each of the three trials, there is a blur over a substantial portion of the screen.
-At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[I include a screenshot providing an example of what the participants were able to see with the blur included in the [Appendix](#sec-2-a).] For the obstruction, I utilized a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
+At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[A screenshot providing an example of what the participants were able to see with the blur included in the [Appendix](#sec-2-a).] For the obstruction, I utilized a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
 The gaussian blur allowed participants to see a blurred visual field beyond the cursor.
@@
 The use of the gaussian blur required that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_mouseviewjs_2022].
-This required participants to either switch browsers or to not participate in the study if they are using Safari at the time they are recruited by Prolific to participate in the study.
+This required participants to either switch browsers or to not participate in the study if they were using Safari at the time they are recruited by Prolific to participate in the study.
 As this requirement is enforced *before* joining the study, this should not have an effect on the number of excluded participants from my original sample.
@@
 
-There are two more trials that are much like the first trial.
-What is different between the two latter trials and the first is that I varied the amount of color that is on the yard sign.
+What is different between the two latter trials and the first is that I varied the amount of color that is on the yard sign in the second and third trials.
 Examples of all of these yard signs are included in the [Appendix](#sec-2-a).
-For readers interested in the more technical details, the [Appendix](#sec-2-a) accompanying this chapter also includes a table of the data collected in the experiment -- @tbl-study-1-measures; reports full results, posterior predictive checks, and more detailed discussions for all of the models used in the remainder of this section.^[Unless noted otherwise, the reflection of uncertainty in the models are credible intervals at the 90% level.
+For readers interested in the more technical details, the [Appendix](#sec-2-a) accompanying this chapter also includes a table of the data collected in the experiment -- @tbl-study-1-measures; this table reports full results, posterior predictive checks, and more detailed discussions for all of the models used in the remainder of this section.^[Unless noted otherwise, the reflection of uncertainty in the models are credible intervals at the 90% level.
 This should not be equated with the frequentist practice of reporting confidence intervals at the 95% level, as credible intervals at this level are often extremely unstable and, more importantly, are interpreted differently.
@@
 This contrasts with a confidence interval used in the frequentist framework which is interpreted as: upon repeated samples, 90% of the confidence intervals contain the true effect.
-To bridge methodological approaches, for those interpreting my credible intervals, I am using two-sided credible intervals here, at the 90% level, the probability that 0 would be the true value given the data would be less than 5% as it would be on one side of my posterior distribution.]
+To bridge methodological approaches, for those interpreting my credible intervals, I am using two-sided credible intervals here -- at the 90% level, the probability that 0 would be the true value given the data would be less than 5% as it would be on one side of my posterior distribution.]
 
@@
 These tables demonstrate a few things.
-First, the average participant in each treatment condition appear to be spending more time exploring the yard signs when there are more "conflicting" colors (trials 2 and 3).
-Second, we see that, for the most part, the average participant in the red and blue yard sign conditions spend more time exploring those yard signs than the participants viewing the white yard sign.
+First, the average participant in each treatment condition appears to be spending more time exploring the yard signs when there are more "conflicting" colors (trials 2 and 3).
+Second, we see that, for the most part, the average participant in the red and blue yard sign conditions spends more time exploring those yard signs than the participants viewing the white yard sign.
 
@@
 The data on the timing and cursor location is much more noisy than I originally anticipated.
-However, as the tests of the next few questions demonstrate, the evidence supports the general conclusion of the systematic differences between individuals that saw either a red, white, or blue yard sign (despite holding everything else but the color constant).
+However, as the tests of the next few questions demonstrate, the evidence supports the general conclusion of systematic differences between individuals that saw either a red, white, or blue yard sign (despite holding everything else but the color constant).
 
@@
 That is, the red and blue yard signs did shift people's perceptions of the partisanship of the candidate relative to the white yard sign.
-Specifically, the evidence suggests that predicted probability of a subject perceiving the candidate with a red yard sign as a Republican is 70%, whereas it is only about 30% when viewing a white yard sign.
+Specifically, the evidence suggests that the predicted probability of a subject perceiving the candidate with a red yard sign as a Republican is 70%, whereas it is only about 30% when viewing a white yard sign.
 The predicted probability that a participant perceived the candidate with the red yard sign as a Democrat is less than 5%.
 However, when viewing a blue yard sign, the predicted probability that a participant reports the candidate to be a Democrat is at about 50% whereas it is only about 10% if the yard sign is white.
-As we saw with the association between a Democratic candidate and a red yard sign, we see that the predicted probability that a participant perceived a candidate with a blue yard sign as a Republican is less than 20% and about 45% as an Independent.
-The full table of results for these models are reported in the [Appendix](#sec-2-a) in @tbl-hypothesis-2-main which contains the rest of the results from these models.
+As we saw with the association between a Democratic candidate and a red yard sign, we see that the predicted probability that a participant perceived a candidate with a blue yard sign as a Republican is less than 20%; it is about 45% as an Independent.
+The full table of results for these models are reported in the [Appendix](#sec-2-a) in @tbl-hypothesis-2-main.
 
@@
 #| layout-nrow: 1
-#| fig-cap: The partisanship of candidates change depending on the color of the yard sign
+#| fig-cap: The perceived partisanship of candidates change depending on the color of the yard sign
 #| fig-subcap:
@@
 As the consistency by which the parties have used either the color red or blue has increased since the 2000's, I suspected that the age of my subjects may moderate this relationship.
-That is, the tendency for subjects to label red yard signs as a Republican candidate versus a different color may be stronger for those who are younger as the consistency in branding is the political environment they have been around longer.
+That is, the tendency for subjects to label red yard signs as a Republican candidate versus a different color may be stronger for those who are younger, given the consistency in branding is the political environment.
 I expected this particular relationship may be weaker for older subjects as they may place current branding strategies in a larger political context where this was not always the case.
 
-I fit two ordered logistic regressions where the independent variables are indicator variables reporting whether the participant received the red (the first model) or they received the blue treatment (the second model).
+I fit similar regressions as before where the independent variables are indicator variables reporting whether the participant received the red (the first model) or they received the blue treatment (the second model).
 Those included in the baseline category for both models are those who received the white yard sign treatment.
@@
 I also explore whether these effects may be weaker for those with colorblindness.
-The results of this model is reported in [@tbl-colorblindness], which is located in the [Appendix](#sec-2-a).
-The results do not suggest that they are.
+The results of this model are reported in [@tbl-colorblindness], which is located in the [Appendix](#sec-2-a).
+The results do not suggest any effects by colorblindness.
 However, given that I had a very small number of respondents reporting colorblindness in my sample, the lack of substantive or statistical effects may be due to the fact that I did recruit enough participants with colorblindness in each group to compare.
@@
 I also test whether my effects here are sensitive to my choice to run two separate regression models -- one for each treatment.
-I fit a single ordered logistic regression with two indicator variables for the treatment coded as: 0 did not receive the red/blue treatment, 1 did receive treatment.
+I fit a single regression with two indicator variables for the treatment coded as: 0 did not receive the red/blue treatment, 1 did receive treatment.
 The full results of this alternative model specification are included in [@tbl-robustness-alt-specification-h-2].
@@
 For example, I presented participants with primarily red (and presumably Republican) yard signs, but with some blue or white in them.
-I pre-registered that the trials that use less "consistent" visual information demonstrate more uncertainty among respondents in their reported perceptions of the candidate's positions.
-Specifically, I expected that participants would perceive the yard signs that have both red and blue on them as more moderate, and that the higher proportion of the color red or blue among the two colors will lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic, respectively.
-This is not to say that I expected the results to change significantly, but rather, that the certainty by which I can predict individuals' guesses of the candidate's partisan affiliation will weaken.
+I pre-registered that the trials that use less "consistent" visual information would demonstrate more uncertainty among respondents in their reported perceptions of the candidate's positions.
+Specifically, I expected that participants would perceive the yard signs that have both red and blue on them as more moderate, and that the higher proportion of the color red or blue among the two colors would lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic, respectively.
+This is not to say that I expected the results to change significantly, but rather, that the certainty by which I can predict individuals' guesses of the candidate's partisan affiliation would weaken.
 
@@
 The predicted probabilities for each outcome occurring under different treatments and for different trials are presented in @fig-h-2a-predictions.
-@tbl-hypothesis-2a and @tbl-hypothesis-2a-cont located in the [Appendix](#sec-2-a) reports the full results of these models while @fig-h-2a-ppc located in the [Appendix](#sec-2-a) reports the posterior predictive checks of these models.
+@tbl-hypothesis-2a and @tbl-hypothesis-2a-cont located in the [Appendix](#sec-2-a) reports the full results of these models, while @fig-h-2a-ppc located in the [Appendix](#sec-2-a) reports the posterior predictive checks of these models.
 
@@
 In other words, voters are not meaningfully more likely to report that the yard sign with less blue on it belongs to a Democratic candidate versus a white and black yard sign.
-So the strength of using a blue yard sign to communicate alignment with the Democratic party weakens if you use less blue relative to white, or if you include red on it.
+So, the strength of using a blue yard sign to communicate alignment with the Democratic party weakens if you use less blue relative to white, or if you include red on it.
 With red yard signs, however, we see that voters still see them as belonging to Republican candidates, even when we reduce the amount of red on the yard sign and even when we include blue.
 
-One potential reason for this may be the association of the American flag when using all three colors given the Republican party's tendency to condemn those who do not adhere to social norms about showing respect to the American flag.
+One potential reason for this may be the association of the American flag when using all three colors, given the Republican party's tendency to condemn those who do not adhere to social norms about showing respect to the American flag.
 This, however, is untestable based on the design of the study.
@@
 
-An important implication of the snap-judgment model is that if individuals perceive candidates using the color red as Republican while candidates using the color blue as Democratic, that partisans may be more attracted to yard signs displaying the color that fits with these associations.
+An important implication of the snap-judgment model is that if individuals perceive candidates using the color red as Republican and candidates using the color blue as Democratic, then partisans may be more attracted to yard signs displaying the color that fits with these associations.
 That is, if the color red conveys group membership to the Republican party, we should expect that Republican individuals should like the red yard signs more and be more willing to vote for candidates using those colors in their campaign materials.
@@
 I fit two logistic regression models with the vote variable as the outcome I am trying to explain.
-In the first of the two logistic regression models, I examine whether the effect that receiving a red versus a white stimuli is moderated by the participants' partisanship.
+In the first of the two logistic regression models, I examine whether the effect of receiving a red versus a white stimuli is moderated by the participants' partisanship.
 As partisanship and its moderating effect on the treatment is of interest here (and partisanship is not being randomly assigned), I control for a number of confounding variables such as attention paid to politics, age, gender identification, and racial identification.
@@
 
-The other analytical tasks do not examine my pre-registered expectations derived from the motivated reasoning portion of the model.
-That is, do people process in-group information faster than out-group information?
-There is, of course, evidence of these tendencies in political circumstances [@lodge_rationalizing_2013].
+Do people process in-group information faster than out-group information? There is, of course, evidence of these tendencies in political circumstances [@lodge_rationalizing_2013].
 
-To examine whether my pre-registered expectation that motivated reasoning is also present in the processing of politically-relevant color, I examine the following: the difference in the amount of time between the start of viewing a stimulus and clicking "Next" to stop viewing the stimulus, among those who were viewing a presumed co-partisan yard sign relative to those viewing a presumed out-partisan yard sign.
+To examine my pre-registered expectation that motivated reasoning is also present in the processing of politically-relevant color, I examine the following: the difference in the amount of time between the start of viewing a stimulus and clicking "Next" to stop viewing the stimulus, among those who were viewing a presumed co-partisan yard sign relative to those viewing a presumed out-partisan yard sign.
 As the outcome is a count of the amount of time participants spent looking at a yard sign, I turn to a class of regression models that work well for explaining outcomes measured as count data.^[By the nature of my measure, I do not believe that participants can record a value of 0 as time elapsed is measured in milliseconds.
@@
 Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.] I therefore fit two poisson-gamma models (also referred to as negative binomial regressions).
-I am interested in explaining whether time elapsed can comes not only from the color of the yard sign that the subject is viewing, but also whether this effect is moderated by an individual's partisanship.
+I am interested in explaining whether time elapsed can come not only from the color of the yard sign that the subject is viewing, but also whether this effect is moderated by an individual's partisanship.
 I therefore include an interaction term between stimuli and the partisan identification of the respondent.
@@
 
-Campaigns appear to systematically use the colors red and blue at different rates depending on whether the district is more "up for grabs" or whether it is a partisan stronghold.
+I began by looking at whether congressional districts seem to display features that are consistent with my snap-judgment model.
+I found evidence that campaigns appear to systematically use the colors red and blue at different rates depending on whether the district is more "up for grabs" or whether it is a partisan stronghold.
 Specifically, my first study suggests that campaigns use more blue on their yard signs in districts that have a higher vote share for Democrats in the five previous years, and use red much less often in these same circumstances.
 This fits with the strategies communicated to me by a campaign marketing firm.
-Another question coming from that conversation and the existing literature was whether voters actually make these associations.
+Of course, another question coming from that conversation and the existing literature was, most critically, whether there is individual-level evidence that voters actually make these associations.
 
 Evidence from my experiment suggests that the use of the colors red and blue convey partisan information, while a third color like white provides very little useful political information.
-The experiment provides evidence that individuals see candidates that use red on a yard sign as more Republican and candidates that use blue as more Democratic.
+The experiment provides systematic evidence that individuals see candidates that use red on a yard sign as more Republican and candidates that use blue as more Democratic.
 Evidence from the experiment also suggests that using less of those partisan colors and using both colors makes it a bit harder for individuals to make partisan associations.
@@
 
-Having established some baseline findings, in the next chapter I examine whether the snap-judgment model holds up in more complex settings.
-Specifically, I next move to consider whether color can shape how we have conversations about politics with others, as well as the degree to which color can be a tool inhibiting political persuasion.
+Having established some baseline findings, in the next chapter I examine whether the snap-judgment model holds up in more complex settings, and with respect to other behavioral outcomes.
+Specifically, I next move to consider whether color can shape how we have conversations about politics with others, and whether color can be something that inhibits political persuasion.
 

### 2023-12-04 chapter_2/src/slides/color-book.qmd

@@
 
-Subjects will spend more time and will move their cursor more when looking at <span style='color: #00aef3'>blue</span> and <span style='color: #b70000'>red</span> yard signs
+Subjects will spend less time and will move their cursor less when looking at <span style='color: #00aef3'>blue</span> and <span style='color: #b70000'>red</span> yard signs
 

### 2023-12-04 grants/carts/src/Roberts_POLISCI_GRAD.qmd

---
subtitle: Project description & research plan
format:
  fancy-doc-pdf:
    toc: false
    latex-output-dir: ../out/
    biblatex: true
    #filters:
      #- "_extensions/andrewheiss/wordcount/citeproc.lua"
      #- "_extensions/andrewheiss/wordcount/wordcount.lua"
author:
  - name: Damon C. Roberts
    affiliations:
      - name: Univeristy of Colorado Boulder
    email: damon.roberts-1@colorado.edu
bibliography: 
  - "../../../assets/references.bib"
---

## Background of the bigger project

Since the 2000 Presidential election, the use of the color red has become synonymous with the Republican party, while the use of the color blue has become synonymous with the Democratic party [@elving_2014_npr]. Though the two parties have leaned into the colors used in media depictions of electoral maps (see @fig-party-brand as an example), it remains unclear whether these associations are strong for the public, and whether these associations influence a political outcomes, including attitude expression and behaviors.[^roberts_polisci_grad-1] This project addresses these questions.

[^roberts_polisci_grad-1]: Additional work should be done here to examine why the two political parties have gone with these two colors. This is especially true given that in other countries the color red is often picked up by left-leaning parties while the color blue is picked up by right-leaning parties [see @maestre_medero_2022_pr]. I imagine that there is a feedback loop between the parties and the public that continues to strengthen the association between these particular colors and the parties. The goal of this project is to first establish what the cognitive mechanisms are for the public to establish these associations. This work can then be helpful for those that want to build upon these ideas to explore the motivations for the parties to continue to use these colors.

::: {#fig-party-brand layout-ncol="2"}
![Republicans pre-2000](../../../chapter_2/src/assets/img/rnc_logo_pre-2000.png){#fig-republican}

![Democrats pre-2000](../../../chapter_2/src/assets/img/dnc_logo_1960.png){#fig-democrat}

![Republicans 2023](../../../chapter_2/src/assets/img/rnc_logo_2023.png){#fig-republican-post}

![Democrats 2023](../../../chapter_2/src/assets/img/dnc_logo_2023.png){#fig-democrat-post}

Party logos
:::

Though some may consider color a small concern in the grand scheme of politics, this project argues the opposite. This dissertation lays out a cognitive model that explains how colors may have potent consequences for perceptions of the political affiliations of candidates, individuals, and groups. In the project I also consider how color influences a variety of significant (political) outcomes -- these include vote choice in low information environments, the willingness to have a conversation with another person about politics, the conditions under which persuasion can occur, and where people choose to live.

While the outcomes of this project vary, the underlying goal is to examine the ways in which visual information -- and even one of the most simple forms of visual information, color -- influences long-studied outcomes in political behavior and political psychology. I do this by developing a cognitive model of visual information processing.

In the first empirical chapter of this project, I find that not only is there correlational evidence consistent with my argument -- that Republican campaigns use more red and less blue in Republican strongholds and that Democratic campaigns use more blue and less red in Democratic strongholds, but I also find experimental evidence of a randomly selected sample of Americans suggesting that subjects make the associations between the colors red and blue with Republicans and Democrats, respectively. In addition, evidence from my sample suggests that these associations are strong enough to influence expressed preference towards political candidates. Specifically, that Republican subjects prefer candidates with a red yard sign over candidates with a blue yard sign and that Democratic subjects prefer candidates with a blue yard sign over candidates with a red yard sign.

## The study for which I seek funding

There are other ways people may engage in democratic politics. The political outcome of interest in this chapter is how it may influence the degree to which we have conversations with others about politics. In an age of hyper-polarization in politics [@iyengar_affect_2012], there is growing evidence suggesting that people do not want to talk politics with those they perceive as being from the other political party due to the significant discomfort that often accompanies those conversations [@mutz_hearing_2006]. But, it is not always the case that we have *a priori* information on the partisanship of someone we might have a political conversation with. There is some evidence suggesting that we look for visual cues such as whether someone is wearing a Patagonia jacket versus a Carhartt jacket [@carlson_what_2022]. This work examines much more complicated cues. In the spirit of the whole of the project, I build on this work of political deliberation and causal predictors of the propensity to engage in political deliberation to argue that we automatically and pre-cognitively infer partisanship with something as simple as color, and not just brand preferences for clothing.

In this chapter, I am currently collecting data for a first study which establishes whether the color of a t-shirt for a potential political discussion partner may evoke these associations and encourage a preference to avoid the conversation if the hypothetical discussion partner is an out-partisan. The second study for this chapter is what I am seeking funding for.

The chapter for which I am seeking funding is to examine whether the effects I pre-registered for the first study are moderated by whether participants are primed to think of politics or not. The plan for the second study is to replicate study 1, however, I intend to have half of the participants primed with politics by asking them a political attitudes questionnaire before the treatment and another half to be asked these questions afterwards.

To provide more detail, I am currently collecting data on Study 1 where participants are randomly presented with one of the two images in @fig-protocol.

::: {#fig-protocol layout-ncol="2"}
![Red Condition](../../../chapter_3/assets/protocol/republican_avatar.png){#fig-red-condition}

![Blue Condition](../../../chapter_3/assets/protocol/democrat_avatar.png){#fig-blue-condition}

Treatment
:::

Along with the image, participants are informed that they have been paired with a discussion partner who has made an avatar to protect their privacy (I inform participants that they will have an opportunity to create their own avatar). They are then asked a series of questions that all attempt to capture the participant's willingness to participate in a conversation with that discussion partner.

In the second study, I will replicate study 1, with a slight change to examine whether or not politics being primed matters for participants. I pre-register that it will. In cases where participants are not already thinking about politics (where they haven't been primed with questionnaires about politics), I suspect the effects of the color of the shirt in the avatar should not follow the same patterns as they would for the participants who were randomly assigned to be asked questions about politics first.

This addition to the design is pivotal not only to this chapter but to the larger project: it helps me test the boundary conditions of my argument that colors matter in shaping a variety of democratic political behaviors.

I have pre-registered my expectations for both studies and have preformed target sample size calculations for this second study which are reflected in my grant application. I intend to collect the sample from Prolific.

## Impact

The impact of this project falls in a few dimensions. First, studying the role of deliberation in shaping political participation and knowledge significant. There is a large area of work in political science that demonstrates that conversations about politics can encourage participation from individuals who are not previously engaged, that it can increase feelings of political efficacy, and that we can use them as a source of information about current events, issues, and policy. Tackling the question of what predicts the propensity by which we participate in these conversations is helpful. The second dimension is that my theory is highlighting a automatic and pre-cognitive process that can shape how we feel about the potential of engaging in a political conversation. If we are avoiding conversations that can encourage participation and building knowledge of politics based on impressions, this can have potentially significant ramifications for democracy.

## Budget Justification

| Item                 | Units | Price per unit                                  | Total   |
|----------------------|-------|-------------------------------------------------|:--------|
| Participant payment  | 700   | 1.20 (based on median of 6 minutes to complete and rate of 12.00/hour) | 840    |
| Prolific Service Fee | 280   | 1                                               | 280     |
| Total Funding Needed |       |                                                 | 1120.00 |

: Budget Justification

### 2023-12-04 chapter_1/src/manuscript.qmd
drafting the theory chapter a bit

# A theory of processing politically-relevant visual information

In this chapter I will explain a theory of how visually-based political marketing works. This theory encompasses many types of visual information. As you will see, this theory builds upon existing theories of political information processing by incorporating theories from fields like psychology and neuroscience.

While I intend for the theory to be one in which scholars can apply to a number of different types of visual information, the rest of this project will focus on an almost universal and commonly covered form of visual information used in politics: color. Color is so salient in politics that we often describe partisanship by associated colors. For example, Iowa is a red state whereas New York is a blue state. Professional political scientists also tend to use the colors red and blue in the titles of their peer-reviewed papers to indicate the paper's topic being on partisanship. One example would be @goggin_what_2020 with the title of a paper being, "What Goes with Red and Blue? Mapping Partisan and Ideological Associations in the Minds of Voters".

This is symbolic of the field of political science as a whole. While the associations of the colors red and blue emerged in the 2000 Presidential Election [@elving_color_2014] and a handful of scholars [see @schloss_politics_2014;@williams_whats_2022] have documented these strong associations with color and the two dominant parties, there remains to be a theory about how these associations come to be and what the implications are for voters.

Why is this the case? Visual information, at large, is comparatively understudied in the field. The field largely considers information that are quite common and clearly contain political information such as stated policy preferences, conversations with our friends about politics, and text with political information from the news or campaigns. Relative to these more traditionally considered forms of information, visual information is much harder to pin down. Though, for many of us, visual information is ubiquitous, it is highly contextual information. As I will elaborate upon more later in this chapter and in [Chapter 3](../../chapter_3/manuscript.qmd), colors like red and blue can represent different things in different contexts and, as a result, have different effects on other forms of cognitive processing. Not only is visual information quite complex, but theorizing about it becomes harder when we consider how interdisciplinary the theorizing becomes. To not operate in a vacuum, a scholar who wants to theorize about the role of visual information in politics should consider fields such as neuroscience, psychology, marketing, and communication. I agree with @bucy_editors_2021 who discuss this challenge to the study of visual politics when they argue that each of these fields have their own methodological and generative modelling traditions, but they also apply their theories to many different contexts that may not necessarily be easily mappable to political science. These features make it quite difficult for political scientists to take some of these theories and apply it to politics though it may seem to be important low-hanging fruit.

Before examining what these fields would inform political scientists who want to theorize about visual information processing (or in this case, color), I will first discuss existing, and highly interdisciplinary efforts, to theorize about how people process political information in the political context of the United States. I will then explain how I can build upon these existing theories and fold in rich theorizing from these other fields about visual information processing. While doing so, I will present the theory that is the focus of the book. I will refer to this theory as the snap-judgment model of political information processing. Once I explain this theory, I will close this chapter with a discussion about how this contrasts with existing theories of political information processing, but I will more importantly discuss how this theory contributes to these existing models.

## The two canonical models of political information processing

There are two dominant models of how the public in the United States process political information and express attitudes in response to such information. There are, of course, many more than these two; particularly in the fields of survey and public opinion research [see @tourangeau_psychology_2000]. I will focus on the two most commonly used in political science, however, as they synthesize many of these other alternative models and are quite commonly used by political psychologists.

Zaller's [-@zaller_nature_1992;@zaller_simple_1992] "memory" model of political information processing and attitude expression is one of the most popular psychological models in political science. As opposed to viewing citizens as Aristotle's ideal democratic citizens, this "memory" model characterizes citizens as flawed Bayesian updaters. While the application of this model largely focuses on the model's implications for how we express an attitude given existing knowledge, this model characterizes how we "Receive" and "Accept" new information.

In the "memory" model, @zaller_nature_1992 characterizes the public as Bayesian updaters who, when gathering information about politics, will develop a schema about how that information relates to existing information. That is, citizens are not passively consuming political information from political elites; which is much of the focus in @zaller_nature_1992. These "predispositions" that people have influence the degree to which and *how* we organize this new information. The degree to which this new information becomes part of our cognitive schema depends upon these values. As a result, and like other related models at the time that were interested in explaining inconsistency in survey responses, the information that we have in our central cognitive schema for some political object depends upon those predispositions. As a result of these features, not all new political information will prove influential in our expressed political attitudes all of the time.

To help readers view the key contributions of the memory model, I created @fig-zaller-model which emphasizes the key processes involved in processing new information, incorporating, and then using that information to express an attitude. Though extremely simplistic, each node reflects a step in the model. We see that at each step, various predispositions mediate the relationship between the Receive-Accept and Accept-Sample nodes.

```{mermaid}
%%| label: fig-zaller-model
%%| fig-cap: Memory model of political information processing
%%| fig-width: 5
%%{init: {'theme':'base', 'themeVariables':{'primaryColor':'#ffffff', 'primaryBorderColor': '#000000'}}}%%
flowchart TB
    direction TB
    A[New information from a political elite] -->|"Predispositions (e.g., Ideology and sociodemographics)" | B[Receiver adds the new information to their schema]
    B -->|"Predispositions (e.g., Ideology and sociodemographics)"| C[Receiver expresses an attitude based on the schema]
```

The next canonical model of political information processing is Lodge and Taber's [-@lodge_rationalizing_2013] "online" model. This model also views the public as selectively incorporating Bayesian updaters. Like Zaller's [-@zaller_nature_1992] "memory" model, the Lodge and Taber's [-@lodge_rationalizing_2013] "online" model is heavily interdisciplinary. However, they characterize this "Receive" and "Accept" processes of political information as slightly different with significant implications.

One of the psychological theories that Lodge and Taber incorporate into their model of psychological processing is motivated reasoning is referred to as "motivated reasoning" [see @taber_motivated_2006]. The psychological theory of motivated reasoning suggests that the degree to which we gather new information that goes against our pre-existing viewpoints depends on which motivation we presently have. In summarizing this theory, @kunda_case_1990 argues that in contexts where we are motivated to gather information so that we are accurate we are more likely to incorporate all new information; even new information that challenges our pre-existing views. However, according to @kunda_case_1990, we often default to the motivation of selectively gathering information that fits with our pre-existing views in an attempt to have more evidence that we can cite to defend our position to those who may wish to challenge them. This theory of motivated reasoning has been and is still quite popular among social psychologists who examine how members of social groups might justify their negative views of those in another group while maintaining positive views of those in their own group, despite the presence any contradictory evidence.

Though, Zaller's [-@zaller_nature_1992] considers the role of ideology as one of the "predispositions" that influence the reception and acceptance of new information, Lodge and Taber's key innovation is that partisan identity and the degree to which we are motivated to defend the political perspectives of our partisan confederates is **the** pre-disposition that influences the degree to which we consider new information [@lodge_rationalizing_2013]. This perspective predicts that rather than the public appearing to be somewhat regularly biased, but also inconsistent, in expressing their attitudes about something in the face of new information, this model suggests that the public are somewhat predictably going to gather information and express attitudes that align with those of those holding the same partisan identification. This model has been significant for informing theories around political polarization in the United States as well as conversations around the degree to which political persuasion is possible with the public.

Another feature of Lodge and Taber's [-@lodge_rationalizing_2013] model is that it considers the role of affect. Throughout this book, I conceptualize affect as valanced (positive or negative) reactions to some political object. This departs from conceptualizations popular among political scientists where some see it as somewhat synonymous with emotion [see @marcus_affective_2000]. However, I depart with this to align with popular conceptualizations [see @sander_cambridge_2013] that distinguish affect from emotion where affect is a pre-conscious valanced reaction to an object and I conceptualize emotion as a discrete or categorical classification of these valanced reactions which require some degree of conscious processing. In the online model, they include the theory of affect transfer which, when we conceptualize the brain as a network of interconnected nodes [see @collins_spreading-activation_1975], suggests that if an individual dislikes a directive to ICE that limits the number of deportations that they can carry out then we would predict that the same individual would also dislike a directive that extends protection to children of non-documented parents that immigrated to the United States by enrolling in the DACA program due to the person's preferences for restrictive immigration.

Relative to Zaller's [-@zaller_nature_1992] memory model, the online model is much more permissive of context. Besides the rhetorical devices that the particular messenger uses and the pre-dispositions that the receiver has, Lodge and Taber's [-@lodge_rationalizing_2013] model presents a situation where there are many more mediating factors that influence these processes. The degree to which we are motivated to engage with this information in the first place depends on particular motivations that we may have such as to gather accurate information or information that makes us feel more confident that our pre-existing preferences are accurate. As a result of emotion, pre-dispositions such as anxiety can induce this accuracy motivation [@marcus_affective_2000]. Further, we do not just consume this information but the degree to which this information evokes a directionally valanced evaluation depends on what prior information is salient (or "hot" in line with Lodge and Taber's [-@lodge_rationalizing_2013] use of the phrase from the theory of hot cognition) when we consume this new information.

While there are some differences between these models, they also agree on foundational perspectives of how memory is used to generate attitudes. The first is the perspective that information is organized in a schema. This conceptualization borrows significantly from the perspective that the brain is organized as a set of associated nodes in a network. This perspective has been a powerful perspective in a number of fields that study cognition. In this perspective, the cognition works because we have nodes which identify a particular piece of information. These nodes are connected to each other in a mental schema. Or some structured organization of information or memories. These connections between nodes, however are not equally strong. Rather, the strength of these nodes depend on a variety of features. Though the memory and online model vary in which features matter for influencing the strength of these nodes, they still consider the influence of activated confounding information that can make some of these connections between nodes more relevant than others. As a result, both models suggest that we do not just gather information and then just calculate the average between a pros and cons list. Rather, the degree to which a new node is added and used in the future depends on which nodes it is attached to when being encoded as memory.

### 2023-12-04 chapter_1/src/manuscript.qmd
closing up some drafting for today

@@
 The first is the perspective that information is organized in a schema.
-This conceptualization borrows significantly from the perspective that the brain is organized as a set of associated nodes in a network.
+This conceptualization borrows significantly from the perspective that the brain is organized as a set of associated nodes in a network [@collins_spreading-activation_1975].
 This perspective has been a powerful perspective in a number of fields that study cognition.
 In this perspective, the cognition works because we have nodes which identify a particular piece of information.
-These nodes are connected to each other in a mental schema.
-Or some structured organization of information or memories.
+These nodes are connected to each other in a mental schema; or some structured organization of information or memories.
 These connections between nodes, however are not equally strong.
@@
 Rather, the degree to which a new node is added and used in the future depends on which nodes it is attached to when being encoded as memory.
+
+For the purposes of this project, a key commonality between these models is that they are theorizing about how pre-conscious cognitive processes not only shape how we interpret our political world but also how these processes shape how we react to this political reality.
+These models are widely cited and inform most contemporary political psychology.
+One way in which we can build upon the impact of these models is to consider forms of information that are perhaps more common than text or persuasive arguments provided political elites is by adjusting these models to account for visual information.
+Many of the fundamentals present in these models are necessary to theorize about visual information.
+However, making slight adjustments to consider the temporal ordering of what types of information are processed first has significant implications for how we understand what influences our understanding of the political world and how the public come to express an attitude.
+
+## A theory of how visual information matters to politics

### 2023-12-05 chapter_1/src/manuscript.qmd
a full draft of the theory chapter. Needs lots of edits, but that's okay

@@
 
+## Gathering the pieces to the puzzle
+
+Existing models of information processing in politics are largely considered in the context of consuming news and following statements by politicians and political candidates.
+I argue that there is another way in which politicians may communicate information with the mass public that has significant downstream impacts on political cognition and attitude expression: visual information.
+
+Let me first start off by departing from talking about politics for a minute.
+Visual branding is a significant factor in predicting consumer behavior.
+Marketing is not simply producing catchy slogans but is also about how to visually present a brand.
+There is ample evidence suggesting that choices in visual presentation has significant influence on whether or not a consumer will purchase one of your products.
+For example, evidence suggests that hotels that have colors like red are much less likely to be booked relative to hotel rooms that feature softer colors like blues and beiges [@kuo_impact_2023].
+
+As this example demonstrates, color is a significant form of visual information that can influence how we behave.
+But, why?
+There is a rich literature in marketing referred to as color theory which suggests that colors evokes particular affective and emotive reactions.
+For example, @cimbalo_emotionally_1978 demonstrates that colors like red and blue contain different emotive associations.
+Specifically that red can evoke negative emotions and blue can contain positive and more soothing emotions.
+
+Connecting this idea to that of the work that conceptualizes memory as an associative network, colors are not simply just something that exists but it is a node that contains its own associations.
+Like any node or memory, color does not have to hold one connection nor do all connections have equal strength under every circumstance.
+Let me illustrate this with a simple example.
+
+```{mermaid}
+%%| label: fig-color-associations
+%%| fig-cap: Colors are associative nodes
+%%| fig-width: 5
+%%{init: {'theme':'base', 'themeVariables':{'primaryColor':'#ffffff', 'primaryBorderColor': '#000000'}}}%%
+flowchart LR;
+
+A[Yellow] --> B[Sweatshirt]
+A --> C[Banana]
+A --> D[Sunrise]
+A --> E[Los Angeles Rams]
+```
+
+@fig-color-associations presents all the different things that we may associate the color Yellow with.
+We might associate it with our favorite sweatshirt; with a food item, a banana; the sunrise; and the Los Angeles Rams.
+You may think of different things when you think of the color yellow.
+This is because you may have different connections to the "yellow node" in your head than I do.
+This arises with different experiences and differences in the salience of those associations because of your cognitive schema.
+However, 3 months from now you may think of different things when asked what you associate with the color yellow.
+This is because your schema is reorganized or different aspects of your schema are accessed because of the context you are in.
+Perhaps, today you think of the Los Angeles Rams, but say 3 months from now it is April and you are thinking about the Milwaukee Brewers because it is now baseball season and the Super Bowl happened a couple months ago.
+
+Complicating this a bit more, we do not only hold these associations with particular objects, but theories of associative memory suggests that nodes in our pre-existing cognitive schemas are highly multi-dimensional [@kahana_laws_2022].
+We can see the most simple example of this in @fig-color-associations.
+We can think of the color yellow as being associated with clothing items, food items, a time of day, and a sports team.
+Associations with the color yellow are not only constrained by the type of object it is such as only food items.
+A more complicated example is that the color yellow can also contain affective associations too.
+
+Colors can contain affective associations through connections to the affective associations we have with related objects.
+Affect is a strong and central part to human memory.
+Most memories contain some affective component to them [@kensinger_affective_2022].
+When we think back to some event in our life, rarely do we only recall what happened but we often recall how it made us feel -- and sometimes we may start to feel happy, angry, or fearful like we did in that recalled event.
+Going back to the idea of affect transfer as discussed by Lodge and Taber [-@lodge_rationalizing_2013] who applied in in the context of politics, colors contain affective information not necessarily as a result of any inherent property about the color but because of the affect that comes with the objects that we commonly associate with that color [@cimbalo_emotionally_1978].
+
+So, what does this mean for politics?
+As the first chapter discussed, colors have been present throughout the political history of the United States.
+Politicians and political candidates are conveying information to potential voters and to the public when they select particular colors.
+This occurs through the same cognitive mechanisms that I have discussed thus far.
+As we gain more experience with connecting particular colors to a particular political idea or set of political ideas, the strength connecting these nodes increases and makes it a more central part of our cognitive schema.
+Over time, we build these associations with visual information and particular political ideas or political individuals.
+The associated affective responses that we have to those political ideas or figures can transfer onto those colors as we strengthen the association of the color with the political ideas or figures.
+
+In the context of the United States, the colors red and blue are ubiquitous in politics.
+Since the 2000 Presidential Election, news organizations have consistently converged on the use of the colors red and blue to convey to the public whether the Republican or the Democrat, respectively, won a particular electoral district [@elving_color_2014].
+Extending these ideas about how associations between color and some object can come to form in the brain, we may expect that the associations of the colors red and blue with Republicans and Democrats in the United States would occur.
+
+It is not only that associations between a particular political party and their ideas or prominent figures are associated with these colors, but we may expect that it will have significant political consequence.
+Going back to the role of colors in marketing and consumer behavior, a foundational idea that produces this theory is that the affective associations with a color has downstream effects on behavior.
+In non-political contexts, there is a rich literature in affective neuroscience and cognition that traces the evoked affect to behavioral outcomes in a wide-variety of contexts [@kensinger_affective_2022].
+In fact, these ideas have been debated in cognition all the way back to the father of modern Biology and Evolutionary Psychology, Charles Darwin, and has been an area of scientific debate ever since.
+In political science, there is a rich area of political psychology focused on tracing emotive and affective reactions to political information to behavior.
+For example, @marcus_affective_2000 develop Affective Intelligence Theory which argues that anxiety induces information-seeking behavior among the public and can be a strong predictor of following politics more closely.
+@lodge_rationalizing_2013 builds on this Affective Intelligence Theory and argues how this can influence motivated reasoning.
+Adding more nuance to these arguments, @pheonix_anger_2019 also has discussed the implications of stereotypes for Black Americans and how Black Americans can engage in emotional restraint to not express Anger which is an emotion induced from moral outrage that can have a positive effect on political participation.
+In short, emotion and affect are common in politics and that it has significant predictive power for political behavior.
+
+So, where do these ideas leave us?
+Building upon all of these ideas, we have all of the pieces to build the puzzle that is understanding how visual information is involved in politics.
+This is the objective of the next section.
+
 ## A theory of how visual information matters to politics
+
+Visual information is processed extremely quickly.
+For example, @ames_impression_2012 demonstrate that to form an impression about another based on visual information of a social interaction takes only about 33 milliseconds (abbreviated as ms).
+Going back to our days in high school physics, we may recall that light travels faster than sound due to the tendency for sound requiring some degree of matter for sound to travel by.
+This is why in the vacuum of space, light travels much easier relative to sound.
+
+If we are receiving this visual information first, then we might expect that the pre-conscious cognitive mechanisms start the process of political cognition before traditionally considered mediums of political information.
+So, let's more directly discuss this cognitive process in politics now that we understand the relevant fundamentals of cognition.
+
+First, we receive visual information as wavelengths that are passed to our retina.
+Our retina passes this information to our optic nerve as an electrical signal to our visual cortex.
+Once in our visual cortex, the process of connecting those nodes of visual information in the cortex activates the paths to related nodes across our brain [@goldstein_sensation_2017].
+While this glosses over important physiological components such as ganglion cells, the differences between the V1 and V4 sections of the visual cortex, this still illustrates how the information is received and starts those now familiar cognitive processes.
+
+Once the visual information has been decoded, our brain will want to find information from those electrical signals.
+It therefore starts looking down all of these forking paths that connect nodes together.
+In other words, he associative network has been activated.
+Once activated, we will continue to spend effort on paths that continually provides more relevant information and will abandon paths that are less relevant and informative.
+
+As affective neuroscientists argue, we are not only accessing memories associating the color yellow with a sweatshirt, but we are also looking for associated nodes that contain affective information as well [see @kensinger_affective_2022].
+Such as yellow with a clothing item that we like.
+Once we make these connections, we will have an affective response to this newly decoded visual information as informed by related visual information that contains affective information.
+
+So, how does this work with political visual information? @fig-theory presents what I call the snap-judgment model of politically-relevant visual information processing.
+
+{{< include ../../assets/_theory.qmd >}}
+
+We are in a political setting.
+Knowing that we are in a political setting, we should be primed to expect that the information we will receive will contain political messages or is designed to convey political information.
+Just like if I was in a department store and saw yellow out of the corner of my eye, I'd expect it to be a sweater much more than I would expect for it to be a banana.
+The reverse is true if I were in a grocery store instead of a department store.
+What this means for politics, critically, is that visual information that can be political and non-political will depend on whether or not I am in a context that receiving information about politics makes sense.
+For example, I would not be surprised to receive visual information about politics when watching advertisements during election season or at a political rally, but would be surprised and confused if this happened when attending an NBA game.
+Likewise, I would be surprised and confused to be seeing information about the NBA at a political event rather than information about politics.
+This is a central boundary condition for this theory.
+Not all visual information is political all of the time.
+This is because information as nodes can be associated to a number of different things and we can find different meanings from them in different contexts.
+
+Once I have consumed visual information about politics, this cognitive process that I have belabored is activated.
+I seek to find political meaning from that visual information.
+Pre-consciously my brain seeks to go down these finite forking paths to find which associated node can give me valuable information.
+
+Since politics is primed, it is likely more successful and efficient if I search through nodes related to politics and not any and everything that can conceivably be related.
+So, my brain elects to look through potentially relevant nodes that are part of a cognitive schema that I may have about politics.
+My brain continues to refine which paths it goes down by finding paths with strong associations -- or high amounts of similarity to the information that I am currently working with.
+
+Once I settle on a node or set of connected nodes, I form an impression or a reaction to that political information through affect transfer.
+If I want to understand whether I should continue to engage or disengage with the source of the information, I need to have some set of related pre-existing attitudes that I can rely upon to help me as I do not yet have a formed attitude about the current visual information that I am interacting with.
+
+As this is a pre-conscious process, the attitude that I rely upon to make a decision about whether to continue interacting with the source of this information will be a valanced affective response as opposed to a cognitive and more laborious process of having an emotive and more nuanced reaction.
+This valanced response will either encourage me to disengage from the object or to continue engaging with it.
+
+In politics, negatively valanced information often encourages a disengagement motivation while positively valanced information encourages continued engagement [see @lodge_rationalizing_2013;@valentino_election_2011].
+For example, those who are Democrats who come across a Donald J.
+Trump rally, they may be much more likely to be motivated to disengage and change the channel or scroll to the next video than a Republican who might have more positively valanced associations with Trump than a Democrat.
+Evidence for tendencies like this play out in a number of different settings in the affectively polarized era that characterizes contemporary politics in the United States [see @mutz_hearing_2006;@iyengar_affect_2012;@iyengar_origins_2019].
+
+Once these motivations have been activated, we are likely to stay disengaged or engaged with the political object unless new information countervails that.
+This new information could be more visual information, or it could be information that is processed later such as a stated policy position.
+The cognitive process of finding meaning in the new information restarts and is evaluated to either be negative or positively valanced.
+Once making that determination, our affective state (the total state of how we feel) will directionally remain the same, or it will adjust.
+
+Critically, however, the information that we temporally process first will carry significant weight relative to the new information.
+As time goes on, memory falters and we do not remember all of the details of the information.
+Critically, what remains is the affective state the information encouraged but not necessarily all of the details [@kahana_laws_2022; see also @lodge_rationalizing_2013].
+As that information is then encoded as memory and becomes part of your cognitive schema that will be used to form a "snap-judgment" of subsequent experiences.
+
+Critically, what this model implies is that simple information that is temporally processed *before* more complicated forms of information will shape our actions and perceptions of any subsequent information.
+For simple visual information such as color, this means that color can be a significant influence on how we perceive and respond to substantive political information such as a stated policy position.
+Let me illustrate the implications of this with an example.
+
+Previous models of political information processing would examine how a Democrat and a Republican may differentially respond to viewing a speech orated by Donald J.
+Trump.
+The memory-based model would suggest that highly informed Democrats and Republicans, who have a robust ideological schema would be less persuaded than those who are less informed.
+In that situation, highly informed Democrats would be much less likely to express agreement with Trump or to change their position.
+Meanwhile, highly informed Republicans may be less persuaded, but because they already agree with Trump's positions.
+Less informed Republicans and Democrats may be more open to persuasion due to the fact that this new information from Trump is not drowned out by the significant information that may countervail the new information provided by Trump.
+The online model diverges from this to argue that the fact that Trump is speaking, Democrats are already likely to be motivated to not even consider any of the information that Trump is providing while Republicans will be much more willing to accept all of it.
+
+Before Trump even goes to speak at the podium, however, these Republican and Democratic viewers are met with a lot of visual information of the stage.
+Perhaps they see a stage with a red backdrop -- one that is descriptively associated with Republicans [see @elving_color_2014;@schloss_politics_2014].
+In agreement with the online model that refines the memory-based model, I should expect that these colors have already activated a cognitive process which encourages the affective state and motivations to disengage or engage more with the television before Trump has even entered the stage.

### 2023-12-06 chapter_1/src/manuscript.qmd
editing the draft a bit

@@
 
-In this chapter I will explain a theory of how visually-based political marketing works.
-This theory encompasses many types of visual information.
-As you will see, this theory builds upon existing theories of political information processing by incorporating theories from fields like psychology and neuroscience.
+In this chapter I will present a theory of how political visual objects are used by the public to make decisions.
+As I will argue throughout the chapter, existing models of political information processing set the foundation for the theory I present here.
+However, there requires adjustment to the underlying cognitive mechanisms to account for differences in how the brain processes visual information relative to things like a stated policy position of a political candidate that you read in the news paper or hear while watching a video.
 
 While I intend for the theory to be one in which scholars can apply to a number of different types of visual information, the rest of this project will focus on an almost universal and commonly covered form of visual information used in politics: color.
-Color is so salient in politics that we often describe partisanship by associated colors.
-For example, Iowa is a red state whereas New York is a blue state.
-Professional political scientists also tend to use the colors red and blue in the titles of their peer-reviewed papers to indicate the paper's topic being on partisanship.
+I do this for a few reasons.
+First, color is so salient in politics that we often describe partisanship by associated colors.
+For example, Iowa is a "red state" whereas New York is a "blue state." Professional political scientists also tend to use the colors red and blue in the titles of their peer-reviewed papers to indicate the paper's topic being on partisanship.
 One example would be @goggin_what_2020 with the title of a paper being, "What Goes with Red and Blue?
 Mapping Partisan and Ideological Associations in the Minds of Voters".
+Second, color is one of the most simple forms of visual information that we receive.
+Given this, color seems to not only be an important starting place but it also allows for the focus to be on the foundations of how visual information is processed as opposed to immediately adding too many layers of complexity that I risk undertheorizing about the key mechanisms and overtheorize about nuances that do not apply in most real-world cases.
 
-This is symbolic of the field of political science as a whole.
-While the associations of the colors red and blue emerged in the 2000 Presidential Election [@elving_color_2014] and a handful of scholars [see @schloss_politics_2014;@williams_whats_2022] have documented these strong associations with color and the two dominant parties, there remains to be a theory about how these associations come to be and what the implications are for voters.
+Why is it necessary for me to start with simple cases?
+Visual information, at large, is comparatively understudied in the field.
+The field largely considers information that are quite common and explicitly political such as stated policy preferences, conversations with our friends about politics, and text with political information from the news or campaigns.
+This is not an indictment on the field.
+In fact, political psychologists have made significant strides to theorize about political information processing.
+The dominant theories coming from these interdisciplinary efforts are at the core of the theory that I present here.
+The reason there is relatively little theorizing about visual information and not more explicitly political information is likely due to the methodological challenges that come with theorizing about visual experiences.
 
-Why is this the case?
-Visual information, at large, is comparatively understudied in the field.
-The field largely considers information that are quite common and clearly contain political information such as stated policy preferences, conversations with our friends about politics, and text with political information from the news or campaigns.
 Relative to these more traditionally considered forms of information, visual information is much harder to pin down.
@@
 
-Before examining what these fields would inform political scientists who want to theorize about visual information processing (or in this case, color), I will first discuss existing, and highly interdisciplinary efforts, to theorize about how people process political information in the political context of the United States.
-I will then explain how I can build upon these existing theories and fold in rich theorizing from these other fields about visual information processing.
-While doing so, I will present the theory that is the focus of the book.
+While it may be difficult, these efforts are worthwhile.
+As I will discuss, the key implication of the theory is that visual information will shape the pre-conscious processing of this more explicitly political information.
+In other words, the model suggests that the visual information that we consume will impact the degree to which we accept and the attitudes we express in response to explicitly political information; we form an impression or a snap-judgment that will influence the information that comes afterwards.
+This would help us further refine our understanding of how voters can make decisions with relatively little information, whether or not we will have a conversation with others about politics, and how we form impressions about the political leanings of groups of people to name a few examples.
+
+Before presenting a theory of visual information processing in politics, I will first discuss the dominant models of political information processing.
+As I have mentioned, the mechanisms outlined in these theories are at the core of the theory that I present.
+Both practically and conceptually, my model of visual information processing amends these existing models so that they may better generate predictions about how visual information influences political cognition.
+After introducing some of the key mechanisms outlined in those theories, I will present the theory that is the focus of the book.
 I will refer to this theory as the snap-judgment model of political information processing.
@@
 As opposed to viewing citizens as Aristotle's ideal democratic citizens, this "memory" model characterizes citizens as flawed Bayesian updaters.
-While the application of this model largely focuses on the model's implications for how we express an attitude given existing knowledge, this model characterizes how we "Receive" and "Accept" new information.
+While the application of this model largely focuses on the model's implications for how we express an attitude by "Sampling" from our existing knowledge, this model characterizes how we "Receive" and "Accept" new information.
 
-In the "memory" model, @zaller_nature_1992 characterizes the public as Bayesian updaters who, when gathering information about politics, will develop a schema about how that information relates to existing information.
-That is, citizens are not passively consuming political information from political elites; which is much of the focus in @zaller_nature_1992.
-These "predispositions" that people have influence the degree to which and *how* we organize this new information.
-The degree to which this new information becomes part of our cognitive schema depends upon these values.
-As a result, and like other related models at the time that were interested in explaining inconsistency in survey responses, the information that we have in our central cognitive schema for some political object depends upon those predispositions.
+In the "memory" model, @zaller_nature_1992 characterizes the public as Bayesian updaters who, when gathering information about politics, will develop a cognitive schema about how that information relates to existing information.
+That is, citizens are not passively consuming political information from political elites -- which is much of the focus in @zaller_nature_1992.
+Rather, the public actively integrate this information.
+Nevertheless, they do not weigh all new information the same.
+The public have a number of "predispositions" that have influence on the degree to which and *how* we organize this new information.
 As a result of these features, not all new political information will prove influential in our expressed political attitudes all of the time.
 
-To help readers view the key contributions of the memory model, I created @fig-zaller-model which emphasizes the key processes involved in processing new information, incorporating, and then using that information to express an attitude.
-Though extremely simplistic, each node reflects a step in the model.
+To help readers view the key contributions of the memory model, I summarize the basics in @fig-zaller-model which emphasizes the key processes involved in processing new information, incorporating, and then using that information to express an attitude.
+Though the figure is extremely simplistic, each node reflects a step in the model.
 We see that at each step, various predispositions mediate the relationship between the Receive-Accept and Accept-Sample nodes.
@@
 
-One of the psychological theories that Lodge and Taber incorporate into their model of psychological processing is motivated reasoning is referred to as "motivated reasoning" [see @taber_motivated_2006].
+One of the psychological theories that Lodge and Taber incorporate into their model of psychological processing is referred to as "motivated reasoning" [see @taber_motivated_2006].
 The psychological theory of motivated reasoning suggests that the degree to which we gather new information that goes against our pre-existing viewpoints depends on which motivation we presently have.
@@
 However, according to @kunda_case_1990, we often default to the motivation of selectively gathering information that fits with our pre-existing views in an attempt to have more evidence that we can cite to defend our position to those who may wish to challenge them.
-This theory of motivated reasoning has been and is still quite popular among social psychologists who examine how members of social groups might justify their negative views of those in another group while maintaining positive views of those in their own group, despite the presence any contradictory evidence.
+This theory of motivated reasoning has been and is still quite popular among social psychologists who examine how members of social groups might justify their negative views of those in another group while maintaining positive views of those in their own group, despite the presence any contradictory evidence [see @redlawsk_affective_2010].
 
@@
 This departs from conceptualizations popular among political scientists where some see it as somewhat synonymous with emotion [see @marcus_affective_2000].
-However, I depart with this to align with popular conceptualizations [see @sander_cambridge_2013] that distinguish affect from emotion where affect is a pre-conscious valanced reaction to an object and I conceptualize emotion as a discrete or categorical classification of these valanced reactions which require some degree of conscious processing.
-In the online model, they include the theory of affect transfer which, when we conceptualize the brain as a network of interconnected nodes [see @collins_spreading-activation_1975], suggests that if an individual dislikes a directive to ICE that limits the number of deportations that they can carry out then we would predict that the same individual would also dislike a directive that extends protection to children of non-documented parents that immigrated to the United States by enrolling in the DACA program due to the person's preferences for restrictive immigration.
+However, I depart with this to align with popular conceptualizations that distinguish affect from emotion where affect is a pre-conscious valanced reaction to an object and I conceptualize emotion as a discrete or categorical classification of these valanced reactions which require some degree of conscious processing [see @sander_cambridge_2013].
+In the online model, they include the theory of affect transfer which, when we conceptualize the brain as a network of interconnected nodes [see @collins_spreading-activation_1975], suggests that if an individual dislikes, for example, a directive to ICE that limits the number of deportations that they can carry out then we would predict that the same individual would also dislike a directive that extends protection to children of non-documented parents that immigrated to the United States by enrolling in the DACA program due to the person's preferences for restrictive immigration.
+This aligns with popular conceptualizations of how attitudes form by considering memories as heavily affectively-laden [@fazio_attitudes_2007].
 
@@
 The degree to which we are motivated to engage with this information in the first place depends on particular motivations that we may have such as to gather accurate information or information that makes us feel more confident that our pre-existing preferences are accurate.
-As a result of emotion, pre-dispositions such as anxiety can induce this accuracy motivation [@marcus_affective_2000].
+As a result of emotion, predispositions such as anxiety can induce this accuracy motivation [@marcus_affective_2000].
 Further, we do not just consume this information but the degree to which this information evokes a directionally valanced evaluation depends on what prior information is salient (or "hot" in line with Lodge and Taber's [-@lodge_rationalizing_2013] use of the phrase from the theory of hot cognition) when we consume this new information.
@@
 This conceptualization borrows significantly from the perspective that the brain is organized as a set of associated nodes in a network [@collins_spreading-activation_1975].
-This perspective has been a powerful perspective in a number of fields that study cognition.
+This perspective has been foundational for a number of fields that study cognition.
 In this perspective, the cognition works because we have nodes which identify a particular piece of information.
-These nodes are connected to each other in a mental schema; or some structured organization of information or memories.
-These connections between nodes, however are not equally strong.
-Rather, the strength of these nodes depend on a variety of features.
+These nodes are connected to each other in a mental schema; or some structured organization of information [@collins_spreading-activation_1975;@kahana_laws_2022].
+These connections between nodes, however are not equally strong [@fazio_attitudes_2007].
+Rather, the strength of these nodes depend on a variety of features [@fazio_attitudes_2007;@kahana_laws_2022].
 Though the memory and online model vary in which features matter for influencing the strength of these nodes, they still consider the influence of activated confounding information that can make some of these connections between nodes more relevant than others.
-As a result, both models suggest that we do not just gather information and then just calculate the average between a pros and cons list.
+As a result, both models suggest that we do not just gather information and then just perform some arithmetic on a pros and cons list.
 Rather, the degree to which a new node is added and used in the future depends on which nodes it is attached to when being encoded as memory.
@@
 Many of the fundamentals present in these models are necessary to theorize about visual information.
-However, making slight adjustments to consider the temporal ordering of what types of information are processed first has significant implications for how we understand what influences our understanding of the political world and how the public come to express an attitude.
+Nevertheless, making slight adjustments to consider the temporal ordering of what types of information are processed first has significant implications for how we understand what influences our understanding of the political world and how the public come to express an attitude.
 
@@
 
-Let me first start off by departing from talking about politics for a minute.
+Let me first start off by departing from talking about politics for a minute and consider a related topic: marketing and the role of color.
 Visual branding is a significant factor in predicting consumer behavior.
@@
 
-@fig-color-associations presents all the different things that we may associate the color Yellow with.
+@fig-color-associations presents all the different things that we may associate the color yellow with.
 We might associate it with our favorite sweatshirt; with a food item, a banana; the sunrise; and the Los Angeles Rams.
@@
 Associations with the color yellow are not only constrained by the type of object it is such as only food items.
-A more complicated example is that the color yellow can also contain affective associations too.
+A more complicated example is that the color yellow can also contain differing affective associations too depending on the object.
 
 Colors can contain affective associations through connections to the affective associations we have with related objects.
-Affect is a strong and central part to human memory.
-Most memories contain some affective component to them [@kensinger_affective_2022].
+Affect is a strong and central part to human memory [see @fazio_attitudes_2007;@kensinger_affective_2022].
 When we think back to some event in our life, rarely do we only recall what happened but we often recall how it made us feel -- and sometimes we may start to feel happy, angry, or fearful like we did in that recalled event.
-Going back to the idea of affect transfer as discussed by Lodge and Taber [-@lodge_rationalizing_2013] who applied in in the context of politics, colors contain affective information not necessarily as a result of any inherent property about the color but because of the affect that comes with the objects that we commonly associate with that color [@cimbalo_emotionally_1978].
+This is because memories are simply refired electrical signals between a particular network of neurons that were originally active during experiencing (encoding) the event [@fazio_attitudes_2007].
+Going back to the idea of affect transfer, as discussed by Lodge and Taber [-@lodge_rationalizing_2013] who applied in in the context of politics, colors contain affective information not necessarily as a result of any inherent property about the color but because of the affect that comes with the objects that we commonly associate with that color [@cimbalo_emotionally_1978].
 
@@
 It is not only that associations between a particular political party and their ideas or prominent figures are associated with these colors, but we may expect that it will have significant political consequence.
-Going back to the role of colors in marketing and consumer behavior, a foundational idea that produces this theory is that the affective associations with a color has downstream effects on behavior.
+Going back to the role of colors in marketing and consumer behavior, a foundational idea for this theory is that the affective associations with a color has downstream effects on behavior.
 In non-political contexts, there is a rich literature in affective neuroscience and cognition that traces the evoked affect to behavioral outcomes in a wide-variety of contexts [@kensinger_affective_2022].
@@
 For example, @ames_impression_2012 demonstrate that to form an impression about another based on visual information of a social interaction takes only about 33 milliseconds (abbreviated as ms).
-Going back to our days in high school physics, we may recall that light travels faster than sound due to the tendency for sound requiring some degree of matter for sound to travel by.
+Going back to our days in high school physics, we may recall that light travels faster than sound as it requiring some degree of matter for it to travel by.
 This is why in the vacuum of space, light travels much easier relative to sound.
+Not that sound does not travel in space, it is just much slower.
 
@@
 Once in our visual cortex, the process of connecting those nodes of visual information in the cortex activates the paths to related nodes across our brain [@goldstein_sensation_2017].
-While this glosses over important physiological components such as ganglion cells, the differences between the V1 and V4 sections of the visual cortex, this still illustrates how the information is received and starts those now familiar cognitive processes.
+While this glosses over important physiological components such as the role of ganglion cells and the differences between the V1 and V4 sections of the visual cortex, this still illustrates how the information is received and starts those now familiar cognitive processes.
 
-Once the visual information has been decoded, our brain will want to find information from those electrical signals.
+Once the visual information has been decoded, our brain will want to find information, or meaning, from those electrical signals.
 It therefore starts looking down all of these forking paths that connect nodes together.
-In other words, he associative network has been activated.
+In other words, the associative network has been activated.
 Once activated, we will continue to spend effort on paths that continually provides more relevant information and will abandon paths that are less relevant and informative.
@@
 
-We are in a political setting.
-Knowing that we are in a political setting, we should be primed to expect that the information we will receive will contain political messages or is designed to convey political information.
-Just like if I was in a department store and saw yellow out of the corner of my eye, I'd expect it to be a sweater much more than I would expect for it to be a banana.
-The reverse is true if I were in a grocery store instead of a department store.
-What this means for politics, critically, is that visual information that can be political and non-political will depend on whether or not I am in a context that receiving information about politics makes sense.
-For example, I would not be surprised to receive visual information about politics when watching advertisements during election season or at a political rally, but would be surprised and confused if this happened when attending an NBA game.
-Likewise, I would be surprised and confused to be seeing information about the NBA at a political event rather than information about politics.
-This is a central boundary condition for this theory.
-Not all visual information is political all of the time.
+When in a political setting, one should be primed to expect that the information will contain political messages or is designed to convey political information.
+Similar to being in a department store and seeing yellow out of the corner of one's eye, an individual would be much more likely to expect to see a sweater as opposed to a banana.
+The reverse is true if one were in a grocery store instead of a department store.
+What this means for politics, critically, is that visual information that can be political and non-political will depend on whether or not one is in a context that receiving information about politics makes sense.
+For example, one would not be surprised to receive visual information about politics when watching advertisements during election season or at a political rally, but would be surprised and confused if this happened when attending an NBA game.
+Likewise, one would be surprised and perhaps confused to see information about the NBA at a political event rather than information about politics.
+This is a central boundary condition for this theory: not all visual information is political all of the time.
 This is because information as nodes can be associated to a number of different things and we can find different meanings from them in different contexts.
 
-Once I have consumed visual information about politics, this cognitive process that I have belabored is activated.
-I seek to find political meaning from that visual information.
-Pre-consciously my brain seeks to go down these finite forking paths to find which associated node can give me valuable information.
+Once one consumes visual information about politics, this cognitive process that I have belabored is activated.
+One will seek to find political meaning from that visual information.
+This pre-conscious process that the brain starts will go down these finite forking paths to find which associated node provides information about the current stimulus.
 
-Since politics is primed, it is likely more successful and efficient if I search through nodes related to politics and not any and everything that can conceivably be related.
-So, my brain elects to look through potentially relevant nodes that are part of a cognitive schema that I may have about politics.
-My brain continues to refine which paths it goes down by finding paths with strong associations -- or high amounts of similarity to the information that I am currently working with.
+Since politics is primed, it is likely more successful and efficient to search through nodes related to politics and not any and everything that can conceivably be related.
+So, the brain elects to look through potentially relevant nodes that are part of a cognitive schema about politics.
+The brain continues to refine which paths it goes down by finding paths with strong associations -- or high amounts of similarity to the stimulus.
 
-Once I settle on a node or set of connected nodes, I form an impression or a reaction to that political information through affect transfer.
-If I want to understand whether I should continue to engage or disengage with the source of the information, I need to have some set of related pre-existing attitudes that I can rely upon to help me as I do not yet have a formed attitude about the current visual information that I am interacting with.
+Once identifying a node or set of connected nodes, affect transfer would enable me to form an impression or a reaction to that political information.
+This affect transfer enables a behavioral response: to continue to engage or disengage from an object.
 
 As this is a pre-conscious process, the attitude that I rely upon to make a decision about whether to continue interacting with the source of this information will be a valanced affective response as opposed to a cognitive and more laborious process of having an emotive and more nuanced reaction.
-This valanced response will either encourage me to disengage from the object or to continue engaging with it.
+This valanced response will either encourage me to disengage from the object or to continue engaging with it [@sander_cambridge_2013].
 
@@
 Once these motivations have been activated, we are likely to stay disengaged or engaged with the political object unless new information countervails that.
+That is, we have an encoded memory that suggests an object is negative or positive and to change these motivations will requires some degree of changing our mind.
 This new information could be more visual information, or it could be information that is processed later such as a stated policy position.
@@
 Critically, however, the information that we temporally process first will carry significant weight relative to the new information.
-As time goes on, memory falters and we do not remember all of the details of the information.
+As time goes on, memory falters and we do not remember all of the details of the information [@kahana_laws_2022].
 Critically, what remains is the affective state the information encouraged but not necessarily all of the details [@kahana_laws_2022; see also @lodge_rationalizing_2013].
@@
 In agreement with the online model that refines the memory-based model, I should expect that these colors have already activated a cognitive process which encourages the affective state and motivations to disengage or engage more with the television before Trump has even entered the stage.
+
+The next chapter explores a common example of political marketing: yard signs.
+The goal of the chapter is to establish whether visual information in politics is considered by voters at all.
+It also allows for me to present evidence suggesting that voters consider the colors red and blue to be information about the partisanship of a political candidate in a situation where they lack more information about them (since it is a fictional candidate for a fictional election).
+The remaining chapters not only consider different contexts in which these colors can convey information about partisanship and the behavioral consequences, but they also consider claims I make in this chapter such as the highly contextual nature of this information as well as the downstream effects that the snap-judgment generated from visual information has on the effects of traditional political information subsequently processed on attitude expression.

### 2023-12-06 chapter_2/src/appendix.qmd
putting it all into one file

@@
 #| tbl-cap: The effect of democratic vote share on color choices for yard sign
-
+list_fitted[["h_5"]] <- list_fitted[["h_5"]][c(1,2)]
 names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
@@
   , escape = FALSE
-  #, output = "latex"
+  , output = "latex"
 )

### 2023-12-06 chapter_2/src/manuscript.qmd
putting it all into one file

@@
-# Does color convey political information?
-<!--
-    - Description: QMD script for empirical chapter 1
-    - Updated: 2023-07-16
-    - Notes:
-        * Code:
-        * Writing:
--->
+# Do political yard signs convey information?
 
@@
 
-Now that I have presented some background and have introduced the snap-judgment model of politically-relevant visual information, this chapter is a first attempt to tackle the question, "Do colors provide political information that shape attitudes?" There are two goals that I am hoping to achieve in this chapter.
-The first is to convince the reader that the colors red and blue convey affiliative information.
-The second is that these connections between colors and political groups can shape political outcomes.
+Do colors actually shape political attitudes among the mass public?
+There are two goals that I am hoping to achieve in this chapter.
+The first is to convince the reader that the colors red and blue convey consistent, affiliative information.
+The second is that these connections between colors and political groups can indeed affect political outcomes.
 
-This chapter applies the snap-judgment model to a simple case: the use of color on yard signs used by campaigns in elections.
-I focus on yard signs as they are a common form of campaign marketing and evidence suggests that they can shape individual behavior [@makse_politics_2019] and electoral outcomes [@green_effects_2016].
-Additionally, I start by examining the colors red and blue.
-While there are other colors that may provide political information -- black and white for Black Lives Matter and Blue Lives Matter movements, the overarching goal of this book is to lay the foundation for a larger research agenda in visual political psychology [@bucy_editors_2021].
-Without such foundations, we would be jumping into the study of complex cases and circumstances without a firm grasp of how things matter on a more fundamental level.
+Many understand -- in a general sense -- that "colors matter" when it comes to attitudes and behaviors.
+Color theorists and scholars of marketing understand color as having important implications for reactions to a product and resulting consumer behavior.
+For example, @kuo_impact_2023 demonstrate that hotel rooms that use more "cool colors" (blues, greens, etc.) evoke positive affect for potential customers and that these positive affective responses are predictive of their eventual choice to book the room.
+Colors mean a varying number of things, however.
 
-Before getting into things, it is worth noting that while there indeed is empirical and experiential evidence suggesting that Republicans use the color red and Democrats use the color blue [@schloss_politics_2014;@williams_whats_2022], there is currently no theoretical framework that explains how these connections happen at the individual level.
-As a side note, one might find it unsatisfying that I do not address *how* these associations between color and the parties came about.
-While the connections between Republicans with the color red and Democrats with the color blue seemed to quicken after the 2000 Presidential election (with news networks consistently using those colors in campaign coverage [@elving_color_2014]), it is not clear if this was a deliberate choice, or whether this was yet another symptom of an increasingly polarized public.
-An undertaking to address the specifics of this part of American political history would likely be a different book project.
+The role of visuals in politics is receiving more attention among interdisciplinary scholars in fields like communication, political science, and the psychological sciences.
+While many of these studies examine fascinating but complicated forms of visual information such as symbology [@williams_whats_2022] and visual framing [@grabe_image_2009], we have yet to integrate these interdisciplinary perspectives with existing models of political information processing -- this will enable us to better understand how these visual forms of information act as cues [see @lilleker_power_2019], and what their potential consequences might be for political behavior among the mass public.
 
-To preview, in this chapter I propose two studies to evaluate the claims I make about yard signs.
-Yard signs are a simple yet effective source of campaign branding for political candidates as they convey information that is often useful for voters' partisanship [@campbell_american_1969].
+In this chapter, I build upon descriptive evidence suggesting that Democratic campaigns use the color blue more than Republican campaigns [@williams_whats_2022] and that Republican voters express a preference for red during election season [@schloss_politics_2014].
+I present a snap-judgment model of politically-relevant visual information processing that outlines a) the cognitive processes that drive these associations and b) notes how those associations drive important political outcomes.
+I draw upon theories of associative memory and spreading activation [see @collins_spreading-activation_1975] to conceptualize the association of the colors red and blue with Republicans and Democrats, thinking of them as as two interconnected nodes.
+I conceptualize these connections as carrying affective information -- an idea informed by perspectives on biological survival reaching back to Darwin [@ralph_neuroscience_2018].
+When these nodes are activated by exposure to these colors in political contexts, other related nodes become active and contain affective information.
+As partisanship evokes strong affective reactions for many members of the public [@iyengar_affect_2012], this activation elicits an affective reaction.
+Considering that most visual information -- including these processes of association -- occur pre-cognitively [@ames_impression_2012;@fazio_attitudes_2007;@sander_cambridge_2013], I argue that the elicited affective response to such information can be "transferred" [see @morris_activation_2003;@taber_illusion_2016] to later post-cognitive processing of more traditional forms of political information such as stated policy positions.
+The implication of this is that these associations can *pre-cognitively* inform reactions to political information and political behavior
+
+To preview, in this chapter I conduct two studies to evaluate the claims I make about yard signs.
+Yard signs are a simple yet effective source of campaign branding for political candidates, as they convey information that is often useful for voters' partisanship [@campbell_american_1969].
 As yard signs are a simple and static form of campaign advertising, they cannot rely heavily on more complicated forms of information.
@@
 With these characteristics, yard signs are an ideal candidate both from a design and substantive standpoint.
-From a design standpoint, as they are static forms of party branding they have fewer moving parts, which helps isolate the effect that color has on shaping attitudes.
+From a design standpoint, as a static form of party branding they have fewer moving parts, which helps isolate the effect that color has on shaping attitudes.
 From a substantive standpoint, while we understand that yard signs matter to campaigns, we have yet to systematically explore more simple design choices such as color.
 
-In [Study 1](#study-1), I find descriptive evidence suggesting that campaigns use the colors red and blue on their yard signs at different rates depending on the success of Republicans and Democrats according to previous election returns.
-It is unclear, however, whether these patterns are based on elite perceptions of how to communicate partisanship to voters or whether campaigns have successfully identified a cognitive process linking the colors red and blue with Republicans and Democrats.
-Accordingly, in [Study 2](#study-2), I conduct an online experiment that examines whether the public notice color and whether their attitudes are shaped by the presence of "Republican red" and "Democratic blue" on the yard signs of a political candidate.
-I find that these associations do exist among the public.
-Specifically, individuals consistently and strongly associate Republicans with the color red and the Democrats with the color Blue.
-As a result, partisan individuals' willingness to vote for a candidate can be dramatically different depending on whether the color used in the yard sign aligns with their partisan identification.
+In [Study 1](#study-1), I conduct an online experiment that examines whether individuals notice color, and whether their attitudes are shaped by the presence of "Republican red" and "Democratic blue" on the yard signs of a political candidate.
+I find that these associations do exist among respondents.
+Specifically, individuals consistently and strongly associate Republicans with the color red and the Democrats with the color blue.
+I present experimental evidence that partisan individuals' willingness to vote for a candidate may be different depending on whether the color used in a yard sign aligns with their partisan identification.
+In [Study 2](#study-1), I want to examine whether there is observational evidence consistent with my theory.
+I find descriptive evidence suggesting that campaigns use the colors red and blue on their yard signs -- in districts -- at different rates depending on the success of Republicans and Democrats in previous elections.
+This paints a picture of the world that is consistent with my theory.
+However, this study does not make clear whether these patterns are based on elite perceptions of how to communicate partisanship to voters, or whether campaigns have successfully identified a cognitive process linking the colors red and blue with Republicans and Democrats.
 
-While these two studies highlight endogenous processes between campaigns and voters, to be clear, I am not arguing that either of these patterns only one way.
-In fact, I believe that there is a necessary feedback loop between the parties and their bases of support.
+While these two studies highlight endogenous processes between campaigns and voters, to be clear, I wish to be clear that I am not arguing that either of these patterns works in one direction.
+Rather, in all likelihood there is a necessary feedback loop between the parties and their bases of support.
 Voters support candidates who signal strong allegiance to the party to increase their chances for electoral success [@utych_voter-centric_2020], and the parties are motivated to distinguish themselves [@lee_insecure_2016;@clifford_how_2020] as a result of their high levels of ideological and affective polarization [@dietrich_using_2021;@enders_issues_2021].
-I leave teasing out directionality for subsequent analyses.
 
-These findings bring much needed evidence in support of the conventional wisdom that the colors red and blue convey political information.
-Perhaps what is most intriguing about my results is that I find that the colors red and blue alone seem to make individuals willing to vote for a candidate.
-The association between the colors red and blue are strong enough that individuals express a willingness to cast a vote for a candidate based on the color of the candidate's yard sign; this occurs without the individual confirming that the candidate matches their policy stances or partisan affiliation.
-These tendencies, even if only based on a hunch among the professionals on the ground, seem to lead to descriptive differences in the use of these colors with respect to strategy.
-The following chapters dig a bit deeper into the idea that colors can shape attitudes, pitting the information individuals get from color against information gleaned from explicit policy stances.
+Still, together, the findings bring much needed evidence in support of the conventional wisdom that the colors red and blue convey political information.
+The implication of the theory and these findings are that partisan attachments are automatically activated through things as seemingly simple and ubiquitous as color.
+These activated partisan attachments then have causal effects for attitude expression and political behavior.
+Given the existing literature demonstrating low-levels of political engagement among the mass public [see @hibbing_stealth_2002], as well as the hyper-polarized nature of contemporary politics [see @iyengar_affect_2012], this chapter's argument and findings reinforce the idea that voters need not consume any substantive political information before expressing a willingness to cast a vote for a candidate.
 
@@
 Existing models of political information processing (abbreviated here as *pip*) primarily focus on complex forms of political information, such as policy positions, communicated verbally or through text.
-As individuals process visual information before other sorts of information, we might expect that they may form a snap-judgment or the initial appraisal of an object with visual information as opposed to these more complex forms of information.
+As individuals process visual information pre-cognitively, we might expect that they may form a snap-judgment about it -- this is in contrast to complex forms of information that often require (orders of magnitude) more cognitive effort.
 
-Color and other simple visual information are processed much quicker and occur more frequently than text-based information that may be communicated, for example, through a news article [@mehta_blue_2009].
-But as color and other visual information are processed differently, we should also consider their use as political information.
-As visual information is affectively encoded [@cimbalo_emotionally_1978], it can affect the affective state and the latter processing of more complex information, such as text.
-The visual information provides a snap-judgment or an impression of the object through faster processing, and activates particular neurological processes that influence subsequent information appraisals [@ames_impression_2012].
-This implies that snap-judgments from visual forms of political information may have downstream effects that shape the way in which we engage with traditionally considered forms of political information.
+Colors and other simple pieces of visual information are processed much more quickly; these actually occur more frequently than text-based information that may be communicated, for example, via a news article [@mehta_blue_2009].
+And, it is because color and other visual information are processed differently that their roles in communicating political information need to be considered.
+As visual information is affectively encoded [@cimbalo_emotionally_1978], it can affect the affective state and the latter processing of more complex information that scholars typically consider (e.g., text).
+That is, the visual information provides a snap-judgment -- an impression of the object through faster processing -- and activates particular neurological processes that influence subsequent information appraisals [@ames_impression_2012].
+In other words, this means that snap-judgments from visual political information may have downstream effects that shape the way in which we engage with traditionally considered forms of political information.
 
-Before expanding upon the role of colors in shaping political attitudes, let me first define an attitude as a concept.
+Before expanding upon the role of colors in shaping political attitudes, let's first define attitudes.
 An attitude represents an accessible, valanced evaluation of associated prior information and experiences.
@@
 This implies that we should be able to measure attitudes, but that such an operationalization requires careful consideration of the context's role in any given measure of an attitude (as they result from memories) [@fazio_attitudes_2007].
-In this chapter, I consider color's effect on shaping attitudes about a political object -- a yard sign.
-As I hold this constant in the chapter, concerns about the variation in what people are thinking about when seeing the color red and blue are less important here, though later chapters grapple with this consideration.
+In this chapter, I consider color's effect when it comes to shaping attitudes about a political object -- a yard sign.
+As I hold certain features constant in my studies, concerns about potential variation in what people are thinking about when seeing the color red and blue are less important for present purposes (though later chapters grapple with this consideration).
 
-In line with existing theories of *pip*, I conceptualize attitudes as associative.
-This means that attitudes may be unstable (though not in a random sense).
+I use a popular conceptualization of attitudes as emerging from accessed associated memories [see @lodge_rationalizing_2013; see also @collins_spreading-activation_1975].
+The implication of such a conceptualization is that attitudes may be unstable (though not in the sense that they are random).
 That is, as attitudes are associative, they manifest slightly differently depending on the associative paths activated [@fazio_attitudes_2007].
 The retrieval of relevant memories to the attitude depends on many factors, such as the recency of the event, the similarity of the context, and the importance or salience of the memory [@kahana_laws_2022].
-This means that the memories retrieved to contribute to an attitude that is quite variable.
+This means that the memories retrieved to contribute to an attitude may be quite variable.
 However, to understand where that variability comes from, we must understand the deeper processes influencing how information is encoded and later retrieved.
@@
 When individuals access a memory, they do not just recall an object, but they may recall visual information, such as the color of an object [@mehta_blue_2009].
-Due to these features, colors can be processed pre-consciously and very quickly [@mehta_blue_2009].
+Due to these features, colors are processed pre-cognitively [@mehta_blue_2009].
 As they are affectively encoded, their associations with particular memories contribute to the evaluative component of the memory.
 For example, individuals associate colors like red with anger and arousal [@valdez_effects_1994], whereas they associate blue with things like happiness and pleasure [@dandrade_colors_1974].
-This means that colors are compelling as contextual information that shapes the subsequent processing and integration of "traditional" forms of political information used to construct attitudes.
-As the preference for a particular color correlates with political attitudes [@schloss_politics_2014], colors may have some causal influence upon political attitudes.
 
-According to the literature in affective neuroscience, visual information is processed in various parts of the brain, such as the visual cortex [@goldstein_sensation_2017].
-These types of processes do not occur in discrete regions of the brain, as some like to think.
+The implication of such a process is that colors are compelling as contextual information that shapes the subsequent processing and integration of "traditional" forms of political information used to construct attitudes.
+As theories of affect transfer suggest, the affective reactions to our pre-cognitive processing of information persist when we transition to cognitive and post-cognitive states [@morris_activation_2003; see @taber_illusion_2016].
+As the preference for a particular color correlates with political attitudes [@schloss_politics_2014], I expect that colors may have a causal influence on post-cognitive expressions of political attitudes.
+
+According to the literature in affective neuroscience, visual information is processed in more than one region of the brain, such as the visual cortex [@goldstein_sensation_2017].
+That is, these types of processes do not occur in discrete regions of the brain, as some like to think.
 As attitudes are associative, components of the brain work as a complex highway connecting different types of information.
 As a result, the processing of visual information will activate other areas of the brain and will make associated paths "hot." One such area is the amygdala.
-Neuroscientists believe that as visual information is quickly and subconsciously processed, the amygdala takes and appraises it based on the paths it activated; this generates a simple affective response to such information [@winkielman_emotion_2011].
-
-A less technical description of the processes occurring here might look something like this: once politically-relevant visual information is detected, the retina passes it to the brain.
-Once there, the brain attempts to classify the visual information by activating networks of neurons associated with the current information.
-With these activated pathways, the brain also attempts to appraise such information based on quick classification.
-For attitude formation, this implies that, as memories are affectively encoded [@kensinger_affective_2022], these memories help areas such as the amygdala to appraise the current information.
+Neuroscientists believe that as visual information is quickly and pre-cognitively processed, the amygdala takes and appraises it based on the paths it activated; this generates a simple affective response to such information [@winkielman_emotion_2011].
 
 These fast affective classifications are valanced rather than the more laborious categorization of specific emotions (e.g., anger, anxiety, fear, happiness).
-What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_emotions_2000], I think of affect as a more extensive system -- one that considers emotion a conscious classification process that occurs after the initial valanced appraisals of an object [@sander_cambridge_2013;@ralph_neuroscience_2018].
-That is, emotion -- the complex classification of appraisals -- is a conscious component of affect.
-By contrast, the pre-conscious process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_emotion_2011;@dror_deconstructing_2017].
+What this means is that rather than conceptualizing the affective component of this process in line with the popular conceptualizations in political science, such as affective intelligence theory [@marcus_emotions_2000], I conceptualize affect as a more extensive system -- one that considers emotion a cognitive classification process that occurs after the initial valanced appraisals of an object [@sander_cambridge_2013;@ralph_neuroscience_2018].
+That is, emotion -- the complex classification of appraisals -- is a cognitive component of affect.
+*By contrast, the pre-cognitive process of affect occurs first with the simple and automatic valanced classification of an object [@winkielman_emotion_2011;@dror_deconstructing_2017].*
 
-The pre-conscious appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_election_2011;@ralph_neuroscience_2018].
+The pre-cognitive appraisals of the visual information one encounters encourages particular behavioral and attitudinal motivations [@valentino_election_2011;@ralph_neuroscience_2018].
 This has evolutionary roots for survival [@ralph_neuroscience_2018;@parker_blink_2003].
@@
 
-What the snap-judgment model predicts is happening in your head is something like the following: as soon as the light bounces off the sign (to produce a particular wavelength) and reaches your eyes, your brain is already trying to make sense of this information.
+What the snap-judgment model predicts is happening in your head would be the following: as soon as the light bounces off the sign (to produce a particular wavelength) and reaches your eyes, your brain is already trying to make sense of this information.
 This is a valuable tool for survival that biology has optimized for millions of years [@parker_blink_2003].
-Rather than slowly processing the visual information and finding yourself in the jaws of a predator, or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and subconsciously [@newell_unified_1990].
+Rather than slowly processing the visual information and finding yourself in the jaws of a predator, or processing it quickly but forming the wrong impression and running away from a friend, the brain processes the information quickly and pre-cognitively [@newell_unified_1990].
 To make sense of such information, it accesses familiar information similar to what it is currently attempting to process, and it does this for the purposes of efficiency [@kahana_laws_2022].
 This means accessing memories that contain valanced information [@kensinger_affective_2022]: should I avoid this, or is it pleasant?
-Once the brain has finished such processing, it can pass its prediction to your conscious memory.
+Once the brain has finished such processing, it can pass its prediction to your cognitive memory.
 Once you form a reflex of avoid or approach, this opens up space for your brain to process the more complex information: to take the patterns of the light as shapes that construct symbols and letters.
@@
 
-From this discussion, I developed the following pre-registered hypotheses: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that colors observed shape perceptions about the person and ideological symbol represented in the branding -- this means that individuals express different levels of preference for receiving more information that is consistent with their preferences ($H_{2}$); that the consistency of information explains more positive perceptions (i.e., simple visual information paired with more complex "traditional" information) ($H_{3}$); positive and consistent information is processed more quickly than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) -- this is inline with their primary objective of reelection [@fenno_congressmen_1973;@mayhew_congress_1974].
+From this discussion, I expect the following: that the average potential voter pays attention to the colors used in campaign branding ($H_{1}$); that colors observed shape perceptions about the person and ideological symbol represented in the branding -- this means that individuals express different levels of preference for receiving more information that is consistent with their preferences ($H_{2}$); that the consistency of information explains more positive perceptions (i.e., simple visual information paired with more complex "traditional" information) ($H_{3}$); positive and consistent information is processed more quickly than negative and inconsistent, negative and consistent, and positive and inconsistent information ($H_{4}$); and finally that campaigns make strategic choices about their branding to attract voters ($H_{5}$) -- this is in line with their primary objective of reelection [@fenno_congressmen_1973;@mayhew_congress_1974].
 A summary of these hypotheses is presented in @tbl-hypotheses.
@@
 
-In [Study 1](#study-1) I start with testing $H_5$.
-In some informal conversations that I had with political campaign professionals, it became clear that the descriptive evidence connecting the colors red and blue with Republicans and Democrats is still very much based on experience.
-
-> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
-We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
-The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
-
-It appears that campaigns recognize that these are not simply patterns that journalists [see @elving_color_2014] and researchers [see @williams_whats_2022] have picked up on, bit that they are associations held by voters and campaigns respond accordingly:
-
-> Beyond that, I generally suggest that considering associations with party is generally a good place to start.
-For example, if you're running in a Democratic primary and that's the race that's going to most likely decide who ultimately gets elected, then blues are a good place to start.
-
-In the comments above, we see some qualification in that there are other colors that can be useful beyond red and blue.
-Still, a potential implication is that the value of colors associated with a particular place can be a way for candidates to communicate attachment to a district and its constituents.
-Still, there is a preference for campaigns to use as few colors as possible to save on costs -- simpler is better.
-What particularly stood out to me was when I was told:
-
-> You want voters to be able to look at whatever collateral you have, including lawn signs, and be able to identify that it's your material without ever having to read it.
-If you do one thing long enough, voters tend to start to associate specific color schemes with specific candidates.
-
-So, unsurprisingly, campaigns care about how they market themselves.
-And it seems as though campaigns want to tap into quick and efficient information processing for voters and potential voters.
-However, as also noted during the conversation:
-
-> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
-
-Though it appears that at least one consulting firm of campaign marketing professionals recognize the potential value of using the colors red and blue to cue to the partisanship of a candidate, there is still significant uncertainty about how widespread these patterns are with political campaigns in the United States and whether voters actually do make these associations.
-The first piece of empirical evidence in this chapter examines whether we observe systematic patterns between campaigns in the use of the colors red and blue on their yard signs.
-[Study 2](#study-2) then takes my predictions from the snap-judgment model to examine whether these associations exist among voters and what the consequences are.
-
-To gather evidence generalizing the belief that campaigns strategically use the colors red and blue to tap into possible associations of these colors with partisanship, I began by collecting data from the MIT Election Lab that reports the electoral results of the House of Representative elections from the years 1970-2020.
-The data tell me which candidate got how many votes in each House election across the United States.
-With these data, I calculated the rolling 5-year average of the Democratic party's vote share for each district.
-
-Next, I downloaded around 1,000 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design.
-I used the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.
-
-This approach to measure of the proportion of the Republican red and Democrat blue colors takes a lot of the guess work out of manually coding this.
-For example, I downloaded the GOP logo used on the GOP's official Twitter account during the 2022 midterm election cycle.
-To What `OpenCV` does is it loads the image and converts it to a three-dimensional `numpy` array that contains the GBR (reverse of RGB) values for the pixels in the image.
-I standardize the image to be 224 $\times$ 224 pixels.
-The computer is trained to detect the range of the Republican red and Democrat blue colors.
-Once trained, the computer detects the pixels that do not contain values within the pre-specified range and converts those pixels to be black.
-
-```{python}
-#| label: example detection
-#| echo: false
-
-from sys import path # for path management
-from cv2 import imread, imwrite # for color detection
-    #* user-defined
-#path.append("../")
-from PY.helper import colorDetector
-
-# Define colors to detect
-    #* White
-        #** Not defined. Default for colorDetector()
-    #* Red
-republican_red = [232, 27, 35] # target color
-red_lower = [93, 9, 12] # lower end of spectrum for red
-red_higher = [237, 69, 75] # higher end of spectrum for red
-
-# Load gop image to read
-img = imread("./assets/img/gop_2022.png")
-
-# Detect colors
-percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
-
-transformed= imwrite("../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
-
-masked= imwrite("../data/temp/study_2/gop_2022_detected.png", result) # save masked image
-```
-
-::: {#fig-color-detection-example layout-ncol="2"}
-![Resized original image](../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
-
-![Masked](../data/temp/study_2/gop_2022_detected.png){#fig-masked}
-
-Detecting colors in the GOP logo
-:::
-
-I then extract the non-black pixels in the array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$]
-
-```{python}
-#| output: asis
-# Print calculated percentage of example
-print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
-```
-
-With the data on the proportion of each of the yard signs using the red and blue colors, I merged these data with the MIT Election Lab Data.
-This left me with data from the House elections between 2018 and 2020.
-While the data are limited in the number of elections they reflect, they allow me to hold the district composition constant, as redistricting occurs after the Census every 10 years.
-However, each district and state is different in their laws surrounding elections, and are different in terms of political context.
-I wanted to examine whether there are meaningful differences between districts that are partisan "strongholds" (Democrats or Republicans tend to get elected in a district) relative to districts that are much less so.
-To do this, I included a model with intercepts with no pooling.
-That is, a model that includes an intercept for each state-district unit.
-Though my outcome of interest (proportion of the yard sign that is red or blue) are continuous (it can take any real number, so not an integer), the outcome is bounded between 0 and 1.
-While the traditional approach may be to use ordinary least squares, such a technique often can lead to poor model fit, introduce systematic error, and lead to results that are quite unstable.
-To not bog down readers with a lot of technical jargon, the model that I end up using is called an ordered beta regression which allows me to efficiently and accurately predict outcomes that can be 0 or 1, or any real number between 0 and 1 [@kubinec_ordered_2022].
-For a more technical discussion about why I choose this over other techniques in the beta regression family, please see the [Appendix](#sec-2-a).
-
-Once I fit these models, I used the `marginaleffects` [@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as explained by the 5-year rolling average Democratic candidates' vote share.
-The grand mean here reflects that I am not showing the predicted proportion of the use of these outcomes for each state-district, but rather that I am averaging across all districts to provide a single line in my figure.
-These results are included in @fig-study-2-pred.
-
-```{r}
-#| label: fig-study-2-pred
-#| layout-ncol: 1
-#| fig-cap: More blue on the yard signs in Democratic strongholds
-#| fig-subcap:
-#|   - Proportion of red
-#|   - Proportion of blue
-red <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["red"]]
-  , treatment = "Red"
-  , hypothesis = "H5"
-)
-blue <- predicted_prob_bar(
-  fitted_model = list_fitted[["h_5"]][["blue"]]
-  , treatment = "Blue"
-  , hypothesis = "H5"
-)
-red
-blue
-```
-
-The results demonstrate that districts where Democrats are historically more successful see yard signs with a lower proportion of red on them, while those same districts see more blue on them.
-Again, these empirical results do not claim that campaigns are doing this either because voters are encouraging them to take this strategy, or that they are doing it as a way to proactively get voters to make these associations.
-My informal conversation does seem to indicate that campaigns are responding to associations that exist in the brains of voters already as opposed to undertaking efforts to generate such associations or to strengthen them.
-Though my empirical evidence is consistent with the argument that campaigns systematically vary in their use of color depending on electoral context, it remains descriptive and I cannot directly test "strategy." To tease out which of those questions is the right one requires more sophisticated approaches and data that could allow me to leverage redistricting (to see how these outcomes change due to some unrelated, external shock).
-The data available to me do not allow me to do that at this time.
-While this is a useful way to understand how these associations of the colors red and blue with Republicans and Democrats exist at a macro-level, this project is fundamentally curious about how these associations have come to be formed among the public and what their consequences are for attitude expression and behavior.
-[Study 2](#study-2) is a test of these central questions in the context of elections.
-
-## Study 2
-
-The purpose of [Study 2](#sec-study-2) is to examine whether the color choices on an almost ubiquitous form of campaign branding -- yard signs -- influence people's perceptions of political candidates.
+The purpose of [Study 1](#sec-study-1) is to examine whether the color choices on an almost ubiquitous form of campaign branding -- yard signs -- influence people's perceptions of political candidates.
 Evidence suggests that yard signs *do* matter in shaping political attitudes [@makse_politics_2019], vote intentions [@makse_politics_2019], and even electoral outcomes [@green_effects_2016].
@@
 I then test the claim that the effects on perception are moderated by how consistent the color is with the more complex information displayed on the yard sign.
-Finally, [Study 2](#study-2) closes with an examination of whether positive information that contains consistency is processed more quickly than negative or inconsistent information.
+Finally, [Study 1](#sec-study-1) closes with an examination of whether positive information that contains consistency is processed more quickly than negative or inconsistent information.
 That is, do partisans quickly detect and encode information from a clearly co-partisan political candidate?
@@
 
-I recruited participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where individuals are provided with a demographics and political attitudes questionnaire.
-As I am concerned about priming effects introduced by these questions, while I am simultaneously concerned about bias introduced by post-treatment control [@montgomery_how_2018], I randomly selected half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
-This questionnaire included common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, patriotism, and political knowledge.
+I recruited participants from Prolific.[^color_influence_pre-reg_anon-3] After providing informed consent to participate in the study, Prolific redirects subjects to Pavlovia,[^color_influence_pre-reg_anon-4] where I provided participants with a demographics and political attitudes questionnaire.
+Due to concerns about priming effects introduced by these questions as well as concerns of bias introduced by post-treatment control [@montgomery_how_2018], I randomly selected half of the participants to receive the questionnaire post-treatment and the other half receive it pre-treatment.
+This questionnaire includes common questions about the participant's ascriptive characteristics, and about the participant's political ideology, partisan identification, interest in politics, and political knowledge.
 
-[^color_influence_pre-reg_anon-3]: I paid subjects a rate of \$12.00 per hour. On top of the price per participant, Prolific charged a 30% servicing fee.
+[^color_influence_pre-reg_anon-3]: I pay subjects a rate of \$12.00 per hour. On top of the price per participant, Prolific charges a 30% servicing fee.
 
 [^color_influence_pre-reg_anon-4]: Pavolovia allows for researchers to host and run open source experiments for about \$0.20 per participant (to cover their server costs).
-I used it primarily to integrate the JavaScript components from the jsPsych package [@leeuw_jspsych_2015] for my experimental design.
+I use it primarily to integrate the JavaScript components from the jsPsych package [@leeuw_jspsych_2015] for my experimental design.
 
 I included those questions due to expectations that they may act as confounds for my hypotheses.
-I included some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these correlates with partisan identification [see @campbell_american_1969;@mason_uncivil_2018].
+I included some questions collecting information on participants' ascriptive and descriptive characteristics such as age, education, gender identity, and racial identity, as a number of these correlate with partisan identification [see @campbell_american_1969;@mason_uncivil_2018].
 Though political knowledge does predict the strength of an individual's partisan identification [@lodge_rationalizing_2013], attention paid to politics is likely a more important confounding variable for my application.
 The purpose of color in politics is to act as a heuristic for people (a cognitive shortcut).
-On the one hand, if individuals are aware of the tendency for Republicans to use and be associated with the color red and the degree to which they know factual information about politics is not entirely relevant.
+On the one hand, if individuals are aware of the tendency for Republicans to use and be associated with the color red, and the degree to which they know factual information about politics is not entirely relevant.
 On the other hand, those that pay no attention to politics whatsoever may be less likely to be aware of such associations.
@@
 In the first trial of the experiment, I randomly presented participants with one of three possible yard signs.
-These yard signs are simple, with the text "Riley Ready to Lead" and a solid background color of either "Republican red," "Democratic Blue," or White.^[See [Appendix](#sec-2-a) to view all of the stimuli used in [Study 1](#study-1).] There is an added component to this, as well as in the other two trials.
+These yard signs are simple, with the text "Riley Ready to Lead" and a solid background color of either "Republican red," "Democratic blue," or white.^[See [Appendix](#sec-2-a) to view all of the stimuli used in [Study 1](#study-1).] There is an added component to this, as well as in the other two trials.
 
@@
 population.
-This means that Mouseview.js was a handy tool for my study.
+As a result, Mouseview.js enables me to take advantage of a survey experiment format (and a better sample) while capturing information about how participants explored the yard signs.
 
-When viewing each yard sign in each of the three trials, I placed a blur over a substantial portion of the screen.
-At any given point in time, participants could view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[I include a screenshot providing an example of what the participants were able to see with the blur included in the [Appendix](#sec-2-a).] Participants moved their cursor to explore the yard sign.
-I alloted 5000 ms to perform the exploration before the image disappears; I did this to encourage a consistent and short duration to explore the image.^[In marketing research, some studies give participants about 6000 ms in eye-tracking studies to examine a brand and formulate an intention to purchase a product or not [@wedel_review_2008].
+To ensure that participants have a standardized initial placement of their cursor for each trial, I displayed a blank page before viewing the yard sign that requires participants to click a "Next" button.
+Immediately after clicking "Next," participants were shown the yard sign.
+The goal is to ensure that variation in where participants explore the image is not dependent on a non-standard starting point for their cursor.
+
+When viewing each yard sign in each of the three trials, there is a blur over a substantial portion of the screen.
+At any given point in time, participants can view only 8% of the image without an obstruction, which simulates the observation that we typically foveate on about 8% of our available visual field at any given time [@wedel_review_2008].^[A screenshot providing an example of what the participants were able to see with the blur included in the [Appendix](#sec-2-a).] For the obstruction, I utilized a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
+The gaussian blur allowed participants to see a blurred visual field beyond the cursor.
+This allowed participants to see enough to take purposeful action to explore blurred parts of the image that attract them [@anwyl-irvine_mouseviewjs_2022].
+The use of the gaussian blur required that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_mouseviewjs_2022].
+This required participants to either switch browsers or to not participate in the study if they were using Safari at the time they are recruited by Prolific to participate in the study.
+As this requirement is enforced *before* joining the study, this should not have an effect on the number of excluded participants from my original sample.
+
+Participants move their cursor to explore the yard sign.
+I alloted 5000 ms to perform the exploration before the image disappears; I did this to encourage a consistent and short duration to explore the image and to formulate an impression of the candidate.^[In marketing research, some studies give participants about 6000 ms in eye-tracking studies to examine a brand and formulate an intention to purchase a product or not [@wedel_review_2008].
 With Mouseview.js, a study examining the tool's correlation with optical responses to viewing disgust-and-pleasure evoking images uses 1000 ms; but is intended to be an extended amount of time [@anwyl-irvine_mouseviewjs_2022].]
@@
 After exploring the image in each trial, I asked participants whether they felt that the candidate supposedly owning the yard sign was a Democrat, a Republican, or Neither.
-After completing the three trials, I asked subjects to indicate their preference among the three images (one from each trial).
+After completing the three trials, I asked subjects to indicate their preference among the three signs (one from each trial).
 
-To ensure that participants have a standardized initial placement of their cursor, I displayed a blank page before viewing the yard sign that requires participants to click a "Next" button.
-Immediately after clicking "Next," participants were shown the yard sign.
-The goal is to ensure that variation in where participants explore the image is not dependent on a non-standard starting point for their cursor.
-I additionally utilized a gaussian blur for the overlay of the image, rather than a solid overlay obstructing the participant's view entirely.
-The gaussian blur allowed participants to see a blurred visual field beyond the cursor.
-This allowed participants to see enough to take purposeful action to explore blurred parts of the image that attracted them [@anwyl-irvine_mouseviewjs_2022].
-The use of the gaussian blur required that participants use a web browser other than Safari because of a known issue [@anwyl-irvine_mouseviewjs_2022].
-This required participants to either switch browsers or to not participate in the study if they are using Safari at the time they are recruited by Prolific to participate in the study.
-As this requirement is enforced *before* joining the study, this should not have an effect on the number of excluded participants from my original sample.
-
-There were two more trials that are much like the first trial.
-What was different between the two latter trials and the first is that I varied the amount of color that is on the yard sign.
+What is different between the two latter trials and the first is that I varied the amount of color that is on the yard sign in the second and third trials.
 Examples of all of these yard signs are included in the [Appendix](#sec-2-a).
-For readers interested in the more technical details, the [Appendix](#sec-2-a) accompanying this chapter also includes a table of the data collected in the experiment -- @tbl-study-1-measures; reports full results, posterior predictive checks, and more detailed discussions for all of the models used in the remainder of this section.^[Unless noted otherwise, the reflection of uncertainty in the models are credible intervals at the 90% level.
+For readers interested in the more technical details, the [Appendix](#sec-2-a) accompanying this chapter also includes a table of the data collected in the experiment -- @tbl-study-1-measures; this table reports full results, posterior predictive checks, and more detailed discussions for all of the models used in the remainder of this section.^[Unless noted otherwise, the reflection of uncertainty in the models are credible intervals at the 90% level.
 This should not be equated with the frequentist practice of reporting confidence intervals at the 95% level, as credible intervals at this level are often extremely unstable and, more importantly, are interpreted differently.
@@
 About 40% of the sample identifies as female, and about 70% of the sample identifies as White (while only 10% report being Hispanic and Black).
-The average respondent in the sample reported leaning Democratic.
+The average respondent in the sample reports leaning Democratic.
 
@@
 
-To address this first question, I used a couple of proxy measures for people's attention paid to the yard signs.
+To address this first question, I use a couple of proxy measures for people's attention paid to the yard signs.
 I collected the first measure through recording the movement of the subjects' cursors along the x-and-y-axes.
-The second measure accounted for the amount of time participants' cursors linger over a particular coordinate on their screen.
+The second measure accounts for the amount of time participants' cursors linger over a particular coordinate on their screen.
 Presumably, the more participants explore the yard sign, the more they are finding visual information that they can use to evaluate the candidate.
-While these two measures are simple proxies and are not direct measures of "noticing the yard sign," they allow us to get a sense of the patterns by which people explore the yard signs across treatment conditions.
+While these two measures are simple proxies and are not direct measures of "noticing the yard sign," they allow for one to get a sense of the patterns by which people explore the yard signs across treatment conditions.
 This also bolsters my confidence in the degree to which variation between the treatments among different groups of participants is due to actual differences in how people processed these treatments, and not due to random chance.
@@
 Now, I turn to exploring how features about the subjects themselves may shape the way that individuals interact and respond to this visual information on the yard signs.
-The data on the timing and cursor location is much more noisy than I had originally anticipated.
-However, as the tests of the next few questions demonstrate, the evidence supports the general conclusion of the systematic differences between individuals that saw either a red, white, or blue yard sign (despite holding everything else but the color constant).
+The data on the timing and cursor location is much more noisy than I originally anticipated.
+However, as the tests of the next few questions demonstrate, the evidence supports the general conclusion of systematic differences between individuals that saw either a red, white, or blue yard sign (despite holding everything else but the color constant).
 
@@
 When interpreting the error bars, you will want to look at the difference in the error bars *between* yard sign treatments rather than *within* treatment.
+
 We see that the models indicate substantive and statistically meaningful differences between the yard sign treatments for each outcome.
 That is, the red and blue yard signs did shift people's perceptions of the partisanship of the candidate relative to the white yard sign.
-The credible intervals of these models are reported in the [Appendix](#sec-2-a) in @tbl-hypothesis-2-main which contains the rest of the results from these models.
-
-Digging in a little bit more about what these perceptions were, the predicted probability that subjects perceived the candidate with a red yard sign to be Republican is around 70%, whereas it is only about 30% when viewing a white yard sign.
-When given a red yard sign, the predicted probability the candidate is marked to be an independent is about 30% and less than 5% to be a Democrat.
-However, when viewing a blue yard sign, the predicted probability of a subject perceiving the candidate to be a Democrat is at about 50% whereas it is less at about 10% with a white yard sign.
-When viewing a blue yard sign, the predicted probability of subjects perceiving the candidate to be a Republican is less than 20% and about 45% to be an Independent.
-The full results are reported in @tbl-hypothesis-2-main in the [Appendix](#sec-2-a).
+Specifically, the evidence suggests that the predicted probability of a subject perceiving the candidate with a red yard sign as a Republican is 70%, whereas it is only about 30% when viewing a white yard sign.
+The predicted probability that a participant perceived the candidate with the red yard sign as a Democrat is less than 5%.
+However, when viewing a blue yard sign, the predicted probability that a participant reports the candidate to be a Democrat is at about 50% whereas it is only about 10% if the yard sign is white.
+As we saw with the association between a Democratic candidate and a red yard sign, we see that the predicted probability that a participant perceived a candidate with a blue yard sign as a Republican is less than 20%; it is about 45% as an Independent.
+The full table of results for these models are reported in the [Appendix](#sec-2-a) in @tbl-hypothesis-2-main.
 
@@
 For example, I presented participants with primarily red (and presumably Republican) yard signs, but with some blue or white in them.
-I expected that the trials that use less "consistent" visual information demonstrate more uncertainty among respondents in their reported perceptions of the candidate's positions.
-Specifically, I expected that participants would perceive the yard signs that have both red and blue on them as more moderate, and that the higher proportion of the color red or blue among the two colors will lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic, respectively.
-This is not to say that I expected the results to change significantly, but rather, that the certainty by which I can predict individuals' guesses of the candidate's partisan affiliation will weaken.
+I pre-registered that the trials that use less "consistent" visual information would demonstrate more uncertainty among respondents in their reported perceptions of the candidate's positions.
+Specifically, I expected that participants would perceive the yard signs that have both red and blue on them as more moderate, and that the higher proportion of the color red or blue among the two colors would lead respondents, on average, to be more likely to believe that the candidate leans more Republican or Democratic, respectively.
+This is not to say that I expected the results to change significantly, but rather, that the certainty by which I can predict individuals' guesses of the candidate's partisan affiliation would weaken.
 
@@
 In the appendix, @tbl-h-4-dispersion summarizes the time elapsed outcome variable; this demonstrates over-dispersion.
-Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.] I therefore fit two poisson-gamma models (sometimes referred to as negative binomial regressions).
-I am interested in explaining whether time elapsed can comes not only from the color of the yard sign that the subject is viewing, but also whether this effect is moderated by an individual's partisanship.
+Given this, rather than using a count model assuming a poisson-distributed outcome, I instead assume an outcome distributed as poisson-gamma.] I therefore fit two poisson-gamma models (also referred to as negative binomial regressions).
+I am interested in explaining whether time elapsed can come not only from the color of the yard sign that the subject is viewing, but also whether this effect is moderated by an individual's partisanship.
 I therefore include an interaction term between stimuli and the partisan identification of the respondent.
@@
 @fig-h-4 presents the average predicted elapsed time for participants in different contexts.
-Overall, these results communicate inconclusive support for my expectations on $H_4$ in either regression model.
+Overall, these results communicate inconclusive support for my pre-registered expectations on $H_4$ in either regression model.
 Strong Democrats do not appear to spend more time looking at red yard signs than white ones, but once I account for the variation in the data, I cannot be sure that these differences are not due to random chance.
 I also observe that there are not really any differences (substantive or statistical) between partisans looking at blue versus white yard signs.
+
+## Study 2
+
+In [Study 2](#study-1) I test $H_5$.
+Though my focus is on the cognitive mechanisms for individuals, I want to examine whether practitioners of political marketing also perceive that these associations exist and are influential.
+In some informal conversations that I had with political campaign professionals, it became clear that the descriptive evidence connecting the colors red and blue with Republicans and Democrats is still very much based on instinct rather than empirical evidence.
+
+> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party.
+We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
+The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.
+
+Comments from practitioners like this suggest that campaigns recognize that these are not simply patterns that journalists [see @elving_color_2014] and researchers [see @williams_whats_2022] have picked up on; they are associations held by voters, and campaigns respond accordingly:
+
+> Beyond that, I generally suggest that considering associations with party is generally a good place to start.
+For example, if you're running in a Democratic primary and that's the race that's going to most likely decide who ultimately gets elected, then blues are a good place to start.
+
+In the comments like these, we see some qualification that there are other colors which betray ideological positions.
+Still, a potential implication is that the value of colors associated with a particular place can be a way for candidates to communicate attachment to a district and its constituents.
+That said, there is a preference for campaigns to use as few colors as possible to save on costs -- simpler is better.
+A comment that particularly stood out was:
+
+> You want voters to be able to look at whatever collateral you have, including lawn signs, and be able to identify that it's your material without ever having to read it.
+If you do one thing long enough, voters tend to start to associate specific color schemes with specific candidates.
+
+So, unsurprisingly, a conversation with a practitioner reveals that campaigns care about how they market themselves.
+And it seems as though campaigns want to tap into quick and efficient information processing for voters and potential voters.
+However, as also noted during the conversation:
+
+> A lot of decisions are still made on purely gut feelings as opposed to taking a more multi-disciplinary evidence-based approach.
+
+Comments like this suggest the following: although it appears that at least once consulting firm of campaign marketing professionals recognize the potential value of using the colors red and blue to cue to the partisanship of a candidate, there is still significant uncertainty about how widespread these patterns are with political campaigns in the United States, and whether voters actually do make these associations.
+Do districts in campaign seasons take on a look that is consistent with my theory?
+
+To gather evidence generalizing the belief that campaigns strategically use the colors red and blue to tap into possible associations of these colors with partisanship, I began by collecting data from the MIT Election Lab -- specifically, I gathered data on the electoral results of the House of Representative elections from the years 1970-2020.
+The data report the number of votes for each candidate in any given race.
+With these data, I calculate the rolling 5-year average of the Democratic party's vote share for each district to account for particularly unique electoral events.
+
+Next, I use a combination of HTML and XML tags to identify and then download around 1,000 yard signs from House elections from the years 2016 to 2022; these were taken from the website of the Center for American Politics and Design.
+I used the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.
+
+This approach to measuring the proportion of the Republican red and Democratic blue colors takes a lot of the guess work out of manually coding this.
+For example, I downloaded the GOP logo used on the GOP's official Twitter account during the 2022 midterm election cycle.
+`OpenCV` loads the image and converts it to a three-dimensional `numpy` array that contains the BGR (reverse of RGB) values for the pixels in the image.
+I standardize the image to be 224 $\times$ 224 pixels.
+The computer is trained to detect the "Republican red" and "Democratic blue" colors.
+Once trained, the computer detects the pixels that do not contain values within the pre-specified range and converts those pixels to be black.
+To validate this classification and transformation of the pixels, I include the original image next to the transformed image in @fig-color-detection-example.
+
+```{python}
+#| label: example detection
+#| echo: false
+
+from sys import path # for path management
+from cv2 import imread, imwrite # for color detection
+    #* user-defined
+#path.append("../")
+from PY.helper import colorDetector
+
+# Define colors to detect
+    #* White
+        #** Not defined. Default for colorDetector()
+    #* Red
+republican_red = [232, 27, 35] # target color
+red_lower = [93, 9, 12] # lower end of spectrum for red
+red_higher = [237, 69, 75] # higher end of spectrum for red
+
+# Load gop image to read
+img = imread("./assets/img/gop_2022.png")
+
+# Detect colors
+percent, img_transformed, result = colorDetector(img = img, color_upper = red_higher, color_lower = red_lower)
+
+transformed= imwrite("../data/temp/study_2/gop_2022_transformed.png", img_transformed) # save transformed image
+
+masked= imwrite("../data/temp/study_2/gop_2022_detected.png", result) # save masked image
+```
+
+::: {#fig-color-detection-example layout-ncol="2"}
+![Resized original image](../data/temp/study_2/gop_2022_transformed.png){#fig-resized}
+
+![Masked](../data/temp/study_2/gop_2022_detected.png){#fig-masked}
+
+Detecting colors in the GOP logo
+:::
+
+I then extract the non-black pixels from my array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$] Summary statistics of these calculated proportions for red and blue are included in the [Appendix](#tbl-yard-sign-summary).
+
+```{python}
+#| output: asis
+# Print calculated percentage of example
+print("For the example in @fig-color-detection-example, about {:.2f}".format(percent) + " of the image is red.")
+```
+
+With the data on the proportion of each of the yard signs using the red and blue colors, I then merge these data with the MIT Election Lab Data.
+This leaves me with data from the House elections between 2018 and 2020.
+While the data are limited in the number of elections they reflect, they allow me to hold the district composition constant, as redistricting occurs after the Census every 10 years.
+However, each district and state is different in their laws surrounding elections, and are different in terms of political context.
+I wanted to examine whether there are meaningful differences between districts that are partisan "strongholds" (Democrats or Republicans tend to get elected in a district) relative to districts that are much less so.
+To do this, I specify a model that includes an intercept for each state-district unit.
+Though my outcome of interest (proportion of the yard sign that is red or blue) is continuous (it can take any real number), the outcome is bounded between 0 and 1.
+While the traditional approach may be to use ordinary least squares, such a technique often can result in poor model fit, introduce systematic error, and lead to results that are quite unstable.
+To account for these concerns, I use an ordered beta regression which specifies a link function constraining the conditional distribution of the outcome to be between 0 and 1; I also induce cut-points akin to the fractional logistic regression which allows for the outcome to also appear as strictly equal to 0 or 1 [@kubinec_ordered_2022].
+Interested readers can find a discussion of how the ordered beta regression compares to other estimators in the beta regression family in the [Appendix](#sec-2-a).
+
+Once I fit these models, I used the `marginaleffects` [@arel-bundock_marginaleffects_2022] package to calculate the grand mean of the predicted proportion of the use of the color red or blue for these yard signs, as it correlates with the 5-year rolling average Democratic candidates' vote share.
+These results are included in @fig-study-2-pred.
+
+```{r}
+#| label: fig-study-2-pred
+#| layout-ncol: 1
+#| fig-cap: More blue on the yard signs in Democratic strongholds
+#| fig-subcap:
+#|   - Proportion of red
+#|   - Proportion of blue
+red <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["red"]]
+  , treatment = "Red"
+  , hypothesis = "H5"
+)
+blue <- predicted_prob_bar(
+  fitted_model = list_fitted[["h_5"]][["blue"]]
+  , treatment = "Blue"
+  , hypothesis = "H5"
+)
+red
+blue
+```
+
+The results suggest a correlation between districts where Democrats are historically more electorally successful and a lower proportion of red on their yard signs.
+Inversely, those same districts tend to have yard signs with a higher proportion of blue on them.
+It is important to note that these results are strictly correlational.
+From these results I do not claim that campaigns are doing this either because voters are encouraging them to take this strategy, or that they are doing it as a way to proactively get voters to make these associations.
+Though I do control for unobserved confounds through removing district and year level pooling, there are a number of contextual features that may be unique to a particular district in a particular election year that I do not account for and that threaten claims of causal direction.
+Though the data available to me limit my ability make a causal claim, these data nonetheless provide evidence consistent with the story I have relayed and the one provided to me in my informal conversations with practitioners.
 
@@
 
-Campaigns appear to systematically use the colors red and blue at different rates depending on whether the district is more "up for grabs" or whether it is a partisan stronghold.
-Specifically, my first study suggests that campaigns use more blue on their yard signs in districts that have a higher vote share for Democrats in the five previous years, and use red much less often in these same circumstances.
-This fits with the strategies communicated to me by a campaign marketing firm.
-Another question coming from that conversation and the existing literature was whether voters actually make these associations.
-
 Evidence from my experiment suggests that the use of the colors red and blue convey partisan information, while a third color like white provides very little useful political information.
-The experiment provides evidence that individuals see candidates that use red on a yard sign as more Republican and candidates that use blue as more Democratic.
+The experiment provides systematic evidence that individuals see candidates that use red on a yard sign as more Republican and candidates that use blue as more Democratic.
 Evidence from the experiment also suggests that using less of those partisan colors and using both colors makes it a bit harder for individuals to make partisan associations.
@@
 
-Having established some baseline findings, in the next chapter I examine whether the snap-judgment model holds up in more complex settings.
-Specifically, I next move to consider whether color can shape how we have conversations about politics with others, as well as the degree to which color can be a tool inhibiting political persuasion.
+I closed by looking at whether congressional districts seem to display features that are consistent with my snap-judgment model.
+I found evidence that campaigns appear to systematically use the colors red and blue at different rates depending on whether the district is more "up for grabs" or whether it is a partisan stronghold.
+Specifically, my first study suggests that campaigns use more blue on their yard signs in districts that have a higher vote share for Democrats in the five previous years, and use red much less often in these same circumstances.
+This fits with the strategies communicated to me by a campaign marketing firm.
+
+Having established some baseline findings, in the next chapter I examine whether the snap-judgment model holds up in more complex settings, and with respect to other behavioral outcomes.
+Specifically, I next move to consider whether color can shape how we have conversations about politics with others, and whether color can be something that inhibits political persuasion.
+Most importantly, I can test my claims that the role of color is contextual.

### 2023-12-06 chapter_2/src/R/predicted_prob_bar.R

@@ -24,7 +24,7 @@ predicted_prob_bar <- function( # nolint: object_usage_linter.
   , x_label = "Color of yard sign"
   , y_label = "Pr(Party of candidate)"
   , legend_title = "Party of candidate"
-  , gray = TRUE
+  , gray = FALSE
 ) {
   # Create a list of options for what to do when need to switch to grayscale
   if (gray != TRUE) {

### 2023-12-07 chapter_2/src/manuscript.qmd
doing a bit more drafting

@@
 Do colors actually shape political attitudes among the mass public?
-There are two goals that I am hoping to achieve in this chapter.
+Using the model covered in [Chapter 1](../../chapter_1/src/manuscript.qmd), there are two goals that I am hoping to achieve in this chapter.
 The first is to convince the reader that the colors red and blue convey consistent, affiliative information.
@@
 Many understand -- in a general sense -- that "colors matter" when it comes to attitudes and behaviors.
-Color theorists and scholars of marketing understand color as having important implications for reactions to a product and resulting consumer behavior.
+As discussed in the previous chapter, color theorists and scholars of marketing understand color as having important implications for reactions to a product and resulting consumer behavior.
 For example, @kuo_impact_2023 demonstrate that hotel rooms that use more "cool colors" (blues, greens, etc.) evoke positive affect for potential customers and that these positive affective responses are predictive of their eventual choice to book the room.
@@
 In this chapter, I build upon descriptive evidence suggesting that Democratic campaigns use the color blue more than Republican campaigns [@williams_whats_2022] and that Republican voters express a preference for red during election season [@schloss_politics_2014].
-I present a snap-judgment model of politically-relevant visual information processing that outlines a) the cognitive processes that drive these associations and b) notes how those associations drive important political outcomes.
-I draw upon theories of associative memory and spreading activation [see @collins_spreading-activation_1975] to conceptualize the association of the colors red and blue with Republicans and Democrats, thinking of them as as two interconnected nodes.
+I present a first test of the snap-judgment model of politically-relevant visual information processing that outlines a) the cognitive processes that drive these associations and b) notes how those associations drive important political outcomes.
+As discussed in [Chapter 1](../../chapter_1/src/manuscript.qmd), I draw upon theories of associative memory and spreading activation [see @collins_spreading-activation_1975] to conceptualize the association of the colors red and blue with Republicans and Democrats, thinking of them as as two interconnected nodes.
 I conceptualize these connections as carrying affective information -- an idea informed by perspectives on biological survival reaching back to Darwin [@ralph_neuroscience_2018].

### 2024-01-15 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
sent draft of third empirical chapter pre-reg to commte

@@
   Previous chapters of this project demonstrate that the colors red and blue convey information about the partisan affiliation of another individual, and that this information influences a number of attitudes and behaviors.
-This chapter's goal is to add to these findings in a couple of directions: (1) do these findings generalize to shaping the attitudes and behaviors directed towards groups of people and (2) do these results contribute to the growing literature about the effects of polarization on seemingly non-political attitudes and behaviors?
+This chapter's goal is to add to these findings in a couple of ways: (1) do these findings generalize to shaping the attitudes and behaviors directed towards groups of people and (2) do these results contribute to the growing literature about the effects of polarization on seemingly non-political attitudes and behaviors?
 
@@
 First, I want to expand upon the previous chapters by examining whether snap-judgments are used to evaluate groups of people.
-Second, I want to expand upon the previous chapters by examining whether the previous findings extend to non-political objects.
+Second, I want to expand upon the previous chapters by examining whether the previous findings extend to non-political decisions.
 That is, this chapter seeks to further push my testing of the boundary conditions of the snap-judgment model.
-The third goal is that this chapter might address an important, but still yet to be solved, puzzle with the literature of partisan sorting that I discuss with more detail in the next section.
+The third goal is that this chapter addresses an important, but still yet to be solved, puzzle with the literature of partisan sorting that I discuss with more detail in the next section.
 
 To achieve these three goals, the chapter builds upon a growing set of work suggesting that the politicultural differences between Democrats and Republicans are shaping seemingly non-political attitudes and behaviors such as one's choice in which neighborhood to live in.
-I argue in this chapter that the prevalence of red and blue cars in the driveways of houses in a neighborhood shift people's perceptions of the partisan composition of the neighborhood, and as a result, will make people less willing to move to that neighborhood when they perceive they'd be in the political minority of that neighborhood.
+I argue in this chapter that the prevalence of red and blue vehicles in the driveways of houses in a neighborhood shift people's perceptions of the partisan composition of the neighborhood, and as a result, will make people less willing to move to that neighborhood when they perceive they'd be in the political minority of that neighborhood.
 While these snap-judgments influence attitude expression toward reported willingness to move to a neighborhood, subsequent information such as job opportunities, performance of schools, average wages to cost of living ratio, and other information limits the efficacy of these initial judgments.
@@
 Others have replicated and built upon this work by suggesting that while there are many different types of lifestyles that Republicans and Democrats can take on, there is increasingly clear distinction between Republicans and Democrat archetypes [@rogers_politicultural_2022].
-These politicultural distinctions are clear enough that some scholars trained a computer to make accurate inferences (upwards of 80%) of the partisan composition of a neighborhood by using only Google images of the cars parked there [@gebru_using_2017].
+These politicultural distinctions are clear enough that some scholars trained a computer to make accurate inferences (upwards of 80%) of the partisan composition of a neighborhood by using only Google images of the vehicles parked there [@gebru_using_2017].
 
@@
 @gimpel_seeking_2015 demonstrates that describing a neighborhood with explicit and implicit information (e.g., racial composition) about the partisan composition influences whether one expresses a desire or not to move and live there.
-Further work corroborates this finding by providing evidence from a number of studies which demonstrate that not only do people associate particular characteristics of a neighborhood such as the prevalence of churches with Republicans and hybrid cars with Democrats, but also that these features attract co-partisans and repulse out-partisans [@motyl_how_2020].
+Further work corroborates this finding by providing evidence from a number of studies which demonstrate that not only do people associate particular characteristics of a neighborhood such as the prevalence of churches with Republicans and hybrid vehicles with Democrats, but also that these features attract co-partisans and repulse out-partisans [@motyl_how_2020].
 
@@
 As discussed thus far in the chapter, non-political objects are often associated with particular partisan leanings.
-For example, the modal car in a neighborhood conveys the partisan composition of the whole neighborhood [@hetherington_prius_2018;@gebru_using_2017].
+For example, the modal vehicle in a neighborhood conveys the partisan composition of the whole neighborhood [@hetherington_prius_2018;@gebru_using_2017].
 In the same spirit as the rest of this book, we do not need to necessarily distinguish between complex forms of information such as whether someone drives a hybrid sedan and a Ford pickup truck.
-Information giving insight into one's partisanship may even be as subtle as their color choice in car.
-For a reader who thinks "hypothesizing about car color choice and partisanship is a reach," I agree.
+Information giving insight into one's partisanship may even be as subtle as their color choice in vehicle.
+For a reader who thinks "hypothesizing about vehicle color choice and partisanship is a reach," I agree.
 As stated at the outset of the chapter, the goal of the chapter is to extend past applications of the snap-judgment model to explicitly partisan objects such as yard signs as we did in [Chapter 2](../../../chapter_2/src/manuscript.qmd) and to really challenge the model by looking at non-political objects that we may not readily associate with partisanship.
@@
 As the other chapters demonstrate, one useful and efficient heuristic to convey partisanship is the use of color.
-If we are concerned about the partisanship of our neighbors, we may rely on information such as the color of our potential neighbors' cars (or other pieces of their property for that matter) to infer their partisanship.
+If we are concerned about the partisanship of our neighbors, we may rely on information such as the color of our potential neighbors' vehicles (or other pieces of their property for that matter) to infer their partisanship.
 
-To most of us, we likely do not trust the color of a car as a basis to infer partisanship as other forms of information such as whether a potential neighbor is displaying a political yard sign.
+To most of us, we likely do not trust the color of a vehicle as a basis to infer partisanship as other forms of information such as whether a potential neighbor is displaying a political yard sign.
 However, political yard signs usually only show up every couple of years during the election season and are displayed by those who tend to be highly politically active -- so, they are not universally displayed [@makse_politics_2019].
 Additionally, other decisions such as the color of the house are determined by Homeowners Associations (HOAs).
-The choices of car colors are less constrained by other external factors.
-So, we may reasonably assume that if we see a neighborhood with a significant number of red cars, we may assume that the local sports team color must be red.
+The choices of vehicle colors are less constrained by other external factors.
+So, we may reasonably assume that if we see a neighborhood with a significant number of red vehicles, we may assume that the local sports team color must be red.
 However, in line with predictions from Affective Intelligence Theory, states of uncertainty and anxiety predict information seeking behavior [see @marcus_anxiety_1993].
 That is, if we are searching for cues toward the partisan composition of the neighborhood, we may then assume that the neighborhood has a large number of Republicans, whether that is accurate or not.
-Once we have used that association between the colors red and blue with partisan affiliation, we will form a snap-judgment of our neighbors based on the color of their cars when absent other information.
+Once we have used that association between the colors red and blue with partisan affiliation, we will form a snap-judgment of our neighbors based on the color of their vehicles when absent other information.
 That impression will then elicit a positive or negative attitude toward the neighbors and neighborhood as well as encourage a congruent behavioral reaction such as wanting to avoid the neighborhood or an affinity toward it.
@@
 
-There are many characteristics of a neighborhood besides car color that can better convey information about the partisanship of a neighborhood such as whether it is mixed use, in an urban or rural setting, whether there are Black Lives Matter flags, and whether the cars tend to be pickup trucks or sedans.
+There are many characteristics of a neighborhood besides vehicle color that can better convey information about the partisanship of a neighborhood such as whether it is mixed use, in an urban or rural setting, whether there are Black Lives Matter flags, and whether the vehicles tend to be pickup trucks or sedans.
 However, the role of color is to act as a form of pre-conscious impression formation.
@@
 
-{{< include ../../../assets/_theory.qmd >}}
-
 # Experimental test
 
-Applying the snap-judgment model to an individual's choice to move to a neighborhood yields the following hypotheses: when primed to think about politics, participants will perceive the neighborhood to be more Republican when the favorite car color is red and to be more Democratic when the favorite car color is blue, relative to those that are not primed to think about politics ($H_1$); with all else equal, Republicans that see that the modal color of car is red are more likely to report wanting to move to the neighborhood than if the modal car color were blue ($H_2$); with all else equal, Democrats that see the modal color of blue are more likely to report wanting to move to the neighborhood than if the modal car color were red ($H_3$); once we include more information about a neighborhood's partisan composition, then the strength of their desire to live in a neighborhood will increase if congruent with their partisan affiliation ($H_4$) and will weaken if incongruent with their partisan affiliation ($H_5$).
+Applying the snap-judgment model to an individual's choice to move to a neighborhood yields the following hypotheses: when primed to think about politics, participants will perceive the neighborhood to be more Republican when the favorite vehicle color is red and to be more Democratic when the favorite vehicle color is blue, relative to those that are not primed to think about politics ($H_1$); with all else equal, Republicans that see that the modal color of vehicle is red are more likely to report wanting to move to the neighborhood than if the modal vehicle color were blue ($H_2$); with all else equal, Democrats that see the modal color of blue are more likely to report wanting to move to the neighborhood than if the modal vehicle color were red ($H_3$); once we include more information about a neighborhood's partisan composition, then the strength of their desire to live in a neighborhood will increase if congruent with their partisan affiliation ($H_4$) and will weaken if incongruent with their partisan affiliation ($H_5$).
 
@@
 The treatment involves randomly assigning participants to view one of two versions of a fictional real estate posting.
-The characteristics of the neighborhood are exactly the same between the two conditions except for the "favorite color of car" in the neighborhood.
-In the first condition the "favorite color of car" is reported by displaying a red swatch.
-In the second condition, the "favorite color of car" reported by displaying a blue swatch.
-Participants are presented with a feeling thermometer ranging from 0-100 where participants are asked to "Rate their feelings toward the neighborhood as warm (100) or cold (0)".
-They are also presented with a 5-item Likert scale to indicate, "How much would [they] like to live in this neighborhood?"
+The characteristics of the neighborhood are exactly the same between the two conditions except for the "favorite color of vehicle" in the neighborhood.
+In the first condition the "favorite color of vehicle" is reported by displaying a red swatch.
+In the second condition, the "favorite color of vehicle" reported by displaying a blue swatch.
+To encourage quick decision making underneath the flyer participants are presented with a feeling thermometer ranging from 0-100 where participants are asked to "Rate their feelings toward the neighborhood as warm (100) or cold (0)".
+They are also presented with a 10-item scale to indicate, "How much would [they] like to live in this neighborhood?"
 
-::: {#fig-treatments layout-ncol=2}
+![Blue treatment](./assets/treatments/blue-treatment.png){#fig-blue-treatment}
 
-![Blue treatment](./assets/treatments/blue_mockup.png){#fig-blue-treatment}
+![Red treatment](./assets/treatments/red-treatment.png){#fig-red-treatment}
 
-![Red treatment](./assets/treatments/red_mockup.png){#fig-red-treatment}
-
-Treatments
-:::
-
-Once the participants have responded to these questions, they are then given a "second page" describing the neighborhood.
+Once the participants have responded to these questions, they are then given a "second page" describing the neighborhood which displays as a text box with bullet-points of further information about the neighborhood.
 The information subjects sees depends on which of two conditions they are randomly assigned into.
-In one condition, the information indicates that the neighborhood is "40 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition presents the same information but instead describes the neighborhood as "10 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." With this new information, I ask participants "Rate their feelings toward the neighborhood as warm (100) or cold (0)" and are given a feeling thermometer scale to record their response.
-I also ask them "How much would [they] like to live in this neighborhood?" and are given a 5-item Likert scale to record their response.
+In the explicitly Republican condition, the information indicates that the neighborhood is "40 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition acts as a explicitly Democratic condition by presenting the same information but instead describes the neighborhood as "10 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." With this new information, I ask participants, on the same screen, to "Rate their feelings toward the neighborhood as warm (100) or cold (0)" and are given a feeling thermometer scale to record their response.
+I also ask them "How much would [they] like to live in this neighborhood?" and are given a 10-item scale to record their response.
+After answering these questions, I include a manipulation check asking participants what the favorite activity in the neighborhood was with 5 different options: music, movies, football, basketball, and going for drives.
+Participants who do not answer movies will be excluded from analysis.
 
@@
 I also want to hold constant potential confounders of the treatment's effect on a participant outside of their partisanship such as sex and colorblindness, as well as attention paid to politics.
-Using these models will allow me to test the first hypothesis which predicts that people will report liking the neighborhood more when the favorite car color aligns with their partisan group -- red with Republicans and blue with Democrats, as they project the association between the colors red and blue with their partisan group onto the neighborhood.
+Using these models will allow me to test the first hypothesis which predicts that people will report liking the neighborhood more when the favorite vehicle color aligns with their partisan group -- red with Republicans and blue with Democrats, as they project the association between the colors red and blue with their partisan group onto the neighborhood.
 I then examine the second hypothesis which predicts that updating this information with consistent cultural stereotypes of partisan preferences for neighborhood features strengthens one's affect towards the neighborhood as a result of this new information strengthening my participants' certainty about the partisan composition of the neighborhood.
@@
 
-The outcome of interest is a 5-item Likert scale.
+The outcome of interest is a 10-item Likert scale.
 So the following models will be ordered logistic regressions.
-Much like I did with the previous models, I fit a model that includes an interaction term so that I can test whether the effect of self-reported partisan identity on a preference to live in a particular neighborhood is moderated by the reported favorite car color in that neighborhood and whether these effects are strengthened (in either direction) once we follow-up with more information.
+Much like I did with the previous models, I fit a model that includes an interaction term so that I can test whether the effect of self-reported partisan identity on a preference to live in a particular neighborhood is moderated by the reported favorite vehicle color in that neighborhood and whether these effects are strengthened (in either direction) once we follow-up with more information.
 As the modeling strategy is the same, I include the same confounding variables.
@@
 However, it is important to note that this is a quite conservative estimate of the proportion of insincere responses as this estimate comes from platforms that are notorious for poor convenience samples such as MTURK.
+Given experience previous experience with this platform, I expect that I will need to exclude somewhere between 20 and 40% of subjects due to insincere responses.
 

### 2024-02-19 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
working on rewriting simulations. Will have to rewrite the code for the outcome variable then re-run simulations

@@
 
-To achieve these three goals, the chapter builds upon a growing set of work suggesting that the politicultural differences between Democrats and Republicans are shaping seemingly non-political attitudes and behaviors such as one's choice in which neighborhood to live in.
+To achieve these three goals, the chapter builds upon existing work demonstrating our capacity to infer the partisanship of others in low information settings by relying on heuristics built from associations experienced previously [@kam_name_2013], as well as growing set of work suggesting that the politicultural differences between Democrats and Republicans are shaping seemingly non-political attitudes and behaviors -- such as one's choice in which neighborhood to live in.
 I argue in this chapter that the prevalence of red and blue vehicles in the driveways of houses in a neighborhood shift people's perceptions of the partisan composition of the neighborhood, and as a result, will make people less willing to move to that neighborhood when they perceive they'd be in the political minority of that neighborhood.
@@
 As a result of this tendency to speak out as a political minority in front of a group of people, individuals have fewer out-partisans in their group of folks they regularly discuss politics with [@butters_polarized_2022].
+
+We do not have to actively keep score to inform this behavior.
+Theories of recognition heuristics suggest that even in low-information settings, like not necessarily knowing the partisan identification of another person, we are capable of inferring the partisanship of another by using associations we have previously made between partisans and their various attributes [@kam_name_2013].
+In other words, we do not necessarily need to know that our Uncle Bob identifies as a Democrat, but we can use information about Bob and about the modal Democrat to infer their partisanship.
 
@@
 To most of us, we likely do not trust the color of a vehicle as a basis to infer partisanship as other forms of information such as whether a potential neighbor is displaying a political yard sign.
-However, political yard signs usually only show up every couple of years during the election season and are displayed by those who tend to be highly politically active -- so, they are not universally displayed [@makse_politics_2019].
+However, political yard signs usually only show up every couple of years during the election season and are displayed by those who tend to be highly politically active -- so, they are not universally displayed [see @kam_name_2013; see also @makse_politics_2019].
 Additionally, other decisions such as the color of the house are determined by Homeowners Associations (HOAs).
@@
 That is, if we are searching for cues toward the partisan composition of the neighborhood, we may then assume that the neighborhood has a large number of Republicans, whether that is accurate or not.
+
 Once we have used that association between the colors red and blue with partisan affiliation, we will form a snap-judgment of our neighbors based on the color of their vehicles when absent other information.
@@
 To test these hypotheses, I conduct an experiment involving a fictional real estate posting.
+I randomly assign half of the participants view the treatment before responding to demographic and political attitude questionnaires containing control variables while the other half view it after.
+The experiment is a 2x3 factorial design.
 The treatment involves randomly assigning participants to view one of two versions of a fictional real estate posting.
 The characteristics of the neighborhood are exactly the same between the two conditions except for the "favorite color of vehicle" in the neighborhood.
-In the first condition the "favorite color of vehicle" is reported by displaying a red swatch.
-In the second condition, the "favorite color of vehicle" reported by displaying a blue swatch.
+In the first type of posting the "favorite color of vehicle" is reported by displaying a red swatch.
+In the second type of posting, the "favorite color of vehicle" reported by displaying a blue swatch.
 To encourage quick decision making underneath the flyer participants are presented with a feeling thermometer ranging from 0-100 where participants are asked to "Rate their feelings toward the neighborhood as warm (100) or cold (0)".
@@
 Once the participants have responded to these questions, they are then given a "second page" describing the neighborhood which displays as a text box with bullet-points of further information about the neighborhood.
-The information subjects sees depends on which of two conditions they are randomly assigned into.
-In the explicitly Republican condition, the information indicates that the neighborhood is "40 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition acts as a explicitly Democratic condition by presenting the same information but instead describes the neighborhood as "10 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." With this new information, I ask participants, on the same screen, to "Rate their feelings toward the neighborhood as warm (100) or cold (0)" and are given a feeling thermometer scale to record their response.
+There are three sets of information about the neighborhood that participants are randomly assigned to see.
+In the explicitly Republican condition, the information indicates that the neighborhood is "20 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition acts as a explicitly Democratic condition by presenting the same information but instead describes the neighborhood as "20 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." In the final condition, participants are just told that the neighborhood is "20 minutes from the nearest metro area".
+
+With this new information, I ask participants, on the same screen, to "Rate their feelings toward the neighborhood as warm (100) or cold (0)" and are given a feeling thermometer scale to record their response.
 I also ask them "How much would [they] like to live in this neighborhood?" and are given a 10-item scale to record their response.
@@
 The first outcome of interest is the reported feeling thermometer that ranges from 0-100.
-I divide the response to this outcome variable by 10 and fit an ordered beta regression [see @kubinec_ordered_2022].
+I divide the response to this outcome variable by 100 and fit an ordered beta regression [see @kubinec_ordered_2022].
 As I am interested in examining how these treatments impact perceptions and resulting preferences based on partisanship, I interact the treatment with the self-reported partisan identity of the participant to examine how a participants' preference for that neighborhood is moderated by the treatment.
@@
   ...
-    RedTreatment = draw_binary( # Simulate treatment assignment with prob 1/3
+    RedTreatment = sample( # Simulate treatment assignment with prob 1/3
+        1:3,
         N,
-        prob = 1/2
+        replace=TRUE
+    ),
+    BlueTreatment = draw_binary( # Simulate treatment assignment with prob 1/3
+      N, 
+      mean = 1/3
     ),
@@
             prob = (
-              E + 1.5 * RedTreatment + 1.5 * PartyId + 2 * RedTreatment * PartyId + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+              E + 1.5 * RedTreatment - 1.5 * BlueTreatment + 1.5 * PartyId + 2 * RedTreatment * PartyId - 2 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
             )
@@
             mean = (
-              E + 1 * RedTreatment + 1 * PartyId + 2 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+              E + 1 * RedTreatment - 1 * BlueTreatment + 1 * PartyId + 2 * RedTreatment * PartyID - 2 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
             )
@@
         prob = (
-          E + 1 * RedTreatment + 2 * PartyID + 2.5 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+          E + 1 * RedTreatment  - 1 * BlueTreatment + 2 * PartyID + 2.5 * RedTreatment * PartyID - 2.5 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
         )
@@
         mean = (
-          E + 0.5 * RedTreatment + 1.5 * PartyId + 2.5 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+          E + 0.5 * RedTreatment - 0.5 * BlueTreatment + 1.5 * PartyId + 2.5 * RedTreatment * PartyID - 2.5 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
         )
@@
 )
+dgp$BlueTreatment <- NA
+dgp$BlueTreatment[dgp$RedTreatment == 0] <- 0
+dgp$BlueTreatment[dgp$RedTreatment == -1] <- 1
+dgp$RedTreatment[dgp$RedTreatment == -1] <- NA
 ```
@@
   \hat{Move_i} = Cumulative(logit^{-1}(\alpha_1 + \alpha_2 + \alpha_3 + \alpha_4 \\ 
-   + \beta_1 \times Red Treatment + \beta_2 \times Partisanship \\
-   + \beta_3 \times Red treatment \times Partisanship \\ 
-   + \beta_4 \times Age + \beta_5 \times Gender \\
-   + \beta_6 \times White + \beta_7 \times Attention))
+   + \beta_1 \times Red Treatment + \beta_2 \times Blue Treatment + \beta_3 \times Partisanship \\
+   + \beta_4 \times Red treatment \times Partisanship \\ 
+   + \beta_5 \times Blue treatment \times Partisanship \\
+   + \beta_6 \times Age + \beta_7 \times Gender \\
+   + \beta_8 \times White + \beta_9 \times Attention))
 \end{split}
@@
   formula <- brmsformula(
-    move ~ RedTreatment + PartyID + RedTreatment * PartyID + age + gender + white + attention
+    move ~ RedTreatment + BlueTreatment + PartyID + RedTreatment * PartyID + BlueTreatment * PartyID + age + gender + white + attention
   )
@@
     n=c(200, 400, 600, 800)
-    , num_samples = 500
+    , num_samples = 2
     , formula = formula
@@
 #|  - "Red treatment"
+#|  - "Blue treatment"
 #|  - "Party Identification"
 #|  - "Red treatment x Party Identification"
+#|  - "Blue treatment x Party Identification"
 #|  - "Age"
@@
   , "Red treatment"
+  , "Blue treatment"
   , "Partisanship"
   , "Red treatment x Partisanship"
+  , "Blue treatment x Partisanship"
   , "Age"
@@
 plotList[[7]]
+plotList[[8]]
+plotList[[9]]
 ```

### 2024-02-19 chapter_4/src/prr/R/helper.R

@@ -3,91 +3,94 @@
 #' @param seed seed
 #' @return data.table
 #' @export
-one_sample <- function(N = 100, seed = 121022) {
-  base::set.seed(seed)
-  #* define population
-  dgp <- fabricatr::fabricate(
-    N = 1000000 # N in the population
-    , E = stats::rnorm(N) # epsilon term
-    , age = base::round( # define age variable
-      stats::runif(N, 18, 85)
-    )
-    , gender = fabricatr::draw_binary( # define binary gender identity variable
-      N
-      , prob = 0.5
-    )
-    , white = fabricatr::draw_binary( # define white indicator variable
-      N
-      , prob = 0.6
-    )
-    , PartyID = fabricatr::draw_ordered( # define party identity variable as 3-item ordinal
-      x = stats::rnorm(
-        N
-        , mean = 0.4 * age - 0.6 * gender + 0.7 * white + E
-      )
-      , breaks = base::c(
-        -Inf, 20.14, 23.01, Inf
-      )
-    )
-    , attention = fabricatr::draw_likert( # define Attention variable as 5-item ordinal
-      x = stats::rnorm(
-        N
-        , mean = 0.5 * age - 0.3 * gender + 0.1 * white + E
-      )
-      , min = 0
-      , max = 100
-      , bins = 5
-    )
-    , RedTreatment = fabricatr::draw_binary( # Simulate treatment assignment with prob 1/3
-      N
-      , prob = 0.5
-    )
-    , preference = fabricatr::draw_likert( # Define Preference outcome variable as 5-item ordinal
-        x = stats::rnorm(
+one_sample <- function(n = 100, seed = 121022) {
+    base::set.seed(seed)
+    #* define population
+    dgp <- fabricatr::fabricate(
+        N = 1000000 # N in the population
+        , E = stats::rnorm(N) # epsilon term
+        , age = base::round( # define age variable
+          stats::runif(N, 18, 85)
+        )
+        , gender = fabricatr::draw_binary( # define binary gender identity variable
           N
-          , mean = E + 1.5 * RedTreatment + 1.5 * PartyID + 2 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+          , prob = 0.5
         )
-        , min = 0
-        , max = 100
-        , bins = 2
-      )
-    , move = fabricatr::draw_likert( # Define move outcome variable as Likert variable
-      x = stats::rnorm(
-        N
-        , mean = (
[…]

### 2024-02-19 chapter_4/src/prr/feedback-memo.qmd
re-writing based on feedback for final chapter. Will need to re-write code for outcome variables. Then re-run simulations

---
subtitle: Response memo
format:
  fancy-doc-pdf:
    toc: false
    latex-output-dir: ../out/
    biblatex: true
    #filters:
      #- "_extensions/andrewheiss/wordcount/citeproc.lua"
      #- "_extensions/andrewheiss/wordcount/wordcount.lua"
author:
  - name: Damon C. Roberts
    affiliations:
      - name: Univeristy of Colorado Boulder
    email: damon.roberts-1@colorado.edu
bibliography: 
  - "../../../assets/references.bib"
---

Thank you everyone for your comments. To ensure that I am covering all of your feedback before I submit IRB materials and sort out funding for this final chapter, I want to place the changes in a memo so that you don't have to re-read the pre-registered version of the chapter.

### 2024-02-27 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
Updating files for IRB

@@
 Much like I did with the previous models, I fit a model that includes an interaction term so that I can test whether the effect of self-reported partisan identity on a preference to live in a particular neighborhood is moderated by the reported favorite vehicle color in that neighborhood and whether these effects are strengthened (in either direction) once we follow-up with more information.
-As the modeling strategy is the same, I include the same confounding variables.
+Here, I am conducting a triple interaction.
+As the partisanship of the participants is still not randomized, I include the same confounding variables.
 
@@
   # Define model arguments
-  formula <- brmsformula(
-    move ~ RedTreatment + BlueTreatment + PartyID + RedTreatment * PartyID + BlueTreatment * PartyID + age + gender + white + attention
-  )
   compiled <- stan_model(
@@
     ,model_name = "moveModel"
-  )
-  family <- cumulative(link = "logit")
-  priors <- prior(
-    stats::Normal(0,1)
-    ,class = b
   )
@@
     , num_samples = 2
-    , formula = formula
     , compiled = compiled
-    , family = family
-    , priors = priors
     , cores = cores

### 2024-02-27 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
now need to figure out the pre-post simulation.

@@
   # Define model arguments
+  formula <- brmsformula(
+    move ~ RedTreatment + PartyID + RedTreatment * PartyID + age + gender + white + attention
+  )
   compiled <- stan_model(
@@
     ,model_name = "moveModel"
+  )
+  family <- cumulative(link = "logit")
+  priors <- prior(
+    stats::Normal(0,1)
+    ,class = b
   )
@@
     , num_samples = 2
+    , formula = formula
     , compiled = compiled
+    , family = family
+    , priors = priors
     , cores = cores
@@
 #|  - "Red treatment"
-#|  - "Blue treatment"
 #|  - "Party Identification"
 #|  - "Red treatment x Party Identification"
-#|  - "Blue treatment x Party Identification"
 #|  - "Age"
@@
   , "Red treatment"
-  , "Blue treatment"
   , "Partisanship"
   , "Red treatment x Partisanship"
-  , "Blue treatment x Partisanship"
   , "Age"

### 2024-02-27 chapter_4/src/prr/R/helper.R

@@ -42,14 +42,15 @@ one_sample <- function(n = 100, seed = 121022) {
             N
             , prob=1/2
         )
-        , RepTreatment = base_sample(
+        , RepTreatment = base::sample(
             -1:1
             , N
+            , replace=TRUE
         )
         , preference = fabricatr::draw_likert( # Define Preference outcome variable as 5-item ordinal
             x = stats::rnorm(
                 N
-                , mean = E + 1.5 * RedTreatment + -1.5 * BlueTreatment + 1.5 * PartyID + 2 * RedTreatment * PartyID + - 2 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+                , mean = E + 1.5 * RedTreatment + 1.5 * PartyID + 2 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
             )
             , min = 0
             , max = 100
@@ -59,7 +60,7 @@ one_sample <- function(n = 100, seed = 121022) {
             x = stats::rnorm(
                 N
                 , mean = (
-                    E + 1.5 * RedTreatment - 1.5 * BlueTreatment + 1.5 * PartyID + 2 * RedTreatment * PartyID - 2 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+                    E + 1.5 * RedTreatment + 1.5 * PartyID + 2 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
                 )
             )
             , min = 0
@@ -69,7 +70,7 @@ one_sample <- function(n = 100, seed = 121022) {
         , preference_post = fabricatr::draw_likert( # Define Preference (post new information) outcome variable as 3-item ordinal
             x = stats::rnorm(
                 N
-                , mean = E + 1 * RedTreatment - 1 * BlueTreatment + 2 * PartyID + 2.5 * RedTreatment * PartyID - 2.5 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+                , mean = E + 1 * RedTreatment + 1 * RepTreatment + 2 * PartyID + 2.5 * RedTreatment * RepTreatment * PartyID * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
             )
             , min = 0
[…]

### 2024-02-28 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
model is setup. Now run simultations

--- 2024-02-27 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
@@
     ]
-    , rstan[stan_model]
+    , rstan[stan_model, rstan_options]
     , ./R/helper[
@@
   cores <- detectCores()-1
+  rstan_options(auto_write=TRUE)
 } else {
@@
   # Define model arguments
+  formula <- brmsformula(
+    move_diff ~ RedTreatment + RepTreatment + PartyID + RedTreatment * RepTreatment * PartyID + age + gender + white + attention
+  )
   compiled <- stan_model(
-    "./STAN/move_model.stan"
+    "./STAN/move_post.stan"
     ,model_name = "moveModel"
+  )
+  family <- gaussian()
+  priors <- prior(
+    stats::Normal(0,1)
+    ,class = b
   )
@@
     n=c(200, 400, 600, 800)
-    , num_samples = 2
+    , num_samples = 500
+    , formula = formula
     , compiled = compiled
+    , family = family
+    , priors = priors
     , cores = cores
@@
   , "Red treatment"
-  , "Blue treatment"
+  , "Republican treatment"
   , "Partisanship"
-  , "Red treatment x Partisanship"
-  , "Blue treatment x Partisanship"
+  , "Red treatment x Republican treatment x Partisanship"
   , "Age"

### 2024-02-28 chapter_4/src/prr/R/helper.R

@@ -90,6 +90,7 @@ one_sample <- function(n = 100, seed = 121022) {
     )
     #* take sample of population with size n
     sampled <- dgp[base::sample(1:base::nrow(dgp), n), ]
+    sampled["move_diff"] <- sampled["move_post"] - sampled["move"]
     # return it 
     return(sampled)
 }
@@ -148,13 +149,14 @@ discrepancy <- function (
         , "b[5]"
         , "b[6]"
         , "b[7]"
+        , "b[8]"
     )
     # Define a empty data.table
     rejectDF <- stats::setNames(
         data.table::data.table(
             base::matrix(
                 nrow = 0
-                , ncol = 7
+                , ncol = 8
             )
         ),
         parameters

### 2024-02-28 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
finished up the new draft

@@
 To encourage quick decision making underneath the flyer participants are presented with a feeling thermometer ranging from 0-100 where participants are asked to "Rate their feelings toward the neighborhood as warm (100) or cold (0)".
-They are also presented with a 10-item scale to indicate, "How much would [they] like to live in this neighborhood?"
+They are also presented with a 10-item scale to indicate, "How much would [they] like to live in this neighborhood?", and finally, "What do [they] think the political leanings are of the neighborhood is?" with the options being Republican, Democratic, or Neither.
 
@@
 
-The first outcome of interest is the reported feeling thermometer that ranges from 0-100.
-I divide the response to this outcome variable by 100 and fit an ordered beta regression [see @kubinec_ordered_2022].
-As I am interested in examining how these treatments impact perceptions and resulting preferences based on partisanship, I interact the treatment with the self-reported partisan identity of the participant to examine how a participants' preference for that neighborhood is moderated by the treatment.
-As I am unable to randomly assign my participants' self-reported partisan identity, I want to ensure that I isolate the main and conditional effects of self-reported partisan identification from confounders such as age, and education.
-I also want to hold constant potential confounders of the treatment's effect on a participant outside of their partisanship such as sex and colorblindness, as well as attention paid to politics.
-Using these models will allow me to test the first hypothesis which predicts that people will report liking the neighborhood more when the favorite vehicle color aligns with their partisan group -- red with Republicans and blue with Democrats, as they project the association between the colors red and blue with their partisan group onto the neighborhood.
-I then examine the second hypothesis which predicts that updating this information with consistent cultural stereotypes of partisan preferences for neighborhood features strengthens one's affect towards the neighborhood as a result of this new information strengthening my participants' certainty about the partisan composition of the neighborhood.
-These tests do not examine whether it influences one's willingness to move to the neighborhood, only one's preferences toward it.
-In this way, these tests are much like the outcomes examined in the common experimental tests of the observed positive affect toward neighborhoods with a partisan composition aligned with your own identity.
-The next outcome of interest examines the degree to which someone is willing to move to the neighborhood on this same information.
-
-The outcome of interest is a 10-item Likert scale.
-So the following models will be ordered logistic regressions.
-Much like I did with the previous models, I fit a model that includes an interaction term so that I can test whether the effect of self-reported partisan identity on a preference to live in a particular neighborhood is moderated by the reported favorite vehicle color in that neighborhood and whether these effects are strengthened (in either direction) once we follow-up with more information.
-Here, I am conducting a triple interaction.
-As the partisanship of the participants is still not randomized, I include the same confounding variables.
+To examine $H_1$, I will simply use descriptive statistics to examine the marginals of how people perceived the partisanship of the neighborhood after viewing  the flyer.
+To examine $H_2$ and $H_3$, I fit an ordinal logistic regression where the outcome variable is the 10-item Likert of individuals reporting "How much [they'd] like to live here" immediately after viewing the yard sign.
+I will interact the treatment with self-reported partisan identification.
+I will also include the ascriptive and descriptive individual characteristics as control variables as partisan identification cannot be randomly assigned.
+To examine $H_4$ and $H_5$, I take the difference between subjects' initial responses to the question about their desire to live in the neighborhood after they saw the second page and the same question when they initially responded to it after the flyer.
+I then fit a regression with a Gaussian link function (OLS) where I have a triple interaction between the flyer treatment, the second page treatment, and partisan identification.
+Like I did before, I include the common ascriptive and descriptive characteristic questions as control variables.
 
@@
   ...
-    RedTreatment = sample( # Simulate treatment assignment with prob 1/3
-        1:3,
+    RedTreatment = draw_binary( # Simulate treatment assignment with probability of 1/2
+        N,
+        prob=1/2
+    ),
+    RepTreatment = sample(
+      -1:1, # Randomly assign the sample into one of three treatment conditions
       N,
       replace=TRUE
-    ),
-    BlueTreatment = draw_binary( # Simulate treatment assignment with prob 1/3
-      N, 
-      mean = 1/3
     ),
@@
             prob = (
-              E + 1.5 * RedTreatment - 1.5 * BlueTreatment + 1.5 * PartyId + 2 * RedTreatment * PartyId - 2 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+              E + 1.5 * RedTreatment + 1.5 * PartyId + 2 * RedTreatment * PartyId + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
             )
@@
             mean = (
-              E + 1 * RedTreatment - 1 * BlueTreatment + 1 * PartyId + 2 * RedTreatment * PartyID - 2 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+              E + 1 * RedTreatment + 1 * PartyId + 2 * RedTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
             )
@@
         prob = (
-          E + 1 * RedTreatment  - 1 * BlueTreatment + 2 * PartyID + 2.5 * RedTreatment * PartyID - 2.5 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+          E + 1 * RedTreatment  + 1 * RepTreatment + 2 * PartyID + 2.5 * RedTreatment * RepTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
         )
@@
         mean = (
-          E + 0.5 * RedTreatment - 0.5 * BlueTreatment + 1.5 * PartyId + 2.5 * RedTreatment * PartyID - 2.5 * BlueTreatment * PartyID + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
+          E + 0.5 * RedTreatment + 0.5 * RepTreatment + 1.5 * PartyId + 2.5 * RedTreatment * RepTreatment * PartyID  + 0.5 * age + 0.3 * gender + 0.1 * white + 0.1 * attention
         )
@@
 )
-dgp$BlueTreatment <- NA
-dgp$BlueTreatment[dgp$RedTreatment == 0] <- 0
-dgp$BlueTreatment[dgp$RedTreatment == -1] <- 1
-dgp$RedTreatment[dgp$RedTreatment == -1] <- NA
 ```
@@
   \beta_i \sim Normal(0, 1) \\
-  \hat{Move_i} = Cumulative(logit^{-1}(\alpha_1 + \alpha_2 + \alpha_3 + \alpha_4 \\ 
-   + \beta_1 \times Red Treatment + \beta_2 \times Blue Treatment + \beta_3 \times Partisanship \\
-   + \beta_4 \times Red treatment \times Partisanship \\ 
-   + \beta_5 \times Blue treatment \times Partisanship \\
-   + \beta_6 \times Age + \beta_7 \times Gender \\
-   + \beta_8 \times White + \beta_9 \times Attention))
+  \hat{Move_i} = Normal(\alpha_1 + \alpha_2 + \alpha_3 + \alpha_4 \\ 
+   + \beta_1 \times Red Treatment + \beta_2 \times Republican Treatment + \beta_3 \times Partisanship \\
+   + \beta_4 \times Red treatment \times Republican Treatment \times Partisanship \\ 
+   + \beta_5 \times Age + \beta_6 \times Gender \\
+   + \beta_7 \times White + \beta_8 \times Attention)
 \end{split}
@@
 
-These priors suggest that I believe 68% of my beta coefficients on a logged-odds scale, given the data, should be between -1 and 1; with the median of the estimates at 0.
-This is quite a conservative estimate given that the primary $\beta$ coefficients of interest are both at 0.1 on the logged-odds scale.
+These priors suggest that I believe 68% of my beta coefficients, given the data, should be between -1 and 1; with the median of the estimates at 0.
 
@@
 #|  - "Red treatment"
+#|  - "Republican treatment"
 #|  - "Party Identification"
-#|  - "Red treatment x Party Identification"
+#|  - "Red treatment x Republican treatment x Party Identification"
 #|  - "Age"
@@
 plotList[[8]]
-plotList[[9]]
 ```

### 2024-03-06 chapter_1/src/manuscript.qmd

@@
 In this chapter I will present a theory of how political visual objects are used by the public to make decisions.
-As I will argue throughout the chapter, existing models of political information processing set the foundation for the theory I present here.
-However, there requires adjustment to the underlying cognitive mechanisms to account for differences in how the brain processes visual information relative to things like a stated policy position of a political candidate that you read in the news paper or hear while watching a video.
+*That is, politically-relevant visual objects are information for the public.* I consider existing models of political information processing as the foundation for the theory I present here.
+Nevertheless they require adjustment to account for the underlying cognitive mechanisms to account for differences in how the brain processes visual information relative to things like a stated policy position of a political candidate that you read in the news paper or hear while watching a video.
 
@@
 Why is it necessary for me to start with simple cases?
-Visual information, at large, is comparatively understudied in the field.
+Visual information, at large, is comparatively understudied in political science.
 The field largely considers information that are quite common and explicitly political such as stated policy preferences, conversations with our friends about politics, and text with political information from the news or campaigns.
@@
 After introducing some of the key mechanisms outlined in those theories, I will present the theory that is the focus of the book.
-I will refer to this theory as the snap-judgment model of political information processing.
+I will refer to this theory as *the snap-judgment model of political information processing*.
 Once I explain this theory, I will close this chapter with a discussion about how this contrasts with existing theories of political information processing, but I will more importantly discuss how this theory contributes to these existing models.
@@
 There are, of course, many more than these two; particularly in the fields of survey and public opinion research [see @tourangeau_psychology_2000].
-I will focus on the two most commonly used in political science, however, as they synthesize many of these other alternative models and are quite commonly used by political psychologists.
+I will focus on the two most commonly used in political science, however, as they synthesize many of these other alternative models and are quite commonly used by political psychologists due to their focus on mechanisms about how information is encoded and converted into an attitude.
 
@@
 In the "memory" model, @zaller_nature_1992 characterizes the public as Bayesian updaters who, when gathering information about politics, will develop a cognitive schema about how that information relates to existing information.
-That is, citizens are not passively consuming political information from political elites -- which is much of the focus in @zaller_nature_1992.
+That is, citizens are not passively consuming political information from political elites.
 Rather, the public actively integrate this information.
@@
 The public have a number of "predispositions" that have influence on the degree to which and *how* we organize this new information.
-As a result of these features, not all new political information will prove influential in our expressed political attitudes all of the time.
+As a result of these features, *not all new political information will prove influential in our expressed political attitudes all of the time*.
 
@@
 Like Zaller's [-@zaller_nature_1992] "memory" model, the Lodge and Taber's [-@lodge_rationalizing_2013] "online" model is heavily interdisciplinary.
-However, they characterize this "Receive" and "Accept" processes of political information as slightly different with significant implications.
+However, they characterize this "Receive" and "Accept" processes of political information as slightly different mechanistically with significant implications.
 
@@
 However, according to @kunda_case_1990, we often default to the motivation of selectively gathering information that fits with our pre-existing views in an attempt to have more evidence that we can cite to defend our position to those who may wish to challenge them.
-This theory of motivated reasoning has been and is still quite popular among social psychologists who examine how members of social groups might justify their negative views of those in another group while maintaining positive views of those in their own group, despite the presence any contradictory evidence [see @redlawsk_affective_2010].
+This theory of motivated reasoning has been and is still quite popular among social psychologists who examine how members of social groups might justify their negative views of those in another group while maintaining positive views of those in their own group, despite the presence of contradictory evidence [see @redlawsk_affective_2010].
 
@@
 Marketing is not simply producing catchy slogans but is also about how to visually present a brand.
-There is ample evidence suggesting that choices in visual presentation has significant influence on whether or not a consumer will purchase one of your products.
+There is ample evidence suggesting that choices in visual presentation has significant influence on whether or not a consumer will purchase a product.
 For example, evidence suggests that hotels that have colors like red are much less likely to be booked relative to hotel rooms that feature softer colors like blues and beiges [@kuo_impact_2023].
@@
 For example, @cimbalo_emotionally_1978 demonstrates that colors like red and blue contain different emotive associations.
-Specifically that red can evoke negative emotions and blue can contain positive and more soothing emotions.
+Specifically, @cimbalo_emotionally_1978 finds evidence suggesting that red can evoke negative emotions and blue can contain positive and more soothing emotions.
 
@@
 Like any node or memory, color does not have to hold one connection nor do all connections have equal strength under every circumstance.
+That is, while red has a tendency to evoke negative emotions in marketing settings, it does not necessarily mean it is strictly emotively negative under every circumstance due to its potential to be connected to nodes with positive associations.
 Let me illustrate this with a simple example.
@@
 @fig-color-associations presents all the different things that we may associate the color yellow with.
-We might associate it with our favorite sweatshirt; with a food item, a banana; the sunrise; and the Los Angeles Rams.
-You may think of different things when you think of the color yellow.
+We might associate it with our favorite clothing item, a sweatshirt; with a food item, a banana; a time of day, the sunrise; and an American football team, the Los Angeles Rams.
+You may have come up with a different list.
 This is because you may have different connections to the "yellow node" in your head than I do.
@@
 Colors can contain affective associations through connections to the affective associations we have with related objects.
+That is, affect can transfer due to intermediary associations.
 Affect is a strong and central part to human memory [see @fazio_attitudes_2007;@kensinger_affective_2022].
 When we think back to some event in our life, rarely do we only recall what happened but we often recall how it made us feel -- and sometimes we may start to feel happy, angry, or fearful like we did in that recalled event.
-This is because memories are simply refired electrical signals between a particular network of neurons that were originally active during experiencing (encoding) the event [@fazio_attitudes_2007].
+This is because these particular connected nodes to constitute a memory are simply refired electrical signals between a particular network of neurons that were originally active during experiencing (encoding) the event [@fazio_attitudes_2007].
 Going back to the idea of affect transfer, as discussed by Lodge and Taber [-@lodge_rationalizing_2013] who applied in in the context of politics, colors contain affective information not necessarily as a result of any inherent property about the color but because of the affect that comes with the objects that we commonly associate with that color [@cimbalo_emotionally_1978].
@@
 
-In the context of the United States, the colors red and blue are ubiquitous in politics.
+In the context of politics in the United States, the colors red and blue are ubiquitous.
 Since the 2000 Presidential Election, news organizations have consistently converged on the use of the colors red and blue to convey to the public whether the Republican or the Democrat, respectively, won a particular electoral district [@elving_color_2014].
@@
 
-First, we receive visual information as wavelengths that are passed to our retina.
-Our retina passes this information to our optic nerve as an electrical signal to our visual cortex.
+First, we receive visual information as wavelengths that are passed to our retina [@goldstein_sensation_2017].
+Our retina passes this information to our optic nerve as an electrical signal to our visual cortex [@goldstein_sensation_2017].
 Once in our visual cortex, the process of connecting those nodes of visual information in the cortex activates the paths to related nodes across our brain [@goldstein_sensation_2017].
-While this glosses over important physiological components such as the role of ganglion cells and the differences between the V1 and V4 sections of the visual cortex, this still illustrates how the information is received and starts those now familiar cognitive processes.
+While this glosses over important physiological components such as the role of ganglion cells and the differences between the V1 and V4 sections of the visual cortex [see @goldstein_sensation_2017], this still illustrates how the information is received and starts those now familiar cognitive processes.
 
@@
 In other words, the associative network has been activated.
-Once activated, we will continue to spend effort on paths that continually provides more relevant information and will abandon paths that are less relevant and informative.
+Once activated, we will continue to exert effort on paths that continually provides more relevant information and will abandon paths that are less relevant and informative.
 
@@
 
-So, how does this work with political visual information? @fig-theory presents what I call the snap-judgment model of politically-relevant visual information processing.
+So, how does this work with political visual information?
+@fig-theory presents what I call the snap-judgment model of politically-relevant visual information processing.
+Note, in the following chapters I will go over this process again specific to the political context of topic to demonstrate the contextual flexibility of this model.
+Here, I will provide a very general overview of the model.
 
@@
 
-Once one consumes visual information about politics, this cognitive process that I have belabored is activated.
+Once one consumes visual information about politics, this cognitive process of associative networks that I have belabored is activated.
 One will seek to find political meaning from that visual information.
+We do not have to tell our brain to find meaning from this information, it just does it automatically as part of its pre-conscious processing.
 This pre-conscious process that the brain starts will go down these finite forking paths to find which associated node provides information about the current stimulus.

### 2024-03-06 chapter_3/src/cleaning/data-loading.R
adding cleaning scripts for ch2 st2

@@ -1,0 +1,30 @@
+# Loading data file
+
+# Notes
+# *     Description
+# **        Script that loads and stores the data into a DB
+
+# Load libraries
+box::use(
+    haven[read_sav],
+    duckdb[...],
+    DBI[dbConnect,dbExecute]
+)
+
+# Connect to the DB
+con <- dbConnect(duckdb(), dbdir = "./chapter_3/data/clean/study_1.db")
+
+# Load the file
+df <- read_sav(
+    "./chapter_3/data/original/CCES23_CUB_OUTPUT.sav"
+)
+df_common <- read_sav(
+    "./chapter_3/data/original/CCES23_COMMON_OUTPUT.sav"
+)
+
+# Store the data in the DB
+dbWriteTable(con, "OriginalModule", df)
+dbWriteTable(con, "OriginalCommon", df_common)
+
+# Disconnect from the database
+dbDisconnect(con)

### 2024-03-10 chapter_3/src/chapter_3.qmd
working on the models a little bit

--- 2023-08-09 chapter_3/src/prr/dcr_color_and_deliberation_prr.qmd
@@
----
-title: |
-  How does visual information influence social interactions?
-code-repo: |
-  For replication, go to: <https://github.com/DamonCharlesRoberts/book_project/chapter_3>.
-author:
-  - name: Damon C. Roberts
-    email: damon.roberts-1@colorado.edu
-    orcid: 0000-0002-4360-3675
-    title: PhD Candidate
-    affiliations:
-      - id: CU
-        name: University of Colorado Boulder
-        department: Political Science
-        address: 333 UCB
-        city: Boulder
-        region: CO 
-        postal-code: 80309-0333
-abstract: |
-  If colors have associations with partisan groups, do they shape our willingness to converse with others?
-This chapter argues that colors are not only relevant to politics and act as a reliable heuristic for people to determine the partisanship of another person, but it additionally makes the argument that this has downstream consequences for our attitudes and behaviors.
-The existing literature on political deliberation is currently grappling with the capacity of conversations to persuade others about politics.
-There is mixed evidence suggesting that it can get people to change their minds under the right conditions.
-However, these "right" conditions are often challenging to develop organically.
-This chapter presents a theory that I refer to as the snap-judgment model of political visual information processing that explains one potential source of this limitation.
-Here, I present a pre-registered report that elaborates on this literature, how the theory helps with this puzzle, and presents two research designs test my claims.
-I conclude the pre-registered report with a simulation exploring the sensitivity of conclusions I can draw from such a research design and resulting modeling strategies.
+# How does visual information influence social interactions? {#sec-3}
 
-bibliography: ["../../../assets/deliberation-chapter-references.bib"]
-format:
-  hikmah-pdf:
-    # Spit out in drafts directory
-    latex-output-dir: "../../out/prr"
-    # Use biblatex-chicago
-    biblatex-chicago: true
-    biblio-style: authordate
-    biblatexoptions: 
-      - backend=biber
-      - autolang=hyphen
-      - isbn=false
-      - uniquename=false
-    geometry:
-      - top=1in
-      - bottom=1in
-      - left=1in
-      - right=1in
-      - heightrounded
-    linestretch: 2
-    fontsize: 12pt
-date: today
-nocite: |
-  @allaire_quarto_2022
-execute:
-  echo: false
-  warning: false
-  message: false
-  cache: false
-params:
-  replicate: false
----
-{{< pagebreak >}}
+```{r}
+#| echo: false
 
-# Introduction
+# Load the functions
+box::use(
+    datasummary[...]
+)
+
+```
+
+## Introduction
 
@@
 
-# The cognitive architecture of attitudes
+## The cognitive architecture of attitudes
 
@@
 
-# The cognitive architecture and color in politics
+## The cognitive architecture and color in politics
 
@@
 
-# Study 1 {#sec-study-1}
+## Study 1 {#sec-study-1}
 
-## Study design
+### Study design
 
@@
 
-## Modeling strategy
+### Modeling strategy
 
@@
 
-# Study 2
+## Study 2
 
-## Study design
+### Study design
 
@@
 
-# Simulation {#sec-simulation}
-
-The stated models above have theoretical motivations.
-Unfortunately for the social scientist, our theoretical motivations do not necessarily mean that our inferential ones also follow.
-The purpose of these simulations is not to convince myself or the reader that my stated modeling strategy is appropriate and "good" in some objective sense.
-Rather, its purpose is to give me a sense of the sensitivity of my ability to draw correct conclusions despite the reasonable amounts of uncertainty that quantitative work generates.
-
-I intend to fit these models through the Bayesian regression framework.
-There are a number of benefits to Bayesian approaches to regression and hypothesis testing that scholars have debated for centuries.
-I am not going to hash out those debates here.
-However, from the perspective of pre-registering my expectations of a model, a Bayesian approach to regression seems particularly appropriate.
-The primary reason for this is that the Bayesian approach to regression requires that you report your prior beliefs about the explanatory effect of your predictor variables on an outcome.
-You incorporate these prior beliefs into your model as a distribution that indicates what you think is the most likely size of the effect and the probability of other less-likely effect sizes.
-This allows you to reflect uncertainty about the size of the effect but still makes explicit what you believe.
-You multiply your prior distribution with your likelihood distribution constructed with the data.
-This approach enables me to report my beliefs and my associated uncertainty about those effect sizes.
-They do not dictate the model, however.
-The more data you have, the less weight your prior beliefs have -- even ones that indicate you have little uncertainty about your beliefs.
-As the size of the data removes the "subjectivity" that many believe to be a problem introduced in Bayesian approaches to regression, one particularly important part of this pre-registered report is to demonstrate the sensitivity of my ability to draw inferences based on the size of my sample Additionally, some of my stated models are more complex than others.
-Therefore, the amount of information my model needs to be sure that my hypotheses are correct increases.
-
-I first start by using the `fabricatr` package [@blair_fabricatr_2022] to simulate population data for both studies.
-I generate these simulated data from data generating processes that I define.^[I include the particulars of these data generating processes in the supplementary materials.
-I do not include them here because the primary goal of this exercise is to see whether or not I can draw correct inferences about reasonably similar data generating processes rather than on me defining these data generating processes as correct themselves.] I randomly draw from this population dataset at four different sample sizes: 200, 400, 600, and 800.
-For each of these sample sizes, I draw 100 samples.
-I do not perform these simulations for [Study 2](#study-2) as the design is largely the same, as well as the modeling strategies.
-
-```{r}
-#| label: setup
-#setwd("./src/prr")
-# modularly load packages
-box::use(
-  ./R/sample[
-    study_simulator
-  ]
-  , ./R/model[
-    fit_sims
-  ]
-  , ./R/plot[...]
-  , data.table[...]
-  , parallel[...]
-  , brms[
-    make_stancode
-    , brmsformula
-    , set_prior
-    , bernoulli
-    , cumulative
-  ]
-  , rstan[
-    stan_model
-  ]
-)
-# Set up cores
-cores <- detectCores() - 1
-# List sample size
-list_sample_size <- c(200, 400, 600, 800)
-# Number of samples
-int_n_samples <- 1000
-```
-
-```{r}
-#| label: simulate
-if (params$replicate == TRUE) {
-  # sample the data at different sample sizes
-  list_simulated <- mclapply(
-    list_sample_size
-    , function(x) {
-      df_sample <- study_simulator(
-        study = 1
-        , n = x
-        , n_samples = int_n_samples
-        , seed = 121022
-      )
-      # Return df_sample
-      return(df_sample)
-    }
-    , mc.cores = cores
-  )
-  # store in a rdata file
-  save(
-    list_simulated
-    , file = "../../data/temp/prr/simulated_samples.RData"
-  )
-} else {
-  load(
-    file = "../../data/temp/prr/simulated_samples.RData"
-  )
-}
-```
-
-On each of these samples, I fit the stated models using the `rstan` package [@stan_development_team_rstan_2023].
-For all models, I define my prior distribution as a normal distribution with a mean of 0 and a standard deviation of 1.
-While this is not truly my prior beliefs of the effect sizes, I am using the prior distribution as an informed prior that states that I largely believe the effects to be zero, or at least to be very small.
-This acts as a quite conservative test of my models' ability to lead me to the correct inferences.
-Once fitted, I find the minimum and maximum value on the posterior distribution for each of my coefficients and identify whether that posterior distribution overlaps with zero.
-My hypotheses are directional in that I not only believe that the effect of my predictor terms should not be zero, but I also believe that these effects are either positive or negative.
-
-I calculate a true positive rate by first ensuring that the minimum and maximum values of my posterior distribution for each $\hat{\beta_i}$ coefficient do not overlap with zero.
-If I would come to the wrong conclusion about my hypothesis by examining my posterior distribution, I record a value of 0; if it is correct, I code it as a 1.
-I then average over the 100 samples for each sample size.
-This gives me a true positive rate for each sample size for each $\hat{\beta_i}$ coefficient.
-
-```{r}
-#| label: make-stan-code
-if (params$replicate == TRUE) {
-  df_example <- list_simulated[[1]][
-    sample == 1,
-  ]
-  df_example_split_rep <- df_example[
-    party_id == "Strong Republican" | party_id == "Republican" | party_id == "Lean Republican"
-  ]
-  df_example_split_dem <- df_example[
-    party_id == "Strong Democrat" | party_id == "Democrat" | party_id == "Lean Democrat"
-  ]
-  # Model 1: Predict whether they notice
-  formula_study_1_model_1 <- brmsformula(
-    notice ~ prime
-  )
-  prior_study_1_model_1 <- set_prior(
-    "normal(0,1)"
-    , class = "b"
-  )
-  stancode_study_1_model_1 <- make_stancode(
-    formula = formula_study_1_model_1
-    , data = df_example
-    , family = bernoulli(link = "logit")
-    , prior = prior_study_1_model_1
-    , save_model = "./STAN/study_1_model_1.stan"
-  )
-
-  # Model 2: Predict willingness
-    #* Full interaction
-  formula_study_1_model_2 <- brmsformula(
-    willing ~ blue_shirt + prime + party_id + blue_shirt * prime * party_id + gender + education + income + conflict + attention
-  )
-  prior_study_1_model_2 <- set_prior(
-    "normal(0,1)"
-    , class = "b"
-  )
-  stancode_study_1_model_2 <- make_stancode(
-    formula = formula_study_1_model_2
-    , data = df_example
-    , family = cumulative(link = "logit")
-    , prior = prior_study_1_model_2
-    , save_model = "./STAN/study_1_model_2.stan"
-  )
-    #* Split sample
-  formula_study_1_model_2_alt <- brmsformula(
-    willing ~ blue_shirt + prime + blue_shirt * prime + gender + education + income + conflict + attention
-  )
-  prior_study_1_model_2_alt <- set_prior(
-    "normal(0, 1)"
-    , class = "b"
-  )
-  stancode_study_1_model_2_alt <- make_stancode(
-    formula = formula_study_1_model_2_alt
-    , data = df_example_split_rep
-    , data2 = df_example_split_dem
-    , family = cumulative(link = "logit")
-    , prior = prior_study_1_model_2_alt
-    , save_model = "./STAN/study_1_model_2_alt.stan"
-  )
-}
-```
-
-```{r}
-#| label: fit-simulated-models
-if (params$replicate == TRUE) {
-  # Model 1
-    #* Compile the stan model
-  compiled_study_1_model_1 <- stan_model(
-    file = "./STAN/study_1_model_1.stan"
-    , model_name = "study_1_model_1"
-  )
-    #* Define model formula
-  formula_study_1_model_1 <- brmsformula(
-    notice ~ prime
-  )
-    #* Define the family
-  family_study_1_model_1 <- bernoulli(link = "logit")
-    #* Define priors
-  prior_study_1_model_1 <- set_prior(
-    "normal(0,1)"
-    , class = "b"
-  )
-    #* Fit model at different sample sizes
-  list_fitted_samples <- mclapply(
-    list_simulated
-    , function(x) {
-      fit_sims(
-        data_frame = x
-        , compiled_stan_model = compiled_study_1_model_1
-        , formula = formula_study_1_model_1
-        , family = family_study_1_model_1
-        , prior = prior_study_1_model_1
-      )
-    }
-    , mc.cores = cores
-  )
-    #* collapse into a single data.table object
-  names(list_fitted_samples) <- list_sample_size
-  df_fitted_samples_model_1 <- rbindlist(
-    list_fitted_samples
-    , idcol = "sample_size"
-  )[
-    , sample_size := factor(sample_size)
-  ]
-  # Model 2
-    #* Compile the stan model
-  compiled_study_1_model_2 <- stan_model(
-    file = "./STAN/study_1_model_2.stan"
-    , model_name = "study_1_model_2"
-  )
-    #* Define model formula
-  formula_study_1_model_2 <- brmsformula(
-    willing ~ blue_shirt + prime + party_id + blue_shirt * prime * party_id + gender + education + income + conflict + attention
-  )
-    #* Define the family
-  family_study_1_model_2 <- cumulative(link = "logit")
-    #* Define priors
-  prior_study_1_model_2 <- set_prior(
-    "normal(0, 1)"
-    , class = "b"
-  )
-    #* Fit model at different sample sizes
-  list_fitted_samples_model_2 <- mclapply(
-    list_simulated
-    , function(x) {
-      fit_sims(
-        data_frame = x
-        , compiled_stan_model = compiled_study_1_model_2,
-        , parameters = c("b[1]", "b[2]", "b[3]", "b[4]")
-        , formula = formula_study_1_model_2
-        , priors = prior_study_1_model_2
-        , family = family_study_1_model_2
-      )
-    }
-    , mc.cores = cores
-  )
-    #* collapse into a single data.table object
-  names(list_fitted_samples_model_2) <- list_sample_size
-  df_fitted_samples_model_2 <- rbindlist(
-    list_fitted_samples_model_2
-    , idcol = "sample_size"
-  )[
-    , sample_size := factor(sample_size)
-  ]
-    #* alternative model
-      #** compile model
-  compiled_study_1_model_2_alt <- stan_model(
-    file = "./STAN/study_1_model_2_alt.stan"
-    , model_name = "study_1_model_2_alt"
-  )
-      #** formula
-  formula_study_1_model_2_alt <- brmsformula(
-    willing ~ blue_shirt + prime + blue_shirt * prime
-  )
-      #** clean data
-  list_sim_rep_data <- lapply(
-    list_simulated
-    , function(x) {
-      x[
-        party_id == "Strong Republican" | party_id == "Republican" | party_id == "Lean Republican"
-      ]
-    }
-  )
-  list_sim_dem_data <- lapply(
-    list_simulated
-    , function(x) {
-      x[
-        party_id == "Strong Democrat" | party_id == "Democrat" | party_id == "Lean Democrat"
-      ]
-    }
-  )
-      #** fit model
-  list_fitted_samples_model_2_alt <- mclapply(
-    list_simulated
-    , function(x) {
-        fit_sims(
-          data_frame = x
-          , compiled_stan_model = compiled_study_1_model_2_alt
-          , parameters = c("b[1]", "b[2]", "b[3]")
-          , formula = formula_study_1_model_2_alt
-          , priors = prior_study_1_model_2_alt
-          , family = family_study_1_model_2
-        )
-    }
-    , mc.cores = cores
-  )
-  names(list_fitted_samples_model_2_alt) <- list_sample_size
-  df_fitted_samples_model_2_alt <- rbindlist(
-    list_fitted_samples_model_2_alt
-    , idcol= "sample_size"
-  )
-
-  # Save results
-    #* study 1, model 1
-  save(
-    df_fitted_samples_model_1
-    , file = "../../data/temp/prr/fitted_model_1.RData"
-  )
-    #* study 1, model 2
-  save(
-    df_fitted_samples_model_2
-    , file = "../../data/temp/prr/fitted_model_2.RData"
-  )
-    #* study 1, model 2 alternate
-  save(
-    df_fitted_samples_model_2_alt
-    , file = "../../data/temp/prr/fitted_model_2_alt.RData"
-  )
-} else {
-  load(
-    file = "../../data/temp/prr/fitted_model_1.RData"
-  )
-  load(
-    file = "../../data/temp/prr/fitted_model_2.RData"
-  )
-  load(
-    file = "../../data/temp/prr/fitted_model_2_alt.RData"
-  )
-}
-```
-
-The following histograms report the true positive rate for each $\hat{\beta_i}$ coefficient at different sample sizes for [Study 1](#study-1).
-Across models and across the two studies, I see that most models perform pretty well at any of the sample sizes.
-It is important to note that these sample sizes reflect the number of observations included in the models, not the total sample size.
-As many online convenience samples struggle with inattentive respondents, insincere responses, bots, etcetera [see @kennedy_strategies_2021], I am going to be quite conservative and try to recruit at least 800 respondents for these two studies.
-
-```{r}
-#| label: fig-true-positive-study-1-model-1
-#| fig-cap: True positive rate from simulations - Model 1
-#| fig-width: 8
-#| layout-nrow: 1
-plot_study_1_model_1 <- true_positive_plot(data_frame = df_fitted_samples_model_1)
-plot_study_1_model_1[[1]]
-
-```
-
-```{r}
-#| label: fig-true-positive-study-1-model-2
-#| fig-cap: True positive rate from simulations - Model 2
-#| fig-width: 8
-#| layout-nrow: 2
-#| fig-subcap:
-#|   - $\hat{\beta}_1$
-#|   - $\hat{\beta}_2$
-#|   - $\hat{\beta}_3$
-#|   - $\hat{\beta}_4$
-plot_study_1_model_2 <- true_positive_plot(data_frame = df_fitted_samples_model_2)
-plot_study_1_model_2[[1]]
-plot_study_1_model_2[[2]]
-plot_study_1_model_2[[3]]
-plot_study_1_model_2[[4]]
-```
-
-```{r}
-#| label: fig-true-positive-study-1-model-2-alt
-#| fig-cap: True positive rate from simulations - Model 2, Split sample
-#| fig-width: 8
-#| layout-nrow: 2
-#| fig-subcap:
-#|   - $\hat{\beta}_1$
-#|   - $\hat{\beta}_2$
-#|   - $\hat{\beta}_3$
-
-plot_study_1_model_2_alt <- true_positive_plot(data_frame = df_fitted_samples_model_2_alt)
-plot_study_1_model_2_alt[[1]]
-plot_study_1_model_2_alt[[2]]
-plot_study_1_model_2_alt[[3]]
-```
-
-# Discussion
-
-Previous chapters provide (as of right now) preliminary evidence supporting my claim that color matters and convey group-based partisan information to average citizens.
-This chapter pushes the envelope in a few ways.
-First, this chapter seeks to move past the argument that "people notice color, and it is relevant in politics." Specifically, this chapter seeks to examine whether it has the capacity to shape attitudes and behavior by elaborating on the mechanisms by which it does so.
-Second, it examines the limitations or the scope conditions of this claim.
-It argues that this works so long as politics is salient.
-Third, this chapter argues that color does not simply act as an alternative form of political information influencing political attitudes and their resulting behaviors but that it shapes the way we consider more traditionally considered forms of political information, such as stated policy positions.
-Fourth, this chapter explores the way in which that color influences our tendencies to avoid conversations about politics with out-partisans and to be more amenable to conversations with those we already agree with.
-
-This pre-registered report documents my expectations before collecting or seeing any data that I can leverage to explore these claims.
-It also provides documentation of my concrete hypotheses, modeling strategies, and expectations about the sensitivity by which my research design and modeling strategies allow me to draw correct inferences from the data.
-
 {{< pagebreak >}}

### 2024-03-10 chapter_3/src/cleaning/data-loading.R

@@ -27,4 +27,4 @@ dbWriteTable(con, "OriginalModule", df)
 dbWriteTable(con, "OriginalCommon", df_common)
 
 # Disconnect from the database
-dbDisconnect(con)
+dbDisconnect(con, shutdown=TRUE)

### 2024-03-10 chapter_3/src/cleaning/study-1-cleaning.R

@@ -5,21 +5,25 @@
 # **        Python script for the cleaning of the study 1 data.
 
 # Load modules
-import duckdb as db
-import polars as pl
+box::use(
+    DBI[dbConnect, dbExecute],
+    duckdb[duckdb]
+)
 
 # Connect to db
-con = db.connect("./chapter_3/data/clean/study_1.db")
+con <- dbConnect(duckdb(), dbdir="./chapter_3/data/clean/study_1.db")
 
 # Cleaning
-con.execute(
-    '''
+dbExecute(
+    con,
+    "
     CREATE OR REPLACE VIEW
         CleanTemp
     AS
     SELECT
         /* CaseID */
         caseid,
+        teamweight,
         /* 
             PoliticalPrime
                 CUB3D01 - Version 1, 2, 3, 4
@@ -254,11 +258,12 @@ con.execute(
         ) AS Attention,
     FROM
         OriginalModule;
-    '''
+    "
 )
 
-con.execute(
-    '''
+dbExecute(
+    con,
+    "
     CREATE OR REPLACE TABLE
         Clean
     AS
@@ -282,8 +287,8 @@ con.execute(
             ) AS CorrectColor,
         FROM
             CleanTemp AS t;
-    '''
+    "
 )
 
 # Close the connection
-con.close()
+dbDisconnect(con, shutdown=TRUE)

### 2024-03-10 chapter_3/src/models/study-1-models.R

@@ -1,0 +1,28 @@
+# Study 1 Models
+
+# Notes
+# *     Description
+# **        Script that executes Study 1 models
+
+# Load libraries
+box::use(
+    duckdb[...],
+    DBI[dbConnect, dbGetQuery],
+    brms[...]
+)
+
+# Connect to the DB
+con <- dbConnect(duckdb(), dbdir = "./chapter_3/data/clean/study_1.db", read_only=TRUE)
+
+# Load the table
+df <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND PoliticalPrime == 1;")
+
+# Models
+# *     H2
+mod <- brm(
+   ConversationAgree ~ BlueShirt + Dem3 + BlueShirt * Dem3 + White + Education + Attention + DislikeArgue + EnjoyChallenge,
+   data = df,
+   prior = set_prior("normal(0, 1)", class="b"),
+)
+# Disconnect from the database
+dbDisconnect(con, shutdown=TRUE)

### 2024-03-10 chapter_3/src/chapter_3.qmd
trying out the models a bit

@@
 box::use(
-    datasummary[...]
+  DBI[dbConnect, dbGetQuery],
+  modelsummary[datasummary_skim]
 )
 
+# Connect to the db
+con <- dbConnect(
+  duckdb::duckdb(),
+  dbdir = "./chapter_3/data/clean/study_1.db",
+  read_only=TRUE
+)
+
+# Load the data
+df_descriptives <- dbGetQuery(
+  con,
+  "
+  SELECT
+    Age,
+    Gender AS 'Gender (Male, Female, Non-Binary, Other)',
+    Education,
+    White,
+    Attention,
+    Dem3 AS 'PID (Republican, Independent, Democrat)',
+    DislikeArgue AS 'Dislike Arguing',
+    EnjoyChallenge AS 'Enjoy Challenging'
+  FROM 
+    Clean;
+  "
+)
+df_primed <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND PoliticalPrime == 1;")
 ```
@@
 [Study 1](#study-1) seeks to address $H_1$ and $H_2$.
-In [Study 1](#study-1), I recruit participants from ***[YouGov/Qualtrics/Whatever online panels are in vogue that week]***.
+In [Study 1](#study-1), I recruit participants from YouGov in a module of the Congressional Election Study.
 First, I ask participants several questions about their demographic background (i.e., age, gender identity, education, and income).
 I additionally present them with a battery to measure conflict avoidance as potential confounds.
+@tbl-descriptive-demo presents the basic demographics of my participants.
+
+```{r}
+#| label: tbl-descriptive-demo
+#| tbl-cap: Descriptive statistics of sample
+#| echo: false
+datasummary_skim(data=df_descriptives)
+```
 
@@
 
-### Modeling strategy
+### Results
 
 To address $H_1$, the outcome variable of interest is whether or not people notice the color of the shirt (0 or 1,) as explained by whether they received the political prime or not (0 or 1).
-I will fit a logistic regression to examine whether there are differences in the outcome depending on this prime.
+To measure whether participants notice the color of the shirt, I ask them to report what the color of the shirt was.
+I then compare that to the color of the shirt that they actually saw.
+Those who reported the correct color received a value of 1 and those who were incorrect received a value of 1.
+I fit a logistic regression to examine whether there are differences in the outcome depending on this prime.
+
+- Do people notice color when they are in the political prime v not
+- Do people who are conflict avoidant notice the color of shirt or not?
 

### 2024-03-10 chapter_3/src/models/study-1-models.R

@@ -4,6 +4,9 @@
 # *     Description
 # **        Script that executes Study 1 models
 
+# Initialize list for the models
+mod_h1 <- list()
+mod_h2 <- list()
 # Load libraries
 box::use(
     duckdb[...],
@@ -15,14 +18,32 @@ box::use(
 con <- dbConnect(duckdb(), dbdir = "./chapter_3/data/clean/study_1.db", read_only=TRUE)
 
 # Load the table
+df_h1 <- dbGetQuery(con, "SELECT CorrectColor, DislikeArgue, PoliticalPrime FROM Clean;")
 df <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND PoliticalPrime == 1;")
 
 # Models
+# *     H1
+mod_h1["main"] <- brm(
+    CorrectColor ~ PoliticalPrime,
+    data = df_h1,
+    prior = set_prior("normal(0, 1)", class="b"),
+)
+mod_h1["conflict"] <- brm(
+    CorrectColor ~ DislikeArgue,
+    data = df_h1,
+    prior = set_prior("normal(0, 1)", class="b"),
+)
 # *     H2
-mod <- brm(
+mod_h2["main"] <- brm(
    ConversationAgree ~ BlueShirt + Dem3 + BlueShirt * Dem3 + White + Education + Attention + DislikeArgue + EnjoyChallenge,
    data = df,
    prior = set_prior("normal(0, 1)", class="b"),
+)
+
+# Save model results
+save(
+    mod_h1, mod_h2,
+    file="./chapter_3/data/models/study-1-models.RData"
 )
 # Disconnect from the database
 dbDisconnect(con, shutdown=TRUE)

### 2024-03-10 chapter_3/src/chapter_3.qmd
adding a couple more descriptives

@@
 )
+df_h1 <- dbGetQuery(con, "SELECT CorrectColor FROM Clean")
 df_primed <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND PoliticalPrime == 1;")
@@
 Those who reported the correct color received a value of 1 and those who were incorrect received a value of 1.
+@tbl-h1-descriptive presents the descriptive statistics for the sample.
+
+```{r}
+#| label: tbl-h1-descriptive
+#| tbl-cap: Sample performance of noticing color
+#| echo: false
+datasummary_skim(data=df_h1)
+```
+
 I fit a logistic regression to examine whether there are differences in the outcome depending on this prime.

### 2024-03-12 chapter_3/src/chapter_3.qmd
writing a bit more

@@
   DBI[dbConnect, dbGetQuery],
-  modelsummary[datasummary_skim]
+  modelsummary[datasummary_skim],
+  marginaleffects[...],
+  tidybayes[stat_halfeye],
+  ggplot2[...]
 )
@@
 )
-df_h1 <- dbGetQuery(con, "SELECT CorrectColor FROM Clean")
+df_h1_descriptive <- dbGetQuery(con, "SELECT CorrectColor FROM Clean")
 df_primed <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND PoliticalPrime == 1;")
+df_dvs <- dbGetQuery(con, "SELECT ConversationAgree, ViewsAgree, InitiateAgree FROM Clean;")
+
+# Load the models
+load("./chapter_3/data/models/study-1-models.RData")
 ```
@@
 
-After getting some background information on my participants, I randomly split the sample into two conditions.
+After collecting some background information on my participants, I randomly split the sample into two conditions.
 The first condition is a "political prime" condition, and the second is a "no political prime" condition.
@@
 
+```{r}
+#| label: tbl-dvs
+#| tbl-cap: Sample responses to outcome variables
+#| echo: false
+
+datasummary_skim(data=df_dvs)
+```
+
+@tbl-dvs presents the descriptive statistics of how participants responded to measures of the propensity for them to engage in a conversation with their hypothetical discussion partner once viewing their avatar.
+Overall, we see that the average participant is a bit ambivalent on all the measures.
+The average participant is somewhat willing to agree to have a conversation with their hypothetical discussion partner after viewing the avatar, neither agree nor disagree with the statement that they will agree with the view points of their hypothetical discussion partner, and neither agree nor disagree with the statement that they would initiate a conversation with their hypothetical discussion partner.
+
 To address $H_1$, the outcome variable of interest is whether or not people notice the color of the shirt (0 or 1,) as explained by whether they received the political prime or not (0 or 1).
@@
 Those who reported the correct color received a value of 1 and those who were incorrect received a value of 1.
-@tbl-h1-descriptive presents the descriptive statistics for the sample.
+@tbl-h1-descriptive presents the descriptive statistics for the sample on how they performed with this question.
 
@@
 I fit a logistic regression to examine whether there are differences in the outcome depending on this prime.
+I fit this model with with a Gaussian prior centered around 0 with a standard deviation of 1.
+In other words, my prior suggests that the beta coefficient with the highest relative probability of occurring and that, if it is not 0, it should most likely be between -1 and 1.
+The results of this model are presented in @fig-h1-main.
 
-- Do people notice color when they are in the political prime v not
-- Do people who are conflict avoidant notice the color of shirt or not?
+```{r}
+#| label: fig-h1-main
+#| fig-cap: Predicted probability of identifying the correct color
+#| fig-subcap:
+#|   - Political prime
+#|   - I dislike arguing about politics
+#|   - I enjoy challenging the opinions of others
+#| echo: false
+
+plot_predictions(
+  mod_h1_main,
+  condition="PoliticalPrime"
+) +
+theme_minimal()+
+scale_x_discrete(
+  breaks=c("0", "1"),
+  labels=c("Not Primed", "Primed")
+) +
+labs(
+  y = "Pr(Correct) = 1"
+)
+
+plot_predictions(
+   mod_h1_conflict,
+  condition="DislikeArgue"
+) +
+theme_minimal()+
+scale_x_continuous(
+  breaks=c(-2, 0, 2),
+  labels=c("Strongly Disagree", "Neither agree nor disagree", "Strongly agree")
+) +
+labs(
+  y = "Pr(Correct) = 1"
+)
+
+plot_predictions(
+   mod_h1_conflict_b,
+  condition="EnjoyChallenge"
+) +
+theme_minimal()+
+scale_x_continuous(
+  breaks=c(-2, 0, 2),
+  labels=c("Strongly Disagree", "Neither agree nor disagree", "Strongly agree")
+) +
+labs(
+  y = "Pr(Correct) = 1"
+)
+```
+
+This model suggests that those who received the political prime were slightly less likely to correctly identify the color of shirt on the avatar.
+The difference, however, is quite small substantively.
+Given that 90% of the sample correctly identified the color of shirt on the avatar, there may just be too little variation.
+
+A key insight from the literature on deliberation is that individuals who are conflict avoidant are likely to avoid engaging in a conversation with those they may disagree with and will use visual characteristics as heuristics to make inferences about how likely disagreement will occur [@carlson_what_2022].
+In the political questionnaire, I asked participants whether they "Dislike arguing about politics" ^[A value of -2 corresponds to a response of Strongly disagree, and a value of 2 corresponds to a response of Strongly agree.] and whether they "enjoy challenging the opinion of others" ^[A value of -2 corresponds to a response of Strongly disagree, and a value of 2 corresponds to a response of Strongly agree.].
+Though not a pre-registered hypothesis, the snap-judgment model agrees with the literature in that people are likely to feel more anxious when faced with the possibility of disagreement and will engage in information-seeking behavior to make a decision about what to do next.
+Like the literature on deliberation, we'd expect that those who are more conflict avoidant will be more likely to correctly identify the color as they are more likely to seek such information to help infer the partisanship of a potential discussion partner.
+
+To test this, I fit two logistic regression models regressing the participants' ability to correctly identify the color of shirt on these two measures that proxy conflict avoidance.
+I use the same priors as before.
+The results of these models are included in @fig-h1-main.
+
+The first model suggests that those who dislike arguing about politics are relatively more likely to correctly identify the color of shirt than those who do enjoy arguing about politics.
+The effects are quite small, however.
+Turning to the next model, we see that those who enjoy challenging others' views are relatively less likely to correctly identify the avatar's shirt color than those who find much less enjoyment out of it.
+These effects are also quite small.
 
@@
 This effect, however, is likely moderated by a couple of things.
-First, if $H_1$ holds, the polarity in outcome responses will be partly explained by whether politics is at the top of the mind.
-Second, I expect that the strength of the relationship of the shirt color and the priming will depend on the party identification of the study participant.
-More specifically, if they are Republican, I would expect that those with the political prime who see a red shirt will be much more favorable of conversing with the fictional discussion partner than those without the political prime and those who saw a fictional discussion partner with a blue shirt.
+If they are Republican, I would expect that those with the political prime who see a red shirt will be much more favorable of conversing with the fictional discussion partner than those without the political prime and those who saw a fictional discussion partner with a blue shirt.
 I expect the opposite for self-identifying Democrats -- Democrats who receive the political prime will report being more willing to have a conversation with the discussion partner when the partner is wearing a blue shirt relative to Democrats who did not receive a prime *and* Democrats who saw a discussion partner with a red shirt.
@@
 
-In the [Simulation section](#simulation) below, I provide further details discussing some practical considerations I must weigh in my decisions.
-In particular, both model choices to examine $H_2$ are rather complicated models.
-As my models will rely on the Bayesian implementation of regression, the inferences I can draw are dependent on the data from the sample, much more so as it does not rely on assumptions about long-run tendencies.
-Therefore, I want to examine my models' ability to converge on the correct answer given various sample sizes.
-In that section, I provide more details about the model, sample sizes, and prior distribution specifications.
+```{r}
+#| label: fig-h2
+#| fig-cap: The marginal effect of agreeing to have a conversation with a discussion partner
+#| fig-subcap:
+#|   - Democrats
+#|   - Republicans
+mfx_dem <- slopes(mod_h2_dem,
+    variables = "BlueShirt",
+    newdata = datagrid(PoliticalPrime = 0:1)) |>
+    posterior_draws()
+mfx_rep <- slopes(mod_h2_rep,
+    variables = "BlueShirt",
+    newdata = datagrid(PoliticalPrime = 0:1)) |>
+    posterior_draws()
+
+ggplot(mfx_dem, aes(x = draw, fill = factor(PoliticalPrime))) +
+    stat_halfeye(slab_alpha = .5) +
+    labs(x = "Marginal Effect of a blue shirt on having a conversation",
+         y = "Posterior density",
+         fill = "PoliticalPrime") +
+    scale_fill_manual(
+      "Political Prime", values=c("#404040", "#00AEF3"), labels=c("Not primed", "Primed")
+    ) +
+    theme_minimal()
+
+ggplot(mfx_rep, aes(x = draw, fill = factor(PoliticalPrime))) +
+    stat_halfeye(slab_alpha = .5) +
+    labs(x = "Marginal Effect of a blue shirt on having a conversation",
+         y = "Posterior density") +
+    scale_fill_manual(
+      "Political Prime", values=c("#404040", "#ff0803"), labels=c("Not primed", "Primed")
+    ) +
+    theme_minimal()
+```
+
+The results suggest that the political prime did not have a substantive effect on shifting Democratic or Republican identifying participants.
+In the model with the Democratic participants, we see that those who received the political prime were slightly more likely to be willing to have a conversation with their hypothetical discussion partner than those without the political prime.
+When examining the results of the model with Republican participants, we see that those who received the political prime were more willing to have a conversation with a discussion partner wearing a Red shirt relative to those who did not receive the political prime.
+Conversely, Republican participants were less likely to have a conversation with a hypothetical discussion partner who was wearing a blue shirt when primed relative to those who were not primed.
+
+Next, I examine whether these small effects appear for other measures of participants' perceptions of a conversation partner.
+In addition to asking participants whether they would be willing to have a conversation with their hypothetical discussion partner, I also asked them whether they "think that [they] would agree about most things with this person" and whether they "can see [themselves] initiating the conversation with this person." I fit the same models but instead regress these outcomes on my predictors.
+@fig-h2-agree presents the posterior draws of the marginal effect that the treatment has on perceptions of agreement conditional on whether the participant received a political prime.
+@fig-h2-initiate also presents the posterior draws of the marginal effect but on whether participants would initiate a conversation with their discussion partner based upon the treatment when conditioned on whether they received the political prime or not.
+
+```{r}
+#| label: fig-h2-agree
+#| fig-cap: The marginal effect of belief of agreeing with a discussion partner
+#| fig-subcap:
+#|   - Democrats
+#|   - Republicans
+mfx_dem <- slopes(mod_h2_agree_dem,
+    variables = "BlueShirt",
+    newdata = datagrid(PoliticalPrime = 0:1)) |>
+    posterior_draws()
+mfx_rep <- slopes(mod_h2_agree_rep,
+    variables = "BlueShirt",
+    newdata = datagrid(PoliticalPrime = 0:1)) |>
+    posterior_draws()
+
+ggplot(mfx_dem, aes(x = draw, fill = factor(PoliticalPrime))) +
+    stat_halfeye(slab_alpha = .5) +
+    labs(x = "Marginal Effect of a blue shirt on perception of agreement",
+         y = "Posterior density",
+         fill = "PoliticalPrime") +
+    scale_fill_manual(
+      "Political Prime", values=c("#404040", "#00AEF3"), labels=c("Not primed", "Primed")
+    ) +
+    theme_minimal()
+
+ggplot(mfx_rep, aes(x = draw, fill = factor(PoliticalPrime))) +
+    stat_halfeye(slab_alpha = .5) +
+    labs(x = "Marginal Effect of a blue shirt on perception of agreement",
+         y = "Posterior density") +
+    scale_fill_manual(
+      "Political Prime", values=c("#404040", "#ff0803"), labels=c("Not primed", "Primed")
+    ) +
+    theme_minimal()
+```
+
+In terms of whether participants are perceive that they will agree with the discussion partner, we also do not find much of a difference between those who were primed versus not.
+Looking at Democratic participants, we see that those who were primed and those who were not primed are functionally equivalent in their perceptions of whether they would agree with their hypothetical discussion partner.
+Like Democratic participants, we cannot even see a difference between the median value of the posteriors on the marginal effect of the political prime on perceptions of agreement.
+This means that Republicans who were primed relative to those who were not perceive similar levels of agreement with their discussion partner.
+
+```{r}
+#| label: fig-h2-initiate
+#| fig-cap: The marginal effect of belief of initiating a conversation
+#| fig-subcap:
+#|   - Democrats
+#|   - Republicans
+mfx_dem <- slopes(mod_h2_initiate_dem,
+    variables = "BlueShirt",
+    newdata = datagrid(PoliticalPrime = 0:1)) |>
+    posterior_draws()
+mfx_rep <- slopes(mod_h2_initiate_rep,
+    variables = "BlueShirt",
+    newdata = datagrid(PoliticalPrime = 0:1)) |>
+    posterior_draws()
+
+ggplot(mfx_dem, aes(x = draw, fill = factor(PoliticalPrime))) +
+    stat_halfeye(slab_alpha = .5) +
+    labs(x = "Marginal Effect of a blue shirt on initiating a conversation",
+         y = "Posterior density",
+         fill = "PoliticalPrime") +
+    scale_fill_manual(
+      "Political Prime", values=c("#404040", "#00AEF3"), labels=c("Not primed", "Primed")
+    ) +
+    theme_minimal()
+
+ggplot(mfx_rep, aes(x = draw, fill = factor(PoliticalPrime))) +
+    stat_halfeye(slab_alpha = .5) +
+    labs(x = "Marginal Effect of a blue shirt on initiating a conversation",
+         y = "Posterior density") +
+    scale_fill_manual(
+      "Political Prime", values=c("#404040", "#ff0803"), labels=c("Not primed", "Primed")
+    ) +
+    theme_minimal()
+```
+
+First turning to Democratic participants, we see that Democrats who saw a potential discussion partner with a blue shirt were slightly more likely to report initiating a conversation when primed relative to those who were not primed.
+These differences are quite small, however.
+We see an even smaller difference between the prime's conditional effect of the treatment upon willingness to initiate a conversation among Republican participants.
+That is, among Republican participants, the those who were primed reported the same willingness to initiate a conversation with a discussion partner regardless of whether they wre primed or not primed with politics.
 

### 2024-03-12 chapter_3/src/cleaning/study-1-cleaning.R

@@ -54,57 +54,57 @@ dbExecute(
         /*
             ConversationAgree
             CUB3D02 - I am willing to have a conversation with this person
-            -2 - Strongly disagree: 5
-            -1 - Somewhat disagree: 4
-            0 - Neither agree nor disagree: 3
-            1 - Somewhat agree: 2
-            2 - Strongly agree: 1
+            1 - Strongly disagree: 5
+            2 - Somewhat disagree: 4
+            3 - Neither agree nor disagree: 3
+            4 - Somewhat agree: 2
+            5 - Strongly agree: 1
         */
         (
             CASE
-                WHEN CUB3D02 == 5 THEN -2
-                WHEN CUB3D02 == 4 THEN -1
-                WHEN CUB3D02 == 3 THEN 0
-                WHEN CUB3D02 == 2 THEN 1
-                WHEN CUB3D02 == 1 THEN 2
+                WHEN CUB3D02 == 5 THEN 1
+                WHEN CUB3D02 == 4 THEN 2
+                WHEN CUB3D02 == 3 THEN 3
+                WHEN CUB3D02 == 2 THEN 4
+                WHEN CUB3D02 == 1 THEN 5
                 ELSE NULL
             END
         ) AS ConversationAgree,
         /*
             ViewsAgree
             CUB3D03 - I think I would agree about most things with this person
-            -2 - Strongly disagree: 5
-            -1 - Somewhat disagree: 4
-            0 - Neither agree nor disagree: 3
-            1 - Somewhat agree: 2
-            2 - Strongly agree: 1
+            1 - Strongly disagree: 5
+            2 - Somewhat disagree: 4
+            3 - Neither agree nor disagree: 3
+            4 - Somewhat agree: 2
+            5 - Strongly agree: 1
         */
         (
             CASE
-                WHEN CUB3D03 == 5 THEN -2
-                WHEN CUB3D03 == 4 THEN -1
-                WHEN CUB3D03 == 3 THEN 0
-                WHEN CUB3D03 == 2 THEN 1
-                WHEN CUB3D03 == 1 THEN 2
+                WHEN CUB3D03 == 5 THEN 1
+                WHEN CUB3D03 == 4 THEN 2
+                WHEN CUB3D03 == 3 THEN 3
+                WHEN CUB3D03 == 2 THEN 4
+                WHEN CUB3D03 == 1 THEN 5
                 ELSE NULL
             END
         ) AS ViewsAgree,
         /*
[…]

### 2024-03-12 chapter_3/src/models/study-1-models.R

@@ -4,6 +4,8 @@
 # *     Description
 # **        Script that executes Study 1 models
 
+# Set the seed
+set.seed(12102022)
 # Initialize list for the models
 mod_h1 <- list()
 mod_h2 <- list()
@@ -11,38 +13,75 @@ mod_h2 <- list()
 box::use(
     duckdb[...],
     DBI[dbConnect, dbGetQuery],
-    brms[...]
+    brms[...],
+    marginaleffects[...]
 )
 
 # Connect to the DB
 con <- dbConnect(duckdb(), dbdir = "./chapter_3/data/clean/study_1.db", read_only=TRUE)
 
-# Load the table
-df_h1 <- dbGetQuery(con, "SELECT CorrectColor, DislikeArgue, PoliticalPrime FROM Clean;")
-df <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND PoliticalPrime == 1;")
+# Load the data
+df_h1 <- dbGetQuery(con, "SELECT CorrectColor, DislikeArgue, PoliticalPrime, EnjoyChallenge FROM Clean;")
+df_dem <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND Dem3 == 1;")
+df_rep <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND Dem3 == -1;")
 
 # Models
 # *     H1
-mod_h1["main"] <- brm(
+mod_h1_main <- brm(
     CorrectColor ~ PoliticalPrime,
     data = df_h1,
     prior = set_prior("normal(0, 1)", class="b"),
 )
-mod_h1["conflict"] <- brm(
+mod_h1_conflict <- brm(
     CorrectColor ~ DislikeArgue,
     data = df_h1,
     prior = set_prior("normal(0, 1)", class="b"),
 )
-# *     H2
-mod_h2["main"] <- brm(
-   ConversationAgree ~ BlueShirt + Dem3 + BlueShirt * Dem3 + White + Education + Attention + DislikeArgue + EnjoyChallenge,
-   data = df,
-   prior = set_prior("normal(0, 1)", class="b"),
+mod_h1_conflict_b <- brm(
+    CorrectColor ~ EnjoyChallenge,
+    data = df_h1,
+    prior = set_prior("normal(0, 1)", class="b")
 )
-
+# *     H2
+mod_h2_dem <- brm(
[…]

### 2024-03-13 chapter_2/src/appendix.qmd
some drafting done

@@
   , escape = FALSE
-  , output = "latex"
+  , output = "markdown"
 )
@@
   , histogram = FALSE
+  , output = "markdown"
 )

### 2024-03-13 chapter_3/src/models/study-1-models.R

@@ -81,7 +81,11 @@ mod_h2_initiate_rep <- brm(
 )
 # Save model results
 save(
-    df_h1, df, mod_h1_main, mod_h1_conflict, mod_h2_dem, mod_h2_rep,
+    df_h1, df,
+    mod_h1_main, mod_h1_conflict, mod_h1_conflict_b,
+    mod_h2_dem, mod_h2_rep,
+    mod_h2_agree_dem, mod_h2_agree_rep,
+    mod_h2_initiate_dem, mod_h2_initiate_rep,
     file="./chapter_3/data/models/study-1-models.RData"
 )
 # Disconnect from the database

### 2024-03-23 chapter_2/src/manuscript.qmd

@@
     )
-    , output = "latex"
+    , output = "markdown"
 )
@@
   , notes = "Data source: Prolific sample."
-  , escape = FALSE
-  , output = "latex"
+  , output = "markdown"
 )

### 2024-03-23 chapter_3/src/appendix.qmd

## Chapter 3 Appendix {#sec-3-a}

```{r}
#| label: appendix-3-setup

# Load functions
box::use(
  DBI[dbConnect, dbGetQuery],
  modelsummary[modelsummary]
)
options(modelsummary_format_numeric_latex = "plain")
# Load the models
load("../data/models/study-1-models.RData")
```

### Measures

+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Measure                     | Question                                                                                                                                                                                                                                                                                                  | Coded as                                                                                                                                                           |
+=============================+:=========================================================================================================================================================================================================================================================================================================:+:==================================================================================================================================================================:+
| Age                         | Confirm your age                                                                                                                                                                                                                                                                                          | Text entry                                                                                                                                                         |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Gender                      | What is your gender identity?                                                                                                                                                                                                                                                                             | Non-binary, Female, Male, Prefer not to choose, Other                                                                                                              |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Race                        | Which ethnic or racial category best describes you?                                                                                                                                                                                                                                                       | White, non-Hispanic; Black, non-Hispanic; Hispanic; Asian or Native Hawaiian/other Pacific Islander; Native American/Alaska Native or other race; Multiple races   |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Attention                   | How often do you pay attention to what is going on in government and politics?                                                                                                                                                                                                                            | Always; Most of the time; About half the time; Some of the time; Never                                                                                             |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Dislike Argue               | Do you agree or disagree with the following statement: I dislike arguing about politics.                                                                                                                                                                                                                  | 1 = Strongly disagree, 2 = Somewhat disagree, 3 = Neither agree nor disagree, 4 = Somewhat agree, 5 = Strongly agree                                               |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Enjoy Challenge             | Do you agree or disagree with the following statement: I enjoy challenging the opinions of others.                                                                                                                                                                                                        | 1 = Strongly disagree, 2 = Somewhat disagree, 3 = Neither agree nor disagree, 4 = Somewhat agree, 5 = Strongly agree                                               |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Party ID                    | Generally speaking, do you usually think of yourself as a Democrat, a Republican, an Independent, or what?; Would you say that you are a strong [Republican/Democrat] or not a very strong [Republican/Democrat]?; Do you think of yourself as closer to the Republican party or to the Democratic party? | Republican, Democrat, Independent, Other; Strong, Not very strong; Closer to the Republican party, Neither, Closer to Democratic                                   |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Attn. Check                 | What was the color of the shirt the avatar was wearing?                                                                                                                                                                                                                                                   | I am very certain it was red, I am fairly certain it was red, I am not sure, I am fairly certain it was blue, I am very certain it was blue                        |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Political Prime             | Viewed political attitudes questionnaire before treatment.                                                                                                                                                                                                                                                | 0 = Did not respond to political attitude questionnaire first, 1 = Did respond to questionnaire first                                                              |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Blue Shirt Treatment        | Viewed Blue Shirt or Red shirt                                                                                                                                                                                                                                                                            | 0 = Assigned to red shirt treatment, 1 = Assigned to blue shirt treatment                                                                                          |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Conversation Agree          | Do you agree or disagree with the following statement: I am willing to have a conversation with this person.                                                                                                                                                                                              | 1 = Strongly disagree, 2 = Somewhat disagree, 3 = Neither agree nor disagree, 4 = Somewhat agree, 5 = Strongly agree                                               |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Views Agree                 | Do you agree or disagree with the following statement: I think I would agree about most things with this person.                                                                                                                                                                                          | 1 = Strongly disagree, 2 = Somewhat disagree, 3 = Neither agree nor disagree, 4 = Somewhat agree, 5 = Strongly agree                                               |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Initiate Agree              | Do you agree or disagree with the following statement: I can see myself initiating the conversation with this person.                                                                                                                                                                                     | 1 = Strongly disagree, 2 = Somewhat disagree, 3 = Neither agree nor disagree, 4 = Somewhat agree, 5 = Strongly agree                                               |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+

: Study 1 Measures {#tbl-study-1-measures}

{{< pagebreak >}}

### $H_1$

```{r}
#| label: tbl-ch3-hypothesis-1-main
#| tbl-cap: Full results for reported models in $H_1$
# Redefine names
list_fitted_split_1 <- list(
  "Political Prime" = mod_h1_main
  , "Dislike Arguing" = mod_h1_conflict
  , "Enjoy challenging" = mod_h1_conflict_b
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_PoliticalPrime" = "Political Prime"
    , "b_DislikeArgue" = "Dislike Argue"
    , "b_EnjoyChallenge" = "Enjoy Challenge"
    , "b_Intercept" = "Intercept"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: CES"
    , "Coefficients reflect the effect in terms of logged-odds."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

### $H_3$

```{r}
#| label: tbl-ch3-hypothesis-2-main
#| tbl-cap: Full results for reported models in $H_1$
# Redefine names
list_fitted_split_1 <- list(
  "Republicans" = mod_h2_dem,
  "Democrats" = mod_h2_rep
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_PoliticalPrime" = "Political Prime"
    , "b_BlueShirt" = "Blue Shirt"
    , "b_PoliticalPrime:BlueShirt" = "Political Prime $\\times$ Blue Shirt"
    , "b_White" = "White"
    , "b_Education" = "Education"
    , "b_Attention" = "Attention"
    , "b_DislikeArgue" = "Dislike Argue"
    , "b_EnjoyChallenge" = "Enjoy Challenge"
    , "b_Intercept" = "Intercept"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: CES"
    , "Coefficients reflect the effect in terms of logged-odds."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

```{r}
#| label: tbl-ch3-hypothesis-2-agree
#| tbl-cap: Full results for rep#| orted models in $H_2$ where the outcome is perception of sharing same views
# Redefine names
list_fitted_split_1 <- list(
  "Republicans" = mod_h2_agree_dem,
  "Democrats" = mod_h2_agree_rep
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_PoliticalPrime" = "Political Prime"
    , "b_BlueShirt" = "Blue Shirt"
    , "b_PoliticalPrime:BlueShirt" = "Political Prime $\\times$ Blue Shirt"
    , "b_White" = "White"
    , "b_Education" = "Education"
    , "b_Attention" = "Attention"
    , "b_DislikeArgue" = "Dislike Argue"
    , "b_EnjoyChallenge" = "Enjoy Challenge"
    , "b_Intercept" = "Intercept"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: CES"
    , "Coefficients reflect the effect in terms of logged-odds."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

```{r}
#| label: tbl-ch3-hypothesis-2-initiate
#| tbl-cap: Full results for reported models in $H_2$ where the outcome is initiating a conversation
# Redefine names
list_fitted_split_1 <- list(
  "Republicans" = mod_h2_initiate_dem,
  "Democrats" = mod_h2_initiate_rep
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_PoliticalPrime" = "Political Prime"
    , "b_BlueShirt" = "Blue Shirt"
    , "b_PoliticalPrime:BlueShirt" = "Political Prime $\\times$ Blue Shirt"
    , "b_White" = "White"
    , "b_Education" = "Education"
    , "b_Attention" = "Attention"
    , "b_DislikeArgue" = "Dislike Argue"
    , "b_EnjoyChallenge" = "Enjoy Challenge"
    , "b_Intercept" = "Intercept"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: CES"
    , "Coefficients reflect the effect in terms of logged-odds."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

### 2024-03-23 chapter_3/src/chapter_3.qmd

@@
 )
-
+options(modelsummary_format_numeric_latex = "plain")
 # Connect to the db
@@
   duckdb::duckdb(),
-  dbdir = "./chapter_3/data/clean/study_1.db",
+  dbdir = "../data/clean/study_1.db",
   read_only=TRUE
@@
 # Load the models
-load("./chapter_3/data/models/study-1-models.RData")
+load("../data/models/study-1-models.RData")
 ```
@@
 
-{{< include ../../../assets/_theory.qmd >}}
+{{< include ../../assets/_theory.qmd >}}
 
@@
 
-<!--
-  NOTE: ADD SOMETHING ABOUT ASYMMETRIC POLARIZATION
--->
-
 ## Study 1 {#sec-study-1}
@@
 First, I ask participants several questions about their demographic background (i.e., age, gender identity, education, and income).
-I additionally present them with a battery to measure conflict avoidance as potential confounds.
-@tbl-descriptive-demo presents the basic demographics of my participants.
+@tbl-ch3-study1-descriptive-demo presents the basic demographics of my participants.
 
 ```{r}
-#| label: tbl-descriptive-demo
+#| label: tbl-ch3-study1-descriptive-demo
 #| tbl-cap: Descriptive statistics of sample
 #| echo: false
-datasummary_skim(data=df_descriptives)
+datasummary_skim(data=df_descriptives, output="markdown")
 ```
@@
 This includes questions about their partisan identification and their attention to politics.
+I additionally present them with a battery to measure conflict avoidance.
 While I do not make a significant effort to prime politics, I design these questions to make politics salient for them.
@@
 For those not primed with politics beforehand, we should expect that the color of the shirt should not matter and for there to not be any substantively different levels of willingness to have that conversation between the red shirt, blue shirt conditions; the color of the shirt is not particularly relevant information.
+The images of the avatars are included in @fig-ch3-treatments.
+There are a few reasons for the choice in the treatment.
+First, I chose an avatar so that I am able to hold characteristics other than the shirt color constant.
+In other words, any differences in how people respond to the avatar should be because of the shirt color since that is the only thing that changes.
+Second, I did not want participants to feel confident in inferring the partisanship of the discussion partner from characteristics besides the shirt.
+Descriptively, white men tend to identify as Republican [@kaufmann_culture_2002].
+Women tend to be more split between Republicans and Democrats.
+Additionally, I chose an avatar of someone who was not White as that has been a much more consistent base for Republicans.
+Among non-White options, Latinos tend to be much less of a consistent base for either party.
+While they tend to lean more Democratic, conservative views and Republican attachments tend to be more common among some segments of the Latino community [@morin_is_2020].
+Given this, it helps reduce the chance of generating a heterogeneous treatment in that some participants may see the race and gender characteristics as conflicting with the color of shirt when.
+
+::: {#fig-ch3-treatments layout-ncol="2"}
+![Red Condition](../assets/protocol/republican_avatar.png){#fig-red-condition}
+
+![Blue Condition](../assets/protocol/democrat_avatar.png){#fig-blue-condition}
+
+Treatment
+:::
 
@@
 ```{r}
-#| label: tbl-dvs
+#| label: tbl-ch3-study1-dvs
 #| tbl-cap: Sample responses to outcome variables
@@
 
-datasummary_skim(data=df_dvs)
+datasummary_skim(data=df_dvs, output="markdown")
 ```
 
-@tbl-dvs presents the descriptive statistics of how participants responded to measures of the propensity for them to engage in a conversation with their hypothetical discussion partner once viewing their avatar.
+@tbl-ch3-study1-dvs presents the descriptive statistics of how participants responded to measures of the propensity for them to engage in a conversation with their hypothetical discussion partner once viewing their avatar.
 Overall, we see that the average participant is a bit ambivalent on all the measures.
@@
 
-To address $H_1$, the outcome variable of interest is whether or not people notice the color of the shirt (0 or 1,) as explained by whether they received the political prime or not (0 or 1).
+To address $H_1$, I test whether participants in the political prime condition are more likely to correctly identify the color of the shirt as I expect that it could be used as a heuristic to infer the partisanship of their hypothetical discussion partner.
 To measure whether participants notice the color of the shirt, I ask them to report what the color of the shirt was.
@@
 Those who reported the correct color received a value of 1 and those who were incorrect received a value of 1.
-@tbl-h1-descriptive presents the descriptive statistics for the sample on how they performed with this question.
+@tbl-ch3-h1-descriptive presents the descriptive statistics for the sample on how they performed with this question.
 
 ```{r}
-#| label: tbl-h1-descriptive
+#| label: tbl-ch3-h1-descriptive
 #| tbl-cap: Sample performance of noticing color
 #| echo: false
-datasummary_skim(data=df_h1)
+datasummary_skim(data=df_h1, output="markdown")
 ```
@@
 In other words, my prior suggests that the beta coefficient with the highest relative probability of occurring and that, if it is not 0, it should most likely be between -1 and 1.
-The results of this model are presented in @fig-h1-main.
+The predicted probability of correctly identifying the color of shirt depending on the priming condition are presented in @fig-ch3-h1-main.^[The table of full results are included in @tbl-ch3-hypothesis-1-main.]
 
 ```{r}
-#| label: fig-h1-main
+#| label: fig-ch3-h1-main
 #| fig-cap: Predicted probability of identifying the correct color
@@
 
-This model suggests that those who received the political prime were slightly less likely to correctly identify the color of shirt on the avatar.
-The difference, however, is quite small substantively.
+This model suggests those that those who received the political prime were slightly less likely to correctly identify the color of shirt on the avatar than those who were not primed.
+The difference between the political prime and the non-political prime conditions, however, is quite small substantively.
 Given that 90% of the sample correctly identified the color of shirt on the avatar, there may just be too little variation.
@@
 
-To test this, I fit two logistic regression models regressing the participants' ability to correctly identify the color of shirt on these two measures that proxy conflict avoidance.
+To test this, I fit two logistic regression models regressing the participants' ability to correctly identify the color of shirt on these two proxies of conflict avoidance.
 I use the same priors as before.
-The results of these models are included in @fig-h1-main.
+The results of these models are included in @fig-ch3-h1-main.^[The full results are reported in @tbl-ch-3-hypothesis-2-main.]
 
@@
 Therefore, I also consider a split sample approach whereby I split my sample into Democrats and Republicans and run a regression on each sub-sample.
-For each of these regressions, I include an interaction term to study the moderating effect of the prime on the effect that shirt color has on willingness to talk to them.
+For each of these ordinal logistic regressions, I include an interaction term to study the moderating effect of the prime on the effect that shirt color has on willingness to talk to them.
 Since party identification is not randomly assigned, I include potential confounders impact people's propensity to discuss politics and their party identification (i.e., age, gender, education, income, and conflict avoidance).
+The conditional marginal effects are presented in @fig-ch3-h2.^[The full results are reported in @tbl-ch3-hypothesis-2-main.]
 
 ```{r}
-#| label: fig-h2
+#| label: fig-ch3-h2
 #| fig-cap: The marginal effect of agreeing to have a conversation with a discussion partner
@@
     stat_halfeye(slab_alpha = .5) +
-    labs(x = "Marginal Effect of a blue shirt on having a conversation",
+    labs(x = " Conditional Marginal Effect of a blue shirt on having a conversation",
          y = "Posterior density",
@@
     stat_halfeye(slab_alpha = .5) +
-    labs(x = "Marginal Effect of a blue shirt on having a conversation",
+    labs(x = "Conditional Marginal Effect of a blue shirt on having a conversation",
          y = "Posterior density") +
@@
 
-The results suggest that the political prime did not have a substantive effect on shifting Democratic or Republican identifying participants.
+First, it appears that the color of shirt did not have much of an effect in shifting participants' willingness to have a conversation.
+Furthermore, the results suggest that the political prime did not have a substantive effect on shifting Democratic or Republican identifying participants.
 In the model with the Democratic participants, we see that those who received the political prime were slightly more likely to be willing to have a conversation with their hypothetical discussion partner than those without the political prime.
@@
 Conversely, Republican participants were less likely to have a conversation with a hypothetical discussion partner who was wearing a blue shirt when primed relative to those who were not primed.
+In summary, among both Republicans and Democrats the average marginal effect of the color of shirt is small and so is the conditional marginal effect of the political prime.
 
-Next, I examine whether these small effects appear for other measures of participants' perceptions of a conversation partner.
-In addition to asking participants whether they would be willing to have a conversation with their hypothetical discussion partner, I also asked them whether they "think that [they] would agree about most things with this person" and whether they "can see [themselves] initiating the conversation with this person." I fit the same models but instead regress these outcomes on my predictors.
-@fig-h2-agree presents the posterior draws of the marginal effect that the treatment has on perceptions of agreement conditional on whether the participant received a political prime.
-@fig-h2-initiate also presents the posterior draws of the marginal effect but on whether participants would initiate a conversation with their discussion partner based upon the treatment when conditioned on whether they received the political prime or not.
+Next, I examine whether these small effects appear for other measures of participants' perceptions of their assigned conversation partner.
+In addition to asking participants whether they would be willing to have a conversation with their hypothetical discussion partner, I also asked them whether they "think that [they] would agree about most things with this person" and whether they "can see [themselves] initiating the conversation with this person." I fit the same model as before with these alternative measures.
+@fig-ch3-h2-agree presents the posterior draws of the average marginal effect that the treatment has on perceptions of agreement conditional on whether the participant received a political prime.^[The full results are presented in @tbl-ch3-hypothesis-2-agree.] @fig-h2-initiate also presents the posterior draws of the marginal effect but on whether participants would initiate a conversation with their discussion partner based upon the treatment when conditioned on whether they received the political prime or not.^[The full results are presented in @tbl-ch3-hypothesis-2-initiate.]
 
 ```{r}
-#| label: fig-h2-agree
+#| label: fig-ch3-h2-agree
 #| fig-cap: The marginal effect of belief of agreeing with a discussion partner
@@
     stat_halfeye(slab_alpha = .5) +
-    labs(x = "Marginal Effect of a blue shirt on perception of agreement",
+    labs(x = "Conditional Marginal Effect of a blue shirt on perception of agreement",
          y = "Posterior density",
@@
     stat_halfeye(slab_alpha = .5) +
-    labs(x = "Marginal Effect of a blue shirt on perception of agreement",
+    labs(x = "Conditional Marginal Effect of a blue shirt on perception of agreement",
          y = "Posterior density") +
@@
 
-In terms of whether participants are perceive that they will agree with the discussion partner, we also do not find much of a difference between those who were primed versus not.
+In terms of whether participants are perceive that they will agree with the discussion partner, we see that the marginal effect of the color of shirt is quite small.
+We also do not find much of a difference between the marginal effect of the political prime treatment.
 Looking at Democratic participants, we see that those who were primed and those who were not primed are functionally equivalent in their perceptions of whether they would agree with their hypothetical discussion partner.
-Like Democratic participants, we cannot even see a difference between the median value of the posteriors on the marginal effect of the political prime on perceptions of agreement.
+Like Democratic participants, we cannot even see a difference between the median value of the posteriors on the marginal effect of the political prime on perceptions of agreement on the plot.
 This means that Republicans who were primed relative to those who were not perceive similar levels of agreement with their discussion partner.
@@
 ```{r}
-#| label: fig-h2-initiate
+#| label: fig-ch3-h2-initiate
 #| fig-cap: The marginal effect of belief of initiating a conversation
@@
     stat_halfeye(slab_alpha = .5) +
-    labs(x = "Marginal Effect of a blue shirt on initiating a conversation",
+    labs(x = "Conditional Marginal Effect of a blue shirt on initiating a conversation",
          y = "Posterior density",
@@
     stat_halfeye(slab_alpha = .5) +
-    labs(x = "Marginal Effect of a blue shirt on initiating a conversation",
+    labs(x = "Conditional Marginal Effect of a blue shirt on initiating a conversation",
          y = "Posterior density") +
@@
 That is, among Republican participants, the those who were primed reported the same willingness to initiate a conversation with a discussion partner regardless of whether they wre primed or not primed with politics.
+
+### Discussion
+
+Study 1 presents a number of "null" results. However, these results are a valuable contribution to the book. I will start with a key insight for the book.
+
+While the previous chapter demonstrates robust and strong results in support of the idea that the colors red and blue matter to politics, this study presents results that demonstrate their limitations.
+While a key insight gleaned from the study was that political priming does not appear to matter much (see a discussion of this below), we also see that participants are largely reluctant to have a conversation regardless of whether the shirt is red or blue.
+
+The second key contribution of this study is that political priming had a small effect on determining whether someone will have a conversation.
+There are a few reasons why this may be.
+If we take these results at their face value this would suggest that individuals are not paying attention to the clothing of others when making decisions on who to talk politics with.
+These results cut against not only a significant amount of research on political deliberation but also on social psychology.
+This is particularly reinforced by the finding in this study that those who are more conflict avoidant were no more likely to seek out information to determine whether there would be conflict -- to use the color of shirt as an inferential heuristic.
+We saw that partisan respondents were no more or less likely to report that they would have a disagreement with their assigned discussion partner regardless of the color of shirt or whether they were primed to think of politics.
+
+A natural inclination may attempt to point to flaws in the experimental design as a reason to ignore these findings.
+These findings do not replicate a significant number of studies.
+It is a fair tendency.
+One criticism might be that the sample was underpowered.
+This criticism would state that I have too few participants in each of the groups (e.g., Republicans placed in the blue shirt condition and were primed with politics compared to Republicans placed in the red shirt condition and were not primed with politics).
+While this may be true, simulations from my pre-registration suggested that this should not be a factor.
+My simulations when I pre-registered this study suggested that if there were a substantively meaningful effect of the treatments upon these outcomes, design and modeling choices should still be capable of detecting it.
+
+A second criticism would be that the treatment is too weak.
+This is a fair critique.
+I do not believe that this critique is enough to suggest that we should then take these results, put them in a folder somewhere and never let them see the light of day, however.
+If the treatment is indeed too weak, this is valuable information for those who study the factors explaining the propensity of political deliberation.
+Though experiments are powerful tools to control the noise and to isolate the causal effect of one predictor on an outcome, they are often hard to get right.
+Unless we field a number of experiments that make small tweaks to an experimental treatment in the social sciences, it is difficult to know whether the treatment's efficacy is generalizable and how slight tweaks to exposure to the treatment would influence our conclusions.
+What these results do is demonstrate a lower bound for the effects of outward representations of partisanship on an individual's propensity to engage in political deliberation.
+While wearing a "MAGA hat" may be an extremely obvious sign of partisan attachments, simply wearing a blue or red shirt may be too subtle for individuals to be willing to infer the partisan attachment of another person.
+
+To disagree with myself, participants did notice the color of shirt of their potential discussion partner -- 90% of the sample was able to correctly identify the color of shirt their discussion partner was wearing.
+This leads me to a third reason one may be cautious about these results is that participating in the CES may have primed politics for participants before they even reached my experiment.
+If this is the case, it is a significant flaw in the execution of the study that would explain not only the weak differences between the prime and not primed conditions but also the effects of the treatment in the first place -- everyone may have been interpreting the discussion partner with a blue shirt as a Democrat and the partner with a red shirt as a Republican.
+
+Study 2 will address a few things.
+I identified Study 2 as a test for $H_3$ and $H_4$ in my pre-registration.
+It can also help assuage this final concern by examining whether the color of shirt is a useful heuristic to infer partisanship of another person -- even in the face of explicit information about their political beliefs.
 

### 2024-03-23 chapter_3/src/cleaning/data-loading.R
doing some cleaning

@@ -1,30 +1,0 @@
-# Loading data file
-
-# Notes
-# *     Description
-# **        Script that loads and stores the data into a DB
-
-# Load libraries
-box::use(
-    haven[read_sav],
-    duckdb[...],
-    DBI[dbConnect,dbExecute]
-)
-
-# Connect to the DB
-con <- dbConnect(duckdb(), dbdir = "./chapter_3/data/clean/study_1.db")
-
-# Load the file
-df <- read_sav(
-    "./chapter_3/data/original/CCES23_CUB_OUTPUT.sav"
-)
-df_common <- read_sav(
-    "./chapter_3/data/original/CCES23_COMMON_OUTPUT.sav"
-)
-
-# Store the data in the DB
-dbWriteTable(con, "OriginalModule", df)
-dbWriteTable(con, "OriginalCommon", df_common)
-
-# Disconnect from the database
-dbDisconnect(con, shutdown=TRUE)

### 2024-03-23 chapter_3/src/cleaning/study-1-loading.R
some cleaning for study 2

@@ -1,0 +1,30 @@
+# Loading data file
+
+# Notes
+# *     Description
+# **        Script that loads and stores the data into a DB
+
+# Load libraries
+box::use(
+    haven[read_sav],
+    duckdb[...],
+    DBI[dbConnect,dbExecute]
+)
+
+# Connect to the DB
+con <- dbConnect(duckdb(), dbdir = "./chapter_3/data/clean/study_1.db")
+
+# Load the file
+df <- read_sav(
+    "./chapter_3/data/original/CCES23_CUB_OUTPUT.sav"
+)
+df_common <- read_sav(
+    "./chapter_3/data/original/CCES23_COMMON_OUTPUT.sav"
+)
+
+# Store the data in the DB
+dbWriteTable(con, "OriginalModule", df)
+dbWriteTable(con, "OriginalCommon", df_common)
+
+# Disconnect from the database
+dbDisconnect(con, shutdown=TRUE)

### 2024-03-23 chapter_3/src/cleaning/study-2-cleaning.R

@@ -1,0 +1,260 @@
+# Study 2 Cleaning
+
+# Notes
+# *     Description
+# **        Script for the cleaning of study 2 data.
+
+# Load modules
+box::use(
+    DBI[dbConnect, dbExecute],
+    duckdb[duckdb]
+)
+
+# Connect to db
+con <- dbConnect(duckdb(), dbdir = "./chapter_3/data/clean/study-2.db")
+
+# Cleaning
+dbExecute(
+    con,
+    "
+    CREATE OR REPLACE VIEW
+        CleanTemp
+    AS
+    SELECT
+        /* Participant ID */
+        Q22 AS part_id,
+        /* 
+            age 
+                Not changed
+        */
+        \"age.\" AS age,
+        /*
+            female
+                sex - Male, Female
+                0 - Male
+                1 - Female
+        */
+        (
+            CASE
+                WHEN \"sex.\" == 'Male' THEN 0
+                WHEN \"sex.\" == 'Female' THEN 1
+                ELSE NULL
+            END
+        ) AS female,
+        /*
+            education
+                education - Did not complete high school, HS Diploma, Some college, 2-year degree, Bachelor's degree, post-graduate or professional degree
+                1 - Did not complete high school
+                2 - High school diploma
+                3 - Some college, no degree
+                4 - 2-year degree
+                5 - Bachelor's degree
+                6 - Post-graduate or professional degree
+        */
+        (
+            CASE
+                WHEN education == 'Did not complete high school' THEN 1
+                WHEN education == 'High school diploma' THEN 2
+                WHEN education == 'Some college, no degree' THEN 3
+                WHEN education == '2-year degree' THEN 4
+                WHEN education LIKE 'Bachelor%s degree' THEN 5
+                WHEN education == 'Post-graduate or professional degree' THEN 6
+                ELSE NULL
+            END
+        ) AS education,
+        /*
+            white
+                race - White, Black or African American, Hispanic or latino, Asian or Asian-American, Native American, Middle Eastern, Two or more races, other
+                0 - Other
+                1 - White
+        */
+        (
+            CASE
+                WHEN \"race.\" == 'White' THEN 1
+                WHEN \"race.\" != 'White' THEN 0
[…]

### 2024-03-23 chapter_3/src/cleaning/study-2-loading.R

@@ -1,0 +1,32 @@
+# Loading data files
+
+# Notes
+# *     Description
+# **        Script that loads and stores the data into a db.
+
+# Load libraries
+box::use(
+    duckdb[...],
+    DBI[dbConnect, dbExecute]
+)
+
+# Connect to the DB
+con <- dbConnect(duckdb(), dbdir = "./chapter_3/data/clean/study-2.db")
+
+# Load the prolific demographics file
+df_demo <- read.csv(
+    "./chapter_3/data/original/prolific-demo-data.csv"
+)
+
+# Load the Qualtrics data
+df <- read.csv(
+    "./chapter_3/data/original/study-2.csv", header=TRUE
+)
+df <- df[-c(1:6), ]
+
+# Store the data in the DB
+dbWriteTable(con, "Qualtrics", df, overwrite=TRUE)
+dbWriteTable(con, "Prolific", df_demo, overwrite=TRUE)
+
+# Disconnect from the database
+dbDisconnect(con, shutdown=TRUE)
